### 2020-12-18 aFEM_paper.tex
Tex upload
Initial upload of tex documents

\documentclass[10pt,a4paper,onecolumn]{article} \usepackage[latin1]{inputenc}
\usepackage{amsmath,enumitem,datetime,xfrac,fix-cm,color,multirow,siunitx}
\usepackage{amsfonts,amssymb,mathtools,stmaryrd,dsfont,tikz,amsthm}
\usepackage[cm]{fullpage}
\definecolor{linkColor}{rgb}{0.5, 0.5, 0.5}
\usepackage[colorlinks, allcolors=linkColor, bookmarks=True]{hyperref}
\usepackage[capitalise]{cleveref}
\usetikzlibrary{positioning,trees}
\usepackage{algorithm,algpseudocode}
\graphicspath{{Figures/}}
\DeclareGraphicsExtensions{.pdf,.png}
\numberwithin{equation}{section}
\newtheorem{definition}{Definition}[section]\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]\newtheorem{example}{Example}[section]
\newtheorem{remark}{Remark}[section]
\makeatletter\let\c@definition\c@theorem\let\c@definition\c@theorem\makeatother
\makeatletter\let\c@lemma\c@theorem\let\c@lemma\c@theorem\makeatother
\makeatletter\let\c@example\c@theorem\let\c@example\c@theorem\makeatother
\makeatletter\let\c@remark\c@theorem\let\c@remark\c@theorem\makeatother
\newtheorem*{theorem*}{Theorem}

\newcommand{\Partial}[2]{\frac{\partial #1}{\partial #2}}
\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\C{A}}
\newcommand{\Vector}[3]{ \begin{pmatrix} #1 \\ #2 \\ #3 \end{pmatrix}}
\newcommand{\MTwo}[4]{\begin{pmatrix} #1 & #2 \\ #3 & #4 \end{pmatrix}}
\newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
\renewcommand{\sfrac}[2]{\,^{#1}\!\!/\!_{#2}}
\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
\newcommand{\op}[1]{\operatorname{#1}}\newcommand{\overtext}[2]{\stackrel{\text{#1}}{#2}}
\newcommand{\xmapsfrom}[1]{\reflectbox{$\xmapsto{\reflectbox{\scalebox{0.87}[0.69]{$#1$}}}$}}
\newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
\renewcommand{\P}{\F{P}}\newcommand{\E}{\F{E}}\newcommand{\1}{\F{1}}
\newcommand{\tab}{\indent}\newcommand{\Tab}{\newline\tab}
\renewcommand{\circle}[1]{\raisebox{.5pt}{\rm{\textcircled{\raisebox{-.9pt} {#1}}}}}
\newcommand{\intbar}{-\hspace{-10.5pt}\int}\newcommand{\todo}[1]{{\color{red}#1}}
\DeclareMathOperator{\st}{\;s.t.\;}\DeclareMathOperator{\as}{\;a.s.\;}\renewcommand{\epsilon}{\varepsilon}
\DeclareMathOperator*{\Union}{\bigcup}\DeclareMathOperator{\union}{\cup}
\DeclareMathOperator*{\Intersect}{\bigcap}\DeclareMathOperator{\intersect}{\cap}
\renewcommand{\bar}{\overline}\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
\renewcommand{\vec}{\mathbf}
\DeclareMathOperator*{\argmin}{argmin}\DeclareMathOperator{\TV}{TV}
\DeclareMathOperator{\prox}{prox}\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\id}{id}\DeclareMathOperator{\sign}{sign}

\newcounter{adaptStepCounter}
\newenvironment{adaptiveStep}{\refstepcounter{adaptStepCounter}}{}
\crefname{adaptStepCounter}{step}{steps}

% TODO: get rid of this stuff...
\let\linop\C
\usepackage{clipboard}\newclipboard{aFEMclipboard}
\newcommand{\UCmath}[1]{%
	\begingroup
	\ucmathlist\uppercase\expandafter{#1}%
	\endgroup
}
\newcommand{\ucmathlist}{%
	\def\alpha{\mathrm{A}}%
	\def\beta{\mathrm{B}}%
	\let\gamma=\Gamma
	\let\delta=\Delta
	\def\epsilon{\mathrm{E}}%
	\def\varepsilon{\mathrm{E}}%
	\def\zeta{\mathrm{Z}}%
	\def\eta{\mathrm{H}}%
	\let\theta=\Theta
	\let\vartheta=\Theta
	\def\iota{\mathrm{I}}%
	\def\kappa{\mathrm{K}}%
	\let\lambda=\Lambda
	\def\mu{\mathrm{M}}%
	\def\nu{\mathrm{N}}%
	\let\xi=\Xi
	\let\pi=\Pi
	\let\varpi=\Pi
	\def\rho{\mathrm{P}}%
	\def\varrho{\mathrm{P}}%
	\let\sigma=\Sigma
	\def\tau{\mathrm{T}}%
	\let\upsilon=\Upsilon
	\let\phi=\Phi
	\let\varphi=\Phi
	\def\chi{\mathrm{X}}%
	\let\psi=\Psi
	\let\omega=\Omega
}
\newcommand{\caps}[1]{\UCmath{#1}}
\usepackage{xstring}
\newcommand*{\Func}[1]{%
	\IfEqCase{#1}{%
		{0}{\op{E}}%
		{1}{\op{F}}%
		{2}{\op{G}}%
		{3}{\op{H}}%
	}[\op{F}#1]%
}
\newcommand*{\func}[1]{%
	\IfEqCase{#1}{%
		{0}{\op{e}}%
		{1}{\op{f}}%
		{2}{\op{g}}%
		{3}{\op{h}}%
	}[\op{f}#1]%
}
\newcommand*{\varf}[1]{%
	\IfEqCase{#1}{%
		{0}{u}%
		{1}{v}%
		{2}{w}%
	}[u#1]%
}
\newcommand*{\spcf}[1]{%
	\IfEqCase{#1}{%
		{0}{\F{U}}%
		{1}{\F{V}}%
		{2}{\F{W}}%
	}[\F{U}#1]%
}
\newcommand*{\vard}[1]{%
	\IfEqCase{#1}{%
		{0}{\varphi}%
		{1}{\psi}%
	}[\varphi #1]%
}
\newcommand*{\spcd}[1]{%
	\IfEqCase{#1}{%
		{0}{\Phi}%
		{1}{\Psi}%
	}[\Phi#1]%
}
\newcommand*{\varx}[1]{%
	\IfEqCase{#1}{%
		{0}{x}%
		{1}{y}%
		{2}{z}%
		{3}{r}%
	}[x#1]%
}
\newcommand*{\vart}[1]{%
	\IfEqCase{#1}{%
		{0}{s}%
		{1}{t}%
	}[t#1]%
}
\newcommand*{\vars}[1]{%
	\IfEqCase{#1}{%
		{0}{\alpha}%
		{1}{\beta}%
		{2}{\gamma}%
		{3}{a}%
		{4}{b}%
		{5}{c}%
	}[k#1]%
}
\newcommand*{\data}[1]{%
	\IfEqCase{#1}{%
		{0}{\eta}%
		{1}{\nu}%
	}[g]%
}
\newcommand{\Domain}{\Omega}
\newcommand{\domain}{\omega}
\newcommand{\diam}{\op{diam}}
\newcommand{\meshsize}{h}
\DeclareMathOperator{\noise}{noise}

% capital forms
\newcommand*{\Varx}[1]{\caps{\varx{#1}}}
\newcommand*{\Varf}[1]{\caps{\varf{#1}}}
\newcommand*{\Vart}[1]{\caps{\vart{#1}}}
\newcommand*{\Vars}[1]{\caps{\vars{#1}}}
% vector forms
\newcommand*{\vvarx}[1]{\vec{\varx{#1}}}\newcommand*{\vVarx}[1]{\vec{\Varx{#1}}}
\newcommand*{\vvart}[1]{\vec{\vart{#1}}}\newcommand*{\vvars}[1]{\vec{\vars{#1}}}
\newcommand*{\vvard}[1]{\vec{\vard{#1}}}\newcommand*{\vdata}[1]{\vec{\data{#1}}}
\newcommand*{\vVarf}[1]{\vecf{\Varf{#1}}}\newcommand*{\vvarf}[1]{\vecf{\varf{#1}}}

\author{Robert Tovey}
\date{\longdate\today}
\title{FISTA with adaptive discretisations}
\begin{document}
	\maketitle

%In many variational approaches to inverse problems, optimisation problems are often written in a continuous setting but solved with a discrete optimisation algorithm. Consider what happens when $\sqrt{e^2}$ is computed in your favourite programming language. We have asked a `continuous' question and have been given a `discrete' answer with very well controlled error bounds.
%
%The parallel to this for optimisation is that we still do not have infinite computing memory or processing power, but we still want to compute minimisers to a known accuracy with efficient implementations. It is typically much harder to control discretisation errors in optimisation problems, for instance the $\Gamma$-convergence of discrete total variation \cite{Bartels2012,Bartels2015} or the approximation errors for wavelets/curvelets/sheerlets \cite{Mallat1999,Candes2004,Guo2007}. These are typically quite weak guarantees valid for asymptotic resolution/time and are hard to quantify in a specific example. In this work we propose an algorithm with three aims:
%\begin{itemize}
%	\item All computations are discrete but the asymptotic reconstruction is exact, even for infinite dimensional reconstructions in a Banach space, with a guaranteed rate.
%	\item Distance to the infinite dimensional minimiser can be quantified.
%	\item Discretisation is adaptively optimised for the particular minimiser.
%\end{itemize}
%
%We choose to modify the FISTA algorithm because it is quite general and performs very well in discrete optimisation problems. The strategy will be to follow the standard FISTA algorithm as closely as possible. The only difference is that at each iteration, computations will only be performed on a finite dimensional subspace. 
%
%One key issue is that FISTA is intrinsically designed to converge only in $L^2$. In finite dimensions there is no issue, all norms are equal and so convergence rates are equal for all problems up to scaling constants. On the other hand, in infinite dimensions there exist minimisers which are not in $L^2$. In this case, we find that the rate will always be slower than for standard FISTA but still at a guaranteed rate.
%
%We perform two numerical experiments where the minimiser is in $L^1\setminus L^2$ which demonstrates the reduced rate. We also show an example where the minimiser is in $\ell^2(\R^m)$ for some $m$ which is not known a priori and observe that the refining FISTA algorithm achieves linear convergence.

\section{Introduction}
The standard setting of the Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) is that there exists a Hilbert space $\F H$ over which we wish to minimise the function 
\begin{equation}\label{eq:ca: min F = fD+fC}
	\min_{\varf0\in\F H}\Func0(\varf0)  \qquad\text{such that}\qquad \Func0(\varf0)\coloneqq \func1(\varf0) + \func2(\varf0),
\end{equation}
where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function. FISTA is a practically fast algorithm which, for many choices of $\Func0$, generates a sequence of iterates $\varf0_n\in\F H$ such that $\Func0(\varf0_n)$ converges at the optimal rate of $O(n^{-2})$ \cite{Beck2009,Chambolle2015}.

The canonical example for this work will be the Lasso energy,
$$\Func0(\varf0) = \tfrac12\norm{\A\varf0-\vdata0}_2^2 + \mu\norm{\varf0}_1$$
where $\vdata0\in\R^m$ is some observed data, $\A\colon \C M(\R^d)\to \R^m$ is the forward map and $\mu>0$ is a chosen scalar. It is known that there exist minimisers of $\Func0$ of the form:
$$\varf0^* = \sum_{i=1}^{m}\vars0_i\delta_{\vvarx0_i}, $$
for some $\vars0_i\in\R$ and where $\delta_{\vvarx0_i}$ is the Dirac delta function centred at $\vvarx0_i\in\R^d$ \cite{Unser2016,Boyer2019}. The challenge with this minimiser is that $\varf0^*\in L^1\setminus L^2$, so exact FISTA cannot be applied to this problem. On the other hand, $\varf0^*$ has a very nice structure which we expect can be easily and efficiently represented by, for instance, a basis of finite elements.

In this work we propose a modification of FISTA which addresses both of these points. During each iteration we restrict computation to a subspace, i.e. $\varf0_n\in\spcf0^n\subset\F H$.
For infinite dimensional optimisation, this allows us to reconstruct $\varf0^*$ to an arbitrary precision in finite time. Alternatively, for finite dimensional optimisation this potentially allows for a more computationally efficient variant of the classical FISTA algorithm.

Inexact optimisation is a well-established field which can be seen to encompass methods such as coordinate descent \cite{Wright2015}, stochastic gradient \cite{Spall2005,Bottou2018}, or indeed approximate FISTA-like algorithms \cite{Jiang2012,Villa2013}. The result of \Cref{thm:ca: exponential FISTA convergence} is very similar to \cite[Proposition 2]{Schmidt2011} and \cite[Proposition 3.3]{Aujol2015}. The key novelty is the concept of convergence outside of the Hilbert space $\F H$. Additionally assuming that errors come from quantified subspace approximations, we can also provide explicit rates.

\subsection{Outline}
This chapter is organised as follows. \Cref{sec:ca: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, \Cref{alg:ca: refining FISTA}. The main theoretical contribution of this work is the convergence analysis of \Cref{alg:ca: refining FISTA} which is split into two parts: first we outline the proof structure in \Cref{sec:ca: recipe}, then we state the specific results in the case of FISTA in \Cref{sec:ca: FISTA convergence}. The main results are \Cref{thm:ca: exponential FISTA convergence} and \Cref{thm:ca: practical refinement criteria} which extend the convergence of FISTA to infinite dimensional Banach spaces with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.

\Cref{sec:ca: general examples} presents some general results for the application of \Cref{alg:ca: refining FISTA} and \Cref{sec:ca: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation. In particular, we describe how to choose efficient refining discretisations to approximate $\varf0^*$, estimate the convergence of $\Func0$, and identify the support of $\varf0^*$. The numerical results in \Cref{sec:ca: numerics} demonstrate these techniques in four different models demonstrating the sharpness of our analysis and the computational efficiency of adaptive discretisations.

\section{Definitions and notation}\label{sec:ca: prelims}
We consider optimisation of \eqref{eq:ca: min F = fD+fC} over two spaces, the Banach space $(\spcf0,\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
$$ \exists\varf0^*\in \spcf0 \quad\st\quad \Func0(\varf0^*) = \min_{\varf0\in\spcf0}\Func0(\varf0) = \min_{\varf0\in\F H}\Func0(\varf0).$$
We further define
$$\Func0_0\colon \varf0\mapsto \Func0(\varf0)-\Func0(\varf0^*).$$
Note that $\Func0_0$ is uniquely defined, even if $\varf0^*$ may not be.

We propose a refining FISTA algorithm in \Cref{alg:ca: refining FISTA} for a choice of refining subspaces $\spcf0^n\subset\spcf0^{n+1}\subset \spcf0\cap\F H$ for $n=0,1,\ldots$. The only difference is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$. Indeed, if $\spcf0^n=\spcf0=\F H$ then this is just the standard FISTA algorithm.

Without loss of generality we will assume $L=1$, i.e. $\nabla\func1$ is 1-Lipschitz. To get the general statement of any of the results which follow, replace $\Func0$ with $\frac{\Func0}{L}$. Implicitly, the only impact of $L$ is scaling the convergence rates which are only given up to a constant factor anyway. A more important distinction is to say that the properties of $\func1$ and $\func2$ are stated with respect to the Hilbert norm. In particular,
$$\norm{\nabla\func1(\varf0)- \nabla\func1(\varf1)} \leq \norm{\varf0-\varf1}$$
for all $\varf0,\varf1\in\F H$ and $\func2$ is called `simple' if
$$\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \func2(\varf0) $$
is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$.

Finally we introduce the concept of an orthogonal projection in the setting of this work. For a subspace $\spcf0^n\subset\spcf0\cap\F H$ we define the orthogonal projection $\Pi_n\colon (\spcf0^n)^*\to \spcf0^n$ to be any extension of the function such that 
$$\IP{\Pi_n\varf0}{\varf1} = \IP{\varf0}{\varf1} \text{ for all } \varf0\in(\spcf0^n)^*, \ \varf1\in\spcf0^n.$$
This definition is non-standard as we view $(\spcf0^n)^*$ embedded in $\spcf0$. Note that $\spcf0^n\subset\F H$ implies that $(\spcf0^n)^*\supset\F H$, therefore $\Pi_n$ is an extension of the classical orthogonal projection. It is convenient to allow an extension here because $\spcf0$ may be bigger than $\F H$, $(\spcf0^n)^*$ is the largest space such that $\Pi_n$ is well-defined. Beyond this, the Hahn-Banach theorem may allow the domain of $\Pi_n$ to be extended further, but the definition is no longer unique. For example, in 1D the value of $\IP{\delta_0}{\frac{1}{\sqrt[4]{\varx0}}}$ is not well-defined, but the value of $\IP{\delta_0}{\1_{[0,1]}}$ can be chosen to be consistent with some sequence of molifiers. To account for this possibility, we shall state that the domain of $\Pi_n$ is $\bar{(\spcf0^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.

Constant factors will generally not be tracked during the proofs in this chapter. For sequences $(a_n)_{n=1}^\infty$,$(b_n)_{n=1}^\infty$ we will frequently use the notation:
\begin{align*}
	a_n \lesssim b_n \qquad &\iff \qquad \exists C,N>0 \st a_n \leq C b_n \text{ for all } n>N,
	\\ a_n \simeq b_n \qquad &\iff \qquad a_n\lesssim b_n \lesssim a_n.
\end{align*}

\begin{algorithm}[b!]\caption{Refining sub-space FISTA}\label{alg:ca: refining FISTA}
	\centering
	\begin{algorithmic}[1]
		\State Choose $(\spcf0^n)_{n\in\F N}$, $\varf0_0\in \spcf0^0$ and some FISTA stepsize choice $(\vart1_n)$
		\State $\varf1_0\gets \varf0_0, n\gets0$
		\Repeat
		\State $\bar{\varf0}_n \gets (1-\tfrac{1}{\vart1_n})\varf0_n + \tfrac{1}{\vart1_n}\varf1_n$
		\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \func1(\bar{\varf0}_n)}^2+\func2(\varf0)$
		\State $\varf1_{n+1} \gets (1-\vart1_n)\varf0_n + \vart1_n\varf0_{n+1}$
		\State $n\gets n+1$
		\Until{converged}
	\end{algorithmic}
\end{algorithm}

\section{General proof recipe}\label{sec:ca: recipe}
In this work we focus on the FISTA algorithm, however, the key ingredients of the proof do not rely on the particular structure of FISTA. In this section we will sketch the general `recipe' of the convergence proof for adaptive schemes in a Banach space setting.

During this section, we will refer to the structure of FISTA as motivation. In particular, we recall the classical FISTA convergence guarantee given in \cite[Theorem 2]{Chambolle2015}:
\begin{equation}\label{eq:ca: classical FISTA}
	t_N^2\Func0_0(\varf0_N) + \sum^{N-1}_{n=1}\rho_n\Func0_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf0^*}^2 \leq \tfrac12\norm{\varf0_0-\varf0^*}^2
\end{equation}
for some $t_N\simeq N$ and $\rho_n\geq0$.

\subsubsection{Step 1: Quantifying the scaling properties}
\begin{adaptiveStep}\label{step:ca: step 1 smoothness}
	The first step is to quantify how $\Func0$ and $\norm\cdot$ behave as the discretisation refines, or resolution increases. In \Cref{alg:ca: refining FISTA} we are given the subspaces $\spcf0^n$ which we partition into a sequence of milestones. In particular, we assume there exists $n_k\in\F N$ and constants $\vars3_{\Varf0},\vars3_{\Func0}\geq1$ such that:
	$$n_0<n_1<\ldots, \qquad \norm{\argmin_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0)} \lesssim \vars3_{\Varf0}^k, \qquad \text{and}\qquad \min_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0) \lesssim \vars3_{\Func0}^{-k}.$$

	The idea is that $\spcf0^{n_k}$ is a discretisation at resolution $\meshsize^k$ for some $\meshsize<1$ and therefore the minimum of $\Func0_0$ decays exponentially while the norm of discrete minimisers potentially grows exponentially. In \Cref{sec:ca: general examples} we will see that this exponential scaling is very natural.

	The value of $\vars3_{\Varf0}$ is dictated by the Banach space $\spcf0$ in relation $\F H$. If $\varf0^*\in \spcf0\setminus\F H$, as for Lasso, then the right-hand side of \eqref{eq:ca: classical FISTA} becomes infinity. All norms are equivalent on finite dimensional subspaces, but the scaling of this relationship is quantified by $\vars3_{\Varf0}>1$. The value of $\vars3_{\Func0}>1$ is an indicator of how easy $\Func0$ is to discretise. If $\Func0$ is very smooth and the choice of discrete basis is very efficient then $\vars3_{\Func0}$ is large. The trade-off between $\vars3_{\Func0}$ and $\vars3_{\Varf0}$ dictates the final convergence rate of the algorithm.
\end{adaptiveStep}

\subsubsection{Step 2: Generalising the convergence bound}
\begin{adaptiveStep}\label{step:ca: step 2 convergence bound}
	The bound in \eqref{eq:ca: classical FISTA} is only valid when $\spcf0^n$ is a constant sequence. The first analytical step is to quantify the effect of refinement. \Cref{thm:ca: mini FISTA convergence} gives an expression for this for generic choices of $\spcf0^n$ in \Cref{alg:ca: refining FISTA}.

	If $\spcf0^n$ is a constant sequence then \Cref{thm:ca: mini FISTA convergence} recovers the right-hand side of \eqref{eq:ca: classical FISTA} through a large telescoping sum, the exact form of the sum does not matter at this moment. Without further assumptions, the sum does not telescope and the bound grows linearly with $n$. If we re-introduce the sequence $n_k$ from the previous step then we can simplify this inequality. In particular, if 
	$$ \spcf0^{n_k} = \spcf0^{n_k+1} = \ldots = \spcf0^{n_{k+1}-1},$$
	then the right-hand side will telescope on the intervals $(n_k,n_{k+1})$ and scale only with $k\simeq\log(n)$. The result of this is presented in \Cref{thm:ca: mini exponential FISTA convergence}.

	The take-home message here is that the introduction of the milestones $n_k$ greatly simplifies the convergence bound expression and allows us to utilise the scaling properties described in \Cref{step:ca: step 1 smoothness}.
\end{adaptiveStep}

\subsubsection{Step 3: Sufficiently fast refinement}
\begin{adaptiveStep}\label{step:ca: step 3 sufficiently fast}
	In \Cref{step:ca: step 2 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq:ca: classical FISTA} by a constant factor. In particular, it is equivalent to run \Cref{alg:ca: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed subspace $\spcf0^N$. \Cref{thm:ca: sufficiently fast} shows that this is true so long as $\spcf0^n$ refine sufficiently quickly, i.e. $n_k$ are sufficiently small. In summary, in comparison with \eqref{eq:ca: classical FISTA}, we show $$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} = O\left(\frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\Func0(\varf0)}^2}{N^2}\right)$$
	for all $N\leq n_K$. 
\end{adaptiveStep}

\subsubsection{Step 4: Sufficiently slow refinement}
\begin{adaptiveStep}\label{step:ca: step 4 sufficiently slow}
	The result of \Cref{step:ca: step 3 sufficiently fast} is sufficient to prove convergence, but not directly a rate. If the subspaces refine too quickly then this factor of $\norm{\varf0^*}=\infty$ will slow the rate of convergence. Refinement should happen sufficiently quickly so that we do not waste time overfitting to the discretisation, but low resolution problems converge faster therefore we should then refine as slowly as possible. \Cref{thm:ca: sufficiently slow} balances these two factors in an optimal way for the FISTA algorithm. This results in a convergence guarantee of the form
	$$ \Func0_0(\varf0_N) \lesssim \frac{N^{2\epsilon}}{N^2}$$
	for all $N\in\F N$, some $\epsilon\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\Func0}$. In particular, if $\varf0^*\in\F H$ then $\epsilon=0$ recovers the classical rate.
\end{adaptiveStep}

\subsubsection{Step 5: Adaptivity}
\begin{adaptiveStep}\label{step:ca: step 5 adaptivity}
	Up to this point we have implicitly focused on the case where $\spcf0^n$ and $n_k$ are chosen a priori. Here we emphasise some of the challenges which are faced when extending results to allow for on-the-fly greedy adaptivity.

	Spatial adaptivity is robust, so long as the scaling properties of \Cref{step:ca: step 1 smoothness} are satisfied. The only other constraint is to ensure that the partial telescoping of \Cref{step:ca: step 2 convergence bound} still holds. In the case of FISTA, \Cref{thm:ca: mini exponential FISTA convergence} shows that this only requires the existence of $\tilde{\varf2}_k\in\spcf0^{n_k}$ such that 
	$$\tilde{\varf2}_k\in\spcf0^{n_k}\cap\spcf0^{n_k+1}\cap\ldots\cap\spcf0^{n_{k+1}-1}.$$

	Refinement time adaptivity is more challenging for FISTA due to the non-descent property of the algorithm. The idea is that resolution should increase rapidly while $\Func0$ is `easy' to optimise then default to the rate of \Cref{step:ca: step 4 sufficiently slow} when it is `hard'. The result of this is \Cref{thm:ca: stronger exponential FISTA convergence} which shows 
	$$ \min_{n\leq N}\Func0_0(\varf0_n) \lesssim \frac{N^{2\epsilon}}{N^2}$$
	for all $N\in\F N$, the same $\epsilon\in[0,1)$ from \Cref{step:ca: step 4 sufficiently slow}. The penalty for accelerating the refinement time is a potential loss of stability in $\Func0(\varf0_n)$, however, the asymptotic rate is equivalent and this behaviour has not been seen in numerical experiments.
\end{adaptiveStep}

\section{Proof of convergence}\label{sec:ca: FISTA convergence}
In this section we follow the recipe motivated in \Cref{sec:ca: recipe} to prove convergence of two variants of \Cref{alg:ca: refining FISTA}. Motivated by this argument, we will first formalise the definition of the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$.
\begin{definition}\label{def:ca: exp subspaces}
	Fix $\vars3_{\Varf0},\vars3_{\Func0}\geq 1$ and a sequence of subspaces $\{\tilde{\spcf0}^k\subset\F H\cap\spcf0\st k\in\F N\}$. We say that $\{\tilde{\spcf0}^k\}$ is a \emph{$(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$} if 
	$$ \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k \qquad\text{and}\qquad \Func0_0(\tilde{\varf2}_k) \lesssim \vars3_{\Func0}^{-k} $$
	for all $k\in\F N$ and some choice $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$.
\end{definition}
In this section we will simply assume that such sequences exist and in \Cref{sec:ca: general examples} we will give some more general examples. Each of the main theorems and lemmas will be stated with a sketch proof in this section. The details of the proofs are either trivial or very technical and are therefore placed in \Cref{app:ca: FISTA convergence} to preserve the flow of the argument.

\subsection{Computing the convergence bound}
For \Cref{step:ca: step 2 convergence bound} of \Cref{sec:ca: recipe} we look to replicate the classical bound of the form in \eqref{eq:ca: classical FISTA} for \Cref{alg:ca: refining FISTA}. The proofs in this step follow the classical arguments of \cite{Beck2009,Chambolle2015} very closely.

\subsubsection{Single iterations}
We first wish to understand a single iteration of \Cref{alg:ca: refining FISTA}. This is done through the following two lemmas.
\begin{lemma}[equivalent to {\cite[Lemma 1]{Chambolle2015}}]\label{thm:ca: descent lemma}
	\Copy{thm:ca: descent lemma}{
		Suppose $\nabla \func1$ is 1-Lipschitz, for any $\bar{\varf0}\in \spcf0^{n-1}$ define
		$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \func1(\bar{\varf0})}^2+\func2(\varf0).$$
		Then, for all $\varf2\in\bar{(\spcf0^n)^*}\supset\F H$, we have
		$$\Func0(\varf0) + \tfrac12\norm{\varf0-\Pi_n\varf2}^2 \leq \Func0(\Pi_n\varf2) + \tfrac12\norm{\bar{\varf0}-\Pi_n\varf2}^2$$
		where $\Pi_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.
	}
\end{lemma}
This is exactly the result of \cite{Chambolle2015} applied to the function $\varf0\mapsto\Func0(\Pi_n\varf0)$. Applying \Cref{thm:ca: descent lemma} to the iterates from \Cref{alg:ca: refining FISTA} gives a more explicit inequality.

\begin{lemma}[analogous to {\cite[Theorem 2]{Chambolle2015}, \cite[Theorem 1]{Beck2009}}]\label{thm:ca: one step FISTA}
	\Copy{thm:ca: one step FISTA}{
		Let $\spcf0^n\subset\F H\cap\spcf0$ and $\varf2_n\in\spcf0^n$ be chosen arbitrarily and $\varf0_n$/$\varf1_n$ be generated by \Cref{alg:ca: refining FISTA} for all $n\in\F N$.
		For all $n\in\F N$ it holds that}
	\begin{equation}
		\vart1_{n}^2(\Func0(\varf0_{n}) - \Func0(\varf2_n)) - (\vart1_{n}^2-\vart1_{n})(\Func0(\varf0_{n-1})-\Func0(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.\label{eq:ca: one-step FISTA}
	\end{equation}
\end{lemma}

The proof of this lemma is a result of the convexity of $\Func0$ for a well chosen $\varf2$ in \Cref{thm:ca: descent lemma}.

\subsubsection{Generic convergence bound}
\Cref{thm:ca: one step FISTA} gives us an understanding of a single iteration of \Cref{alg:ca: refining FISTA}, summing over $n$ then gives our generic convergence bound for any variant of \Cref{alg:ca: refining FISTA}.

\begin{theorem}\label{thm:ca: mini FISTA convergence}
	\Copy{thm:ca: mini FISTA convergence}{
		Fix a sequence of subspaces $\{\spcf0^n\subset\spcf0\cap\F H\st n\in\F N\}$, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(\vart1_n)_{n\in\F N}$. Let $\varf0_n$ and $\varf1_n$ be generated by \Cref{alg:ca: refining FISTA}. 
		Then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have}
	\begin{multline}\label{eq:ca: FISTA inequality}
		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
		\\ + \sum^N_{n=1} \vart1_n\Func0_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
	\end{multline}
\end{theorem}
This result is the key approximation for showing convergence of FISTA with refining sub-spaces. In the classical setting, we have $\spcf0^n=\spcf0=\F H$, $\varf2_n=\varf0^*$ and the extra terms on the right-hand side collapse to 0.

%The natural choice in \Cref{eq:ca: FISTA inequality} is $\varf2_n=\Pi_n\varf0^*$, however, there are simple counter-examples which give $\Func0(\Pi_n\varf0^*)=\infty$ and so this inequality becomes useless. A simple example, if $\func1(\varf0) = \norm{\varf0}_2^2$, $\func2$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$ and $\spcf0^n$ is a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$. On the other hand, $\Pi_n \varf0^*$ is the piecewise projection to the mean so it must be that $\Pi_n \varf0^*\notin \F D$. To see this, suppose one of these pixels is $[\varx0_0-\meshsize,\varx0_0+\meshsize]$, then $$\Pi_n\varf0^*\left(\varx0_0+\sfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \intbar_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}\varf0^*(\varx0)d\varx0= \varx0_0 < \varx0_0+\sfrac\meshsize2,$$
%which violates the constraint of $\F D$.
%
%The choice $\varf2_n=\argmin_{\varf0\in\spcf0^n}\Func0(\varf0)$ is much more robust and allows us to apply this algorithm much more broadly. The penalty for this flexibility is a more complicated analysis, each time the sub-space changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.

\subsubsection{Convergence bound with milestones}
In standard FISTA, the right-hand side of \eqref{eq:ca: FISTA inequality} is a constant. The following lemma minimises the growth of the `constant' as a function of $N$ by partially telescoping the sum on the right-hand side. 
\begin{lemma}\label{thm:ca: mini exponential FISTA convergence}
	\Copy{thm:ca: mini exponential FISTA convergence}{
		Let $\varf0_n$, $\varf1_n$ be generated by \Cref{alg:ca: refining FISTA}, $(n_k\in\F N)_{k=0}^\infty$ be a monotone increasing sequence, and define
		$$\tilde{\spcf0}^k \coloneqq \spcf0^{n_k}, \qquad \tilde{\varf2}_k \in \argmin_{\varf0\in\tilde{\spcf0}^k} \Func0(\varf0).$$
		If
		$$ \tilde{\varf2}_k \in \spcf0^n \qquad\text{ for all }\qquad n_k\leq n<n_{k+1},\ k\in\F N,$$
		then for all $K\in\F N$, $n_K\leq N<n_{K+1}$ we have
		\begin{multline*}
			\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \frac{\norm{\varf1_N-\tilde{\varf2}_K}^2}{2} \leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\Func0_0(\tilde{\varf2}_K) \\+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\Func0_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}
		\end{multline*}
		where $C = \frac{\norm{\varf0_0-\tilde{\varf2}_0}^2-\norm{\tilde{\varf2}_0}^2}{2}$.
	}
\end{lemma}
The introduction of $n_k$ has greatly simplified the expression of \Cref{thm:ca: mini FISTA convergence}. On the right-hand side, we now only consider $\Func0_0$ evaluated on the sequence $\tilde{\varf2}_k$ and there are only $K$ non-zero inner-product terms remaining.

\subsection{Refinement without overfitting}
The result of \Cref{thm:ca: mini exponential FISTA convergence} is still optimal in the sense that it reduces to \eqref{eq:ca: classical FISTA} when $\spcf0^n=\spcf0$, however, now we would like to achieve the equivalent rate (up to a constant factor) including refinement. This can be likened to the idea of overfitting to the discretisation. It is only efficient to optimise the discrete energy while the discrete gap $\Func0(\varf0_n)-\Func0(\tilde{\varf2}_k)$ is comparable to the continuous gap $\Func0(\varf0_n)-\Func0(\varf0^*)$.

This is achieved by two assumptions, first we use the structure of \Cref{def:ca: exp subspaces} to quantify the properties of the refinement, then we force $K$ to scale with $\log(N)$ to slow the growth of the right hand side. This is summarised in the following lemma.

\begin{lemma}\label{thm:ca: sufficiently fast}
	\Copy{thm:ca: sufficiently fast}{
		Suppose $\spcf0^n, \varf0_n, \varf1_n$ and $n_k$ satisfy the conditions of \Cref{thm:ca: mini exponential FISTA convergence} and $\{\tilde{\spcf0}^k\}$ forms an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$.
		If either:
		\begin{itemize}
			\item $\vars3_{\Varf0}>1$ and $n_k^2\lesssim \vars3_{\Func0}^k\vars3_{\Varf0}^{2k}$,
			\item or $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\Func0}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty,$
		\end{itemize}
		then
		$$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}$$
		for all $n_K\leq N< n_{K+1}$.}
\end{lemma}

We make two observations of the optimality of \Cref{thm:ca: sufficiently fast}:
\begin{itemize}
	\item The convergence guarantee for $N$ iterations of classical FISTA in the space $\spcf0^N$ is 
	$$ \Func0_0(\varf0_N) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\Func0(\varf0)}^2}{N^2} + \min_{\varf0\in\spcf0^N}\Func0(\varf0) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} + \vars3_{\Func0}^{-K}.$$
	This is equivalent to \Cref{thm:ca: sufficiently fast} under the conditions on $n_k$.
	\item If $\spcf0$ is finite dimensional then the $\vars3_{\Varf0}=1$ is almost trivially satisfied. Norms in finite dimensions are equivalent and any discretisation can be achieved with a finite number of refinements (i.e. the sums over $k$ are finite). 
\end{itemize}

\subsubsection{Convergence rate}
At the end of \Cref{step:ca: step 3 sufficiently fast} we have shown that $\Func0(\varf0_n)$ converges at a rate depending on $k$ and $n$ so long as $k$ grows sufficiently quickly. On the other hand, as $k$ grows, the rate becomes worse and so we need to also put a lower limit on the growth of $n_k$. The following lemma computes the global convergence rate of $\Func0(\varf0_n)$ when $k$ grows at the minimum rate which is consistent with \Cref{thm:ca: sufficiently fast}.

As a special case, note that if $\vars3_{\Varf0}=1$ then \Cref{thm:ca: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate. This is in fact a special case of \cite{Aujol2015}. If $\varf0^*\in\F H$ then it is not possible to refine `too quickly' and the following lemma is not needed.

\begin{lemma}\label{thm:ca: sufficiently slow}
	\Copy{thm:ca: sufficiently slow}{
		Suppose $\varf0_n$ and $n_k$ are sequences satisfying 
		$$\Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \vars3_{\Func0}^K\vars3_{\Varf0}^{2K},$$
		then 
		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\epsilon)}}\qquad \text{ where } \qquad \epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}.$$}
\end{lemma}

\subsubsection{FISTA convergence with a priori discretisation}
We can summarise \Cref{thm:ca: mini exponential FISTA convergence,thm:ca: sufficiently fast,thm:ca: sufficiently slow} into a single FISTA iteration. The following theorem states the convergence guarantees when $\spcf0^n$ and $n_k$ are chosen a priori.
\begin{theorem}\label{thm:ca: exponential FISTA convergence}
	\Copy{thm:ca: exponential FISTA convergence}{
		Let $\{\tilde{\spcf0}^k\st k\in\F N\}$ be an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$ and choose any $\spcf0^n$ such that 
		$$ \tilde{\spcf0}^k = \spcf0^{n_k}, \qquad \tilde{\varf2}_k \in \spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
		for all $k\in\F N$. Compute $\varf0_n$, $\varf1_n$ by \Cref{alg:ca: refining FISTA} and choose $\tilde{\varf2}_k \in \argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$.

		\bigbreak\noindent Suppose that either:
		\begin{itemize}
			\item $\vars3_{\Varf0}>1$ and $n_k^2\simeq \vars3_{\Func0}^k\vars3_{\Varf0}^{2k}$,
			\item or $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\Func0}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$,
		\end{itemize}
		then
		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\epsilon)}}\qquad \text{ where } \qquad \epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}$$
		uniformly for $N\in\F N$.
	}
\end{theorem}
This theorem is very easy to implement and requires very little knowledge of how to estimate $\Func0_0(\varf0_n)$. So long as $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be computed analytically, choosing $\tilde{\spcf0}^k$ to be uniform discretisations and $\tilde{\spcf0}^k = \spcf0^{n_k}=\ldots= \spcf0^{n_{k+1}-1}$ will give the stated convergence rate.

\subsubsection{FISTA convergence with adaptivity}
\Cref{thm:ca: sufficiently fast} gives a sufficient condition for converging at the rate $O(N^{2(\epsilon-1)})$ but it is not necessary and in fact limits the potential convergence rate. To see this, if $\vars3_{\Func0}$ is a sharp estimate of $\Func0$, note that 
$$\Func0_0(\varf0_N) \geq \min_{\varf0\in\spcf0^N}\Func0_0(\varf0) \simeq \vars3_{\Func0}^{-K} \simeq\frac{\vars3_{\Varf0}^{2K}}{N^2} \simeq N^{2(\epsilon-1)}.$$
To go beyond this rate (for example the linear convergence which will be seen in \Cref{sec:ca: wavelet examples}) we need to consider choosing $n_k$ adaptively.

While \Cref{thm:ca: exponential FISTA convergence} also allows for spatial adaptivity, we will make further comment here as it links strongly with the choice of $n_k$. Suppose $\{\tilde{\spcf0}^k\st k\in\F N\}$ is an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$. To ensure that $\{\spcf0^{n_k}\st k\in\F N\}$ also satisfies the condition, it is sufficient to verify two properties:
$$ \varf0^{n_K-1}\in\spcf0^{n_K}\subset \bigcup_{k=0}^K\tilde{\spcf0}^k \qquad\text{and}\qquad \Func0_0(\varf0^{n_K-1}) \lesssim \vars3_{\Func0}^{-K}.$$
The subspace inclusion guarantees the condition for $\vars3_{\Varf0}$ and $\Func0_0(\tilde{\varf2}_K) = \min_{\varf0\in\spcf0^{n_K}}\Func0_0(\varf0) \leq \Func0_0(\varf0_{n_K-1})$ confirms the condition for $\vars3_{\Func0}$.

For both adaptive choice of $n_k$ and $\spcf0^n$, accurate estimation of $\Func0_0(\varf0_n)$ is key. The idea of the following theorem is that we combine estimates of $\Func0_0(\varf0_n)$ with a `backstop' condition; `small' refinements can happen at any time and `big' refinements should happen as soon as $\Func0_0(\varf0_n)\lesssim \vars3_{\Func0}^{-k}$ for the appropriate $k\in\F N$.

Without any way to estimate $\Func0_0(\varf0_n)$, we must rely on \Cref{thm:ca: sufficiently fast} for a naive a priori bound. If $\Func0_0(\varf0_n)$ can be computed exactly then we do not need to enforce $n_k^2\lesssim \vars3_{\Func0}^k\vars3_{\Varf0}^{2k}$ at all; it is implicitly guaranteed. For any intermediate case, we should combine estimates and choose the best one. This is summarised by \Cref{thm:ca: stronger exponential FISTA convergence}.

\begin{theorem}\label{thm:ca: stronger exponential FISTA convergence}
	\Copy{thm:ca: stronger exponential FISTA convergence}{
		Let $\{\spcf0^n\subset\F H\cap\spcf0\st n\in\F N\}$ be a sequence of subspaces and $n_k\in\F N$ a monotone increasing sequence such that
		$$ \tilde{\spcf0}^k \coloneqq \spcf0^{n_k}\ni \varf0_{n_k-1}, \qquad \tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
		for all $k\in\F N$.
		Compute $\varf0_n$, $\varf1_n$ by \Cref{alg:ca: refining FISTA}.

		\bigbreak\noindent Suppose there exist $\vars3_{\Varf0},\vars3_{\Func0}\geq1$ such that either:
		\begin{itemize}
			\item $\vars3_{\Varf0}>1$ and $n_k^2\lesssim \vars3_{\Func0}^k\vars3_{\Varf0}^{2k}$,
			\item or $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\Func0}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$
		\end{itemize}
		and both
		$$ \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k \qquad\text{and}\qquad \Func0_0(\varf0_{n_K-1}) \lesssim \vars3_{\Func0}^{-K}.$$
		Whenever these conditions on $n_k$ are satisfied, then
		$$\min_{n\leq N}\Func0_0(\varf0_n) \lesssim \frac{1}{N^{2(1-\epsilon)}}\qquad \text{ where } \qquad \epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}$$
		uniformly for $N\in\F N$.
	}
\end{theorem}
This theorem can be directly compared with \Cref{thm:ca: exponential FISTA convergence}. In particular, we note that the convergence rate is the same in both theorems but the price for better adaptivity is a slightly weaker stability guarantee (i.e. the addition of the min on the left-hand side).

In a practical sense, \Cref{thm:ca: exponential FISTA convergence} provides a worst case convergence rate but if the observed convergence is faster then the refinement should also be accelerated. The issue arises if $\Func0$ is a function which is `easy' to minimise for small $n$ ($n_k$ is small) but `hard' for large $n$ (\Cref{thm:ca: sufficiently fast} becomes sharp). If this behaviour is made to oscillate, then the convergence will also be oscillatory although still optimal in the sense of \Cref{thm:ca: stronger exponential FISTA convergence}.

\begin{remark}
	The convergence guarantee of \Cref{thm:ca: stronger exponential FISTA convergence} can be strengthened back to the monotone statement $\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\epsilon)}}$ whenever $$\tilde{\varf2}_k \in \bigcap_{n=n_k}^N\spcf0^n$$
	for the appropriate $k\in\F N$. This shows that the non-monotone convergence guarantee is somehow related to non-monotonicity of the discretisation, if $\spcf0^n\subset\spcf0^{n+1}$ for all $n\in\F N$ then the above condition is always satisfied. It is currently unclear how to make this statement more precise without an excessive number of constraints on the choice of $\spcf0^n$.
\end{remark}

\Cref{thm:ca: stronger exponential FISTA convergence} relies on estimation of when $\Func0_0(\varf0_n) \lesssim \vars3_{\Func0}^{-k}$ although there are many equivalent characterisations for this. Some are described in the following lemma.

\begin{lemma}\label{thm:ca: practical refinement criteria}
	\Copy{thm:ca: practical refinement criteria}{
		Let $\{\tilde{\spcf0}^k\st k\in\F N\}$ be a sequence of subspaces with some points $\varf0_k\in \tilde{\spcf0}^k$ and $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$. Suppose that $\norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k$. Any of the following conditions are sufficient to show that $\{\tilde{\spcf0}^k\}$ is an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$:
		\begin{enumerate}
			\item Small continuous gap refinement: $ \Func0_0(\varf0_k)\leq \vars1\vars3_{\Func0}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
			\item Small discrete gap refinement: $\Func0_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\Func0}^{-k}$ and $ \Func0_0(\varf0_k)-\Func0_0(\tilde{\varf2}_{k-1})\leq \vars1\vars3_{\Func0}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
			\item Small relative gap refinement: $ \Func0_0(\varf0_k) - \Func0_0(\tilde{\varf2}_{k-1}) \leq \vars1\Func0_0(\varf0_k)$ for all $k\in\F N$, some $0<\vars1\leq \frac{1}{1+\vars3_{\Func0}}$.
			\item Small continuous gradient refinement: $ \Norm{\partial\Func0(\varf0_k)}_*\leq \vars1\vars3_{\Func0}^{-k}$ for all $k\in\F N$, some $\vars1>0$, and sublevel sets of $\Func0$ are $\Norm\cdot$-bounded.
			\item Small discrete gradient refinement: $\Func0_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\Func0}^{-k}$ and $\Norm{\Pi_k\partial\Func0(\varf0_k)}_*\leq \vars1\vars3_{\Func0}^{-k}$ for all $k\in\F N$, some $\vars1>0$, and sublevel sets of $\Func0$ are $\Norm\cdot$-bounded. The operator $\Pi_k\colon\F H\to\tilde{\spcf0}^k$ is the orthogonal projection.
		\end{enumerate}
	}
\end{lemma}

The refinement criteria described by \Cref{thm:ca: practical refinement criteria} can be split into two groups. Cases (1), (3), and (4) justify that $\tilde{\spcf0}^k$ is good enough whenever $\varf0_k$ (or $\varf0_{n_k-1}$ in \Cref{thm:ca: stronger exponential FISTA convergence}) is contained in $\tilde{\spcf0}^k$. In cases (2) and (5), $\varf0_k$ is good enough to choose $n_k$ but $\varf0_k\in\tilde{\spcf0}^k$ is not sufficient to validate $\tilde{\spcf0}^k$ on its own.

Another splitting of the criteria is into gap and gradient computations. Typically, gradient norms (in (4) and (5)) should be easier to estimate than gaps because they only require local knowledge rather than global, i.e. $\partial\Func0(\varf0_n)$ rather than an estimate of $\Func0(\varf0^*)$. Implicitly, the global information comes from an extra condition on $\Func0$ to assert that sublevel sets are bounded.

\section{General examples}\label{sec:ca: general examples}
In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, \Cref{alg:ca: refining FISTA} is much more broadly applicable. The aim of this section is to justify this fact and demonstrate that the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be easily computed in many examples.

The trivial source of examples is any problem where $\spcf0$ is finite dimensional. In this case \Cref{thm:ca: exponential FISTA convergence,thm:ca: stronger exponential FISTA convergence} both achieve the standard FISTA rate, almost by default. The conditions on $\{\spcf0^n\st n\in\F N\}$ prevent `oscillations' in the discretisation and therefore \Cref{alg:ca: refining FISTA} becomes standard FISTA after a finite number of iterations (i.e. $n_k=\infty$ for some $k$).

For less trivial examples, we explore the use of finite element bases for discretisation when $\F H = L^2(\Domain)$ for some compact $\Domain\subset\R^d$. Informally, we wish to generate spaces $\{\tilde{\spcf0}^k\st k\in\F N\}$ with the properties:
\begin{itemize}
	\item each $\tilde{\spcf0}^k$ is a finite dimensional subspace of $L^\infty$, 
	\item each $\tilde{\spcf0}^k$ can be spanned by shifting and rescaling elements of $\tilde{\spcf0}^0$,
	\item and $\tilde{\spcf0}^k$ are known to have good approximation rates in $\Norm\cdot$.
\end{itemize}
The first point makes it easy to compute the analytical equivalence between $\norm\cdot$ and $\Norm\cdot$, the second point dictates the scaling with respect to $k$, the third point links back to optimisation. Our formal definitions for finite element spaces are given below.
\begin{definition}
	Suppose $\spcf0\subset L^p(\Domain)$ for some compact domain $\Domain\subset\R^d$. We say that $\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$ is a \emph{mesh} if 
	$$\domain_i^k\subset\Domain, \qquad |\domain_i^k\cap\domain^k_j| = 0$$
	for all $i$ and $j$. We say that $\tilde{\spcf0}^k\subset \spcf0\cap\F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\varf0\in\tilde{\spcf0}^k$ there exists $\varf0_i^k\in\tilde{\spcf0}^k$ such that
	$$\supp(\varf0_i^k)\subset \bar{\domain_i^k}, \qquad \varf0(\vvarx0) = \varf0^k_i(\vvarx0) \qquad \text{ for a.e. }\vvarx0\in\domain_i^k, \text{ all } i\in\F N.$$

	We say that a sequence of finite element sub-spaces $\tilde{\spcf0}^k\subset \spcf0\cap \F H$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\spcf0}^0$ such that for any $\varf0_i^k\in\tilde{\spcf0}^k$ with $\supp(\varf0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that 
	$$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \varf0_i^k(\vvarx0) = \sum_{j=1}^N\vars2_je_j(\vars0 \vvarx0+\vvars1) \quad \text{ for a.e. }\vvarx0\in\domain_i^k, \quad \supp(e_j(\vars0\cdot+\vvars1))\subset\bar{\domain_i^k}. $$

	We say that $(\tilde{\spcf0}^k)_k$ is \emph{of order $p$} if
	$$\min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*} \lesssim_{\varf0^*} \meshsize^{kp}.$$
	We allow the implicit constant to have any dependence on $\varf0^*$ so long as it is finite. In the case of Sobolev spaces, we would expect an inequality of the form
	$\min_{\varf2\in\tilde{\spcf0}^k}\norm{\varf2-\varf0^*}_{W^{0,q}} \lesssim \meshsize^{kp}\norm{\varf0^*}_{W^{p,q}}$ \cite{Strang1972}.
\end{definition}
We note that any piecewise polynomial finite element space can be used to form a $\meshsize$-refining sequence of subspaces. Wavelets almost satisfy this definition but not the support condition, each space contains every scale of wavelet. Similarly, a Fourier basis does satisfy nice scaling properties but each basis vector has global support. Both of these exceptions are important and could be accounted for with further analysis but we focus on the more standard finite element case. The following theorem shows that all finite element spaces achieve the same basic rates of convergence in \Cref{alg:ca: refining FISTA}, depending on the particular properties of $\Norm\cdot$ and $\Func0$.
\begin{theorem}\label{thm:ca: generic a_U and a_E}
	Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$. If $(\tilde{\spcf0}^k)_k$ is a sequence of $\meshsize$-refining finite element spaces of order $p$ then
	\begin{align*}
		\vars3_{\Varf0} &\leq \splitln{1}{q\geq 2}{\sqrt{\meshsize^{-d}}}{q<2},
		\\\vars3_{\Func0} &\geq \begin{cases}
			\meshsize^{-p} & \Func0 \text{ is $\Norm\cdot$-Lipschitz at }\varf0^*
			\\\meshsize^{-2p} & \Func0 \text{ is $\Norm\cdot$-smooth at }\varf0^*
		\end{cases}\ .
	\end{align*}
	If $\func2$ is not Lipschitz at $\varf0^*$ but $\func1$ is $\Norm\cdot$-Lipschitz and 
	$$\min_{\varf2\in\tilde{\spcf0}^k}\left\{\Norm{\varf2-\varf0^*}\st \func2(\varf2)\leq \func2(\varf0^*)\right\} \lesssim \min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*},$$
	then, again, $\vars3_{\Func0}\geq\meshsize^{-p}$. 
\end{theorem}
The proof of this theorem is in \Cref{app:ca: generic a_U and a_E}. The main take-home for this theorem is that the computation of $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ is typically very simple and obvious given a particular choice of $\Norm\cdot$ and $\Func0$. The only non-trivial case is when $\func2$ is not smooth enough to estimate directly. So long as $\tilde{\spcf0}^k$ are sufficiently dense in sublevel sets of $\func2$, the smoothness of $\func1$ is sufficient to give a convergence rate.

\section{Lasso minimisation}\label{sec:ca: Lasso definition}
We now return to the concrete example of Lasso which will be used for numerical results in \Cref{sec:ca: numerics}. We consider three forms of Lasso which will be referred to as continuous, countable, and discete Lasso depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively. In each case, the energy can be written as 
\begin{equation}\label{eq:ca: Lasso energy}
	\Func0(\varf0) = \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu\Norm{\varf0}
\end{equation}
for some $\A\colon \spcf0\cup\F H\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$.

The aim of this section is to develop all of the necessary tools for implementing \Cref{alg:ca: refining FISTA} on the energy \eqref{eq:ca: Lasso energy} through either \Cref{thm:ca: exponential FISTA convergence} or \Cref{thm:ca: stronger exponential FISTA convergence}. This includes computing the rates $\vars3_{\Varf0}$ and $\vars3_{\Func0}$, estimating the continuous gap $\Func0_0(\varf0_n)$, and developing an efficient refinement choice for $\spcf0^n$.

\subsection{Continuous case}\label{sec:ca: continuous lasso rate}
We start by estimating rates in the case $\spcf0=\C M(\Domain)$ where $\Domain =[0,1]^d$. In this case we choose $\tilde{\spcf0}^k$ to be the span of all piecewise constant functions on a mesh of squares with maximum side length $2^{-k}$ (i.e. $\meshsize=\sfrac12$).

We would like to apply \Cref{thm:ca: generic a_U and a_E} to compute the rate of convergence although $\norm\cdot_1$ is too strong a metric and results in order $p=0$. This can be seen because for any $\varf0\in L^1(\Domain^d)$, 
$$\norm{\varf0-\delta_0}_1 = \sup_{\vard0\in C(\Domain^d), \norm{\vard0}_\infty\leq 1} \IP{\vard0}{\varf0-\delta_0} = \norm{\varf0}_1+\norm{\delta_0}_1 \geq 1.$$ 
The result of \Cref{thm:ca: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ (whether or not $p=0$) and choosing $\Norm\cdot$ to be an appropriate negative Sobolev norm or transport metric gives $p=1$ and $\vars3_{\Func0} = 2^1$. We will work through this second statement explicitly to demonstrate the additional requirements on $\A$.

For any $\varf2\in\tilde{\spcf0}^k$ such that $\norm{\varf2}_1\leq \norm{\varf0^*}_1$, we have
\begin{align*}
	\Func0(\varf2)-\Func0(\varf0^*) &=  \tfrac12\norm{\A\varf2-\vdata0}^2 - \tfrac12\norm{\A\varf0^*-\vdata0}^2 + \mu\left(\Norm{\varf2}-\Norm{\varf0^*}\right)
	\\&\leq \tfrac12\norm{\A\varf2-\vdata0}^2 - \tfrac12\norm{\A\varf0^*-\vdata0}^2
	\\&= \IP{\tfrac12\A(\varf2+\varf0^*)-\vdata0}{\A(\varf2-\varf0^*)}
	\\&\leq \max(\norm{\A\varf2-\vdata0},\norm{\A\varf0^*-\vdata0})\norm{\A(\varf2-\varf0^*)} 
	\\&\leq \sqrt{2\Func0(\varf2)}\norm{\A(\varf2-\varf0^*)}.
\end{align*}
For any bounded linear extension to the orthogonal projection $\tilde\Pi_k\colon\spcf0\to\tilde{\spcf0}^k$, choose $\varf2 = \tilde\Pi_k\varf0^*$, then we get
$$\Func0(\varf2)-\Func0(\varf0^*) \lesssim \norm{\A(\tilde\Pi_k\varf0^*-\varf0^*)} \leq \norm{(\tilde\Pi_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$$
Expanding this operator norm further,
\begin{multline*}
	\norm{(\tilde\Pi_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde\Pi_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}} 
	\\= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}
\end{multline*}
where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.

This computation confirms two things, firstly that the scaling constant is indeed $\vars3_{\Func0} = 2$, and secondly that the required smoothness to achieve a good rate with \Cref{alg:ca: refining FISTA} is that $\A^*\colon\R^m\to C^1(\Domain)$ is a bounded operator. This accounts for the fact that $\C M(\Domain)$ is such a large space containing distributions. In \Cref{sec:ca: smoothing operators} we will show two practical examples were this (semi)norm is accurately computable.

Inserting the computed rates into \Cref{thm:ca: exponential FISTA convergence} or \Cref{thm:ca: stronger exponential FISTA convergence} gives the guaranteed convergence rate
\begin{equation}\label{eq:ca: Lasso energy rate}
	\epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} = \frac{d}{1+d} \quad \implies \quad \Func0_0(\varf0_N) \lesssim N^{-2(1-\epsilon)} = N^{-\frac{2}{1+d}}.
\end{equation}
This energy rate also corresponds to a resolution rate, on iteration $N$ with $N^2\sim (\vars3_{\Func0}\vars3_{\Varf0}^2)^k$ we expect the resolution to be
\begin{equation}\label{eq:ca: Lasso resolution rate}
	\meshsize = 2^{-k} = \left(\vars3_{\Func0}\vars3_{\Varf0}^2\right)^{\frac{k}{1+d}} \sim N^{-\frac{2}{1+d}}.
\end{equation}

\subsection{Countable and discrete case}
We now extend the rate computations to the case when $\spcf0=\ell^1(\R)$, or a finite dimensional subspace. The key fact here is that, even when $\spcf0$ is infinite dimensional, it is known (e.g. \cite[Theorem 2]{Unser2016} and \cite[Corollary 2]{Boyer2019}) that $\varf0^*$ can be chosen to have at most $m$ non-zeros. If this is the case, then $\varf0^*\in \ell^2(\R)$; this makes the analysis much simpler than in the continuous case. In this subsection we will ignore the discrete case as a simple sub-case of the countable.

For countable Lasso we consider discretisation subspaces of the form 
$$\tilde{\spcf0}^k = \{\varf0\in \ell^1(\R) \st i\notin J_k\implies \varf0_i=0\}$$ for some sets $J_k\subset\F N$, i.e. infinite vectors with finitely many non-zeros. The key change in analysis from the continuous case is that sparse vectors in $\ell^1(\R)$ are also in $\ell^2(\R)$. Because of this, $\vars3_{\Varf0}=1$ which leads to the expected optimal rate
$$\min_{n\leq N} \Func0_0(\varf0_n) \lesssim \frac{1}{N^2},$$
independent of $\vars3_{\Func0}$ or any additional properties of $\A$. The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of \Cref{thm:ca: exponential FISTA convergence,thm:ca: stronger exponential FISTA convergence} hold trivially.

\subsection{Refinement metrics}\label{sec:ca: Lasso gap and gradient}
\Cref{thm:ca: practical refinement criteria} shows that adaptive refinement can be performed based on estimates of the function gap or the gradient. In this subsection we provide estimates for these values which can be easily computed.

\subsubsection{Bounds for discretised functionals}\label{sec:ca: bound discrete}
We start by computing estimates for discretised Lasso. This covers the cases when either continuous/countable Lasso is projected onto $\spcf0^n$, or $\spcf0$ is finite dimensional. For notation we will use the continuous case. To recover the other cases, just replace continuous indexing ($\varf0(\vvarx0)$) with discrete ($\varf0_i$).

Let $\Pi_n\colon\spcf0\to\spcf0^n$ denote the orthogonal projection (in fact the unique bounded extension). For Lasso, discretising the function $\Func0$ ($\varf0\mapsto\Func0(\Pi_n\varf0)$) is equivalent to replacing $\varf0$ with $\Pi_n\varf0$, and $\A^*$ with $\Pi_n\A^*$.

\paragraph{Discrete gradient}
We can use this formulation to compute the discrete sub-derivative at $\varf0_n\in\spcf0^n$:
\begin{align*}
	\partial_n \Func0(\Pi_n\varf0_n)(\vvarx0) &= [\Pi_n\A^*(\A\varf0_n-\vdata0)](\vvarx0) + \begin{cases}
		\{+\mu\} & \varf0_n(\vvarx0)>0 \\ [-\mu,\mu] & \varf0_n(\vvarx0)=0 
		\\\{-\mu\} & \varf0_n(\vvarx0)<0 
	\end{cases} 
	\\&\eqqcolon [\Pi_n\A^*(\A\varf0_n-\vdata0)](\vvarx0) + \mu\Pi_n\sign(\varf0_n(\vvarx0))
\end{align*}
where we define $\vart0+\mu[-1,1] = [\vart0-\mu,\vart0+\mu]$ for all $\vart0\in\R$, $\mu\geq0$.

We need a metric to decide whether $\partial_n\Func0$ is small. As $\Norm\cdot = \norm\cdot_1$, the natural metric is $\Norm\cdot_* = \norm\cdot_\infty$ and so we get the estimate
\begin{align*}
	\Norm{\partial_n \Func0(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\min\left\{|\varf1| \st \varf1\in \Pi_n\A^*(\A\varf0_n-\vdata0)(\vvarx0) +  \mu\sign(\varf0_n(\vvarx0))\right\}
	\\&= \max_{\vvarx0\in\Domain}\begin{cases}
		|[\Pi_n\A^*(\A\varf0_n-\vdata0)(\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
		\\|[\Pi_n\A^*(\A\varf0_n-\vdata0)(\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
		\\\max\left(|[\Pi_n\A^*(\A\varf0_n-\vdata0)(\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
	\end{cases}
\end{align*}
which can be used in \Cref{thm:ca: practical refinement criteria}.

\paragraph{Discrete gap}
We now move on to the discrete gap, $\Func0(\varf0_n)-\min_{\varf0\in\spcf0^n}\Func0(\varf0)$. This can be computed with a dual representation, such as that used by \cite{Duval2017a},
\begin{align*}
	\min_{\varf0\in \spcf0^n} \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu\Norm{\varf0} &= \min_{\varf0\in\F H}\max_{\vvard0\in\R^m} \ip{(\A\Pi_n\varf0-\vdata0)}{ \vvard0} +\mu\Norm{\Pi_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
	\\&= \max_{\vvard0\in\R^m}\min_{\varf0\in\F H} \ip{(\A\Pi_n\varf0-\vdata0)}{\vvard0} +\mu\Norm{\Pi_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
	\\&= \max_{\vvard0\in\R^m} \splitln{-\ip{\vdata0}{\vvard0} -\tfrac12\norm{\vvard0}_{\ell^2}^2}{\Norm{\Pi_n\A^*\vvard0}_*\leq \mu}{-\infty}{\text{else}}
	\\&= -\min_{\vvard0\in\R^m} \underbrace{\tfrac12\norm{\vvard0}_{\ell^2}^2+\ip{\vdata0}{\vvard0}}_{\eqqcolon \Func0^*(\vvard0)}  + \chi(\Norm{\Pi_n\A^*\vvard0}_*\leq \mu).
\end{align*}
In particular,
$$\Func0(\varf0) - \min_{\varf0\in\spcf0^n}\Func0(\varf0) = \Func0(\varf0) + \min_{\Norm{\Pi_n\A^*\vvard0}_*\leq \mu} \Func0^*(\vvard0) \leq \Func0(\varf0) + \Func0^*(\vvard0)$$
for any feasible $\vvard0\in\R^m$. Differentiating the saddle point with respect to $\vvard0$, if $\vvard0^*$ is the maximiser for $\varf0^*\in\argmin_{\varf0\in\spcf0^n}\Func0(\varf0)$ then
$$ \vvard0^* = \A\varf0^*-\vdata0.$$
We remark briefly that it is more conventional to include the constraint in the definition of $\Func0^*$. We choose to omit it here to highlight that it is only the constraint which changes between the discrete and continuous cases; $\Func0^*$ will remain the same.

Given $\varf0_n\in \spcf0^n$, the optimality condition motivates a simple rule for choosing $\vvard0$:
$$\vvard0_n\coloneqq \A\varf0_n - \vdata0, \qquad \Func0(\varf0)-\min_{\varf0'\in\spcf0^n}\Func0(\varf0') \leq \Func0(\varf0) +\min_{\vars2\geq 0}\left\{\Func0^*(\vars2\vvard0_n) \st \vars2 \Norm{\Pi_n\A^*\vvard0_n}_*\leq \mu\right\}$$
with optimal choice
$$\vars2 =\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\Pi_n\A^*\vvard0_n}_*}\right)\right).$$
To apply \Cref{alg:ca: refining FISTA}, we are assuming that both $\func1(\varf0_n) = \frac12\norm{\vvard0_n}_{\ell^2}^2$ and $\Pi_n\nabla\func1(\varf0_n) = \Pi_n\A^*\vvard0_n$ are easily computable, therefore $\vars2$ and $\Func0(\varf0_n) +\Func0^*(\vars2\vvard0_n)$ are also easy to compute.

\subsubsection{Bounds for countable functionals}
Extending the results of \Cref{sec:ca: bound discrete} to $\spcf0=\ell^1(\R)$ is analytically very simple but relies heavily on the specific choice of $\A$. The computations of gradients and gaps carry straight over replacing $\Pi_n$ with $\id$ and adding the sets $J_n\subset\F N$ which define $\spcf0^n = \{\varf0\in\ell^1\st i\notin J_n\implies \varf0_i=0\}$. In particular,
\begin{align*}
	\Norm{\partial\Func0(\varf0_n)}_* &= \max_{i\in\F N}\begin{cases}
		|[\A^*\vvard0_n]_i + \mu| & [\varf0_n]_i>0
		\\|[\A^*\vvard0_n]_i - \mu| & [\varf0_n]_i<0
		\\\max\left(|[\A^*\vvard0_n]_i| - \mu, 0\right) & [\varf0_n]_i = 0
	\end{cases}
	\\ \Func0_0(\varf0_n) &\leq \Func0(\varf0_n) + \Func0(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right)
\end{align*}
where $\vvard0_n = \A\varf0_n-\vdata0\in\R^m$ is always exactly computable.

In the countable case, the sets $J_n$ give a clear partition into known/unknown values in these definitions. For $i\in J_n$ the computation is the same as in \Cref{sec:ca: bound discrete}, then for $i\notin J_n$ we know $[\varf0_n]_i=0$ which simplifies the remaining computations. This leads to:
\begin{align*}
	\Norm{\partial\Func0(\varf0_n)}_* &= \max\left(\max_{i\in J_n}|[\partial\Func0(\varf0_n)]_i|,\ \max_{i\notin J_n} |[\partial\Func0(\varf0_n)]_i|\right)
	\\&= \max\left(\Norm{\partial_n\Func0(\varf0_n)}_*,\ \max_{i\notin J_n} |[\A^*\vvard0_n]_i|-\mu\right)
	\\ \Norm{\A^*\vvard0_n}_* &= \max\left(\max_{i\in J_n}|[\A^*\vvard0_n]_i|,\ \max_{i\notin J_n} |[\A^*\vvard0_n]_i|\right)
	\\ &= \max\left(\Norm{\Pi_n\A^*\vvard0_n}_*,\ \max_{i\notin J_n} |[\A^*\vvard0_n]_i|\right).
\end{align*}
Both estimates only rely on an upper bound of $\max_{i\notin J_n} |[\A^*\vvard0_n]_i|$. This must be computed on a per-example basis, one example is seen in \Cref{sec:ca: wavelet examples}.

\subsubsection{Bounds for continuous functionals}\label{sec:ca: bound continuous}
Finally, we extend the results of \Cref{sec:ca: bound discrete} to continuous Lasso. Similar to the countable case, the exact formulae can be written down immediately:
\begin{align*}
	\Norm{\partial\Func0(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\begin{cases}
		|[\A^*\vvard0_n](\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
		\\|[\A^*\vvard0_n](\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
		\\\max\left(|[\A^*\vvard0_n](\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
	\end{cases}
	\\ \Func0_0(\varf0_n) &\leq \Func0(\varf0_n) + \Func0(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right).
\end{align*}
If these quantities are not analytically tractable then we use the mesh $\F M^n$ corresponding to $\spcf0^n$ to decompose the bounds:
\begin{align*}
	\Norm{\partial \Func0(\varf0_n)}_* &= \max_{\domain_i^n\in\F M^n} \begin{cases}
		\norm{\A^*\vvard0_n + \mu}_{L^\infty(\domain_i^n)} & \varf0_n|_{\domain_i^n} > 0
		\\\norm{\A^*\vvard0_n - \mu}_{L^\infty(\domain_i^n)} & \varf0_n|_{\domain_i^n} < 0
		\\\max(0, \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}-\mu) & \varf0_n|_{\domain_i^n} = 0
	\end{cases}
	\\ \Norm{\A^*\vvard0_n}_* &= \max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}.
\end{align*}
Now, both estimates rely on cell-wise supremum norms of $\A^*\vvard0_n$ which we assume is sufficiently smooth. We will use a cell-wise Taylor expansion to provide such an estimate which is both accurate and relatively tight. For instance, let $\vvarx0_i$ be the midpoint of the square $\domain_i^n$, then 
$$\norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq |[\A^*\vvard0_n](\vvarx0_i)| + \frac{\op{diam}(\domain_i^n)}{2}|[\nabla\A^*\vvard0_n](\vvarx0_i)| + \frac{\op{diam}(\domain_i^n)^2}{8}|\A^*\vvard0_n|_{C^2}.$$
In this work we chose a first order expansion because we are looking for extrema of $\A^*\vvard0_n$, i.e. we are most interested in the squares $\domain_i^n$ such that 
$$|[\A^*\vvard0_n](\vvarx0_i)| \approx \mu, \qquad |[\nabla\A^*\vvard0_n](\vvarx0_i)| \approx 0, \qquad [\nabla^2\A^*\vvard0_n](\vvarx0_i) \preceq 0. $$
A zeroth order expansion would be optimally inefficient (approximating $|[\nabla\A^*\vvard0_n](\vvarx0_i)|$ with $|\A^*\vvard0_n|_{C^1}$) and a second order expansion would possibly be the most elegant but harder to implement. We found that a first order expansion was simple and efficient.

The bounds presented here for continuous Lasso emphasise the twinned properties required for adaptive mesh optimisation. The mesh should be refined greedily to the structures of $\varf0^*$, but also must be sufficiently uniform to prove that $\varf0^*$ is the function we are approximating. This is a classical exploitation/exploration trade-off; exploiting visible structure whilst searching for other structures which are not yet visible.

\subsection{Support detection}\label{sec:ca: support detection}
The main motivation for using Lasso in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\varf0^*$ is also provably close to the `true' support \cite{Duval2017a,Poon2018}. If $\varf0_n\approx \varf0^*$ in the appropriate sense, then we should also be able to quantify the statement $\op{supp}(\varf0_n)\approx\op{supp}(\varf0^*)$. This is the aim of this subsection.

The work of \cite{Duval2017a,Poon2018} and many others characterise the support of $\varf0^*$ very precisely. In particular, the support is at most $m$ distinct points and (with continuous notation) are a subset of $\{ \vvarx0\in\Domain \st |\A^*\vvard0^*|(\vvarx0) = \mu\} $. Less formally, this can also be seen from the the gradient computations in \Cref{sec:ca: Lasso gap and gradient}, for all $\vvarx0\in\supp(\varf0^*)$
$$0\in \partial \Func0(\varf0^*)(\vvarx0) = [\A^*\vvard0^*](\vvarx0) + \mu\sign(\varf0^*(\vvarx0)).$$
From a computational perspective, identifying the support accurately allows for the most efficient choice of $\spcf0^n$, however, to exclude areas from the support requires very accurate quantification.

Heuristically, we will use strong convexity of $\Func0^*$ and smoothness of $\A^*$ to quantify the statement:
$$ \text{if}\quad \Func0(\varf0_n) + \Func0^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st |[\A^*\vvard0_n](\vvarx0)|\ll \mu\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
First we use the strong convexity of $\Func0^*$, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible then
$$\tfrac12\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}^2 \leq \Func0^*(\vars2_0\vvard0_n) - \Func0^*(\vvard0^*) = \Func0^*(\vars2_0\vvard0_n) + \Func0(\varf0^*) \leq \Func0^*(\vars2_0\vvard0_n) + \Func0(\varf0_n),$$
which gives an easily computable bound on $\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}$. Now we estimate $\A^*\vvard0_n$ on the support of $\varf0^*$:
\begin{align*}
	\min_{\vvarx0\in\supp(\varf0^*)} |[\Pi_n\A^*\vvard0_n](\vvarx0)| &\geq \min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0_n](\vvarx0)|
	\\&= \frac1{\vars2_0}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vars2_0 \vvard0_n](\vvarx0)|
	\\&\geq \frac1{\vars2_0}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0^*](\vvarx0)| - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
	\\&= \frac1{\vars2_0}\min_{\vvarx0\in\supp(\varf0^*)} \mu - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
	\\&\geq \frac1{\vars2_0}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vvard0_n-\vvard0^*}_{\ell^2}\right).
\end{align*}
Therefore,
\begin{equation}
	|[\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\Func0(\varf0_n)+\Func0^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq:ca: support equation}
\end{equation}
This equation is valid when $\vvarx0$ is either a continuous or countable index, the only distinction is to switch to $\ell^\infty$ in the norm of $\A^*$. To make the equivalent statement on the discretised problem, simply replace $\vars2_0$ with $\vars2$ and $\A^*$ with $\Pi_n\A^*$.

We can make two quick observations about this formula:
\begin{itemize}
	\item The convergence guarantee from \Cref{thm:ca: exponential FISTA convergence} is for the quantity $\Func0(\varf0_n)-\Func0(\varf0^*)$, the more relevant quantity here is $\Func0^*(\vars2_0\vvard0_n)+\Func0(\varf0^*)$ for which there is no proven rate.
	\item In \Cref{sec:ca: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
\end{itemize}

\subsection{Operator norms}\label{sec:ca: smoothing operators}
For numerical implementation of Lasso, we are required to accurately estimate several operator norms of $\A$. For $\func1$ to be 1-Lipschitz we must divide by $\norm{\A^*\A}$, and the adaptivity described in \Cref{sec:ca: continuous lasso rate,sec:ca: bound continuous,sec:ca: support detection} requires estimates of $|\A^*|_{\ell^2\to L^\infty}$, $|\A^*|_{\ell^2\to C^1}$, and $|\A^*|_{\ell^2\to C^2}$. The aim for this section is to provide estimates of these norms and seminorms for the numerical examples presented in \Cref{sec:ca: numerics}.

We start by specifying the structure of $\A$. By linearity, there must exist kernels $\vard1_j\in \F H\cap\spcf0^*$ such that $(\A\varf0)_j = \IP{\vard1_j}{\varf0}$ for all $\varf0\in \F H\cup\spcf0$, $j=1,\ldots,m$. In this form, the adjoint can be written precisely, $\A^*\colon\R^m\to \F H$ by 
$$[\A^*\vvarx3](\vvarx0) = \sum_{j=1}^m \varx3_j\vard1_j(\vvarx0) \qquad \text{ for all }\vvarx0\in\Domain,\ \vvarx3\in\R^m.$$

The following lemma allows for exact computation of the operator norm of $\A$, as needed to ensure that $\func1$ is 1-Lipschitz.
\begin{lemma}\label{thm:ca: norm bound L2}
	If $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in \F H$ for $j\in[m]$, then
	$ \norm{\A^*\A} = \norm{\A\A^*} $
	where $\A\A^*\in\R^{m\times m}$ has entries $(\A\A^*)_{i,j} = \IP{\vard1_i}{\vard1_j}$
	and the matrix norm is the standard spectral norm.
\end{lemma}
\begin{proof}
	The operator $\A$ has a finite dimensional range, therefore it also has a singular value decomposition. This shows that $ \norm{\A^*\A} = \norm{\A\A^*} $. To compute the entries of $\A\A^*\colon\R^m\to\R^m$, observe that for any $\vvarx3\in\R^m$
	$$ (\A\A^*\vvarx3)_i = \IP{\vard1_i}{\A^*\vvarx3} = \IP{\vard1_i}{\sum_{j=1}^m\varx3_j\vard1_j} = \sum_{j=1}^m \IP{\vard1_i}{\vard1_j}\varx3_j.$$
	As required.
\end{proof}
If $\norm{\A^*\A}$ is not analytically tractable, then \Cref{thm:ca: norm bound L2} enables it to be computed using standard finite dimensional methods. The operator $\A\A^*$ is always finite dimensional and can be computed without discretisation error.

In the continuous case, when $\F H=L^2(\Domain)$ we also need to estimate the smoothness properties of $\A^*$. A generic result for this is given in the following lemma.
\begin{lemma}\label{thm:ca: norm bound smoothness}
	If $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in L^2(\Domain)\cap C^k(\Domain)$ for $j\in[m]$, then for all $\frac1q+\frac1{q^*}=1$, $q\in[1,\infty]$, we have
	\begin{align*}
		|\A^*\vvarx3|_{C^k}&\coloneqq \sup_{\vvarx0\in\Domain} |\nabla^k[\A^*\vvarx3]|(\vvarx0) \leq \sup_{\vvarx0\in\Domain}\norm{(\nabla^k\vard1_j(\vvarx0))_{j=1}^m}_{\ell^{q^*}}\norm{\vvarx3}_{\ell^q},
		\\ |\A^*|_{\ell^2\to C^k}&\coloneqq \sup_{\norm{\vvarx3}_{\ell^2}\leq 1} |\A^*\vvarx3|_{C^k} \leq \sup_{\vvarx0\in\Domain}\norm{(\nabla^k\vard1_j(\vvarx0))_{j=1}^m}_{\ell^{q^*}}\times \splitln{1}{q\geq 2}{\sqrt{m^{2-q}}}{q<2}.
	\end{align*}
\end{lemma}
\begin{proof}
	For the first inequality, we apply the H\"older inequality on $\R^m$:
	$$ |\nabla^k[\A^*\vvarx3]|(\vvarx0) = \left|\sum_{j=1}^m\nabla^k\vard1_j(\vvarx0)\varx3_j\right|
	\leq \left(\sum_{j=1}^m|\nabla^k\vard1_j(\vvarx0)|^{q^*}\right)^{\frac{1}{q^*}}\norm{\vvarx3}_{\ell^q} = \norm{(\nabla^k\vard1_j(\vvarx0))_j}_{\ell^{q^*}}\norm{\vvarx3}_{\ell^q}.$$
	For the second inequality, if $q>2$ and $\sum_{j=1}^m \varx3_j^2\leq 1$, then $|\varx3_j|\leq 1$ for all $j$ and $\norm{\vvarx3}_{\ell^q}^q\leq \norm{\vvarx3}_{\ell^2}^2\leq 1$. If $q<2$ and $\norm{\vvarx3}_{\ell^2}\leq 1$, then we again use H\"older's inequality:
	$$\sum_{j=1}^m \varx3_j^q \leq \left(\sum_{j=1}^m 1^{Q^*}\right)^{\frac1{Q^*}} \left(\sum_{j=1}^m \varx3_j^{qQ}\right)^{\frac1{Q}} \leq m^{\frac{2-q}{2}}$$
	for $Q = \frac2q$.
\end{proof}

\subsubsection{Concrete examples}
\Cref{thm:ca: norm bound smoothness} demonstrates how the smoothness of $\A$ relates to the smoothness of the kernels $\psi_j$, possibly scaling with respect to $m$. We now present explicit examples of the computations in both \Cref{thm:ca: norm bound smoothness,thm:ca: norm bound L2} for the numerical results in \Cref{sec:ca: numerics}. These examples are common in practical applications and we show the result of \Cref{thm:ca: norm bound examples} in the main text to demonstrate that, while sometimes hard to compute by hand, the constants can estimated accurately in an efficient manner. The Gaussian case is by far the most technical, therefore we will provide a little further explanation at the end of the theorem.
\begin{theorem}\label{thm:ca: norm bound examples}
	\Copy{thm:ca: norm bound examples}{
		Suppose $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in \F H=L^2([0,1]^d)$ for $j\in[m]$.
		\begin{enumerate}
			\item[Case 1:] If $\vard1_j(\vvarx0) = \splitln{1}{\vvarx0\in \F{\Varx0}_j}{0}{\text{ else}}$ for some collection $\F{\Varx0}_j\subset\Domain$ such that $\F{\Varx0}_i\cap \F{\Varx0}_j = \emptyset$ for all $i\neq j$, then 
			$$\norm{\A}_{L^2\to\ell^2} = \max_j \sqrt{|\F{\Varx0}_j|}.$$

			\item[Case 2:] If $\vard1_j(\vvarx0) = \cos(\ip{\vvars3_j}{\vvarx0})$ for some frequencies $\vvars3_j\in\R^d$ with $|\vvars3_j|\leq \Vars3$, then
			$$\norm{\A}_{L^2\to\ell^2} \leq \sqrt{m}, \qquad |\A^*\vvarx3|_{C^k}\leq m^{1-\frac1q}\Vars3^k\norm{\vvarx3}_q, \qquad |\A^*|_{\ell^2\to C^k}\leq \sqrt{m}\Vars3^k$$
			for all $\vvarx3\in\R^m$ and $q\in[1,\infty]$.

			\item[Case 3:] Suppose $\vard1_j(\vvarx0) = (2\pi\sigma^2)^{-\frac{d}{2}}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right)$ for some regular mesh $\vvarx0_j\in[0,1]^d$ and separation $\Delta$. i.e. 
			$$\{\vvarx0_j\st j\in[m]\} = \{\vvarx0_0 + (j_1\Delta,\ldots,j_d\Delta)\st j_i\in[\hat m]\}$$
			for some $\vvarx0_0\in\R^d$, $\hat m\coloneqq\sqrt[d]{m}$. For all $\frac1q + \frac{1}{q^*} = 1$, $q\in(1,\infty]$, we get
			\begin{align*}
				\norm{\A}_{L^2\to\ell^2} &\leq \bigg((4\pi\sigma^2)^{-\frac d2}\sum_{j=-2\hat m,\ldots,2\hat m}\exp(-\tfrac{\Delta^2}{4\sigma^2}j^2)\bigg)^d,
				\\ |\A^*\vvarx3|_{C^0} &\leq (2\pi\sigma^2)^{-\frac{d}{2}}\bigg(\sum_{\vec j\in J}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}}\norm{\vvarx3}_q,
				\\ |\A^*\vvarx3|_{C^1} &\leq \frac{(2\pi\sigma^2)^{-\frac{d}{2}}}{\sigma}\frac{\Delta}{\sigma}\bigg(\sum_{\vec j\in J}(|\vec j|+\delta)^{q^*}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}}\norm{\vvarx3}_q,
				\\ |\A^*\vvarx3|_{C^2} &\leq \frac{(2\pi\sigma^2)^{-\frac{d}{2}}}{\sigma^2} \bigg(\sum_{\vec j\in J} \left(1+\tfrac{\Delta^2}{\sigma^2}(|\vec j|+\delta)^2\right)^{q^*}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}} \norm{\vvarx3}_q,
			\end{align*}
			where $\delta= \frac{\sqrt d}{2}$ and $J=\{\vec j\in\F Z^d \st \norm{\vec j}_{\ell^\infty}\leq 2\hat m\}$. The case for $q=1$ can be inferred from the standard limit of $\norm\cdot_{{q^*}}\to \norm\cdot_{\infty}$ for $q^*\to\infty$. For $\Delta\ll\sigma$ (i.e. high resolution data), we get the scaling behaviour
			$$ \norm{\A}_{L^2\to\ell^2} \lesssim \Delta^{-d}, \qquad |\A^*\vvarx3|_{C^k} \lesssim \sigma^{-k}\Delta^{-\tfrac{d}{q^*}}\norm{\vvarx3}_q, \qquad |\A^*|_{\ell^2\to C^k} \lesssim \sigma^{-k}\Delta^{-\frac{d}{2}},$$
			for $k=0,1,2$.
		\end{enumerate}
	}
\end{theorem}

The sharpest method for estimating these norms is of course to compute them. This is most cumbersome for Gaussian kernels, however, the sums converge faster than exponentially and so the computational burden should be very small. On the other hand, if $\Delta$ is small, then the sum is just a quadrature estimate for some continuous integrals. These integrals can be computed analytically and provide a much more intuitive grasp of the scaling with respect to dimensionality, grid spacing, and Gaussian width.

\section{Numerical examples}\label{sec:ca: numerics}
We present four numerical Lasso examples. The first two are in 1D to demonstrate the performance of different variants of \Cref{alg:ca: refining FISTA}, both with and without adaptivity. In particular, we explore sparse Gaussian deconvolution and sparse signal recovery from Fourier data; each displays slightly different behaviour in terms of optimisation. We compare with the \emph{continuous basis pursuit} (CBP) discretisation \cite{Ekanadham2011, Duval2017b} which is also designed to achieve super-resolution accuracy within a convex framework. More details of this method will be provided in \Cref{sec:ca: 1D Lasso examples}.

The next example is 2D reconstruction from Radon or X-ray data with wavelet-sparsity. As the forward operator is not sufficiently smooth, we must optimise in $\ell^1(\R)$ which naturally leads to the choice of a wavelet basis.

Finally, we process a dataset which represents a realistic application and (simulated) dataset for \Cref{alg:ca: refining FISTA} in biological microscopy, referred to as STORM microscopy. In essence, the task is to perform 2D Gaussian de-blurring/super-resolution and denoising to find the location of sparse spikes of signal.

In this section, the main aim is to minimise the exact Lasso energy $\Func0_0(\varf0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'. \Cref{thm:ca: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\Func0_0(\varf0_n)$ so it is this monotone estimate which is plotted. To clarify, as $\Func0(\varf0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\Func0_0(\varf0_n) \approx \min_{n\leq N}\Func0(\varf0_n) + \min_{n'\leq n}\Func0^*(\vars2_0\vvard0_{n'})$. Another quantity of interest is minimisation of the discrete Lasso energy $\min_{n\leq N}\Func0(\varf0_n) + \min_{n'\leq n}\Func0^*(\vars2\vvard0_{n'})$ which will be referred to as the `discrete gap'. Note that for the adaptive schemes, this may not be exactly monotonic because the discrete dual problem is changing with $N$.

\subsection{1D continuous Lasso}\label{sec:ca: 1D Lasso examples}
In this example we choose $\spcf0=\C M([0,1])$ and $\A\colon \spcf0\to \R^{30}$ with either random Fourier kernels:
$$(\A\varf0)_j = \int_0^1\cos(\vars3_j\varx0)\varf0(\varx0), \qquad \vars3_j\sim \op{Uniform}[-100,100],\ j\in[30],\ \mu =0.02, $$
or Gaussian kernels on a regular grid:
$$(\A\varf0)_j = (2\pi\sigma^2)^{-\frac12}\int_0^1\exp\left(-\frac{(\varx0-(j-1)\Delta)^2}{2\sigma^2}\right)\varf0(\varx0), \quad \sigma=0.12,\ \Delta = \tfrac1{29},\ j\in[30],\ \mu=0.06.$$

Many variants of FISTA are compared for these examples but the key alternative viewed here is the CBP discretisation. There are many methods designed to minimise the continuous Lasso energy in \eqref{eq:ca: Lasso energy} \cite{Bredies2013,Castro2016,Boyd2017,Catala2019} however, most result in a non-convex discretised problem to solve. We have focused on CBP because it approximates $\varf0^*$ through a convex discrete optimisation problem which is asymptotically exact in the limit $\meshsize\to0$. It can even be solved efficiently with FISTA which allows for direct comparison with the uniform and adaptive mesh approaches. As explained by \cite{Ekanadham2011, Duval2017b}, the idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen. If $\varf0^*$ has only one Dirac spike in each pixel then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.

As shown in \Cref{sec:ca: Lasso definition}, in 1D we have $\vars3_{\Varf0} = \vars3_{\Func0} = 2$. The estimates given in \eqref{eq:ca: Lasso energy rate} and \eqref{eq:ca: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\Func0_0(\varf0_n)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$. To achieve these rates, we implement a refinement criterion from \Cref{thm:ca: practical refinement criteria} with guarantee of $\Func0_0(\varf0_{n_k-1})\lesssim 2^{-k}$ using the estimates made in \Cref{sec:ca: Lasso gap and gradient}. We choose subspaces $\spcf0^n$ to approximately enforce
$$\Func0(\varf0_n) + \Func0^*(\vars2_0\vvard0_n) \leq 2(\Func0(\varf0_n) + \Func0^*(\vars2\vvard0_n))$$
i.e. the continuous gap is bounded by twice the discrete gap. In particular, note that for $\vars2_0\approx \vars2$,
$$ \Func0^*(\vars2_0\vvard0_n) = \tfrac12\norm{\vars2_0\vvard0_n}^2 + \vars2_0\ip{\vdata0}{\vvard0_n} = \frac{\vars2_0}{\vars2}\left(\frac{\vars2_0}{\vars2}\tfrac12\norm{\vars2\vvard0_n}^2 + \vars2\ip{\vdata0}{\vvard0_n}\right) \approx \frac{\vars2_0}{\vars2} \Func0^*(\vars2\vvard0_n).$$
Inserting this back into the continuous/discrete gap inequality, it becomes 
$$ \frac{\vars2_0}{\vars2} \leq 1 + (2-1)\frac{\Func0(\varf0_n)+\Func0^*(\vars2\vvard0_n)}{\Func0^*(\vars2\vvard0_n)}$$
where 2 was our initial chosen ratio. Converting this into a spatial refinement criteria, recall 
$$ \frac{\vars2_0}{\vars2} \approx \frac{\Norm{\A^*\vvard0_n}_*}{\Norm{\Pi_n\A^*\vvard0_n}_*} = \frac{\max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{\max_{\domain_i^n\in\F M^n} |\Pi_n\A^*\vvard0_n(\domain_i^n)|} \approx \max_{\domain_i^n\in\F M^n}\frac{ \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{|\Pi_n\A^*\vvard0_n(\domain_i^n)|}.$$
If $\frac{\vars2_0}{\vars2}$ is large then there must be pixels (values of $i$) in which this ratio is large. Because of the smoothness of $\A^*\vvard0_n$, refining these pixels will reduce the halve the difference and reduce the balance again. This was found to be an efficient method of selecting pixels for refinement based on quantities which had already been computed. Note briefly that from a heuristic standpoint we are refining for two reasons, aligning with an exploitation/exploration viewpoint. Either the Taylor expansion is tight and it is likely that $\varf0^*$ has support in this point, or the Taylor expansion is loose and we refine to improve our level of uncertainty. This second point guarantees that we find the whole support of $\varf0^*$, not just a subset.

\paragraph{Comparison of discretisation methods}
In \Cref{fig:ca: convergence with ndofs} we compare the three core approaches: fixed uniform
discretisation, adaptive discretisation, and CBP. In particular, we wish to observe their convergence properties as the number of pixels is allowed to grow. In each case we use a FISTA stepsize of $\vart1_n = \frac{n+19}{20}$. The adaptive discretisation is started with one pixel and limited to 128, 256, or 512 pixels while the fixed and CBP discretisations have uniform discretisations with the maximum number of pixels. We observe:
\begin{itemize}
	\item Increasing the number of pixels always increases the accuracy of the optimisation.
	\item The adaptive scheme is much more efficient, in both examples the adaptive scheme with 128 pixels is at least competitive with both fixed discretisations with 512 pixels. In fact, only a maximum of 214 pixels were needed by the adaptive method.
	\item With Fourier kernels the uniform piecewise constant discretisation is more efficient than CBP but in the Gaussian case this is reversed. This suggests that the CBP \emph{does} achieve super-resolution when $\A$ is sufficiently smooth but may be less accurate when the kernels oscillate on the length-scale of a single pixel.
	\item The discrete gaps for non-adaptive optimisation behave as is common for FISTA, initial convergence is polynomial until a locally linear regime activates \cite{Tao2016}. CBP is always slower to converge than the piecewise constant discretisation.
	\item For the adaptive method, the continuous/discrete gaps are very similar for all $n$, as enforced by the refinement criterion.
\end{itemize}
It is not completely fair to judge CBP with the continuous gap because, although it generates a continuous representation, this continuous representation is not necessarily consistent with the discrete gap being optimised, unlike when discretised with finite element methods. On the other hand, this is still the intended interpretation of the algorithm and we have no more appropriate metric in this case.

\begin{figure}[H]\centering
	\includegraphics[width=.84\textwidth]{lasso_ndofs_convergence}
	\caption{Rates of continuous/discrete gap convergence for different Lasso algorithms with 128, 256, or 512 pixels. The `adaptive' method uses the proposed algorithm. Both `fixed' and `CBP' use standard FISTA with a uniform discretisation.}\label{fig:ca: convergence with ndofs}
\end{figure}

\paragraph{Comparison of FISTA variants}
There are many variants of FISTA which can also be implemented in the form of \Cref{alg:ca: refining FISTA} just by updating the $\spcf0^n$ on each iteration. Although we have not proven convergence for all of these, \Cref{fig:ca: convergence with method} compares many methods with either fixed or adaptive discretisations. Each adaptive scheme is allowed up to 1024 pixels and each uniform discretisation uses exactly 1024. Forward-Backward splitting (FB) uses a sequence $\vart1_n=1$ otherwise for FISTA a general $\vart1_n = \frac{n+a-1}{a}$ is used. The restarting scheme is given in \Cref{alg:ci: restarting FISTA} and `greedy' FISTA is given in \Cref{alg:ci: greedy FISTA}. In this example CBP used the greedy FISTA implementation which gave faster observed convergence. \Cref{fig:ca: convergence with method} compares the discrete gaps because it is the accurate metric for fixed discretisations, and for the adaptive discretisation it should also be an accurate predictor of the continuous gap.

\pagebreak The key observations are:
\begin{itemize}
	\item The only algorithm with noticeably different convergence is FB, which is the non-accelerated form of FISTA. Every other algorithm converges at the same approximate rate.
	\item The fixed discretisation schemes have an initial `slow' convergence before reaching a `fast' rate. The solid green line of FISTA $a=2$ appears to achieve the theoretical $\frac1{n^2}$ rate and other FISTA implementations are much faster for large $n$.
	\item During the initial `slow' phase, adaptive and fixed discretisations appear to achieve very similar (discrete) convergence rates. The coarse-to-fine adaptivity is not slower than fixed discretisations in this regime.
	\item \Cref{thm:ca: practical refinement criteria} accurately predicts the $\frac1n$ rate of the adaptive methods, mirrored in the fixed discretisations. This suggests that high-resolution but fixed discretisations are initially limited by the continuous problem before entering the asymptotic discrete regime.
	\item \Cref{thm:ca: practical refinement criteria} only applies to two adaptive schemes, labelled $a=2$ and $a=20$. The remaining FISTA schemes all perform comparably although the restarting scheme is often the slowest. Both $a=20$ and greedy FISTA are consistently the best or near-best performing methods.
\end{itemize}

\begin{figure}[H]\centering
	\includegraphics[width=.84\textwidth]{lasso_convergence}
	\caption{Discrete convergence of different algorithms. `Adaptive' methods use \Cref{alg:ca: refining FISTA} with fewer than 1024 pixels and the remaining methods use a uniform discretisation of 1024 pixels.}\label{fig:ca: convergence with method}
\end{figure}

\paragraph{Comparison of fixed and adaptive discretisation}
Motivated by the findings in \Cref{fig:ca: convergence with method}, we now look more closely at the performance of the $a=20$ and the greedy FISTA schemes. We have analytical results for the former but the latter typically performs the best for non-adaptive optimisation and is never worse than $a=20$ in the adaptive setting. We assume that the aim is to find a function $\varf0_n$ with $\Func0_0(\varf0_n)$ smaller than a given threshold. The question is whether it is faster/more efficient to use the proposed adaptive scheme or to use a classical scheme at sufficiently high uniform resolution. The fixed discretisations use 1024 pixels (i.e. uniform pixel size of $2^{-10}$) and the adaptive discretisation starts with two pixels with an upper limit of 1024.

\Cref{fig:ca: comparison with iteration} shows the convergence with respect to number of iterations. As expected, the fixed discretisation starts with a smaller continuous gap before plateauing to a sub-optimal gap around $\Func0_0=0.1$. In both examples, the greedy FISTA has much faster convergence around $n=100$ and of course the minimum pixel size is constant for the fixed discretisation.

The adaptive optimisation matches the predicted rates well, both gap and minimum pixel size (equal to $2^{-k}$) decay at a rate of approximately $\frac1n$. Interestingly, in the Fourier case the energy decays a little faster and the resolution is a little slower. This is consistent with $\Func0$ being a little bit smoother than predicted (i.e. $\vars2_{\Func0}>2$).

It is clear that the adaptive scheme is able to continue reducing the continuous gap far beyond that of the fixed discretisation. The range $n\in[10^3,10^4]$ is particularly interesting because it is the time when the adaptive and fixed curves intersect in both continuous gap and minimum pixel size. Suppose the stopping criterion is to find $\varf0$ such that $\Func0_0(\varf0)<0.1$. \Cref{fig:ca: comparison with iteration} shows that it is equivalent to `guess' the necessary resolution, or to adaptively refine until reaching the stopping criterion. Both methods would converge after $O(10^3)$ iterations with a minimum pixel size of $2^{-10}$.

\Cref{fig:ca: comparison with time} shows a more practical comparison showing wall-clock computation time and number of pixels (memory usage). Optimisation of the fixed discretisation is faster overall but after around \SI{0.1}{\second}, it is always faster to use the adaptive scheme to achieve a given continuous gap. The reason for this can be seen in the numbers of pixels. At the most extreme, in the same computation time the adaptive scheme can achieve more than a factor of 10 better gap using approximately a factor of 10 fewer pixels. The adaptive scheme re-computes the discrete matrix $\A\Pi_n$ each time there is a refinement, but the fixed schemes only compute it once. The adaptive schemes still seem to converge faster than $\frac1{\op{time}}$.

\begin{figure}\centering
	\includegraphics[width=.84\textwidth]{lasso_reduced_convergence}
	\caption{Continuous convergence of adaptive (coarse-to-fine pixel size) compared with uniform discretisation (constant pixel size) with respect to number of iterations. }\label{fig:ca: comparison with iteration}
\end{figure}
\begin{figure}\centering
	\includegraphics[width=.84\textwidth]{lasso_convergence_time}
	\caption{Continuous convergence of adaptive compared with uniform discretisation with respect to wall-clock time and total number of pixels (memory requirement).}\label{fig:ca: comparison with time}
\end{figure}

\subsection{2D wavelet Lasso}\label{sec:ca: wavelet examples}
In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{\Varx0}^I_i$ where 
$$\F{\Varx0}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{50},-\tfrac12+\tfrac{i}{50}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I \quad \text{ for } i,I\in[50].$$
This is not exactly in the form analysed by \Cref{thm:ca: norm bound examples}, however for each $I$ the sets $\{\F{\Varx0}^I_i\st i\in[50]\}$ are disjoint therefore we can apply \Cref{thm:ca: norm bound examples} block-wise to estimate
$$\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[50]} |\F{\Varx0}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[50]} \int_{\F{\Varx0}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[50]}\ (\A\1)_{i,I}}.$$
$\A$ is not smooth, therefore we can't bound $|\A^*|_{C^k}$ for $k>0$, and so we must look to minimise over $\ell^1$ rather than $L^1$. The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the Lasso form:
$$\min_{\varf0\in \spcf0} \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu \norm{\linop{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \tfrac12\norm{\A\linop{W}\hat{\varf0}-\vdata0}_{\ell^2}^2 + \mu \norm{\hat{\varf0}}_{\ell^1}.$$
The minimisers are related by $\varf0^* = \linop{W}\hat{\varf0}^*$ and, for wavelet bases, $\linop{W}$ is orthonormal so $\norm{\A\linop{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$. From \Cref{sec:ca: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\linop{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$. If $\linop{W}$ is a wavelet transformation then its columns, $w_j\in L^2$, are simply the wavelets themselves and we can use the bound 
\begin{equation*}
	|\IP{w_j}{\A^*\vvard0_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vvard0_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vvard0_n}_{L^2}\leq \norm{\1_{\F{\Varx0}} \A^*\vvard0_n}_{L^2}
\end{equation*}
for all $\F{\Varx0}\supset \supp(w_{\vars0})$.
In the case of the Radon transform, we can compute the left-hand side explicitly for the finitely many $j\in J_n$ but we wish to use the right-hand side in a structured way to avoid computing the infinitely many $j\notin J_n$. To do this, we will take a geometrical perspective on the construction of wavelets to view them in a tree format.

\paragraph{Tree structure of wavelets}
Finite elements are constructed with a mesh which provided a useful tool for adaptive refinement in \Cref{sec:ca: bound continuous}. For wavelets, we will associate a tree with every discretisation and the leaves of the tree form a mesh. This perspective comes from the multi-resolution interpretation of wavelets. We will explain the approach for 1D in detail and then comment on how to extend this picture to higher dimensions. We start with a space $\tilde{\spcf0}^0$ and a normalised mother wavelet $\vard1\colon[0,1]\to \R$ then inductively form $\tilde{\spcf0}^k$ by
$$\tilde{\spcf0}^k = \tilde{\spcf0}^{k-1}\bigcup\left\{w_{j,k}(\varx0) = \sqrt{2}^k\vard1(2^{k}\varx0-j)\st j=0,\ldots 2^k-1\right\}.$$
If we keep track of the support $w_{j,k}$ then we see a tree structure emerging, as shown in \Cref{fig:ca: wavelet tree}.
\begin{figure}\begin{center}\begin{tikzpicture}[grow'=right]
			\tikzstyle{level 1}=[level distance=5em, sibling distance=0em];
			\tikzstyle{level 2}=[level distance=5em, sibling distance=6em];
			\tikzstyle{level 3}=[level distance=5em, sibling distance=3em];
			\tikzstyle{bag} = [text width=3em, text centered];

			\node[bag] {$\tilde{\spcf0}^0$}
			child {node[bag] {$w_{0,0}$ $[0,1]$}
				child {node[bag] {$w_{0,1}$ $[0,\frac12]$}
					child {node[bag] {$w_{0,2}$ $[0,\frac14]$}
						child { node {\ldots} }
					} child {node[bag] {$w_{1,2}$ $[\frac14,\frac12]$}
						child { node {\ldots} }
					}
				} child {node[bag] {$w_{1,1}$ $[\frac12,1]$}
					child {node[bag] {$w_{2,2}$ $[\frac12,\frac34]$}
						child { node {\ldots} }
					} child {node[bag] {$w_{3,2}$ $[\frac34,1]$}
						child { node {\ldots} }
			}}};
	\end{tikzpicture}\end{center}
	\caption{Tree representation of 1D wavelets $w_{j,k}$ are arranged in a tree structure with their support underneath.}\label{fig:ca: wavelet tree}
\end{figure}
Each time a node splits, the support is partitioned exactly between its two children. If we truncate this tree to $J_n$ such that every node either has zero or two children, then the leaves of this tree form a partition of unity. For example
\begin{align*}
	J_n = \{(0,0), (0,1),(1,1), (2,2), (3,2)\} \implies \op{leaf}(J_n) &= \{(0,1), (2,2), (3,2)\}, 
	\\ [0,1] &= [0,\tfrac12]\cup[\tfrac12,\tfrac34]\cup[\tfrac34,1].
\end{align*}
In higher dimensions, the only two things which change are the number of children ($2^d$ for non-leaves) and at each node you store the coefficients of $2^d-1$ wavelets. The support on each node is still a disjoint partition of unity consisting of regular cubes of side length $2^{-k}$ at level $k$. The only change in our own implementation is to translate the support to $[-\tfrac12,\tfrac12]^2$. We briefly remark that the tree structuring of wavelets is not novel and appears more frequently in the Bayesian inverse problems literature, for example in \cite{Castillo2019}.

\paragraph{Continuous gradient estimate}
In \Cref{sec:ca: 1D Lasso examples} we used the continuous gap as a measure for convergence, for wavelets we will use the continuous gradient. With the tree structure we can easily adapt the results of \Cref{sec:ca: Lasso gap and gradient} to estimate gradients (or function gaps). In particular,
\begin{align}
	\Norm{\partial \Func0(\varf0_n)}_* &=\max\left(\Norm{\partial_n\Func0(\varf0_n)}_*, \max_{j\notin J_n} |\IP{w_j}{\A^*\vvard0_n}| -\mu \right) \\&\leq\max\left(\Norm{\partial_n\Func0(\varf0_n)}_*, \max_{j\in \op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu \right).\label{eq:ca: wavelet error metric}
\end{align}
It is interesting to note that 
$$\sum_{j\in\op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0^*}_{L^2}^2 = \norm{\A^*\vvard0^*}_{L^2}^2,$$
therefore the task of refinement is somehow to partition the domain of $\A^*\vvard0^*$ such that no single component has more than $\mu$ magnitude. Also, by strong convexity of the dual problem,
$$\left|\vars2_0\norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} - \norm{\1_{\supp(w_j)}\A^*\vvard0^*}_{L^2}\right| \leq \sqrt{|\supp(w_j)|}\sqrt{2(\Func0(\varf0_n)+\Func0^*(\vars2_0\vvard0_n))},$$
therefore the exact discretisation is reached in finite time. After this point, the discretised problem is equal to the continuous problem, and \Cref{alg:ca: refining FISTA} will behave as in the classical setting.

\paragraph{Numerical results}
We consider two phantoms where $\varf0^\dagger$ is either a binary disc or the Shepp-Logan phantom. No noise is added to the Shepp-Logan data but \SI{5}{\percent} Gaussian white noise is added to the disc data. This is visualised in \Cref{fig:ca: haar data}. All optimisations shown will be spatially adaptive using Haar wavelets and initialised with four degrees of freedom (denoted $\spcf0^1$ in the notation of \Cref{fig:ca: wavelet tree}). The gradient metric shown throughout is the $\ell^2$ norm. Motivated by \eqref{eq:ca: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ such that 
$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\Func0(\varf0_n)}_*,$$
i.e. so that the continuous gradient is less than 10 times the discrete gradient.

\begin{figure}[H]\centering
	\includegraphics[width=.84\textwidth]{haar_data}
	\caption{Phantoms and data used for wavelet-sparse tomography optimisation. The Shepp-Logan data is exact but the data for the disc-phantom has \SI{5}{\percent}\ Gaussian white noise. Without noise the data would be uniform with respect to the angle.}\label{fig:ca: haar data}
\end{figure}

The first numerical results shown in \Cref{fig:ca: haar convergence} compare the same adaptive algorithms as shown in \Cref{fig:ca: convergence with method}. In these examples we see that the greedy FISTA, restarting, and the $a=20$ algorithms achieve almost linear convergence while $a=2$ and the classical FB are significantly slower. The maximum number of wavelet coefficients used was 312,220 and 44,644 for the circle and Shepp-Logan phantoms respectively.

\begin{figure}[H]\centering
	\includegraphics[width=.84\textwidth]{haar_convergence}
	\caption{Discrete convergence of different implementations of \Cref{alg:ca: refining FISTA} with an unlimited number of pixels.}\label{fig:ca: haar convergence}
\end{figure}

As before, we focus on the $a=20$ algorithm to which \Cref{thm:ca: practical refinement criteria} applies, and greedy FISTA which we see achieves slightly faster convergence in \Cref{fig:ca: haar convergence zoom}. Looking at the discrete and continuous gradient norms, we see that they are initially distinct then merge after around 50 iterations. From this point onwards, the continuous and discrete problems are equivalent and the iterations are equivalent to classical FISTA.

\begin{figure}\centering
	\includegraphics[width=.84\textwidth]{haar_reduced_convergence}
	\caption{Discrete/continuous convergence of adaptive FISTA algorithms on the wavelet Lasso optimisation.}\label{fig:ca: haar convergence zoom}
\end{figure}

\subsection{2D continuous Lasso}
Our final application is a super-resolution/de-blurring inverse problem from biological microscopy. The resolution of visible light microscopy is fundamentally limited by the wavelength of visible light. Classically, this limit has held around \SI{250}{\nano\meter}, however, in recent years new techniques have emerged improving resolution to around \SIrange{30}{50}{\nano\meter} \cite{Schermelleh2019}. A big component of this shift is a growing reliance on more powerful data processing techniques. \emph{Stochastic Optical Reconstruction Microscopy} (STORM) is an example of \emph{Single Molecule Localisation Microscopy} (SMLM) where a large number of coarse blurred images are recorded, then re-combined to form a single sparse super-resolved image. In the context of STORM, each recorded image is modelled as a sparse signal convolved with a point-spread function, then corrupted with noise. The Lasso formulation has previously been shown to be effective in the context of STORM \cite{Huang2017,Denoyelle2019}.

In this example we use a simulated dataset provided as part of the 2016 SMLM challenge\footnote{\url{http://bigwww.epfl.ch/smlm/challenge2016/datasets/MT4.N2.HD/Data/data.html}} for benchmarking software in this application. It is common to model the point-spread function as a Gaussian, in this example the corresponding Lasso formulation  is 
$$ (\A\varf0)_{i} = (2\pi\sigma^2)^{-1}\int_{[0,6.4]^2} \exp\left(-\frac{1}{2\sigma^2}\left|\vvarx0- \Delta\begin{pmatrix}i_1+\tfrac12 & i_2+\tfrac12\end{pmatrix}^\top \right|^2\right)\varf0(\vvarx0)$$
where $\sigma=\SI{0.2}{\micro\meter}$, $\Delta=\SI{0.1}{\micro\meter}$, and $i_1,i_2\in[64]$ where $\spcf0=\C M([\SI{0}{\micro\meter},\SI{6.4}{\micro\meter}]^2)$. 3020 frames are provided, examples of which are shown in \Cref{fig:ca: STORM data}. To process this dataset, image intensities were normalised to $[0,1]$ then a constant was subtracted to approximate 0-mean noise. The greedy FISTA algorithm was used for optimisation with $\mu=0.15$, $10^3$ iterations, and a maximum of $10^5$ pixels per image.

Finally, all the reconstructions were summed and the result shown in \Cref{fig:ca: STORM results}. The average pixel width after optimisation was approximately \SI{2.4}{\nano\meter}, a factor of 40 super-resolution. If this resolution had been implemented with a uniform discretisation then it would have required $70\times 10^5$ pixels, nearly a factor of 100 greater than achieved with the adaptive discretisation. Lasso is compared with ThunderSTORM \cite{Ovesny2014}, a popular ImageJ plugin \cite{Schindelin2012} which finds the location of signal using Fourier filtering. The performance of ThunderSTORM was rated very highly in the initial competition by \cite{Sage2015}. Both methods compared here demonstrate the key structures of the reconstruction, however, both are sensitive to tuning parameters. In this examples, Lasso has possibly recovered too little signal and ThunderSTORM contains spurious signal.

\Cref{fig:ca: STORM convergence} shows the convergence behaviour in this example. The estimates given by \eqref{eq:ca: Lasso energy rate} and \eqref{eq:ca: Lasso resolution rate} in dimension $d=2$ predict respectively that the adaptive energy will decay at a rate of $\Func0_0(\varf0_n)\lesssim n^{-\sfrac23}$ so long as the pixel size also decreases at a rate of $\meshsize\sim n^{-\sfrac23}$. This is consistent with the resolution scaling (middle panel) but the energy (left panel in pink) is observed to converge a little faster than predicted.

In this example we also implement the suggestion of \Cref{sec:ca: support detection} to remove pixels from the iteration once we can guarantee they are outside of the support. \eqref{eq:ca: support equation} provides a threshold to identify the support of the discrete/continuous minimiser and the value of this is plotted in the first panel of \Cref{fig:ca: STORM convergence}, in particular the normalised value $1-\frac{\op{threshold}}{\mu}$ which converges to 0 for large $n$. Any pixel $\domain_i^n$ satisfying 
$$ \vars2_0\norm{\Pi_n\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq \op{threshold}$$
guarantees that $\domain_i^n\cap\op{supp}(\varf0^*) = \emptyset$. Once this threshold becomes greater than 0 (plotted value less than 1), we can start reducing the number of pixels instead of just continual refinement. We can see this in the right-hand panel of \Cref{fig:ca: STORM convergence}, after around 30 iterations the total number pixels starts to reduce and stabilise at approximately $6\times10^3$ pixels per frame, well below the upper limit of $10^5$.

\begin{figure}\centering
	\includegraphics[width=.8\textwidth]{STORM_data}
	\caption{Example of images from STORM dataset.}\label{fig:ca: STORM data}
\end{figure}
\begin{figure}\centering
	\includegraphics[width=.77\textwidth]{STORM_recon}
	\caption{Processed results of the STORM dataset. Top left: Lasso optimisation with \Cref{alg:ca: refining FISTA}. Top right: Comparison with ThunderSTORM plugin. Bottom: Average data, no super-resolution or de-blurring.}\label{fig:ca: STORM results}
\end{figure}
\begin{figure}\centering
	\includegraphics[width=\textwidth]{lasso2_convergence}
	\caption{Convergence of adaptive FISTA for STORM dataset. Lines indicate the median value over 3020 STORM frames. Shaded regions indicate the \SIrange{25}{75}{\percent} inter-quartile range.}\label{fig:ca: STORM convergence}
\end{figure}

\section{Conclusions and outlook}
In this work we have proposed a new adaptive variant of FISTA and provided convergence analysis. This algorithm allows FISTA to be applied outside of the classical Hilbert space setting, still with a guaranteed rate of convergence. We have presented several numerical examples where convergence with the refining discretisation is at least as fast as a uniform discretisation, although more efficient with regards to both memory and computation time.

In 1D we see good agreement with the theoretical rate. This rate also seems to be a good predictor for all variants of FISTA tested, although this is yet to be proven. Surprisingly, even the classical methods with a fixed discretisation initially seem limited to the slower adaptive rate for small $n$.

The results in 2D are similar, all tested FISTA methods converge at least at the guaranteed rate. The wavelet example was most impressive, achieving nearly linear convergence in energy. This is similar to the behaviour for classical FISTA although it is also yet to be formally proven.

An interesting observation over all of the adaptive Lasso examples is that the classical oscillatory behaviour of FISTA has not occured. With the monotone gaps plotted, oscillatory convergence should correspond to a piecewise constant descending gap. Either this behaviour only emerges for larger $n$, or the adaptivity mimics the restarting behaviour typically used to avoid oscillation. The perturbation provided by the refinement is sufficient to stop FISTA overshooting the minimiser and maintain a predictable rate of convergence to the minimiser. This may also explain why the standard restarting FISTA showed little improvement in these examples.

Moving forward, it would be interesting to see how far the analysis extends to other optimisation algorithms. To cover the numerical results, this would necessitate repeating the presented argument for Forward-Backward splitting and for the modifications of FISTA suggested by \cite{Liang2018}. We feel that the extension to the primal-dual algorithm proposed by \cite{Chambolle2011} should also be possible where there is a classical bound of the form $\min_{n\leq N}\Func0(\varf0_n)+\Func0^*(\vvard0_n) \lesssim \frac{\norm{\varf0_0-\varf0^*}^2 + \norm{\vvard0_0-\vvard0^*}^2}{N}$. This has the same basic ingredients as FISTA although there is now the extra dual variable to account for.

Another interesting outlook is to relax the requirement for $\func1$ to be smooth on the whole of $\spcf0\cap\F H$. An example where this is not the case is the dual problem to total variation denoising where we have
$$ \Func0(\varf0) = \norm{\op{div}\varf0-\vdata0}^2 + \chi(\norm{\varf0}_\infty\leq \mu).$$
The divergence operator is not bounded in $L^2$ but is on each subspace $\spcf0^n$. It is not clear if it is possible to incorporate this into FISTA without restarting each time the step-size changes.

\bibliographystyle{apalike}\bibliography{references} % alpha is also a decent style
\newpage\appendix
\section{Proofs for FISTA convergence}\label{app:ca: FISTA convergence}
This section contains all of the statements and proofs of the results contained in \Cref{sec:ca: FISTA convergence}.

\subsection{Proofs for Step 2}

\begin{lemma}[\Cref{thm:ca: descent lemma}]\label{app:thm:ca: descent lemma}
	\Paste{thm:ca: descent lemma}
\end{lemma}
\begin{proof}
	This is exactly the result of \cite[Lemma 1]{Chambolle2015} applied to the function $\varf0\mapsto\Func0(\Pi_n\varf0)$.
\end{proof}

\begin{theorem*}[\Cref{thm:ca: one step FISTA}]
	\Paste{thm:ca: one step FISTA}
	\begin{equation}
		\vart1_{n}^2(\Func0(\varf0_{n}) - \Func0(\varf2_n)) - (\vart1_{n}^2-\vart1_{n})(\Func0(\varf0_{n-1})-\Func0(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.\label{app:eq:ca: one-step FISTA}
	\end{equation}
\end{theorem*}
\begin{proof}
	Modifying \cite[Theorem 2]{Chambolle2015}, for $n\geq1$ we apply \Cref{app:thm:ca: descent lemma} with $\bar{\varf0} = \bar{\varf0}_{n-1}$ and $\varf2 = (1-\frac{1}{\vart1_{n}})\varf0_{n-1} + \frac{1}{\vart1_{n}}\varf2_n$. This gives
	$$\Func0(\varf0_{n}) + \tfrac12\norm{\tfrac{1}{\vart1_{n}}\varf1_{n}-\tfrac{1}{\vart1_{n}}\varf2_n}^2 \leq \Func0\left((1-\tfrac{1}{\vart1_{n}})\varf0_{n-1}+\tfrac{1}{\vart1_{n}}\varf2_n\right) + \tfrac12\norm{\tfrac{1}{\vart1_{n}}\varf1_{n-1}-\tfrac{1}{\vart1_{n}}\varf2_n}^2.$$
	By the convexity of $\Func0$, this reduces to
	\begin{align*}
		\Func0(\varf0_{n}) - \Func0(\varf2_n) - (1-\tfrac{1}{\vart1_{n}})[\Func0(\varf0_{n-1})-\Func0(\varf2_n)] &\leq \tfrac1{2\vart1_{n}^2}\norm{\varf1_{n-1}-\varf2_n}^2 - \tfrac1{2\vart1_{n}^2}\norm{\varf1_{n}-\varf2_n}^2
		\\ &= \tfrac1{2\vart1_{n}^2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \tfrac1{\vart1_{n}^2}\IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.
	\end{align*}
\end{proof}

\begin{theorem}[\Cref{thm:ca: mini FISTA convergence}]\label{app:thm:ca: mini FISTA convergence}
	\Paste{thm:ca: mini FISTA convergence}
	\begin{multline}\label{app:eq:ca: FISTA inequality}
		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
		\\ + \sum^N_{n=1} \vart1_n\Func0_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
	\end{multline}
\end{theorem}
\begin{proof}
	\Cref{app:thm:ca: mini FISTA convergence} is just a summation of \eqref{app:eq:ca: one-step FISTA} over all $n=1,\ldots,N$. To see this: first add and subtract $\Func0(\varf0^*)$ to each term on the left-hand side to convert $\Func0$ to $\Func0_0$, then move $\Func0_0(\varf2_n)$ to the right-hand side. Now \eqref{app:eq:ca: one-step FISTA} becomes
	$$ \vart1_n^2\Func0_0(\varf0_n) - (\vart1_n^2-\vart1_n)\Func0_0(\varf0_{n-1}) \leq \vart1_n\Func0_0(\varf2_n) + \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_n}^2\right] + \IP{\varf1_n-\varf1_{n-1}}{\varf2_n}. $$
	Summing this inequality from $n=1$ to $n=N$ gives
	$$\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}(\underbrace{\vart1_n^2-\vart1_{n+1}^2+\vart1_{n+1}}_{=\rho_n})\Func0_0(\varf0_n) \leq \frac{\norm{\varf1_0}^2-\norm{\varf1_N}^2}{2} + \sum_{n=1}^N \vart1_n\Func0_0(\varf2_n)+\IP{\varf1_n-\varf1_{n-1}}{\varf2_n}.$$
	This is almost in the desired form, however, we would like to flip the roles of $\varf1_n$/$\varf2_n$ in the final inner product term. Re-writing the right-hand side gives
	$$\sum_{n=1}^N\IP{\varf1_n-\varf1_{n-1}}{\varf2_n} = \IP{\varf1_N}{\varf2_N} - \IP{\varf1_0}{\varf2_0}+ \sum_{n=1}^N\IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.$$
	Noting $\varf1_0=\varf0_0$, combining the previous two equations proves the statement of \Cref{app:thm:ca: mini FISTA convergence}.
\end{proof}

\newpage\noindent The following lemma is used to produce a sharper estimate on sequences $\vart1_n$.
\begin{lemma}\label{app:ca: tn upper bound}
	If $\rho_n=\vart1_{n}^2-\vart1_{n+1}^2+\vart1_{n+1}\geq0$, $\vart1_n\geq 1$ for all $n\in\F N$ then $\vart1_n\leq n-1 +\vart1_1$.
\end{lemma}
\begin{proof}
	This is trivially true for $n=1$. Suppose true for $n-1$, the condition on $\rho_{n-1}$ gives
	$$\vart1_n^2 -\vart1_n \leq \vart1_{n-1}^2 \leq (n-2+\vart1_1)^2 = (n-1+\vart1_1)^2 -2(n-1+\vart1_1) + 1.$$
	Assuming the contradiction, if $\vart1_n> n-1+\vart1_1$ then we get $n-1+\vart1_1 < 1$ but $\vart1_1\geq 1$ so this becomes $n<1$ which completes the contradiction.
\end{proof}

\begin{lemma}[\Cref{thm:ca: mini exponential FISTA convergence}]\label{app:thm:ca: mini exponential FISTA convergence}
	\Paste{thm:ca: mini exponential FISTA convergence}
\end{lemma}
\begin{proof}
	This is just a telescoping of the right-hand side of \eqref{app:eq:ca: FISTA inequality} with the introduction of $n_k$ and simplification $\varf2_n = \tilde{\varf2}_k$,
	\begin{multline*}
		\tfrac12\norm{\varf2_N}^2 + \sum^N_{n=1} \vart1_n\Func0_0(\Pi_n\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n} = \tfrac12\norm{\tilde{\varf2}_K}^2 + \sum_{n=n_K}^N\vart1_n\Func0_0(\tilde{\varf2}_K) 
		\\+ \sum_{k=1}^K\sum_{n=n_{k-1}}^{n_k-1}\vart1_n\Func0_0(\tilde{\varf2}_K) 
		+ \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}.
	\end{multline*}
	\begin{samepage}
		By \Cref{app:ca: tn upper bound}, $\vart1_n\leq n$ so we can further simplify
		$$\sum_{n=\vars3}^{\vars4-1}\vart1_n \leq \sum_{n=\vars3}^{\vars4-1}n = (\vars4-\vars3)\frac{\vars4-1+\vars3}{2} \leq \frac{\vars4^2-\vars3^2}{2}$$
		to get the required bound.
	\end{samepage}
\end{proof}

\subsection{Proof for Step 3}
\begin{lemma}[\Cref{thm:ca: sufficiently fast}]\label{app:thm:ca: sufficiently fast}
	\Paste{thm:ca: sufficiently fast}
\end{lemma}
\todo{This proof is quite long and not very explicit. Should I compute the constant?}
\begin{proof}
	Inserting the assumed rates into \Cref{app:thm:ca: mini exponential FISTA convergence} gives
	$$	\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 \lesssim \vars3_{\Varf0}^{2K} + (N+1)^2\vars3_{\Func0}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\Func0}^{-k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + \vars3_{\Varf0}^{2k}.$$
	Each case now needs its own induction. When $\vars3_{\Varf0}>1$ we simplify the inequality to 
	\begin{align*}
		\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim \vars3_{\Varf0}^{2K} + \vars3_{\Varf0}^{2K+2} + \sum_{k=1}^{K}\vars3_{\Varf0}^{2k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}
		\\&\leq C_1\left(\vars3_{\Varf0}^{2K+2} + \frac{\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1} + \sum_{k=1}^{K}\vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\right).
	\end{align*}
	for some $C_1$ sufficiently large. Assume $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2\vars3_{\Varf0}^k$ for $k\leq K$, then for $N=n_{K+1}-1$ we have
	$$\tfrac12\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}^2 \leq \frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right).$$
	If $C_2$ is sufficiently large, then $\frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right) \leq \tfrac12C_2^2\vars3_{\Varf0}^{2K+2}$ which completes the induction. This bounds the growth of the right hand side and so for any $N<n_{K+1}$ we have $t_N^2\Func0_0(\varf0_N) \lesssim \vars3_{\Varf0}^{2K}$.

	When $\vars3_{\Varf0}=1$, the assumptions are stronger so the induction becomes more direct. Assuming $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2$ for $k\leq K$, there exists $C_1>0$ such that 
	\begin{align*}
		\vart1_{N+1}^2\Func0_0(\varf0_{N+1}) + \tfrac12\norm{\varf1_{N+1}-\tilde{\varf2}_{K}}^2 &\leq C_1 + \max_{k\leq K}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}
		\\&\leq C_1 + C_2.
	\end{align*}
	If $C_2$ is sufficiently large then $C_1 + C_2 \leq \tfrac14C_2^2$ which completes the second induction. This confirms $t_N^2\Func0_0(\varf0_N) \leq \tfrac14C_2^2$ is bounded uniformly.
\end{proof}

\subsection{Proof for Step 4}
\begin{lemma}[\Cref{thm:ca: sufficiently slow}]\label{app:thm:ca: sufficiently slow}
	\Paste{thm:ca: sufficiently slow}
\end{lemma}
\begin{proof}
	The proof is direct computation,
	$$ \log N^2 \geq \log C + K\left(\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2\right)$$ 
	which leads to
	\begin{align*}
		\vars3_{\Varf0}^{2K} & = \exp(K\log \vars3_{\Varf0}^2)
		\\&\leq \exp\left(\log N^2\frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} - \frac{\log C\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}\right)
		\\&\lesssim N^{2\epsilon}
	\end{align*}
	as required.
\end{proof}

\begin{theorem}[\Cref{thm:ca: exponential FISTA convergence}]
	\Paste{thm:ca: exponential FISTA convergence}
\end{theorem}
\begin{proof}
	If the conditions of this theorem are satisfied, then so are \Cref{app:thm:ca: mini exponential FISTA convergence,app:thm:ca: sufficiently fast,app:thm:ca: sufficiently slow}. The final result is just the conclusion of \Cref{app:thm:ca: sufficiently slow}.
\end{proof}

\subsection{Proofs for Step 5}
\begin{theorem}[\Cref{thm:ca: stronger exponential FISTA convergence}]\label{app:thm:ca: stronger exponential FISTA convergence}
	\Paste{thm:ca: stronger exponential FISTA convergence}
\end{theorem}
\begin{proof}
	To apply \Cref{app:thm:ca: sufficiently fast}, we need
	$$n_k^2\lesssim \splitln{(\vars3_{\Func0}\vars3_{\Varf0}^2)^k}{\vars3_{\Varf0}>1}{k^{-2}\vars3_{\Func0}^k}{\vars3_{\Varf0}=1}, \qquad \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^{k}, \qquad \text{ and } \Func0_0(\tilde{\varf2}_k)\lesssim \vars3_{\Func0}^{-k}$$
	and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$ when $\vars3_{\Varf0}=1$. The only one which is not directly assumed is easily verified,
	$$\Func0_0(\tilde{\varf2}_k) = \min_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0) \leq\Func0_0(\varf0_{n_k-1}) \lesssim \vars3_{\Func0}^{-k}.$$
	Therefore, the result of \Cref{app:thm:ca: sufficiently fast} gives
	$$\Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{\vart1_N^2} \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}.$$
	In the case $\vars3_{\Varf0}=1$, this is already the optimal rate and therefore sharp. If this were sharp for general $\vars3_{\Varf0}$ and $\Func0$, then we gain nothing by refining early (increasing $K$ for fixed $N$) however, we can at least guarantee that refining early does not lose the optimal rate.

	\begin{samepage}
		If we fix $N^2\lesssim (\vars3_{\Func0}\vars3_{\Varf0}^2)^k$, then
		$$\min_{n\leq N} \Func0_0(\varf0_n)\lesssim \splitln{\vars3_{\Func0}^{-k}}{N>n_k}{ \sfrac{\vars3_{\Varf0}^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_{\Varf0}^{2k},\vars3_{\Varf0}^{2k}) \lesssim N^{-2(1-\epsilon)}$$
		as required.
	\end{samepage}
\end{proof}

\begin{lemma}[\Cref{thm:ca: practical refinement criteria}]
	\Paste{thm:ca: practical refinement criteria}
\end{lemma}
\todo{This is a very long theorem which I don't really use in the end. The result is a little bit useful but not difficult.}
\begin{proof}
	The proof is simply to justify that the conditions of \Cref{app:thm:ca: stronger exponential FISTA convergence} are met for all refinement criteria described here. $\norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k$ is enforced at every step and condition (2) guarantees the back-stop condition on $n_k$.

	To complete the requirements of \Cref{app:thm:ca: stronger exponential FISTA convergence}, we first need to show inductively that $\Func0_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\Func0}^{-k}$, then it follows that $\Func0_0(\varf0_{n_k-1})\leq C\vars3_{\Func0}^{-k}$. To be explicit, when $\Func0$ has bounded sublevel sets, assume that the bound for $\{\varf0\in\F H\st \Func0(\varf0)\leq \Func0(\varf0_0)\}$ is $R>0$.

	For (2) and (5) the decay of $\Func0_0(\tilde{\varf2}_{k-1})$ is already assumed but otherwise we need to perform the formal induction. Assume $\Func0_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\Func0}^{1-k}$, then for each remaining adaptive criterion:
	\begin{itemize}
		\item[(1)] $\Func0_0(\tilde{\varf2}_k)\leq \Func0_0(\varf0_{k})\leq\vars1 \vars3_{\Func0}^{-k}$ by definition, the induction holds if $C\geq \vars1$.
		\item[(3)] $\Func0_0(\tilde{\varf2}_k)\leq \Func0_0(\varf0_{k})\leq\frac{\vars1}{1-\vars1}\Func0_0(\tilde{\varf2}_{k-1})$, the induction holds if $\vars1\leq \frac{1}{1+\vars3_{\Func0}}$.
		\item[(4)] $\Func0_0(\tilde{\varf2}_k)\leq \Func0_0(\varf0_{k}) \leq \IP{\partial\Func0(\varf0_{k})}{\varf0_{n_k-1}-\varf0^*} \leq 2R\vars1\vars3_{\Func0}^{-k}$, the induction holds for $C\geq 2R\vars1$.
	\end{itemize}
	In each case, with $C$ sufficiently large, the induction holds. Now we can return to the precise condition of \Cref{app:thm:ca: stronger exponential FISTA convergence}, $\Func0_0(\varf0_{n_k-1}) \leq C'\vars3_{\Func0}^{-k}$. Assume true for $k-1$. For each adaptive criterion:
	\begin{itemize}
		\item[(1)] $\Func0_0(\varf0_{k})\leq\vars1 \vars3_{\Func0}^{-k}$ is by definition.
		\item[(2)] $\Func0_0(\varf0_{k})\leq\vars1 \vars3_{\Func0}^{-k} + \Func0_0(\tilde{\varf2}_{k-1})$ requires $C'\geq \vars1+\vars3_{\Func0}C$.
		\item[(3)] $\Func0_0(\varf0_{k})\leq\frac{\vars1}{1-\vars1}\Func0_0(\tilde{\varf2}_{k-1})$ requires $C'\geq \frac{\vars1}{1-\vars1}C$.
		\item[(4)] $\Func0_0(\varf0_{k}) \leq 2R\vars1\vars3_{\Func0}^{-k}$, the induction holds for large $C'$.
		\item[(5)] $\Func0_0(\varf0_{k})\leq 2R\vars1\vars3_{\Func0}^{-k} + \Func0_0(\tilde{\varf2}_{k-1})$, the induction holds for large $C'\geq 2R\vars1+C$.
	\end{itemize}
	This completes the requirements of \Cref{app:thm:ca: stronger exponential FISTA convergence}, therefore also this proof.
\end{proof}

\section{Proof of \texorpdfstring{\Cref{thm:ca: generic a_U and a_E}}{rates for general finite element spaces}}\label{app:ca: generic a_U and a_E}
\todo{This whole section is unnecessary for the numerics. It is possibly useful to get a general understanding of the rates one can achieve but not strong enough for Lasso. It is quite a long proof for that level of reward\ldots}
The proof of \Cref{thm:ca: generic a_U and a_E} is the result of the following three lemmas. The first, \Cref{app:thm:ca: generic a_U bound}, is a general quantification of the equivalence between $L^q$ and $L^2$ norms on finite dimensional sub-spaces. A special case occurs when $q=1$ because the dual norm is a supremum rather than an integral. In \Cref{app:thm:ca: specific a_U bound}, this locality is exploited by finite element spaces, which we assumed had a basis with local support. \Cref{app:thm:ca: generic a_E bound} then performs the computations for the $\vars3_{\Func0}$ constant depending on the smoothness properties of $\Func0$.

\begin{lemma}\label{app:thm:ca: generic a_U bound}
	Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$. Let $\tilde{\spcf0}\subset \spcf0\cap\F H$ be a finite dimensional subspace with orthonormal basis $\{e_j\st j=1,\ldots,\op{dim}(\tilde{\spcf0})\}\subset\tilde{\spcf0}$ and orthogonal projection $\Pi\colon\F H\to\tilde{\spcf0}$. If these conditions hold, then:
	\begin{itemize}
		\item if $q\geq 2$, then $$\norm{\Pi\varf2} \lesssim \Norm{\varf2}, $$
		\item otherwise, if $e_j\in \spcf0^*$, then
		$$\norm{\Pi\varf2} \leq \sqrt{\op{dim}(\tilde{\spcf0})}\max_j\Norm{e_j}_*\Norm{\varf2},$$
		\item otherwise, if $e_j\in L^\infty(\Domain)$ and $ |\{j:e_j(\vvarx0)\neq 0\}|\leq C$ for almost all $\vvarx0\in\Domain$, then
		$$\norm{\Pi\varf2} \lesssim \sqrt C\max_j\norm{e_j}_{L^\infty}\Norm{\varf2} $$
	\end{itemize}
	uniformly for all $\varf2\in \F H$.
\end{lemma}
\begin{proof}
	The first statement for $q\geq 2$ is from H\"older's inequality combined with the fact that compact domains have finite volume,
	$$\norm{\Pi\varf2}^2 \leq \norm{\varf2}^2 = \norm{\varf2}_2^2 = \norm{\varf2^2}_1 \lesssim \norm{\varf2}_q^2 \lesssim \Norm{\varf2}^2.$$
	The remaining statements come from the equivalence of norms on finite dimensional spaces. Note that
	$$\norm{\Pi\varf2} = \frac{\IP{\Pi\varf2}{\Pi\varf2}}{\norm{\Pi\varf2}} = \frac{\IP{\Pi\varf2}{\varf2}}{\norm{\Pi\varf2}} \leq \frac{\Norm{\Pi\varf2}_*}{\norm{\Pi\varf2}}\Norm{\varf2},$$
	therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\tilde{\spcf0}$. Switching to the given basis, for $\varf0 = \sum_j \varx3_je_j$ we have
	\begin{align*}
		\norm{\varf0}^2 &= \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} \varx3_j^2 = \norm{\vvarx3}_{\ell^2}^2,
		\\\Norm{\varf0}_*&\leq \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} |\varx3_j|\Norm{e_j}_* \leq \max_j\Norm{e_j}_*\norm{\vvarx3}_{\ell^1},
		\\\implies \frac{\Norm{\varf0}_*}{\norm{\varf0}} &\leq \max_j\Norm{e_j}_*\frac{\norm{\vvarx3}_{\ell^1}}{\norm{\vvarx3}_{\ell^2}} \leq \max_j\Norm{e_j}_*\sqrt{\op{dim}(\tilde{\spcf0})}.
	\end{align*}
	Alternatively, we can use the inequality
	$$\norm{\Pi\varf2} = \frac{\IP{\Pi\varf2}{\varf2}}{\norm{\Pi\varf2}} \leq \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\norm{\varf2}_1\lesssim  \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\norm{\varf2}_q \lesssim \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\Norm{\varf2}.$$
	This simplifies the equivalence constant because for any $\varf0 = \sum \varx3_je_j$ and $\mu>1$, there exists a set of points $\vvarx0\in\Domain$ with non-zero measure such that $\norm{\varf0}_\infty\leq \mu|\varf0(\vvarx0)|$. This gives
	\begin{align*}
		\norm{\varf0}^2 &= \sum \varx3_j^2 \geq \sum_{e_j(\vvarx0)\neq 0} \varx3_j^2,
		\\\norm{\varf0}_\infty& \leq \mu|\varf0(\vvarx0)| \leq \mu\sum_{e_j(\vvarx0)\neq 0} |\varx3_j|\norm{e_j}_\infty,
		\\\implies \frac{\norm{\varf0}_\infty}{\norm{\varf0}} &\leq \mu\max_j\norm{e_j}_\infty\sqrt{C}.
	\end{align*}
	This inequality holds for all $\mu>1$ therefore also for $\mu=1$. Essentially, with an extra smoothness assumption on $e_j$, we can reduce the dimension of the problem to $\op{dim}(\tilde{\spcf0})=C $ and use the previous result.
\end{proof}

\begin{lemma}\label{app:thm:ca: specific a_U bound}
	Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$. Let $(\tilde{\spcf0}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces with orthogonal projections $\tilde\Pi_k\colon\F H\to\tilde{\spcf0}^k $. If $q\geq 2$,
	$$\norm{\tilde\Pi_k\varf2} \lesssim \Norm{\varf2}, $$
	otherwise,
	$$\norm{\tilde\Pi_k\varf2} \lesssim \sqrt{\op{dim}(\tilde{\spcf0}^0)}\meshsize^{-\frac{kd}{2}}\Norm{\varf2} $$
	uniformly for all $\varf2\in \F H$.
\end{lemma}
\begin{proof}
	Most of the conditions of \Cref{app:thm:ca: generic a_U bound} are already satisfied. Denote $C=\op{dim}(\tilde{\spcf0^0})$ and $\{e_j\st j\in[C]\}$ the standard orthonormal basis of $\tilde{\spcf0}^0$. The scaling properties of $\meshsize$-refining finite element spaces guarantee that the value of $C$ satisfies the conditions of \Cref{app:thm:ca: generic a_U bound} and a basis of $\tilde{\spcf0}^k$ is given by
	$$ \left\{\vvarx0\mapsto\varf0_j(\vars0^{i,k}\vvarx0+\vvars1^{i,k}) \qquad\st\qquad i=1,\ldots,|\F M^k|,\ j=1,\ldots,C\right\}$$
	for some $\vars0^{i,k}\in\R^{d\times d}$, and $\vvars1^{i,k}\in\R^d$ such that $0<\op{det}(\vars0^{i,k})\lesssim \meshsize^{-kd}$.

	We now compute the scaling constant in \Cref{app:thm:ca: generic a_U bound}:
	$$ \frac{\norm{\varf0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}_\infty}{\norm{\varf0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}} = \frac{\norm{\varf0_j}_\infty}{\sqrt{\int_{\domain_i^k} e_j(\vars0^{i,k} \vvarx0+\vvars1^{i,k})^2d\vvarx0}} = \frac{\norm{\varf0_j}_\infty}{\sqrt{\op{det}(\vars0^{i,k})^{-1}}} \lesssim \meshsize^{-\frac{kd}{2}}.$$
	This value is independent of $j$ and gives the desired bound as a result of \Cref{app:thm:ca: generic a_U bound}.
\end{proof}

\begin{lemma}\label{app:thm:ca: generic a_E bound}
	Let $(\tilde{\spcf0}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\varf2}^k=\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$.
	\begin{enumerate}
		\item If $\Func0$ is $\Norm\cdot$-Lipschitz at $\varf0^*$, then
		$\Func0(\tilde{\varf2}^k)-\Func0(\varf0^*) \lesssim \meshsize^p\Norm{\varf0^*}.$
		\item If $\Func0$ is $\Norm\cdot$-smooth at $\varf0^*$, then 
		$\Func0(\tilde{\varf2}^k)-\Func0(\varf0^*) \lesssim \meshsize^{2p}\Norm{\varf0^*}.$
		\item If $\func1$ is $\Norm\cdot$-Lipschitz at $\varf0^*$ and 
		$$\min_{\varf2\in\tilde{\spcf0}^k}\left\{\Norm{\varf2-\varf0^*}\st \func2(\varf2)\leq \func2(\varf0^*)\right\} \lesssim \min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*}$$
		uniformly for $k\in\F N$, then
		$\Func0(\tilde{\varf2}^k)-\Func0(\varf0^*) \lesssim \meshsize^p\Norm{\varf0^*}.$
	\end{enumerate}
\end{lemma}
\begin{proof}
	Each statement is by definition, observe
	\begin{gather*}
		\Func0(\varf2)-\Func0(\varf0^*) \leq \op{Lip}(\Func0)\Norm{\varf2-\varf0^*},
		\\\Func0(\varf2)-\Func0(\varf0^*) \leq \IP{\partial \Func0(\varf2)}{(\varf2-\varf0^*)} = \IP{\nabla \Func0(\varf2)-\nabla \Func0(\varf0^*)}{ \varf2-\varf0^*} \leq \op{Lip}(\nabla F)\Norm{\varf2-\varf0^*}^2,
		\\\Func0(\varf2)-\Func0(\varf0^*) \leq \func1(\varf2)-\func1(\varf0^*) \leq \op{Lip}(\func1)\Norm{\varf2-\varf0^*}.
	\end{gather*}
	Minimising over the right-hand side over $\varf2$ and substituting the definition of order gives the desired result.
\end{proof}

\section{Operator norms for numerical examples}
\begin{theorem}[\Cref{thm:ca: norm bound examples}]\label{app:thm:ca: norm bound examples}
	\Paste{thm:ca: norm bound examples}
\end{theorem}
\todo{A very boring theorem but needs to be somewhere to justify the numerics. I don't know if the $\Delta\ll\sigma$ case is interesting to anyone else.}
\begin{proof}[Proof case 1:]
	From \Cref{thm:ca: norm bound L2} we have 
	$$(\A\A^*)_{i,j} = \IP{\1_{\F{\Varx0}_i}}{\1_{\F{\Varx0}_j}} = |\F{\Varx0}_i\cap \F{\Varx0}_j| = \splitln{|\F{\Varx0}_i|}{i=j}{0}{i\neq j}.$$
	Therefore, $\A\A^*$ is a diagonal matrix and $\norm{\A\A^*}_{\ell^2\to\ell^2} = \max_j |\F{\Varx0}_j|$ completes the result.
\end{proof}

\begin{proof}[Proof case 2:]
	$\vard1_j$ are not necessarily orthogonal however $|\IP{\vard1_i}{\vard1_j}|\leq 1$ therefore we can estimate
	$$\norm{\A\A^*}_{\ell^2\to\ell^2} \leq \norm{\A\A^*}_{\ell^\infty\to\ell^\infty} \leq m.$$
	Now looking to apply \Cref{thm:ca: norm bound smoothness}, note $\norm{\nabla^k\vard1_j}_\infty \leq \Vars3^k$, therefore
	\begin{align*}
		|\A^*\vvarx3|_{C^k}&\leq \Vars3^k m^{\frac1{q^*}}\norm{\vvarx3}_q = \Vars3^k m^{1-\frac1{q}}\norm{\vvarx3}_q,
		\\|\A^*|_{\ell^2\to C^k} &\leq \Vars3^k \min_{q\in[1,\infty]}m^{1-\frac1q}\sqrt{m}^{\max(0,2-q)} = \sqrt{m}\Vars3^k.
	\end{align*}
\end{proof}

\begin{proof}[Proof of asymptotic case 3:]
	In the Gaussian case, we build our approximations around the idea that sums of Gaussians on a regular grid look like a discretised integral. The first example can be used to approximate the operator norm. Computing the inner products gives
	\\\parbox{\linewidth+5pt}{\begin{multline*}
				\IP{\vard1_i}{\vard1_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vvarx0-\vvarx0_i|^2}{2\sigma^2}-\tfrac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right) \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right) 
				\\= (4\pi\sigma^2)^{-\frac d2} \exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right).
	\end{multline*}}
	Estimating the operator norm,
	\\{\centering\resizebox{.9\textwidth}{!}{\parbox{\textwidth}{\begin{align*}
					\norm{\A\A^*}_{\ell^2\to\ell^2}&\leq \norm{\A\A^*}_{\ell^\infty\to\ell^\infty} = \max_{i\in[m]} \sum_{j=1}^m |\IP{\vard1_i}{\vard1_j}| 
					\\&= \max_{i\in[m]}(4\pi\sigma^2)^{-\frac d2}\sum_{j_1,\ldots,j_d\in[\hat m]} \exp\left(-\frac{(j_1\Delta-i_1\Delta)^2+\ldots+(j_d\Delta-i_d\Delta)^2}{4\sigma^2}\right)
					\\&\leq (4\pi\sigma^2)^{-\frac d2}\sum_{\vec j\in\F Z^d\cap[-\hat m,\hat m]^d} \exp\left(-\frac{(j_1\Delta)^2+\ldots+(j_d\Delta)^2}{4\sigma^2}\right)
					\\&= \frac{(4\pi)^{-\frac d2}}{\Delta^d}\sum_{\vec j\in\F Z^d\cap[-\hat m,\hat m]^d} \exp\left(-\frac14\left|\vec j\frac{\Delta}{\sigma}\right|^2\right)\frac{\Delta^d}{\sigma^d}
					\\&\sim \frac{(4\pi\sigma^2)^{-\frac d2}}{\Delta^d}\int_{\R^d} \exp\left(-\tfrac{|\vvarx0|^2}{4\sigma^2}\right) \quad = \Delta^{-d}.
	\end{align*}}}}
	\\This is a nice approximation because it depends only on $\Delta$, overcoming the $\frac1\sigma$ scaling. To convert this into an upper bound, we just compute the sum explicitly. In particular, as the sum factorises over dimensions,
	$$\norm{\A\A^*}_{\ell^2\to\ell^2} \leq (4\pi\sigma^2)^{-\frac d2}\left(\sum_{j=-\hat m,\ldots, \hat m}\exp\left(-\tfrac{\Delta^2}{4\sigma^2}j^2\right)\right)^d.$$
	Applying the same ideas to \Cref{thm:ca: norm bound smoothness}, note
	$$\begin{array}{rll}
			\displaystyle |\vard1_j(\vvarx0)| &\displaystyle= \left|\vard1_j(\vvarx0)\right| &\displaystyle = (2\pi\sigma^2)^{-\frac d2}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
			\\\displaystyle |\nabla\vard1_j(\vvarx0)| &\displaystyle= \left|\frac{\vvarx0-\vvarx0_j}{\sigma^2}\vard1_j(\vvarx0)\right| &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma}\frac{|\vvarx0-\vvarx0_j|}{\sigma}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
			\\|\nabla^2\vard1_j(\vvarx0)| &\displaystyle =\left|\frac1{\sigma^2} + \frac{(\vvarx0-\vvarx0_j)(\vvarx0-\vvarx0_j)^\top }{\sigma^4}\right|\vard1_j(\vvarx0) &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma^2}\left(1+\frac{|\vvarx0-\vvarx0_j|^2}{\sigma^2}\right)\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right).
	\end{array}$$
	With the substitution $\vvarx0=\frac{\Delta}{\sigma}\vec j$, the asymptotic bounds on these are clear:
	\begin{align*}
		\sum_{\vec j\in[\hat m]^d} |\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim (2\pi\sigma^2)^{-\frac{dq^*}{2}}\frac{\sigma^d}{\Delta^d}\int_{\R^d}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right),
		\\\sum_{\vec j\in[\hat m]^d} |\nabla\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma}\frac{\sigma^d}{\Delta^d}\int_{\R^d}|\vvarx0|^{q^*}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right),
		\\\sum_{\vec j\in[\hat m]^d} |\nabla^2\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^2}\frac{\sigma^d}{\Delta^d}\int_{\R^d}(1+|\vvarx0|^2)^{q^*}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right).
	\end{align*}
\end{proof}

\begin{proof}[Proof of precise case 3:]
	In the asymptotic case we have shown
	$$\begin{array}{rll}
			\displaystyle |\vard1_j(\vvarx0)| &\displaystyle= \left|\vard1_j(\vvarx0)\right| &\displaystyle = (2\pi\sigma^2)^{-\frac d2}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
			\\\displaystyle |\nabla\vard1_j(\vvarx0)| &\displaystyle= \left|\frac{\vvarx0-\vvarx0_j}{\sigma^2}\vard1_j(\vvarx0)\right| &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma}\frac{|\vvarx0-\vvarx0_j|}{\sigma}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
			\\|\nabla^2\vard1_j(\vvarx0)| &\displaystyle =\left|\frac1{\sigma^2} + \frac{(\vvarx0-\vvarx0_j)(\vvarx0-\vvarx0_j)^\top }{\sigma^4}\right|\vard1_j(\vvarx0) &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma^2}\left(1+\frac{|\vvarx0-\vvarx0_j|^2}{\sigma^2}\right)\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right).
	\end{array}$$
	We now wish to sum over $j=1,\ldots,m$ and produce an upper bound on these, independent of $t$. To do so we will use the following lemma.

	\begin{lemma}\label{app:ca: exp sum bound}
		Suppose $q>0$. If the polynomial $p(|\vvarx0|) = \sum p_k|\vvarx0|^k$ has non-negative coefficients and $\vvarx0\in[-m,m]^d$, then
		$$\sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq m}} p(|\vec{j}-\vvarx0|)\exp\left(-\tfrac{q|\vec{j}-\vvarx0|^2}{2}\right)\leq \left[\sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq2m}}p(|\vec{j}|+\delta)\exp\left(-\frac{q\max(0,|\vec{j}|-\delta)^2}{2}\right)\right]$$
		where $\delta\coloneqq \frac{\sqrt{d}}{2}$.
	\end{lemma}
	\begin{proof}
		There exists $\hat{\vvarx0}\in[-\tfrac12,\tfrac12]^d$ such that $\vvarx0 + \hat{\vvarx0}\in\F Z^d$, therefore
		\begin{align*}
			\sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq m}} p(|\vec{j}-\vvarx0|)\exp\left(-\tfrac{q|\vec{j}-\vvarx0|^2}{2}\right) &= \sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq m}} p(|\vec{j}-(\vvarx0+\hat{\vvarx0})+\hat{\vvarx0}|)\exp\left(-\tfrac{q|\vec{j}-(\vvarx0+\hat{\vvarx0})+\hat{\vvarx0}|^2}{2}\right)
			\\&\leq \sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq2m}} p(|\vec{j}+\hat{\vvarx0}|)\exp\left(-\tfrac{q|\vec{j}+\hat{\vvarx0}|^2}{2}\right)
			\\&\leq \sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq2m}} p(|\vec{j}|+\delta)\exp\left(-\tfrac{q\max(0,|\vec{j}|-\delta)^2}{2}\right)
		\end{align*}
		as $|\hat{\vvarx0}|\leq \delta$ and $p$ has non-negative coefficients. 
	\end{proof}

	Now, continuing the proof of \Cref{app:thm:ca: norm bound examples}, for $\hat m=\sqrt[d]{m}$, $\delta=\frac{\sqrt{d}}{2}$ and $J=\{\vec{j}\in\F Z^d \st \norm{\vec{j}}_{\ell^\infty}\leq 2\hat m\}$, \Cref{app:ca: exp sum bound} bounds 
	\begin{align*}
		\sum_{j=1}^m |\vard1_j(\vvarx0)|^{q^*} &\leq (2\pi\sigma^2)^{-\frac{dq^*}{2}} \left[\sum_{\vec{j}\in J} \exp\left(-\frac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec{j}|-\delta)^2\right)\right]
		\\\sum_{j=1}^m |\nabla\vard1_j(\vvarx0)|^{q^*} &\leq \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^{q^*}}\frac{\Delta^{q^*}}{\sigma^{q^*}} \left[\sum_{\vec{j}\in J} (|\vec{j}|+\delta)^{q^*}\exp\left(-\frac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec{j}|-\delta)^2\right)\right]
		\\\sum_{j=1}^m |\nabla^2\vard1_j(\vvarx0)|^{q^*} &\leq \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^{2q^*}} \left[\sum_{\vec{j}\in J} \left(1+\frac{\Delta^2}{\sigma^2}(|\vec{j}|+\delta)^2\right)^{q^*}\exp\left(-\frac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec{j}|-\delta)^2\right)\right]
	\end{align*}
	for all $\vvarx0\in\Domain$. In a worst case, this is $O(2^dm)$ time complexity however the summands all decay faster than exponentially and so should converge very quickly.	
\end{proof}

\end{document}

### 2021-01-07 paper.tex
Rename aFEM_paper.tex to paper.tex
Update paper to remove page-break
Update text and figures
Mainly minor text/figure editing. I added more necessary details to the introduction/notation section and simplified the 1D convergence plots in the results.

--- 2020-12-18 aFEM_paper.tex
@@
-\documentclass[10pt,a4paper,onecolumn]{article} \usepackage[latin1]{inputenc}
+\documentclass[10pt,a4paper,onecolumn]{article}
 \usepackage{amsmath,enumitem,datetime,xfrac,fix-cm,color,multirow,siunitx}
-\usepackage{amsfonts,amssymb,mathtools,stmaryrd,dsfont,tikz,amsthm}
+\usepackage{amsfonts,amssymb,mathtools,stmaryrd,dsfont,tikz,amsthm,bm}
+\usepackage[round,colon,authoryear]{natbib}
 \usepackage[cm]{fullpage}
@@
 \renewcommand{\P}{\F{P}}\newcommand{\E}{\F{E}}\newcommand{\1}{\F{1}}
-\newcommand{\tab}{\indent}\newcommand{\Tab}{\newline\tab}
 \renewcommand{\circle}[1]{\raisebox{.5pt}{\rm{\textcircled{\raisebox{-.9pt} {#1}}}}}
@@
 \newenvironment{adaptiveStep}{\refstepcounter{adaptStepCounter}}{}
-\crefname{adaptStepCounter}{step}{steps}
+\crefname{adaptStepCounter}{Step}{Steps}
 
@@
 
-\author{Robert Tovey}
+\author{Robert Tovey and Antonin Chambolle}
 \date{\longdate\today}
@@
 %The parallel to this for optimisation is that we still do not have infinite computing memory or processing power, but we still want to compute minimisers to a known accuracy with efficient implementations.
-It is typically much harder to control discretisation errors in optimisation problems, for instance the $\Gamma$-convergence of discrete total variation \cite{Bartels2012,Bartels2015} or the approximation errors for wavelets/curvelets/sheerlets \cite{Mallat1999,Candes2004,Guo2007}.
+It is typically much harder to control discretisation errors in optimisation problems, for instance the $\Gamma$-convergence of discrete total variation \citep{Bartels2012,Bartels2015} or the approximation errors for wavelets/curvelets/sheerlets \citep{Mallat1999,Candes2004,Guo2007}.
 These are typically quite weak guarantees valid for asymptotic resolution/time and are hard to quantify in a specific example.
@@
 \section{Introduction}
-The standard setting of the Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) is that there exists a Hilbert space $\F H$ over which we wish to minimise the function 
-\begin{equation}\label{eq:ca: min F = fD+fC}
-	\min_{\varf0\in\F H}\Func0(\varf0)  \qquad\text{such that}\qquad \Func0(\varf0)\coloneqq \func1(\varf0) + \func2(\varf0),
+The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was first proposed by \citet{Beck2009} and is now a very popular algorithm for minimising the sum of two convex functions.
+We will write this as the problem of computing
+\begin{equation}\label{eq: min F = fD+fC}
+	u^* \in \argmin_{\varf0\in\F H}\Func0(\varf0)  \qquad\text{such that}\qquad \Func0(\varf0)\coloneqq \func1(\varf0) + \func2(\varf0),
 \end{equation}
 where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function.
-FISTA is a practically fast algorithm which, for many choices of $\Func0$, generates a sequence of iterates $\varf0_n\in\F H$ such that $\Func0(\varf0_n)$ converges at the optimal rate of $O(n^{-2})$ \cite{Beck2009,Chambolle2015}.
-
-The canonical example for this work will be the Lasso energy,
-$$\Func0(\varf0) = \tfrac12\norm{\A\varf0-\vdata0}_2^2 + \mu\norm{\varf0}_1$$
-where $\vdata0\in\R^m$ is some observed data, $\A\colon \C M(\R^d)\to \R^m$ is the forward map and $\mu>0$ is a chosen scalar. It is known that there exist minimisers of $\Func0$ of the form:
-$$\varf0^* = \sum_{i=1}^{m}\vars0_i\delta_{\vvarx0_i}, $$
-for some $\vars0_i\in\R$ and where $\delta_{\vvarx0_i}$ is the Dirac delta function centred at $\vvarx0_i\in\R^d$ \cite{Unser2016,Boyer2019}.
-The challenge with this minimiser is that $\varf0^*\in L^1\setminus L^2$, so exact FISTA cannot be applied to this problem.
-On the other hand, $\varf0^*$ has a very nice structure which we expect can be easily and efficiently represented by, for instance, a basis of finite elements.
-
-In this work we propose a modification of FISTA which addresses both of these points. During each iteration we restrict computation to a subspace, i.e. $\varf0_n\in\spcf0^n\subset\F H$.
-For infinite dimensional optimisation, this allows us to reconstruct $\varf0^*$ to an arbitrary precision in finite time.
-Alternatively, for finite dimensional optimisation this potentially allows for a more computationally efficient variant of the classical FISTA algorithm.
-
-Inexact optimisation is a well-established field which can be seen to encompass methods such as coordinate descent \cite{Wright2015}, stochastic gradient \cite{Spall2005,Bottou2018}, or indeed approximate FISTA-like algorithms \cite{Jiang2012,Villa2013}.
-The result of \Cref{thm:ca: exponential FISTA convergence} is very similar to \cite[Proposition 2]{Schmidt2011} and \cite[Proposition 3.3]{Aujol2015}.
-The key novelty is the concept of convergence outside of the Hilbert space $\F H$.
-Additionally assuming that errors come from quantified subspace approximations, we can also provide explicit rates.
+The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$.
+\citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$ when $u^*\in \F H$ is finite dimensional and \cite{Chambolle2015} extended this result to the general Hilbert space setting.
+Many further works have gone on to demonstrate even faster practical convergence rates for slightly modified variants of FISTA in specific scenarios \citep{some references}.
+
+The contribution of this work is a modified FISTA algorithm which achieves two key properties:
+\begin{itemize}
+	\item we extend the convergence results to the case $\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space.
+The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
+	\item we allow for adaptive discretisation such that $\varf0_n\in\spcf0^n\subset\F H$.
+With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence.
+In the Hilbert space setting this is the original $n^{-2}$ rate.
+In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation in both measures of time and computer memory requirements.
+\end{itemize}
+\todo{There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for the use outside of Hilbert spaces is the key novelty.} Some other works for FISTA-like algorithms include \citep{Jiang2012,Villa2013}.
+Of particular note, our stability estimate for FISTA  in \Cref{thm: exponential FISTA convergence} is very similar to \cite[Proposition 2]{Schmidt2011} and \cite[Proposition 3.3]{Aujol2015}.
+This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations.
+
+\subsection{Canonical example}
+While the analysis of this work is applicable to general choices of $\func1$ and $\func2$, we will refer back to the example of the (Beurling) Lasso model both for motivation and for numerical examples.
+We state the Lasso energy as
+\begin{equation}\label{eq: Lasso energy intro}
+	\Func0(\varf0) = \tfrac12\norm{\A\varf0-\vdata0}_2^2 + \mu\norm{\varf0}_1,
+\end{equation}
+where $\vdata0\in\R^m$ is some observed data, $\A\colon \C M(\Domain)\to \R^m$ is the forward map and $\mu>0$ is an appropriately chosen scalar.
+We have $\F H = L^2(\Domain)$ and $\spcf0 = \C M(\Domain)$ the space of measures on $\Domain$ equipped with the $L^1$ norm.
+In the continuous setting $\Domain = [0,1]^d$ and for discrete we have $\Domain=\F N$, i.e.
+$\spcf0\cong\ell^1(\R)$.
+
+It is a well-known result of representer theorems for $\Func0$ \citep{Unser2016,Boyer2019} that there exist minimisers of the form 
+\begin{equation}
+	\varf0^* = \sum_{i=1}^{m}\vars0_i\delta_{\vvarx0_i}, 
+\end{equation}
+for some $\vars0_i\in\R$ and where $\delta_{\vvarx0_i}$ is the Dirac delta function centred at $\vvarx0_i\in\R^d$.
+
+This is a practical example where we have the relation $\varf0^*$ does not lie in the Hilbert space $\F H$, and yet it is very easy to approximate with a discrete basis.
+Our approach will be to use finite elements which can clearly generalise to other examples.
 
@@
 This chapter is organised as follows.
-\Cref{sec:ca: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, \Cref{alg:ca: refining FISTA}.
-The main theoretical contribution of this work is the convergence analysis of \Cref{alg:ca: refining FISTA} which is split into two parts: first we outline the proof structure in \Cref{sec:ca: recipe}, then we state the specific results in the case of FISTA in \Cref{sec:ca: FISTA convergence}.
-The main results are \Cref{thm:ca: exponential FISTA convergence} and \Cref{thm:ca: practical refinement criteria} which extend the convergence of FISTA to infinite dimensional Banach spaces with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.
-
-\Cref{sec:ca: general examples} presents some general results for the application of \Cref{alg:ca: refining FISTA} and \Cref{sec:ca: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation.
+\Cref{sec: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, \Cref{alg: refining FISTA}.
+The main theoretical contribution of this work is the convergence analysis of \Cref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in \Cref{sec: recipe}, then we state the specific results in the case of FISTA in \Cref{sec: FISTA convergence}.
+The main results are \Cref{thm: exponential FISTA convergence} and \Cref{thm: practical refinement criteria} which extend the convergence of FISTA to infinite dimensional Banach spaces with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.
+
+\Cref{sec: general examples} presents some general results for the application of \Cref{alg: refining FISTA} and \Cref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation.
 In particular, we describe how to choose efficient refining discretisations to approximate $\varf0^*$, estimate the convergence of $\Func0$, and identify the support of $\varf0^*$.
-The numerical results in \Cref{sec:ca: numerics} demonstrate these techniques in four different models demonstrating the sharpness of our analysis and the computational efficiency of adaptive discretisations.
-
-\section{Definitions and notation}\label{sec:ca: prelims}
-We consider optimisation of \eqref{eq:ca: min F = fD+fC} over two spaces, the Banach space $(\spcf0,\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
-$$ \exists\varf0^*\in \spcf0 \quad\st\quad \Func0(\varf0^*) = \min_{\varf0\in\spcf0}\Func0(\varf0) = \min_{\varf0\in\F H}\Func0(\varf0).$$
-We further define
-$$\Func0_0\colon \varf0\mapsto \Func0(\varf0)-\Func0(\varf0^*).$$
-Note that $\Func0_0$ is uniquely defined, even if $\varf0^*$ may not be.
-
-We propose a refining FISTA algorithm in \Cref{alg:ca: refining FISTA} for a choice of refining subspaces $\spcf0^n\subset\spcf0^{n+1}\subset \spcf0\cap\F H$ for $n=0,1,\ldots$.
+The numerical results in \Cref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.
+
+\section{Definitions and notation}\label{sec: prelims}
+We consider optimisation of \eqref{eq: min F = fD+fC} over two spaces, the Banach space $(\spcf0,\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
+\begin{equation} 
+	\exists\varf0^*\in \spcf0 \quad\st\quad \Func0(\varf0^*) = \min_{\varf0\in\spcf0}\Func0(\varf0) = \min_{\varf0\in\F H}\Func0(\varf0).
+\end{equation}
+Furthermore, define the translated energy
+\begin{equation}
+	\Func0_0\colon\spcf0\cup\F H\to \R,\qquad \Func0_0(\varf0) \coloneqq \Func0(\varf0)-\Func0(\varf0^*).
+\end{equation}
+Note that the value of $\Func0_0$ is uniquely defined, even if $\varf0^*$ may not be. \todo{We could just say $E_0=E$ without loss of generality, just like $L=1$.}
+
+The proposed generalised FISTA algorithm is stated in \Cref{alg: refining FISTA} for an arbitrary choice of refining subspaces $\spcf0^n\subset \spcf0\cap\F H$ for $n=0,1,\ldots$.
 The only difference is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$.
-Indeed, if $\spcf0^n=\spcf0=\F H$ then this is just the standard FISTA algorithm.
+If $\spcf0^n=\spcf0=\F H$ then we recover the standard FISTA algorithm.
 
@@
 
+One defining property of the FISTA algorithm is an appropriate choice of inertia, dictated by $\vart1_n$. In particular, we will say that $(\vart1_n)_{n=0}^\infty$ is a \emph{FISTA stepsize} if
+\begin{equation}\label{def: t_n and rho_n}
+	t_0 = 1, \qquad t_n \geq 1, \qquad \text{and}\qquad \rho_n \coloneqq t_n^2 - t_{n+1}^2 + t_{n+1} \geq 0\qquad \text{ for all }n=0,1,\ldots
+\end{equation}
+
 Finally we introduce the concept of an orthogonal projection in the setting of this work.
@@
 Note that $\spcf0^n\subset\F H$ implies that $(\spcf0^n)^*\supset\F H$, therefore $\Pi_n$ is an extension of the classical orthogonal projection.
-It is convenient to allow an extension here because $\spcf0$ may be bigger than $\F H$, $(\spcf0^n)^*$ is the largest space such that $\Pi_n$ is well-defined.
+It is convenient to allow an extension here because $\spcf0$ may be bigger than $\F H$, $(\spcf0^n)^*$ is the largest space such that $\Pi_n$ is sufficiently well-defined.
 Beyond this, the Hahn-Banach theorem may allow the domain of $\Pi_n$ to be extended further, but the definition is no longer unique.
@@
 
-Constant factors will generally not be tracked during the proofs in this chapter. For sequences $(a_n)_{n=1}^\infty$,$(b_n)_{n=1}^\infty$ we will frequently use the notation:
+The precise constants associated to a given rate are given in the statements of the theorems but, for convenience, are otherwise omitted from the text.
+For sequences $(a_n)_{n=1}^\infty$,$(b_n)_{n=1}^\infty$ we will use the notation:
 \begin{align*}
@@
 
-\begin{algorithm}[b!]\caption{Refining sub-space FISTA}\label{alg:ca: refining FISTA}
+\begin{algorithm}\caption{Refining sub-space FISTA}\label{alg: refining FISTA}
 	\centering
@@
 		\State $\bar{\varf0}_n \gets (1-\tfrac{1}{\vart1_n})\varf0_n + \tfrac{1}{\vart1_n}\varf1_n$
-		\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \func1(\bar{\varf0}_n)}^2+\func2(\varf0)$
+		\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \func1(\bar{\varf0}_n)}^2+\func2(\varf0)$ \Comment{Only modification, $\spcf0^{n+1}\subset \spcf0$}
 		\State $\varf1_{n+1} \gets (1-\vart1_n)\varf0_n + \vart1_n\varf0_{n+1}$
@@
 
-\section{General proof recipe}\label{sec:ca: recipe}
-In this work we focus on the FISTA algorithm, however, the key ingredients of the proof do not rely on the particular structure of FISTA.
-In this section we will sketch the general `recipe' of the convergence proof for adaptive schemes in a Banach space setting.
-
-During this section, we will refer to the structure of FISTA as motivation. In particular, we recall the classical FISTA convergence guarantee given in \cite[Theorem 2]{Chambolle2015}:
-\begin{equation}\label{eq:ca: classical FISTA}
+\section{General proof recipe}\label{sec: recipe}
+In this section we give an intuitive outline of the full proof for convergence of \cref{alg: refining FISTA} before giving formal theorems and proofs in the next section.
+First we recall the classical FISTA convergence guarantee given by \citet[Theorem 2]{Chambolle2015}:
+\begin{equation}\label{eq: classical FISTA}
 	t_N^2\Func0_0(\varf0_N) + \sum^{N-1}_{n=1}\rho_n\Func0_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf0^*}^2 \leq \tfrac12\norm{\varf0_0-\varf0^*}^2
 \end{equation}
-for some $t_N\simeq N$ and $\rho_n\geq0$.
-
-\subsubsection{Step 1: Quantifying the scaling properties}
-\begin{adaptiveStep}\label{step:ca: step 1 smoothness}
-	The first step is to quantify how $\Func0$ and $\norm\cdot$ behave as the discretisation refines, or resolution increases.
-In \Cref{alg:ca: refining FISTA} we are given the subspaces $\spcf0^n$ which we partition into a sequence of milestones.
-In particular, we assume there exists $n_k\in\F N$ and constants $\vars3_{\Varf0},\vars3_{\Func0}\geq1$ such that:
-	$$n_0<n_1<\ldots, \qquad \norm{\argmin_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0)} \lesssim \vars3_{\Varf0}^k, \qquad \text{and}\qquad \min_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0) \lesssim \vars3_{\Func0}^{-k}.$$
-
-	The idea is that $\spcf0^{n_k}$ is a discretisation at resolution $\meshsize^k$ for some $\meshsize<1$ and therefore the minimum of $\Func0_0$ decays exponentially while the norm of discrete minimisers potentially grows exponentially.
-In \Cref{sec:ca: general examples} we will see that this exponential scaling is very natural.
-
-	The value of $\vars3_{\Varf0}$ is dictated by the Banach space $\spcf0$ in relation $\F H$.
-If $\varf0^*\in \spcf0\setminus\F H$, as for Lasso, then the right-hand side of \eqref{eq:ca: classical FISTA} becomes infinity.
-All norms are equivalent on finite dimensional subspaces, but the scaling of this relationship is quantified by $\vars3_{\Varf0}>1$.
-The value of $\vars3_{\Func0}>1$ is an indicator of how easy $\Func0$ is to discretise.
-If $\Func0$ is very smooth and the choice of discrete basis is very efficient then $\vars3_{\Func0}$ is large.
+for some FISTA stepsize choice $t_N\simeq N$ and $\rho_n\geq0$.
+
+\paragraph{Step 1: Quantifying the stability}
+\begin{adaptiveStep}\label{step: step 1 stability}
+	The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting subspaces $\spcf0^n$.
+In the notation of \cref{alg: refining FISTA}, \cref{thm: mini FISTA convergence} shows that
+	\begin{equation}\label{eq: mini FISTA convergence}
+		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf2_N}^2 \leq \tfrac12\norm{\varf0_0-\varf2_0}^2 +\tfrac{\norm{\varf2_N}^2-\norm{\varf2_0}^2}2 + \sum^N_{n=1} \vart1_n\Func0_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}
+	\end{equation}
+	for $\varf2_n = \argmin_{\varf0\in\spcf0^n}\Func0(\varf0)$.
+The similarities to \eqref{eq: classical FISTA} are clear.
+If $\spcf0^n=\spcf0$, then we have $\varf2_n=\varf0^*$ and the two estimates agree.
+These extra terms quantify the robustness to changing of discretisation.
+\end{adaptiveStep}
+
+\paragraph{Step 2: Quantifying the scaling properties}
+\begin{adaptiveStep}\label{step: step 2 smoothness}
+	To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\spcf0^n$.
+To do so, we construct a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\Func0}\geq1$ such that for each $k\in\F N$
+	\begin{equation}
+		n\leq n_k \implies \norm{\varf2_n} \lesssim \vars3_{\Varf0}^k, \qquad n\geq n_k \implies \Func0_0(\varf2_n) \lesssim \vars3_{\Func0}^{-k}.
+	\end{equation}
+	The choice of exponential scaling is very natural if we consider the $\spcf0^n$ to be the subspace of functions discretised on a uniform mesh.
+If that mesh sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$.
+The integer $n_k$ should then be the time when the mesh has refined $k$ times.
+
+	The value of $\vars3_{\Varf0}$ is dictated by the smoothness of the norm of $\spcf0$ with respect to that of $\F H$.
+If $\norm{\varf0^*}<\infty$, then the value is $\vars3_{\Varf0}=1$, otherwise there is some damage to the rate of convergence generated by this factor.
+On the other hand, the value of $\vars3_{\Func0}$ is dictated by the smoothness of $\Func0$ at the point $\varf0^*$.
+If an efficient basis is used, then $\vars3_{\Func0}$ is large.
 The trade-off between $\vars3_{\Func0}$ and $\vars3_{\Varf0}$ dictates the final convergence rate of the algorithm.
@@
 
-\subsubsection{Step 2: Generalising the convergence bound}
-\begin{adaptiveStep}\label{step:ca: step 2 convergence bound}
-	The bound in \eqref{eq:ca: classical FISTA} is only valid when $\spcf0^n$ is a constant sequence.
-The first analytical step is to quantify the effect of refinement.
-\Cref{thm:ca: mini FISTA convergence} gives an expression for this for generic choices of $\spcf0^n$ in \Cref{alg:ca: refining FISTA}.
-
-	If $\spcf0^n$ is a constant sequence then \Cref{thm:ca: mini FISTA convergence} recovers the right-hand side of \eqref{eq:ca: classical FISTA} through a large telescoping sum, the exact form of the sum does not matter at this moment.
-Without further assumptions, the sum does not telescope and the bound grows linearly with $n$.
-If we re-introduce the sequence $n_k$ from the previous step then we can simplify this inequality.
-In particular, if
+\paragraph{Step 3: Generalising the convergence bound}
+\begin{adaptiveStep}\label{step: step 3 convergence bound}
+	In this step we combine the FISTA stability estimate with the subspace approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\Func0}$ and $\vars3_{\Varf0}$.
+For example, if $\spcf0^n$ is of the form
 	$$ \spcf0^{n_k} = \spcf0^{n_k+1} = \ldots = \spcf0^{n_{k+1}-1},$$
-	then the right-hand side will telescope on the intervals $(n_k,n_{k+1})$ and scale only with $k\simeq\log(n)$. The result of this is presented in \Cref{thm:ca: mini exponential FISTA convergence}.
-
-	The take-home message here is that the introduction of the milestones $n_k$ greatly simplifies the convergence bound expression and allows us to utilise the scaling properties described in \Cref{step:ca: step 1 smoothness}.
+	then many terms on the right-hand side of \eqref{eq: mini FISTA convergence} telescope to 0.
+The result of this is presented in \Cref{thm: mini exponential FISTA convergence} but the moral is that the stability error in \eqref{eq: mini FISTA convergence} should scale in proportion to the $k$ (related to the resolution) rather than the total number of iterations $N$.
 \end{adaptiveStep}
 
-\subsubsection{Step 3: Sufficiently fast refinement}
-\begin{adaptiveStep}\label{step:ca: step 3 sufficiently fast}
-	In \Cref{step:ca: step 2 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq:ca: classical FISTA} by a constant factor.
-In particular, it is equivalent to run \Cref{alg:ca: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed subspace $\spcf0^N$.
-\Cref{thm:ca: sufficiently fast} shows that this is true so long as $\spcf0^n$ refine sufficiently quickly, i.e.
+\paragraph{Step 4: Sufficiently fast refinement}
+\begin{adaptiveStep}\label{step: step 4 sufficiently fast}
+	In \Cref{step: step 3 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor.
+In particular, it is equivalent to run \Cref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed subspace $\spcf0^N$.
+The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\Func0_0(\varf0_N)\lesssim \norm{\varf0_0-\varf2_N}^2 = O(\vars3_{\Varf0}^{2K})$ for $N\leq n_K$.
+\Cref{thm: sufficiently fast} shows that \Cref{alg: refining FISTA} can achieve the same order of approximation so long as $\spcf0^n$ refine sufficiently quickly, i.e.
 $n_k$ are sufficiently small.
-In summary, in comparison with \eqref{eq:ca: classical FISTA}, we show $$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} = O\left(\frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\Func0(\varf0)}^2}{N^2}\right)$$
-	for all $N\leq n_K$. 
 \end{adaptiveStep}
 
-\subsubsection{Step 4: Sufficiently slow refinement}
-\begin{adaptiveStep}\label{step:ca: step 4 sufficiently slow}
-	The result of \Cref{step:ca: step 3 sufficiently fast} is sufficient to prove convergence, but not directly a rate.
-If the subspaces refine too quickly then this factor of $\norm{\varf0^*}=\infty$ will slow the rate of convergence.
-Refinement should happen sufficiently quickly so that we do not waste time overfitting to the discretisation, but low resolution problems converge faster therefore we should then refine as slowly as possible.
-\Cref{thm:ca: sufficiently slow} balances these two factors in an optimal way for the FISTA algorithm.
-This results in a convergence guarantee of the form
-	$$ \Func0_0(\varf0_N) \lesssim \frac{N^{2\epsilon}}{N^2}$$
-	for all $N\in\F N$, some $\epsilon\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\Func0}$. In particular, if $\varf0^*\in\F H$ then $\epsilon=0$ recovers the classical rate.
+\paragraph{Step 5: Sufficiently slow refinement}
+\begin{adaptiveStep}\label{step: step 5 sufficiently slow}
+	The result of \Cref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate.
+If the subspaces refine too quickly, then the influence of $\norm{\varf0^*}=\infty$ will slow the rate of convergence.
+If the resolution is too coarse then we are overfitting to the discrete minimiser, but if the resolution is too fine then convergence of the energy is slow.
+\Cref{thm: sufficiently slow} balances these two factors in an optimal way for \cref{alg: refining FISTA} resulting in a convergence rate of
+	$$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\epsilon}}{N^2}$$
+	for all $N\in\F N$, some $\epsilon\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\Func0}$. In particular, if $\varf0^*\in\F H$ then we recover the classical rate with $\epsilon=0$.
 \end{adaptiveStep}
 
-\subsubsection{Step 5: Adaptivity}
-\begin{adaptiveStep}\label{step:ca: step 5 adaptivity}
-	Up to this point we have implicitly focused on the case where $\spcf0^n$ and $n_k$ are chosen a priori.
-Here we emphasise some of the challenges which are faced when extending results to allow for on-the-fly greedy adaptivity.
-
-	Spatial adaptivity is robust, so long as the scaling properties of \Cref{step:ca: step 1 smoothness} are satisfied.
-The only other constraint is to ensure that the partial telescoping of \Cref{step:ca: step 2 convergence bound} still holds.
-In the case of FISTA, \Cref{thm:ca: mini exponential FISTA convergence} shows that this only requires the existence of $\tilde{\varf2}_k\in\spcf0^{n_k}$ such that
-	$$\tilde{\varf2}_k\in\spcf0^{n_k}\cap\spcf0^{n_k+1}\cap\ldots\cap\spcf0^{n_{k+1}-1}.$$
-
-	Refinement time adaptivity is more challenging for FISTA due to the non-descent property of the algorithm.
-The idea is that resolution should increase rapidly while $\Func0$ is `easy' to optimise then default to the rate of \Cref{step:ca: step 4 sufficiently slow} when it is `hard'.
-The result of this is \Cref{thm:ca: stronger exponential FISTA convergence} which shows
+\paragraph{Step 6: Adaptivity}
+\begin{adaptiveStep}\label{step: step 6 adaptivity}
+	Up to this point we have implicitly focused on the case where $\spcf0^n$ (and $n_k$) are chosen a priori.
+Here we emphasise some of the challenges which are faced when extending results to allow for greedy adaptivity.
+
+	Spatial adaptivity is robust, so long as the scaling properties of \Cref{step: step 2 smoothness} are satisfied.
+The only other constraint is to ensure that the partial telescoping of \Cref{step: step 3 convergence bound} still holds.
+\Cref{thm: mini exponential FISTA convergence} shows that a sufficient condition is
+	$$\spcf0^{n_k}\subset\spcf0^{n_k+1}\subset\ldots\subset\spcf0^{n_{k+1}-1}.$$
+	Convergence is most stable if the approximation spaces $\spcf0^n$ satisfy a monotone inclusion, breaking the monotonicity requires more care.
+
+	Adaptively choosing the time of refinement is more challenging due to the non-descent property of FISTA.
+The idea is that $\spcf0^n$ should be refined as soon as the value $\Func0(\varf0_n)$ is sufficiently close to $\Func0(\varf2_n)$.
+This is analysed in \Cref{thm: stronger exponential FISTA convergence} which shows convergence results of the form
 	$$ \min_{n\leq N}\Func0_0(\varf0_n) \lesssim \frac{N^{2\epsilon}}{N^2}$$
-	for all $N\in\F N$, the same $\epsilon\in[0,1)$ from \Cref{step:ca: step 4 sufficiently slow}.
+	for all $N\in\F N$, with the same $\epsilon\in[0,1)$ from \Cref{step: step 5 sufficiently slow}.
 The penalty for accelerating the refinement time is a potential loss of stability in $\Func0(\varf0_n)$, however, the asymptotic rate is equivalent and this behaviour has not been seen in numerical experiments.
@@
 
-\section{Proof of convergence}\label{sec:ca: FISTA convergence}
-In this section we follow the recipe motivated in \Cref{sec:ca: recipe} to prove convergence of two variants of \Cref{alg:ca: refining FISTA}.
-Motivated by this argument, we will first formalise the definition of the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$.
-\begin{definition}\label{def:ca: exp subspaces}
+\section{Proof of convergence}\label{sec: FISTA convergence}
+In this section we follow the recipe motivated in \Cref{sec: recipe} to prove convergence of two variants of \Cref{alg: refining FISTA}.
+Each of the main theorems and lemmas will be stated with a sketch proof in this section.
+The details of the proofs are either trivial or very technical and are therefore placed in \Cref{app: FISTA convergence} to preserve the flow of the argument.
+
+\subsection{Computing the convergence bound}
+For \Cref{step: step 1 stability} of \Cref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for \Cref{alg: refining FISTA}.
+The proofs in this step follow the classical arguments of \citep{Beck2009,Chambolle2015} very closely.
+
+\subsubsection{Single iterations}
+We first wish to understand a single iteration of \Cref{alg: refining FISTA}. This is done through the following two lemmas.
+\begin{lemma}[equivalent to {\cite[Lemma 1]{Chambolle2015}}]\label{thm: descent lemma}
+	\Copy{thm: descent lemma}{
+		Suppose $\nabla \func1$ is 1-Lipschitz, for any $\bar{\varf0}\in \spcf0^{n-1}$ define
+		$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \func1(\bar{\varf0})}^2+\func2(\varf0).$$
+		Then, for all $\varf2\in\bar{(\spcf0^n)^*}\supset\F H$, we have
+		$$\Func0(\varf0) + \tfrac12\norm{\varf0-\Pi_n\varf2}^2 \leq \Func0(\Pi_n\varf2) + \tfrac12\norm{\bar{\varf0}-\Pi_n\varf2}^2$$
+		where $\Pi_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.
+	}
+\end{lemma}
+\noindent This is exactly the result of \citep{Chambolle2015} applied to the function $\varf0\mapsto\Func0(\Pi_n\varf0)$.
+Applying \Cref{thm: descent lemma} to the iterates from \Cref{alg: refining FISTA} gives a more explicit inequality.
+
+\begin{lemma}[analogous to {\cite[Theorem 2]{Chambolle2015}, \cite[Theorem 1]{Beck2009}}]\label{thm: one step FISTA}
+	\Copy{thm: one step FISTA}{
+		Let $\spcf0^n\subset\F H\cap\spcf0$ and $\varf2_n\in\spcf0^n$ be chosen arbitrarily and $\varf0_n$/$\varf1_n$ be generated by \Cref{alg: refining FISTA} for all $n\in\F N$.
+		For all $n\in\F N$ it holds that}
+	\begin{equation}
+		\vart1_{n}^2(\Func0(\varf0_{n}) - \Func0(\varf2_n)) - (\vart1_{n}^2-\vart1_{n})(\Func0(\varf0_{n-1})-\Func0(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.\label{eq: one-step FISTA}
+	\end{equation}
+\end{lemma}
+\noindent The proof is given in \cref{app:thm: one step FISTA} and is a result of the convexity of $\Func0$ for a well chosen $\varf2$ in \Cref{thm: descent lemma}.
+
+\subsubsection{Generic convergence bound}
+\Cref{thm: one step FISTA} gives us an understanding of a single iteration of \Cref{alg: refining FISTA}, summing over $n$ then gives our generic convergence bound for any variant of \Cref{alg: refining FISTA}.
+
+\begin{theorem}\label{thm: mini FISTA convergence}
+	\Copy{thm: mini FISTA convergence}{
+		Fix a sequence of subspaces $\{\spcf0^n\subset\spcf0\cap\F H\st n\in\F N\}$, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(\vart1_n)_{n\in\F N}$.
+Let $\varf0_n$ and $\varf1_n$ be generated by \Cref{alg: refining FISTA}.
+		Then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have}
+	\begin{equation}\label{eq: FISTA inequality}
+		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
+		 + \sum^N_{n=1} \vart1_n\Func0_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
+	\end{equation}
+\end{theorem}
+\noindent The proof is given in \cref{app:thm: mini FISTA convergence}.
+This result is the key approximation for showing convergence of FISTA with refining sub-spaces.
+In the classical setting, we have $\spcf0^n=\spcf0=\F H$, $\varf2_n=\varf0^*$ and the extra terms on the right-hand side collapse to 0.
+
+The natural choice in \eqref{eq: FISTA inequality} is $\varf2_n=\Pi_n\varf0^*$, however, there are simple counter-examples which give $\Func0(\Pi_n\varf0^*)=\infty$ and so this inequality becomes useless.
+A simple example, if $\func1(\varf0) = \norm{\varf0}_2^2$, $\func2$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$ and $\spcf0^n$ is a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$.
+On the other hand, suppose one of the pixels of the discretisation is $[\varx0_0-\meshsize,\varx0_0+\meshsize]$, then
+$$\Pi_n\varf0^*\left(\varx0_0+\sfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varx0-\vars5)^2d\varx0 = \varx0_0 < \varx0_0+\sfrac\meshsize2.$$
+In particular $\Pi_n\varf0^* \notin\F D$ therefore $\Func0(\Pi_n\varf0^*) = \infty$.
+
+The choice $\varf2_n=\argmin_{\varf0\in\spcf0^n}\Func0(\varf0)$ is much more robust and allows us to apply \cref{alg: refining FISTA} more broadly.
+The penalty for this flexibility is a more complicated analysis, each time the sub-space changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.
+
+\subsection{Convergence bound with milestones}
+In standard FISTA, the right-hand side of \eqref{eq: FISTA inequality} is a constant.
+The following lemma minimises the growth of the `constant' as a function of $N$ by partially telescoping the sum on the right-hand side.
+Before progressing to the content of \cref{step: step 3 convergence bound}, we will first formalise the definition of the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ introduced in \Cref{step: step 2 smoothness}.
+\begin{definition}\label{def: exp subspaces}
 	Fix $\vars3_{\Varf0},\vars3_{\Func0}\geq 1$ and a sequence of subspaces $\{\tilde{\spcf0}^k\subset\F H\cap\spcf0\st k\in\F N\}$.
@@
 \end{definition}
-In this section we will simply assume that such sequences exist and in \Cref{sec:ca: general examples} we will give some more general examples.
-Each of the main theorems and lemmas will be stated with a sketch proof in this section.
-The details of the proofs are either trivial or very technical and are therefore placed in \Cref{app:ca: FISTA convergence} to preserve the flow of the argument.
-
-\subsection{Computing the convergence bound}
-For \Cref{step:ca: step 2 convergence bound} of \Cref{sec:ca: recipe} we look to replicate the classical bound of the form in \eqref{eq:ca: classical FISTA} for \Cref{alg:ca: refining FISTA}.
-The proofs in this step follow the classical arguments of \cite{Beck2009,Chambolle2015} very closely.
-
-\subsubsection{Single iterations}
-We first wish to understand a single iteration of \Cref{alg:ca: refining FISTA}. This is done through the following two lemmas.
-\begin{lemma}[equivalent to {\cite[Lemma 1]{Chambolle2015}}]\label{thm:ca: descent lemma}
-	\Copy{thm:ca: descent lemma}{
-		Suppose $\nabla \func1$ is 1-Lipschitz, for any $\bar{\varf0}\in \spcf0^{n-1}$ define
-		$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \func1(\bar{\varf0})}^2+\func2(\varf0).$$
-		Then, for all $\varf2\in\bar{(\spcf0^n)^*}\supset\F H$, we have
-		$$\Func0(\varf0) + \tfrac12\norm{\varf0-\Pi_n\varf2}^2 \leq \Func0(\Pi_n\varf2) + \tfrac12\norm{\bar{\varf0}-\Pi_n\varf2}^2$$
-		where $\Pi_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.
-	}
-\end{lemma}
-This is exactly the result of \cite{Chambolle2015} applied to the function $\varf0\mapsto\Func0(\Pi_n\varf0)$.
-Applying \Cref{thm:ca: descent lemma} to the iterates from \Cref{alg:ca: refining FISTA} gives a more explicit inequality.
-
-\begin{lemma}[analogous to {\cite[Theorem 2]{Chambolle2015}, \cite[Theorem 1]{Beck2009}}]\label{thm:ca: one step FISTA}
-	\Copy{thm:ca: one step FISTA}{
-		Let $\spcf0^n\subset\F H\cap\spcf0$ and $\varf2_n\in\spcf0^n$ be chosen arbitrarily and $\varf0_n$/$\varf1_n$ be generated by \Cref{alg:ca: refining FISTA} for all $n\in\F N$.
-		For all $n\in\F N$ it holds that}
-	\begin{equation}
-		\vart1_{n}^2(\Func0(\varf0_{n}) - \Func0(\varf2_n)) - (\vart1_{n}^2-\vart1_{n})(\Func0(\varf0_{n-1})-\Func0(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.\label{eq:ca: one-step FISTA}
-	\end{equation}
-\end{lemma}
-
-The proof of this lemma is a result of the convexity of $\Func0$ for a well chosen $\varf2$ in \Cref{thm:ca: descent lemma}.
-
-\subsubsection{Generic convergence bound}
-\Cref{thm:ca: one step FISTA} gives us an understanding of a single iteration of \Cref{alg:ca: refining FISTA}, summing over $n$ then gives our generic convergence bound for any variant of \Cref{alg:ca: refining FISTA}.
-
-\begin{theorem}\label{thm:ca: mini FISTA convergence}
-	\Copy{thm:ca: mini FISTA convergence}{
-		Fix a sequence of subspaces $\{\spcf0^n\subset\spcf0\cap\F H\st n\in\F N\}$, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(\vart1_n)_{n\in\F N}$.
-Let $\varf0_n$ and $\varf1_n$ be generated by \Cref{alg:ca: refining FISTA}.
-		Then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have}
-	\begin{multline}\label{eq:ca: FISTA inequality}
-		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
-		\\ + \sum^N_{n=1} \vart1_n\Func0_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
-	\end{multline}
-\end{theorem}
-This result is the key approximation for showing convergence of FISTA with refining sub-spaces.
-In the classical setting, we have $\spcf0^n=\spcf0=\F H$, $\varf2_n=\varf0^*$ and the extra terms on the right-hand side collapse to 0.
-
-%The natural choice in \Cref{eq:ca: FISTA inequality} is $\varf2_n=\Pi_n\varf0^*$, however, there are simple counter-examples which give $\Func0(\Pi_n\varf0^*)=\infty$ and so this inequality becomes useless.
-A simple example, if $\func1(\varf0) = \norm{\varf0}_2^2$, $\func2$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$ and $\spcf0^n$ is a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$.
-On the other hand, $\Pi_n \varf0^*$ is the piecewise projection to the mean so it must be that $\Pi_n \varf0^*\notin \F D$.
-To see this, suppose one of these pixels is $[\varx0_0-\meshsize,\varx0_0+\meshsize]$, then $$\Pi_n\varf0^*\left(\varx0_0+\sfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \intbar_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}\varf0^*(\varx0)d\varx0= \varx0_0 < \varx0_0+\sfrac\meshsize2,$$
-%which violates the constraint of $\F D$.
-%
-%The choice $\varf2_n=\argmin_{\varf0\in\spcf0^n}\Func0(\varf0)$ is much more robust and allows us to apply this algorithm much more broadly.
-The penalty for this flexibility is a more complicated analysis, each time the sub-space changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.
-
-\subsubsection{Convergence bound with milestones}
-In standard FISTA, the right-hand side of \eqref{eq:ca: FISTA inequality} is a constant.
-The following lemma minimises the growth of the `constant' as a function of $N$ by partially telescoping the sum on the right-hand side.
-\begin{lemma}\label{thm:ca: mini exponential FISTA convergence}
-	\Copy{thm:ca: mini exponential FISTA convergence}{
-		Let $\varf0_n$, $\varf1_n$ be generated by \Cref{alg:ca: refining FISTA}, $(n_k\in\F N)_{k=0}^\infty$ be a monotone increasing sequence, and define
+In this section we will simply assume that such sequences exist and in \Cref{sec: general examples} we will give some more general examples.
+
+\begin{lemma}\label{thm: mini exponential FISTA convergence}
+	\Copy{thm: mini exponential FISTA convergence}{
+		Let $\varf0_n$, $\varf1_n$ be generated by \Cref{alg: refining FISTA}, $(n_k\in\F N)_{k=0}^\infty$ be a monotone increasing sequence, and define
 		$$\tilde{\spcf0}^k \coloneqq \spcf0^{n_k}, \qquad \tilde{\varf2}_k \in \argmin_{\varf0\in\tilde{\spcf0}^k} \Func0(\varf0).$$
@@
 \end{lemma}
-The introduction of $n_k$ has greatly simplified the expression of \Cref{thm:ca: mini FISTA convergence}.
-On the right-hand side, we now only consider $\Func0_0$ evaluated on the sequence $\tilde{\varf2}_k$ and there are only $K$ non-zero inner-product terms remaining.
+\noindent The proof is given in \cref{app:thm: mini exponential FISTA convergence}.
+The introduction of $n_k$ has greatly compressed the expression of \Cref{thm: mini FISTA convergence}.
+On the right-hand side, we now only consider $\Func0_0$ evaluated on the sequence $\tilde{\varf2}_k$ and there are $K$ elements to the sum rather than $N$.
 
 \subsection{Refinement without overfitting}
-The result of \Cref{thm:ca: mini exponential FISTA convergence} is still optimal in the sense that it reduces to \eqref{eq:ca: classical FISTA} when $\spcf0^n=\spcf0$, however, now we would like to achieve the equivalent rate (up to a constant factor) including refinement.
-This can be likened to the idea of overfitting to the discretisation.
-It is only efficient to optimise the discrete energy while the discrete gap $\Func0(\varf0_n)-\Func0(\tilde{\varf2}_k)$ is comparable to the continuous gap $\Func0(\varf0_n)-\Func0(\varf0^*)$.
-
-This is achieved by two assumptions, first we use the structure of \Cref{def:ca: exp subspaces} to quantify the properties of the refinement, then we force $K$ to scale with $\log(N)$ to slow the growth of the right hand side.
-This is summarised in the following lemma.
-
-\begin{lemma}\label{thm:ca: sufficiently fast}
-	\Copy{thm:ca: sufficiently fast}{
-		Suppose $\spcf0^n, \varf0_n, \varf1_n$ and $n_k$ satisfy the conditions of \Cref{thm:ca: mini exponential FISTA convergence} and $\{\tilde{\spcf0}^k\}$ forms an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$.
+The aim of \cref{step: step 4 sufficiently fast} is to show that $n$ iterations of \cref{alg: refining FISTA} is no slower (up to a constant factor) than $n$ iterations of classical FISTA on the space $\spcf0^n$.
+In other words, we would like to ensure that
+\begin{equation}
+	\Func0(\varf0_n) - \min_{\varf0\in\spcf0^n}\Func0(\varf0) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^n}\Func0(\varf0)}^2}{n^2}
+\end{equation}
+uniformly in $n$.
+If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of subspaces.
+This can be interpreted as an overfitting to the discretisation of $\Func0|_{\spcf0^n}$ rather than the desired function $\Func0|_{\spcf0}$.
+Combining the assumptions given by \Cref{def: exp subspaces} and the result of \cref{thm: mini exponential FISTA convergence}, the following lemma proves the convergence of \cref{alg: refining FISTA} provided that the refinement times $n_k$ are sufficiently small (i.e.
+$\spcf0^n$ grows sufficiently quickly).
+
+\begin{lemma}\label{thm: sufficiently fast}
+	\Copy{thm: sufficiently fast}{
+		Suppose $\spcf0^n, \varf0_n, \varf1_n$ and $n_k$ satisfy the conditions of \Cref{thm: mini exponential FISTA convergence} and $\{\tilde{\spcf0}^k\}$ forms an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$.
 		If either:
@@
 
-We make two observations of the optimality of \Cref{thm:ca: sufficiently fast}:
+\noindent The proof is given in \cref{app:thm: sufficiently fast}. We make two observations of the optimality of \Cref{thm: sufficiently fast}:
 \begin{itemize}
 	\item The convergence guarantee for $N$ iterations of classical FISTA in the space $\spcf0^N$ is 
-	$$ \Func0_0(\varf0_N) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\Func0(\varf0)}^2}{N^2} + \min_{\varf0\in\spcf0^N}\Func0(\varf0) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} + \vars3_{\Func0}^{-K}.$$
-	This is equivalent to \Cref{thm:ca: sufficiently fast} under the conditions on $n_k$.
+	$$ \Func0_0(\varf0_N) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\Func0(\varf0)}^2}{N^2} + \min_{\varf0\in\spcf0^N}\Func0_0(\varf0) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} + \vars3_{\Func0}^{-K}.$$
+	This is equivalent to \Cref{thm: sufficiently fast} under the conditions on $n_k$.
 	\item If $\spcf0$ is finite dimensional then the $\vars3_{\Varf0}=1$ is almost trivially satisfied.
@@
 
-\subsubsection{Convergence rate}
-At the end of \Cref{step:ca: step 3 sufficiently fast} we have shown that $\Func0(\varf0_n)$ converges at a rate depending on $k$ and $n$ so long as $k$ grows sufficiently quickly.
+\subsection{Convergence rate}
+In \Cref{thm: sufficiently fast} we show that $\Func0(\varf0_n)$ converges at a rate depending on $k$ and $n$ so long as $k$ grows sufficiently quickly.
 On the other hand, as $k$ grows, the rate becomes worse and so we need to also put a lower limit on the growth of $n_k$.
-The following lemma computes the global convergence rate of $\Func0(\varf0_n)$ when $k$ grows at the minimum rate which is consistent with \Cref{thm:ca: sufficiently fast}.
-
-As a special case, note that if $\vars3_{\Varf0}=1$ then \Cref{thm:ca: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate.
-This is in fact a special case of \cite{Aujol2015}.
+The following lemma completes \cref{step: step 5 sufficiently slow} by computing the global convergence rate of $\Func0_0(\varf0_n)$ when $k$ grows at the minimum rate which is consistent with \Cref{thm: sufficiently fast}.
+
+As a special case, note that if $\vars3_{\Varf0}=1$ then \Cref{thm: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate.
+This is in fact a special case of \citep{Aujol2015}.
 If $\varf0^*\in\F H$ then it is not possible to refine `too quickly' and the following lemma is not needed.
 
-\begin{lemma}\label{thm:ca: sufficiently slow}
-	\Copy{thm:ca: sufficiently slow}{
+\begin{lemma}\label{thm: sufficiently slow}
+	\Copy{thm: sufficiently slow}{
 		Suppose $\varf0_n$ and $n_k$ are sequences satisfying 
@@
 \end{lemma}
+\noindent The proof is given in \cref{app:thm: sufficiently slow}.
 
 \subsubsection{FISTA convergence with a priori discretisation}
-We can summarise \Cref{thm:ca: mini exponential FISTA convergence,thm:ca: sufficiently fast,thm:ca: sufficiently slow} into a single FISTA iteration.
-The following theorem states the convergence guarantees when $\spcf0^n$ and $n_k$ are chosen a priori.
-\begin{theorem}\label{thm:ca: exponential FISTA convergence}
-	\Copy{thm:ca: exponential FISTA convergence}{
+We can summarise \Cref{thm: mini exponential FISTA convergence,thm: sufficiently fast,thm: sufficiently slow} into a single theorem stating the convergence guarantees when $\spcf0^n$ and $n_k$ are chosen a priori.
+\begin{theorem}\label{thm: exponential FISTA convergence}
+	\Copy{thm: exponential FISTA convergence}{
 		Let $\{\tilde{\spcf0}^k\st k\in\F N\}$ be an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$ and choose any $\spcf0^n$ such that 
-		$$ \tilde{\spcf0}^k = \spcf0^{n_k}, \qquad \tilde{\varf2}_k \in \spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
-		for all $k\in\F N$. Compute $\varf0_n$, $\varf1_n$ by \Cref{alg:ca: refining FISTA} and choose $\tilde{\varf2}_k \in \argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$.
+		$$ \tilde{\spcf0}^k = \spcf0^{n_k}, \qquad \tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
+		for all $k\in\F N$. Compute $\varf0_n$, $\varf1_n$ by \Cref{alg: refining FISTA}.
 
@@
 \end{theorem}
-This theorem is very easy to implement and requires very little knowledge of how to estimate $\Func0_0(\varf0_n)$.
+\noindent This theorem is very easy to implement and requires very little knowledge of how to estimate $\Func0_0(\varf0_n)$.
 So long as $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be computed analytically, choosing $\tilde{\spcf0}^k$ to be uniform discretisations and $\tilde{\spcf0}^k = \spcf0^{n_k}=\ldots= \spcf0^{n_{k+1}-1}$ will give the stated convergence rate.
@@
 \subsubsection{FISTA convergence with adaptivity}
-\Cref{thm:ca: sufficiently fast} gives a sufficient condition for converging at the rate $O(N^{2(\epsilon-1)})$ but it is not necessary and in fact limits the potential convergence rate.
-To see this, if $\vars3_{\Func0}$ is a sharp estimate of $\Func0$, note that
-$$\Func0_0(\varf0_N) \geq \min_{\varf0\in\spcf0^N}\Func0_0(\varf0) \simeq \vars3_{\Func0}^{-K} \simeq\frac{\vars3_{\Varf0}^{2K}}{N^2} \simeq N^{2(\epsilon-1)}.$$
-To go beyond this rate (for example the linear convergence which will be seen in \Cref{sec:ca: wavelet examples}) we need to consider choosing $n_k$ adaptively.
-
-While \Cref{thm:ca: exponential FISTA convergence} also allows for spatial adaptivity, we will make further comment here as it links strongly with the choice of $n_k$.
-Suppose $\{\tilde{\spcf0}^k\st k\in\F N\}$ is an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$.
-To ensure that $\{\spcf0^{n_k}\st k\in\F N\}$ also satisfies the condition, it is sufficient to verify two properties:
-$$ \varf0^{n_K-1}\in\spcf0^{n_K}\subset \bigcup_{k=0}^K\tilde{\spcf0}^k \qquad\text{and}\qquad \Func0_0(\varf0^{n_K-1}) \lesssim \vars3_{\Func0}^{-K}.$$
-The subspace inclusion guarantees the condition for $\vars3_{\Varf0}$ and $\Func0_0(\tilde{\varf2}_K) = \min_{\varf0\in\spcf0^{n_K}}\Func0_0(\varf0) \leq \Func0_0(\varf0_{n_K-1})$ confirms the condition for $\vars3_{\Func0}$.
-
-For both adaptive choice of $n_k$ and $\spcf0^n$, accurate estimation of $\Func0_0(\varf0_n)$ is key.
-The idea of the following theorem is that we combine estimates of $\Func0_0(\varf0_n)$ with a `backstop' condition; `small' refinements can happen at any time and `big' refinements should happen as soon as $\Func0_0(\varf0_n)\lesssim \vars3_{\Func0}^{-k}$ for the appropriate $k\in\F N$.
-
-Without any way to estimate $\Func0_0(\varf0_n)$, we must rely on \Cref{thm:ca: sufficiently fast} for a naive a priori bound.
-If $\Func0_0(\varf0_n)$ can be computed exactly then we do not need to enforce $n_k^2\lesssim \vars3_{\Func0}^k\vars3_{\Varf0}^{2k}$ at all; it is implicitly guaranteed.
-For any intermediate case, we should combine estimates and choose the best one.
-This is summarised by \Cref{thm:ca: stronger exponential FISTA convergence}.
-
-\begin{theorem}\label{thm:ca: stronger exponential FISTA convergence}
-	\Copy{thm:ca: stronger exponential FISTA convergence}{
+There are two properties of the sequence $(\spcf0^n)_0^\infty$ which we may wish to decide adaptively: the refinement times $n_k$ and the exact spaces $\{\spcf0^n \st n_k\leq n<n_{k+1}\}$.
+We will refer to these as time and spatial adaptivity respectively.
+
+\Cref{thm: sufficiently fast} gives a sufficient condition on $n_k$ for converging at the rate $O(N^{2(\epsilon-1)})$ but it is not necessary. Indeed for $n\leq n_k$ the result shows 
+$$\Func0_0(\varf0_n) \geq \min_{\varf0\in\spcf0^n}\Func0_0(\varf0) = O(\vars3_{\Func0}^{-k}) = O(n^{2(\epsilon-1)})$$
+which suggests that to converge faster than $n^{2(\epsilon-1)}$ requires choosing smaller $n_k$.
+As an example, in \Cref{sec: wavelet examples} we will see \cref{alg: refining FISTA} can converge at a linear rate, although this is not possible without adaptive refinement times.
+On the other hand, choice of spatial adaptivity has no impact on rate but can impact computational efficiency.
+It will be permitted to use greedy discretisation techniques so long as each collection $\{\spcf0^n \st n_k\leq n<n_{k+1}\}$ satisfies a monotonicity condition.
+
+While \Cref{thm: exponential FISTA convergence} also allows for spatial adaptivity, we will simplify the requirements to a form which seems more practical for implementation and also allows for time adaptivity.
+We make the assumption that the choice of $n_k$ depends only on the value $\Func0(u^{n_k-1})$ and therefore make $u^{n_k-1}$ the root of our requirements.
+\cref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\Func0_0(\varf0^{n_k-1})\lesssim \vars3_{\Func0}^{-k}$.
+However, the value of $\Func0_0$ may be hard to estimate and so we introduce a `backstop' condition which ensures that convergence is no slower than the rate given by \Cref{thm: exponential FISTA convergence}.
+The only constraint on spatial adaptivity is the piecewise monotone inclusion and that $\spcf0^{n_k} \ni u^{n_k-1}$.
+This is confirmed by the following theorem.
+\begin{theorem}\label{thm: stronger exponential FISTA convergence}
+	\Copy{thm: stronger exponential FISTA convergence}{
 		Let $\{\spcf0^n\subset\F H\cap\spcf0\st n\in\F N\}$ be a sequence of subspaces and $n_k\in\F N$ a monotone increasing sequence such that
@@
 		for all $k\in\F N$.
-		Compute $\varf0_n$, $\varf1_n$ by \Cref{alg:ca: refining FISTA}.
+		Compute $\varf0_n$, $\varf1_n$ by \Cref{alg: refining FISTA}.
 
@@
 \end{theorem}
-This theorem can be directly compared with \Cref{thm:ca: exponential FISTA convergence}.
-In particular, we note that the convergence rate is the same in both theorems but the price for better adaptivity is a slightly weaker stability guarantee (i.e.
+\noindent The proof is given in \cref{app:thm: stronger exponential FISTA convergence}.
+If we directly compare \Cref{thm: exponential FISTA convergence,thm: stronger exponential FISTA convergence}, we note that the convergence rate is the same in both theorems but the price for better adaptivity is a slightly weaker stability guarantee (i.e.
 the addition of the min on the left-hand side).
-
-In a practical sense, \Cref{thm:ca: exponential FISTA convergence} provides a worst case convergence rate but if the observed convergence is faster then the refinement should also be accelerated.
-The issue arises if $\Func0$ is a function which is `easy' to minimise for small $n$ ($n_k$ is small) but `hard' for large $n$ (\Cref{thm:ca: sufficiently fast} becomes sharp).
-If this behaviour is made to oscillate, then the convergence will also be oscillatory although still optimal in the sense of \Cref{thm:ca: stronger exponential FISTA convergence}.
-
-\begin{remark}
-	The convergence guarantee of \Cref{thm:ca: stronger exponential FISTA convergence} can be strengthened back to the monotone statement $\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\epsilon)}}$ whenever $$\tilde{\varf2}_k \in \bigcap_{n=n_k}^N\spcf0^n$$
-	for the appropriate $k\in\F N$.
-This shows that the non-monotone convergence guarantee is somehow related to non-monotonicity of the discretisation, if $\spcf0^n\subset\spcf0^{n+1}$ for all $n\in\F N$ then the above condition is always satisfied.
-It is currently unclear how to make this statement more precise without an excessive number of constraints on the choice of $\spcf0^n$.
-\end{remark}
-
-\Cref{thm:ca: stronger exponential FISTA convergence} relies on estimation of when $\Func0_0(\varf0_n) \lesssim \vars3_{\Func0}^{-k}$ although there are many equivalent characterisations for this.
-Some are described in the following lemma.
-
-\begin{lemma}\label{thm:ca: practical refinement criteria}
-	\Copy{thm:ca: practical refinement criteria}{
+In \Cref{thm: exponential FISTA convergence}, as in the original FISTA algorithm, the sequence $\Func0(\varf0_n)$ is not monotone but the magnitude of oscillation is guaranteed to decay in time.
+This behaviour is boundedness is lost in \cref{thm: stronger exponential FISTA convergence} although it still holds on a subsequence.
+Although we do not prove it here, it can be shown that the stronger condition
+\begin{equation}
+	\tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}\cap\ldots\cap \spcf0^N
+\end{equation}
+is sufficient to restore the stronger guarantee on $\Func0_0(\varf0_n)$. Again, monotonicity of $\spcf0^n$ corresponds with improved stability of \cref{alg: refining FISTA}.
+
+To enable more practical implementation of \Cref{thm: stronger exponential FISTA convergence}, the following lemma describes several refinement time strategies which provide sufficient condition for $\Func0_0(\varf0_n) \lesssim \vars3_{\Func0}^{-k}$.
+\begin{lemma}\label{thm: practical refinement criteria}
+	\Copy{thm: practical refinement criteria}{
 		Let $\{\tilde{\spcf0}^k\st k\in\F N\}$ be a sequence of subspaces with some points $\varf0_k\in \tilde{\spcf0}^k$ and $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$.
@@
 
-The refinement criteria described by \Cref{thm:ca: practical refinement criteria} can be split into two groups.
-Cases (1), (3), and (4) justify that $\tilde{\spcf0}^k$ is good enough whenever $\varf0_k$ (or $\varf0_{n_k-1}$ in \Cref{thm:ca: stronger exponential FISTA convergence}) is contained in $\tilde{\spcf0}^k$.
-In cases (2) and (5), $\varf0_k$ is good enough to choose $n_k$ but $\varf0_k\in\tilde{\spcf0}^k$ is not sufficient to validate $\tilde{\spcf0}^k$ on its own.
+\noindent The proof is given in \cref{app:thm: practical refinement criteria}.
+The refinement criteria described by \Cref{thm: practical refinement criteria} can be split into two groups.
+Cases (1), (3), and (4) justify that any choice of $\tilde{\spcf0}^k\ni\varf0_k$ (or $\varf0_{n_k-1}$ in \Cref{thm: stronger exponential FISTA convergence}) satisfies the required conditions.
+In cases (2) and (5), $\varf0_k$ is sufficient to choose the refinement time $n_k$ but not the subspace $\tilde{\spcf0}^k$.
+In these cases one could choose $\tilde{\spcf0}^k$ to be a uniform discretisation with apriori estimates, for example.
 
 Another splitting of the criteria is into gap and gradient computations.
-Typically, gradient norms (in (4) and (5)) should be easier to estimate than gaps because they only require local knowledge rather than global, i.e.
+Typically, gradient norms (in (4) and (5)) should be easier to estimate than function gaps because they only require local knowledge rather than global, i.e.
 $\partial\Func0(\varf0_n)$ rather than an estimate of $\Func0(\varf0^*)$.
@@
 
-\section{General examples}\label{sec:ca: general examples}
-In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, \Cref{alg:ca: refining FISTA} is much more broadly applicable.
-The aim of this section is to justify this fact and demonstrate that the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be easily computed in many examples.
-
-The trivial source of examples is any problem where $\spcf0$ is finite dimensional.
-In this case \Cref{thm:ca: exponential FISTA convergence,thm:ca: stronger exponential FISTA convergence} both achieve the standard FISTA rate, almost by default.
-The conditions on $\{\spcf0^n\st n\in\F N\}$ prevent `oscillations' in the discretisation and therefore \Cref{alg:ca: refining FISTA} becomes standard FISTA after a finite number of iterations (i.e.
-$n_k=\infty$ for some $k$).
-
-For less trivial examples, we explore the use of finite element bases for discretisation when $\F H = L^2(\Domain)$ for some compact $\Domain\subset\R^d$.
-Informally, we wish to generate spaces $\{\tilde{\spcf0}^k\st k\in\F N\}$ with the properties:
-\begin{itemize}
-	\item each $\tilde{\spcf0}^k$ is a finite dimensional subspace of $L^\infty$, 
-	\item each $\tilde{\spcf0}^k$ can be spanned by shifting and rescaling elements of $\tilde{\spcf0}^0$,
-	\item and $\tilde{\spcf0}^k$ are known to have good approximation rates in $\Norm\cdot$.
-\end{itemize}
-The first point makes it easy to compute the analytical equivalence between $\norm\cdot$ and $\Norm\cdot$, the second point dictates the scaling with respect to $k$, the third point links back to optimisation.
-Our formal definitions for finite element spaces are given below.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage {\Huge\todo{I don't know if this section should remain}}
+\section{General examples}\label{sec: general examples}
+In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, \Cref{alg: refining FISTA} is much more broadly applicable.
+The aim of this section is to justify this claim by demonstrating that the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be easily computed in many examples.
+
+The cases where $\spcf0$ is finite or countable dimensional are quite straight forward.
+If the total number of refinements is finite (i.e.
+$\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$) then $\vars3_{\Varf0} = 1$.
+This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in \cref{sec: Lasso definition}.
+The examples we will consider here are where $\F H = L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$, and $\{\tilde{\spcf0}^n\st n\in\F N\}$ are finite dimensional finite-element--like spaces.
+We will now clarify exactly what is meant by these properties and then demonstrate that they are sufficient to find simple formulae for the values $\vars3_{\Varf0}$ and $\vars3_{\Func0}$.
+
 \begin{definition}
 	Suppose $\spcf0\subset L^p(\Domain)$ for some compact domain $\Domain\subset\R^d$. We say that $\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$ is a \emph{mesh} if 
-	$$\domain_i^k\subset\Domain, \qquad |\domain_i^k\cap\domain^k_j| = 0$$
+	$$\domain_i^k\subset\Domain \qquad\text{and} \qquad |\domain_i^k\cap\domain^k_j| = 0$$
 	for all $i$ and $j$.
@@
 
-	We say that a sequence of finite element sub-spaces $\tilde{\spcf0}^k\subset \spcf0\cap \F H$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\spcf0}^0$ such that for any $\varf0_i^k\in\tilde{\spcf0}^k$ with $\supp(\varf0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
+	We say that a sequence of finite element sub-spaces $(\tilde{\spcf0}^k)_{k=0}^\infty$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\spcf0}^0\cap L^\infty(\Domain)$ such that for any $\varf0_i^k\in\tilde{\spcf0}^k$ with $\supp(\varf0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
 	$$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \varf0_i^k(\vvarx0) = \sum_{j=1}^N\vars2_je_j(\vars0 \vvarx0+\vvars1) \quad \text{ for a.e.
@@
 	$$\min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*} \lesssim_{\varf0^*} \meshsize^{kp}.$$
-	We allow the implicit constant to have any dependence on $\varf0^*$ so long as it is finite. In the case of Sobolev spaces, we would expect an inequality of the form
-	$\min_{\varf2\in\tilde{\spcf0}^k}\norm{\varf2-\varf0^*}_{W^{0,q}} \lesssim \meshsize^{kp}\norm{\varf0^*}_{W^{p,q}}$ \cite{Strang1972}.
+	We allow the implicit constant to have any dependence on $\varf0^*$ so long as it is finite. For example, in the case of Sobolev spaces we would expect an inequality of the form
+	$\min_{\varf2\in\tilde{\spcf0}^k}\norm{\varf2-\varf0^*}_{W^{0,q}} \lesssim \meshsize^{kp}\norm{\varf0^*}_{W^{p,q}}$ \citep{Strang1972}.
 \end{definition}
@@
 Wavelets almost satisfy this definition but not the support condition, each space contains every scale of wavelet.
-Similarly, a Fourier basis does satisfy nice scaling properties but each basis vector has global support.
+\todo{Is that true?
+If the wavelet has compact support then it should admit a basis with disjoint support?} Similarly, a Fourier basis does satisfy the scaling properties but each basis vector has global support.
 Both of these exceptions are important and could be accounted for with further analysis but we focus on the more standard finite element case.
-The following theorem shows that all finite element spaces achieve the same basic rates of convergence in \Cref{alg:ca: refining FISTA}, depending on the particular properties of $\Norm\cdot$ and $\Func0$.
-\begin{theorem}\label{thm:ca: generic a_U and a_E}
+The following theorem shows that all finite element spaces achieve the same basic rates of convergence in \Cref{alg: refining FISTA}, depending on the particular properties of $\Norm\cdot$ and $\Func0$.
+\begin{theorem}\label{thm: generic a_U and a_E}
 	Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
@@
 		\vars3_{\Varf0} &\leq \splitln{1}{q\geq 2}{\sqrt{\meshsize^{-d}}}{q<2},
-		\\\vars3_{\Func0} &\geq \begin{cases}
+		& \vars3_{\Func0} &\geq \begin{cases}
 			\meshsize^{-p} & \Func0 \text{ is $\Norm\cdot$-Lipschitz at }\varf0^*
@@
 \end{theorem}
-The proof of this theorem is in \Cref{app:ca: generic a_U and a_E}.
-The main take-home for this theorem is that the computation of $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ is typically very simple and obvious given a particular choice of $\Norm\cdot$ and $\Func0$.
+The proof of this theorem is in \Cref{app: generic a_U and a_E}.
+The main take-home for this theorem is that the computation of $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\Func0$.
 The only non-trivial case is when $\func2$ is not smooth enough to estimate directly.
@@
 
-\section{Lasso minimisation}\label{sec:ca: Lasso definition}
-We now return to the concrete example of Lasso which will be used for numerical results in \Cref{sec:ca: numerics}.
-We consider three forms of Lasso which will be referred to as continuous, countable, and discete Lasso depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
+\newpage 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Lasso minimisation}\label{sec: Lasso definition}
+We now return to the concrete example of Lasso which will be used for numerical results in \Cref{sec: numerics}.
+We consider three forms of Lasso which will be referred to as continuous, countable, and discrete Lasso depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
 In each case, the energy can be written as
-\begin{equation}\label{eq:ca: Lasso energy}
+\begin{equation}\label{eq: Lasso energy}
 	\Func0(\varf0) = \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu\Norm{\varf0}
@@
 
-The aim of this section is to develop all of the necessary tools for implementing \Cref{alg:ca: refining FISTA} on the energy \eqref{eq:ca: Lasso energy} through either \Cref{thm:ca: exponential FISTA convergence} or \Cref{thm:ca: stronger exponential FISTA convergence}.
+The aim of this section is to develop all of the necessary tools for implementing \Cref{alg: refining FISTA} on the energy \eqref{eq: Lasso energy} using the convergence guarantees of either \Cref{thm: exponential FISTA convergence} or \Cref{thm: stronger exponential FISTA convergence}.
 This includes computing the rates $\vars3_{\Varf0}$ and $\vars3_{\Func0}$, estimating the continuous gap $\Func0_0(\varf0_n)$, and developing an efficient refinement choice for $\spcf0^n$.
 
-\subsection{Continuous case}\label{sec:ca: continuous lasso rate}
+\subsection{Continuous case}\label{sec: continuous lasso rate}
 We start by estimating rates in the case $\spcf0=\C M(\Domain)$ where $\Domain =[0,1]^d$.
@@
 
-We would like to apply \Cref{thm:ca: generic a_U and a_E} to compute the rate of convergence although $\norm\cdot_1$ is too strong a metric and results in order $p=0$.
+Application of \Cref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although although $\norm\cdot_1$ is too strong a metric and results in $\vars3_{\Func0}=2^0$.
 This can be seen because for any $\varf0\in L^1(\Domain^d)$,
-$$\norm{\varf0-\delta_0}_1 = \sup_{\vard0\in C(\Domain^d), \norm{\vard0}_\infty\leq 1} \IP{\vard0}{\varf0-\delta_0} = \norm{\varf0}_1+\norm{\delta_0}_1 \geq 1.$$ 
-The result of \Cref{thm:ca: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ (whether or not $p=0$) and choosing $\Norm\cdot$ to be an appropriate negative Sobolev norm or transport metric gives $p=1$ and $\vars3_{\Func0} = 2^1$.
-We will work through this second statement explicitly to demonstrate the additional requirements on $\A$.
-
-For any $\varf2\in\tilde{\spcf0}^k$ such that $\norm{\varf2}_1\leq \norm{\varf0^*}_1$, we have
-\begin{align*}
+\begin{equation}
+	\norm{\varf0-\delta_0}_1 = \sup_{\vard0\in C(\Domain^d), \norm{\vard0}_\infty\leq 1} \IP{\vard0}{\varf0-\delta_0} = \norm{\varf0}_1+\norm{\delta_0}_1 \geq 1.
+\end{equation}
+To improve our estimate of $\vars3_{\Func0}$ requires additional assumptions on $\A$. For any $\varf2\in\tilde{\spcf0}^k$ such that $\norm{\varf2}_1\leq \norm{\varf0^*}_1$, we compute
+\begin{align}
 	\Func0(\varf2)-\Func0(\varf0^*) &=  \tfrac12\norm{\A\varf2-\vdata0}^2 - \tfrac12\norm{\A\varf0^*-\vdata0}^2 + \mu\left(\Norm{\varf2}-\Norm{\varf0^*}\right)
@@
 	\\&\leq \sqrt{2\Func0(\varf2)}\norm{\A(\varf2-\varf0^*)}.
-\end{align*}
-For any bounded linear extension to the orthogonal projection $\tilde\Pi_k\colon\spcf0\to\tilde{\spcf0}^k$, choose $\varf2 = \tilde\Pi_k\varf0^*$, then we get
+\end{align}
+Choosing $\varf2 = \tilde\Pi_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde\Pi_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
 $$\Func0(\varf2)-\Func0(\varf0^*) \lesssim \norm{\A(\tilde\Pi_k\varf0^*-\varf0^*)} \leq \norm{(\tilde\Pi_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$$
-Expanding this operator norm further,
-\begin{multline*}
+Expanding the operator norm further,
+\begin{multline}
 	\norm{(\tilde\Pi_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde\Pi_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}}
 	\\= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}
-\end{multline*}
+\end{multline}
 where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.
 
-This computation confirms two things, firstly that the scaling constant is indeed $\vars3_{\Func0} = 2$, and secondly that the required smoothness to achieve a good rate with \Cref{alg:ca: refining FISTA} is that $\A^*\colon\R^m\to C^1(\Domain)$ is a bounded operator.
-This accounts for the fact that $\C M(\Domain)$ is such a large space containing distributions.
-In \Cref{sec:ca: smoothing operators} we will show two practical examples were this (semi)norm is accurately computable.
-
-Inserting the computed rates into \Cref{thm:ca: exponential FISTA convergence} or \Cref{thm:ca: stronger exponential FISTA convergence} gives the guaranteed convergence rate
-\begin{equation}\label{eq:ca: Lasso energy rate}
-	\epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} = \frac{d}{1+d} \quad \implies \quad \Func0_0(\varf0_N) \lesssim N^{-2(1-\epsilon)} = N^{-\frac{2}{1+d}}.
-\end{equation}
-This energy rate also corresponds to a resolution rate, on iteration $N$ with $N^2\sim (\vars3_{\Func0}\vars3_{\Varf0}^2)^k$ we expect the resolution to be
-\begin{equation}\label{eq:ca: Lasso resolution rate}
-	\meshsize = 2^{-k} = \left(\vars3_{\Func0}\vars3_{\Varf0}^2\right)^{\frac{k}{1+d}} \sim N^{-\frac{2}{1+d}}.
+This computation confirms two things, firstly that the scaling constant is indeed $\vars3_{\Func0} = 2$, and secondly that the required smoothness to achieve a good rate with \Cref{alg: refining FISTA} is that $\A^*\colon\R^m\to C^1(\Domain)$ is a bounded operator.
+This accounts for using the weaker topology of $\C M(\Domain)$ rather than $L^1(\Domain)$.
+In \Cref{sec: smoothing operators} we will show two practical examples were this (semi)norm is accurately computable.
+
+Inserting the computed rates into \Cref{thm: exponential FISTA convergence} or \Cref{thm: stronger exponential FISTA convergence} gives the guaranteed convergence rate
+\begin{equation}\label{eq: Lasso energy rate}
+	\epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} = \frac{d}{1+d} \quad \implies \quad \Func0_0(\varf0_n) \lesssim n^{-2(1-\epsilon)} = n^{-\frac{2}{1+d}}.
+\end{equation}
+This rate can be used to infer the required resolution at each iteration, in particular on iteration $n$ with $n^2\sim (\vars3_{\Func0}\vars3_{\Varf0}^2)^k$ we expect the resolution to be
+\begin{equation}\label{eq: Lasso resolution rate}
+	2^{-k} = \left(\vars3_{\Func0}\vars3_{\Varf0}^2\right)^{\frac{k}{1+d}} \sim n^{-\frac{2}{1+d}}.
 \end{equation}
@@
 independent of $\vars3_{\Func0}$ or any additional properties of $\A$.
-The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of \Cref{thm:ca: exponential FISTA convergence,thm:ca: stronger exponential FISTA convergence} hold trivially.
-
-\subsection{Refinement metrics}\label{sec:ca: Lasso gap and gradient}
-\Cref{thm:ca: practical refinement criteria} shows that adaptive refinement can be performed based on estimates of the function gap or the gradient.
+The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of \Cref{thm: exponential FISTA convergence,thm: stronger exponential FISTA convergence} hold trivially.
+
+\subsection{Refinement metrics}\label{sec: Lasso gap and gradient}
+\Cref{thm: practical refinement criteria} shows that adaptive refinement can be performed based on estimates of the function gap or the gradient.
 In this subsection we provide estimates for these values which can be easily computed.
 
-\subsubsection{Bounds for discretised functionals}\label{sec:ca: bound discrete}
+\subsubsection{Bounds for discretised functionals}\label{sec: bound discrete}
 We start by computing estimates for discretised Lasso.
 This covers the cases when either continuous/countable Lasso is projected onto $\spcf0^n$, or $\spcf0$ is finite dimensional.
-For notation we will use the continuous case.
-To recover the other cases, just replace continuous indexing ($\varf0(\vvarx0)$) with discrete ($\varf0_i$).
-
-Let $\Pi_n\colon\spcf0\to\spcf0^n$ denote the orthogonal projection (in fact the unique bounded extension).
-For Lasso, discretising the function $\Func0$ ($\varf0\mapsto\Func0(\Pi_n\varf0)$) is equivalent to replacing $\varf0$ with $\Pi_n\varf0$, and $\A^*$ with $\Pi_n\A^*$.
+For notation we will use the continuous case, to recover the other cases just replace continuous indexing with discrete (i.e.
+$\varf0(\vvarx0) \leadsto \varf0_i$).
+
+Let $\Pi_n\colon\spcf0\to\spcf0^n$ denote an orthogonal projection (uniquely determined on $\C H$).
+For Lasso, the discretised function $\varf0\mapsto\Func0(\Pi_n\varf0)$ is equivalent to replacing $\varf0$ with $\Pi_n\varf0$, and $\A^*$ with $\Pi_n\A^*$.
 
 \paragraph{Discrete gradient}
-We can use this formulation to compute the discrete sub-derivative at $\varf0_n\in\spcf0^n$:
-\begin{align*}
+We can use $\Pi_n$ to compute the discrete sub-derivative at $\varf0_n\in\spcf0^n$:
+\begin{align}
 	\partial_n \Func0(\Pi_n\varf0_n)(\vvarx0) &= [\Pi_n\A^*(\A\varf0_n-\vdata0)](\vvarx0) + \begin{cases}
@@
 	\\&\eqqcolon [\Pi_n\A^*(\A\varf0_n-\vdata0)](\vvarx0) + \mu\Pi_n\sign(\varf0_n(\vvarx0))
-\end{align*}
+\end{align}
 where we define $\vart0+\mu[-1,1] = [\vart0-\mu,\vart0+\mu]$ for all $\vart0\in\R$, $\mu\geq0$.
 
-We need a metric to decide whether $\partial_n\Func0$ is small. As $\Norm\cdot = \norm\cdot_1$, the natural metric is $\Norm\cdot_* = \norm\cdot_\infty$ and so we get the estimate
-\begin{align*}
+As $\Norm\cdot = \norm\cdot_1$, the natural metric for $\partial_n\Func0$ is $\Norm\cdot_* = \norm\cdot_\infty$ which we can estimate
+\begin{align}
 	\Norm{\partial_n \Func0(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\min\left\{|\varf1| \st \varf1\in \Pi_n\A^*(\A\varf0_n-\vdata0)(\vvarx0) +  \mu\sign(\varf0_n(\vvarx0))\right\}
@@
 	\end{cases}
-\end{align*}
-which can be used in \Cref{thm:ca: practical refinement criteria}.
+\end{align}
+which can be used directly in \Cref{thm: practical refinement criteria}.
 
 \paragraph{Discrete gap}
-We now move on to the discrete gap, $\Func0(\varf0_n)-\min_{\varf0\in\spcf0^n}\Func0(\varf0)$. This can be computed with a dual representation, such as that used by \cite{Duval2017a},
-\begin{align*}
+We now move on to the discrete gap, $\Func0(\varf0_n)-\min_{\varf0\in\spcf0^n}\Func0(\varf0)$. This can be computed with a dual representation, such as that used by \citet{Duval2017a},
+\begin{align}
 	\min_{\varf0\in \spcf0^n} \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu\Norm{\varf0} &= \min_{\varf0\in\F H}\max_{\vvard0\in\R^m} \ip{(\A\Pi_n\varf0-\vdata0)}{ \vvard0} +\mu\Norm{\Pi_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
@@
 	\\&= -\min_{\vvard0\in\R^m} \underbrace{\tfrac12\norm{\vvard0}_{\ell^2}^2+\ip{\vdata0}{\vvard0}}_{\eqqcolon \Func0^*(\vvard0)}  + \chi(\Norm{\Pi_n\A^*\vvard0}_*\leq \mu).
-\end{align*}
+\end{align}
 In particular,
-$$\Func0(\varf0) - \min_{\varf0\in\spcf0^n}\Func0(\varf0) = \Func0(\varf0) + \min_{\Norm{\Pi_n\A^*\vvard0}_*\leq \mu} \Func0^*(\vvard0) \leq \Func0(\varf0) + \Func0^*(\vvard0)$$
-for any feasible $\vvard0\in\R^m$. Differentiating the saddle point with respect to $\vvard0$, if $\vvard0^*$ is the maximiser for $\varf0^*\in\argmin_{\varf0\in\spcf0^n}\Func0(\varf0)$ then
-$$ \vvard0^* = \A\varf0^*-\vdata0.$$
+\begin{equation}
+	\Func0(\varf0) - \min_{\varf0\in\spcf0^n}\Func0(\varf0) = \Func0(\varf0) + \min_{\vvard0\in\R^m\st \Norm{\Pi_n\A^*\vvard0}_*\leq \mu} \Func0^*(\vvard0) \leq \Func0(\varf0) + \Func0^*(\vvard0)
+\end{equation}
+for any feasible $\vvard0\in\R^m$. We further derive the criticality condition, if $(\varf0^*,\vvard0^*)$ is a saddle point, then
+\begin{equation}
+	\vvard0^* = \A\varf0^*-\vdata0.
+\end{equation}
 We remark briefly that it is more conventional to include the constraint in the definition of $\Func0^*$.
@@
 Given $\varf0_n\in \spcf0^n$, the optimality condition motivates a simple rule for choosing $\vvard0$:
-$$\vvard0_n\coloneqq \A\varf0_n - \vdata0, \qquad \Func0(\varf0)-\min_{\varf0'\in\spcf0^n}\Func0(\varf0') \leq \Func0(\varf0) +\min_{\vars2\geq 0}\left\{\Func0^*(\vars2\vvard0_n) \st \vars2 \Norm{\Pi_n\A^*\vvard0_n}_*\leq \mu\right\}$$
+\begin{equation}
+	\vvard0_n\coloneqq \A\varf0_n - \vdata0, \qquad \Func0(\varf0)-\min_{\varf0'\in\spcf0^n}\Func0(\varf0') \leq \Func0(\varf0) +\min_{\vars2\geq 0}\left\{\Func0^*(\vars2\vvard0_n) \st \vars2 \Norm{\Pi_n\A^*\vvard0_n}_*\leq \mu\right\}
+\end{equation}
 with optimal choice
-$$\vars2 =\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\Pi_n\A^*\vvard0_n}_*}\right)\right).$$
-To apply \Cref{alg:ca: refining FISTA}, we are assuming that both $\func1(\varf0_n) = \frac12\norm{\vvard0_n}_{\ell^2}^2$ and $\Pi_n\nabla\func1(\varf0_n) = \Pi_n\A^*\vvard0_n$ are easily computable, therefore $\vars2$ and $\Func0(\varf0_n) +\Func0^*(\vars2\vvard0_n)$ are also easy to compute.
+\begin{equation}
+	\vars2 =\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\Pi_n\A^*\vvard0_n}_*}\right)\right).
+\end{equation}
+To apply \Cref{alg: refining FISTA}, we are assuming that both $\func1(\varf0_n) = \frac12\norm{\vvard0_n}_{\ell^2}^2$ and $\Pi_n\nabla\func1(\varf0_n) = \Pi_n\A^*\vvard0_n$ are easily computable, therefore $\vars2$ and $\Func0(\varf0_n) +\Func0^*(\vars2\vvard0_n)$ are also easy to compute.
 
 \subsubsection{Bounds for countable functionals}
-Extending the results of \Cref{sec:ca: bound discrete} to $\spcf0=\ell^1(\R)$ is analytically very simple but relies heavily on the specific choice of $\A$.
-The computations of gradients and gaps carry straight over replacing $\Pi_n$ with $\id$ and adding the sets $J_n\subset\F N$ which define $\spcf0^n = \{\varf0\in\ell^1\st i\notin J_n\implies \varf0_i=0\}$.
+Extending the results of \Cref{sec: bound discrete} to $\spcf0=\ell^1(\R)$ is analytically very simple but relies heavily on the specific choice of $\A$.
+The computations of gradients and gaps carry straight over replacing $\Pi_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\spcf0^n = \{\varf0\in\ell^1\st i\notin J_n\implies \varf0_i=0\}$.
 In particular,
-\begin{align*}
+\begin{align}
 	\Norm{\partial\Func0(\varf0_n)}_* &= \max_{i\in\F N}\begin{cases}
@@
 	\\ \Func0_0(\varf0_n) &\leq \Func0(\varf0_n) + \Func0(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right)
-\end{align*}
+\end{align}
 where $\vvard0_n = \A\varf0_n-\vdata0\in\R^m$ is always exactly computable.
@@
 In the countable case, the sets $J_n$ give a clear partition into known/unknown values in these definitions.
-For $i\in J_n$ the computation is the same as in \Cref{sec:ca: bound discrete}, then for $i\notin J_n$ we know $[\varf0_n]_i=0$ which simplifies the remaining computations.
+For $i\in J_n$ the computation is the same as in \Cref{sec: bound discrete}, then for $i\notin J_n$ we know $[\varf0_n]_i=0$ which simplifies the remaining computations.
 This leads to:
-\begin{align*}
+\begin{align}
 	\Norm{\partial\Func0(\varf0_n)}_* &= \max\left(\max_{i\in J_n}|[\partial\Func0(\varf0_n)]_i|,\ \max_{i\notin J_n} |[\partial\Func0(\varf0_n)]_i|\right)
@@
 	\\ &= \max\left(\Norm{\Pi_n\A^*\vvard0_n}_*,\ \max_{i\notin J_n} |[\A^*\vvard0_n]_i|\right).
-\end{align*}
-Both estimates only rely on an upper bound of $\max_{i\notin J_n} |[\A^*\vvard0_n]_i|$. This must be computed on a per-example basis, one example is seen in \Cref{sec:ca: wavelet examples}.
-
-\subsubsection{Bounds for continuous functionals}\label{sec:ca: bound continuous}
-Finally, we extend the results of \Cref{sec:ca: bound discrete} to continuous Lasso. Similar to the countable case, the exact formulae can be written down immediately:
-\begin{align*}
+\end{align}
+Both estimates only rely on an upper bound of $\max_{i\notin J_n} |[\A^*\vvard0_n]_i|$. One example computing this value is seen in \Cref{sec: wavelet examples}.
+
+\subsubsection{Bounds for continuous functionals}\label{sec: bound continuous}
+Finally we extend the results of \Cref{sec: bound discrete} to continuous Lasso. Similar to the countable case, the exact formulae can be written down immediately:
+\begin{align}
 	\Norm{\partial\Func0(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\begin{cases}
@@
 	\\ \Func0_0(\varf0_n) &\leq \Func0(\varf0_n) + \Func0(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right).
-\end{align*}
+\end{align}
 If these quantities are not analytically tractable then we use the mesh $\F M^n$ corresponding to $\spcf0^n$ to decompose the bounds:
-\begin{align*}
+\begin{align}
 	\Norm{\partial \Func0(\varf0_n)}_* &= \max_{\domain_i^n\in\F M^n} \begin{cases}
@@
 	\\ \Norm{\A^*\vvard0_n}_* &= \max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}.
-\end{align*}
+\end{align}
 Now, both estimates rely on cell-wise supremum norms of $\A^*\vvard0_n$ which we assume is sufficiently smooth.
-We will use a cell-wise Taylor expansion to provide such an estimate which is both accurate and relatively tight.
+We will therefore use a cell-wise Taylor expansion to provide a simple and accurate estimate.
 For instance, let $\vvarx0_i$ be the midpoint of the square $\domain_i^n$, then
-$$\norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq |[\A^*\vvard0_n](\vvarx0_i)| + \frac{\op{diam}(\domain_i^n)}{2}|[\nabla\A^*\vvard0_n](\vvarx0_i)| + \frac{\op{diam}(\domain_i^n)^2}{8}|\A^*\vvard0_n|_{C^2}.$$
+\begin{equation}\label{eq: Taylor approximation}
+	\norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq |[\A^*\vvard0_n](\vvarx0_i)| + \frac{\op{diam}(\domain_i^n)}{2}|[\nabla\A^*\vvard0_n](\vvarx0_i)| + \frac{\op{diam}(\domain_i^n)^2}{8}|\A^*\vvard0_n|_{C^2}.
+\end{equation}
 In this work we chose a first order expansion because we are looking for extrema of $\A^*\vvard0_n$, i.e. we are most interested in the squares $\domain_i^n$ such that 
-$$|[\A^*\vvard0_n](\vvarx0_i)| \approx \mu, \qquad |[\nabla\A^*\vvard0_n](\vvarx0_i)| \approx 0, \qquad [\nabla^2\A^*\vvard0_n](\vvarx0_i) \preceq 0. $$
+\begin{equation}
+	|[\A^*\vvard0_n](\vvarx0_i)| \approx \mu, \qquad |[\nabla\A^*\vvard0_n](\vvarx0_i)| \approx 0, \qquad [\nabla^2\A^*\vvard0_n](\vvarx0_i) \preceq 0. 
+\end{equation}
 A zeroth order expansion would be optimally inefficient (approximating $|[\nabla\A^*\vvard0_n](\vvarx0_i)|$ with $|\A^*\vvard0_n|_{C^1}$) and a second order expansion would possibly be the most elegant but harder to implement.
@@
 The bounds presented here for continuous Lasso emphasise the twinned properties required for adaptive mesh optimisation.
-The mesh should be refined greedily to the structures of $\varf0^*$, but also must be sufficiently uniform to prove that $\varf0^*$ is the function we are approximating.
+The mesh should be refined greedily to the structures of $\varf0^*$, but also must be sufficiently uniform to provide a good estimate for $\Func0(\varf0^*)$.
 This is a classical exploitation/exploration trade-off; exploiting visible structure whilst searching for other structures which are not yet visible.
 
-\subsection{Support detection}\label{sec:ca: support detection}
-The main motivation for using Lasso in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\varf0^*$ is also provably close to the `true' support \cite{Duval2017a,Poon2018}.
+\subsection{Support detection}\label{sec: support detection}
+The main motivation for using Lasso in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\varf0^*$ is also provably close to the `true' support \citep{Duval2017a,Poon2018}.
 If $\varf0_n\approx \varf0^*$ in the appropriate sense, then we should also be able to quantify the statement $\op{supp}(\varf0_n)\approx\op{supp}(\varf0^*)$.
-This is the aim of this subsection.
-
-The work of \cite{Duval2017a,Poon2018} and many others characterise the support of $\varf0^*$ very precisely.
-In particular, the support is at most $m$ distinct points and (with continuous notation) are a subset of $\{ \vvarx0\in\Domain \st |\A^*\vvard0^*|(\vvarx0) = \mu\} $.
-Less formally, this can also be seen from the the gradient computations in \Cref{sec:ca: Lasso gap and gradient}, for all $\vvarx0\in\supp(\varf0^*)$
-$$0\in \partial \Func0(\varf0^*)(\vvarx0) = [\A^*\vvard0^*](\vvarx0) + \mu\sign(\varf0^*(\vvarx0)).$$
-From a computational perspective, identifying the support accurately allows for the most efficient choice of $\spcf0^n$, however, to exclude areas from the support requires very accurate quantification.
+Such methods are referred to as \emph{safe screening} rules \citep{ElGhaoui2010} which gradually identify the support and allow the optimisation algorithm to constrain parts of the reconstruction to 0.
+In this subsection we propose a new simple screening rule which is capable of generalising to our continuous subspace approximation setting.
+It is likely that more advanced methods \citep{Bonnefoy2015,Ndiaye2017} can also be adapted, although that is beyond the scope of this work.
+The key difference is the allowance of inexact computations resulting from estimates such as \eqref{eq: Taylor approximation}.
+
+The work of \citep{Duval2017a,Poon2018} and many others characterise the support of $\varf0^*$ very precisely.
+In particular, the support is at most $m$ distinct points and are a subset of $\{ \vvarx0\in\Domain \st |\A^*\vvard0^*|(\vvarx0) = \mu\} $ (an equivalent statement holds for the countable case).
+Less formally, this can also be seen from the the gradient computations in \Cref{sec: Lasso gap and gradient}, for all $\vvarx0\in\supp(\varf0^*)$ we have
+\begin{equation}
+	0\in \partial \Func0(\varf0^*)(\vvarx0) = [\A^*\vvard0^*](\vvarx0) + \mu\sign(\varf0^*(\vvarx0)).
+\end{equation}
 
@@
 First we use the strong convexity of $\Func0^*$, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible then
-$$\tfrac12\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}^2 \leq \Func0^*(\vars2_0\vvard0_n) - \Func0^*(\vvard0^*) = \Func0^*(\vars2_0\vvard0_n) + \Func0(\varf0^*) \leq \Func0^*(\vars2_0\vvard0_n) + \Func0(\varf0_n),$$
+\begin{equation}
+	\tfrac12\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}^2 \leq \Func0^*(\vars2_0\vvard0_n) - \Func0^*(\vvard0^*) = \Func0^*(\vars2_0\vvard0_n) + \Func0(\varf0^*) \leq \Func0^*(\vars2_0\vvard0_n) + \Func0(\varf0_n),
+\end{equation}
 which gives an easily computable bound on $\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}$. Now we estimate $\A^*\vvard0_n$ on the support of $\varf0^*$:
-\begin{align*}
+\begin{align}
 	\min_{\vvarx0\in\supp(\varf0^*)} |[\Pi_n\A^*\vvard0_n](\vvarx0)| &\geq \min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0_n](\vvarx0)|
@@
 	\\&\geq \frac1{\vars2_0}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vvard0_n-\vvard0^*}_{\ell^2}\right).
-\end{align*}
+\end{align}
 Therefore,
 \begin{equation}
-	|[\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\Func0(\varf0_n)+\Func0^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq:ca: support equation}
+	|[\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\Func0(\varf0_n)+\Func0^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq: support equation}
 \end{equation}
@@
 To make the equivalent statement on the discretised problem, simply replace $\vars2_0$ with $\vars2$ and $\A^*$ with $\Pi_n\A^*$.
-
-We can make two quick observations about this formula:
+There are two short observations on this formula:
 \begin{itemize}
-	\item The convergence guarantee from \Cref{thm:ca: exponential FISTA convergence} is for the quantity $\Func0(\varf0_n)-\Func0(\varf0^*)$, the more relevant quantity here is $\Func0^*(\vars2_0\vvard0_n)+\Func0(\varf0^*)$ for which there is no proven rate.
-	\item In \Cref{sec:ca: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
+	\item The convergence guarantee from \Cref{thm: exponential FISTA convergence} is for the quantity $\Func0(\varf0_n)-\Func0(\varf0^*)$, the more relevant quantity here is $\Func0^*(\vars2_0\vvard0_n)+\Func0(\varf0^*)$ for which there is no proven rate.
+	\item In \Cref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
 \end{itemize}
 
-\subsection{Operator norms}\label{sec:ca: smoothing operators}
+\subsection{Operator norms}\label{sec: smoothing operators}
 For numerical implementation of Lasso, we are required to accurately estimate several operator norms of $\A$.
-For $\func1$ to be 1-Lipschitz we must divide by $\norm{\A^*\A}$, and the adaptivity described in \Cref{sec:ca: continuous lasso rate,sec:ca: bound continuous,sec:ca: support detection} requires estimates of $|\A^*|_{\ell^2\to L^\infty}$, $|\A^*|_{\ell^2\to C^1}$, and $|\A^*|_{\ell^2\to C^2}$.
-The aim for this section is to provide estimates of these norms and seminorms for the numerical examples presented in \Cref{sec:ca: numerics}.
+For $\func1$ to be 1-Lipschitz we must divide by $\norm{\A^*\A}$, and the adaptivity described in \Cref{sec: continuous lasso rate,sec: bound continuous,sec: support detection} requires the values of $|\A^*|_{\ell^2\to L^\infty}$, $|\A^*|_{\ell^2\to C^1}$, and $|\A^*|_{\ell^2\to C^2}$.
+The aim for this section is to provide estimates of these norms and seminorms for the numerical examples presented in \Cref{sec: numerics}.
 
@@
 In this form, the adjoint can be written precisely, $\A^*\colon\R^m\to \F H$ by
-$$[\A^*\vvarx3](\vvarx0) = \sum_{j=1}^m \varx3_j\vard1_j(\vvarx0) \qquad \text{ for all }\vvarx0\in\Domain,\ \vvarx3\in\R^m.$$
+\begin{equation}
+	[\A^*\vvarx3](\vvarx0) = \sum_{j=1}^m \varx3_j\vard1_j(\vvarx0) \qquad \text{ for all }\vvarx0\in\Domain,\ \vvarx3\in\R^m.
+\end{equation}
 
 The following lemma allows for exact computation of the operator norm of $\A$, as needed to ensure that $\func1$ is 1-Lipschitz.
-\begin{lemma}\label{thm:ca: norm bound L2}
+\begin{lemma}\label{thm: norm bound L2}
 	If $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in \F H$ for $j\in[m]$, then
@@
 To compute the entries of $\A\A^*\colon\R^m\to\R^m$, observe that for any $\vvarx3\in\R^m$
-	$$ (\A\A^*\vvarx3)_i = \IP{\vard1_i}{\A^*\vvarx3} = \IP{\vard1_i}{\sum_{j=1}^m\varx3_j\vard1_j} = \sum_{j=1}^m \IP{\vard1_i}{\vard1_j}\varx3_j.$$
-	As required.
+	\begin{equation}
+		(\A\A^*\vvarx3)_i = \IP{\vard1_i}{\A^*\vvarx3} = \IP{\vard1_i}{\sum_{j=1}^m\varx3_j\vard1_j} = \sum_{j=1}^m \IP{\vard1_i}{\vard1_j}\varx3_j
+	\end{equation}
+	as required.
 \end{proof}
-If $\norm{\A^*\A}$ is not analytically tractable, then \Cref{thm:ca: norm bound L2} enables it to be computed using standard finite dimensional methods.
+If $\norm{\A^*\A}$ is not analytically tractable, then \Cref{thm: norm bound L2} enables it to be computed using standard finite dimensional methods.
 The operator $\A\A^*$ is always finite dimensional and can be computed without discretisation error.
@@
 In the continuous case, when $\F H=L^2(\Domain)$ we also need to estimate the smoothness properties of $\A^*$. A generic result for this is given in the following lemma.
-\begin{lemma}\label{thm:ca: norm bound smoothness}
+\begin{lemma}\label{thm: norm bound smoothness}
 	If $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in L^2(\Domain)\cap C^k(\Domain)$ for $j\in[m]$, then for all $\frac1q+\frac1{q^*}=1$, $q\in[1,\infty]$, we have
-	\begin{align*}
+	\begin{align}
 		|\A^*\vvarx3|_{C^k}&\coloneqq \sup_{\vvarx0\in\Domain} |\nabla^k[\A^*\vvarx3]|(\vvarx0) \leq \sup_{\vvarx0\in\Domain}\norm{(\nabla^k\vard1_j(\vvarx0))_{j=1}^m}_{\ell^{q^*}}\norm{\vvarx3}_{\ell^q},
 		\\ |\A^*|_{\ell^2\to C^k}&\coloneqq \sup_{\norm{\vvarx3}_{\ell^2}\leq 1} |\A^*\vvarx3|_{C^k} \leq \sup_{\vvarx0\in\Domain}\norm{(\nabla^k\vard1_j(\vvarx0))_{j=1}^m}_{\ell^{q^*}}\times \splitln{1}{q\geq 2}{\sqrt{m^{2-q}}}{q<2}.
-	\end{align*}
+	\end{align}
 \end{lemma}
@@
 	$$ |\nabla^k[\A^*\vvarx3]|(\vvarx0) = \left|\sum_{j=1}^m\nabla^k\vard1_j(\vvarx0)\varx3_j\right|
-	\leq \left(\sum_{j=1}^m|\nabla^k\vard1_j(\vvarx0)|^{q^*}\right)^{\frac{1}{q^*}}\norm{\vvarx3}_{\ell^q} = \norm{(\nabla^k\vard1_j(\vvarx0))_j}_{\ell^{q^*}}\norm{\vvarx3}_{\ell^q}.$$
-	For the second inequality, if $q>2$ and $\sum_{j=1}^m \varx3_j^2\leq 1$, then $|\varx3_j|\leq 1$ for all $j$ and $\norm{\vvarx3}_{\ell^q}^q\leq \norm{\vvarx3}_{\ell^2}^2\leq 1$.
+	\leq \left(\sum_{j=1}^m|\nabla^k\vard1_j(\vvarx0)|^{q^*}\right)^{\frac{1}{q^*}}\norm{\vvarx3}_{\ell^q} = \norm{(\nabla^k\vard1_j(\vvarx0))_j}_{\ell^{q^*}}\norm{\vvarx3}_{\ell^q}\;.$$
+	For the second inequality, if $q\geq2$ and $\sum_{j=1}^m \varx3_j^2\leq 1$, then $|\varx3_j|\leq 1$ for all $j$ and $\norm{\vvarx3}_{\ell^q}^q\leq \norm{\vvarx3}_{\ell^2}^2\leq 1$.
 If $q<2$ and $\norm{\vvarx3}_{\ell^2}\leq 1$, then we again use H\"older's inequality:
@@
 \subsubsection{Concrete examples}
-\Cref{thm:ca: norm bound smoothness} demonstrates how the smoothness of $\A$ relates to the smoothness of the kernels $\psi_j$, possibly scaling with respect to $m$.
-We now present explicit examples of the computations in both \Cref{thm:ca: norm bound smoothness,thm:ca: norm bound L2} for the numerical results in \Cref{sec:ca: numerics}.
-These examples are common in practical applications and we show the result of \Cref{thm:ca: norm bound examples} in the main text to demonstrate that, while sometimes hard to compute by hand, the constants can estimated accurately in an efficient manner.
+\Cref{thm: norm bound smoothness} demonstrates how the smoothness of $\A$ relates to the smoothness of the kernels $\psi_j$, possibly scaling with respect to $m$.
+We now present explicit examples of the computations in both \Cref{thm: norm bound smoothness,thm: norm bound L2} for the numerical results in \Cref{sec: numerics}.
+These examples are common in practical applications and we show the result of \Cref{thm: norm bound examples} in the main text to demonstrate that, while sometimes hard to compute by hand, the constants can estimated accurately in an efficient manner.
 The Gaussian case is by far the most technical, therefore we will provide a little further explanation at the end of the theorem.
-\begin{theorem}\label{thm:ca: norm bound examples}
-	\Copy{thm:ca: norm bound examples}{
+\begin{theorem}\label{thm: norm bound examples}
+	\Copy{thm: norm bound examples}{
 		Suppose $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in \F H=L^2([0,1]^d)$ for $j\in[m]$.
@@
 			for some $\vvarx0_0\in\R^d$, $\hat m\coloneqq\sqrt[d]{m}$. For all $\frac1q + \frac{1}{q^*} = 1$, $q\in(1,\infty]$, we get
-			\begin{align*}
+			\begin{align}
 				\norm{\A}_{L^2\to\ell^2} &\leq \bigg((4\pi\sigma^2)^{-\frac d2}\sum_{j=-2\hat m,\ldots,2\hat m}\exp(-\tfrac{\Delta^2}{4\sigma^2}j^2)\bigg)^d,
@@
 				\\ |\A^*\vvarx3|_{C^2} &\leq \frac{(2\pi\sigma^2)^{-\frac{d}{2}}}{\sigma^2} \bigg(\sum_{\vec j\in J} \left(1+\tfrac{\Delta^2}{\sigma^2}(|\vec j|+\delta)^2\right)^{q^*}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}} \norm{\vvarx3}_q,
-			\end{align*}
+			\end{align}
 			where $\delta= \frac{\sqrt d}{2}$ and $J=\{\vec j\in\F Z^d \st \norm{\vec j}_{\ell^\infty}\leq 2\hat m\}$.
 The case for $q=1$ can be inferred from the standard limit of $\norm\cdot_{{q^*}}\to \norm\cdot_{\infty}$ for $q^*\to\infty$.
-For $\Delta\ll\sigma$ (i.e.
-high resolution data), we get the scaling behaviour
-			$$ \norm{\A}_{L^2\to\ell^2} \lesssim \Delta^{-d}, \qquad |\A^*\vvarx3|_{C^k} \lesssim \sigma^{-k}\Delta^{-\tfrac{d}{q^*}}\norm{\vvarx3}_q, \qquad |\A^*|_{\ell^2\to C^k} \lesssim \sigma^{-k}\Delta^{-\frac{d}{2}},$$
-			for $k=0,1,2$.
 		\end{enumerate}
@@
 This is most cumbersome for Gaussian kernels, however, the sums converge faster than exponentially and so the computational burden should be very small.
-On the other hand, if $\Delta$ is small, then the sum is just a quadrature estimate for some continuous integrals.
-These integrals can be computed analytically and provide a much more intuitive grasp of the scaling with respect to dimensionality, grid spacing, and Gaussian width.
-
-\section{Numerical examples}\label{sec:ca: numerics}
+
+\section{Numerical examples}\label{sec: numerics}
 We present four numerical Lasso examples.
-The first two are in 1D to demonstrate the performance of different variants of \Cref{alg:ca: refining FISTA}, both with and without adaptivity.
+The first two are in 1D to demonstrate the performance of different variants of \Cref{alg: refining FISTA}, both with and without adaptivity.
 In particular, we explore sparse Gaussian deconvolution and sparse signal recovery from Fourier data; each displays slightly different behaviour in terms of optimisation.
-We compare with the \emph{continuous basis pursuit} (CBP) discretisation \cite{Ekanadham2011, Duval2017b} which is also designed to achieve super-resolution accuracy within a convex framework.
-More details of this method will be provided in \Cref{sec:ca: 1D Lasso examples}.
+We compare with the \emph{continuous basis pursuit} (CBP) discretisation \citep{Ekanadham2011, Duval2017b} which is also designed to achieve super-resolution accuracy within a convex framework.
+More details of this method will be provided in \Cref{sec: 1D Lasso examples}.
 
@@
 
-Finally, we process a dataset which represents a realistic application and (simulated) dataset for \Cref{alg:ca: refining FISTA} in biological microscopy, referred to as STORM microscopy.
+Finally, we process a dataset which represents a realistic application in biological microscopy, referred to as STORM microscopy.
 In essence, the task is to perform 2D Gaussian de-blurring/super-resolution and denoising to find the location of sparse spikes of signal.
@@
 In this section, the main aim is to minimise the exact Lasso energy $\Func0_0(\varf0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
-\Cref{thm:ca: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\Func0_0(\varf0_n)$ so it is this monotone estimate which is plotted.
+\Cref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\Func0_0(\varf0_n)$ so it is this monotone estimate which is plotted.
 To clarify, as $\Func0(\varf0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\Func0_0(\varf0_n) \approx \min_{n\leq N}\Func0(\varf0_n) + \min_{n'\leq n}\Func0^*(\vars2_0\vvard0_{n'})$.
 Another quantity of interest is minimisation of the discrete Lasso energy $\min_{n\leq N}\Func0(\varf0_n) + \min_{n'\leq n}\Func0^*(\vars2\vvard0_{n'})$ which will be referred to as the `discrete gap'.
-Note that for the adaptive schemes, this may not be exactly monotonic because the discrete dual problem is changing with $N$.
-
-\subsection{1D continuous Lasso}\label{sec:ca: 1D Lasso examples}
+Note that for the adaptive schemes this may not be exactly monotonic as the discrete dual problem changes with $N$.
+
+\subsection{1D continuous Lasso}\label{sec: 1D Lasso examples}
 In this example we choose $\spcf0=\C M([0,1])$ and $\A\colon \spcf0\to \R^{30}$ with either random Fourier kernels:
-$$(\A\varf0)_j = \int_0^1\cos(\vars3_j\varx0)\varf0(\varx0), \qquad \vars3_j\sim \op{Uniform}[-100,100],\ j\in[30],\ \mu =0.02, $$
+\begin{equation}
+	(\A\varf0)_j = \int_0^1\cos(\vars3_j\varx0)\varf0(\varx0), \qquad \vars3_j\sim \op{Uniform}[-100,100],\ j=1,2,\ldots,30,\ \mu =0.02, 
+\end{equation}
 or Gaussian kernels on a regular grid:
-$$(\A\varf0)_j = (2\pi\sigma^2)^{-\frac12}\int_0^1\exp\left(-\frac{(\varx0-(j-1)\Delta)^2}{2\sigma^2}\right)\varf0(\varx0), \quad \sigma=0.12,\ \Delta = \tfrac1{29},\ j\in[30],\ \mu=0.06.$$
-
-Many variants of FISTA are compared for these examples but the key alternative viewed here is the CBP discretisation.
-There are many methods designed to minimise the continuous Lasso energy in \eqref{eq:ca: Lasso energy} \cite{Bredies2013,Castro2016,Boyd2017,Catala2019} however, most result in a non-convex discretised problem to solve.
+\begin{equation}
+	(\A\varf0)_j = (2\pi\sigma^2)^{-\frac12}\int_0^1\exp\left(-\frac{(\varx0-(j-1)\Delta)^2}{2\sigma^2}\right)\varf0(\varx0), \quad \sigma=0.12,\ \Delta = \tfrac1{29},\ j=1,2,\ldots,30,\ \mu=0.06.
+\end{equation}
+
+Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.
+There are many methods designed to minimise the continuous Lasso energy in \eqref{eq: Lasso energy} \citep[c.f.][]{Bredies2013,Castro2016,Boyd2017,Catala2019} however, most result in a non-convex discretised problem to solve.
 We have focused on CBP because it approximates $\varf0^*$ through a convex discrete optimisation problem which is asymptotically exact in the limit $\meshsize\to0$.
 It can even be solved efficiently with FISTA which allows for direct comparison with the uniform and adaptive mesh approaches.
-As explained by \cite{Ekanadham2011, Duval2017b}, the idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen.
+As explained by \citep{Ekanadham2011, Duval2017b}, the idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen.
 If $\varf0^*$ has only one Dirac spike in each pixel then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.
 
-As shown in \Cref{sec:ca: Lasso definition}, in 1D we have $\vars3_{\Varf0} = \vars3_{\Func0} = 2$.
-The estimates given in \eqref{eq:ca: Lasso energy rate} and \eqref{eq:ca: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\Func0_0(\varf0_n)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$.
-To achieve these rates, we implement a refinement criterion from \Cref{thm:ca: practical refinement criteria} with guarantee of $\Func0_0(\varf0_{n_k-1})\lesssim 2^{-k}$ using the estimates made in \Cref{sec:ca: Lasso gap and gradient}.
+As shown in \Cref{sec: Lasso definition}, in 1D we have $\vars3_{\Varf0} = \vars3_{\Func0} = 2$.
+The estimates given in \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\Func0_0(\varf0_n)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$.
+To achieve these rates, we implement a refinement criterion from \Cref{thm: practical refinement criteria} with guarantee of $\Func0_0(\varf0_{n_k-1})\lesssim 2^{-k}$ using the estimates made in \Cref{sec: Lasso gap and gradient}.
 We choose subspaces $\spcf0^n$ to approximately enforce
-$$\Func0(\varf0_n) + \Func0^*(\vars2_0\vvard0_n) \leq 2(\Func0(\varf0_n) + \Func0^*(\vars2\vvard0_n))$$
+\begin{equation}
+	\Func0(\varf0_n) + \Func0^*(\vars2_0\vvard0_n) \leq 2(\Func0(\varf0_n) + \Func0^*(\vars2\vvard0_n)),
+\end{equation}
 i.e. the continuous gap is bounded by twice the discrete gap. In particular, note that for $\vars2_0\approx \vars2$,
-$$ \Func0^*(\vars2_0\vvard0_n) = \tfrac12\norm{\vars2_0\vvard0_n}^2 + \vars2_0\ip{\vdata0}{\vvard0_n} = \frac{\vars2_0}{\vars2}\left(\frac{\vars2_0}{\vars2}\tfrac12\norm{\vars2\vvard0_n}^2 + \vars2\ip{\vdata0}{\vvard0_n}\right) \approx \frac{\vars2_0}{\vars2} \Func0^*(\vars2\vvard0_n).$$
+\begin{equation}
+	\Func0^*(\vars2_0\vvard0_n) = \tfrac12\norm{\vars2_0\vvard0_n}^2 + \vars2_0\ip{\vdata0}{\vvard0_n} = \frac{\vars2_0}{\vars2}\left(\frac{\vars2_0}{\vars2}\tfrac12\norm{\vars2\vvard0_n}^2 + \vars2\ip{\vdata0}{\vvard0_n}\right) \approx \frac{\vars2_0}{\vars2} \Func0^*(\vars2\vvard0_n).
+\end{equation}
 Inserting this back into the continuous/discrete gap inequality, it becomes 
-$$ \frac{\vars2_0}{\vars2} \leq 1 + (2-1)\frac{\Func0(\varf0_n)+\Func0^*(\vars2\vvard0_n)}{\Func0^*(\vars2\vvard0_n)}$$
+\begin{equation}
+	\frac{\vars2_0}{\vars2} \leq 1 + (2-1)\frac{\Func0(\varf0_n)+\Func0^*(\vars2\vvard0_n)}{\Func0^*(\vars2\vvard0_n)}
+\end{equation}
 where 2 was our initial chosen ratio. Converting this into a spatial refinement criteria, recall 
-$$ \frac{\vars2_0}{\vars2} \approx \frac{\Norm{\A^*\vvard0_n}_*}{\Norm{\Pi_n\A^*\vvard0_n}_*} = \frac{\max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{\max_{\domain_i^n\in\F M^n} |\Pi_n\A^*\vvard0_n(\domain_i^n)|} \approx \max_{\domain_i^n\in\F M^n}\frac{ \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{|\Pi_n\A^*\vvard0_n(\domain_i^n)|}.$$
+\begin{equation}
+	\frac{\vars2_0}{\vars2} \approx \frac{\Norm{\A^*\vvard0_n}_*}{\Norm{\Pi_n\A^*\vvard0_n}_*} = \frac{\max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{\max_{\domain_i^n\in\F M^n} |\Pi_n\A^*\vvard0_n(\domain_i^n)|} \approx \max_{\domain_i^n\in\F M^n}\frac{ \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{|\Pi_n\A^*\vvard0_n(\domain_i^n)|}.
+\end{equation}
 If $\frac{\vars2_0}{\vars2}$ is large then there must be pixels (values of $i$) in which this ratio is large.
-Because of the smoothness of $\A^*\vvard0_n$, refining these pixels will reduce the halve the difference and reduce the balance again.
+Because of the smoothness of $\A^*\vvard0_n$, refining these pixels will halve the difference and therefore contract $\frac{\vars2_0}{\vars2}$ back towards 1.
 This was found to be an efficient method of selecting pixels for refinement based on quantities which had already been computed.
 Note briefly that from a heuristic standpoint we are refining for two reasons, aligning with an exploitation/exploration viewpoint.
-Either the Taylor expansion is tight and it is likely that $\varf0^*$ has support in this point, or the Taylor expansion is loose and we refine to improve our level of uncertainty.
-This second point guarantees that we find the whole support of $\varf0^*$, not just a subset.
+The trigger is always the result of an estimate from the cell-wise Taylor expansion.
+If the estimate is accurate, then that cell is likely to intersect the support of $\varf0^*$ and refining directly improves the resolution of the support of $\varf0^*$.
+Otherwise, if the estimate is loose then the refinement improves the accuracy of the Taylor expansion and consequently improves the screening of new pixels from the support of $\varf0^*$.
+This second point guarantees that we converge to the global minimiser $\varf0^*$, rather than a sub-optimal critical point.
 
 \paragraph{Comparison of discretisation methods}
-In \Cref{fig:ca: convergence with ndofs} we compare the three core approaches: fixed uniform
+In \Cref{fig: convergence with ndofs} we compare the three core approaches: fixed uniform
 discretisation, adaptive discretisation, and CBP.
@@
 	\item Increasing the number of pixels always increases the accuracy of the optimisation.
-	\item The adaptive scheme is much more efficient, in both examples the adaptive scheme with 128 pixels is at least competitive with both fixed discretisations with 512 pixels.
-In fact, only a maximum of 214 pixels were needed by the adaptive method.
+	\item The adaptive scheme is much more efficient, in both examples the adaptive scheme with 128 pixels is at least as good as both fixed discretisations with 512 pixels.
+In fact, only a maximum of 214 pixels were needed by the adaptive method in either example.
 	\item With Fourier kernels the uniform piecewise constant discretisation is more efficient than CBP but in the Gaussian case this is reversed.
 This suggests that the CBP \emph{does} achieve super-resolution when $\A$ is sufficiently smooth but may be less accurate when the kernels oscillate on the length-scale of a single pixel.
-	\item The discrete gaps for non-adaptive optimisation behave as is common for FISTA, initial convergence is polynomial until a locally linear regime activates \cite{Tao2016}.
+	\item The discrete gaps for non-adaptive optimisation behave as is common for FISTA, initial convergence is polynomial until a locally linear regime activates \citep{Tao2016}.
 CBP is always slower to converge than the piecewise constant discretisation.
@@
 It is not completely fair to judge CBP with the continuous gap because, although it generates a continuous representation, this continuous representation is not necessarily consistent with the discrete gap being optimised, unlike when discretised with finite element methods.
-On the other hand, this is still the intended interpretation of the algorithm and we have no more appropriate metric in this case.
+On the other hand, this is still the intended interpretation of the algorithm and we have no more appropriate metric for success in this case.
 
@@
 The `adaptive' method uses the proposed algorithm.
-Both `fixed' and `CBP' use standard FISTA with a uniform discretisation.}\label{fig:ca: convergence with ndofs}
+Both `fixed' and `CBP' use standard FISTA with a uniform discretisation.}\label{fig: convergence with ndofs}
 \end{figure}
@@
 \paragraph{Comparison of FISTA variants}
-There are many variants of FISTA which can also be implemented in the form of \Cref{alg:ca: refining FISTA} just by updating the $\spcf0^n$ on each iteration.
-Although we have not proven convergence for all of these, \Cref{fig:ca: convergence with method} compares many methods with either fixed or adaptive discretisations.
+\Cref{fig: convergence with method} compares many methods with either fixed or adaptive discretisations.
 Each adaptive scheme is allowed up to 1024 pixels and each uniform discretisation uses exactly 1024.
-Forward-Backward splitting (FB) uses a sequence $\vart1_n=1$ otherwise for FISTA a general $\vart1_n = \frac{n+a-1}{a}$ is used.
-The restarting scheme is given in \Cref{alg:ci: restarting FISTA} and `greedy' FISTA is given in \Cref{alg:ci: greedy FISTA}.
+The `Greedy FISTA' implementation was proposed by \citet{Liang2018} and we include the adaptive variant despite a lack of convergence proof.
+The remaining FISTA algorithms use a FISTA time step of $\vart1_n = \frac{n+a-1}{a}$ for the given value of $a$, as proposed by \citet{Chambolle2015}.
 In this example CBP used the greedy FISTA implementation which gave faster observed convergence.
-\Cref{fig:ca: convergence with method} compares the discrete gaps because it is the accurate metric for fixed discretisations, and for the adaptive discretisation it should also be an accurate predictor of the continuous gap.
-
-\pagebreak The key observations are:
+\Cref{fig: convergence with method} compares the discrete gaps because it is the accurate metric for fixed discretisations, and for the adaptive discretisation it should also be an accurate predictor of the continuous gap.
+
+The key observations are:
 \begin{itemize}
-	\item The only algorithm with noticeably different convergence is FB, which is the non-accelerated form of FISTA. Every other algorithm converges at the same approximate rate.
-	\item The fixed discretisation schemes have an initial `slow' convergence before reaching a `fast' rate.
-The solid green line of FISTA $a=2$ appears to achieve the theoretical $\frac1{n^2}$ rate and other FISTA implementations are much faster for large $n$.
+	\item Each algorithm displays very similar convergence properties. The main difference is that the reconstructions with fixed discretisations accelerate after $10^4$-$10^5$ iterations.
 	\item During the initial `slow' phase, adaptive and fixed discretisations appear to achieve very similar (discrete) convergence rates.
 The coarse-to-fine adaptivity is not slower than fixed discretisations in this regime.
-	\item \Cref{thm:ca: practical refinement criteria} accurately predicts the $\frac1n$ rate of the adaptive methods, mirrored in the fixed discretisations.
-This suggests that high-resolution but fixed discretisations are initially limited by the continuous problem before entering the asymptotic discrete regime.
-	\item \Cref{thm:ca: practical refinement criteria} only applies to two adaptive schemes, labelled $a=2$ and $a=20$.
-The remaining FISTA schemes all perform comparably although the restarting scheme is often the slowest.
-Both $a=20$ and greedy FISTA are consistently the best or near-best performing methods.
+	\item \Cref{thm: practical refinement criteria} accurately predicts the $\frac1n$ rate of the adaptive methods, mirrored in the fixed discretisations.
+This suggests that high-resolution discretisations are also initially limited by this $\frac1n$ rate before entering the asymptotic regime.
+	\item The fastest FISTA algorithm is consistently the greedy one, although $a=20$ is very comparable.
 \end{itemize}
@@
 \begin{figure}[H]\centering
-	\includegraphics[width=.84\textwidth]{lasso_convergence}
+	\includegraphics[width=.84\textwidth]{lasso_convergence_short}
 	\caption{Discrete convergence of different algorithms.
-`Adaptive' methods use \Cref{alg:ca: refining FISTA} with fewer than 1024 pixels and the remaining methods use a uniform discretisation of 1024 pixels.}\label{fig:ca: convergence with method}
+`Adaptive' methods use \Cref{alg: refining FISTA} with fewer than 1024 pixels and the remaining methods use a uniform discretisation of 1024 pixels.}\label{fig: convergence with method}
 \end{figure}
@@
 \paragraph{Comparison of fixed and adaptive discretisation}
-Motivated by the findings in \Cref{fig:ca: convergence with method}, we now look more closely at the performance of the $a=20$ and the greedy FISTA schemes.
+Motivated by the findings in \Cref{fig: convergence with method}, we now look more closely at the performance of the $a=20$ and the greedy FISTA schemes.
 We have analytical results for the former but the latter typically performs the best for non-adaptive optimisation and is never worse than $a=20$ in the adaptive setting.
-We assume that the aim is to find a function $\varf0_n$ with $\Func0_0(\varf0_n)$ smaller than a given threshold.
+We assume that the numerical aim is to find a function $\varf0_n$ with $\Func0_0(\varf0_n)$ smaller than a given threshold.
 The question is whether it is faster/more efficient to use the proposed adaptive scheme or to use a classical scheme at sufficiently high uniform resolution.
@@
 
-\Cref{fig:ca: comparison with iteration} shows the convergence with respect to number of iterations.
+\Cref{fig: comparison with iteration} shows the convergence with respect to number of iterations.
 As expected, the fixed discretisation starts with a smaller continuous gap before plateauing to a sub-optimal gap around $\Func0_0=0.1$.
@@
 This is consistent with $\Func0$ being a little bit smoother than predicted (i.e.
-$\vars2_{\Func0}>2$).
+$\vars3_{\Func0}>2$).
 
@@
 Suppose the stopping criterion is to find $\varf0$ such that $\Func0_0(\varf0)<0.1$.
-\Cref{fig:ca: comparison with iteration} shows that it is equivalent to `guess' the necessary resolution, or to adaptively refine until reaching the stopping criterion.
+\Cref{fig: comparison with iteration} shows that it is equivalent to `guess' the necessary resolution, or to adaptively refine until reaching the stopping criterion.
 Both methods would converge after $O(10^3)$ iterations with a minimum pixel size of $2^{-10}$.
 
-\Cref{fig:ca: comparison with time} shows a more practical comparison showing wall-clock computation time and number of pixels (memory usage).
+\Cref{fig: comparison with time} shows a more practical comparison showing wall-clock computation time and number of pixels (memory usage).
 Optimisation of the fixed discretisation is faster overall but after around \SI{0.1}{\second}, it is always faster to use the adaptive scheme to achieve a given continuous gap.
@@
 The adaptive scheme re-computes the discrete matrix $\A\Pi_n$ each time there is a refinement, but the fixed schemes only compute it once.
-The adaptive schemes still seem to converge faster than $\frac1{\op{time}}$.
+The adaptive schemes still seem to converge faster than $\frac1{\op{time}}$, which is the expected rate if time per iteration is constant.
 
@@
 	\caption{Continuous convergence of adaptive (coarse-to-fine pixel size) compared with uniform discretisation (constant pixel size) with respect to number of iterations.
-}\label{fig:ca: comparison with iteration}
+}\label{fig: comparison with iteration}
 \end{figure}
@@
 	\includegraphics[width=.84\textwidth]{lasso_convergence_time}
-	\caption{Continuous convergence of adaptive compared with uniform discretisation with respect to wall-clock time and total number of pixels (memory requirement).}\label{fig:ca: comparison with time}
+	\caption{Continuous convergence of adaptive compared with uniform discretisation with respect to wall-clock time and total number of pixels (memory requirement).}\label{fig: comparison with time}
 \end{figure}
 
-\subsection{2D wavelet Lasso}\label{sec:ca: wavelet examples}
+\subsection{2D wavelet Lasso}\label{sec: wavelet examples}
 In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{\Varx0}^I_i$ where 
-$$\F{\Varx0}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{50},-\tfrac12+\tfrac{i}{50}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I \quad \text{ for } i,I\in[50].$$
-This is not exactly in the form analysed by \Cref{thm:ca: norm bound examples}, however for each $I$ the sets $\{\F{\Varx0}^I_i\st i\in[50]\}$ are disjoint therefore we can apply \Cref{thm:ca: norm bound examples} block-wise to estimate
-$$\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[50]} |\F{\Varx0}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[50]} \int_{\F{\Varx0}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[50]}\ (\A\1)_{i,I}}.$$
+\begin{equation}
+	\F{\Varx0}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{50},-\tfrac12+\tfrac{i}{50}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I \quad \text{ for } i,I=1,2,\ldots,50.
+\end{equation}
+This is not exactly in the form analysed by \Cref{thm: norm bound examples}, however for each $I$ the sets $\{\F{\Varx0}^I_i\st i\in[50]\}$ are disjoint therefore we can apply \Cref{thm: norm bound examples} block-wise to estimate
+\begin{equation}
+	\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[50]} |\F{\Varx0}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[50]} \int_{\F{\Varx0}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[50]}\ (\A\1)_{i,I}}\;.
+\end{equation}
 $\A$ is not smooth, therefore we can't bound $|\A^*|_{C^k}$ for $k>0$, and so we must look to minimise over $\ell^1$ rather than $L^1$.
 The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the Lasso form:
-$$\min_{\varf0\in \spcf0} \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu \norm{\linop{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \tfrac12\norm{\A\linop{W}\hat{\varf0}-\vdata0}_{\ell^2}^2 + \mu \norm{\hat{\varf0}}_{\ell^1}.$$
+\begin{equation}
+	\min_{\varf0\in \spcf0} \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu \norm{\linop{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \tfrac12\norm{\A\linop{W}\hat{\varf0}-\vdata0}_{\ell^2}^2 + \mu \norm{\hat{\varf0}}_{\ell^1}.
+\end{equation}
 The minimisers are related by $\varf0^* = \linop{W}\hat{\varf0}^*$ and, for wavelet bases, $\linop{W}$ is orthonormal so $\norm{\A\linop{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$.
-From \Cref{sec:ca: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\linop{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$.
+From \Cref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\linop{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$.
 If $\linop{W}$ is a wavelet transformation then its columns, $w_j\in L^2$, are simply the wavelets themselves and we can use the bound
-\begin{equation*}
+\begin{equation}
 	|\IP{w_j}{\A^*\vvard0_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vvard0_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vvard0_n}_{L^2}\leq \norm{\1_{\F{\Varx0}} \A^*\vvard0_n}_{L^2}
-\end{equation*}
-for all $\F{\Varx0}\supset \supp(w_{\vars0})$.
+\end{equation}
+for all $\F{\Varx0}\supset \supp(w_j)$.
 In the case of the Radon transform, we can compute the left-hand side explicitly for the finitely many $j\in J_n$ but we wish to use the right-hand side in a structured way to avoid computing the infinitely many $j\notin J_n$.
@@
 \paragraph{Tree structure of wavelets}
-Finite elements are constructed with a mesh which provided a useful tool for adaptive refinement in \Cref{sec:ca: bound continuous}.
+Finite elements are constructed with a mesh which provided a useful tool for adaptive refinement in \Cref{sec: bound continuous}.
 For wavelets, we will associate a tree with every discretisation and the leaves of the tree form a mesh.
@@
 $$\tilde{\spcf0}^k = \tilde{\spcf0}^{k-1}\bigcup\left\{w_{j,k}(\varx0) = \sqrt{2}^k\vard1(2^{k}\varx0-j)\st j=0,\ldots 2^k-1\right\}.$$
-If we keep track of the support $w_{j,k}$ then we see a tree structure emerging, as shown in \Cref{fig:ca: wavelet tree}.
+If we keep track of the support $w_{j,k}$, then we see a tree structure emerging, as shown in \Cref{fig: wavelet tree}.
 \begin{figure}\begin{center}\begin{tikzpicture}[grow'=right]
@@
 	\end{tikzpicture}\end{center}
-	\caption{Tree representation of 1D wavelets $w_{j,k}$ are arranged in a tree structure with their support underneath.}\label{fig:ca: wavelet tree}
+	\caption{Tree representation of 1D wavelets $w_{j,k}$ are arranged in a tree structure with their support underneath.}\label{fig: wavelet tree}
 \end{figure}
@@
 The only change in our own implementation is to translate the support to $[-\tfrac12,\tfrac12]^2$.
-We briefly remark that the tree structuring of wavelets is not novel and appears more frequently in the Bayesian inverse problems literature, for example in \cite{Castillo2019}.
+We briefly remark that the tree structuring of wavelets is not novel and appears more frequently in the Bayesian inverse problems literature, for example see \citet{Castillo2019}.
 
 \paragraph{Continuous gradient estimate}
-In \Cref{sec:ca: 1D Lasso examples} we used the continuous gap as a measure for convergence, for wavelets we will use the continuous gradient.
-With the tree structure we can easily adapt the results of \Cref{sec:ca: Lasso gap and gradient} to estimate gradients (or function gaps).
+In \Cref{sec: 1D Lasso examples} we used the continuous gap as a measure for convergence, for wavelets we will use the continuous gradient.
+With the tree structure we can easily adapt the results of \Cref{sec: Lasso gap and gradient} to estimate gradients (or function gaps).
 In particular,
 \begin{align}
-	\Norm{\partial \Func0(\varf0_n)}_* &=\max\left(\Norm{\partial_n\Func0(\varf0_n)}_*, \max_{j\notin J_n} |\IP{w_j}{\A^*\vvard0_n}| -\mu \right) \\&\leq\max\left(\Norm{\partial_n\Func0(\varf0_n)}_*, \max_{j\in \op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu \right).\label{eq:ca: wavelet error metric}
+	\Norm{\partial \Func0(\varf0_n)}_* &=\max\left(\Norm{\partial_n\Func0(\varf0_n)}_*, \max_{j\notin J_n} |\IP{w_j}{\A^*\vvard0_n}| -\mu \right) \\&\leq\max\left(\Norm{\partial_n\Func0(\varf0_n)}_*, \max_{j\in \op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu \right).\label{eq: wavelet error metric}
 \end{align}
 It is interesting to note that 
-$$\sum_{j\in\op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0^*}_{L^2}^2 = \norm{\A^*\vvard0^*}_{L^2}^2,$$
+\begin{equation}
+	\sum_{j\in\op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0^*}_{L^2}^2 = \norm{\A^*\vvard0^*}_{L^2}^2,
+\end{equation}
 therefore the task of refinement is somehow to partition the domain of $\A^*\vvard0^*$ such that no single component has more than $\mu$ magnitude. Also, by strong convexity of the dual problem,
-$$\left|\vars2_0\norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} - \norm{\1_{\supp(w_j)}\A^*\vvard0^*}_{L^2}\right| \leq \sqrt{|\supp(w_j)|}\sqrt{2(\Func0(\varf0_n)+\Func0^*(\vars2_0\vvard0_n))},$$
+\begin{equation}
+	\left|\vars2_0\norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} - \norm{\1_{\supp(w_j)}\A^*\vvard0^*}_{L^2}\right| \leq \sqrt{|\supp(w_j)|}\sqrt{2(\Func0(\varf0_n)+\Func0^*(\vars2_0\vvard0_n))},
+\end{equation}
 therefore the exact discretisation is reached in finite time.
-After this point, the discretised problem is equal to the continuous problem, and \Cref{alg:ca: refining FISTA} will behave as in the classical setting.
+After this point, the discretised problem is equal to the continuous problem, and \Cref{alg: refining FISTA} will behave as in the classical setting.
 
@@
 No noise is added to the Shepp-Logan data but \SI{5}{\percent} Gaussian white noise is added to the disc data.
-This is visualised in \Cref{fig:ca: haar data}.
-All optimisations shown will be spatially adaptive using Haar wavelets and initialised with four degrees of freedom (denoted $\spcf0^1$ in the notation of \Cref{fig:ca: wavelet tree}).
+This is visualised in \Cref{fig: haar data}.
+All optimisations shown will be spatially adaptive using Haar wavelets and initialised with four degrees of freedom (denoted $\spcf0^1$ in the notation of \Cref{fig: wavelet tree}).
 The gradient metric shown throughout is the $\ell^2$ norm.
-Motivated by \eqref{eq:ca: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ such that
-$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\Func0(\varf0_n)}_*,$$
-i.e. so that the continuous gradient is less than 10 times the discrete gradient.
-
-\begin{figure}[H]\centering
+Motivated by \eqref{eq: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ to ensure that
+$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\Func0(\varf0_n)}_*$$
+for all $j$ and $n$ (i.e. so that the continuous gradient is less than 10 times the discrete gradient).
+
+\begin{figure}\centering
 	\includegraphics[width=.84\textwidth]{haar_data}
@@
 The Shepp-Logan data is exact but the data for the disc-phantom has \SI{5}{\percent}\ Gaussian white noise.
-Without noise the data would be uniform with respect to the angle.}\label{fig:ca: haar data}
+Without noise the data would be uniform with respect to the angle.}\label{fig: haar data}
 \end{figure}
 
-The first numerical results shown in \Cref{fig:ca: haar convergence} compare the same adaptive algorithms as shown in \Cref{fig:ca: convergence with method}.
-In these examples we see that the greedy FISTA, restarting, and the $a=20$ algorithms achieve almost linear convergence while $a=2$ and the classical FB are significantly slower.
+The first numerical results shown in \Cref{fig: haar convergence} compare the same adaptive algorithms as shown in \Cref{fig: convergence with method}.
+In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ and the classical FB are significantly slower.
 The maximum number of wavelet coefficients used was 312,220 and 44,644 for the circle and Shepp-Logan phantoms respectively.
 
-\begin{figure}[H]\centering
-	\includegraphics[width=.84\textwidth]{haar_convergence}
-	\caption{Discrete convergence of different implementations of \Cref{alg:ca: refining FISTA} with an unlimited number of pixels.}\label{fig:ca: haar convergence}
+\begin{figure}\centering
+	\includegraphics[width=.84\textwidth]{haar_convergence_short}
+	\caption{Discrete convergence of different implementations of \Cref{alg: refining FISTA} with an unlimited number of pixels.}\label{fig: haar convergence}
 \end{figure}
 
-As before, we focus on the $a=20$ algorithm to which \Cref{thm:ca: practical refinement criteria} applies, and greedy FISTA which we see achieves slightly faster convergence in \Cref{fig:ca: haar convergence zoom}.
+As before, we focus on the $a=20$ algorithm to which \Cref{thm: practical refinement criteria} applies, and greedy FISTA which we see achieves slightly faster convergence in \Cref{fig: haar convergence zoom}.
 Looking at the discrete and continuous gradient norms, we see that they are initially distinct then merge after around 50 iterations.
@@
 
-\begin{figure}\centering
+\begin{figure}[H]\centering
 	\includegraphics[width=.84\textwidth]{haar_reduced_convergence}
-	\caption{Discrete/continuous convergence of adaptive FISTA algorithms on the wavelet Lasso optimisation.}\label{fig:ca: haar convergence zoom}
+	\caption{Discrete/continuous convergence of adaptive FISTA algorithms on the wavelet Lasso optimisation.}\label{fig: haar convergence zoom}
 \end{figure}
@@
 The resolution of visible light microscopy is fundamentally limited by the wavelength of visible light.
-Classically, this limit has held around \SI{250}{\nano\meter}, however, in recent years new techniques have emerged improving resolution to around \SIrange{30}{50}{\nano\meter} \cite{Schermelleh2019}.
+Classically, this limit has held around \SI{250}{\nano\meter}, however, in recent years new techniques have emerged improving resolution to around \SIrange{30}{50}{\nano\meter} \citep{Schermelleh2019}.
 A big component of this shift is a growing reliance on more powerful data processing techniques.
@@
 In the context of STORM, each recorded image is modelled as a sparse signal convolved with a point-spread function, then corrupted with noise.
-The Lasso formulation has previously been shown to be effective in the context of STORM \cite{Huang2017,Denoyelle2019}.
+The Lasso formulation has previously been shown to be effective in the context of STORM, see for instance \citet{Huang2017,Denoyelle2019}.
 
@@
 It is common to model the point-spread function as a Gaussian, in this example the corresponding Lasso formulation  is
-$$ (\A\varf0)_{i} = (2\pi\sigma^2)^{-1}\int_{[0,6.4]^2} \exp\left(-\frac{1}{2\sigma^2}\left|\vvarx0- \Delta\begin{pmatrix}i_1+\tfrac12 & i_2+\tfrac12\end{pmatrix}^\top \right|^2\right)\varf0(\vvarx0)$$
-where $\sigma=\SI{0.2}{\micro\meter}$, $\Delta=\SI{0.1}{\micro\meter}$, and $i_1,i_2\in[64]$ where $\spcf0=\C M([\SI{0}{\micro\meter},\SI{6.4}{\micro\meter}]^2)$.
-3020 frames are provided, examples of which are shown in \Cref{fig:ca: STORM data}.
+\begin{equation}
+	(\A\varf0)_{i} = (2\pi\sigma^2)^{-1}\int_{[0,6.4]^2} \exp\left(-\frac{1}{2\sigma^2}\left|\vvarx0- \Delta\begin{pmatrix}i_1+\tfrac12 & i_2+\tfrac12\end{pmatrix}^\top \right|^2\right)\varf0(\vvarx0)\,d\vvarx0, \qquad \sigma=\SI{0.2}{\micro\meter},\ \Delta=\SI{0.1}{\micro\meter}
+\end{equation}
+for $i_1,i_2 = 1,2,\ldots,64$ and $\spcf0=\C M([\SI{0}{\micro\meter},\SI{6.4}{\micro\meter}]^2)$.
+3020 frames are provided, examples of which are shown in \Cref{fig: STORM data}.
 To process this dataset, image intensities were normalised to $[0,1]$ then a constant was subtracted to approximate 0-mean noise.
@@
 
-Finally, all the reconstructions were summed and the result shown in \Cref{fig:ca: STORM results}.
+\begin{figure}\centering
+	\includegraphics[width=.8\textwidth]{STORM_data}
+	\caption{Example of images from STORM dataset.}\label{fig: STORM data}
+\end{figure}
+
+Finally, all the reconstructions were summed and the result shown in \Cref{fig: STORM results}.
 The average pixel width after optimisation was approximately \SI{2.4}{\nano\meter}, a factor of 40 super-resolution.
 If this resolution had been implemented with a uniform discretisation then it would have required $70\times 10^5$ pixels, nearly a factor of 100 greater than achieved with the adaptive discretisation.
-Lasso is compared with ThunderSTORM \cite{Ovesny2014}, a popular ImageJ plugin \cite{Schindelin2012} which finds the location of signal using Fourier filtering.
-The performance of ThunderSTORM was rated very highly in the initial competition by \cite{Sage2015}.
+Lasso is compared with ThunderSTORM \citep{Ovesny2014}, a popular ImageJ plugin \citep{Schindelin2012} which finds the location of signal using Fourier filtering.
+The performance of ThunderSTORM was rated very highly in the initial competition by \citet{Sage2015}.
 Both methods compared here demonstrate the key structures of the reconstruction, however, both are sensitive to tuning parameters.
@@
 
-\Cref{fig:ca: STORM convergence} shows the convergence behaviour in this example.
-The estimates given by \eqref{eq:ca: Lasso energy rate} and \eqref{eq:ca: Lasso resolution rate} in dimension $d=2$ predict respectively that the adaptive energy will decay at a rate of $\Func0_0(\varf0_n)\lesssim n^{-\sfrac23}$ so long as the pixel size also decreases at a rate of $\meshsize\sim n^{-\sfrac23}$.
+\Cref{fig: STORM convergence} shows the convergence behaviour in this example.
+The estimates given by \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=2$ predict respectively that the adaptive energy will decay at a rate of $\Func0_0(\varf0_n)\lesssim n^{-\sfrac23}$ so long as the pixel size also decreases at a rate of $\meshsize\sim n^{-\sfrac23}$.
 This is consistent with the resolution scaling (middle panel) but the energy (left panel in pink) is observed to converge a little faster than predicted.
 
-In this example we also implement the suggestion of \Cref{sec:ca: support detection} to remove pixels from the iteration once we can guarantee they are outside of the support.
-\eqref{eq:ca: support equation} provides a threshold to identify the support of the discrete/continuous minimiser and the value of this is plotted in the first panel of \Cref{fig:ca: STORM convergence}, in particular the normalised value $1-\frac{\op{threshold}}{\mu}$ which converges to 0 for large $n$.
+In this example we also implement the suggestion of \Cref{sec: support detection} to remove pixels from the iteration once we can guarantee they are outside of the support.
+\eqref{eq: support equation} provides a threshold to identify the support of the discrete/continuous minimiser and the value of this is plotted in the first panel of \Cref{fig: STORM convergence}, in particular the normalised value $1-\frac{\op{threshold}}{\mu}$ which converges to 0 for large $n$.
 Any pixel $\domain_i^n$ satisfying
-$$ \vars2_0\norm{\Pi_n\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq \op{threshold}$$
+\begin{equation}
+	 \vars2_0\norm{\Pi_n\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq \op{threshold}
+\end{equation}
 guarantees that $\domain_i^n\cap\op{supp}(\varf0^*) = \emptyset$.
 Once this threshold becomes greater than 0 (plotted value less than 1), we can start reducing the number of pixels instead of just continual refinement.
-We can see this in the right-hand panel of \Cref{fig:ca: STORM convergence}, after around 30 iterations the total number pixels starts to reduce and stabilise at approximately $6\times10^3$ pixels per frame, well below the upper limit of $10^5$.
-
-\begin{figure}\centering
-	\includegraphics[width=.8\textwidth]{STORM_data}
-	\caption{Example of images from STORM dataset.}\label{fig:ca: STORM data}
+This is seen in the right-hand panel of \Cref{fig: STORM convergence}, after around 30 iterations the total number pixels starts to reduce and stabilise at approximately $6\times10^3$ pixels per frame, well below the upper limit of $10^5$.
+
+\begin{figure}[H]\centering
+	\includegraphics[width=\textwidth]{lasso2_convergence}
+	\caption{Convergence of adaptive FISTA for STORM dataset.
+Lines indicate the median value over 3020 STORM frames.
+Shaded regions indicate the \SIrange{25}{75}{\percent} inter-quartile range.}\label{fig: STORM convergence}
 \end{figure}
@@
 	\caption{Processed results of the STORM dataset.
-Top left: Lasso optimisation with \Cref{alg:ca: refining FISTA}.
+Top left: Lasso optimisation with \Cref{alg: refining FISTA}.
 Top right: Comparison with ThunderSTORM plugin.
-Bottom: Average data, no super-resolution or de-blurring.}\label{fig:ca: STORM results}
-\end{figure}
-\begin{figure}\centering
-	\includegraphics[width=\textwidth]{lasso2_convergence}
-	\caption{Convergence of adaptive FISTA for STORM dataset.
-Lines indicate the median value over 3020 STORM frames.
-Shaded regions indicate the \SIrange{25}{75}{\percent} inter-quartile range.}\label{fig:ca: STORM convergence}
+Bottom: Average data, no super-resolution or de-blurring.}\label{fig: STORM results}
 \end{figure}
@@
 
-An interesting observation over all of the adaptive Lasso examples is that the classical oscillatory behaviour of FISTA has not occured.
+An interesting observation over all of the adaptive Lasso examples is that the classical oscillatory behaviour of FISTA has not occurred.
 With the monotone gaps plotted, oscillatory convergence should correspond to a piecewise constant descending gap.
-Either this behaviour only emerges for larger $n$, or the adaptivity mimics the restarting behaviour typically used to avoid oscillation.
-The perturbation provided by the refinement is sufficient to stop FISTA overshooting the minimiser and maintain a predictable rate of convergence to the minimiser.
-This may also explain why the standard restarting FISTA showed little improvement in these examples.
+Either this behaviour only emerges for larger $n$, or the adaptivity provides a dampening effect for this oscillation.
 
 Moving forward, it would be interesting to see how far the analysis extends to other optimisation algorithms.
-To cover the numerical results, this would necessitate repeating the presented argument for Forward-Backward splitting and for the modifications of FISTA suggested by \cite{Liang2018}.
-We feel that the extension to the primal-dual algorithm proposed by \cite{Chambolle2011} should also be possible where there is a classical bound of the form $\min_{n\leq N}\Func0(\varf0_n)+\Func0^*(\vvard0_n) \lesssim \frac{\norm{\varf0_0-\varf0^*}^2 + \norm{\vvard0_0-\vvard0^*}^2}{N}$.
-This has the same basic ingredients as FISTA although there is now the extra dual variable to account for.
-
-Another interesting outlook is to relax the requirement for $\func1$ to be smooth on the whole of $\spcf0\cap\F H$.
-An example where this is not the case is the dual problem to total variation denoising where we have
-$$ \Func0(\varf0) = \norm{\op{div}\varf0-\vdata0}^2 + \chi(\norm{\varf0}_\infty\leq \mu).$$
-The divergence operator is not bounded in $L^2$ but is on each subspace $\spcf0^n$. It is not clear if it is possible to incorporate this into FISTA without restarting each time the step-size changes.
+Other variants of FISTA, such as the `greedy' implementation used here or the traditional Forward-Backward algorithm, should also be receptive to the analysis performed here.
+Furthermore, it would also interesting to attempt to replicate this refinement argument to extend the primal-dual algorithm proposed by \citet{Chambolle2011} or the Douglas-Rachford algorithm proposed by \citet{Douglas1956}.
 
@@
 \newpage\appendix
-\section{Proofs for FISTA convergence}\label{app:ca: FISTA convergence}
-This section contains all of the statements and proofs of the results contained in \Cref{sec:ca: FISTA convergence}.
-
-\subsection{Proofs for Step 2}
-
-\begin{lemma}[\Cref{thm:ca: descent lemma}]\label{app:thm:ca: descent lemma}
-	\Paste{thm:ca: descent lemma}
-\end{lemma}
+\section{Proofs for FISTA convergence}\label{app: FISTA convergence}
+This section contains all of the statements and proofs of the results contained in \Cref{sec: FISTA convergence}.
+
+\subsection{Proofs for Step 3}
+
+\begin{theorem}[\Cref{thm: one step FISTA}]\label{app:thm: one step FISTA}
+	\Paste{thm: one step FISTA}
+	\begin{equation}
+		\vart1_{n}^2(\Func0(\varf0_{n}) - \Func0(\varf2_n)) - (\vart1_{n}^2-\vart1_{n})(\Func0(\varf0_{n-1})-\Func0(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.\label{app:eq: one-step FISTA}
+	\end{equation}
+\end{theorem}
 \begin{proof}
-	This is exactly the result of \cite[Lemma 1]{Chambolle2015} applied to the function $\varf0\mapsto\Func0(\Pi_n\varf0)$.
-\end{proof}
-
-\begin{theorem*}[\Cref{thm:ca: one step FISTA}]
-	\Paste{thm:ca: one step FISTA}
-	\begin{equation}
-		\vart1_{n}^2(\Func0(\varf0_{n}) - \Func0(\varf2_n)) - (\vart1_{n}^2-\vart1_{n})(\Func0(\varf0_{n-1})-\Func0(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.\label{app:eq:ca: one-step FISTA}
-	\end{equation}
-\end{theorem*}
-\begin{proof}
-	Modifying \cite[Theorem 2]{Chambolle2015}, for $n\geq1$ we apply \Cref{app:thm:ca: descent lemma} with $\bar{\varf0} = \bar{\varf0}_{n-1}$ and $\varf2 = (1-\frac{1}{\vart1_{n}})\varf0_{n-1} + \frac{1}{\vart1_{n}}\varf2_n$.
+	Modifying \cite[Theorem 2]{Chambolle2015}, for $n\geq1$ we apply \Cref{thm: descent lemma} with $\bar{\varf0} = \bar{\varf0}_{n-1}$ and $\varf2 = (1-\frac{1}{\vart1_{n}})\varf0_{n-1} + \frac{1}{\vart1_{n}}\varf2_n$.
 This gives
-	$$\Func0(\varf0_{n}) + \tfrac12\norm{\tfrac{1}{\vart1_{n}}\varf1_{n}-\tfrac{1}{\vart1_{n}}\varf2_n}^2 \leq \Func0\left((1-\tfrac{1}{\vart1_{n}})\varf0_{n-1}+\tfrac{1}{\vart1_{n}}\varf2_n\right) + \tfrac12\norm{\tfrac{1}{\vart1_{n}}\varf1_{n-1}-\tfrac{1}{\vart1_{n}}\varf2_n}^2.$$
+	\begin{equation}
+		\Func0(\varf0_{n}) + \tfrac12\norm{\tfrac{1}{\vart1_{n}}\varf1_{n}-\tfrac{1}{\vart1_{n}}\varf2_n}^2 \leq \Func0\left((1-\tfrac{1}{\vart1_{n}})\varf0_{n-1}+\tfrac{1}{\vart1_{n}}\varf2_n\right) + \tfrac12\norm{\tfrac{1}{\vart1_{n}}\varf1_{n-1}-\tfrac{1}{\vart1_{n}}\varf2_n}^2.
+	\end{equation}
 	By the convexity of $\Func0$, this reduces to
-	\begin{align*}
+	\begin{align}
 		\Func0(\varf0_{n}) - \Func0(\varf2_n) - (1-\tfrac{1}{\vart1_{n}})[\Func0(\varf0_{n-1})-\Func0(\varf2_n)] &\leq \tfrac1{2\vart1_{n}^2}\norm{\varf1_{n-1}-\varf2_n}^2 - \tfrac1{2\vart1_{n}^2}\norm{\varf1_{n}-\varf2_n}^2
 		\\ &= \tfrac1{2\vart1_{n}^2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \tfrac1{\vart1_{n}^2}\IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.
-	\end{align*}
+	\end{align}
 \end{proof}
 
-\begin{theorem}[\Cref{thm:ca: mini FISTA convergence}]\label{app:thm:ca: mini FISTA convergence}
-	\Paste{thm:ca: mini FISTA convergence}
-	\begin{multline}\label{app:eq:ca: FISTA inequality}
+\begin{theorem}[\Cref{thm: mini FISTA convergence}]\label{app:thm: mini FISTA convergence}
+	\Paste{thm: mini FISTA convergence}
+	\begin{multline}\label{app:eq: FISTA inequality}
 		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
@@
 \begin{proof}
-	\Cref{app:thm:ca: mini FISTA convergence} is just a summation of \eqref{app:eq:ca: one-step FISTA} over all $n=1,\ldots,N$.
+	\Cref{app:thm: mini FISTA convergence} is just a summation of \eqref{app:eq: one-step FISTA} over all $n=1,\ldots,N$.
 To see this: first add and subtract $\Func0(\varf0^*)$ to each term on the left-hand side to convert $\Func0$ to $\Func0_0$, then move $\Func0_0(\varf2_n)$ to the right-hand side.
-Now \eqref{app:eq:ca: one-step FISTA} becomes
-	$$ \vart1_n^2\Func0_0(\varf0_n) - (\vart1_n^2-\vart1_n)\Func0_0(\varf0_{n-1}) \leq \vart1_n\Func0_0(\varf2_n) + \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_n}^2\right] + \IP{\varf1_n-\varf1_{n-1}}{\varf2_n}.
-$$
+Now \eqref{app:eq: one-step FISTA} becomes
+	\begin{equation}
+		\vart1_n^2\Func0_0(\varf0_n) - (\vart1_n^2-\vart1_n)\Func0_0(\varf0_{n-1}) \leq \vart1_n\Func0_0(\varf2_n) + \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_n}^2\right] + \IP{\varf1_n-\varf1_{n-1}}{\varf2_n}.
+	\end{equation}
 	Summing this inequality from $n=1$ to $n=N$ gives
-	$$\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}(\underbrace{\vart1_n^2-\vart1_{n+1}^2+\vart1_{n+1}}_{=\rho_n})\Func0_0(\varf0_n) \leq \frac{\norm{\varf1_0}^2-\norm{\varf1_N}^2}{2} + \sum_{n=1}^N \vart1_n\Func0_0(\varf2_n)+\IP{\varf1_n-\varf1_{n-1}}{\varf2_n}.$$
+	\begin{equation}
+		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}(\underbrace{\vart1_n^2-\vart1_{n+1}^2+\vart1_{n+1}}_{=\rho_n})\Func0_0(\varf0_n) \leq \frac{\norm{\varf1_0}^2-\norm{\varf1_N}^2}{2} + \sum_{n=1}^N \vart1_n\Func0_0(\varf2_n)+\IP{\varf1_n-\varf1_{n-1}}{\varf2_n}.
+	\end{equation}
 	This is almost in the desired form, however, we would like to flip the roles of $\varf1_n$/$\varf2_n$ in the final inner product term. Re-writing the right-hand side gives
-	$$\sum_{n=1}^N\IP{\varf1_n-\varf1_{n-1}}{\varf2_n} = \IP{\varf1_N}{\varf2_N} - \IP{\varf1_0}{\varf2_0}+ \sum_{n=1}^N\IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.$$
-	Noting $\varf1_0=\varf0_0$, combining the previous two equations proves the statement of \Cref{app:thm:ca: mini FISTA convergence}.
+	\begin{equation}
+		\sum_{n=1}^N\IP{\varf1_n-\varf1_{n-1}}{\varf2_n} = \IP{\varf1_N}{\varf2_N} - \IP{\varf1_0}{\varf2_0}+ \sum_{n=1}^N\IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
+	\end{equation}
+	Noting that $\varf1_0=\varf0_0$, the previous two equations combine to prove the statement of \Cref{app:thm: mini FISTA convergence}.
 \end{proof}
@@
 \newpage\noindent The following lemma is used to produce a sharper estimate on sequences $\vart1_n$.
-\begin{lemma}\label{app:ca: tn upper bound}
+\begin{lemma}\label{app: tn upper bound}
 	If $\rho_n=\vart1_{n}^2-\vart1_{n+1}^2+\vart1_{n+1}\geq0$, $\vart1_n\geq 1$ for all $n\in\F N$ then $\vart1_n\leq n-1 +\vart1_1$.
@@
 	This is trivially true for $n=1$. Suppose true for $n-1$, the condition on $\rho_{n-1}$ gives
-	$$\vart1_n^2 -\vart1_n \leq \vart1_{n-1}^2 \leq (n-2+\vart1_1)^2 = (n-1+\vart1_1)^2 -2(n-1+\vart1_1) + 1.$$
-	Assuming the contradiction, if $\vart1_n> n-1+\vart1_1$ then we get $n-1+\vart1_1 < 1$ but $\vart1_1\geq 1$ so this becomes $n<1$ which completes the contradiction.
+	\begin{equation}
+		\vart1_n^2 -\vart1_n \leq \vart1_{n-1}^2 \leq (n-2+\vart1_1)^2 = (n-1+\vart1_1)^2 -2(n-1+\vart1_1) + 1.
+	\end{equation}
+	Assuming the contradiction, if $\vart1_n> n-1+\vart1_1$ then the above equation simplifies to $n-1+\vart1_1 < 1$. However, $\vart1_1\geq 1$ implying that $n<1$ which completes the contradiction.
 \end{proof}
 
-\begin{lemma}[\Cref{thm:ca: mini exponential FISTA convergence}]\label{app:thm:ca: mini exponential FISTA convergence}
-	\Paste{thm:ca: mini exponential FISTA convergence}
+\begin{lemma}[\Cref{thm: mini exponential FISTA convergence}]\label{app:thm: mini exponential FISTA convergence}
+	\Paste{thm: mini exponential FISTA convergence}
 \end{lemma}
 \begin{proof}
-	This is just a telescoping of the right-hand side of \eqref{app:eq:ca: FISTA inequality} with the introduction of $n_k$ and simplification $\varf2_n = \tilde{\varf2}_k$,
-	\begin{multline*}
+	This is just a telescoping of the right-hand side of \eqref{app:eq: FISTA inequality} with the introduction of $n_k$ and simplification $\varf2_n = \tilde{\varf2}_k$,
+	\begin{multline}
 		\tfrac12\norm{\varf2_N}^2 + \sum^N_{n=1} \vart1_n\Func0_0(\Pi_n\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n} = \tfrac12\norm{\tilde{\varf2}_K}^2 + \sum_{n=n_K}^N\vart1_n\Func0_0(\tilde{\varf2}_K)
@@
 		+ \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}.
-	\end{multline*}
-	\begin{samepage}
-		By \Cref{app:ca: tn upper bound}, $\vart1_n\leq n$ so we can further simplify
+	\end{multline}
+	By \Cref{app: tn upper bound}, $\vart1_n\leq n$ so we can further simplify
 	$$\sum_{n=\vars3}^{\vars4-1}\vart1_n \leq \sum_{n=\vars3}^{\vars4-1}n = (\vars4-\vars3)\frac{\vars4-1+\vars3}{2} \leq \frac{\vars4^2-\vars3^2}{2}$$
 	to get the required bound.
-	\end{samepage}
 \end{proof}
 
-\subsection{Proof for Step 3}
-\begin{lemma}[\Cref{thm:ca: sufficiently fast}]\label{app:thm:ca: sufficiently fast}
-	\Paste{thm:ca: sufficiently fast}
+\subsection{Proof for Step 4}
+\begin{lemma}[\Cref{thm: sufficiently fast}]\label{app:thm: sufficiently fast}
+	\Paste{thm: sufficiently fast}
 \end{lemma}
@@
 \begin{proof}
-	Inserting the assumed rates into \Cref{app:thm:ca: mini exponential FISTA convergence} gives
-	$$	\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 \lesssim \vars3_{\Varf0}^{2K} + (N+1)^2\vars3_{\Func0}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\Func0}^{-k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + \vars3_{\Varf0}^{2k}.$$
+	Inserting the assumed rates into \Cref{app:thm: mini FISTA convergence} gives
+	\begin{equation}
+		\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 \lesssim \vars3_{\Varf0}^{2K} + (N+1)^2\vars3_{\Func0}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\Func0}^{-k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + \vars3_{\Varf0}^{2k}.
+	\end{equation}
 	Each case now needs its own induction. When $\vars3_{\Varf0}>1$ we simplify the inequality to 
-	\begin{align*}
+	\begin{align}
 		\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim \vars3_{\Varf0}^{2K} + \vars3_{\Varf0}^{2K+2} + \sum_{k=1}^{K}\vars3_{\Varf0}^{2k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}
 		\\&\leq C_1\left(\vars3_{\Varf0}^{2K+2} + \frac{\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1} + \sum_{k=1}^{K}\vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\right).
-	\end{align*}
+	\end{align}
 	for some $C_1$ sufficiently large. Assume $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2\vars3_{\Varf0}^k$ for $k\leq K$, then for $N=n_{K+1}-1$ we have
-	$$\tfrac12\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}^2 \leq \frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right).$$
+	\begin{equation}
+		\tfrac12\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}^2 \leq \frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right).
+	\end{equation}
 	If $C_2$ is sufficiently large, then $\frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right) \leq \tfrac12C_2^2\vars3_{\Varf0}^{2K+2}$ which completes the induction.
@@
 Assuming $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2$ for $k\leq K$, there exists $C_1>0$ such that
-	\begin{align*}
+	\begin{align}
 		\vart1_{N+1}^2\Func0_0(\varf0_{N+1}) + \tfrac12\norm{\varf1_{N+1}-\tilde{\varf2}_{K}}^2 &\leq C_1 + \max_{k\leq K}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}
 		\\&\leq C_1 + C_2.
-	\end{align*}
+	\end{align}
 	If $C_2$ is sufficiently large then $C_1 + C_2 \leq \tfrac14C_2^2$ which completes the second induction. This confirms $t_N^2\Func0_0(\varf0_N) \leq \tfrac14C_2^2$ is bounded uniformly.
@@
 
-\subsection{Proof for Step 4}
-\begin{lemma}[\Cref{thm:ca: sufficiently slow}]\label{app:thm:ca: sufficiently slow}
-	\Paste{thm:ca: sufficiently slow}
+\subsection{Proof for Step 5}
+\begin{lemma}[\Cref{thm: sufficiently slow}]\label{app:thm: sufficiently slow}
+	\Paste{thm: sufficiently slow}
 \end{lemma}
@@
 	The proof is direct computation,
-	$$ \log N^2 \geq \log C + K\left(\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2\right)$$ 
+	\begin{equation}
+		\log N^2 \geq \log C + K\left(\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2\right)
+	\end{equation}
 	which leads to
-	\begin{align*}
+	\begin{align}
 		\vars3_{\Varf0}^{2K} & = \exp(K\log \vars3_{\Varf0}^2)
@@
 		\\&\lesssim N^{2\epsilon}
-	\end{align*}
+	\end{align}
 	as required.
@@
 
-\begin{theorem}[\Cref{thm:ca: exponential FISTA convergence}]
-	\Paste{thm:ca: exponential FISTA convergence}
+\begin{theorem}[\Cref{thm: exponential FISTA convergence}]
+	\Paste{thm: exponential FISTA convergence}
 \end{theorem}
 \begin{proof}
-	If the conditions of this theorem are satisfied, then so are \Cref{app:thm:ca: mini exponential FISTA convergence,app:thm:ca: sufficiently fast,app:thm:ca: sufficiently slow}.
-The final result is just the conclusion of \Cref{app:thm:ca: sufficiently slow}.
+	If the conditions of this theorem are satisfied, then so are \Cref{app:thm: mini exponential FISTA convergence,app:thm: sufficiently fast,app:thm: sufficiently slow}.
+The final result is just the conclusion of \Cref{app:thm: sufficiently slow}.
 \end{proof}
 
-\subsection{Proofs for Step 5}
-\begin{theorem}[\Cref{thm:ca: stronger exponential FISTA convergence}]\label{app:thm:ca: stronger exponential FISTA convergence}
-	\Paste{thm:ca: stronger exponential FISTA convergence}
+\subsection{Proofs for Step 6}
+\begin{theorem}[\Cref{thm: stronger exponential FISTA convergence}]\label{app:thm: stronger exponential FISTA convergence}
+	\Paste{thm: stronger exponential FISTA convergence}
 \end{theorem}
 \begin{proof}
-	To apply \Cref{app:thm:ca: sufficiently fast}, we need
-	$$n_k^2\lesssim \splitln{(\vars3_{\Func0}\vars3_{\Varf0}^2)^k}{\vars3_{\Varf0}>1}{k^{-2}\vars3_{\Func0}^k}{\vars3_{\Varf0}=1}, \qquad \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^{k}, \qquad \text{ and } \Func0_0(\tilde{\varf2}_k)\lesssim \vars3_{\Func0}^{-k}$$
+	To apply \Cref{app:thm: sufficiently fast}, we need
+	\begin{equation}
+		n_k^2\lesssim \splitln{(\vars3_{\Func0}\vars3_{\Varf0}^2)^k}{\vars3_{\Varf0}>1}{k^{-2}\vars3_{\Func0}^k}{\vars3_{\Varf0}=1}, \qquad \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^{k}, \qquad \text{ and } \Func0_0(\tilde{\varf2}_k)\lesssim \vars3_{\Func0}^{-k}
+	\end{equation}
 	and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$ when $\vars3_{\Varf0}=1$. The only one which is not directly assumed is easily verified,
-	$$\Func0_0(\tilde{\varf2}_k) = \min_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0) \leq\Func0_0(\varf0_{n_k-1}) \lesssim \vars3_{\Func0}^{-k}.$$
-	Therefore, the result of \Cref{app:thm:ca: sufficiently fast} gives
-	$$\Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{\vart1_N^2} \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}.$$
+	\begin{equation}
+		\Func0_0(\tilde{\varf2}_k) = \min_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0) \leq\Func0_0(\varf0_{n_k-1}) \lesssim \vars3_{\Func0}^{-k}.
+	\end{equation}
+	Therefore, the result of \Cref{app:thm: sufficiently fast} gives
+	\begin{equation}
+		\Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{\vart1_N^2} \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}.
+	\end{equation}
 	In the case $\vars3_{\Varf0}=1$, this is already the optimal rate and therefore sharp.
@@
 
-	\begin{samepage}
 	If we fix $N^2\lesssim (\vars3_{\Func0}\vars3_{\Varf0}^2)^k$, then
-		$$\min_{n\leq N} \Func0_0(\varf0_n)\lesssim \splitln{\vars3_{\Func0}^{-k}}{N>n_k}{ \sfrac{\vars3_{\Varf0}^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_{\Varf0}^{2k},\vars3_{\Varf0}^{2k}) \lesssim N^{-2(1-\epsilon)}$$
+	\begin{equation}
+		\min_{n\leq N} \Func0_0(\varf0_n)\lesssim \splitln{\vars3_{\Func0}^{-k}}{N>n_k}{ \sfrac{\vars3_{\Varf0}^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_{\Varf0}^{2k},\vars3_{\Varf0}^{2k}) \lesssim N^{-2(1-\epsilon)}
+	\end{equation}
 	as required.
-	\end{samepage}
 \end{proof}
 
-\begin{lemma}[\Cref{thm:ca: practical refinement criteria}]
-	\Paste{thm:ca: practical refinement criteria}
+\begin{lemma}[\Cref{thm: practical refinement criteria}]\label{app:thm: practical refinement criteria}
+	\Paste{thm: practical refinement criteria}
 \end{lemma}
@@
 \begin{proof}
-	The proof is simply to justify that the conditions of \Cref{app:thm:ca: stronger exponential FISTA convergence} are met for all refinement criteria described here.
+	The proof is simply to justify that the conditions of \Cref{app:thm: stronger exponential FISTA convergence} are met for all refinement criteria described here.
 $\norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k$ is enforced at every step and condition (2) guarantees the back-stop condition on $n_k$.
 
-	To complete the requirements of \Cref{app:thm:ca: stronger exponential FISTA convergence}, we first need to show inductively that $\Func0_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\Func0}^{-k}$, then it follows that $\Func0_0(\varf0_{n_k-1})\leq C\vars3_{\Func0}^{-k}$.
+	To complete the requirements of \Cref{app:thm: stronger exponential FISTA convergence}, we first need to show inductively that $\Func0_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\Func0}^{-k}$, then it follows that $\Func0_0(\varf0_{n_k-1})\leq C\vars3_{\Func0}^{-k}$.
 To be explicit, when $\Func0$ has bounded sublevel sets, assume that the bound for $\{\varf0\in\F H\st \Func0(\varf0)\leq \Func0(\varf0_0)\}$ is $R>0$.
@@
 	In each case, with $C$ sufficiently large, the induction holds.
-Now we can return to the precise condition of \Cref{app:thm:ca: stronger exponential FISTA convergence}, $\Func0_0(\varf0_{n_k-1}) \leq C'\vars3_{\Func0}^{-k}$.
+Now we can return to the precise condition of \Cref{app:thm: stronger exponential FISTA convergence}, $\Func0_0(\varf0_{n_k-1}) \leq C'\vars3_{\Func0}^{-k}$.
 Assume true for $k-1$.
@@
 	\end{itemize}
-	This completes the requirements of \Cref{app:thm:ca: stronger exponential FISTA convergence}, therefore also this proof.
+	This completes the requirements of \Cref{app:thm: stronger exponential FISTA convergence}, therefore also this proof.
 \end{proof}
 
-\section{Proof of \texorpdfstring{\Cref{thm:ca: generic a_U and a_E}}{rates for general finite element spaces}}\label{app:ca: generic a_U and a_E}
+\section{Proof of \texorpdfstring{\Cref{thm: generic a_U and a_E}}{rates for general finite element spaces}}\label{app: generic a_U and a_E}
 \todo{This whole section is unnecessary for the numerics.
@@
 It is quite a long proof for that level of reward\ldots}
-The proof of \Cref{thm:ca: generic a_U and a_E} is the result of the following three lemmas.
-The first, \Cref{app:thm:ca: generic a_U bound}, is a general quantification of the equivalence between $L^q$ and $L^2$ norms on finite dimensional sub-spaces.
+The proof of \Cref{thm: generic a_U and a_E} is the result of the following three lemmas.
+The first, \Cref{app:thm: generic a_U bound}, is a general quantification of the equivalence between $L^q$ and $L^2$ norms on finite dimensional sub-spaces.
 A special case occurs when $q=1$ because the dual norm is a supremum rather than an integral.
-In \Cref{app:thm:ca: specific a_U bound}, this locality is exploited by finite element spaces, which we assumed had a basis with local support.
-\Cref{app:thm:ca: generic a_E bound} then performs the computations for the $\vars3_{\Func0}$ constant depending on the smoothness properties of $\Func0$.
-
-\begin{lemma}\label{app:thm:ca: generic a_U bound}
+In \Cref{app:thm: specific a_U bound}, this locality is exploited by finite element spaces, which we assumed had a basis with local support.
+\Cref{app:thm: generic a_E bound} then performs the computations for the $\vars3_{\Func0}$ constant depending on the smoothness properties of $\Func0$.
+
+\begin{lemma}\label{app:thm: generic a_U bound}
 	Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
@@
 		\item otherwise, if $e_j\in \spcf0^*$, then
-		$$\norm{\Pi\varf2} \leq \sqrt{\op{dim}(\tilde{\spcf0})}\max_j\Norm{e_j}_*\Norm{\varf2},$$
+		\begin{equation}
+			\norm{\Pi\varf2} \leq \sqrt{\op{dim}(\tilde{\spcf0})}\max_j\Norm{e_j}_*\Norm{\varf2},
+		\end{equation}
 		\item otherwise, if $e_j\in L^\infty(\Domain)$ and $ |\{j:e_j(\vvarx0)\neq 0\}|\leq C$ for almost all $\vvarx0\in\Domain$, then
-		$$\norm{\Pi\varf2} \lesssim \sqrt C\max_j\norm{e_j}_{L^\infty}\Norm{\varf2} $$
+		\begin{equation}
+			\norm{\Pi\varf2} \lesssim \sqrt C\max_j\norm{e_j}_{L^\infty}\Norm{\varf2}
+		\end{equation}
 	\end{itemize}
@@
 	The first statement for $q\geq 2$ is from H\"older's inequality combined with the fact that compact domains have finite volume,
-	$$\norm{\Pi\varf2}^2 \leq \norm{\varf2}^2 = \norm{\varf2}_2^2 = \norm{\varf2^2}_1 \lesssim \norm{\varf2}_q^2 \lesssim \Norm{\varf2}^2.$$
+	\begin{equation}
+		\norm{\Pi\varf2}^2 \leq \norm{\varf2}^2 = \norm{\varf2}_2^2 = \norm{\varf2^2}_1 \lesssim \norm{\varf2}_q^2 \lesssim \Norm{\varf2}^2.
+	\end{equation}
 	The remaining statements come from the equivalence of norms on finite dimensional spaces. Note that
-	$$\norm{\Pi\varf2} = \frac{\IP{\Pi\varf2}{\Pi\varf2}}{\norm{\Pi\varf2}} = \frac{\IP{\Pi\varf2}{\varf2}}{\norm{\Pi\varf2}} \leq \frac{\Norm{\Pi\varf2}_*}{\norm{\Pi\varf2}}\Norm{\varf2},$$
+	\begin{equation}
+		\norm{\Pi\varf2} = \frac{\IP{\Pi\varf2}{\Pi\varf2}}{\norm{\Pi\varf2}} = \frac{\IP{\Pi\varf2}{\varf2}}{\norm{\Pi\varf2}} \leq \frac{\Norm{\Pi\varf2}_*}{\norm{\Pi\varf2}}\Norm{\varf2},
+	\end{equation}
 	therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\tilde{\spcf0}$. Switching to the given basis, for $\varf0 = \sum_j \varx3_je_j$ we have
-	\begin{align*}
+	\begin{align}
 		\norm{\varf0}^2 &= \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} \varx3_j^2 = \norm{\vvarx3}_{\ell^2}^2,
@@
 		\\\implies \frac{\Norm{\varf0}_*}{\norm{\varf0}} &\leq \max_j\Norm{e_j}_*\frac{\norm{\vvarx3}_{\ell^1}}{\norm{\vvarx3}_{\ell^2}} \leq \max_j\Norm{e_j}_*\sqrt{\op{dim}(\tilde{\spcf0})}.
-	\end{align*}
+	\end{align}
 	Alternatively, we can use the inequality
-	$$\norm{\Pi\varf2} = \frac{\IP{\Pi\varf2}{\varf2}}{\norm{\Pi\varf2}} \leq \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\norm{\varf2}_1\lesssim  \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\norm{\varf2}_q \lesssim \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\Norm{\varf2}.$$
+	\begin{equation}
+		\norm{\Pi\varf2} = \frac{\IP{\Pi\varf2}{\varf2}}{\norm{\Pi\varf2}} \leq \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\norm{\varf2}_1\lesssim  \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\norm{\varf2}_q \lesssim \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\Norm{\varf2}.
+	\end{equation}
 	This simplifies the equivalence constant because for any $\varf0 = \sum \varx3_je_j$ and $\mu>1$, there exists a set of points $\vvarx0\in\Domain$ with non-zero measure such that $\norm{\varf0}_\infty\leq \mu|\varf0(\vvarx0)|$.
 This gives
-	\begin{align*}
+	\begin{align}
 		\norm{\varf0}^2 &= \sum \varx3_j^2 \geq \sum_{e_j(\vvarx0)\neq 0} \varx3_j^2,
@@
 		\\\implies \frac{\norm{\varf0}_\infty}{\norm{\varf0}} &\leq \mu\max_j\norm{e_j}_\infty\sqrt{C}.
-	\end{align*}
+	\end{align}
 	This inequality holds for all $\mu>1$ therefore also for $\mu=1$.
@@
 
-\begin{lemma}\label{app:thm:ca: specific a_U bound}
+\begin{lemma}\label{app:thm: specific a_U bound}
 	Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
@@
 \begin{proof}
-	Most of the conditions of \Cref{app:thm:ca: generic a_U bound} are already satisfied.
+	Most of the conditions of \Cref{app:thm: generic a_U bound} are already satisfied.
 Denote $C=\op{dim}(\tilde{\spcf0^0})$ and $\{e_j\st j\in[C]\}$ the standard orthonormal basis of $\tilde{\spcf0}^0$.
-The scaling properties of $\meshsize$-refining finite element spaces guarantee that the value of $C$ satisfies the conditions of \Cref{app:thm:ca: generic a_U bound} and a basis of $\tilde{\spcf0}^k$ is given by
-	$$ \left\{\vvarx0\mapsto\varf0_j(\vars0^{i,k}\vvarx0+\vvars1^{i,k}) \qquad\st\qquad i=1,\ldots,|\F M^k|,\ j=1,\ldots,C\right\}$$
+The scaling properties of $\meshsize$-refining finite element spaces guarantee that the value of $C$ satisfies the conditions of \Cref{app:thm: generic a_U bound} and a basis of $\tilde{\spcf0}^k$ is given by
+	\begin{equation}
+		\left\{\vvarx0\mapsto\varf0_j(\vars0^{i,k}\vvarx0+\vvars1^{i,k}) \qquad\st\qquad i=1,\ldots,|\F M^k|,\ j=1,\ldots,C\right\}
+	\end{equation}
 	for some $\vars0^{i,k}\in\R^{d\times d}$, and $\vvars1^{i,k}\in\R^d$ such that $0<\op{det}(\vars0^{i,k})\lesssim \meshsize^{-kd}$.
 
-	We now compute the scaling constant in \Cref{app:thm:ca: generic a_U bound}:
-	$$ \frac{\norm{\varf0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}_\infty}{\norm{\varf0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}} = \frac{\norm{\varf0_j}_\infty}{\sqrt{\int_{\domain_i^k} e_j(\vars0^{i,k} \vvarx0+\vvars1^{i,k})^2d\vvarx0}} = \frac{\norm{\varf0_j}_\infty}{\sqrt{\op{det}(\vars0^{i,k})^{-1}}} \lesssim \meshsize^{-\frac{kd}{2}}.$$
-	This value is independent of $j$ and gives the desired bound as a result of \Cref{app:thm:ca: generic a_U bound}.
+	We now compute the scaling constant in \Cref{app:thm: generic a_U bound}:
+	\begin{equation}
+		\frac{\norm{\varf0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}_\infty}{\norm{\varf0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}} = \frac{\norm{\varf0_j}_\infty}{\sqrt{\int_{\domain_i^k} e_j(\vars0^{i,k} \vvarx0+\vvars1^{i,k})^2d\vvarx0}} = \frac{\norm{\varf0_j}_\infty}{\sqrt{\op{det}(\vars0^{i,k})^{-1}}} \lesssim \meshsize^{-\frac{kd}{2}}.
+	\end{equation}
+	This value is independent of $j$ and gives the desired bound as a result of \Cref{app:thm: generic a_U bound}.
 \end{proof}
 
-\begin{lemma}\label{app:thm:ca: generic a_E bound}
+\begin{lemma}\label{app:thm: generic a_E bound}
 	Let $(\tilde{\spcf0}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\varf2}^k=\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$.
@@
 	Each statement is by definition, observe
-	\begin{gather*}
+	\begin{gather}
 		\Func0(\varf2)-\Func0(\varf0^*) \leq \op{Lip}(\Func0)\Norm{\varf2-\varf0^*},
@@
 		\\\Func0(\varf2)-\Func0(\varf0^*) \leq \func1(\varf2)-\func1(\varf0^*) \leq \op{Lip}(\func1)\Norm{\varf2-\varf0^*}.
-	\end{gather*}
+	\end{gather}
 	Minimising over the right-hand side over $\varf2$ and substituting the definition of order gives the desired result.
@@
 \section{Operator norms for numerical examples}
-\begin{theorem}[\Cref{thm:ca: norm bound examples}]\label{app:thm:ca: norm bound examples}
-	\Paste{thm:ca: norm bound examples}
+\begin{theorem}[\Cref{thm: norm bound examples}]\label{app:thm: norm bound examples}
+	\Paste{thm: norm bound examples}
 \end{theorem}
@@
 \begin{proof}[Proof case 1:]
-	From \Cref{thm:ca: norm bound L2} we have 
-	$$(\A\A^*)_{i,j} = \IP{\1_{\F{\Varx0}_i}}{\1_{\F{\Varx0}_j}} = |\F{\Varx0}_i\cap \F{\Varx0}_j| = \splitln{|\F{\Varx0}_i|}{i=j}{0}{i\neq j}.$$
+	From \Cref{thm: norm bound L2} we have 
+	\begin{equation}
+		(\A\A^*)_{i,j} = \IP{\1_{\F{\Varx0}_i}}{\1_{\F{\Varx0}_j}} = |\F{\Varx0}_i\cap \F{\Varx0}_j| = \splitln{|\F{\Varx0}_i|}{i=j}{0}{i\neq j}.
+	\end{equation}
 	Therefore, $\A\A^*$ is a diagonal matrix and $\norm{\A\A^*}_{\ell^2\to\ell^2} = \max_j |\F{\Varx0}_j|$ completes the result.
@@
 	$\vard1_j$ are not necessarily orthogonal however $|\IP{\vard1_i}{\vard1_j}|\leq 1$ therefore we can estimate
-	$$\norm{\A\A^*}_{\ell^2\to\ell^2} \leq \norm{\A\A^*}_{\ell^\infty\to\ell^\infty} \leq m.$$
-	Now looking to apply \Cref{thm:ca: norm bound smoothness}, note $\norm{\nabla^k\vard1_j}_\infty \leq \Vars3^k$, therefore
-	\begin{align*}
+	\begin{equation}
+		\norm{\A\A^*}_{\ell^2\to\ell^2} \leq \norm{\A\A^*}_{\ell^\infty\to\ell^\infty} \leq m.
+	\end{equation}
+	Now looking to apply \Cref{thm: norm bound smoothness}, note $\norm{\nabla^k\vard1_j}_\infty \leq \Vars3^k$, therefore
+	\begin{align}
 		|\A^*\vvarx3|_{C^k}&\leq \Vars3^k m^{\frac1{q^*}}\norm{\vvarx3}_q = \Vars3^k m^{1-\frac1{q}}\norm{\vvarx3}_q,
 		\\|\A^*|_{\ell^2\to C^k} &\leq \Vars3^k \min_{q\in[1,\infty]}m^{1-\frac1q}\sqrt{m}^{\max(0,2-q)} = \sqrt{m}\Vars3^k.
-	\end{align*}
+	\end{align}
 \end{proof}
 
-\begin{proof}[Proof of asymptotic case 3:]
-	In the Gaussian case, we build our approximations around the idea that sums of Gaussians on a regular grid look like a discretised integral.
+%\begin{proof}[Proof of asymptotic case 3:]
+%	In the Gaussian case, we build our approximations around the idea that sums of Gaussians on a regular grid look like a discretised integral.
 The first example can be used to approximate the operator norm.
 Computing the inner products gives
-	\\\parbox{\linewidth+5pt}{\begin{multline*}
+%	\begin{multline}
+%		\IP{\vard1_i}{\vard1_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vvarx0-\vvarx0_i|^2}{2\sigma^2}-\tfrac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right) \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right)
+%		\\= (4\pi\sigma^2)^{-\frac d2} \exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right).
+%	\end{multline}
+%	Estimating the operator norm,
+%	\begin{align}
+%		\norm{\A\A^*}_{\ell^2\to\ell^2}&\leq \norm{\A\A^*}_{\ell^\infty\to\ell^\infty} = \max_{i\in[m]} \sum_{j=1}^m |\IP{\vard1_i}{\vard1_j}| 
+%		\\&= \max_{i\in[m]}(4\pi\sigma^2)^{-\frac d2}\sum_{j_1,\ldots,j_d\in[\hat m]} \exp\left(-\frac{(j_1\Delta-i_1\Delta)^2+\ldots+(j_d\Delta-i_d\Delta)^2}{4\sigma^2}\right)
+%		\\&\leq (4\pi\sigma^2)^{-\frac d2}\sum_{\vec j\in\F Z^d\cap[-\hat m,\hat m]^d} \exp\left(-\frac{(j_1\Delta)^2+\ldots+(j_d\Delta)^2}{4\sigma^2}\right)
+%		\\&= \frac{(4\pi)^{-\frac d2}}{\Delta^d}\sum_{\vec j\in\F Z^d\cap[-\hat m,\hat m]^d} \exp\left(-\frac14\left|\vec j\frac{\Delta}{\sigma}\right|^2\right)\frac{\Delta^d}{\sigma^d}
+%		\\&\sim \frac{(4\pi\sigma^2)^{-\frac d2}}{\Delta^d}\int_{\R^d} \exp\left(-\tfrac{|\vvarx0|^2}{4\sigma^2}\right) \quad = \Delta^{-d}.
+%	\end{align}
+%	This is a nice approximation because it depends only on $\Delta$, overcoming the $\frac1\sigma$ scaling.
+To convert this into an upper bound, we just compute the sum explicitly.
+In particular, as the sum factorises over dimensions,
+%	$$\norm{\A\A^*}_{\ell^2\to\ell^2} \leq (4\pi\sigma^2)^{-\frac d2}\left(\sum_{j=-\hat m,\ldots, \hat m}\exp\left(-\tfrac{\Delta^2}{4\sigma^2}j^2\right)\right)^d.$$
+%	Applying the same ideas to \Cref{thm: norm bound smoothness}, note
+%	$$\begin{array}{rll}
+%			\displaystyle |\vard1_j(\vvarx0)| &\displaystyle= \left|\vard1_j(\vvarx0)\right| &\displaystyle = (2\pi\sigma^2)^{-\frac d2}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
+%			\\\displaystyle |\nabla\vard1_j(\vvarx0)| &\displaystyle= \left|\frac{\vvarx0-\vvarx0_j}{\sigma^2}\vard1_j(\vvarx0)\right| &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma}\frac{|\vvarx0-\vvarx0_j|}{\sigma}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
+%			\\|\nabla^2\vard1_j(\vvarx0)| &\displaystyle =\left|\frac1{\sigma^2} + \frac{(\vvarx0-\vvarx0_j)(\vvarx0-\vvarx0_j)^\top }{\sigma^4}\right|\vard1_j(\vvarx0) &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma^2}\left(1+\frac{|\vvarx0-\vvarx0_j|^2}{\sigma^2}\right)\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right).
+%	\end{array}$$
+%	With the substitution $\vvarx0=\frac{\Delta}{\sigma}\vec j$, the asymptotic bounds on these are clear:
+%	\begin{align*}
+%		\sum_{\vec j\in[\hat m]^d} |\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim (2\pi\sigma^2)^{-\frac{dq^*}{2}}\frac{\sigma^d}{\Delta^d}\int_{\R^d}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right),
+%		\\\sum_{\vec j\in[\hat m]^d} |\nabla\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma}\frac{\sigma^d}{\Delta^d}\int_{\R^d}|\vvarx0|^{q^*}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right),
+%		\\\sum_{\vec j\in[\hat m]^d} |\nabla^2\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^2}\frac{\sigma^d}{\Delta^d}\int_{\R^d}(1+|\vvarx0|^2)^{q^*}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right).
+%	\end{align*}
+%\end{proof}
+
+\begin{proof}[Proof case 3:]
+	In the Gaussian case, we build our approximations around the idea that sums of Gaussians should converge very quickly.
+The first example can be used to approximate the operator norm.
+Computing the inner products gives
+	\begin{multline}
 		\IP{\vard1_i}{\vard1_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vvarx0-\vvarx0_i|^2}{2\sigma^2}-\tfrac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right) \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right)
 		\\= (4\pi\sigma^2)^{-\frac d2} \exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right).
-	\end{multline*}}
+	\end{multline}
 	Estimating the operator norm,
-	\\{\centering\resizebox{.9\textwidth}{!}{\parbox{\textwidth}{\begin{align*}
+	\begin{align}
 		\norm{\A\A^*}_{\ell^2\to\ell^2}&\leq \norm{\A\A^*}_{\ell^\infty\to\ell^\infty} = \max_{i\in[m]} \sum_{j=1}^m |\IP{\vard1_i}{\vard1_j}| 
@@
 		\\&\leq (4\pi\sigma^2)^{-\frac d2}\sum_{\vec j\in\F Z^d\cap[-\hat m,\hat m]^d} \exp\left(-\frac{(j_1\Delta)^2+\ldots+(j_d\Delta)^2}{4\sigma^2}\right)
-					\\&= \frac{(4\pi)^{-\frac d2}}{\Delta^d}\sum_{\vec j\in\F Z^d\cap[-\hat m,\hat m]^d} \exp\left(-\frac14\left|\vec j\frac{\Delta}{\sigma}\right|^2\right)\frac{\Delta^d}{\sigma^d}
-					\\&\sim \frac{(4\pi\sigma^2)^{-\frac d2}}{\Delta^d}\int_{\R^d} \exp\left(-\tfrac{|\vvarx0|^2}{4\sigma^2}\right) \quad = \Delta^{-d}.
-	\end{align*}}}}
-	\\This is a nice approximation because it depends only on $\Delta$, overcoming the $\frac1\sigma$ scaling.
-To convert this into an upper bound, we just compute the sum explicitly.
-In particular, as the sum factorises over dimensions,
-	$$\norm{\A\A^*}_{\ell^2\to\ell^2} \leq (4\pi\sigma^2)^{-\frac d2}\left(\sum_{j=-\hat m,\ldots, \hat m}\exp\left(-\tfrac{\Delta^2}{4\sigma^2}j^2\right)\right)^d.$$
-	Applying the same ideas to \Cref{thm:ca: norm bound smoothness}, note
-	$$\begin{array}{rll}
-			\displaystyle |\vard1_j(\vvarx0)| &\displaystyle= \left|\vard1_j(\vvarx0)\right| &\displaystyle = (2\pi\sigma^2)^{-\frac d2}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
-			\\\displaystyle |\nabla\vard1_j(\vvarx0)| &\displaystyle= \left|\frac{\vvarx0-\vvarx0_j}{\sigma^2}\vard1_j(\vvarx0)\right| &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma}\frac{|\vvarx0-\vvarx0_j|}{\sigma}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
-			\\|\nabla^2\vard1_j(\vvarx0)| &\displaystyle =\left|\frac1{\sigma^2} + \frac{(\vvarx0-\vvarx0_j)(\vvarx0-\vvarx0_j)^\top }{\sigma^4}\right|\vard1_j(\vvarx0) &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma^2}\left(1+\frac{|\vvarx0-\vvarx0_j|^2}{\sigma^2}\right)\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right).
-	\end{array}$$
-	With the substitution $\vvarx0=\frac{\Delta}{\sigma}\vec j$, the asymptotic bounds on these are clear:
-	\begin{align*}
-		\sum_{\vec j\in[\hat m]^d} |\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim (2\pi\sigma^2)^{-\frac{dq^*}{2}}\frac{\sigma^d}{\Delta^d}\int_{\R^d}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right),
-		\\\sum_{\vec j\in[\hat m]^d} |\nabla\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma}\frac{\sigma^d}{\Delta^d}\int_{\R^d}|\vvarx0|^{q^*}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right),
-		\\\sum_{\vec j\in[\hat m]^d} |\nabla^2\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^2}\frac{\sigma^d}{\Delta^d}\int_{\R^d}(1+|\vvarx0|^2)^{q^*}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right).
-	\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of precise case 3:]
-	In the asymptotic case we have shown
+		\\&= \left[(4\pi\sigma^2)^{-\frac 12}\sum_{j=-\hat m}^{\hat m} \exp\left(-\frac{\Delta^2j^2}{4\sigma^2}\right)\right]^d.
+	\end{align}
+	This is a nice approximation because it factorises simply over dimensions.
+	Applying the results from \Cref{thm: norm bound smoothness}, note
 	$$\begin{array}{rll}
@@
 
-	\begin{lemma}\label{app:ca: exp sum bound}
+	\begin{lemma}\label{app: exp sum bound}
 		Suppose $q>0$. If the polynomial $p(|\vvarx0|) = \sum p_k|\vvarx0|^k$ has non-negative coefficients and $\vvarx0\in[-m,m]^d$, then
@@
 
-	Now, continuing the proof of \Cref{app:thm:ca: norm bound examples}, for $\hat m=\sqrt[d]{m}$, $\delta=\frac{\sqrt{d}}{2}$ and $J=\{\vec{j}\in\F Z^d \st \norm{\vec{j}}_{\ell^\infty}\leq 2\hat m\}$, \Cref{app:ca: exp sum bound} bounds
+	Now, continuing the proof of \Cref{app:thm: norm bound examples}, for $\hat m=\sqrt[d]{m}$, $\delta=\frac{\sqrt{d}}{2}$ and $J=\{\vec{j}\in\F Z^d \st \norm{\vec{j}}_{\ell^\infty}\leq 2\hat m\}$, \Cref{app: exp sum bound} bounds
 	\begin{align*}

### 2021-01-07 paper.tex
Update bibliography

@@
 \citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$ when $u^*\in \F H$ is finite dimensional and \cite{Chambolle2015} extended this result to the general Hilbert space setting.
-Many further works have gone on to demonstrate even faster practical convergence rates for slightly modified variants of FISTA in specific scenarios \citep{some references}.
+Many further works have gone on to demonstrate even faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.
 
@@
 For \Cref{step: step 1 stability} of \Cref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for \Cref{alg: refining FISTA}.
-The proofs in this step follow the classical arguments of \citep{Beck2009,Chambolle2015} very closely.
+The proofs in this step follow the classical arguments of \citet{Beck2009,Chambolle2015} very closely.
 
@@
 \end{lemma}
-\noindent This is exactly the result of \citep{Chambolle2015} applied to the function $\varf0\mapsto\Func0(\Pi_n\varf0)$.
+\noindent This is exactly the result of \citet{Chambolle2015} applied to the function $\varf0\mapsto\Func0(\Pi_n\varf0)$.
 Applying \Cref{thm: descent lemma} to the iterates from \Cref{alg: refining FISTA} gives a more explicit inequality.
@@
 As a special case, note that if $\vars3_{\Varf0}=1$ then \Cref{thm: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate.
-This is in fact a special case of \citep{Aujol2015}.
+This is in fact a special case of \citet{Aujol2015}.
 If $\varf0^*\in\F H$ then it is not possible to refine `too quickly' and the following lemma is not needed.
@@
 
-The work of \citep{Duval2017a,Poon2018} and many others characterise the support of $\varf0^*$ very precisely.
+The work of \citet{Duval2017a,Poon2018} and many others characterise the support of $\varf0^*$ very precisely.
 In particular, the support is at most $m$ distinct points and are a subset of $\{ \vvarx0\in\Domain \st |\A^*\vvard0^*|(\vvarx0) = \mu\} $ (an equivalent statement holds for the countable case).
@@
 It can even be solved efficiently with FISTA which allows for direct comparison with the uniform and adaptive mesh approaches.
-As explained by \citep{Ekanadham2011, Duval2017b}, the idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen.
+As explained by \citet{Ekanadham2011, Duval2017b}, the idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen.
 If $\varf0^*$ has only one Dirac spike in each pixel then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.
@@
 \end{theorem}
-\todo{A very boring theorem but needs to be somewhere to justify the numerics. I don't know if the $\Delta\ll\sigma$ case is interesting to anyone else.}
 \begin{proof}[Proof case 1:]

### 2021-01-11 paper.tex
Update paper
Some corrections given by Antonin and rewriting of the proof of Lemma A.4

@@
 \Cref{thm: sufficiently slow} balances these two factors in an optimal way for \cref{alg: refining FISTA} resulting in a convergence rate of
-	$$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\epsilon}}{N^2}$$
-	for all $N\in\F N$, some $\epsilon\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\Func0}$. In particular, if $\varf0^*\in\F H$ then we recover the classical rate with $\epsilon=0$.
+	$$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
+	for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\Func0}$. In particular, if $\varf0^*\in\F H$ then we recover the classical rate with $\kappa=0$.
 \end{adaptiveStep}
@@
 This is analysed in \Cref{thm: stronger exponential FISTA convergence} which shows convergence results of the form
-	$$ \min_{n\leq N}\Func0_0(\varf0_n) \lesssim \frac{N^{2\epsilon}}{N^2}$$
-	for all $N\in\F N$, with the same $\epsilon\in[0,1)$ from \Cref{step: step 5 sufficiently slow}.
+	$$ \min_{n\leq N}\Func0_0(\varf0_n) \lesssim \frac{N^{2\kappa}}{N^2}$$
+	for all $N\in\F N$, with the same $\kappa\in[0,1)$ from \Cref{step: step 5 sufficiently slow}.
 The penalty for accelerating the refinement time is a potential loss of stability in $\Func0(\varf0_n)$, however, the asymptotic rate is equivalent and this behaviour has not been seen in numerical experiments.
@@
 	\Copy{thm: mini exponential FISTA convergence}{
-		Let $\varf0_n$, $\varf1_n$ be generated by \Cref{alg: refining FISTA}, $(n_k\in\F N)_{k=0}^\infty$ be a monotone increasing sequence, and define
-		$$\tilde{\spcf0}^k \coloneqq \spcf0^{n_k}, \qquad \tilde{\varf2}_k \in \argmin_{\varf0\in\tilde{\spcf0}^k} \Func0(\varf0).$$
-		If
-		$$ \tilde{\varf2}_k \in \spcf0^n \qquad\text{ for all }\qquad n_k\leq n<n_{k+1},\ k\in\F N,$$
-		then for all $K\in\F N$, $n_K\leq N<n_{K+1}$ we have
+		Let $\varf0_n$, $\varf1_n$ be generated by \Cref{alg: refining FISTA}, $(n_k\in\F N)_{k=0}^\infty$ be a monotone increasing sequence, and choose
+		$$\tilde{\varf2}_k \in \spcf0^{n_k} \cap \spcf0^{n_k+1}\cap \ldots \cap \spcf0^{n_{k+1}-1}$$
+		for each $k\in\F N$. If such a sequence exists, then for all $K\in\F N$, $n_K\leq N<n_{K+1}$ we have
 		\begin{multline*}
@@
 	\Copy{thm: sufficiently fast}{
-		Suppose $\spcf0^n, \varf0_n, \varf1_n$ and $n_k$ satisfy the conditions of \Cref{thm: mini exponential FISTA convergence} and $\{\tilde{\spcf0}^k\}$ forms an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$.
+		Suppose $\spcf0^n, \varf0_n, \varf1_n$ and $n_k$ satisfy the conditions of \Cref{thm: mini exponential FISTA convergence} and $\{\tilde{\spcf0}^k\}$ forms an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$ with
+		$$\tilde{\varf2}_k\in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)\right]\cap\spcf0^{n_k}\cap\spcf0^{n_k+1}\cap\ldots\cap\spcf0^{n_{k+1}-1}.$$
 		If either:
@@
 		then 
-		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\epsilon)}}\qquad \text{ where } \qquad \epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}.$$}
+		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}.$$}
 \end{lemma}
@@
 		then
-		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\epsilon)}}\qquad \text{ where } \qquad \epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}$$
+		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}$$
 		uniformly for $N\in\F N$.
@@
 
-\Cref{thm: sufficiently fast} gives a sufficient condition on $n_k$ for converging at the rate $O(N^{2(\epsilon-1)})$ but it is not necessary. Indeed for $n\leq n_k$ the result shows 
-$$\Func0_0(\varf0_n) \geq \min_{\varf0\in\spcf0^n}\Func0_0(\varf0) = O(\vars3_{\Func0}^{-k}) = O(n^{2(\epsilon-1)})$$
-which suggests that to converge faster than $n^{2(\epsilon-1)}$ requires choosing smaller $n_k$.
+\Cref{thm: sufficiently fast} gives a sufficient condition on $n_k$ for converging at the rate $O(N^{2(\kappa-1)})$ but it is not necessary. Indeed for $n\leq n_k$ the result shows 
+$$\Func0_0(\varf0_n) \geq \min_{\varf0\in\spcf0^n}\Func0_0(\varf0) = O(\vars3_{\Func0}^{-k}) = O(n^{2(\kappa-1)})$$
+which suggests that to converge faster than $n^{2(\kappa-1)}$ requires choosing smaller $n_k$.
 As an example, in \Cref{sec: wavelet examples} we will see \cref{alg: refining FISTA} can converge at a linear rate, although this is not possible without adaptive refinement times.
@@
 		Whenever these conditions on $n_k$ are satisfied, then
-		$$\min_{n\leq N}\Func0_0(\varf0_n) \lesssim \frac{1}{N^{2(1-\epsilon)}}\qquad \text{ where } \qquad \epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}$$
+		$$\min_{n\leq N}\Func0_0(\varf0_n) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}$$
 		uniformly for $N\in\F N$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage {\Huge\todo{I don't know if this section should remain}}
 \section{General examples}\label{sec: general examples}
@@
 
-\newpage 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{equation}\label{eq: Lasso energy rate}
-	\epsilon = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} = \frac{d}{1+d} \quad \implies \quad \Func0_0(\varf0_n) \lesssim n^{-2(1-\epsilon)} = n^{-\frac{2}{1+d}}.
+	\kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} = \frac{d}{1+d} \quad \implies \quad \Func0_0(\varf0_n) \lesssim n^{-2(1-\kappa)} = n^{-\frac{2}{1+d}}.
 \end{equation}
@@
 		\tfrac12\norm{\varf2_N}^2 + \sum^N_{n=1} \vart1_n\Func0_0(\Pi_n\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n} = \tfrac12\norm{\tilde{\varf2}_K}^2 + \sum_{n=n_K}^N\vart1_n\Func0_0(\tilde{\varf2}_K)
-		\\+ \sum_{k=1}^K\sum_{n=n_{k-1}}^{n_k-1}\vart1_n\Func0_0(\tilde{\varf2}_K) 
+		\\+ \sum_{k=1}^K\sum_{n=n_{k-1}}^{n_k-1}\vart1_n\Func0_0(\tilde{\varf2}_{k-1}) 
 		+ \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}.
@@
 \end{lemma}
-\todo{This proof is quite long and not very explicit. Should I compute the constant?}
 \begin{proof}
-	Inserting the assumed rates into \Cref{app:thm: mini FISTA convergence} gives
-	\begin{equation}
-		\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 \lesssim \vars3_{\Varf0}^{2K} + (N+1)^2\vars3_{\Func0}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\Func0}^{-k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + \vars3_{\Varf0}^{2k}.
-	\end{equation}
-	Each case now needs its own induction. When $\vars3_{\Varf0}>1$ we simplify the inequality to 
-	\begin{align}
-		\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim \vars3_{\Varf0}^{2K} + \vars3_{\Varf0}^{2K+2} + \sum_{k=1}^{K}\vars3_{\Varf0}^{2k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}
-		\\&\leq C_1\left(\vars3_{\Varf0}^{2K+2} + \frac{\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1} + \sum_{k=1}^{K}\vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\right).
-	\end{align}
-	for some $C_1$ sufficiently large. Assume $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2\vars3_{\Varf0}^k$ for $k\leq K$, then for $N=n_{K+1}-1$ we have
-	\begin{equation}
-		\tfrac12\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}^2 \leq \frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right).
-	\end{equation}
-	If $C_2$ is sufficiently large, then $\frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right) \leq \tfrac12C_2^2\vars3_{\Varf0}^{2K+2}$ which completes the induction.
-This bounds the growth of the right hand side and so for any $N<n_{K+1}$ we have $t_N^2\Func0_0(\varf0_N) \lesssim \vars3_{\Varf0}^{2K}$.
-
-	When $\vars3_{\Varf0}=1$, the assumptions are stronger so the induction becomes more direct.
-Assuming $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2$ for $k\leq K$, there exists $C_1>0$ such that
-	\begin{align}
-		\vart1_{N+1}^2\Func0_0(\varf0_{N+1}) + \tfrac12\norm{\varf1_{N+1}-\tilde{\varf2}_{K}}^2 &\leq C_1 + \max_{k\leq K}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}
-		\\&\leq C_1 + C_2.
-	\end{align}
-	If $C_2$ is sufficiently large then $C_1 + C_2 \leq \tfrac14C_2^2$ which completes the second induction. This confirms $t_N^2\Func0_0(\varf0_N) \leq \tfrac14C_2^2$ is bounded uniformly.
+	Starting from \Cref{app:thm: mini exponential FISTA convergence} we get
+	\begin{align}
+		\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\Func0_0(\tilde{\varf2}_K) + \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\Func0_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}
+		\\& \leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2}{2}\Func0_0(\tilde{\varf2}_K) \notag
+		\\&\hspace{100pt}+\sum_{k=1}^K \frac{n_k^2}{2}\Func0_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}+\tilde{\varf2}_{k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}.
+	\end{align}
+	The inductive step now depends on the value of $\vars3_{\Varf0}$.
+	\begin{description}
+		\item[Case $\vars3_{\Varf0}>1$:] We simplify the inequality
+		\begin{align}
+			\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim \vars3_{\Varf0}^{2K} + (N+1)^2\vars3_{\Func0}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\Func0}^{-k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + \vars3_{\Varf0}^{2k}
+			\\&\leq C_1\left[\vars3_{\Varf0}^{2K+2} + \sum_{k=1}^{K}\vars3_{\Varf0}^{2k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\right]
+		\end{align}
+		for some $C_1>C$. Choose $C_2\geq \norm{\varf1_{n_1-1}-\tilde{\varf2}_{1-1}}\vars3_{\Varf0}^{-1}$ such that 
+		\begin{equation}
+			\frac12C_2^2 \geq \frac{C_1}{\vars3_{\Varf0}^2-1}(C_2+\vars3_{\Varf0}^2).
+		\end{equation}
+		Assume $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2\vars3_{\Varf0}^k$ for $1\leq k\leq K$ (trivially true for $K=1$), then for $N=n_{K+1}-1$ we have 
+		\begin{align}
+			\tfrac12\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}^2 &\leq C_1\left[\vars3_{\Varf0}^{2K+2} + \sum_{k=1}^{K}\vars3_{\Varf0}^{2k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\right]
+			\\&\leq C_1\left[\vars3_{\Varf0}^{2K+2} + (1+C_2)\frac{\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\right]
+			\\&\leq \frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right)
+			\\&\leq \tfrac12(C_2\vars3_{\Varf0}^{K+1})^2.
+		\end{align}
+
+		\item[Case $\vars3_{\Varf0}=1$:] Denote $\vars4_k = \norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}$ and note that $\norm{\tilde{\varf2}_{k-1}} \leq \norm{\tilde{\varf2}_{0}} + \sum_0^\infty \vars4_k\lesssim 1$.
+We therefore bound
+		\begin{align}
+			\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim 1 + (N+1)^2\vars3_{\Func0}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\Func0}^{-k} + (\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + 1)b_k
+			\\&\leq C_1\left[1 + \sum_{k=1}^{K}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\vars4_k\right]
+		\end{align}
+		for some $C_1>0$. Choose $C_2\geq \frac{\norm{\varf1_{n_1-1}-\tilde{\varf2}_{1-1}}}{\sum_0^\infty \vars4_k}$ such that 
+		\begin{equation}
+			\frac12C_2^2 \geq C_1\left(1+C_2\sum_1^\infty\vars4_k\right).
+		\end{equation}
+		Assume $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2$ for $1\leq k\leq K$ (trivially true for $K=1$), then for $N=n_{K+1}-1$ we have 
+		\begin{equation}
+			\tfrac12\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}^2 \leq C_1\left[1 + \sum_{k=1}^{K}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\vars4_k\right]
+			\leq C_1\left(1+C_2\sum_1^\infty\vars4_k\right) \leq \frac{C_2^2}{2}
+		\end{equation}
+	\end{description}
+		In both cases, the induction on $\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}$ holds for all $K$ and we have 
+		\begin{equation}
+			\vart1_N^2\Func0_0(\varf0_N) \leq \frac{C_2^2}{2}\vars3_{\Varf0}^{2K}
+		\end{equation}
+		for all $N<n_K-1$.
 \end{proof}
@@
 		\\&\leq \exp\left(\log N^2\frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} - \frac{\log C\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}\right)
-		\\&\lesssim N^{2\epsilon}
+		\\&\lesssim N^{2\kappa}
 	\end{align}
@@
 	\begin{equation}
-		\min_{n\leq N} \Func0_0(\varf0_n)\lesssim \splitln{\vars3_{\Func0}^{-k}}{N>n_k}{ \sfrac{\vars3_{\Varf0}^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_{\Varf0}^{2k},\vars3_{\Varf0}^{2k}) \lesssim N^{-2(1-\epsilon)}
+		\min_{n\leq N} \Func0_0(\varf0_n)\lesssim \splitln{\vars3_{\Func0}^{-k}}{N>n_k}{ \sfrac{\vars3_{\Varf0}^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_{\Varf0}^{2k},\vars3_{\Varf0}^{2k}) \lesssim N^{-2(1-\kappa)}
 	\end{equation}
@@
 \section{Proof of \texorpdfstring{\Cref{thm: generic a_U and a_E}}{rates for general finite element spaces}}\label{app: generic a_U and a_E}
-\todo{This whole section is unnecessary for the numerics.
-It is possibly useful to get a general understanding of the rates one can achieve but not strong enough for Lasso.
-It is quite a long proof for that level of reward\ldots}
 The proof of \Cref{thm: generic a_U and a_E} is the result of the following three lemmas.

### 2021-01-12 paper.tex
Slightly simplified results section

@@
 
-\begin{figure}\centering
+\begin{figure}[H]\centering
 	\includegraphics[width=.84\textwidth]{lasso_reduced_convergence}
@@
 }\label{fig: comparison with iteration}
-\end{figure}
-\begin{figure}\centering
+
+	\vspace*{\floatsep}
+
 	\includegraphics[width=.84\textwidth]{lasso_convergence_time}
@@
 This perspective comes from the multi-resolution interpretation of wavelets.
-We will explain the approach for 1D in detail and then comment on how to extend this picture to higher dimensions.
-We start with a space $\tilde{\spcf0}^0$ and a normalised mother wavelet $\vard1\colon[0,1]\to \R$ then inductively form $\tilde{\spcf0}^k$ by
-$$\tilde{\spcf0}^k = \tilde{\spcf0}^{k-1}\bigcup\left\{w_{j,k}(\varx0) = \sqrt{2}^k\vard1(2^{k}\varx0-j)\st j=0,\ldots 2^k-1\right\}.$$
-If we keep track of the support $w_{j,k}$, then we see a tree structure emerging, as shown in \Cref{fig: wavelet tree}.
+An example is seen in \Cref{fig: wavelet tree} for 1D Haar wavelets, $w_{j,k}(\varx0) = \sqrt{2}^k\vard1(2^{k}\varx0-j)$ where $\vard1 = \1_{[0,1)} - \1_{[-1,0)}$.
 \begin{figure}\begin{center}\begin{tikzpicture}[grow'=right]
@@
 
-			\node[bag] {$\tilde{\spcf0}^0$}
+			\node[text width=7cm] at (-6cm,0) {
+				$\begin{aligned}
+					J_n &= \{(0,0), (0,1), (0,2), (1,2), (1,1)\}
+					\\\op{leaf}(J_n) &= \{(0,2), (1,2), (1,1)\}
+					\\\F M^n &= \left\{[0,\tfrac14),[\tfrac14,\tfrac12),[\tfrac12,1)\right\}
+				\end{aligned}$ };
+
+			\node[bag] at (0,0) {$\tilde{\spcf0}^0$}
 			child {node[bag] {$w_{0,0}$ $[0,1]$}
@@
 					child {node[bag] {$w_{0,2}$ $[0,\frac14]$}
-						child { node {\ldots} }
 					} child {node[bag] {$w_{1,2}$ $[\frac14,\frac12]$}
-						child { node {\ldots} }
 					}
 				} child {node[bag] {$w_{1,1}$ $[\frac12,1]$}
-					child {node[bag] {$w_{2,2}$ $[\frac12,\frac34]$}
-						child { node {\ldots} }
-					} child {node[bag] {$w_{3,2}$ $[\frac34,1]$}
-						child { node {\ldots} }
-			}}};
+			}};
+
 	\end{tikzpicture}\end{center}
@@
 \end{figure}
-Each time a node splits, the support is partitioned exactly between its two children.
-If we truncate this tree to $J_n$ such that every node either has zero or two children, then the leaves of this tree form a partition of unity.
-For example
-\begin{align*}
-	J_n = \{(0,0), (0,1),(1,1), (2,2), (3,2)\} \implies \op{leaf}(J_n) &= \{(0,1), (2,2), (3,2)\}, 
-	\\ [0,1] &= [0,\tfrac12]\cup[\tfrac12,\tfrac34]\cup[\tfrac34,1].
-\end{align*}
 In higher dimensions, the only two things which change are the number of children ($2^d$ for non-leaves) and at each node you store the coefficients of $2^d-1$ wavelets.
@@
 \end{align}
-It is interesting to note that 
-\begin{equation}
-	\sum_{j\in\op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0^*}_{L^2}^2 = \norm{\A^*\vvard0^*}_{L^2}^2,
-\end{equation}
-therefore the task of refinement is somehow to partition the domain of $\A^*\vvard0^*$ such that no single component has more than $\mu$ magnitude. Also, by strong convexity of the dual problem,
-\begin{equation}
-	\left|\vars2_0\norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} - \norm{\1_{\supp(w_j)}\A^*\vvard0^*}_{L^2}\right| \leq \sqrt{|\supp(w_j)|}\sqrt{2(\Func0(\varf0_n)+\Func0^*(\vars2_0\vvard0_n))},
-\end{equation}
-therefore the exact discretisation is reached in finite time.
-After this point, the discretised problem is equal to the continuous problem, and \Cref{alg: refining FISTA} will behave as in the classical setting.
 
@@
 This is visualised in \Cref{fig: haar data}.
-All optimisations shown will be spatially adaptive using Haar wavelets and initialised with four degrees of freedom (denoted $\spcf0^1$ in the notation of \Cref{fig: wavelet tree}).
+All optimisations shown will be spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$.
 The gradient metric shown throughout is the $\ell^2$ norm.
@@
 
-\begin{figure}\centering
-	\includegraphics[width=.84\textwidth]{haar_data}
+The first numerical results shown in \Cref{fig: haar convergence} compare the same adaptive algorithms as shown in \Cref{fig: convergence with method}.
+In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower.
+
+\begin{figure}[H]\centering
+	\includegraphics[width=.85\textwidth]{haar_data}
 	\caption{Phantoms and data used for wavelet-sparse tomography optimisation.
@@
 Without noise the data would be uniform with respect to the angle.}\label{fig: haar data}
-\end{figure}
-
-The first numerical results shown in \Cref{fig: haar convergence} compare the same adaptive algorithms as shown in \Cref{fig: convergence with method}.
-In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ and the classical FB are significantly slower.
-The maximum number of wavelet coefficients used was 312,220 and 44,644 for the circle and Shepp-Logan phantoms respectively.
-
-\begin{figure}\centering
-	\includegraphics[width=.84\textwidth]{haar_convergence_short}
+
+	\vspace*{\floatsep}
+
+	\includegraphics[width=.85\textwidth]{haar_convergence_short}
 	\caption{Discrete convergence of different implementations of \Cref{alg: refining FISTA} with an unlimited number of pixels.}\label{fig: haar convergence}
-\end{figure}
-
-As before, we focus on the $a=20$ algorithm to which \Cref{thm: practical refinement criteria} applies, and greedy FISTA which we see achieves slightly faster convergence in \Cref{fig: haar convergence zoom}.
-Looking at the discrete and continuous gradient norms, we see that they are initially distinct then merge after around 50 iterations.
-From this point onwards, the continuous and discrete problems are equivalent and the iterations are equivalent to classical FISTA.
-
-\begin{figure}[H]\centering
-	\includegraphics[width=.84\textwidth]{haar_reduced_convergence}
-	\caption{Discrete/continuous convergence of adaptive FISTA algorithms on the wavelet Lasso optimisation.}\label{fig: haar convergence zoom}
+
+	\vspace*{\floatsep}
+
+	\includegraphics[width=.85\textwidth]{STORM_data}
+	\caption{Example of images from STORM dataset.}\label{fig: STORM data}
 \end{figure}
@@
 Our final application is a super-resolution/de-blurring inverse problem from biological microscopy.
-The resolution of visible light microscopy is fundamentally limited by the wavelength of visible light.
-Classically, this limit has held around \SI{250}{\nano\meter}, however, in recent years new techniques have emerged improving resolution to around \SIrange{30}{50}{\nano\meter} \citep{Schermelleh2019}.
-A big component of this shift is a growing reliance on more powerful data processing techniques.
-\emph{Stochastic Optical Reconstruction Microscopy} (STORM) is an example of \emph{Single Molecule Localisation Microscopy} (SMLM) where a large number of coarse blurred images are recorded, then re-combined to form a single sparse super-resolved image.
-In the context of STORM, each recorded image is modelled as a sparse signal convolved with a point-spread function, then corrupted with noise.
+In mathematical terms, the observed data is a large number of sparse images which are corrupted by blurring and a large amount of noise, examples are seen in \Cref{fig: STORM data}.
+The task is to compute the centres of the spikes of signal in each image and then re-combine into a single super-resolved image, as in \Cref{fig: STORM results}.
+This technique is referred to as \emph{Single Molecule Localisation Microscopy} (SMLM), of which we consider the specific example of \emph{Stochastic Optical Reconstruction Microscopy} (STORM).
+Readers are directed to works such as by \citet{Sage2015,Sage2019,Schermelleh2019} for further details.
 The Lasso formulation has previously been shown to be effective in the context of STORM, see for instance \citet{Huang2017,Denoyelle2019}.
 
-In this example we use a simulated dataset provided as part of the 2016 SMLM challenge\footnote{\url{http://bigwww.epfl.ch/smlm/challenge2016/datasets/MT4.N2.HD/Data/data.html}} for benchmarking software in this application.
-It is common to model the point-spread function as a Gaussian, in this example the corresponding Lasso formulation  is
+Here we use a simulated dataset provided as part of the 2016 SMLM challenge\footnote{\url{http://bigwww.epfl.ch/smlm/challenge2016/datasets/MT4.N2.HD/Data/data.html}} for benchmarking software in this application.
+The corresponding Lasso formulation is
 \begin{equation}
@@
 
-\begin{figure}\centering
-	\includegraphics[width=.8\textwidth]{STORM_data}
-	\caption{Example of images from STORM dataset.}\label{fig: STORM data}
-\end{figure}
-
 Finally, all the reconstructions were summed and the result shown in \Cref{fig: STORM results}.
 The average pixel width after optimisation was approximately \SI{2.4}{\nano\meter}, a factor of 40 super-resolution.
-If this resolution had been implemented with a uniform discretisation then it would have required $70\times 10^5$ pixels, nearly a factor of 100 greater than achieved with the adaptive discretisation.
+If this resolution had been implemented with a uniform discretisation then it would have required $70\times 10^5$ pixels per frame, nearly a factor of 100 greater than achieved with the adaptive discretisation.
 Lasso is compared with ThunderSTORM \citep{Ovesny2014}, a popular ImageJ plugin \citep{Schindelin2012} which finds the location of signal using Fourier filtering.
@@
 \begin{figure}[H]\centering
-	\includegraphics[width=\textwidth]{lasso2_convergence}
+	\includegraphics[width=.82\textwidth]{lasso2_convergence}
 	\caption{Convergence of adaptive FISTA for STORM dataset.
@@
 \bibliographystyle{apalike}\bibliography{references} % alpha is also a decent style
-\newpage\appendix
+\appendix
 \section{Proofs for FISTA convergence}\label{app: FISTA convergence}
@@
 
-\newpage\noindent The following lemma is used to produce a sharper estimate on sequences $\vart1_n$.
+\noindent The following lemma is used to produce a sharper estimate on sequences $\vart1_n$.
 \begin{lemma}\label{app: tn upper bound}
@@
 \end{lemma}
-\todo{This is a very long theorem which I don't really use in the end. The result is a little bit useful but not difficult.}
 \begin{proof}
@@
 		Suppose $q>0$. If the polynomial $p(|\vvarx0|) = \sum p_k|\vvarx0|^k$ has non-negative coefficients and $\vvarx0\in[-m,m]^d$, then
-		$$\sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq m}} p(|\vec{j}-\vvarx0|)\exp\left(-\tfrac{q|\vec{j}-\vvarx0|^2}{2}\right)\leq \left[\sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq2m}}p(|\vec{j}|+\delta)\exp\left(-\frac{q\max(0,|\vec{j}|-\delta)^2}{2}\right)\right]$$
-		where $\delta\coloneqq \frac{\sqrt{d}}{2}$.
+		$$\sum_{\norm{\vec{j}}_{\ell^\infty}\leq m} p(|\vec{j}-\vvarx0|)\exp\left(-\tfrac{q|\vec{j}-\vvarx0|^2}{2}\right)\leq \sum_{\norm{\vec{j}}_{\ell^\infty}\leq2m}p(|\vec{j}|+\delta)\exp\left(-\frac{q\max(0,|\vec{j}|-\delta)^2}{2}\right)$$
+		where $\delta\coloneqq \frac{\sqrt{d}}{2}$ and $\vec{j}\in\F Z^d$.
 	\end{lemma}
@@
 		\begin{align*}
-			\sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq m}} p(|\vec{j}-\vvarx0|)\exp\left(-\tfrac{q|\vec{j}-\vvarx0|^2}{2}\right) &= \sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq m}} p(|\vec{j}-(\vvarx0+\hat{\vvarx0})+\hat{\vvarx0}|)\exp\left(-\tfrac{q|\vec{j}-(\vvarx0+\hat{\vvarx0})+\hat{\vvarx0}|^2}{2}\right)
-			\\&\leq \sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq2m}} p(|\vec{j}+\hat{\vvarx0}|)\exp\left(-\tfrac{q|\vec{j}+\hat{\vvarx0}|^2}{2}\right)
+			\sum_{\norm{\vec{j}}_{\ell^\infty}\leq m} p(|\vec{j}-\vvarx0|)\exp\left(-\tfrac{q|\vec{j}-\vvarx0|^2}{2}\right) &= \sum_{\norm{\vec{j}}_{\ell^\infty}\leq m} p(|\vec{j}-(\vvarx0+\hat{\vvarx0})+\hat{\vvarx0}|)\exp\left(-\tfrac{q|\vec{j}-(\vvarx0+\hat{\vvarx0})+\hat{\vvarx0}|^2}{2}\right)
+			\\&\leq \sum_{\norm{\vec{j}}_{\ell^\infty}\leq2m} p(|\vec{j}+\hat{\vvarx0}|)\exp\left(-\tfrac{q|\vec{j}+\hat{\vvarx0}|^2}{2}\right)
 			\\&\leq \sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq2m}} p(|\vec{j}|+\delta)\exp\left(-\tfrac{q\max(0,|\vec{j}|-\delta)^2}{2}\right)

### 2021-01-15 paper.tex
Added Parpas reference
attempt to shrink text

@@
 
+%\renewcommand{\Paste}[1]{}
+
 \author{Robert Tovey and Antonin Chambolle}
@@
 	\maketitle
-
-%In many variational approaches to inverse problems, optimisation problems are often written in a continuous setting but solved with a discrete optimisation algorithm.
-Consider what happens when $\sqrt{e^2}$ is computed in your favourite programming language.
-We have asked a `continuous' question and have been given a `discrete' answer with very well controlled error bounds.
-%
-%The parallel to this for optimisation is that we still do not have infinite computing memory or processing power, but we still want to compute minimisers to a known accuracy with efficient implementations.
-It is typically much harder to control discretisation errors in optimisation problems, for instance the $\Gamma$-convergence of discrete total variation \citep{Bartels2012,Bartels2015} or the approximation errors for wavelets/curvelets/sheerlets \citep{Mallat1999,Candes2004,Guo2007}.
-These are typically quite weak guarantees valid for asymptotic resolution/time and are hard to quantify in a specific example.
-In this work we propose an algorithm with three aims:
-%\begin{itemize}
-%	\item All computations are discrete but the asymptotic reconstruction is exact, even for infinite dimensional reconstructions in a Banach space, with a guaranteed rate.
-%	\item Distance to the infinite dimensional minimiser can be quantified.
-%	\item Discretisation is adaptively optimised for the particular minimiser.
-%\end{itemize}
-%
-%We choose to modify the FISTA algorithm because it is quite general and performs very well in discrete optimisation problems.
-The strategy will be to follow the standard FISTA algorithm as closely as possible.
-The only difference is that at each iteration, computations will only be performed on a finite dimensional subspace.
-%
-%One key issue is that FISTA is intrinsically designed to converge only in $L^2$.
-In finite dimensions there is no issue, all norms are equal and so convergence rates are equal for all problems up to scaling constants.
-On the other hand, in infinite dimensions there exist minimisers which are not in $L^2$.
-In this case, we find that the rate will always be slower than for standard FISTA but still at a guaranteed rate.
-%
-%We perform two numerical experiments where the minimiser is in $L^1\setminus L^2$ which demonstrates the reduced rate.
-We also show an example where the minimiser is in $\ell^2(\R^m)$ for some $m$ which is not known a priori and observe that the refining FISTA algorithm achieves linear convergence.
 
@@
 This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations.
+The ideas of \citet{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\func2$.
+The permitted refinement steps are also more broad in our work.
 
@@
 To get the general statement of any of the results which follow, replace $\Func0$ with $\frac{\Func0}{L}$.
-Implicitly, the only impact of $L$ is scaling the convergence rates which are only given up to a constant factor anyway.
 A more important distinction is to say that the properties of $\func1$ and $\func2$ are stated with respect to the Hilbert norm.
 In particular,
-$$\norm{\nabla\func1(\varf0)- \nabla\func1(\varf1)} \leq \norm{\varf0-\varf1}$$
+\begin{equation}
+	\norm{\nabla\func1(\varf0)- \nabla\func1(\varf1)} \leq \norm{\varf0-\varf1}
+\end{equation}
 for all $\varf0,\varf1\in\F H$ and $\func2$ is called `simple' if
-$$\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \func2(\varf0) $$
+\begin{equation}
+	\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \func2(\varf0)
+\end{equation}
 is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$.
@@
 		then
-		$$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}$$
-		for all $n_K\leq N< n_{K+1}$.}
+		$$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}\qquad \text{for all}\qquad n_K\leq N< n_{K+1}.$$
+		}
 \end{lemma}
@@
 	$$ \Func0_0(\varf0_N) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\Func0(\varf0)}^2}{N^2} + \min_{\varf0\in\spcf0^N}\Func0_0(\varf0) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} + \vars3_{\Func0}^{-K}.$$
-	This is equivalent to \Cref{thm: sufficiently fast} under the conditions on $n_k$.
+	This is equivalent to \Cref{thm: sufficiently fast} after the assumptions on $n_k$.
 	\item If $\spcf0$ is finite dimensional then the $\vars3_{\Varf0}=1$ is almost trivially satisfied.
@@
 This is in fact a special case of \citet{Aujol2015}.
-If $\varf0^*\in\F H$ then it is not possible to refine `too quickly' and the following lemma is not needed.
+If $\varf0^*\in\F H$, then it is not possible to refine `too quickly' and the following lemma is not needed.
 
@@
 		then
-		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}$$
-		uniformly for $N\in\F N$.
+		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} \qquad \text{uniformly for } N\in\F N.$$
 		}
 \end{theorem}
-\noindent This theorem is very easy to implement and requires very little knowledge of how to estimate $\Func0_0(\varf0_n)$.
+\noindent This theorem is very easy to implement numerically and requires very little knowledge of how to estimate $\Func0_0(\varf0_n)$.
 So long as $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be computed analytically, choosing $\tilde{\spcf0}^k$ to be uniform discretisations and $\tilde{\spcf0}^k = \spcf0^{n_k}=\ldots= \spcf0^{n_{k+1}-1}$ will give the stated convergence rate.
@@
 \cref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\Func0_0(\varf0^{n_k-1})\lesssim \vars3_{\Func0}^{-k}$.
-However, the value of $\Func0_0$ may be hard to estimate and so we introduce a `backstop' condition which ensures that convergence is no slower than the rate given by \Cref{thm: exponential FISTA convergence}.
+However, the value of $\Func0_0$ may be hard to estimate and so we introduce a `backstop' condition which guarantees that convergence is no slower than the rate given by \Cref{thm: exponential FISTA convergence}.
 The only constraint on spatial adaptivity is the piecewise monotone inclusion and that $\spcf0^{n_k} \ni u^{n_k-1}$.
@@
 In cases (2) and (5), $\varf0_k$ is sufficient to choose the refinement time $n_k$ but not the subspace $\tilde{\spcf0}^k$.
-In these cases one could choose $\tilde{\spcf0}^k$ to be a uniform discretisation with apriori estimates, for example.
+In these cases one could, for example, choose $\tilde{\spcf0}^k$ to be a uniform discretisation with apriori estimates.
 
@@
 In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, \Cref{alg: refining FISTA} is much more broadly applicable.
-The aim of this section is to justify this claim by demonstrating that the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be easily computed in many examples.
+Here we justify this claim by demonstrating that the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be easily computed in many examples.
 
@@
 We note that any piecewise polynomial finite element space can be used to form a $\meshsize$-refining sequence of subspaces.
-Wavelets almost satisfy this definition but not the support condition, each space contains every scale of wavelet.
-\todo{Is that true?
-If the wavelet has compact support then it should admit a basis with disjoint support?} Similarly, a Fourier basis does satisfy the scaling properties but each basis vector has global support.
+Wavelets with a compactly supported basis satisfy this definition but it is hard to specify the value $N$ in general.
+Similarly, a Fourier basis does satisfy the scaling properties but each basis vector has global support.
 Both of these exceptions are important and could be accounted for with further analysis but we focus on the more standard finite element case.
@@
 Expanding the operator norm further,
-\begin{multline}
+\begin{equation}
 	\norm{(\tilde\Pi_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde\Pi_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}}
-	\\= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}
-\end{multline}
+	= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}
+\end{equation}
 where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.
@@
 \end{equation}
-This rate can be used to infer the required resolution at each iteration, in particular on iteration $n$ with $n^2\sim (\vars3_{\Func0}\vars3_{\Varf0}^2)^k$ we expect the resolution to be
+This rate can be used to infer the required resolution at each iteration, in particular on iteration $n$ with $n^2\simeq (\vars3_{\Func0}\vars3_{\Varf0}^2)^k$ we expect the resolution to be
 \begin{equation}\label{eq: Lasso resolution rate}
-	2^{-k} = \left(\vars3_{\Func0}\vars3_{\Varf0}^2\right)^{\frac{k}{1+d}} \sim n^{-\frac{2}{1+d}}.
+	2^{-k} = \left(\vars3_{\Func0}\vars3_{\Varf0}^2\right)^{\frac{k}{1+d}} \simeq n^{-\frac{2}{1+d}}.
 \end{equation}
@@
 infinite vectors with finitely many non-zeros.
-The key change in analysis from the continuous case is that sparse vectors in $\ell^1(\R)$ are also in $\ell^2(\R)$.
-Because of this, $\vars3_{\Varf0}=1$ which leads to the expected optimal rate
-$$\min_{n\leq N} \Func0_0(\varf0_n) \lesssim \frac{1}{N^2},$$
-independent of $\vars3_{\Func0}$ or any additional properties of $\A$.
+The key change in analysis from the continuous case is $\varf0^*\in\ell^2(\R)$, which leads to $\vars3_{\Varf0}=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\Func0}$ or any additional properties of $\A$.
 The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of \Cref{thm: exponential FISTA convergence,thm: stronger exponential FISTA convergence} hold trivially.
@@
 	\\&= \max_{\vvard0\in\R^m}\min_{\varf0\in\F H} \ip{(\A\Pi_n\varf0-\vdata0)}{\vvard0} +\mu\Norm{\Pi_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
-	\\&= \max_{\vvard0\in\R^m} \splitln{-\ip{\vdata0}{\vvard0} -\tfrac12\norm{\vvard0}_{\ell^2}^2}{\Norm{\Pi_n\A^*\vvard0}_*\leq \mu}{-\infty}{\text{else}}
+	\\&= \max_{\vvard0\in\R^m} \splitln{-\ip{\vdata0}{\vvard0} -\tfrac12\norm{\vvard0}_{\ell^2}^2}{\qquad\Norm{\Pi_n\A^*\vvard0}_*\leq \mu}{-\infty}{\qquad\text{else}}
 	\\&= -\min_{\vvard0\in\R^m} \underbrace{\tfrac12\norm{\vvard0}_{\ell^2}^2+\ip{\vdata0}{\vvard0}}_{\eqqcolon \Func0^*(\vvard0)}  + \chi(\Norm{\Pi_n\A^*\vvard0}_*\leq \mu).
@@
 \subsubsection{Bounds for countable functionals}
-Extending the results of \Cref{sec: bound discrete} to $\spcf0=\ell^1(\R)$ is analytically very simple but relies heavily on the specific choice of $\A$.
+Extending the results of \Cref{sec: bound discrete} to $\spcf0=\ell^1(\R)$ is analytically very simple but computationally relies heavily on the specific choice of $\A$.
 The computations of gradients and gaps carry straight over replacing $\Pi_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\spcf0^n = \{\varf0\in\ell^1\st i\notin J_n\implies \varf0_i=0\}$.
@@
 	\min_{\vvarx0\in\supp(\varf0^*)} |[\Pi_n\A^*\vvard0_n](\vvarx0)| &\geq \min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0_n](\vvarx0)|
-	\\&= \frac1{\vars2_0}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vars2_0 \vvard0_n](\vvarx0)|
-	\\&\geq \frac1{\vars2_0}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0^*](\vvarx0)| - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
-	\\&= \frac1{\vars2_0}\min_{\vvarx0\in\supp(\varf0^*)} \mu - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
-	\\&\geq \frac1{\vars2_0}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vvard0_n-\vvard0^*}_{\ell^2}\right).
+	\\&= \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vars2_0 \vvard0_n](\vvarx0)|
+	\\&\geq \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0^*](\vvarx0)| - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
+	\\&= \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} \mu - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
+	\\&\geq \vars2_0^{-1}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vvard0_n-\vvard0^*}_{\ell^2}\right).
 \end{align}
@@
 If $q<2$ and $\norm{\vvarx3}_{\ell^2}\leq 1$, then we again use H\"older's inequality:
-	$$\sum_{j=1}^m \varx3_j^q \leq \left(\sum_{j=1}^m 1^{Q^*}\right)^{\frac1{Q^*}} \left(\sum_{j=1}^m \varx3_j^{qQ}\right)^{\frac1{Q}} \leq m^{\frac{2-q}{2}}$$
+	$$\sum_{j=1}^m \varx3_j^q \leq \Big(\sum_{j=1}^m 1^{Q^*}\Big)^{\frac1{Q^*}} \Big(\sum_{j=1}^m \varx3_j^{qQ}\Big)^{\frac1{Q}} \leq m^{\frac{2-q}{2}}$$
 	for $Q = \frac2q$.
@@
 \subsubsection{Concrete examples}
-\Cref{thm: norm bound smoothness} demonstrates how the smoothness of $\A$ relates to the smoothness of the kernels $\psi_j$, possibly scaling with respect to $m$.
 We now present explicit examples of the computations in both \Cref{thm: norm bound smoothness,thm: norm bound L2} for the numerical results in \Cref{sec: numerics}.
 These examples are common in practical applications and we show the result of \Cref{thm: norm bound examples} in the main text to demonstrate that, while sometimes hard to compute by hand, the constants can estimated accurately in an efficient manner.
-The Gaussian case is by far the most technical, therefore we will provide a little further explanation at the end of the theorem.
 \begin{theorem}\label{thm: norm bound examples}
@@
 			\begin{align}
-				\norm{\A}_{L^2\to\ell^2} &\leq \bigg((4\pi\sigma^2)^{-\frac d2}\sum_{j=-2\hat m,\ldots,2\hat m}\exp(-\tfrac{\Delta^2}{4\sigma^2}j^2)\bigg)^d,
+				\norm{\A}_{L^2\to\ell^2} &\leq \bigg((4\pi\sigma^2)^{-\frac 12}\sum_{j=-2\hat m,\ldots,2\hat m}\exp(-\tfrac{\Delta^2}{4\sigma^2}j^2)\bigg)^d,
 				\\ |\A^*\vvarx3|_{C^0} &\leq (2\pi\sigma^2)^{-\frac{d}{2}}\bigg(\sum_{\vec j\in J}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}}\norm{\vvarx3}_q,
@@
 The first two are in 1D to demonstrate the performance of different variants of \Cref{alg: refining FISTA}, both with and without adaptivity.
-In particular, we explore sparse Gaussian deconvolution and sparse signal recovery from Fourier data; each displays slightly different behaviour in terms of optimisation.
+In particular, we explore sparse Gaussian deconvolution and sparse signal recovery from Fourier data.
 We compare with the \emph{continuous basis pursuit} (CBP) discretisation \citep{Ekanadham2011, Duval2017b} which is also designed to achieve super-resolution accuracy within a convex framework.
@@
 Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.
-There are many methods designed to minimise the continuous Lasso energy in \eqref{eq: Lasso energy} \citep[c.f.][]{Bredies2013,Castro2016,Boyd2017,Catala2019} however, most result in a non-convex discretised problem to solve.
+There are many methods designed to minimise the continuous Lasso energy in \eqref{eq: Lasso energy} \citep[c.f.][]{Bredies2013,Castro2016,Boyd2017,Catala2019} however, most the solution of a non-convex problem.
 We have focused on CBP because it approximates $\varf0^*$ through a convex discrete optimisation problem which is asymptotically exact in the limit $\meshsize\to0$.
-It can even be solved efficiently with FISTA which allows for direct comparison with the uniform and adaptive mesh approaches.
+It can also be optimised with FISTA which allows for direct comparison with the uniform and adaptive mesh approaches.
 As explained by \citet{Ekanadham2011, Duval2017b}, the idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen.
@@
 \end{equation}
-Inserting this back into the continuous/discrete gap inequality, it becomes 
-\begin{equation}
-	\frac{\vars2_0}{\vars2} \leq 1 + (2-1)\frac{\Func0(\varf0_n)+\Func0^*(\vars2\vvard0_n)}{\Func0^*(\vars2\vvard0_n)}
-\end{equation}
-where 2 was our initial chosen ratio. Converting this into a spatial refinement criteria, recall 
-\begin{equation}
-	\frac{\vars2_0}{\vars2} \approx \frac{\Norm{\A^*\vvard0_n}_*}{\Norm{\Pi_n\A^*\vvard0_n}_*} = \frac{\max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{\max_{\domain_i^n\in\F M^n} |\Pi_n\A^*\vvard0_n(\domain_i^n)|} \approx \max_{\domain_i^n\in\F M^n}\frac{ \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{|\Pi_n\A^*\vvard0_n(\domain_i^n)|}.
-\end{equation}
-If $\frac{\vars2_0}{\vars2}$ is large then there must be pixels (values of $i$) in which this ratio is large.
-Because of the smoothness of $\A^*\vvard0_n$, refining these pixels will halve the difference and therefore contract $\frac{\vars2_0}{\vars2}$ back towards 1.
+Converting this into a spatial refinement criteria, recall 
+\begin{equation}
+	\frac{\vars2_0}{\vars2} \approx \frac{\Norm{\A^*\vvard0_n}_*}{\Norm{\Pi_n\A^*\vvard0_n}_*} = \frac{\max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{\max_{\domain_i^n\in\F M^n} |\Pi_n\A^*\vvard0_n(\domain_i^n)|} \approx \max_{\domain_i^n\in\F M^n}\frac{ \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{|\Pi_n\A^*\vvard0_n(\domain_i^n)|}
+\end{equation}
+is the maximum ratio of second vs.
+zeroth order Taylor approximations of $\A^*\vvard0_n$ on pixel $\domain_i^n$.
 This was found to be an efficient method of selecting pixels for refinement based on quantities which had already been computed.
-Note briefly that from a heuristic standpoint we are refining for two reasons, aligning with an exploitation/exploration viewpoint.
-The trigger is always the result of an estimate from the cell-wise Taylor expansion.
-If the estimate is accurate, then that cell is likely to intersect the support of $\varf0^*$ and refining directly improves the resolution of the support of $\varf0^*$.
-Otherwise, if the estimate is loose then the refinement improves the accuracy of the Taylor expansion and consequently improves the screening of new pixels from the support of $\varf0^*$.
-This second point guarantees that we converge to the global minimiser $\varf0^*$, rather than a sub-optimal critical point.
+Note briefly that this greedy strategy directly targets uncertainty, refinements also happen outside of the support of $u_n$ to guarantee that this is representative of $\varf0^*$.
+Such refinement is necessary to avoid critical points of $\Func0$ which are not global minimisers.
 
@@
 \begin{itemize}
-	\item Increasing the number of pixels always increases the accuracy of the optimisation.
 	\item The adaptive scheme is much more efficient, in both examples the adaptive scheme with 128 pixels is at least as good as both fixed discretisations with 512 pixels.
@@
 	\item With Fourier kernels the uniform piecewise constant discretisation is more efficient than CBP but in the Gaussian case this is reversed.
-This suggests that the CBP \emph{does} achieve super-resolution when $\A$ is sufficiently smooth but may be less accurate when the kernels oscillate on the length-scale of a single pixel.
+This suggests that the performance of CBP depends highly on the smoothness of $\A$.
 	\item The discrete gaps for non-adaptive optimisation behave as is common for FISTA, initial convergence is polynomial until a locally linear regime activates \citep{Tao2016}.
 CBP is always slower to converge than the piecewise constant discretisation.
-	\item For the adaptive method, the continuous/discrete gaps are very similar for all $n$, as enforced by the refinement criterion.
+	\item The adaptive refinement criterion succeeds in keeping the continuous/discrete gaps close for all $n$.
 \end{itemize}
@@
 We have analytical results for the former but the latter typically performs the best for non-adaptive optimisation and is never worse than $a=20$ in the adaptive setting.
-We assume that the numerical aim is to find a function $\varf0_n$ with $\Func0_0(\varf0_n)$ smaller than a given threshold.
 The question is whether it is faster/more efficient to use the proposed adaptive scheme or to use a classical scheme at sufficiently high uniform resolution.
 The fixed discretisations use 1024 pixels (i.e.
-uniform pixel size of $2^{-10}$) and the adaptive discretisation starts with two pixels with an upper limit of 1024.
-
-\Cref{fig: comparison with iteration} shows the convergence with respect to number of iterations.
+constant pixel size of $2^{-10}$ in \Cref{fig: comparison with iteration}) and the adaptive discretisation starts with two pixels with an upper limit of 1024.
 As expected, the fixed discretisation starts with a smaller continuous gap before plateauing to a sub-optimal gap around $\Func0_0=0.1$.
-In both examples, the greedy FISTA has much faster convergence around $n=100$ and of course the minimum pixel size is constant for the fixed discretisation.
-
-The adaptive optimisation matches the predicted rates well, both gap and minimum pixel size (equal to $2^{-k}$) decay at a rate of approximately $\frac1n$.
-Interestingly, in the Fourier case the energy decays a little faster and the resolution is a little slower.
-This is consistent with $\Func0$ being a little bit smoother than predicted (i.e.
-$\vars3_{\Func0}>2$).
-
-It is clear that the adaptive scheme is able to continue reducing the continuous gap far beyond that of the fixed discretisation.
-The range $n\in[10^3,10^4]$ is particularly interesting because it is the time when the adaptive and fixed curves intersect in both continuous gap and minimum pixel size.
-Suppose the stopping criterion is to find $\varf0$ such that $\Func0_0(\varf0)<0.1$.
-\Cref{fig: comparison with iteration} shows that it is equivalent to `guess' the necessary resolution, or to adaptively refine until reaching the stopping criterion.
-Both methods would converge after $O(10^3)$ iterations with a minimum pixel size of $2^{-10}$.
-
-\Cref{fig: comparison with time} shows a more practical comparison showing wall-clock computation time and number of pixels (memory usage).
-Optimisation of the fixed discretisation is faster overall but after around \SI{0.1}{\second}, it is always faster to use the adaptive scheme to achieve a given continuous gap.
-The reason for this can be seen in the numbers of pixels.
-At the most extreme, in the same computation time the adaptive scheme can achieve more than a factor of 10 better gap using approximately a factor of 10 fewer pixels.
-The adaptive scheme re-computes the discrete matrix $\A\Pi_n$ each time there is a refinement, but the fixed schemes only compute it once.
-The adaptive schemes still seem to converge faster than $\frac1{\op{time}}$, which is the expected rate if time per iteration is constant.
+
+\Cref{fig: comparison with iteration} shows convergence of pixel size and continuous gap with respect to number of iterations.
+\Cref{fig: comparison with time} shows the more practical attributes of continuous gap and number of pixels against execution time.
+We see that the adaptive discretisation is consistently capable of computing lower energies with fewer pixels and in less time than the uniform discretisation.
+The convergence behaviour is very consistent with respect to number of iterations.
+
+Suppose that the numerical aim is to find a function $\varf0_n$ with $\Func0_0(\varf0_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.
+For $n\in[10^3,10^4]$, in both problems, the adaptive schemes coincide with the fixed schemes in both energy and minimum pixel size.
+On the other hand, we also see that the adaptive scheme achieves this energy in almost an order of magnitude less time and fewer pixels.
 
@@
 Finally, all the reconstructions were summed and the result shown in \Cref{fig: STORM results}.
-The average pixel width after optimisation was approximately \SI{2.4}{\nano\meter}, a factor of 40 super-resolution.
-If this resolution had been implemented with a uniform discretisation then it would have required $70\times 10^5$ pixels per frame, nearly a factor of 100 greater than achieved with the adaptive discretisation.
+The adaptive scheme used fewer than $10^4$ pixels per frame, a fixed discretisation with equivalent resolution of \SI{1.3}{\nano\meter} would have required more than $3\cdot10^6$ per frame.
 Lasso is compared with ThunderSTORM \citep{Ovesny2014}, a popular ImageJ plugin \citep{Schindelin2012} which finds the location of signal using Fourier filtering.
@@
 
-\Cref{fig: STORM convergence} shows the convergence behaviour in this example.
-The estimates given by \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=2$ predict respectively that the adaptive energy will decay at a rate of $\Func0_0(\varf0_n)\lesssim n^{-\sfrac23}$ so long as the pixel size also decreases at a rate of $\meshsize\sim n^{-\sfrac23}$.
-This is consistent with the resolution scaling (middle panel) but the energy (left panel in pink) is observed to converge a little faster than predicted.
-
-In this example we also implement the suggestion of \Cref{sec: support detection} to remove pixels from the iteration once we can guarantee they are outside of the support.
-\eqref{eq: support equation} provides a threshold to identify the support of the discrete/continuous minimiser and the value of this is plotted in the first panel of \Cref{fig: STORM convergence}, in particular the normalised value $1-\frac{\op{threshold}}{\mu}$ which converges to 0 for large $n$.
-Any pixel $\domain_i^n$ satisfying
-\begin{equation}
-	 \vars2_0\norm{\Pi_n\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq \op{threshold}
+\Cref{fig: STORM convergence} shows slightly faster convergence than $n^{-\sfrac23}$ predicted by \eqref{eq: Lasso resolution rate} in dimension $d=2$.
+In this example we also implement the suggestion of \Cref{sec: support detection} to remove pixels outside of the support of $\varf0^*$.
+From \eqref{eq: support equation}, any pixel $\domain_i^n$ satisfying
+\begin{equation}
+	\vars2_0\norm{\Pi_n\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq 1-\frac{\op{threshold}}{\mu}
 \end{equation}
 guarantees that $\domain_i^n\cap\op{supp}(\varf0^*) = \emptyset$.
-Once this threshold becomes greater than 0 (plotted value less than 1), we can start reducing the number of pixels instead of just continual refinement.
-This is seen in the right-hand panel of \Cref{fig: STORM convergence}, after around 30 iterations the total number pixels starts to reduce and stabilise at approximately $6\times10^3$ pixels per frame, well below the upper limit of $10^5$.
+This value is plotted in the first panel of \Cref{fig: STORM convergence}.
+Once this threshold becomes less than 1, we can start reducing the number of pixels instead of just continual refinement, as seen in the right-hand panel after around 30 iterations.
 
@@
 Lines indicate the median value over 3020 STORM frames.
-Shaded regions indicate the \SIrange{25}{75}{\percent} inter-quartile range.}\label{fig: STORM convergence}
+Shaded regions indicate the \SIrange{25}{75}{\percent} inter-quartile range.
+Pixel width is scaled $[0,1]$ rather than $[0,\SI{6.4}{\micro\meter}]$.}\label{fig: STORM convergence}
 \end{figure}
@@
 			\\&\leq C_1\left[\vars3_{\Varf0}^{2K+2} + (1+C_2)\frac{\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\right]
-			\\&\leq \frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right)
-			\\&\leq \tfrac12(C_2\vars3_{\Varf0}^{K+1})^2.
+			\\&\leq \frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right) \leq \tfrac12(C_2\vars3_{\Varf0}^{K+1})^2.
 		\end{align}
@@
 	which leads to
-	\begin{align}
-		\vars3_{\Varf0}^{2K} & = \exp(K\log \vars3_{\Varf0}^2)
-		\\&\leq \exp\left(\log N^2\frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} - \frac{\log C\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}\right)
-		\\&\lesssim N^{2\kappa}
-	\end{align}
+	\begin{equation}
+		\vars3_{\Varf0}^{2K} = \exp(K\log \vars3_{\Varf0}^2)
+		\leq \exp\left(\log N^2\frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} - \frac{\log C\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}\right)
+	\end{equation}
 	as required.
-\end{proof}
-
-\begin{theorem}[\Cref{thm: exponential FISTA convergence}]
-	\Paste{thm: exponential FISTA convergence}
-\end{theorem}
-\begin{proof}
-	If the conditions of this theorem are satisfied, then so are \Cref{app:thm: mini exponential FISTA convergence,app:thm: sufficiently fast,app:thm: sufficiently slow}.
-The final result is just the conclusion of \Cref{app:thm: sufficiently slow}.
 \end{proof}
@@
 
-%\begin{proof}[Proof of asymptotic case 3:]
-%	In the Gaussian case, we build our approximations around the idea that sums of Gaussians on a regular grid look like a discretised integral.
-The first example can be used to approximate the operator norm.
-Computing the inner products gives
-%	\begin{multline}
-%		\IP{\vard1_i}{\vard1_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vvarx0-\vvarx0_i|^2}{2\sigma^2}-\tfrac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right) \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right)
-%		\\= (4\pi\sigma^2)^{-\frac d2} \exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right).
-%	\end{multline}
-%	Estimating the operator norm,
-%	\begin{align}
-%		\norm{\A\A^*}_{\ell^2\to\ell^2}&\leq \norm{\A\A^*}_{\ell^\infty\to\ell^\infty} = \max_{i\in[m]} \sum_{j=1}^m |\IP{\vard1_i}{\vard1_j}| 
-%		\\&= \max_{i\in[m]}(4\pi\sigma^2)^{-\frac d2}\sum_{j_1,\ldots,j_d\in[\hat m]} \exp\left(-\frac{(j_1\Delta-i_1\Delta)^2+\ldots+(j_d\Delta-i_d\Delta)^2}{4\sigma^2}\right)
-%		\\&\leq (4\pi\sigma^2)^{-\frac d2}\sum_{\vec j\in\F Z^d\cap[-\hat m,\hat m]^d} \exp\left(-\frac{(j_1\Delta)^2+\ldots+(j_d\Delta)^2}{4\sigma^2}\right)
-%		\\&= \frac{(4\pi)^{-\frac d2}}{\Delta^d}\sum_{\vec j\in\F Z^d\cap[-\hat m,\hat m]^d} \exp\left(-\frac14\left|\vec j\frac{\Delta}{\sigma}\right|^2\right)\frac{\Delta^d}{\sigma^d}
-%		\\&\sim \frac{(4\pi\sigma^2)^{-\frac d2}}{\Delta^d}\int_{\R^d} \exp\left(-\tfrac{|\vvarx0|^2}{4\sigma^2}\right) \quad = \Delta^{-d}.
-%	\end{align}
-%	This is a nice approximation because it depends only on $\Delta$, overcoming the $\frac1\sigma$ scaling.
-To convert this into an upper bound, we just compute the sum explicitly.
-In particular, as the sum factorises over dimensions,
-%	$$\norm{\A\A^*}_{\ell^2\to\ell^2} \leq (4\pi\sigma^2)^{-\frac d2}\left(\sum_{j=-\hat m,\ldots, \hat m}\exp\left(-\tfrac{\Delta^2}{4\sigma^2}j^2\right)\right)^d.$$
-%	Applying the same ideas to \Cref{thm: norm bound smoothness}, note
-%	$$\begin{array}{rll}
-%			\displaystyle |\vard1_j(\vvarx0)| &\displaystyle= \left|\vard1_j(\vvarx0)\right| &\displaystyle = (2\pi\sigma^2)^{-\frac d2}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
-%			\\\displaystyle |\nabla\vard1_j(\vvarx0)| &\displaystyle= \left|\frac{\vvarx0-\vvarx0_j}{\sigma^2}\vard1_j(\vvarx0)\right| &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma}\frac{|\vvarx0-\vvarx0_j|}{\sigma}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
-%			\\|\nabla^2\vard1_j(\vvarx0)| &\displaystyle =\left|\frac1{\sigma^2} + \frac{(\vvarx0-\vvarx0_j)(\vvarx0-\vvarx0_j)^\top }{\sigma^4}\right|\vard1_j(\vvarx0) &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma^2}\left(1+\frac{|\vvarx0-\vvarx0_j|^2}{\sigma^2}\right)\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right).
-%	\end{array}$$
-%	With the substitution $\vvarx0=\frac{\Delta}{\sigma}\vec j$, the asymptotic bounds on these are clear:
-%	\begin{align*}
-%		\sum_{\vec j\in[\hat m]^d} |\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim (2\pi\sigma^2)^{-\frac{dq^*}{2}}\frac{\sigma^d}{\Delta^d}\int_{\R^d}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right),
-%		\\\sum_{\vec j\in[\hat m]^d} |\nabla\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma}\frac{\sigma^d}{\Delta^d}\int_{\R^d}|\vvarx0|^{q^*}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right),
-%		\\\sum_{\vec j\in[\hat m]^d} |\nabla^2\vard1_{\vec j}(\vvarx0)|^{q^*} &\lesssim \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^2}\frac{\sigma^d}{\Delta^d}\int_{\R^d}(1+|\vvarx0|^2)^{q^*}\exp\left(-\frac{q^*|\vvarx0|^2}{2}\right).
-%	\end{align*}
-%\end{proof}
-
 \begin{proof}[Proof case 3:]

### 2021-01-21 paper.tex
slightly modified the introduction

@@
 \section{Introduction}
-The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was first proposed by \citet{Beck2009} and is now a very popular algorithm for minimising the sum of two convex functions.
-We will write this as the problem of computing
+The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by \citet{Beck2009}
+as an extension of Nesterov's fast gradient method (see~\cite{Nesterov2004})
+and is now a very popular algorithm for minimising the sum of two convex functions.
+We write this as the problem of computing 
 \begin{equation}\label{eq: min F = fD+fC}
@@
 \end{equation}
-where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function.
-The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$.
-\citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$ when $u^*\in \F H$ is finite dimensional and \cite{Chambolle2015} extended this result to the general Hilbert space setting.
-Many further works have gone on to demonstrate even faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.
+where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
+The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$. \citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$.
+% when $u^*\in \F H$ is finite dimensional and
+\cite{Chambolle2015} showed (up to a minor modification) convergence of the iterates in
+a general Hibert space setting.
+% extended this result to the general Hilbert space setting.
+Many further works have gone on to demonstrate %even
+faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.
 
@@
 The permitted refinement steps are also more broad in our work.
-
-\subsection{Canonical example}
-While the analysis of this work is applicable to general choices of $\func1$ and $\func2$, we will refer back to the example of the (Beurling) Lasso model both for motivation and for numerical examples.
-We state the Lasso energy as
-\begin{equation}\label{eq: Lasso energy intro}
-	\Func0(\varf0) = \tfrac12\norm{\A\varf0-\vdata0}_2^2 + \mu\norm{\varf0}_1,
-\end{equation}
-where $\vdata0\in\R^m$ is some observed data, $\A\colon \C M(\Domain)\to \R^m$ is the forward map and $\mu>0$ is an appropriately chosen scalar.
-We have $\F H = L^2(\Domain)$ and $\spcf0 = \C M(\Domain)$ the space of measures on $\Domain$ equipped with the $L^1$ norm.
-In the continuous setting $\Domain = [0,1]^d$ and for discrete we have $\Domain=\F N$, i.e.
-$\spcf0\cong\ell^1(\R)$.
-
-It is a well-known result of representer theorems for $\Func0$ \citep{Unser2016,Boyer2019} that there exist minimisers of the form 
-\begin{equation}
-	\varf0^* = \sum_{i=1}^{m}\vars0_i\delta_{\vvarx0_i}, 
-\end{equation}
-for some $\vars0_i\in\R$ and where $\delta_{\vvarx0_i}$ is the Dirac delta function centred at $\vvarx0_i\in\R^d$.
-
-This is a practical example where we have the relation $\varf0^*$ does not lie in the Hilbert space $\F H$, and yet it is very easy to approximate with a discrete basis.
-Our approach will be to use finite elements which can clearly generalise to other examples.
 
@@
 \section{Lasso minimisation}\label{sec: Lasso definition}
-We now return to the concrete example of Lasso which will be used for numerical results in \Cref{sec: numerics}.
+We now focus on the concrete example of Lasso which will be used for numerical results in \Cref{sec: numerics}.
 We consider three forms of Lasso which will be referred to as continuous, countable, and discrete Lasso depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
@@
 
-\begin{figure}[H]\centering
+\begin{figure}\centering
 	\includegraphics[width=.84\textwidth]{lasso_reduced_convergence}
@@
 	\caption{Continuous convergence of adaptive compared with uniform discretisation with respect to wall-clock time and total number of pixels (memory requirement).}\label{fig: comparison with time}
-\end{figure}
-
-\subsection{2D wavelet Lasso}\label{sec: wavelet examples}
-In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{\Varx0}^I_i$ where 
-\begin{equation}
-	\F{\Varx0}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{50},-\tfrac12+\tfrac{i}{50}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I \quad \text{ for } i,I=1,2,\ldots,50.
-\end{equation}
-This is not exactly in the form analysed by \Cref{thm: norm bound examples}, however for each $I$ the sets $\{\F{\Varx0}^I_i\st i\in[50]\}$ are disjoint therefore we can apply \Cref{thm: norm bound examples} block-wise to estimate
-\begin{equation}
-	\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[50]} |\F{\Varx0}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[50]} \int_{\F{\Varx0}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[50]}\ (\A\1)_{i,I}}\;.
-\end{equation}
-$\A$ is not smooth, therefore we can't bound $|\A^*|_{C^k}$ for $k>0$, and so we must look to minimise over $\ell^1$ rather than $L^1$.
-The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the Lasso form:
-\begin{equation}
-	\min_{\varf0\in \spcf0} \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu \norm{\linop{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \tfrac12\norm{\A\linop{W}\hat{\varf0}-\vdata0}_{\ell^2}^2 + \mu \norm{\hat{\varf0}}_{\ell^1}.
-\end{equation}
-The minimisers are related by $\varf0^* = \linop{W}\hat{\varf0}^*$ and, for wavelet bases, $\linop{W}$ is orthonormal so $\norm{\A\linop{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$.
-From \Cref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\linop{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$.
-If $\linop{W}$ is a wavelet transformation then its columns, $w_j\in L^2$, are simply the wavelets themselves and we can use the bound
-\begin{equation}
-	|\IP{w_j}{\A^*\vvard0_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vvard0_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vvard0_n}_{L^2}\leq \norm{\1_{\F{\Varx0}} \A^*\vvard0_n}_{L^2}
-\end{equation}
-for all $\F{\Varx0}\supset \supp(w_j)$.
-In the case of the Radon transform, we can compute the left-hand side explicitly for the finitely many $j\in J_n$ but we wish to use the right-hand side in a structured way to avoid computing the infinitely many $j\notin J_n$.
-To do this, we will take a geometrical perspective on the construction of wavelets to view them in a tree format.
-
-\paragraph{Tree structure of wavelets}
-Finite elements are constructed with a mesh which provided a useful tool for adaptive refinement in \Cref{sec: bound continuous}.
-For wavelets, we will associate a tree with every discretisation and the leaves of the tree form a mesh.
-This perspective comes from the multi-resolution interpretation of wavelets.
-An example is seen in \Cref{fig: wavelet tree} for 1D Haar wavelets, $w_{j,k}(\varx0) = \sqrt{2}^k\vard1(2^{k}\varx0-j)$ where $\vard1 = \1_{[0,1)} - \1_{[-1,0)}$.
-\begin{figure}\begin{center}\begin{tikzpicture}[grow'=right]
+
+	\vspace*{\floatsep}
+
+	\begin{center}\begin{tikzpicture}[grow'=right]
 		\tikzstyle{level 1}=[level distance=5em, sibling distance=0em];
@@
 \end{figure}
+
+\subsection{2D wavelet Lasso}\label{sec: wavelet examples}
+In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{\Varx0}^I_i$ where 
+\begin{equation}
+	\F{\Varx0}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{50},-\tfrac12+\tfrac{i}{50}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I \quad \text{ for } i,I=1,2,\ldots,50.
+\end{equation}
+This is not exactly in the form analysed by \Cref{thm: norm bound examples}, however for each $I$ the sets $\{\F{\Varx0}^I_i\st i\in[50]\}$ are disjoint therefore we can apply \Cref{thm: norm bound examples} block-wise to estimate
+\begin{equation}
+	\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[50]} |\F{\Varx0}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[50]} \int_{\F{\Varx0}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[50]}\ (\A\1)_{i,I}}\;.
+\end{equation}
+$\A$ is not smooth, therefore we can't bound $|\A^*|_{C^k}$ for $k>0$, and so we must look to minimise over $\ell^1$ rather than $L^1$.
+The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the Lasso form:
+\begin{equation}
+	\min_{\varf0\in \spcf0} \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu \norm{\linop{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \tfrac12\norm{\A\linop{W}\hat{\varf0}-\vdata0}_{\ell^2}^2 + \mu \norm{\hat{\varf0}}_{\ell^1}.
+\end{equation}
+The minimisers are related by $\varf0^* = \linop{W}\hat{\varf0}^*$ and, for wavelet bases, $\linop{W}$ is orthonormal so $\norm{\A\linop{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$.
+From \Cref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\linop{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$.
+If $\linop{W}$ is a wavelet transformation then its columns, $w_j\in L^2$, are simply the wavelets themselves and we can use the bound
+\begin{equation}
+	|\IP{w_j}{\A^*\vvard0_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vvard0_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vvard0_n}_{L^2}\leq \norm{\1_{\F{\Varx0}} \A^*\vvard0_n}_{L^2}
+\end{equation}
+for all $\F{\Varx0}\supset \supp(w_j)$.
+In the case of the Radon transform, we can compute the left-hand side explicitly for the finitely many $j\in J_n$ but we wish to use the right-hand side in a structured way to avoid computing the infinitely many $j\notin J_n$.
+To do this, we will take a geometrical perspective on the construction of wavelets to view them in a tree format.
+
+\paragraph{Tree structure of wavelets}
+Finite elements are constructed with a mesh which provided a useful tool for adaptive refinement in \Cref{sec: bound continuous}.
+For wavelets, we will associate a tree with every discretisation and the leaves of the tree form a mesh.
+This perspective comes from the multi-resolution interpretation of wavelets.
+An example is seen in \Cref{fig: wavelet tree} for 1D Haar wavelets, $w_{j,k}(\varx0) = \sqrt{2}^k\vard1(2^{k}\varx0-j)$ where $\vard1 = \1_{[0,1)} - \1_{[-1,0)}$.
+
 In higher dimensions, the only two things which change are the number of children ($2^d$ for non-leaves) and at each node you store the coefficients of $2^d-1$ wavelets.
@@
 
-\begin{figure}[H]\centering
+\begin{figure}\centering
 	\includegraphics[width=.85\textwidth]{haar_data}
@@
 \end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2021-01-21 paper.tex
quick sync

@@
 \section{Introduction}
-The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by \citet{Beck2009}
-as an extension of Nesterov's fast gradient method (see~\cite{Nesterov2004})
-and is now a very popular algorithm for minimising the sum of two convex functions.
-We write this as the problem of computing 
+The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was first proposed by \citet{Beck2009} and is now a very popular algorithm for minimising the sum of two convex functions.
+We will write this as the problem of computing
 \begin{equation}\label{eq: min F = fD+fC}
@@
 \end{equation}
-where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
-The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$. \citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$.
-% when $u^*\in \F H$ is finite dimensional and
-\cite{Chambolle2015} showed (up to a minor modification) convergence of the iterates in
-a general Hibert space setting.
-% extended this result to the general Hilbert space setting.
-Many further works have gone on to demonstrate %even
-faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.
+where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function.
+The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$.
+\citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$ when $u^*\in \F H$ is finite dimensional and \cite{Chambolle2015} extended this result to the general Hilbert space setting.
+Many further works have gone on to demonstrate even faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.
 
@@
 \end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2021-01-21 paper.tex
manual merge of changes
For some reason my push just wiped out the previous changes to the .tex.

--- 2021-01-21 paper.tex
@@
 \section{Introduction}
-The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by \citet{Beck2009}
-as an extension of Nesterov's fast gradient method (see~\cite{Nesterov2004})
-and is now a very popular algorithm for minimising the sum of two convex functions.
+The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by \citet{Beck2009} as an extension of Nesterov's fast gradient method (see~\cite{Nesterov2004}) and is now a very popular algorithm for minimising the sum of two convex functions.
 We write this as the problem of computing
@@
 where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
-The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$. \citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$.
-% when $u^*\in \F H$ is finite dimensional and
+The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$.
+\citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$.
 \cite{Chambolle2015} showed (up to a minor modification) convergence of the iterates in
-a general Hibert space setting.
-% extended this result to the general Hilbert space setting.
-Many further works have gone on to demonstrate %even
-faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.
+a general Hibert space setting. Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.
 

### 2021-08-04 response.tex
First response to reviewer comments
Many changes throughout document. Changes are tracked with \edit macro.

\documentclass[12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{amsmath,amsfonts,color}
\usepackage[normalem]{ulem}

\newcommand*\justify{%
	\fontdimen2\font=0.4em% interword space
	\fontdimen3\font=0.2em% interword stretch
	\fontdimen4\font=0.1em% interword shrink
	\fontdimen7\font=0.1em% extra space
	\hyphenchar\font=`\-% allowing hyphenation
}
\newcommand{\review}[1]{\texttt{\justify{#1}}}
\newcommand{\F}[1]{\mathbb{#1}}
\let\vecf\vec
\renewcommand{\vec}[1]{\mathbf{#1}}
\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
\renewcommand{\ULthickness}{1.0pt}
\newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
\newcommand{\todo}[1]{{\color{red} #1}}

\title{Response to reviewer comments:\\``FISTA'' in Banach spaces with adaptive discretisations}
\author{Antonin Chambolle and Robert Tovey}
\date{\todo{31st October 2021}}

\begin{document}
\maketitle

We would like to thank both the reviewers for their time and feedback. All changes are marked in the supplementary pdf and a detailed response to each reviewer is given below.

\section{Detailed response to first reviewer}

\begin{enumerate}
	\item \review{The authors base much of the analysis on the objective function and its convergence properties \ldots it would be interesting to know how the solutions $w_n$ converge for the various versions of FISTA.}

	We thank the reviewer for their suggestion but it seems quite challenging to make a general statement. As in your comment, if one has coercivity then the convergence is clear. FISTA is known to converge weakly in the Hilbert-space setting, these guarantees are likely to hold here with the added adaptivity although we have not performed the analysis as it is still a relatively special case. A key component of this is the result $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, in general we do not even expect this quantity to be bounded. It's not clear whether we can leverage the Hilbert-norm structures of FISTA to gain convergence in the Banach space.

	\item \review{On page 9, line 27 the authors require $\Omega$ to be a compact set. Perhaps I am overseeing something, but I would assume that the authors mean to say that $\Omega$ is a connected, open, and bounded set with sufficiently smooth boundary so that $\bar\Omega$ is compact.}

	Thank you, we have made the suggested edit.

	\item \review{page 10 line 21 and 38 typos: Sectoin and although although}

	These typos have been corrected.

	\item \review{page 10 line 36: In the infinite-dimensional context, I think it is clear what the authors mean with $\lVert\cdot\rVert_1$. They clearly state it as TV in (15), but it is a bit misleading especially later when they use $\lVert\cdot\rVert_\infty$.}

	This has been clarified in the text, now equations (15) and (21)-(24). The $\lVert\cdot\rVert_\infty$ only appears as the dual-norm of our ${\vert\kern-0.25ex\vert\kern-0.25ex\vert \cdot \vert\kern-0.25ex\vert\kern-0.25ex\vert}$.

	\item \review{page 12 and elsewhere: $\partial E$ is usually referred to as the subdifferential. I suppose this depends on the literature source you use.}

	As suggested, we have switched to using the term `subdifferential' throughout the document.

	\item \review{My only ``disappointment'' with the paper is that the theory is illustrated with LASSO. As a result, $E$ has a rather favorable structure. There are many examples, e.g., in robust statistics, where it would be more appropriate to use the $\ell^1$ norm instead of the $\ell^2$ norm for misfit. Since the favorable properties of the squared $\ell^2$-norm are often used in the derivations (bounds, constants, etc. in Section 6), I wonder how hard it would be to do the same for other relevant examples.}

	We have avoided non-smooth misfit terms because they are not so convenient for the FISTA framework, one might use a primal-dual or ADMM algorithm to avoid solving a least-squares problem on every iteration. For smooth misfits, you are quite right that most of Sections 6 and 7 can be generalised. The main difference is that the dual problem is very simple for quadratic misfits. If it is hard to compute $E_0(u_n)$, then one has to rely on the subdifferential for the a posteriori refinement strategy.

	\todo{I'm not sure what is being requested here. Is he asking for another numerical example? We could change the data fidelity for the Wavelet example quite easily? I'm actually struggling to think of another common smooth data fidelity which isn't Entropy-smoothed OT...}

	\item \review{page 17, line 28: missing word? ``most require''?}

	Thank you for noticing this mistake.

	\item \review{On page 18, the authors state: Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms}

	\review{This is used to argue that the adaptive schemes are better as they require smaller problems, less memory and less time to get to this point. However, it would appear that Figure 2 indicates that if a sufficiently accurate solution were desired, instead of a point with $E_0(u_n)\leq 0.1$, then we would still need orders of magnitude of 10 more iterations to get to the same accuracy as the nonadaptive schemes.}

	The convergence displayed in Figure 2 is relative to the discretised problem, rather than the continuous one. The behaviour for the continuous gap is shown in Figure 3 (for two of the algorithms from Figure 2). Figure 2 shows that the nonadaptive schemes reach high precision very quickly, but Figure 3 indicates that this does not correlate with accuracy.

	\todo{I could include extra continuous gap (like Figure 1) panels? Or just show continuous gap? At the moment it's perhaps a bit confusing, figures (1,2,3,4,7,9) show (both, discrete, continuous, continuous, discrete, continuous) respectively. It might be simpler just to show the continuous gap after Figure 1 (which compares both).}
\end{enumerate}

\section{Detailed response to second reviewer}
We are very sorry that you found our manuscript so difficult to read. We have tried to extrapolate your comments to also make changes to the rest of the document. To address your first comments we have removed much of the emphasis on the Banach space $\F U$ so that most computations are clearly in the Hilbert space. The Banach space setting is reserved for examples discussed in Sections 5 to 7.

\begin{enumerate}
	\item \review{The main criticism is on section 2: In this section, there are no assumptions that relate $U$ and $H$. If $U=\bar{H}$ (closure in the norm of $U$?) like on page 1, then $H\subset U$, the subspaces $U_n$ are all subspaces of $H$, and $\Pi_n$ is the Riesz isomorphism on $U_n$, which should be the orthogonal projection of the the Riesz isomorphism on $H$ onto $U_n$. Here it is necessary that $U_n$ is a closed subspace.}

	As suggested, we now state that $\F U^n$ are closed in (9) and re-referenced throughout the document. The mention of $\F U$ on page 1 is now just a reference to the Lasso example introduced in a later section.

	\item \review{If $H$ is not a subspace of $U$ then it is not clear that such a projection $\Pi_n$ exists at all.}

	The projections $\Pi_n$ are now defined only on $\F H$.

	\item \review{I wonder, where in the paper the choice of the Banach space $U$ or the properties of $u^*$ matter. I have the impression that the results are all valid, if $U$ is removed from the paper and $E_0$ is defined as $E_0(u)=E(u)-\inf_{v\in H}E(v)$. Then the resulting algorithm tries to compute the infimum of $E$ on $H$ (which might not be attained).}

	Thank you for the suggestion. As previously mentioned, the main introduction of $\F U$ is now postponed to around Section 5.

	\item \review{The line (p2, l 54) defining $\Pi_n$ looks strange: the pairings $\langle\cdot,\cdot\rangle$ cannot both denote the inner product on $H$ as $u\in U_n^*$ might not be in $H$}

	As commented before, we define $\Pi_n$ on $\F H$ to remove the ambiguity.

	\item \review{p.3: in what topology do you want to consider the closure of $U_n^*$? Why is that necessary at all?}

	As commented before, we define $\Pi_n$ on $\F H$ instead of $\F U_n^*$.

	\item \review{These definitions clash in the proof of Lemma 1 (Thm 6): There $w\in U_n+U_{n-1}$ has to be mapped into $U_n^*$ to be able to apply Lemma 2. This happens by means of an unnamed mapping, lets call it $M$, with the property $\Pi_nMw=w$. Again it is not clear whether this mapping exists (under the very abstract setting without any relation between $U$, $H$ and $U_n$, $U_{n-1}$. I think the claimed inequality (68) is wrong if $U_{n-1}$ is not a subspace of $U_n$, as in that case some projections of $u_{n-1}$ onto $U_n$ have to appear in (68).}

	Lemma 1 has now been modified to have $w\in \F U^n$. Equation (9) also has the assumption $u_{n-1}\in \F U^n$, instead of the suggested $\F U^{n-1}\subset \F U^n$.

	\item \review{On page 1, the functions $f,g$ are defined on $H$ only}

	The optimisation is now performed on $\F H$ only.

	\item \review{Does (5) imply strong or weak lower semicontinuity of $g$?}

	$g$ only needs to be weakly lower-semicontinuous for the existence of minimisers. This is now clarified further in the text (now equation (4)).

	\item \review{Lemma 1: There is no Lemma 1 in [10]}

	We apologise for the mistake, the numbering has now been updated.

	\item \review{Lemma 2 (and its proof): There is no Theorem 2 in [10], not even a theorem that somehow resembles the claimed inequality. Also there is no Theorem 1 in [3], at least not in the version of the paper that can be found on Amir Beck's homepage.}

	Again, we apologise for these mistakes and have corrected the references.

	\item \review{p. 5, line 47: should be $\lVert u\rVert_{L^2(0,1)}^2$.}

	This has been modified in the text.
\end{enumerate}

\end{document}

### 2021-08-04 paper.tex
First response to reviewer comments
Many changes throughout document. Changes are tracked with \edit macro.

@@
-\documentclass[10pt,a4paper,onecolumn]{article}
+\RequirePackage{fix-cm}
+\documentclass[smallextended]{svjour3}
+\bibliographystyle{spmpsci}      % mathematics and physical sciences
+\smartqed  % flush right qed marks, e.g. at end of proof
+\usepackage{mathptmx}      % use Times fonts if available on your TeX system
+\usepackage{graphicx}
+\journalname{Computational Optimization and Applications}
+
 \usepackage{amsmath,enumitem,datetime,xfrac,fix-cm,color,multirow,siunitx}
-\usepackage{amsfonts,amssymb,mathtools,stmaryrd,dsfont,tikz,amsthm,bm}
-\usepackage[round,colon,authoryear]{natbib}
-\usepackage[cm]{fullpage}
-\definecolor{linkColor}{rgb}{0.5, 0.5, 0.5}
-\usepackage[colorlinks, allcolors=linkColor, bookmarks=True]{hyperref}
-\usepackage[capitalise]{cleveref}
+\usepackage{amssymb,mathtools,stmaryrd,dsfont,tikz}
+\usepackage{fullpage}
+\usepackage[colorlinks, citecolor=blue, bookmarks=True]{hyperref}
 \usetikzlibrary{positioning,trees}
@@
 \DeclareGraphicsExtensions{.pdf,.png}
-\numberwithin{equation}{section}
-\newtheorem{definition}{Definition}[section]\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]\newtheorem{example}{Example}[section]
-\newtheorem{remark}{Remark}[section]
-\makeatletter\let\c@definition\c@theorem\let\c@definition\c@theorem\makeatother
-\makeatletter\let\c@lemma\c@theorem\let\c@lemma\c@theorem\makeatother
-\makeatletter\let\c@example\c@theorem\let\c@example\c@theorem\makeatother
-\makeatletter\let\c@remark\c@theorem\let\c@remark\c@theorem\makeatother
-\newtheorem*{theorem*}{Theorem}
-
-\newcommand{\Partial}[2]{\frac{\partial #1}{\partial #2}}
-\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\C{A}}
-\newcommand{\Vector}[3]{ \begin{pmatrix} #1 \\ #2 \\ #3 \end{pmatrix}}
-\newcommand{\MTwo}[4]{\begin{pmatrix} #1 & #2 \\ #3 & #4 \end{pmatrix}}
+
+\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\tens{A}}
+\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
 \newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
-\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
 \renewcommand{\sfrac}[2]{\,^{#1}\!\!/\!_{#2}}
-\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
-\newcommand{\op}[1]{\operatorname{#1}}\newcommand{\overtext}[2]{\stackrel{\text{#1}}{#2}}
-\newcommand{\xmapsfrom}[1]{\reflectbox{$\xmapsto{\reflectbox{\scalebox{0.87}[0.69]{$#1$}}}$}}
+\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}
+\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
+\newcommand{\op}[1]{\operatorname{#1}}
 \newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
-\renewcommand{\P}{\F{P}}\newcommand{\E}{\F{E}}\newcommand{\1}{\F{1}}
-\renewcommand{\circle}[1]{\raisebox{.5pt}{\rm{\textcircled{\raisebox{-.9pt} {#1}}}}}
-\newcommand{\intbar}{-\hspace{-10.5pt}\int}\newcommand{\todo}[1]{{\color{red}#1}}
-\DeclareMathOperator{\st}{\;s.t.\;}\DeclareMathOperator{\as}{\;a.s.\;}\renewcommand{\epsilon}{\varepsilon}
-\DeclareMathOperator*{\Union}{\bigcup}\DeclareMathOperator{\union}{\cup}
-\DeclareMathOperator*{\Intersect}{\bigcap}\DeclareMathOperator{\intersect}{\cap}
-\renewcommand{\bar}{\overline}\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
-\renewcommand{\vec}{\mathbf}
-\DeclareMathOperator*{\argmin}{argmin}\DeclareMathOperator{\TV}{TV}
-\DeclareMathOperator{\prox}{prox}\DeclareMathOperator{\supp}{supp}
-\DeclareMathOperator{\id}{id}\DeclareMathOperator{\sign}{sign}
+\newcommand{\1}{\F{1}}
+\DeclareMathOperator{\st}{\;s.t.\;}
+\renewcommand{\epsilon}{\varepsilon}\renewcommand{\bar}{\overline}
+\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
+\DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator{\supp}{supp}
+\DeclareMathOperator{\id}{id}
+\DeclareMathOperator{\sign}{sign}
+\newcommand{\Emin}[1][\varf0]{\inf_{#1\in\F H}\op{E}(#1)}
 
@@
 \newenvironment{adaptiveStep}{\refstepcounter{adaptStepCounter}}{}
-\crefname{adaptStepCounter}{Step}{Steps}
 
 % TODO: get rid of this stuff...
-\let\linop\C
 \usepackage{clipboard}\newclipboard{aFEMclipboard}
-\newcommand{\UCmath}[1]{%
-	\begingroup
-	\ucmathlist\uppercase\expandafter{#1}%
-	\endgroup
-}
-\newcommand{\ucmathlist}{%
-	\def\alpha{\mathrm{A}}%
-	\def\beta{\mathrm{B}}%
-	\let\gamma=\Gamma
-	\let\delta=\Delta
-	\def\epsilon{\mathrm{E}}%
-	\def\varepsilon{\mathrm{E}}%
-	\def\zeta{\mathrm{Z}}%
-	\def\eta{\mathrm{H}}%
-	\let\theta=\Theta
-	\let\vartheta=\Theta
-	\def\iota{\mathrm{I}}%
-	\def\kappa{\mathrm{K}}%
-	\let\lambda=\Lambda
-	\def\mu{\mathrm{M}}%
-	\def\nu{\mathrm{N}}%
-	\let\xi=\Xi
-	\let\pi=\Pi
-	\let\varpi=\Pi
-	\def\rho{\mathrm{P}}%
-	\def\varrho{\mathrm{P}}%
-	\let\sigma=\Sigma
-	\def\tau{\mathrm{T}}%
-	\let\upsilon=\Upsilon
-	\let\phi=\Phi
-	\let\varphi=\Phi
-	\def\chi{\mathrm{X}}%
-	\let\psi=\Psi
-	\let\omega=\Omega
-}
-\newcommand{\caps}[1]{\UCmath{#1}}
 \usepackage{xstring}
-\newcommand*{\Func}[1]{%
-	\IfEqCase{#1}{%
-		{0}{\op{E}}%
-		{1}{\op{F}}%
-		{2}{\op{G}}%
-		{3}{\op{H}}%
-	}[\op{F}#1]%
-}
-\newcommand*{\func}[1]{%
-	\IfEqCase{#1}{%
-		{0}{\op{e}}%
-		{1}{\op{f}}%
-		{2}{\op{g}}%
-		{3}{\op{h}}%
-	}[\op{f}#1]%
-}
 \newcommand*{\varf}[1]{%
@@
 }
+\newcommand*{\Varf}[1]{%
+	\IfEqCase{#1}{%
+		{0}{U}%
+		{1}{V}%
+		{2}{W}%
+	}[u#1]%
+}
 \newcommand*{\spcf}[1]{%
@@
 	}[\varphi #1]%
-}
-\newcommand*{\spcd}[1]{%
-	\IfEqCase{#1}{%
-		{0}{\Phi}%
-		{1}{\Psi}%
-	}[\Phi#1]%
 }
@@
 	}[x#1]%
-}
-\newcommand*{\vart}[1]{%
-	\IfEqCase{#1}{%
-		{0}{s}%
-		{1}{t}%
-	}[t#1]%
 }
@@
 }
-\newcommand*{\data}[1]{%
+\newcommand*{\Vars}[1]{%
 	\IfEqCase{#1}{%
-		{0}{\eta}%
-		{1}{\nu}%
-	}[g]%
-}
-\newcommand{\Domain}{\Omega}
-\newcommand{\domain}{\omega}
+		{0}{\mathrm{A}}%
+		{1}{\mathrm{B}}%
+		{2}{\Gamma}%
+		{3}{A}%
+		{4}{B}%
+		{5}{C}%
+	}[K#1]%
+}
+\newcommand{\data}{\eta}
+\newcommand{\Domain}{\Omega}\newcommand{\domain}{\omega}
 \newcommand{\diam}{\op{diam}}
 \newcommand{\meshsize}{h}
-\DeclareMathOperator{\noise}{noise}
-
-% capital forms
-\newcommand*{\Varx}[1]{\caps{\varx{#1}}}
-\newcommand*{\Varf}[1]{\caps{\varf{#1}}}
-\newcommand*{\Vart}[1]{\caps{\vart{#1}}}
-\newcommand*{\Vars}[1]{\caps{\vars{#1}}}
+
 % vector forms
-\newcommand*{\vvarx}[1]{\vec{\varx{#1}}}\newcommand*{\vVarx}[1]{\vec{\Varx{#1}}}
-\newcommand*{\vvart}[1]{\vec{\vart{#1}}}\newcommand*{\vvars}[1]{\vec{\vars{#1}}}
-\newcommand*{\vvard}[1]{\vec{\vard{#1}}}\newcommand*{\vdata}[1]{\vec{\data{#1}}}
-\newcommand*{\vVarf}[1]{\vecf{\Varf{#1}}}\newcommand*{\vvarf}[1]{\vecf{\varf{#1}}}
-
-%\renewcommand{\Paste}[1]{}
-
-\author{Robert Tovey and Antonin Chambolle}
-\date{\longdate\today}
-\title{FISTA with adaptive discretisations}
+\newcommand*{\vvarx}[1]{\vec{\varx{#1}}}
+\newcommand*{\vvars}[1]{\vec{\vars{#1}}}
+\newcommand*{\vvard}[1]{\vec{\vard{#1}}}
+
+% Macro for tracking changes
+\usepackage[normalem]{ulem}\renewcommand{\ULthickness}{1.0pt}
+\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
+\newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
+%\renewcommand{\edit}[2]{#2}
+
+\author{Antonin Chambolle \and Robert Tovey }
+\institute{A. Chambolle \at
+	CEREMADE, CNRS \& Université Paris Dauphine, PSL Research University, Paris \\
+	\email{chambolle@ceremade.dauphine.fr}, ORCID: 0000-0002-9465-4659          %  \\
+	\and
+	R. Tovey \at
+	MOKAPLAN, INRIA Paris, Paris \\
+	\email{robert.tovey@inria.fr}, ORCID: 0000-0001-5411-2268
+}
+\title{``FISTA'' in Banach spaces with adaptive discretisations}
 \begin{document}
@@
 
+	\begin{abstract}
+		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever the optimisation domain is contained in a suitable Hilbert space.
+We propose a modified algorithm where each iteration is performed in a subspace, and that subspace is allowed to change at every iteration.
+Analytically, this allows us to guarantee convergence in a Banach space setting, although at a reduced rate depending on the conditioning of the specific problem.
+Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.
+	\end{abstract}
+	\keywords{Convex optimization \and Multiscale \and Multigrid \and Sparsity \and Lasso}
+
 	\section{Introduction}
-The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by \citet{Beck2009} as an extension of Nesterov's fast gradient method (see~\cite{Nesterov2004}) and is now a very popular algorithm for minimising the sum of two convex functions.
+	The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by Beck and Teboulle \cite{Beck2009} as an extension of Nesterov's fast gradient method \cite{Nesterov2004} and is now a very popular algorithm for minimising the sum of two convex functions.
 	We write this as the problem of computing
 	\begin{equation}\label{eq: min F = fD+fC}
-	u^* \in \argmin_{\varf0\in\F H}\Func0(\varf0)  \qquad\text{such that}\qquad \Func0(\varf0)\coloneqq \func1(\varf0) + \func2(\varf0),
-\end{equation}
-where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
+		\edit{u^* \in \argmin_{\varf0\in\F H}\op{E}(\varf0)}{\Emin}  \qquad\text{such that}\qquad \op{E}(\varf0)\coloneqq \op{f}(\varf0) + \op{g}(\varf0),
+	\end{equation}
+	where $\op{f}\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\op{g}\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
 The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$.
-\citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$.
-\cite{Chambolle2015} showed (up to a minor modification) convergence of the iterates in
-a general Hibert space setting. Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.
+It has been shown that $\op{E}(\varf0_n) - \edit{\op{E}(u^*)}{\Emin}$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}.
+Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \cite{Tao2016,Liang2017,Alamo2019}.
 
@@
 	\begin{itemize}
-	\item we extend the convergence results to the case $\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space.
+		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{the minimum is not achieved.
+For example, in Lasso discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}.
 The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
@@
 In the Hilbert space setting this is the original $n^{-2}$ rate.
-In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation in both measures of time and computer memory requirements.
+In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation, both in measures of time and computer memory requirements.
 	\end{itemize}
-\todo{There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for the use outside of Hilbert spaces is the key novelty.} Some other works for FISTA-like algorithms include \citep{Jiang2012,Villa2013}.
-Of particular note, our stability estimate for FISTA  in \Cref{thm: exponential FISTA convergence} is very similar to \cite[Proposition 2]{Schmidt2011} and \cite[Proposition 3.3]{Aujol2015}.
+	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for \edit{the use outside of Hilbert spaces}{use with un-attained minima} is the key theoretical novelty.
+Some other works for FISTA-like algorithms include \cite{Jiang2012,Villa2013}.
+Of particular note, our stability estimate for FISTA  in Theorem~\ref{thm: mini FISTA convergence} is very similar to \cite[Prop 2]{Schmidt2011} and \cite[Prop 3.3]{Aujol2015}.
 This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations.
-The ideas of \citet{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\func2$.
+The ideas in \cite{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\op{g}$.
 The permitted refinement steps are also more broad in our work.
@@
 	This chapter is organised as follows.
-\Cref{sec: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, \Cref{alg: refining FISTA}.
-The main theoretical contribution of this work is the convergence analysis of \Cref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in \Cref{sec: recipe}, then we state the specific results in the case of FISTA in \Cref{sec: FISTA convergence}.
-The main results are \Cref{thm: exponential FISTA convergence} and \Cref{thm: practical refinement criteria} which extend the convergence of FISTA to infinite dimensional Banach spaces with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.
-
-\Cref{sec: general examples} presents some general results for the application of \Cref{alg: refining FISTA} and \Cref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation.
-In particular, we describe how to choose efficient refining discretisations to approximate $\varf0^*$, estimate the convergence of $\Func0$, and identify the support of $\varf0^*$.
-The numerical results in \Cref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.
+Section~\ref{sec: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, Algorithm~\ref{alg: refining FISTA}.
+The main theoretical contribution of this work is the convergence analysis of Algorithm~\ref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in Section~\ref{sec: recipe}, then we state the specific results in the case of FISTA in Section~\ref{sec: FISTA convergence}.
+The main results are Theorems~\ref{thm: exponential FISTA convergence}/~\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.
+
+	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation.
+In particular, we describe how to choose efficient refining discretisations to approximate \edit{$\varf0^*$}{$\Emin$}, estimate the convergence of $\op{E}$, and identify the support of \edit{$\varf0^*$}{the minimiser}.
+The numerical results in Section~\ref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.
 
 	\section{Definitions and notation}\label{sec: prelims}
-We consider optimisation of \eqref{eq: min F = fD+fC} over two spaces, the Banach space $(\spcf0,\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
-\begin{equation} 
-	\exists\varf0^*\in \spcf0 \quad\st\quad \Func0(\varf0^*) = \min_{\varf0\in\spcf0}\Func0(\varf0) = \min_{\varf0\in\F H}\Func0(\varf0).
-\end{equation}
+	\edit{We consider optimisation of \eqref{eq: min F = fD+fC} over two spaces, the Banach space $(\spcf0,\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
+	\\\centerline{$\displaystyle \exists\varf0^*\in \spcf0 \quad\st\quad \op{E}(\varf0^*) = \min_{\varf0\in\spcf0}\op{E}(\varf0) = \inf_{\varf0\in\F H}\op{E}(\varf0).$}
 	Furthermore, define the translated energy
-\begin{equation}
-	\Func0_0\colon\spcf0\cup\F H\to \R,\qquad \Func0_0(\varf0) \coloneqq \Func0(\varf0)-\Func0(\varf0^*).
-\end{equation}
-Note that the value of $\Func0_0$ is uniquely defined, even if $\varf0^*$ may not be. \todo{We could just say $E_0=E$ without loss of generality, just like $L=1$.}
-
-The proposed generalised FISTA algorithm is stated in \Cref{alg: refining FISTA} for an arbitrary choice of refining subspaces $\spcf0^n\subset \spcf0\cap\F H$ for $n=0,1,\ldots$.
-The only difference is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$.
-If $\spcf0^n=\spcf0=\F H$ then we recover the standard FISTA algorithm.
+	\\\centerline{$\displaystyle \op{E}_0\colon\spcf0\cup\F H\to \R,\qquad \op{E}_0(\varf0) \coloneqq \op{E}(\varf0)-\op{E}(\varf0^*).$}
+	Note that the value of $\op{E}_0$ is uniquely defined, even if $\varf0^*$ may not be.%
+	\\}{%
+	We consider optimisation of \eqref{eq: min F = fD+fC} over a Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$ with the translated energy
+	\begin{equation}
+		\op{E}_0\colon\F H\to \R,\qquad \op{E}_0(\varf0) \coloneqq \op{E}(\varf0)-\Emin[\tilde{\varf0}].
+	\end{equation}
+	}
+
+	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining }{closed }subspaces $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n=0,1,\ldots$.
+The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$.
+If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{classical} algorithm.
 
 	Without loss of generality we will assume $L=1$, i.e.
-$\nabla\func1$ is 1-Lipschitz.
-To get the general statement of any of the results which follow, replace $\Func0$ with $\frac{\Func0}{L}$.
-A more important distinction is to say that the properties of $\func1$ and $\func2$ are stated with respect to the Hilbert norm.
-In particular,
-\begin{equation}
-	\norm{\nabla\func1(\varf0)- \nabla\func1(\varf1)} \leq \norm{\varf0-\varf1}
-\end{equation}
-for all $\varf0,\varf1\in\F H$ and $\func2$ is called `simple' if
-\begin{equation}
-	\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \func2(\varf0)
+$\nabla\op{f}$ is 1-Lipschitz.
+To get the general statement of any of the results which follow, replace $\op{E}$ with $\frac{\op{E}}{L}$.\edit{ A more important distinction is to say that the properties of $\op{f}$ and $\op{g}$ are stated with respect to the Hilbert norm.}{} In particular,
+	\begin{equation}
+		\norm{\nabla\op{f}(\varf0)- \nabla\op{f}(\varf1)} \leq \norm{\varf0-\varf1}
+	\end{equation}
+	for all $\varf0,\varf1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
+	\begin{equation}
+		\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \op{g}(\varf0)
 	\end{equation}
 	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$.
-
-One defining property of the FISTA algorithm is an appropriate choice of inertia, dictated by $\vart1_n$. In particular, we will say that $(\vart1_n)_{n=0}^\infty$ is a \emph{FISTA stepsize} if
+\edit{}{We denote the orthogonal projection operators $\tens{\Pi}_n\colon\F H\to\spcf0^n$ such that $\tens{\Pi}_n\varf0-\varf0 \perp \varf1$ for all $\varf0\in\F H$, $\varf1\in\spcf0^n$.}
+
+	One defining property of the FISTA algorithm is an appropriate choice of inertia, dictated by $t_n$. In particular, we will say that $(t_n)_{n=0}^\infty$ is a \emph{FISTA stepsize} if
 	\begin{equation}\label{def: t_n and rho_n}
-	t_0 = 1, \qquad t_n \geq 1, \qquad \text{and}\qquad \rho_n \coloneqq t_n^2 - t_{n+1}^2 + t_{n+1} \geq 0\qquad \text{ for all }n=0,1,\ldots
-\end{equation}
-
-Finally we introduce the concept of an orthogonal projection in the setting of this work.
-For a subspace $\spcf0^n\subset\spcf0\cap\F H$ we define the orthogonal projection $\Pi_n\colon (\spcf0^n)^*\to \spcf0^n$ to be any extension of the function such that
-$$\IP{\Pi_n\varf0}{\varf1} = \IP{\varf0}{\varf1} \text{ for all } \varf0\in(\spcf0^n)^*, \ \varf1\in\spcf0^n.$$
+		t_0 = 1, \qquad t_n \geq 1, \qquad \text{and}\qquad \rho_n \coloneqq t_n^2 - t_{n+1}^2 + t_{n+1} \geq 0\qquad \text{ for all }n=0,1,\ldots.
+	\end{equation}
+
+	\edit{Finally we introduce the concept of an orthogonal projection in the setting of this work.
+For a subspace $\spcf0^n\subset\spcf0\cap\F H$ we define the orthogonal projection $\tens{\Pi}_n\colon (\spcf0^n)^*\to \spcf0^n$ to be any extension of the function such that
+	\\\centerline{$\IP{\tens{\Pi}_n\varf0}{\varf1} = \IP{\varf0}{\varf1} \text{ for all } \varf0\in(\spcf0^n)^*, \ \varf1\in\spcf0^n.$}
 	This definition is non-standard as we view $(\spcf0^n)^*$ embedded in $\spcf0$.
-Note that $\spcf0^n\subset\F H$ implies that $(\spcf0^n)^*\supset\F H$, therefore $\Pi_n$ is an extension of the classical orthogonal projection.
-It is convenient to allow an extension here because $\spcf0$ may be bigger than $\F H$, $(\spcf0^n)^*$ is the largest space such that $\Pi_n$ is sufficiently well-defined.
-Beyond this, the Hahn-Banach theorem may allow the domain of $\Pi_n$ to be extended further, but the definition is no longer unique.
+Note that $\spcf0^n\subset\F H$ implies that $(\spcf0^n)^*\supset\F H$, therefore $\tens{\Pi}_n$ is an extension of the classical orthogonal projection.
+It is convenient to allow an extension here because $\spcf0$ may be bigger than $\F H$, $(\spcf0^n)^*$ is the largest space such that $\tens{\Pi}_n$ is sufficiently well-defined.
+Beyond this, the Hahn-Banach theorem may allow the domain of $\tens{\Pi}_n$ to be extended further, but the definition is no longer unique.
 For example, in 1D the value of $\IP{\delta_0}{\frac{1}{\sqrt[4]{\varx0}}}$ is not well-defined, but the value of $\IP{\delta_0}{\1_{[0,1]}}$ can be chosen to be consistent with some sequence of molifiers.
-To account for this possibility, we shall state that the domain of $\Pi_n$ is $\bar{(\spcf0^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.
+To account for this possibility, we shall state that the domain of $\tens{\Pi}_n$ is $\bar{(\spcf0^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.}{}
 
@@
 	\end{align*}
-
-\begin{algorithm}\caption{Refining sub-space FISTA}\label{alg: refining FISTA}
+	\edit{}{For $n\in\F N$ we use the abbreviation $[n] = \{1,2,\ldots,n\}$. When the subdifferential of $\op{E}$ is set-valued, we will use the short-hand
+	\begin{equation}
+		\Norm{\partial\op{E}(\varf0)} \coloneqq \inf_{\varf1\in\partial\op{E}(\varf0)}\Norm{\varf1}
+	\end{equation}
+	for any norm $\Norm\cdot$.}
+
+	\begin{algorithm}\caption{Refining subspace FISTA}\label{alg: refining FISTA}
 		\centering
 		\begin{algorithmic}[1]
-		\State Choose $(\spcf0^n)_{n\in\F N}$, $\varf0_0\in \spcf0^0$ and some FISTA stepsize choice $(\vart1_n)$
+			\State Choose $(\spcf0^n)_{n\in\F N}$, $\varf0_0\in \spcf0^0$ and some FISTA stepsize choice $(t_n)_{n\in\F N}$
 			\State $\varf1_0\gets \varf0_0, n\gets0$
 			\Repeat
-		\State $\bar{\varf0}_n \gets (1-\tfrac{1}{\vart1_n})\varf0_n + \tfrac{1}{\vart1_n}\varf1_n$
-		\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \func1(\bar{\varf0}_n)}^2+\func2(\varf0)$ \Comment{Only modification, $\spcf0^{n+1}\subset \spcf0$}
-		\State $\varf1_{n+1} \gets (1-\vart1_n)\varf0_n + \vart1_n\varf0_{n+1}$
+			\State $\bar{\varf0}_n \gets (1-\tfrac{1}{t_n})\varf0_n + \tfrac{1}{t_n}\varf1_n$
+			\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \op{f}(\bar{\varf0}_n)}^2+\op{g}(\varf0)$ \Comment{Only modification, $\spcf0^{n+1}\subset \spcf0$}
+			\State $\varf1_{n+1} \gets (1-t_n)\varf0_n + t_n\varf0_{n+1}$
 			\State $n\gets n+1$
@@
 	\section{General proof recipe}\label{sec: recipe}
-In this section we give an intuitive outline of the full proof for convergence of \cref{alg: refining FISTA} before giving formal theorems and proofs in the next section.
-First we recall the classical FISTA convergence guarantee given by \citet[Theorem 2]{Chambolle2015}:
+	In this section we give an intuitive outline of the full proof for convergence of Algorithm~\ref{alg: refining FISTA} before giving formal theorems and proofs in the next section.
+First we recall the classical FISTA convergence guarantee given by \cite[\edit{Theorem 2}{Thm 3.1}]{Chambolle2015}:
 	\begin{equation}\label{eq: classical FISTA}
-	t_N^2\Func0_0(\varf0_N) + \sum^{N-1}_{n=1}\rho_n\Func0_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf0^*}^2 \leq \tfrac12\norm{\varf0_0-\varf0^*}^2
+		t_N^2\op{E}_0(\varf0_N) + \sum^{N-1}_{n=1}\rho_n\op{E}_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf0^*}^2 \leq \tfrac12\norm{\varf0_0-\varf0^*}^2
 	\end{equation}
@@
 		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting subspaces $\spcf0^n$.
-In the notation of \cref{alg: refining FISTA}, \cref{thm: mini FISTA convergence} shows that
+In the notation of Algorithm~\ref{alg: refining FISTA}, Theorem~\ref{thm: mini FISTA convergence} shows that
 		\begin{equation}\label{eq: mini FISTA convergence}
-		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf2_N}^2 \leq \tfrac12\norm{\varf0_0-\varf2_0}^2 +\tfrac{\norm{\varf2_N}^2-\norm{\varf2_0}^2}2 + \sum^N_{n=1} \vart1_n\Func0_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}
-	\end{equation}
-	for $\varf2_n = \argmin_{\varf0\in\spcf0^n}\Func0(\varf0)$.
+			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf2_N}^2 \leq \tfrac12\norm{\varf0_0-\varf2_0}^2 +\tfrac{\norm{\varf2_N}^2-\norm{\varf2_0}^2}2 
+			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}
+		\end{equation}
+		for $\varf2_n \in \argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$.
 The similarities to \eqref{eq: classical FISTA} are clear.
-If $\spcf0^n=\spcf0$, then we have $\varf2_n=\varf0^*$ and the two estimates agree.
+If $\spcf0^n=\spcf0$, then we have $\varf2_n=\edit{\varf0^*}{\varf2_0}$ and the two estimates agree.
 These extra terms quantify the robustness to changing of discretisation.
@@
 		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\spcf0^n$.
-To do so, we construct a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\Func0}\geq1$ such that for each $k\in\F N$
-	\begin{equation}
-		n\leq n_k \implies \norm{\varf2_n} \lesssim \vars3_{\Varf0}^k, \qquad n\geq n_k \implies \Func0_0(\varf2_n) \lesssim \vars3_{\Func0}^{-k}.
+To do so, we construct a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
+		\begin{equation}
+			n\leq n_k \implies \norm{\varf2_n} \lesssim \vars3_{\Varf0}^k, \qquad n\geq n_k \implies \op{E}_0(\varf2_n) \lesssim \vars3_{\op{E}}^{-k}.
 		\end{equation}
@@
 
-	The value of $\vars3_{\Varf0}$ is dictated by the smoothness of the norm of $\spcf0$ with respect to that of $\F H$.
+		\edit{The value of $\vars3_{\Varf0}$ is dictated by the smoothness of the norm of $\spcf0$ with respect to that of $\F H$.
 If $\norm{\varf0^*}<\infty$, then the value is $\vars3_{\Varf0}=1$, otherwise there is some damage to the rate of convergence generated by this factor.
-On the other hand, the value of $\vars3_{\Func0}$ is dictated by the smoothness of $\Func0$ at the point $\varf0^*$.
-If an efficient basis is used, then $\vars3_{\Func0}$ is large.
-The trade-off between $\vars3_{\Func0}$ and $\vars3_{\Varf0}$ dictates the final convergence rate of the algorithm.
+On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ at the point $\varf0^*$.}{Suppose $\F H$ is contained in a Banach space $(\spcf0,\Norm\cdot)$ such that $\Norm{\varf2_n}\lesssim 1$, then $\vars3_{\Varf0}$ reflects the smoothness between the two norms.
+If $\vars3_{\Varf0}>1$, then we cannot guarantee the original $n^{-2}$ rate of convergence.
+On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ (measured in $\Norm\cdot$) near minimisers.} %
+		If an efficient basis is used, then $\vars3_{\op{E}}$ is large. The trade-off between $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$ dictates the final convergence rate of the algorithm.
 	\end{adaptiveStep}
@@
 	\begin{adaptiveStep}\label{step: step 3 convergence bound}
-	In this step we combine the FISTA stability estimate with the subspace approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\Func0}$ and $\vars3_{\Varf0}$.
+		In this step we combine the FISTA stability estimate with the subspace approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$.
 For example, if $\spcf0^n$ is of the form
@@
 		then many terms on the right-hand side of \eqref{eq: mini FISTA convergence} telescope to 0.
-The result of this is presented in \Cref{thm: mini exponential FISTA convergence} but the moral is that the stability error in \eqref{eq: mini FISTA convergence} should scale in proportion to the $k$ (related to the resolution) rather than the total number of iterations $N$.
+The result of this is presented in Lemma~\ref{thm: mini exponential FISTA convergence} but the moral is that the stability error in \eqref{eq: mini FISTA convergence} should scale in proportion to the $k$ (related to the resolution) rather than the total number of iterations $N$.
 	\end{adaptiveStep}
@@
 	\begin{adaptiveStep}\label{step: step 4 sufficiently fast}
-	In \Cref{step: step 3 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor.
-In particular, it is equivalent to run \Cref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed subspace $\spcf0^N$.
-The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\Func0_0(\varf0_N)\lesssim \norm{\varf0_0-\varf2_N}^2 = O(\vars3_{\Varf0}^{2K})$ for $N\leq n_K$.
-\Cref{thm: sufficiently fast} shows that \Cref{alg: refining FISTA} can achieve the same order of approximation so long as $\spcf0^n$ refine sufficiently quickly, i.e.
+		In Step~\ref{step: step 3 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor.
+In particular, it is equivalent to run Algorithm~\ref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed subspace $\spcf0^N$.
+The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\op{E}_0(\varf0_N)\lesssim \norm{\varf0_0-\varf2_N}^2 = O(\vars3_{\Varf0}^{2K})$ for $N\leq n_K$.
+Lemma~\ref{thm: sufficiently fast} shows that Algorithm~\ref{alg: refining FISTA} can achieve the same order of approximation, so long as $\spcf0^n$ refine sufficiently quickly, i.e.
 $n_k$ are sufficiently small.
@@
 	\begin{adaptiveStep}\label{step: step 5 sufficiently slow}
-	The result of \Cref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate.
-If the subspaces refine too quickly, then the influence of $\norm{\varf0^*}=\infty$ will slow the rate of convergence.
+		The result of Step~\ref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate.
+If the subspaces refine too quickly, then the influence of \edit{$\norm{\varf0^*}=\infty$}{$\norm{\varf0_n}\to\infty$} will slow the rate of convergence.
 If the resolution is too coarse then we are overfitting to the discrete minimiser, but if the resolution is too fine then convergence of the energy is slow.
-\Cref{thm: sufficiently slow} balances these two factors in an optimal way for \cref{alg: refining FISTA} resulting in a convergence rate of
-	$$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
-	for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\Func0}$. In particular, if $\varf0^*\in\F H$ then we recover the classical rate with $\kappa=0$.
+Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of
+		$$ \op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
+		for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\op{E}}$.
+In particular, if \edit{$\varf0^*\in\F H$}{the minimum is attained in $\F H$,} then we recover the classical rate with $\kappa=0$.
 	\end{adaptiveStep}
@@
 
-	Spatial adaptivity is robust, so long as the scaling properties of \Cref{step: step 2 smoothness} are satisfied.
-The only other constraint is to ensure that the partial telescoping of \Cref{step: step 3 convergence bound} still holds.
-\Cref{thm: mini exponential FISTA convergence} shows that a sufficient condition is
-	$$\spcf0^{n_k}\subset\spcf0^{n_k+1}\subset\ldots\subset\spcf0^{n_{k+1}-1}.$$
+		Spatial adaptivity is robust, so long as the scaling properties of Step~\ref{step: step 2 smoothness} are satisfied.
+The only other constraint is to ensure that the partial telescoping of Step~\ref{step: step 3 convergence bound} still holds.
+Lemma~\ref{thm: mini exponential FISTA convergence} shows that a sufficient condition is
+		$$\edit{}{\varf0_{n_k-1}}\in\spcf0^{n_k}\subset\spcf0^{n_k+1}\subset\ldots\subset\spcf0^{n_{k+1}-1}.$$
 		Convergence is most stable if the approximation spaces $\spcf0^n$ satisfy a monotone inclusion, breaking the monotonicity requires more care.
@@
 		Adaptively choosing the time of refinement is more challenging due to the non-descent property of FISTA.
-The idea is that $\spcf0^n$ should be refined as soon as the value $\Func0(\varf0_n)$ is sufficiently close to $\Func0(\varf2_n)$.
-This is analysed in \Cref{thm: stronger exponential FISTA convergence} which shows convergence results of the form
-	$$ \min_{n\leq N}\Func0_0(\varf0_n) \lesssim \frac{N^{2\kappa}}{N^2}$$
-	for all $N\in\F N$, with the same $\kappa\in[0,1)$ from \Cref{step: step 5 sufficiently slow}.
-The penalty for accelerating the refinement time is a potential loss of stability in $\Func0(\varf0_n)$, however, the asymptotic rate is equivalent and this behaviour has not been seen in numerical experiments.
+The idea is that $\spcf0^n$ should be refined as soon as the value $\op{E}(\varf0_n)$ is sufficiently close to $\op{E}(\varf2_n)$.
+This is analysed in Theorem~\ref{thm: stronger exponential FISTA convergence} (sufficient conditions in Lemma~\ref{thm: practical refinement criteria}) which shows convergence results of the form
+		$$ \min_{n\leq N}\op{E}_0(\varf0_n) \lesssim \frac{N^{2\kappa}}{N^2}$$
+		for all $N\in\F N$, with the same $\kappa\in[0,1)$ from Step~\ref{step: step 5 sufficiently slow}.
+The penalty for accelerating the refinement time is a potential loss of stability in $\op{E}(\varf0_n)$, however, the asymptotic rate is equivalent and this behaviour has not been seen in numerical experiments.
 	\end{adaptiveStep}
@@
 	\section{Proof of convergence}\label{sec: FISTA convergence}
-In this section we follow the recipe motivated in \Cref{sec: recipe} to prove convergence of two variants of \Cref{alg: refining FISTA}.
+	In this section we follow the recipe motivated in Section~\ref{sec: recipe} to prove convergence of two variants of Algorithm~\ref{alg: refining FISTA}.
 Each of the main theorems and lemmas will be stated with a sketch proof in this section.
-The details of the proofs are either trivial or very technical and are therefore placed in \Cref{app: FISTA convergence} to preserve the flow of the argument.
+The details of the proofs are either trivial or very technical and are therefore placed in Section~\ref{app: FISTA convergence} to preserve the flow of the argument.
 
 	\subsection{Computing the convergence bound}
-For \Cref{step: step 1 stability} of \Cref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for \Cref{alg: refining FISTA}.
-The proofs in this step follow the classical arguments of \citet{Beck2009,Chambolle2015} very closely.
+	For Step~\ref{step: step 1 stability} of Section~\ref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for Algorithm~\ref{alg: refining FISTA}.
+The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely.
+
+	\edit{}{Throughout this section we consider a sequence of subspaces $\spcf0^n$ which generate the iterates $\varf0_n$ in Algorithm~\ref{alg: refining FISTA} satisfying
+		\begin{equation}\label{eq: refining subspace definition}
+			\spcf0^n\subset\F H \text{ for } n\in\F N \qquad\text{such that}\qquad \spcf0^n \text{ is closed and }\varf0_n\in\spcf0^{n+1}\text{ for all }n\in\F N
+		\end{equation}
+		with orthogonal projections $\tens{\Pi}_n\colon\F H\to\spcf0^n$.
+	}
 
 	\subsubsection{Single iterations}
-We first wish to understand a single iteration of \Cref{alg: refining FISTA}. This is done through the following two lemmas.
-\begin{lemma}[equivalent to {\cite[Lemma 1]{Chambolle2015}}]\label{thm: descent lemma}
+	We first wish to understand a single iteration of Algorithm~\ref{alg: refining FISTA}. This is done through the following two lemmas.
+	\begin{lemma}[equivalent to {\cite[Lemma \edit{1}{3.1}]{Chambolle2015}}]\label{thm: descent lemma}
 		\Copy{thm: descent lemma}{
-		Suppose $\nabla \func1$ is 1-Lipschitz, for any $\bar{\varf0}\in \spcf0^{n-1}$ define
-		$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \func1(\bar{\varf0})}^2+\func2(\varf0).$$
-		Then, for all $\varf2\in\bar{(\spcf0^n)^*}\supset\F H$, we have
-		$$\Func0(\varf0) + \tfrac12\norm{\varf0-\Pi_n\varf2}^2 \leq \Func0(\Pi_n\varf2) + \tfrac12\norm{\bar{\varf0}-\Pi_n\varf2}^2$$
-		where $\Pi_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.
+			Suppose $\nabla \op{f}$ is 1-Lipschitz, for any $\bar{\varf0}\in \edit{\spcf0^{n}}{\F H}$ define
+			$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \op{f}(\bar{\varf0})}^2+\op{g}(\varf0).$$
+			Then, for all $\varf2\in\edit{\bar{(\spcf0^n)^*}\supset\F H}{\spcf0^n}$, we have
+			\edit{\\\centerline{$\displaystyle \op{E}(\varf0) + \tfrac12\norm{\varf0-\tens{\Pi}_n\varf2}^2 \leq \op{E}(\tens{\Pi}_n\varf2) + \tfrac12\norm{\bar{\varf0}-\tens{\Pi}_n\varf2}^2.$}}{
+			$$\op{E}(\varf0) + \tfrac12\norm{\varf0-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\tens{\Pi}_n\bar{\varf0}-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\bar{\varf0}-\varf2}^2.$$}
+			\edit{where $\tens{\Pi}_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.}{}
 		}
 	\end{lemma}
-\noindent This is exactly the result of \citet{Chambolle2015} applied to the function $\varf0\mapsto\Func0(\Pi_n\varf0)$.
-Applying \Cref{thm: descent lemma} to the iterates from \Cref{alg: refining FISTA} gives a more explicit inequality.
-
-\begin{lemma}[analogous to {\cite[Theorem 2]{Chambolle2015}, \cite[Theorem 1]{Beck2009}}]\label{thm: one step FISTA}
+	\noindent This is exactly the result of \cite{Chambolle2015} applied to the function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$.
+Applying Lemma~\ref{thm: descent lemma} to the iterates from Algorithm~\ref{alg: refining FISTA} gives a more explicit inequality.
+
+	\begin{lemma}[{\edit{analogous to }{}\cite[\edit{Theorem 2}{(17)}]{Chambolle2015}, \cite[\edit{Theorem 1}{Lmma 4.1}]{Beck2009}}]\label{thm: one step FISTA}
 		\Copy{thm: one step FISTA}{
-		Let $\spcf0^n\subset\F H\cap\spcf0$ and $\varf2_n\in\spcf0^n$ be chosen arbitrarily and $\varf0_n$/$\varf1_n$ be generated by \Cref{alg: refining FISTA} for all $n\in\F N$.
-		For all $n\in\F N$ it holds that}
-	\begin{equation}
-		\vart1_{n}^2(\Func0(\varf0_{n}) - \Func0(\varf2_n)) - (\vart1_{n}^2-\vart1_{n})(\Func0(\varf0_{n-1})-\Func0(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.\label{eq: one-step FISTA}
+			Let \edit{$\spcf0^n\subset\F H\cap\spcf0$, }{}$\varf2_n\in\spcf0^n$ be chosen arbitrarily and $\varf0_n$/$\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA} for all $n\in\F N$.
+			For all $n\in\F N$, it holds that}
+		\begin{equation}\Copy{thm:eq: one step FISTA}{
+			t_{n}^2(\op{E}(\varf0_{n}) - \op{E}(\varf2_n)) - (t_{n}^2-t_{n})(\op{E}(\varf0_{n-1})-\op{E}(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.}\label{eq: one-step FISTA}
 		\end{equation}
 	\end{lemma}
-\noindent The proof is given in \cref{app:thm: one step FISTA} and is a result of the convexity of $\Func0$ for a well chosen $\varf2$ in \Cref{thm: descent lemma}.
+	\noindent The proof is given in Theorem~\ref{app:thm: one step FISTA} and is a result of the convexity of $\op{E}$ for a well chosen $\varf2$ in Lemma~\ref{thm: descent lemma}.
 
 	\subsubsection{Generic convergence bound}
-\Cref{thm: one step FISTA} gives us an understanding of a single iteration of \Cref{alg: refining FISTA}, summing over $n$ then gives our generic convergence bound for any variant of \Cref{alg: refining FISTA}.
-
-\begin{theorem}\label{thm: mini FISTA convergence}
+	Lemma~\ref{thm: one step FISTA} gives us an understanding of a single iteration of Algorithm~\ref{alg: refining FISTA}, summing over $n$ then gives our generic convergence bound for any variant of Algorithm~\ref{alg: refining FISTA}.
+
+	\begin{theorem}[\edit{}{analogous to {\cite[Thm 3.2]{Chambolle2015}, \cite[Thm 4.1]{Beck2009}}}]\label{thm: mini FISTA convergence}
 		\Copy{thm: mini FISTA convergence}{
-		Fix a sequence of subspaces $\{\spcf0^n\subset\spcf0\cap\F H\st n\in\F N\}$, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(\vart1_n)_{n\in\F N}$.
-Let $\varf0_n$ and $\varf1_n$ be generated by \Cref{alg: refining FISTA}.
-		Then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have}
-	\begin{equation}\label{eq: FISTA inequality}
-		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
-		 + \sum^N_{n=1} \vart1_n\Func0_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
-	\end{equation}
+			Fix a sequence of subspaces $(\spcf0^n\edit{\subset\spcf0\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$.
+Let $\varf0_n$ and $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA}.
+			Then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have
+		}
+		\begin{equation}\label{eq: FISTA inequality}\Copy{thm:eq: mini FISTA convergence}{
+			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
+			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
+		}\end{equation}
 	\end{theorem}
-\noindent The proof is given in \cref{app:thm: mini FISTA convergence}.
-This result is the key approximation for showing convergence of FISTA with refining sub-spaces.
-In the classical setting, we have $\spcf0^n=\spcf0=\F H$, $\varf2_n=\varf0^*$ and the extra terms on the right-hand side collapse to 0.
-
-The natural choice in \eqref{eq: FISTA inequality} is $\varf2_n=\Pi_n\varf0^*$, however, there are simple counter-examples which give $\Func0(\Pi_n\varf0^*)=\infty$ and so this inequality becomes useless.
-A simple example, if $\func1(\varf0) = \norm{\varf0}_2^2$, $\func2$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$ and $\spcf0^n$ is a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$.
+	\noindent The proof is given in Theorem~\ref{app:thm: mini FISTA convergence}.
+This result is the key approximation for showing convergence of FISTA with refining subspaces.
+In the classical setting, we have $\spcf0^n\edit{=\spcf0}{}=\F H$, $\varf2_n\edit{=\varf0^*}{\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the extra terms on the right-hand side collapse to 0.
+
+	\edit{The}{If there exists a minimiser $\varf0^*\in\argmin_{\varf0\in\F H}\op{E}(\varf0)$, then the } natural choice in \eqref{eq: FISTA inequality} is $\varf2_n=\tens{\Pi}_n\varf0^*$, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\varf0^*)=\infty$ and so this inequality becomes useless.
+For example, if $\op{f}(\varf0) = \norm{\varf0}_{\edit{2}{L^2([0,1])}}^2$, $\op{g}$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$, and $\spcf0^n$ is a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$.
 On the other hand, suppose one of the pixels of the discretisation is $[\varx0_0-\meshsize,\varx0_0+\meshsize]$, then
-$$\Pi_n\varf0^*\left(\varx0_0+\sfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varx0-\vars5)^2d\varx0 = \varx0_0 < \varx0_0+\sfrac\meshsize2.$$
-In particular $\Pi_n\varf0^* \notin\F D$ therefore $\Func0(\Pi_n\varf0^*) = \infty$.
-
-The choice $\varf2_n=\argmin_{\varf0\in\spcf0^n}\Func0(\varf0)$ is much more robust and allows us to apply \cref{alg: refining FISTA} more broadly.
-The penalty for this flexibility is a more complicated analysis, each time the sub-space changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.
+	$$\tens{\Pi}_n\varf0^*\left(\varx0_0+\sfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varx0-\vars5)^2d\varx0 = \varx0_0 < \varx0_0+\sfrac\meshsize2.$$
+	In particular $\tens{\Pi}_n\varf0^* \notin\F D$ therefore $\op{E}(\tens{\Pi}_n\varf0^*) = \infty$.
+The choice $\varf2_n=\argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$ is much more robust and allows us to apply Algorithm~\ref{alg: refining FISTA} more broadly.
+The penalty for this flexibility is a more complicated analysis, each time the subspace changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.
 
@@
 The following lemma minimises the growth of the `constant' as a function of $N$ by partially telescoping the sum on the right-hand side.
-Before progressing to the content of \cref{step: step 3 convergence bound}, we will first formalise the definition of the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ introduced in \Cref{step: step 2 smoothness}.
+Before progressing to the content of Step~\ref{step: step 3 convergence bound}, we will first formalise the definition of the constants $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ introduced in Step~\ref{step: step 2 smoothness}.
 	\begin{definition}\label{def: exp subspaces}
-	Fix $\vars3_{\Varf0},\vars3_{\Func0}\geq 1$ and a sequence of subspaces $\{\tilde{\spcf0}^k\subset\F H\cap\spcf0\st k\in\F N\}$.
-We say that $\{\tilde{\spcf0}^k\}$ is a \emph{$(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$} if
-	$$ \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k \qquad\text{and}\qquad \Func0_0(\tilde{\varf2}_k) \lesssim \vars3_{\Func0}^{-k} $$
-	for all $k\in\F N$ and some choice $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$.
+		Fix $\vars3_{\Varf0},\vars3_{\op{E}}\geq 1$ and a sequence of \edit{subspaces $(\tilde{\spcf0}^k\subset\F H\cap\spcf0)_{k\in\F N}$}{closed subspaces $\tilde{\spcf0}^k\subset\F H$}.
+We say that $(\tilde{\spcf0}^k)_{k\in\F N}$ is a \emph{$(\vars3_{\Varf0},\vars3_{\op{E}})$-discretisation for $\op{E}$} if
+		$$ \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k \qquad\text{and}\qquad \op{E}_0(\tilde{\varf2}_k) \lesssim \vars3_{\op{E}}^{-k} $$
+		for all $k\in\F N$ and some choice $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)$.
 	\end{definition}
-In this section we will simply assume that such sequences exist and in \Cref{sec: general examples} we will give some more general examples.
+	In this section we will simply assume that such sequences exist and in Section~\ref{sec: general examples} we will give some more general examples.
 
@@
 		\Copy{thm: mini exponential FISTA convergence}{
-		Let $\varf0_n$, $\varf1_n$ be generated by \Cref{alg: refining FISTA}, $(n_k\in\F N)_{k=0}^\infty$ be a monotone increasing sequence, and choose
+			Let $\varf0_n$, $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA} \edit{}{with $(\spcf0^n)_{n\in\F N}$ satisfying \eqref{eq: refining subspace definition}}, $(n_k\in\F N)_{k\in\F N}$ be a monotone increasing sequence, and choose
 			$$\tilde{\varf2}_k \in \spcf0^{n_k} \cap \spcf0^{n_k+1}\cap \ldots \cap \spcf0^{n_{k+1}-1}$$
 			for each $k\in\F N$. If such a sequence exists, then for all $K\in\F N$, $n_K\leq N<n_{K+1}$ we have
-		\begin{multline*}
-			\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \frac{\norm{\varf1_N-\tilde{\varf2}_K}^2}{2} \leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\Func0_0(\tilde{\varf2}_K) \\+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\Func0_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}
+		}
+			\begin{multline*}\Copy{thm:eq: mini exponential FISTA convergence}{
+				t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \frac{\norm{\varf1_N-\tilde{\varf2}_K}^2}{2} \leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\op{E}_0(\tilde{\varf2}_K) \\+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\op{E}_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}}
 			\end{multline*}
+		\Copy{thm:end: mini exponential FISTA convergence}{
 			where $C = \frac{\norm{\varf0_0-\tilde{\varf2}_0}^2-\norm{\tilde{\varf2}_0}^2}{2}$.
@@
 	\end{lemma}
-\noindent The proof is given in \cref{app:thm: mini exponential FISTA convergence}.
-The introduction of $n_k$ has greatly compressed the expression of \Cref{thm: mini FISTA convergence}.
-On the right-hand side, we now only consider $\Func0_0$ evaluated on the sequence $\tilde{\varf2}_k$ and there are $K$ elements to the sum rather than $N$.
+	\noindent The proof is given in Lemma~\ref{app:thm: mini exponential FISTA convergence}.
+The introduction of $n_k$ has greatly compressed the expression of Theorem~\ref{thm: mini FISTA convergence}.
+On the right-hand side, we now only consider $\op{E}_0$ evaluated on the sequence $\tilde{\varf2}_k$ and there are $K$ elements to the sum rather than $N$.
 
 	\subsection{Refinement without overfitting}
-The aim of \cref{step: step 4 sufficiently fast} is to show that $n$ iterations of \cref{alg: refining FISTA} is no slower (up to a constant factor) than $n$ iterations of classical FISTA on the space $\spcf0^n$.
+	The aim of Step~\ref{step: step 4 sufficiently fast} is to show that $n$ iterations of Algorithm~\ref{alg: refining FISTA} is no slower (up to a constant factor) than $n$ iterations of classical FISTA on the space $\spcf0^n$.
 In other words, we would like to ensure that
 	\begin{equation}
-	\Func0(\varf0_n) - \min_{\varf0\in\spcf0^n}\Func0(\varf0) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^n}\Func0(\varf0)}^2}{n^2}
+		\op{E}(\varf0_n) - \min_{\varf0\in\spcf0^n}\op{E}(\varf0) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)}^2}{n^2}
 	\end{equation}
@@
 If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of subspaces.
-This can be interpreted as an overfitting to the discretisation of $\Func0|_{\spcf0^n}$ rather than the desired function $\Func0|_{\spcf0}$.
-Combining the assumptions given by \Cref{def: exp subspaces} and the result of \cref{thm: mini exponential FISTA convergence}, the following lemma proves the convergence of \cref{alg: refining FISTA} provided that the refinement times $n_k$ are sufficiently small (i.e.
+This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\spcf0^n}$ rather than the desired function $\op{E}|_{\spcf0}$.
+Combining the assumptions given by Definition~\ref{def: exp subspaces} and the result of Lemma~\ref{thm: mini exponential FISTA convergence}, the following lemma proves the convergence of Algorithm~\ref{alg: refining FISTA} provided that the refinement times $n_k$ are sufficiently small (i.e.
 $\spcf0^n$ grows sufficiently quickly).
@@
 		\Copy{thm: sufficiently fast}{
-		Suppose $\spcf0^n, \varf0_n, \varf1_n$ and $n_k$ satisfy the conditions of \Cref{thm: mini exponential FISTA convergence} and $\{\tilde{\spcf0}^k\}$ forms an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$ with
-		$$\tilde{\varf2}_k\in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)\right]\cap\spcf0^{n_k}\cap\spcf0^{n_k+1}\cap\ldots\cap\spcf0^{n_{k+1}-1}.$$
+			Suppose $\spcf0^n,\ \varf0_n,\ \varf1_n$ and $n_k$ satisfy the conditions of Lemma~\ref{thm: mini exponential FISTA convergence} and $(\tilde{\spcf0}^k)_{k\in\F N}$ forms an $(\vars3_{\Varf0},\vars3_{\op{E}})$-discretisation for $\op{E}$ with
+			$$\tilde{\varf2}_k\in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)\right]\cap\spcf0^{n_k}\cap\spcf0^{n_k+1}\cap\ldots\cap\spcf0^{n_{k+1}-1}.$$
 			If either:
 			\begin{itemize}
-			\item $\vars3_{\Varf0}>1$ and $n_k^2\lesssim \vars3_{\Func0}^k\vars3_{\Varf0}^{2k}$,
-			\item or $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\Func0}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty,$
+				\item $\vars3_{\Varf0}>1$ and $n_k^2\lesssim \vars3_{\op{E}}^k\vars3_{\Varf0}^{2k}$,
+				\item or $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty,$
 			\end{itemize}
 			then
-		$$ \Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}\qquad \text{for all}\qquad n_K\leq N< n_{K+1}.$$
+			$$ \op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}\qquad \text{for all}\qquad n_K\leq N< n_{K+1}.$$
 		}
@@
 
-\noindent The proof is given in \cref{app:thm: sufficiently fast}. We make two observations of the optimality of \Cref{thm: sufficiently fast}:
+	\noindent The proof is given in Lemma~\ref{app:thm: sufficiently fast}. We make two observations of the optimality of Lemma~\ref{thm: sufficiently fast}:
 	\begin{itemize}
 		\item The convergence guarantee for $N$ iterations of classical FISTA in the space $\spcf0^N$ is 
-	$$ \Func0_0(\varf0_N) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\Func0(\varf0)}^2}{N^2} + \min_{\varf0\in\spcf0^N}\Func0_0(\varf0) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} + \vars3_{\Func0}^{-K}.$$
-	This is equivalent to \Cref{thm: sufficiently fast} after the assumptions on $n_k$.
-	\item If $\spcf0$ is finite dimensional then the $\vars3_{\Varf0}=1$ is almost trivially satisfied.
+		$$ \op{E}_0(\varf0_N) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\op{E}(\varf0)}^2}{N^2} + \min_{\varf0\in\spcf0^N}\op{E}_0(\varf0) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} + \vars3_{\op{E}}^{-K}.$$
+		This is equivalent to Lemma~\ref{thm: sufficiently fast} after the assumptions on $n_k$.
+		\item If $\spcf0$ is finite dimensional, then the $\vars3_{\Varf0}=1$ is almost trivially satisfied.
 Norms in finite dimensions are equivalent and any discretisation can be achieved with a finite number of refinements (i.e.
@@
 	\subsection{Convergence rate}
-In \Cref{thm: sufficiently fast} we show that $\Func0(\varf0_n)$ converges at a rate depending on $k$ and $n$ so long as $k$ grows sufficiently quickly.
+	In Lemma~\ref{thm: sufficiently fast} we show that $\op{E}(\varf0_n)$ converges at a rate depending on $k$ and $n$, so long as $k$ grows sufficiently quickly.
 On the other hand, as $k$ grows, the rate becomes worse and so we need to also put a lower limit on the growth of $n_k$.
-The following lemma completes \cref{step: step 5 sufficiently slow} by computing the global convergence rate of $\Func0_0(\varf0_n)$ when $k$ grows at the minimum rate which is consistent with \Cref{thm: sufficiently fast}.
-
-As a special case, note that if $\vars3_{\Varf0}=1$ then \Cref{thm: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate.
-This is in fact a special case of \citet{Aujol2015}.
-If $\varf0^*\in\F H$, then it is not possible to refine `too quickly' and the following lemma is not needed.
+The following lemma completes Step~\ref{step: step 5 sufficiently slow} by computing the global convergence rate of $\op{E}_0(\varf0_n)$ when $k$ grows at the minimum rate which is consistent with Lemma~\ref{thm: sufficiently fast}.
+
+	As a special case, note that if $\vars3_{\Varf0}=1$ then Lemma~\ref{thm: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate.
+This is in fact a special case of that shown in \cite[Prop 3.3]{Aujol2015}.
+If \edit{$\varf0^*\in\F H$}{the minimum is achieved in $\F H$}, then it is not possible to refine `too quickly' and the following lemma is not needed.
 
@@
 			Suppose $\varf0_n$ and $n_k$ are sequences satisfying 
-		$$\Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \vars3_{\Func0}^K\vars3_{\Varf0}^{2K},$$
+			$$\op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \vars3_{\op{E}}^K\vars3_{\Varf0}^{2K},$$
 			then 
-		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}.$$}
+			$$\op{E}_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2}.$$}
 	\end{lemma}
-\noindent The proof is given in \cref{app:thm: sufficiently slow}.
+	\noindent The proof is given in Lemma~\ref{app:thm: sufficiently slow}.
 
 	\subsubsection{FISTA convergence with a priori discretisation}
-We can summarise \Cref{thm: mini exponential FISTA convergence,thm: sufficiently fast,thm: sufficiently slow} into a single theorem stating the convergence guarantees when $\spcf0^n$ and $n_k$ are chosen a priori.
+	We can summarise Lemmas~\ref{thm: mini exponential FISTA convergence} to~\ref{thm: sufficiently slow} into a single theorem stating the convergence guarantees when $\spcf0^n$ and $n_k$ are chosen a priori.
 	\begin{theorem}\label{thm: exponential FISTA convergence}
 		\Copy{thm: exponential FISTA convergence}{
-		Let $\{\tilde{\spcf0}^k\st k\in\F N\}$ be an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$ and choose any $\spcf0^n$ such that 
-		$$ \tilde{\spcf0}^k = \spcf0^{n_k}, \qquad \tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
-		for all $k\in\F N$. Compute $\varf0_n$, $\varf1_n$ by \Cref{alg: refining FISTA}.
+			Let $(\tilde{\spcf0}^k)_{k\in\F N}$ be an $(\vars3_{\Varf0},\vars3_{\op{E}})$-discretisation for $\op{E}$ and choose any $\spcf0^n$ \edit{}{satisfying \eqref{eq: refining subspace definition} }such that
+			$$ \tilde{\spcf0}^k = \spcf0^{n_k}, \qquad \tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
+			for all $k\in\F N$. Compute $\varf0_n$ and $\varf1_n$ by Algorithm~\ref{alg: refining FISTA}.
 
@@
 			\begin{itemize}
-			\item $\vars3_{\Varf0}>1$ and $n_k^2\simeq \vars3_{\Func0}^k\vars3_{\Varf0}^{2k}$,
-			\item or $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\Func0}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$,
+				\item $\vars3_{\Varf0}>1$ and $n_k^2\simeq \vars3_{\op{E}}^k\vars3_{\Varf0}^{2k}$, or
+				\item $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$,
 			\end{itemize}
 			then
-		$$\Func0_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} \qquad \text{uniformly for } N\in\F N.$$
+			$$\op{E}_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2} \qquad \text{uniformly for } N\in\F N.$$
 		}
 	\end{theorem}
-\noindent This theorem is very easy to implement numerically and requires very little knowledge of how to estimate $\Func0_0(\varf0_n)$.
-So long as $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be computed analytically, choosing $\tilde{\spcf0}^k$ to be uniform discretisations and $\tilde{\spcf0}^k = \spcf0^{n_k}=\ldots= \spcf0^{n_{k+1}-1}$ will give the stated convergence rate.
+	\noindent This theorem is very easy to implement numerically and requires very little knowledge of how to estimate $\op{E}_0(\varf0_n)$.
+So long as $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ can be computed analytically, choosing $\tilde{\spcf0}^k$ to be uniform discretisations and $\tilde{\spcf0}^k = \spcf0^{n_k}=\ldots= \spcf0^{n_{k+1}-1}$ will achieve the stated convergence rate.
 
 	\subsubsection{FISTA convergence with adaptivity}
-There are two properties of the sequence $(\spcf0^n)_0^\infty$ which we may wish to decide adaptively: the refinement times $n_k$ and the exact spaces $\{\spcf0^n \st n_k\leq n<n_{k+1}\}$.
-We will refer to these as time and spatial adaptivity respectively.
-
-\Cref{thm: sufficiently fast} gives a sufficient condition on $n_k$ for converging at the rate $O(N^{2(\kappa-1)})$ but it is not necessary. Indeed for $n\leq n_k$ the result shows 
-$$\Func0_0(\varf0_n) \geq \min_{\varf0\in\spcf0^n}\Func0_0(\varf0) = O(\vars3_{\Func0}^{-k}) = O(n^{2(\kappa-1)})$$
+	There are two properties of the sequence $(\spcf0^n)_{n\in\F N}$ which we may wish to decide adaptively: the refinement times $n_k$ and the discretising spaces $\{\spcf0^n \st n_k\leq n<n_{k+1}\}$.
+We will refer to these as temporal and spatial adaptivity respectively.
+
+	Lemma~\ref{thm: sufficiently fast} gives a sufficient condition on $n_k$ for converging at the rate $O(N^{2(\kappa-1)})$, but it is not necessary. Indeed for $n\leq n_k$ the result shows 
+	$$\op{E}_0(\varf0_n) \geq \min_{\varf0\in\spcf0^n}\op{E}_0(\varf0) = O(\vars3_{\op{E}}^{-k}) = O(n^{2(\kappa-1)})$$
 	which suggests that to converge faster than $n^{2(\kappa-1)}$ requires choosing smaller $n_k$.
-As an example, in \Cref{sec: wavelet examples} we will see \cref{alg: refining FISTA} can converge at a linear rate, although this is not possible without adaptive refinement times.
+As an example, in Section~\ref{sec: wavelet examples} we will see Algorithm~\ref{alg: refining FISTA} can converge at a linear rate, although this is not possible without adaptive refinement times.
 On the other hand, choice of spatial adaptivity has no impact on rate but can impact computational efficiency.
@@
 
-While \Cref{thm: exponential FISTA convergence} also allows for spatial adaptivity, we will simplify the requirements to a form which seems more practical for implementation and also allows for time adaptivity.
-We make the assumption that the choice of $n_k$ depends only on the value $\Func0(u^{n_k-1})$ and therefore make $u^{n_k-1}$ the root of our requirements.
-\cref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\Func0_0(\varf0^{n_k-1})\lesssim \vars3_{\Func0}^{-k}$.
-However, the value of $\Func0_0$ may be hard to estimate and so we introduce a `backstop' condition which guarantees that convergence is no slower than the rate given by \Cref{thm: exponential FISTA convergence}.
-The only constraint on spatial adaptivity is the piecewise monotone inclusion and that $\spcf0^{n_k} \ni u^{n_k-1}$.
+	While Theorem~\ref{thm: exponential FISTA convergence} also allows for spatial adaptivity, we will simplify the requirements to a form which seems more practical for implementation and also allows for temporal adaptivity.
+We make the assumption that the choice of $n_k$ depends only on the value $\op{E}(u^{n_k-1})$ and therefore make $u^{n_k-1}$ the root of our requirements.
+Lemma~\ref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\op{E}_0(\varf0^{n_k-1})\lesssim \vars3_{\op{E}}^{-k}$.
+However, the value of $\op{E}_0$ may be hard to estimate and so we retain a `backstop' condition which guarantees that convergence is no slower than the rate given by Theorem~\ref{thm: exponential FISTA convergence}.
+The only constraints on spatial adaptivity are the monotone inclusion properties, $\varf0_n\in\spcf0^{n+1}$ and existence of $\tilde{\varf2}_k$.
 This is confirmed by the following theorem.
@@
 		\Copy{thm: stronger exponential FISTA convergence}{
-		Let $\{\spcf0^n\subset\F H\cap\spcf0\st n\in\F N\}$ be a sequence of subspaces and $n_k\in\F N$ a monotone increasing sequence such that
-		$$ \tilde{\spcf0}^k \coloneqq \spcf0^{n_k}\ni \varf0_{n_k-1}, \qquad \tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
+			Let $(\spcf0^n\subset\F H\edit{\cap\spcf0}{})_{n\in\F N}$ be a sequence of subspaces \edit{}{satisfying \eqref{eq: refining subspace definition} }and $n_k\in\F N$ a monotone increasing sequence such that
+			$$ \tilde{\spcf0}^k \coloneqq \spcf0^{n_k}\edit{\ni \varf0_{n_k-1}}{}, \qquad \tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
 			for all $k\in\F N$.
-		Compute $\varf0_n$, $\varf1_n$ by \Cref{alg: refining FISTA}.
-
-		\bigbreak\noindent Suppose there exist $\vars3_{\Varf0},\vars3_{\Func0}\geq1$ such that either:
+			Compute $\varf0_n$ and $\varf1_n$ by Algorithm~\ref{alg: refining FISTA}.
+
+			\bigbreak\noindent Suppose there exist $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that either:
 			\begin{itemize}
-			\item $\vars3_{\Varf0}>1$ and $n_k^2\lesssim \vars3_{\Func0}^k\vars3_{\Varf0}^{2k}$,
-			\item or $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\Func0}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$
+				\item $\vars3_{\Varf0}>1$ and $n_k^2\lesssim \vars3_{\op{E}}^k\vars3_{\Varf0}^{2k}$, or
+				\item $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$
 			\end{itemize}
 			and both
-		$$ \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k \qquad\text{and}\qquad \Func0_0(\varf0_{n_K-1}) \lesssim \vars3_{\Func0}^{-K}.$$
+			$$ \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k \qquad\text{and}\qquad \op{E}_0(\varf0_{n_K-1}) \lesssim \vars3_{\op{E}}^{-K}.$$
 			Whenever these conditions on $n_k$ are satisfied, then
-		$$\min_{n\leq N}\Func0_0(\varf0_n) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}$$
+			$$\min_{n\leq N}\op{E}_0(\varf0_n) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2}$$
 			uniformly for $N\in\F N$.
@@
 	\end{theorem}
-\noindent The proof is given in \cref{app:thm: stronger exponential FISTA convergence}.
-If we directly compare \Cref{thm: exponential FISTA convergence,thm: stronger exponential FISTA convergence}, we note that the convergence rate is the same in both theorems but the price for better adaptivity is a slightly weaker stability guarantee (i.e.
-the addition of the min on the left-hand side).
-In \Cref{thm: exponential FISTA convergence}, as in the original FISTA algorithm, the sequence $\Func0(\varf0_n)$ is not monotone but the magnitude of oscillation is guaranteed to decay in time.
-This behaviour is boundedness is lost in \cref{thm: stronger exponential FISTA convergence} although it still holds on a subsequence.
+	\noindent The proof is given in Theorem~\ref{app:thm: stronger exponential FISTA convergence}.
+If we directly compare Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence}, we note that the convergence rate is the same in both theorems but the price for better adaptivity (i.e.
+relaxed $(\vars3_{\Varf0},\vars3_{\op{E}})$ assumptions) is a slightly weaker stability guarantee (now convergence of $\min_{n\leq N}\op{E}_0(\varf0_n)$).
+In Theorem~\ref{thm: exponential FISTA convergence}, as in the original FISTA algorithm, the sequence $\op{E}(\varf0_n)$ is not monotone but the magnitude of oscillation is guaranteed to decay in time.
+This behaviour is lost in Theorem~\ref{thm: stronger exponential FISTA convergence} although it still holds on a subsequence.
 Although we do not prove it here, it can be shown that the stronger condition
 	\begin{equation}
-	\tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}\cap\ldots\cap \spcf0^N
-\end{equation}
-is sufficient to restore the stronger guarantee on $\Func0_0(\varf0_n)$. Again, monotonicity of $\spcf0^n$ corresponds with improved stability of \cref{alg: refining FISTA}.
-
-To enable more practical implementation of \Cref{thm: stronger exponential FISTA convergence}, the following lemma describes several refinement time strategies which provide sufficient condition for $\Func0_0(\varf0_n) \lesssim \vars3_{\Func0}^{-k}$.
+		\tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}\cap\ldots\cap \spcf0^N
+	\end{equation}
+	is sufficient to restore the stronger last-iterate guarantee on $\op{E}_0(\varf0_N)$. Again, monotonicity of $\spcf0^n$ corresponds with improved stability of Algorithm~\ref{alg: refining FISTA}.
+
+	To enable a more practical implementation of Theorem~\ref{thm: stronger exponential FISTA convergence}, the following lemma describes several refinement time strategies which provide sufficient condition for $\op{E}_0(\varf0_n) \lesssim \vars3_{\op{E}}^{-k}$.
 	\begin{lemma}\label{thm: practical refinement criteria}
 		\Copy{thm: practical refinement criteria}{
-		Let $\{\tilde{\spcf0}^k\st k\in\F N\}$ be a sequence of subspaces with some points $\varf0_k\in \tilde{\spcf0}^k$ and $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$.
+			Let $(\tilde{\spcf0}^k)_{k\in\F N}$ be a sequence of subspaces with some points $\varf0_k\in \tilde{\spcf0}^k$ and $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)$.
 Suppose that $\norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k$.
-Any of the following conditions are sufficient to show that $\{\tilde{\spcf0}^k\}$ is an $(\vars3_{\Varf0},\vars3_{\Func0})$-discretisation for $\Func0$:
+Any of the following conditions are sufficient to show that $\{\tilde{\spcf0}^k\}$ is an $(\vars3_{\Varf0},\vars3_{\op{E}})$-discretisation for $\op{E}$:
 			\begin{enumerate}
-			\item Small continuous gap refinement: $ \Func0_0(\varf0_k)\leq \vars1\vars3_{\Func0}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
-			\item Small discrete gap refinement: $\Func0_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\Func0}^{-k}$ and $ \Func0_0(\varf0_k)-\Func0_0(\tilde{\varf2}_{k-1})\leq \vars1\vars3_{\Func0}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
-			\item Small relative gap refinement: $ \Func0_0(\varf0_k) - \Func0_0(\tilde{\varf2}_{k-1}) \leq \vars1\Func0_0(\varf0_k)$ for all $k\in\F N$, some $0<\vars1\leq \frac{1}{1+\vars3_{\Func0}}$.
-			\item Small continuous gradient refinement: $ \Norm{\partial\Func0(\varf0_k)}_*\leq \vars1\vars3_{\Func0}^{-k}$ for all $k\in\F N$, some $\vars1>0$, and sublevel sets of $\Func0$ are $\Norm\cdot$-bounded.
-			\item Small discrete gradient refinement: $\Func0_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\Func0}^{-k}$ and $\Norm{\Pi_k\partial\Func0(\varf0_k)}_*\leq \vars1\vars3_{\Func0}^{-k}$ for all $k\in\F N$, some $\vars1>0$, and sublevel sets of $\Func0$ are $\Norm\cdot$-bounded.
-The operator $\Pi_k\colon\F H\to\tilde{\spcf0}^k$ is the orthogonal projection.
+				\item Small continuous gap refinement: $ \op{E}_0(\varf0_k)\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+				\item Small discrete gap refinement: $\op{E}_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $ \op{E}_0(\varf0_k)-\op{E}_0(\tilde{\varf2}_{k-1})\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+				\item Small relative gap refinement: $ \op{E}_0(\varf0_k) - \op{E}_0(\tilde{\varf2}_{k-1}) \leq \vars1\op{E}_0(\varf0_k)$ for all $k\in\F N$, some $0<\vars1\leq \frac{1}{1+\vars3_{\op{E}}}$.
 			\end{enumerate}
+			\edit{}{If, furthermore, there exists a Banach space $(\spcf0,\Norm\cdot)$ with $\spcf0\supset\F H$, then it is also sufficient that:}
+			\begin{enumerate}\setcounter{enumi}{3}
+				\item Small continuous gradient refinement: $ \Norm{\partial\op{E}(\varf0_k)}_*\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded.
+				\item Small discrete gradient refinement: $\op{E}_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $\Norm{\tens{\Pi}_k\partial\op{E}(\varf0_k)}_*\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded.
+			\end{enumerate}
 		}
@@
 
-\noindent The proof is given in \cref{app:thm: practical refinement criteria}.
-The refinement criteria described by \Cref{thm: practical refinement criteria} can be split into two groups.
-Cases (1), (3), and (4) justify that any choice of $\tilde{\spcf0}^k\ni\varf0_k$ (or $\varf0_{n_k-1}$ in \Cref{thm: stronger exponential FISTA convergence}) satisfies the required conditions.
+	\noindent The proof is given in Lemma~\ref{app:thm: practical refinement criteria}.
+The refinement criteria described by Lemma~\ref{thm: practical refinement criteria} can be split into two groups.
+Cases (1), (3), and (4) justify that any choice of $\tilde{\spcf0}^k\ni\varf0_k$ (or $\varf0_{n_k-1}$ in Theorem~\ref{thm: stronger exponential FISTA convergence}) satisfies the required conditions.
 In cases (2) and (5), $\varf0_k$ is sufficient to choose the refinement time $n_k$ but not the subspace $\tilde{\spcf0}^k$.
@@
 Typically, gradient norms (in (4) and (5)) should be easier to estimate than function gaps because they only require local knowledge rather than global, i.e.
-$\partial\Func0(\varf0_n)$ rather than an estimate of $\Func0(\varf0^*)$.
-Implicitly, the global information comes from an extra condition on $\Func0$ to assert that sublevel sets are bounded.
+$\partial\op{E}(\varf0_n)$ rather than an estimate of $\edit{\op{E}(\varf0^*)}{\Emin}$.
+Implicitly, the global information comes from an extra condition on $\op{E}$ to assert that sublevel sets are bounded.
 
@@
 	\section{General examples}\label{sec: general examples}
-In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, \Cref{alg: refining FISTA} is much more broadly applicable.
-Here we justify this claim by demonstrating that the constants $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ can be easily computed in many examples.
-
+	\edit{In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, Algorithm~\ref{alg: refining FISTA} is much more broadly applicable.
+Here we justify this claim by demonstrating that the constants $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ can be easily computed in many examples.
 	The cases where $\spcf0$ is finite or countable dimensional are quite straight forward.
@@
 $\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$) then $\vars3_{\Varf0} = 1$.
-This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in \cref{sec: Lasso definition}.
-The examples we will consider here are where $\F H = L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$, and $\{\tilde{\spcf0}^n\st n\in\F N\}$ are finite dimensional finite-element--like spaces.
-We will now clarify exactly what is meant by these properties and then demonstrate that they are sufficient to find simple formulae for the values $\vars3_{\Varf0}$ and $\vars3_{\Func0}$.
+This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}.
+The examples considered here have $\F H = L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ where $\{\tilde{\spcf0}^n\st n\in\F N\}$ are finite dimensional finite-element--like spaces.
+We will now clarify exactly what is meant by these properties and then demonstrate that they are sufficient to find simple formulae for the values $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$.
+}{
+	We consider the main use of Algorithm~\ref{alg: refining FISTA} to be where there exists a Banach space $(\spcf0,\Norm\cdot)$ such that $\spcf0\supset\F H$ and
+	$$\inf_{\varf0\in\F H} \op{E}(\varf0) = \min_{\varf0\in\spcf0}\op{E}(\varf0) = \op{E}(\varf0^*)$$
+	for some $\varf0^*\in\spcf0$.
+The cases where $\F H$ has finite or countable dimension are quite straightforward.
+If the total number of refinements is finite (i.e.
+$\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$) then $\vars3_{\Varf0} = 1$.
+This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}.
+In this section we give explicit computations of $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subspaces $(\tilde{\spcf0}^n)_{n\in\F N}$ will be finite dimensional finite-element--like spaces, as defined below.
+	}
 
 	\begin{definition}
-	Suppose $\spcf0\subset L^p(\Domain)$ for some compact domain $\Domain\subset\R^d$. We say that $\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$ is a \emph{mesh} if 
+		Suppose $\spcf0\subset L^p(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$\edit{}{ with sufficiently smooth boundary}.
+We say that $\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$ is a \emph{mesh} if
 		$$\domain_i^k\subset\Domain \qquad\text{and} \qquad |\domain_i^k\cap\domain^k_j| = 0$$
 		for all $i$ and $j$.
-We say that $\tilde{\spcf0}^k\subset \spcf0\cap\F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\varf0\in\tilde{\spcf0}^k$ there exists $\varf0_i^k\in\tilde{\spcf0}^k$ such that
+We say that $\tilde{\spcf0}^k\subset \edit{\spcf0\cap}{}\F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\varf0\in\tilde{\spcf0}^k$ there exists $\varf0_i^k\in\tilde{\spcf0}^k$ such that
 		$$\supp(\varf0_i^k)\subset \bar{\domain_i^k}, \qquad \varf0(\vvarx0) = \varf0^k_i(\vvarx0) \qquad \text{ for a.e. }\vvarx0\in\domain_i^k, \text{ all } i\in\F N.$$
 
-	We say that a sequence of finite element sub-spaces $(\tilde{\spcf0}^k)_{k=0}^\infty$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\spcf0}^0\cap L^\infty(\Domain)$ such that for any $\varf0_i^k\in\tilde{\spcf0}^k$ with $\supp(\varf0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
+		We say that a sequence of finite element subspaces $(\tilde{\spcf0}^k)_{k=0}^\infty$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\spcf0}^0\cap L^\infty(\Domain)$ such that for any $\varf0_i^k\in\tilde{\spcf0}^k$ with $\supp(\varf0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
 		$$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \varf0_i^k(\vvarx0) = \sum_{j=1}^N\vars2_je_j(\vars0 \vvarx0+\vvars1) \quad \text{ for a.e.
@@
 		We allow the implicit constant to have any dependence on $\varf0^*$ so long as it is finite. For example, in the case of Sobolev spaces we would expect an inequality of the form
-	$\min_{\varf2\in\tilde{\spcf0}^k}\norm{\varf2-\varf0^*}_{W^{0,q}} \lesssim \meshsize^{kp}\norm{\varf0^*}_{W^{p,q}}$ \citep{Strang1972}.
+		$\min_{\varf2\in\tilde{\spcf0}^k}\norm{\varf2-\varf0^*}_{W^{0,q}} \lesssim \meshsize^{kp}\norm{\varf0^*}_{W^{p,q}}$ \cite{Strang1972}.
 	\end{definition}
 	We note that any piecewise polynomial finite element space can be used to form a $\meshsize$-refining sequence of subspaces.
-Wavelets with a compactly supported basis satisfy this definition but it is hard to specify the value $N$ in general.
+Wavelets with a compactly supported basis behave like a multi-resolution finite element space as there is always overlap in the supports of basis vectors.
 Similarly, a Fourier basis does satisfy the scaling properties but each basis vector has global support.
 Both of these exceptions are important and could be accounted for with further analysis but we focus on the more standard finite element case.
-The following theorem shows that all finite element spaces achieve the same basic rates of convergence in \Cref{alg: refining FISTA}, depending on the particular properties of $\Norm\cdot$ and $\Func0$.
+The following theorem shows that all finite element spaces achieve the same basic rates of convergence in Algorithm~\ref{alg: refining FISTA}, depending on the particular properties of $\Norm\cdot$ and $\op{E}$.
 	\begin{theorem}\label{thm: generic a_U and a_E}
-	Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
+		Suppose $\F H= L^2(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$\edit{}{ with sufficiently smooth boundary} and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
 If $(\tilde{\spcf0}^k)_k$ is a sequence of $\meshsize$-refining finite element spaces of order $p$ then
@@
 			\vars3_{\Varf0} &\leq \splitln{1}{q\geq 2}{\sqrt{\meshsize^{-d}}}{q<2},
-		& \vars3_{\Func0} &\geq \begin{cases}
-			\meshsize^{-p} & \Func0 \text{ is $\Norm\cdot$-Lipschitz at }\varf0^*
-			\\\meshsize^{-2p} & \Func0 \text{ is $\Norm\cdot$-smooth at }\varf0^*
+			& \vars3_{\op{E}} &\geq \begin{cases}
+				\meshsize^{-p} & \op{E} \text{ is $\Norm\cdot$-Lipschitz at }\varf0^*
+				\\\meshsize^{-2p} & \op{E} \text{ is $\Norm\cdot$-smooth at }\varf0^*
 			\end{cases}\ .
 		\end{align*}
-	If $\func2$ is not Lipschitz at $\varf0^*$ but $\func1$ is $\Norm\cdot$-Lipschitz and 
-	$$\min_{\varf2\in\tilde{\spcf0}^k}\left\{\Norm{\varf2-\varf0^*}\st \func2(\varf2)\leq \func2(\varf0^*)\right\} \lesssim \min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*},$$
-	then, again, $\vars3_{\Func0}\geq\meshsize^{-p}$. 
+		If $\op{g}$ is not Lipschitz at $\varf0^*$ but $\op{f}$ is $\Norm\cdot$-Lipschitz and 
+		$$\min_{\varf2\in\tilde{\spcf0}^k}\left\{\Norm{\varf2-\varf0^*}\st \op{g}(\varf2)\leq \op{g}(\varf0^*)\right\} \lesssim \min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*},$$
+		then, again, $\vars3_{\op{E}}\geq\meshsize^{-p}$. 
 	\end{theorem}
-The proof of this theorem is in \Cref{app: generic a_U and a_E}.
-The main take-home for this theorem is that the computation of $\vars3_{\Varf0}$ and $\vars3_{\Func0}$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\Func0$.
-The only non-trivial case is when $\func2$ is not smooth enough to estimate directly.
-So long as $\tilde{\spcf0}^k$ are sufficiently dense in sublevel sets of $\func2$, the smoothness of $\func1$ is sufficient to give a convergence rate.
+	The proof of this theorem is in Appendix~\ref{app: generic a_U and a_E}.
+The main take-home for this theorem is that the computation of $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\op{E}$.
+The only non-trivial case is when $\op{g}$ is not smooth enough to estimate directly.
+So long as $\tilde{\spcf0}^k$ are sufficiently dense in sublevel sets of $\op{g}$, the smoothness of $\op{f}$ is sufficient to give a convergence rate.
 
@@
 	\section{Lasso minimisation}\label{sec: Lasso definition}
-We now focus on the concrete example of Lasso which will be used for numerical results in \Cref{sec: numerics}.
+	We now focus on the specific example of Lasso which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}.
 We consider three forms of Lasso which will be referred to as continuous, countable, and discrete Lasso depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
@@
 	\begin{equation}\label{eq: Lasso energy}
-	\Func0(\varf0) = \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu\Norm{\varf0}
-\end{equation}
-for some $\A\colon \spcf0\cup\F H\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$.
-
-The aim of this section is to develop all of the necessary tools for implementing \Cref{alg: refining FISTA} on the energy \eqref{eq: Lasso energy} using the convergence guarantees of either \Cref{thm: exponential FISTA convergence} or \Cref{thm: stronger exponential FISTA convergence}.
-This includes computing the rates $\vars3_{\Varf0}$ and $\vars3_{\Func0}$, estimating the continuous gap $\Func0_0(\varf0_n)$, and developing an efficient refinement choice for $\spcf0^n$.
+		\op{E}(\varf0) = \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu\Norm{\varf0}
+	\end{equation}
+	for some $\A\colon \spcf0\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$.
+\edit{}{In the continuous-space case, we require $\A^*\colon\R^m\to C(\Domain)$.
+}Let $\varf0^*\in\argmin_{\varf0\in\spcf0}\op{E}(\varf0)$.
+
+	The aim of this section is to develop all of the necessary tools for implementing Algorithm~\ref{alg: refining FISTA} on the energy \eqref{eq: Lasso energy} using the convergence guarantees of either Theorem~\ref{thm: exponential FISTA convergence} or Theorem~\ref{thm: stronger exponential FISTA convergence}.
+This includes computing the rates $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$, estimating the continuous gap $\op{E}_0(\varf0_n)$, and developing an efficient refinement choice for $\spcf0^n$.
 
@@
 
-Application of \Cref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although although $\norm\cdot_1$ is too strong a metric and results in $\vars3_{\Func0}=2^0$.
-This can be seen because for any $\varf0\in L^1(\Domain^d)$,
-\begin{equation}
-	\norm{\varf0-\delta_0}_1 = \sup_{\vard0\in C(\Domain^d), \norm{\vard0}_\infty\leq 1} \IP{\vard0}{\varf0-\delta_0} = \norm{\varf0}_1+\norm{\delta_0}_1 \geq 1.
-\end{equation}
-To improve our estimate of $\vars3_{\Func0}$ requires additional assumptions on $\A$. For any $\varf2\in\tilde{\spcf0}^k$ such that $\norm{\varf2}_1\leq \norm{\varf0^*}_1$, we compute
-\begin{align}
-	\Func0(\varf2)-\Func0(\varf0^*) &=  \tfrac12\norm{\A\varf2-\vdata0}^2 - \tfrac12\norm{\A\varf0^*-\vdata0}^2 + \mu\left(\Norm{\varf2}-\Norm{\varf0^*}\right)
-	\\&\leq \tfrac12\norm{\A\varf2-\vdata0}^2 - \tfrac12\norm{\A\varf0^*-\vdata0}^2
-	\\&= \IP{\tfrac12\A(\varf2+\varf0^*)-\vdata0}{\A(\varf2-\varf0^*)}
-	\\&\leq \max(\norm{\A\varf2-\vdata0},\norm{\A\varf0^*-\vdata0})\norm{\A(\varf2-\varf0^*)} 
-	\\&\leq \sqrt{2\Func0(\varf2)}\norm{\A(\varf2-\varf0^*)}.
-\end{align}
-Choosing $\varf2 = \tilde\Pi_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde\Pi_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
-$$\Func0(\varf2)-\Func0(\varf0^*) \lesssim \norm{\A(\tilde\Pi_k\varf0^*-\varf0^*)} \leq \norm{(\tilde\Pi_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$$
+	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\norm\cdot_1$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$.
+This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$,
+	\begin{equation}
+		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1.
+	\end{equation}
+	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. For any $\varf2\in\tilde{\spcf0}^k$ such that $\Norm{\varf2}\leq \Norm{\varf0^*}$, we compute
+	\begin{align}
+		\op{E}(\varf2)-\op{E}(\varf0^*) &=  \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0^*-\data}_{\ell^2}^2 + \mu\left(\Norm{\varf2}-\Norm{\varf0^*}\right)
+		\\&\leq \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0^*-\data}_{\ell^2}^2
+		\\&= \ip{[\tfrac12\A(\varf2+\varf0^*)-\data]}{\A(\varf2-\varf0^*)}
+		\\&\leq \max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0^*-\data}_{\ell^2})\norm{\A(\varf2-\varf0^*)}_{\ell^2} 
+		\\&\leq \sqrt{2\op{E}(\varf2)}\norm{\A(\varf2-\varf0^*)}_{\ell^2}.
+	\end{align}
+	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
+	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
 	Expanding the operator norm further,
-\begin{equation}
-	\norm{(\tilde\Pi_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde\Pi_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}}
-	= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}
-\end{equation}
+	\\\centerline{$\displaystyle
+		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}}
+		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
+	}{Piecewise constant projection is $L^1$-bounded therefore we can extend $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ by the Hahn-Banach theorem.
+Choosing $\varf2=\tilde{\tens{\Pi}}_k\varf0^*$ gives
+	\begin{align}
+		\op{E}(\varf2)-\op{E}(\varf0^*) &\lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2}
+		\\&= \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0^*}
+		\\&\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0^*}
+		\\&\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0^*}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0^*}
+	\end{align}}
 	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.
 
-This computation confirms two things, firstly that the scaling constant is indeed $\vars3_{\Func0} = 2$, and secondly that the required smoothness to achieve a good rate with \Cref{alg: refining FISTA} is that $\A^*\colon\R^m\to C^1(\Domain)$ is a bounded operator.
+	This computation confirms two things, firstly that the scaling constant is indeed $\vars3_{\op{E}} = 2$, and secondly that the required smoothness to achieve a good rate with Algorithm~\ref{alg: refining FISTA} is that $\A^*\colon\R^m\to C^1(\Domain)$ is a bounded operator.
 This accounts for using the weaker topology of $\C M(\Domain)$ rather than $L^1(\Domain)$.
-In \Cref{sec: smoothing operators} we will show two practical examples were this (semi)norm is accurately computable.
-
-Inserting the computed rates into \Cref{thm: exponential FISTA convergence} or \Cref{thm: stronger exponential FISTA convergence} gives the guaranteed convergence rate
+In Section~\ref{sec: smoothing operators} we will show two practical examples were this (semi)norm is accurately computable.
+
+	Inserting the computed rates into Theorem~\ref{thm: exponential FISTA convergence} or Theorem~\ref{thm: stronger exponential FISTA convergence} gives the guaranteed convergence rate
 	\begin{equation}\label{eq: Lasso energy rate}
-	\kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} = \frac{d}{1+d} \quad \implies \quad \Func0_0(\varf0_n) \lesssim n^{-2(1-\kappa)} = n^{-\frac{2}{1+d}}.
-\end{equation}
-This rate can be used to infer the required resolution at each iteration, in particular on iteration $n$ with $n^2\simeq (\vars3_{\Func0}\vars3_{\Varf0}^2)^k$ we expect the resolution to be
+		\kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2} = \frac{d}{1+d} \quad \implies \quad \op{E}_0(\varf0_n) \lesssim n^{-2(1-\kappa)} = n^{-\frac{2}{1+d}}.
+	\end{equation}
+	This rate can be used to infer the required resolution at each iteration, in particular on iteration $n$ with $n^2\simeq (\vars3_{\op{E}}\vars3_{\Varf0}^2)^k$ we expect the resolution to be
 	\begin{equation}\label{eq: Lasso resolution rate}
-	2^{-k} = \left(\vars3_{\Func0}\vars3_{\Varf0}^2\right)^{\frac{k}{1+d}} \simeq n^{-\frac{2}{1+d}}.
+		2^{-k} = \left(\vars3_{\op{E}}\vars3_{\Varf0}^2\right)^{\frac{k}{1+d}} \simeq n^{-\frac{2}{1+d}}.
 	\end{equation}
@@
 The key fact here is that, even when $\spcf0$ is infinite dimensional, it is known (e.g.
-\cite[Theorem 2]{Unser2016} and \cite[Corollary 2]{Boyer2019}) that $\varf0^*$ can be chosen to have at most $m$ non-zeros.
+\cite[\edit{Theorem 2}{Thm 6}]{Unser2016} and \cite[\edit{Corollary 2}{Cor 3.8}]{Boyer2019}) that $\varf0^*$ can be chosen to have at most $m$ non-zeros.
 If this is the case, then $\varf0^*\in \ell^2(\R)$; this makes the analysis much simpler than in the continuous case.
@@
 infinite vectors with finitely many non-zeros.
-The key change in analysis from the continuous case is $\varf0^*\in\ell^2(\R)$, which leads to $\vars3_{\Varf0}=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\Func0}$ or any additional properties of $\A$.
-The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of \Cref{thm: exponential FISTA convergence,thm: stronger exponential FISTA convergence} hold trivially.
+The key change in analysis from the continuous case is $\varf0^*\in\ell^2(\R)$, which leads to $\vars3_{\Varf0}=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\op{E}}$ or any additional properties of $\A$.
+The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence} hold trivially.
 
 	\subsection{Refinement metrics}\label{sec: Lasso gap and gradient}
-\Cref{thm: practical refinement criteria} shows that adaptive refinement can be performed based on estimates of the function gap or the gradient.
+	Lemma~\ref{thm: practical refinement criteria} shows that adaptive refinement can be performed based on estimates of the function gap or the \edit{gradient}{subdifferential}.
 In this subsection we provide estimates for these values which can be easily computed.
@@
 
-Let $\Pi_n\colon\spcf0\to\spcf0^n$ denote an orthogonal projection (uniquely determined on $\C H$).
-For Lasso, the discretised function $\varf0\mapsto\Func0(\Pi_n\varf0)$ is equivalent to replacing $\varf0$ with $\Pi_n\varf0$, and $\A^*$ with $\Pi_n\A^*$.
+	Let $\tens{\Pi}_n\colon\F H\to\spcf0^n$ denote the orthogonal projection.
+For Lasso, the discretised function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$ is equivalent to replacing $\varf0$ with $\tens{\Pi}_n\varf0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.
 
 	\paragraph{Discrete gradient}
-We can use $\Pi_n$ to compute the discrete sub-derivative at $\varf0_n\in\spcf0^n$:
-\begin{align}
-	\partial_n \Func0(\Pi_n\varf0_n)(\vvarx0) &= [\Pi_n\A^*(\A\varf0_n-\vdata0)](\vvarx0) + \begin{cases}
+	We can use $\tens{\Pi}_n$ to compute the discrete subdifferential at $\varf0_n\in\spcf0^n$:
+	\begin{align}
+		\partial_n \op{E}(\tens{\Pi}_n\varf0_n)(\vvarx0) &= [\tens{\Pi}_n\A^*(\A\varf0_n-\data)](\vvarx0) + \begin{cases}
 			\{+\mu\} & \varf0_n(\vvarx0)>0 \\ [-\mu,\mu] & \varf0_n(\vvarx0)=0 
@@
 		\end{cases} 
-	\\&\eqqcolon [\Pi_n\A^*(\A\varf0_n-\vdata0)](\vvarx0) + \mu\Pi_n\sign(\varf0_n(\vvarx0))
-\end{align}
-where we define $\vart0+\mu[-1,1] = [\vart0-\mu,\vart0+\mu]$ for all $\vart0\in\R$, $\mu\geq0$.
-
-As $\Norm\cdot = \norm\cdot_1$, the natural metric for $\partial_n\Func0$ is $\Norm\cdot_* = \norm\cdot_\infty$ which we can estimate
-\begin{align}
-	\Norm{\partial_n \Func0(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\min\left\{|\varf1| \st \varf1\in \Pi_n\A^*(\A\varf0_n-\vdata0)(\vvarx0) +  \mu\sign(\varf0_n(\vvarx0))\right\}
+		\\&\eqqcolon [\tens{\Pi}_n\A^*(\A\varf0_n-\data)](\vvarx0) + \mu\tens{\Pi}_n\sign(\varf0_n(\vvarx0))
+	\end{align}
+	where we define $s+\mu[-1,1] = [s-\mu,s+\mu]$ for all $s\in\R$, $\mu\geq0$.
+
+	As $\Norm\cdot = \norm\cdot_1$, the natural metric for $\partial_n\op{E}$ is $\Norm\cdot_* = \norm\cdot_\infty$ which we can estimate
+	\begin{align}
+		\Norm{\partial_n \op{E}(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\min\left\{|\varf1| \st \varf1\in \tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0) +  \mu\sign(\varf0_n(\vvarx0))\right\}
 		\\&= \max_{\vvarx0\in\Domain}\begin{cases}
-		|[\Pi_n\A^*(\A\varf0_n-\vdata0)(\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
-		\\|[\Pi_n\A^*(\A\varf0_n-\vdata0)(\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
-		\\\max\left(|[\Pi_n\A^*(\A\varf0_n-\vdata0)(\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
+			|[\tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
+			\\|[\tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
+			\\\max\left(|[\tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
 		\end{cases}
 	\end{align}
-which can be used directly in \Cref{thm: practical refinement criteria}.
+	which can be used directly in Lemma~\ref{thm: practical refinement criteria}.
 
 	\paragraph{Discrete gap}
-We now move on to the discrete gap, $\Func0(\varf0_n)-\min_{\varf0\in\spcf0^n}\Func0(\varf0)$. This can be computed with a dual representation, such as that used by \citet{Duval2017a},
-\begin{align}
-	\min_{\varf0\in \spcf0^n} \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu\Norm{\varf0} &= \min_{\varf0\in\F H}\max_{\vvard0\in\R^m} \ip{(\A\Pi_n\varf0-\vdata0)}{ \vvard0} +\mu\Norm{\Pi_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
-	\\&= \max_{\vvard0\in\R^m}\min_{\varf0\in\F H} \ip{(\A\Pi_n\varf0-\vdata0)}{\vvard0} +\mu\Norm{\Pi_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
-	\\&= \max_{\vvard0\in\R^m} \splitln{-\ip{\vdata0}{\vvard0} -\tfrac12\norm{\vvard0}_{\ell^2}^2}{\qquad\Norm{\Pi_n\A^*\vvard0}_*\leq \mu}{-\infty}{\qquad\text{else}}
-	\\&= -\min_{\vvard0\in\R^m} \underbrace{\tfrac12\norm{\vvard0}_{\ell^2}^2+\ip{\vdata0}{\vvard0}}_{\eqqcolon \Func0^*(\vvard0)}  + \chi(\Norm{\Pi_n\A^*\vvard0}_*\leq \mu).
+	We now move on to the discrete gap, $\op{E}(\varf0_n)-\min_{\varf0\in\spcf0^n}\op{E}(\varf0)$. This can be computed with a dual representation (e.g. \cite{Duval2017a}),
+	\begin{align}
+		\min_{\varf0\in \spcf0^n} \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu\Norm{\varf0} &= \min_{\varf0\in\F H}\max_{\vvard0\in\R^m} \ip{(\A\tens{\Pi}_n\varf0-\data)}{ \vvard0} +\mu\Norm{\tens{\Pi}_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
+		\\&= \max_{\vvard0\in\R^m}\min_{\varf0\in\F H} \ip{(\A\tens{\Pi}_n\varf0-\data)}{\vvard0} +\mu\Norm{\tens{\Pi}_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
+		\\&= \max_{\vvard0\in\R^m} \splitln{-\ip{\data}{\vvard0} -\tfrac12\norm{\vvard0}_{\ell^2}^2}{\qquad\Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu}{-\infty}{\qquad\text{else}}
+		\\&= -\min_{\vvard0\in\R^m} \underbrace{\tfrac12\norm{\vvard0}_{\ell^2}^2+\ip{\data}{\vvard0}}_{\eqqcolon \op{E}^*(\vvard0)}  + \chi(\Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu).
 	\end{align}
@@
 	\begin{equation}
-	\Func0(\varf0) - \min_{\varf0\in\spcf0^n}\Func0(\varf0) = \Func0(\varf0) + \min_{\vvard0\in\R^m\st \Norm{\Pi_n\A^*\vvard0}_*\leq \mu} \Func0^*(\vvard0) \leq \Func0(\varf0) + \Func0^*(\vvard0)
+		\op{E}(\varf0) - \min_{\varf0\in\spcf0^n}\op{E}(\varf0) = \op{E}(\varf0) + \min_{\vvard0\in\R^m\st \Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu} \op{E}^*(\vvard0) \leq \op{E}(\varf0) + \op{E}^*(\vvard0)
 	\end{equation}
@@
 	\begin{equation}
-	\vvard0^* = \A\varf0^*-\vdata0.
-\end{equation}
-We remark briefly that it is more conventional to include the constraint in the definition of $\Func0^*$.
-We choose to omit it here to highlight that it is only the constraint which changes between the discrete and continuous cases; $\Func0^*$ will remain the same.
+		\vvard0^* = \A\varf0^*-\data.
+	\end{equation}
+	We remark briefly that it is more conventional to include the constraint in the definition of $\op{E}^*$.
+We choose to omit it here to highlight that it is only the constraint which changes between the discrete and continuous cases; $\op{E}^*$ will remain the same.
 
@@
 	\begin{equation}
-	\vvard0_n\coloneqq \A\varf0_n - \vdata0, \qquad \Func0(\varf0)-\min_{\varf0'\in\spcf0^n}\Func0(\varf0') \leq \Func0(\varf0) +\min_{\vars2\geq 0}\left\{\Func0^*(\vars2\vvard0_n) \st \vars2 \Norm{\Pi_n\A^*\vvard0_n}_*\leq \mu\right\}
+		\vvard0_n\coloneqq \A\varf0_n - \data, \qquad \op{E}(\varf0)-\min_{\varf0'\in\spcf0^n}\op{E}(\varf0') \leq \op{E}(\varf0) +\min_{\vars2\geq 0}\left\{\op{E}^*(\vars2\vvard0_n) \st \vars2 \Norm{\tens{\Pi}_n\A^*\vvard0_n}_*\leq \mu\right\}
 	\end{equation}
@@
 	\begin{equation}
-	\vars2 =\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\Pi_n\A^*\vvard0_n}_*}\right)\right).
-\end{equation}
-To apply \Cref{alg: refining FISTA}, we are assuming that both $\func1(\varf0_n) = \frac12\norm{\vvard0_n}_{\ell^2}^2$ and $\Pi_n\nabla\func1(\varf0_n) = \Pi_n\A^*\vvard0_n$ are easily computable, therefore $\vars2$ and $\Func0(\varf0_n) +\Func0^*(\vars2\vvard0_n)$ are also easy to compute.
+		\vars2 =\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vvard0_n}_*}\right)\right).
+	\end{equation}
+	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\varf0_n) = \frac12\norm{\vvard0_n}_{\ell^2}^2$ and $\tens{\Pi}_n\nabla\op{f}(\varf0_n) = \tens{\Pi}_n\A^*\vvard0_n$ are easily computable, therefore $\vars2$ and $\op{E}(\varf0_n) +\op{E}^*(\vars2\vvard0_n)$ are also easy to compute.
 
 	\subsubsection{Bounds for countable functionals}
-Extending the results of \Cref{sec: bound discrete} to $\spcf0=\ell^1(\R)$ is analytically very simple but computationally relies heavily on the specific choice of $\A$.
-The computations of gradients and gaps carry straight over replacing $\Pi_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\spcf0^n = \{\varf0\in\ell^1\st i\notin J_n\implies \varf0_i=0\}$.
+	Extending the results of Section~\ref{sec: bound discrete} to $\spcf0=\ell^1(\R)$ is analytically very simple but computationally relies heavily on the specific choice of $\A$.
+The computations of \edit{gradients}{subdifferentials} and gaps carry straight over replacing $\tens{\Pi}_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\spcf0^n = \{\varf0\in\ell^1\st i\notin J_n\implies \varf0_i=0\}$.
 In particular,
 	\begin{align}
-	\Norm{\partial\Func0(\varf0_n)}_* &= \max_{i\in\F N}\begin{cases}
+		\Norm{\partial\op{E}(\varf0_n)}_* &= \max_{i\in\F N}\begin{cases}
 			|[\A^*\vvard0_n]_i + \mu| & [\varf0_n]_i>0
@@
 		\end{cases}
-	\\ \Func0_0(\varf0_n) &\leq \Func0(\varf0_n) + \Func0(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right)
-\end{align}
-where $\vvard0_n = \A\varf0_n-\vdata0\in\R^m$ is always exactly computable.
+		\\ \op{E}_0(\varf0_n) &\leq \op{E}(\varf0_n) + \op{E}(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right)
+	\end{align}
+	where $\vvard0_n = \A\varf0_n-\data\in\R^m$ is always exactly computable.
 
 	In the countable case, the sets $J_n$ give a clear partition into known/unknown values in these definitions.
-For $i\in J_n$ the computation is the same as in \Cref{sec: bound discrete}, then for $i\notin J_n$ we know $[\varf0_n]_i=0$ which simplifies the remaining computations.
+For $i\in J_n$ the computation is the same as in Section~\ref{sec: bound discrete}, then for $i\notin J_n$ we know $[\varf0_n]_i=0$ which simplifies the remaining computations.
 This leads to:
 	\begin{align}
-	\Norm{\partial\Func0(\varf0_n)}_* &= \max\left(\max_{i\in J_n}|[\partial\Func0(\varf0_n)]_i|,\ \max_{i\notin J_n} |[\partial\Func0(\varf0_n)]_i|\right)
-	\\&= \max\left(\Norm{\partial_n\Func0(\varf0_n)}_*,\ \max_{i\notin J_n} |[\A^*\vvard0_n]_i|-\mu\right)
-	\\ \Norm{\A^*\vvard0_n}_* &= \max\left(\max_{i\in J_n}|[\A^*\vvard0_n]_i|,\ \max_{i\notin J_n} |[\A^*\vvard0_n]_i|\right)
-	\\ &= \max\left(\Norm{\Pi_n\A^*\vvard0_n}_*,\ \max_{i\notin J_n} |[\A^*\vvard0_n]_i|\right).
-\end{align}
-Both estimates only rely on an upper bound of $\max_{i\notin J_n} |[\A^*\vvard0_n]_i|$. One example computing this value is seen in \Cref{sec: wavelet examples}.
+		\Norm{\partial\op{E}(\varf0_n)}_* &= \max\left(\max_{i\in J_n}|[\partial\op{E}(\varf0_n)]_i|,\ \sup_{i\notin J_n} |[\partial\op{E}(\varf0_n)]_i|\right)
+		\\&= \max\left(\Norm{\partial_n\op{E}(\varf0_n)}_*,\ \sup_{i\notin J_n} |[\A^*\vvard0_n]_i|-\mu\right)
+		\\ \Norm{\A^*\vvard0_n}_* &= \max\left(\max_{i\in J_n}|[\A^*\vvard0_n]_i|,\ \sup_{i\notin J_n} |[\A^*\vvard0_n]_i|\right)
+		\\ &= \max\left(\Norm{\tens{\Pi}_n\A^*\vvard0_n}_*,\ \sup_{i\notin J_n} |[\A^*\vvard0_n]_i|\right).
+	\end{align}
+	Both estimates only rely on an upper bound of $\max_{i\notin J_n} |[\A^*\vvard0_n]_i|$. One example computing this value is seen in Section~\ref{sec: wavelet examples}.
 
 	\subsubsection{Bounds for continuous functionals}\label{sec: bound continuous}
-Finally we extend the results of \Cref{sec: bound discrete} to continuous Lasso. Similar to the countable case, the exact formulae can be written down immediately:
-\begin{align}
-	\Norm{\partial\Func0(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\begin{cases}
+	Finally we extend the results of Section~\ref{sec: bound discrete} to continuous Lasso. Similar to the countable case, the exact formulae can be written down immediately:
+	\begin{align}
+		\Norm{\partial\op{E}(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\begin{cases}
 			|[\A^*\vvard0_n](\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
@@
 		\end{cases}
-	\\ \Func0_0(\varf0_n) &\leq \Func0(\varf0_n) + \Func0(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\vdata0}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right).
+		\\ \op{E}_0(\varf0_n) &\leq \op{E}(\varf0_n) + \op{E}(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right).
 	\end{align}
@@
 	\begin{align}
-	\Norm{\partial \Func0(\varf0_n)}_* &= \max_{\domain_i^n\in\F M^n} \begin{cases}
+		\Norm{\partial \op{E}(\varf0_n)}_* &= \max_{\domain_i^n\in\F M^n} \begin{cases}
 			\norm{\A^*\vvard0_n + \mu}_{L^\infty(\domain_i^n)} & \varf0_n|_{\domain_i^n} > 0
@@
 	\end{align}
-Now, both estimates rely on cell-wise supremum norms of $\A^*\vvard0_n$ which we assume is sufficiently smooth.
+	Now, both estimates rely on cell-wise supremum norms of $\A^*\vvard0_n$ which we have assumed is sufficiently smooth.
 We will therefore use a cell-wise Taylor expansion to provide a simple and accurate estimate.
@@
 	\end{equation}
-A zeroth order expansion would be optimally inefficient (approximating $|[\nabla\A^*\vvard0_n](\vvarx0_i)|$ with $|\A^*\vvard0_n|_{C^1}$) and a second order expansion would possibly be the most elegant but harder to implement.
+	A zeroth order expansion would be optimally inefficient (approximating $|[\nabla\A^*\vvard0_n](\vvarx0_i)|$ with $|\A^*\vvard0_n|_{C^1}$) and a second order expansion would possibly be more elegant but harder to implement.
 We found that a first order expansion was simple and efficient.
@@
 	The bounds presented here for continuous Lasso emphasise the twinned properties required for adaptive mesh optimisation.
-The mesh should be refined greedily to the structures of $\varf0^*$, but also must be sufficiently uniform to provide a good estimate for $\Func0(\varf0^*)$.
+The mesh should be refined greedily to the structures of $\varf0^*$, but also must be sufficiently uniform to provide a good estimate for $\op{E}(\varf0^*)$.
 This is a classical exploitation/exploration trade-off; exploiting visible structure whilst searching for other structures which are not yet visible.
@@
 	\subsection{Support detection}\label{sec: support detection}
-The main motivation for using Lasso in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\varf0^*$ is also provably close to the `true' support \citep{Duval2017a,Poon2018}.
+	The main motivation for using Lasso in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\varf0^*$ is also provably close to the `true' support \cite{Duval2017a,Poon2018}.
 If $\varf0_n\approx \varf0^*$ in the appropriate sense, then we should also be able to quantify the statement $\op{supp}(\varf0_n)\approx\op{supp}(\varf0^*)$.
-Such methods are referred to as \emph{safe screening} rules \citep{ElGhaoui2010} which gradually identify the support and allow the optimisation algorithm to constrain parts of the reconstruction to 0.
+Such methods are referred to as \emph{safe screening} rules \cite{ElGhaoui2010} which gradually identify the support and allow the optimisation algorithm to constrain parts of the reconstruction to 0.
 In this subsection we propose a new simple screening rule which is capable of generalising to our continuous subspace approximation setting.
-It is likely that more advanced methods \citep{Bonnefoy2015,Ndiaye2017} can also be adapted, although that is beyond the scope of this work.
+It is likely that more advanced methods \cite{Bonnefoy2015,Ndiaye2017} can also be adapted, although that is beyond the scope of this work.
 The key difference is the allowance of inexact computations resulting from estimates such as \eqref{eq: Taylor approximation}.
 
-The work of \citet{Duval2017a,Poon2018} and many others characterise the support of $\varf0^*$ very precisely.
+	The support of $\varf0^*$ has already been characterised very precisely \cite{Duval2017a,Poon2018}.
 In particular, the support is at most $m$ distinct points and are a subset of $\{ \vvarx0\in\Domain \st |\A^*\vvard0^*|(\vvarx0) = \mu\} $ (an equivalent statement holds for the countable case).
-Less formally, this can also be seen from the the gradient computations in \Cref{sec: Lasso gap and gradient}, for all $\vvarx0\in\supp(\varf0^*)$ we have
-\begin{equation}
-	0\in \partial \Func0(\varf0^*)(\vvarx0) = [\A^*\vvard0^*](\vvarx0) + \mu\sign(\varf0^*(\vvarx0)).
-\end{equation}
-
-Heuristically, we will use strong convexity of $\Func0^*$ and smoothness of $\A^*$ to quantify the statement:
-$$ \text{if}\quad \Func0(\varf0_n) + \Func0^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st |[\A^*\vvard0_n](\vvarx0)|\ll \mu\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
-First we use the strong convexity of $\Func0^*$, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible then
-\begin{equation}
-	\tfrac12\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}^2 \leq \Func0^*(\vars2_0\vvard0_n) - \Func0^*(\vvard0^*) = \Func0^*(\vars2_0\vvard0_n) + \Func0(\varf0^*) \leq \Func0^*(\vars2_0\vvard0_n) + \Func0(\varf0_n),
+Less formally, this can also be seen from the the \edit{gradient}{subdifferential} computations in Section~\ref{sec: Lasso gap and gradient}, for all $\vvarx0\in\supp(\varf0^*)$ we have
+	\begin{equation}
+		0\in \partial \op{E}(\varf0^*)(\vvarx0) = [\A^*\vvard0^*](\vvarx0) + \mu\sign(\varf0^*(\vvarx0)).
+	\end{equation}
+
+	Heuristically, we will use strong convexity of $\op{E}^*$ and smoothness of $\A^*$ to quantify the statement:
+	$$ \text{if}\quad \op{E}(\varf0_n) + \op{E}^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st |[\A^*\vvard0_n](\vvarx0)|\ll \mu\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
+	First we use the strong convexity of $\op{E}^*$, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible then
+	\begin{equation}
+		\tfrac12\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}^2 \leq \op{E}^*(\vars2_0\vvard0_n) - \op{E}^*(\vvard0^*) = \op{E}^*(\vars2_0\vvard0_n) + \op{E}(\varf0^*) \leq \op{E}^*(\vars2_0\vvard0_n) + \op{E}(\varf0_n),
 	\end{equation}
@@
 	\begin{align}
-	\min_{\vvarx0\in\supp(\varf0^*)} |[\Pi_n\A^*\vvard0_n](\vvarx0)| &\geq \min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0_n](\vvarx0)|
+		\min_{\vvarx0\in\supp(\varf0^*)} |[\tens{\Pi}_n\A^*\vvard0_n](\vvarx0)| &\geq \min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0_n](\vvarx0)|
 		\\&= \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vars2_0 \vvard0_n](\vvarx0)|
@@
 	\begin{equation}
-	|[\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\Func0(\varf0_n)+\Func0^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq: support equation}
+		|[\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\op{E}(\varf0_n)+\op{E}^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq: support equation}
 	\end{equation}
 	This equation is valid when $\vvarx0$ is either a continuous or countable index, the only distinction is to switch to $\ell^\infty$ in the norm of $\A^*$.
-To make the equivalent statement on the discretised problem, simply replace $\vars2_0$ with $\vars2$ and $\A^*$ with $\Pi_n\A^*$.
+To make the equivalent statement on the discretised problem, simply replace $\vars2_0$ with $\vars2$ and $\A^*$ with $\tens{\Pi}_n\A^*$.
 There are two short observations on this formula:
 	\begin{itemize}
-	\item The convergence guarantee from \Cref{thm: exponential FISTA convergence} is for the quantity $\Func0(\varf0_n)-\Func0(\varf0^*)$, the more relevant quantity here is $\Func0^*(\vars2_0\vvard0_n)+\Func0(\varf0^*)$ for which there is no proven rate.
-	\item In \Cref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
+		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the quantity $\op{E}(\varf0_n)-\op{E}(\varf0^*)$, the more relevant quantity here is $\op{E}^*(\vars2_0\vvard0_n)+\op{E}(\varf0^*)$ for which there is no proven rate.
+		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
 	\end{itemize}
@@
 	For numerical implementation of Lasso, we are required to accurately estimate several operator norms of $\A$.
-For $\func1$ to be 1-Lipschitz we must divide by $\norm{\A^*\A}$, and the adaptivity described in \Cref{sec: continuous lasso rate,sec: bound continuous,sec: support detection} requires the values of $|\A^*|_{\ell^2\to L^\infty}$, $|\A^*|_{\ell^2\to C^1}$, and $|\A^*|_{\ell^2\to C^2}$.
-The aim for this section is to provide estimates of these norms and seminorms for the numerical examples presented in \Cref{sec: numerics}.
+For $\op{f}$ to be 1-Lipschitz we must divide by $|\A\A^*|_{\ell^2\to\ell^2}$, and the adaptivity described in Sections~\ref{sec: continuous lasso rate}, \ref{sec: bound continuous}, and~\ref{sec: support detection} requires the values of $|\A^*|_{\ell^2\to L^\infty}$, $|\A^*|_{\ell^2\to C^1}$, and $|\A^*|_{\ell^2\to C^2}$.
+The aim for this section is to provide estimates of these norms and seminorms for the numerical examples presented in Section~\ref{sec: numerics}.
 
 	We start by specifying the structure of $\A$.
-By linearity, there must exist kernels $\vard1_j\in \F H\cap\spcf0^*$ such that $(\A\varf0)_j = \IP{\vard1_j}{\varf0}$ for all $\varf0\in \F H\cup\spcf0$, $j=1,\ldots,m$.
+By continuity of $\A$, there must exist kernels $\vard1_j\in \F H\cap\spcf0^*$ such that $(\A\varf0)_j = \IP{\vard1_j}{\varf0}$ for all $\varf0\in \F H\cup\spcf0$, $j=1,\ldots,m$.
 In this form, the adjoint can be written precisely, $\A^*\colon\R^m\to \F H$ by
@@
 
-The following lemma allows for exact computation of the operator norm of $\A$, as needed to ensure that $\func1$ is 1-Lipschitz.
+	The following lemma allows for exact computation of the operator norm of $\A$, as needed to ensure that $\op{f}$ is 1-Lipschitz.
 	\begin{lemma}\label{thm: norm bound L2}
@@
 		as required.
-\end{proof}
-If $\norm{\A^*\A}$ is not analytically tractable, then \Cref{thm: norm bound L2} enables it to be computed using standard finite dimensional methods.
+		\qed\end{proof}
+	If $\norm{\A^*\A}$ is not analytically tractable, then Lemma~\ref{thm: norm bound L2} enables it to be computed using standard finite dimensional methods.
 The operator $\A\A^*$ is always finite dimensional and can be computed without discretisation error.
@@
 		for $Q = \frac2q$.
-\end{proof}
-
-\subsubsection{Concrete examples}
-We now present explicit examples of the computations in both \Cref{thm: norm bound smoothness,thm: norm bound L2} for the numerical results in \Cref{sec: numerics}.
-These examples are common in practical applications and we show the result of \Cref{thm: norm bound examples} in the main text to demonstrate that, while sometimes hard to compute by hand, the constants can estimated accurately in an efficient manner.
+		\qed\end{proof}
+
+	\subsubsection{Specific examples}
+	We now present explicit examples of the computations in both Lemmas~\ref{thm: norm bound smoothness} and~\ref{thm: norm bound L2} for the numerical results in Section~\ref{sec: numerics}.
+These examples are common in practical applications and we show the result of Theorem~\ref{thm: norm bound examples} in the main text to demonstrate that, while sometimes hard to compute by hand, the constants can estimated accurately in an efficient manner.
 	\begin{theorem}\label{thm: norm bound examples}
 		\Copy{thm: norm bound examples}{
-		Suppose $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in \F H=L^2([0,1]^d)$ for $j\in[m]$.
+			Suppose $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in L^\infty([0,1]^d)$ for $j\in[m]$.
 			\begin{enumerate}
-			\item[Case 1:] If $\vard1_j(\vvarx0) = \splitln{1}{\vvarx0\in \F{\Varx0}_j}{0}{\text{ else}}$ for some collection $\F{\Varx0}_j\subset\Domain$ such that $\F{\Varx0}_i\cap \F{\Varx0}_j = \emptyset$ for all $i\neq j$, then
-			$$\norm{\A}_{L^2\to\ell^2} = \max_j \sqrt{|\F{\Varx0}_j|}.$$
+				\item[Case 1:] If $\vard1_j(\vvarx0) = \splitln{1}{\vvarx0\in \F{X}_j}{0}{\text{ else}}$ for some collection $\F{X}_j\subset\Domain$ such that $\F{X}_i\cap \F{X}_j = \emptyset$ for all $i\neq j$, then
+				$$\norm{\A}_{L^2\to\ell^2} = \max_{j\in[m]} \sqrt{|\F{X}_j|}.$$
 
@@
 				$$\{\vvarx0_j\st j\in[m]\} = \{\vvarx0_0 + (j_1\Delta,\ldots,j_d\Delta)\st j_i\in[\hat m]\}$$
-			for some $\vvarx0_0\in\R^d$, $\hat m\coloneqq\sqrt[d]{m}$. For all $\frac1q + \frac{1}{q^*} = 1$, $q\in(1,\infty]$, we get
+				for some $\vvarx0_0\in\R^d$, $\hat m\coloneqq\sqrt[d]{m}$. For all $\frac1q + \frac{1}{q^*} = 1$, $q\in(1,\infty]$, we have
 				\begin{align}
@@
 	We present four numerical Lasso examples.
-The first two are in 1D to demonstrate the performance of different variants of \Cref{alg: refining FISTA}, both with and without adaptivity.
+The first two are in 1D to demonstrate the performance of different variants of Algorithm~\ref{alg: refining FISTA}, both with and without adaptivity.
 In particular, we explore sparse Gaussian deconvolution and sparse signal recovery from Fourier data.
-We compare with the \emph{continuous basis pursuit} (CBP) discretisation \citep{Ekanadham2011, Duval2017b} which is also designed to achieve super-resolution accuracy within a convex framework.
-More details of this method will be provided in \Cref{sec: 1D Lasso examples}.
+We compare with the \emph{continuous basis pursuit} (CBP) discretisation \cite{Ekanadham2011,Duval2017b} which is also designed to achieve super-resolution accuracy within a convex framework.
+More details of this method will be provided in Section~\ref{sec: 1D Lasso examples}.
 
@@
 
-In this section, the main aim is to minimise the exact Lasso energy $\Func0_0(\varf0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
-\Cref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\Func0_0(\varf0_n)$ so it is this monotone estimate which is plotted.
-To clarify, as $\Func0(\varf0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\Func0_0(\varf0_n) \approx \min_{n\leq N}\Func0(\varf0_n) + \min_{n'\leq n}\Func0^*(\vars2_0\vvard0_{n'})$.
-Another quantity of interest is minimisation of the discrete Lasso energy $\min_{n\leq N}\Func0(\varf0_n) + \min_{n'\leq n}\Func0^*(\vars2\vvard0_{n'})$ which will be referred to as the `discrete gap'.
-Note that for the adaptive schemes this may not be exactly monotonic as the discrete dual problem changes with $N$.
+	In this section, the main aim is to minimise the exact Lasso energy $\op{E}_0(\varf0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
+Lemma~\ref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\op{E}_0(\varf0_n)$ so it is this monotone estimate which is plotted.
+To clarify, as $\op{E}(\varf0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\op{E}_0(\varf0_n) \approx \min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2_0\vvard0_{n'})$.
+Another quantity of interest is minimisation of the discrete Lasso energy $\min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2\vvard0_{n'})$ which will be referred to as the `discrete gap'.
+Note that for the adaptive schemes the discrete gap may not monotonic as the discrete dual problem changes with $N$.
+
+	The code to reproduce these examples can be found on github\footnote{\href{https://github.com/robtovey/2020SpatiallyAdaptiveFISTA}{https://github.com/robtovey/2020SpatiallyAdaptiveFISTA}}.
 
@@
 	Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.
-There are many methods designed to minimise the continuous Lasso energy in \eqref{eq: Lasso energy} \citep[c.f.][]{Bredies2013,Castro2016,Boyd2017,Catala2019} however, most the solution of a non-convex problem.
+There are many methods designed to minimise the continuous Lasso energy in \eqref{eq: Lasso energy} (c.f.
+\cite{Bredies2013,Castro2016,Boyd2017,Catala2019}) however, most \edit{}{require} the solution of a non-convex problem.
 We have focused on CBP because it approximates $\varf0^*$ through a convex discrete optimisation problem which is asymptotically exact in the limit $\meshsize\to0$.
 It can also be optimised with FISTA which allows for direct comparison with the uniform and adaptive mesh approaches.
-As explained by \citet{Ekanadham2011, Duval2017b}, the idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen.
-If $\varf0^*$ has only one Dirac spike in each pixel then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.
-
-As shown in \Cref{sec: Lasso definition}, in 1D we have $\vars3_{\Varf0} = \vars3_{\Func0} = 2$.
-The estimates given in \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\Func0_0(\varf0_n)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$.
-To achieve these rates, we implement a refinement criterion from \Cref{thm: practical refinement criteria} with guarantee of $\Func0_0(\varf0_{n_k-1})\lesssim 2^{-k}$ using the estimates made in \Cref{sec: Lasso gap and gradient}.
+The idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen \cite{Ekanadham2011,Duval2017b}.
+If $\varf0^*$ has only one Dirac spike in each pixel, then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.
+
+	As shown in Section~\ref{sec: Lasso definition}, in 1D we have $\vars3_{\Varf0} = \vars3_{\op{E}} = 2$.
+The estimates given in \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\op{E}_0(\varf0_n)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$.
+To achieve these rates, we implement a refinement criterion from Lemma~\ref{thm: practical refinement criteria} with guarantee of $\op{E}_0(\varf0_{n_k-1})\lesssim 2^{-k}$ using the estimates made in Section~\ref{sec: Lasso gap and gradient}.
 We choose subspaces $\spcf0^n$ to approximately enforce
 	\begin{equation}
-	\Func0(\varf0_n) + \Func0^*(\vars2_0\vvard0_n) \leq 2(\Func0(\varf0_n) + \Func0^*(\vars2\vvard0_n)),
+		\op{E}(\varf0_n) + \op{E}^*(\vars2_0\vvard0_n) \leq 2(\op{E}(\varf0_n) + \op{E}^*(\vars2\vvard0_n)),
 	\end{equation}
@@
 	\begin{equation}
-	\Func0^*(\vars2_0\vvard0_n) = \tfrac12\norm{\vars2_0\vvard0_n}^2 + \vars2_0\ip{\vdata0}{\vvard0_n} = \frac{\vars2_0}{\vars2}\left(\frac{\vars2_0}{\vars2}\tfrac12\norm{\vars2\vvard0_n}^2 + \vars2\ip{\vdata0}{\vvard0_n}\right) \approx \frac{\vars2_0}{\vars2} \Func0^*(\vars2\vvard0_n).
+		\op{E}^*(\vars2_0\vvard0_n) = \tfrac12\norm{\vars2_0\vvard0_n}^2 + \vars2_0\ip{\data}{\vvard0_n} = \frac{\vars2_0}{\vars2}\left(\frac{\vars2_0}{\vars2}\tfrac12\norm{\vars2\vvard0_n}^2 + \vars2\ip{\data}{\vvard0_n}\right) \approx \frac{\vars2_0}{\vars2} \op{E}^*(\vars2\vvard0_n).
 	\end{equation}
@@
 	\begin{equation}
-	\frac{\vars2_0}{\vars2} \approx \frac{\Norm{\A^*\vvard0_n}_*}{\Norm{\Pi_n\A^*\vvard0_n}_*} = \frac{\max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{\max_{\domain_i^n\in\F M^n} |\Pi_n\A^*\vvard0_n(\domain_i^n)|} \approx \max_{\domain_i^n\in\F M^n}\frac{ \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{|\Pi_n\A^*\vvard0_n(\domain_i^n)|}
+		\frac{\vars2_0}{\vars2} \approx \frac{\Norm{\A^*\vvard0_n}_*}{\Norm{\tens{\Pi}_n\A^*\vvard0_n}_*} = \frac{\max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{\max_{\domain_i^n\in\F M^n} |\tens{\Pi}_n\A^*\vvard0_n(\domain_i^n)|} \approx \max_{\domain_i^n\in\F M^n}\frac{ \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{|\tens{\Pi}_n\A^*\vvard0_n(\domain_i^n)|}
 	\end{equation}
@@
 Note briefly that this greedy strategy directly targets uncertainty, refinements also happen outside of the support of $u_n$ to guarantee that this is representative of $\varf0^*$.
-Such refinement is necessary to avoid critical points of $\Func0$ which are not global minimisers.
+Such refinement is necessary to avoid critical points of $\op{E}$ which are not global minimisers.
 
 	\paragraph{Comparison of discretisation methods}
-In \Cref{fig: convergence with ndofs} we compare the three core approaches: fixed uniform
+	In Figure~\ref{fig: convergence with ndofs} we compare the three core approaches: fixed uniform
 	discretisation, adaptive discretisation, and CBP.
 In particular, we wish to observe their convergence properties as the number of pixels is allowed to grow.
-In each case we use a FISTA stepsize of $\vart1_n = \frac{n+19}{20}$.
+In each case we use a FISTA stepsize of $t_n = \frac{n+19}{20}$.
 The adaptive discretisation is started with one pixel and limited to 128, 256, or 512 pixels while the fixed and CBP discretisations have uniform discretisations with the maximum number of pixels.
@@
 This suggests that the performance of CBP depends highly on the smoothness of $\A$.
-	\item The discrete gaps for non-adaptive optimisation behave as is common for FISTA, initial convergence is polynomial until a locally linear regime activates \citep{Tao2016}.
+		\item The discrete gaps for non-adaptive optimisation behave as is common for FISTA, initial convergence is polynomial until a locally linear regime activates \cite{Tao2016}.
 CBP is always slower to converge than the piecewise constant discretisation.
@@
 
-\begin{figure}[H]\centering
+	\begin{figure}\centering
 		\includegraphics[width=.84\textwidth]{lasso_ndofs_convergence}
@@
 Both `fixed' and `CBP' use standard FISTA with a uniform discretisation.}\label{fig: convergence with ndofs}
+
+		\vspace*{\floatsep}
+
+		\includegraphics[width=.84\textwidth]{lasso_convergence_short}
+		\caption{Discrete convergence of different algorithms.
+`Adaptive' methods use Algorithm~\ref{alg: refining FISTA} with fewer than 1024 pixels and the remaining methods use a uniform discretisation of 1024 pixels.}\label{fig: convergence with method}
 	\end{figure}
@@
 	\paragraph{Comparison of FISTA variants}
-\Cref{fig: convergence with method} compares many methods with either fixed or adaptive discretisations.
+	Figure~\ref{fig: convergence with method} compares many methods with either fixed or adaptive discretisations.
 Each adaptive scheme is allowed up to 1024 pixels and each uniform discretisation uses exactly 1024.
-The `Greedy FISTA' implementation was proposed by \citet{Liang2018} and we include the adaptive variant despite a lack of convergence proof.
-The remaining FISTA algorithms use a FISTA time step of $\vart1_n = \frac{n+a-1}{a}$ for the given value of $a$, as proposed by \citet{Chambolle2015}.
+The `Greedy FISTA' implementation was proposed by in \cite{Liang2018} and we include the adaptive variant despite a lack of convergence proof.
+The remaining FISTA algorithms use a FISTA time step of $t_n = \frac{n+a-1}{a}$ for the given value of $a$, as proposed in \cite{Chambolle2015}.
 In this example CBP used the greedy FISTA implementation which gave faster observed convergence.
-\Cref{fig: convergence with method} compares the discrete gaps because it is the accurate metric for fixed discretisations, and for the adaptive discretisation it should also be an accurate predictor of the continuous gap.
+Figure~\ref{fig: convergence with method} compares the discrete gaps because it is the accurate metric for fixed discretisations, and for the adaptive discretisation it should also be an accurate predictor of the continuous gap.
 
@@
 The coarse-to-fine adaptivity is not slower than fixed discretisations in this regime.
-	\item \Cref{thm: practical refinement criteria} accurately predicts the $\frac1n$ rate of the adaptive methods, mirrored in the fixed discretisations.
+		\item Lemma~\ref{thm: practical refinement criteria} accurately predicts the $\frac1n$ rate of the adaptive methods, mirrored in the fixed discretisations.
 This suggests that high-resolution discretisations are also initially limited by this $\frac1n$ rate before entering the asymptotic regime.
-	\item The fastest FISTA algorithm is consistently the greedy one, although $a=20$ is very comparable.
+		\item The fastest FISTA algorithm is consistently the greedy variant, although $a=20$ is very comparable.
 	\end{itemize}
 
-\begin{figure}[H]\centering
-	\includegraphics[width=.84\textwidth]{lasso_convergence_short}
-	\caption{Discrete convergence of different algorithms.
-`Adaptive' methods use \Cref{alg: refining FISTA} with fewer than 1024 pixels and the remaining methods use a uniform discretisation of 1024 pixels.}\label{fig: convergence with method}
-\end{figure}
-
 	\paragraph{Comparison of fixed and adaptive discretisation}
-Motivated by the findings in \Cref{fig: convergence with method}, we now look more closely at the performance of the $a=20$ and the greedy FISTA schemes.
+	Motivated by the findings in Figure~\ref{fig: convergence with method}, we now look more closely at the performance of the $a=20$ and the greedy FISTA schemes.
 We have analytical results for the former but the latter typically performs the best for non-adaptive optimisation and is never worse than $a=20$ in the adaptive setting.
@@
 The fixed discretisations use 1024 pixels (i.e.
-constant pixel size of $2^{-10}$ in \Cref{fig: comparison with iteration}) and the adaptive discretisation starts with two pixels with an upper limit of 1024.
-As expected, the fixed discretisation starts with a smaller continuous gap before plateauing to a sub-optimal gap around $\Func0_0=0.1$.
-
-\Cref{fig: comparison with iteration} shows convergence of pixel size and continuous gap with respect to number of iterations.
-\Cref{fig: comparison with time} shows the more practical attributes of continuous gap and number of pixels against execution time.
+constant pixel size of $2^{-10}$ in Figure~\ref{fig: comparison with iteration}) and the adaptive discretisation starts with two pixels with an upper limit of 1024.
+As expected, the fixed discretisation starts with a smaller continuous gap before plateauing to a sub-optimal gap around $\op{E}_0=0.1$.
+
+	Figure~\ref{fig: comparison with iteration} shows convergence of pixel size and continuous gap with respect to number of iterations.
+Figure~\ref{fig: comparison with time} shows the more practical attributes of continuous gap and number of pixels against execution time.
 We see that the adaptive discretisation is consistently capable of computing lower energies with fewer pixels and in less time than the uniform discretisation.
@@
 
-Suppose that the numerical aim is to find a function $\varf0_n$ with $\Func0_0(\varf0_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.
+	Suppose that the numerical aim is to find a function $\varf0_n$ with $\op{E}_0(\varf0_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.
 For $n\in[10^3,10^4]$, in both problems, the adaptive schemes coincide with the fixed schemes in both energy and minimum pixel size.
@@
 
-		\node[bag] at (0,0) {$\tilde{\spcf0}^0$}
-		child {node[bag] {$w_{0,0}$ $[0,1]$}
-			child {node[bag] {$w_{0,1}$ $[0,\frac12]$}
-				child {node[bag] {$w_{0,2}$ $[0,\frac14]$}
-				} child {node[bag] {$w_{1,2}$ $[\frac14,\frac12]$}
-				}
-			} child {node[bag] {$w_{1,1}$ $[\frac12,1]$}
+				\node[bag] at (0,0) {$ $}
+				child {node[bag] {$(0,0)$ $[0,1]$}
+					child {node[bag] {$(0,1)$ $[0,\frac12]$}
+						child {node[bag] {$(0,2)$ $[0,\frac14]$}
+						} child {node[bag] {$(1,2)$ $[\frac14,\frac12]$}
+						}
+					} child {node[bag] {$(1,1)$ $[\frac12,1]$}
 				}};
-
 		\end{tikzpicture}\end{center}
-	\caption{Tree representation of 1D wavelets $w_{j,k}$ are arranged in a tree structure with their support underneath.}\label{fig: wavelet tree}
+		\caption{Example tree representation of 1D wavelets.
+Left: nodes, leaves, and mesh of discretisation.
+Right: arrangement into a tree with index $(j,k)$ and corresponding support of wavelet $w_{j,k}$ underneath.}\label{fig: wavelet tree}
 	\end{figure}
@@
 	\subsection{2D wavelet Lasso}\label{sec: wavelet examples}
-In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{\Varx0}^I_i$ where 
-\begin{equation}
-	\F{\Varx0}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{50},-\tfrac12+\tfrac{i}{50}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I \quad \text{ for } i,I=1,2,\ldots,50.
-\end{equation}
-This is not exactly in the form analysed by \Cref{thm: norm bound examples}, however for each $I$ the sets $\{\F{\Varx0}^I_i\st i\in[50]\}$ are disjoint therefore we can apply \Cref{thm: norm bound examples} block-wise to estimate
-\begin{equation}
-	\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[50]} |\F{\Varx0}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[50]} \int_{\F{\Varx0}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[50]}\ (\A\1)_{i,I}}\;.
+	In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{X}^I_i$ where 
+	\begin{equation}
+		\F{X}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{50},-\tfrac12+\tfrac{i}{50}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I \quad \text{ for } i,I=1,2,\ldots,50.
+	\end{equation}
+	This is not exactly in the form analysed by Theorem~\ref{thm: norm bound examples}, however only the sets $\{\F{X}^I_i\st i\in[50]\}$ for each $I$ are disjoint, therefore we apply Theorem~\ref{thm: norm bound examples} block-wise to estimate
+	\begin{equation}
+		\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[50]} |\F{X}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[50]} \int_{\F{X}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[50]}\ (\A\1)_{i,I}}\;.
 	\end{equation}
@@
 	\begin{equation}
-	\min_{\varf0\in \spcf0} \tfrac12\norm{\A\varf0-\vdata0}_{\ell^2}^2 + \mu \norm{\linop{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \tfrac12\norm{\A\linop{W}\hat{\varf0}-\vdata0}_{\ell^2}^2 + \mu \norm{\hat{\varf0}}_{\ell^1}.
-\end{equation}
-The minimisers are related by $\varf0^* = \linop{W}\hat{\varf0}^*$ and, for wavelet bases, $\linop{W}$ is orthonormal so $\norm{\A\linop{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$.
-From \Cref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\linop{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$.
-If $\linop{W}$ is a wavelet transformation then its columns, $w_j\in L^2$, are simply the wavelets themselves and we can use the bound
-\begin{equation}
-	|\IP{w_j}{\A^*\vvard0_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vvard0_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vvard0_n}_{L^2}\leq \norm{\1_{\F{\Varx0}} \A^*\vvard0_n}_{L^2}
-\end{equation}
-for all $\F{\Varx0}\supset \supp(w_j)$.
+		\min_{\varf0\in \spcf0} \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu \norm{\tens{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \tfrac12\norm{\A\tens{W}\hat{\varf0}-\data}_{\ell^2}^2 + \mu \norm{\hat{\varf0}}_{\ell^1}.
+	\end{equation}
+	The minimisers are related by $\varf0^* = \tens{W}\hat{\varf0}^*$ and, for wavelet bases, $\tens{W}$ is orthonormal so $\norm{\A\tens{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$.
+From Section~\ref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\tens{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$.
+If $\tens{W}$ is a wavelet transformation then its columns, $w_j\in L^2$, are simply the wavelets themselves and we can use the bound
+	\begin{equation}
+		|\IP{w_j}{\A^*\vvard0_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vvard0_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vvard0_n}_{L^2}\leq \norm{\1_{\F{X}} \A^*\vvard0_n}_{L^2}
+	\end{equation}
+	for all $\F{X}\supset \supp(w_j)$.
 	In the case of the Radon transform, we can compute the left-hand side explicitly for the finitely many $j\in J_n$ but we wish to use the right-hand side in a structured way to avoid computing the infinitely many $j\notin J_n$.
@@
 	\paragraph{Tree structure of wavelets}
-Finite elements are constructed with a mesh which provided a useful tool for adaptive refinement in \Cref{sec: bound continuous}.
-For wavelets, we will associate a tree with every discretisation and the leaves of the tree form a mesh.
+	Finite elements are constructed with a mesh which provided a useful tool for adaptive refinement in Section~\ref{sec: bound continuous}.
+For wavelets, we will associate a tree with every discretisation and the leaves of the tree correspond to a mesh.
 This perspective comes from the multi-resolution interpretation of wavelets.
-An example is seen in \Cref{fig: wavelet tree} for 1D Haar wavelets, $w_{j,k}(\varx0) = \sqrt{2}^k\vard1(2^{k}\varx0-j)$ where $\vard1 = \1_{[0,1)} - \1_{[-1,0)}$.
+An example is seen in Figure~\ref{fig: wavelet tree} for 1D Haar wavelets, $w_{j,k}(\varx0) = \sqrt{2}^k\vard1(2^{k}\varx0-j)$ where $\vard1 = \1_{[0,1)} - \1_{[-1,0)}$.
 
@@
 The only change in our own implementation is to translate the support to $[-\tfrac12,\tfrac12]^2$.
-We briefly remark that the tree structuring of wavelets is not novel and appears more frequently in the Bayesian inverse problems literature, for example see \citet{Castillo2019}.
+We briefly remark that the tree structuring of wavelets is not novel and appears more frequently in the Bayesian inverse problems literature \cite{Castillo2019}.
 
 	\paragraph{Continuous gradient estimate}
-In \Cref{sec: 1D Lasso examples} we used the continuous gap as a measure for convergence, for wavelets we will use the continuous gradient.
-With the tree structure we can easily adapt the results of \Cref{sec: Lasso gap and gradient} to estimate gradients (or function gaps).
+	In Section~\ref{sec: 1D Lasso examples} we used the continuous gap as a measure for convergence, for wavelets we will use the continuous \edit{gradient}{subdifferential}.
+With the tree structure we can easily adapt the results of Section~\ref{sec: Lasso gap and gradient} to estimate \edit{gradients}{subdifferentials} (or function gaps).
 In particular,
 	\begin{align}
-	\Norm{\partial \Func0(\varf0_n)}_* &=\max\left(\Norm{\partial_n\Func0(\varf0_n)}_*, \max_{j\notin J_n} |\IP{w_j}{\A^*\vvard0_n}| -\mu \right) \\&\leq\max\left(\Norm{\partial_n\Func0(\varf0_n)}_*, \max_{j\in \op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu \right).\label{eq: wavelet error metric}
+		\Norm{\partial \op{E}(\varf0_n)}_* &=\max\left(\Norm{\partial_n\op{E}(\varf0_n)}_*, \max_{j\notin J_n} |\IP{w_j}{\A^*\vvard0_n}| -\mu \right) \\&\leq\max\left(\Norm{\partial_n\op{E}(\varf0_n)}_*, \max_{j\in \op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu \right).\label{eq: wavelet error metric}
 	\end{align}
@@
 	\paragraph{Numerical results}
-We consider two phantoms where $\varf0^\dagger$ is either a binary disc or the Shepp-Logan phantom.
+	We consider two phantoms where the ground-truth is either a binary disc or the Shepp-Logan phantom.
 No noise is added to the Shepp-Logan data but \SI{5}{\percent} Gaussian white noise is added to the disc data.
-This is visualised in \Cref{fig: haar data}.
+This is visualised in Figure~\ref{fig: haar data}.
 All optimisations shown will be spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$.
@@
 Motivated by \eqref{eq: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ to ensure that
-$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\Func0(\varf0_n)}_*$$
+	$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\op{E}(\varf0_n)}_*$$
 	for all $j$ and $n$ (i.e. so that the continuous gradient is less than 10 times the discrete gradient).
 
-The first numerical results shown in \Cref{fig: haar convergence} compare the same adaptive algorithms as shown in \Cref{fig: convergence with method}.
+	The first numerical results shown in Figure~\ref{fig: haar convergence} compare the same adaptive algorithms as shown in Figure~\ref{fig: convergence with method}.
 In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower.
@@
 		\includegraphics[width=.85\textwidth]{haar_convergence_short}
-	\caption{Discrete convergence of different implementations of \Cref{alg: refining FISTA} with an unlimited number of pixels.}\label{fig: haar convergence}
+		\caption{Discrete convergence of different implementations of Algorithm~\ref{alg: refining FISTA} with an unlimited number of pixels.}\label{fig: haar convergence}
 
@@
 		\includegraphics[width=.85\textwidth]{STORM_data}
-	\caption{Example of images from STORM dataset.}\label{fig: STORM data}
+		\caption{Example images from STORM dataset.}\label{fig: STORM data}
 	\end{figure}
@@
 	Our final application is a super-resolution/de-blurring inverse problem from biological microscopy.
-In mathematical terms, the observed data is a large number of sparse images which are corrupted by blurring and a large amount of noise, examples are seen in \Cref{fig: STORM data}.
-The task is to compute the centres of the spikes of signal in each image and then re-combine into a single super-resolved image, as in \Cref{fig: STORM results}.
+In mathematical terms, the observed data is a large number of sparse images which are corrupted by blurring and a large amount of noise, examples are seen in Figure~\ref{fig: STORM data}.
+The task is to compute the centres of the spikes of signal in each image and then re-combine into a single super-resolved image, as in Figure~\ref{fig: STORM results}.
 This technique is referred to as \emph{Single Molecule Localisation Microscopy} (SMLM), of which we consider the specific example of \emph{Stochastic Optical Reconstruction Microscopy} (STORM).
-Readers are directed to works such as by \citet{Sage2015,Sage2019,Schermelleh2019} for further details.
-The Lasso formulation has previously been shown to be effective in the context of STORM, see for instance \citet{Huang2017,Denoyelle2019}.
+Readers are directed to the references \cite{Sage2015,Sage2019,Schermelleh2019} for further details.
+The Lasso formulation has previously been shown to be effective in the context of STORM \cite{Huang2017,Denoyelle2019}.
 
@@
 	\begin{equation}
-	(\A\varf0)_{i} = (2\pi\sigma^2)^{-1}\int_{[0,6.4]^2} \exp\left(-\frac{1}{2\sigma^2}\left|\vvarx0- \Delta\begin{pmatrix}i_1+\tfrac12 & i_2+\tfrac12\end{pmatrix}^\top \right|^2\right)\varf0(\vvarx0)\,d\vvarx0, \qquad \sigma=\SI{0.2}{\micro\meter},\ \Delta=\SI{0.1}{\micro\meter}
-\end{equation}
-for $i_1,i_2 = 1,2,\ldots,64$ and $\spcf0=\C M([\SI{0}{\micro\meter},\SI{6.4}{\micro\meter}]^2)$.
-3020 frames are provided, examples of which are shown in \Cref{fig: STORM data}.
+		(\A\varf0)_{i} = (2\pi\sigma^2)^{-1}\int_{[0,6.4]^2} \exp\left(-\frac{1}{2\sigma^2}\left|\vvarx0- \Delta\begin{pmatrix}i_1+\tfrac12 & i_2+\tfrac12\end{pmatrix}^\top \right|^2\right)\varf0(\vvarx0)\,d\vvarx0, \qquad \sigma=0.2,\ \Delta=0.1
+	\end{equation}
+	for $i_1,i_2 = 1,2,\ldots,64$ and $\spcf0=\C M([0,6.4]^2)$ with lengths in $\SI{}{\micro\meter}$.
+3020 frames are provided, examples of which are shown in Figure~\ref{fig: STORM data}.
 To process this dataset, image intensities were normalised to $[0,1]$ then a constant was subtracted to approximate 0-mean noise.
@@
 
-Finally, all the reconstructions were summed and the result shown in \Cref{fig: STORM results}.
+	Finally, all the reconstructions were summed and the result shown in Figure~\ref{fig: STORM results}.
 The adaptive scheme used fewer than $10^4$ pixels per frame, a fixed discretisation with equivalent resolution of \SI{1.3}{\nano\meter} would have required more than $3\cdot10^6$ per frame.
-Lasso is compared with ThunderSTORM \citep{Ovesny2014}, a popular ImageJ plugin \citep{Schindelin2012} which finds the location of signal using Fourier filtering.
-The performance of ThunderSTORM was rated very highly in the initial competition by \citet{Sage2015}.
+Lasso is compared with ThunderSTORM \cite{Ovesny2014}, a popular ImageJ plugin \cite{Schindelin2012} which finds the location of signal using Fourier filtering.
+The performance of ThunderSTORM was rated very highly in the initial SMLM challenge \cite{Sage2015}.
 Both methods compared here demonstrate the key structures of the reconstruction, however, both are sensitive to tuning parameters.
@@
 
-\Cref{fig: STORM convergence} shows slightly faster convergence than $n^{-\sfrac23}$ predicted by \eqref{eq: Lasso resolution rate} in dimension $d=2$.
-In this example we also implement the suggestion of \Cref{sec: support detection} to remove pixels outside of the support of $\varf0^*$.
+	Figure~\ref{fig: STORM convergence} shows slightly faster convergence than $n^{-\sfrac23}$ predicted by \eqref{eq: Lasso resolution rate} in dimension $d=2$.
+In this example we also implement the suggestion of Section~\ref{sec: support detection} to remove pixels outside of the support of $\varf0^*$.
 From \eqref{eq: support equation}, any pixel $\domain_i^n$ satisfying
 	\begin{equation}
-	\vars2_0\norm{\Pi_n\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq 1-\frac{\op{threshold}}{\mu}
+		\vars2_0\norm{\tens{\Pi}_n\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq 1-\frac{\op{threshold}}{\mu}
 	\end{equation}
 	guarantees that $\domain_i^n\cap\op{supp}(\varf0^*) = \emptyset$.
-This value is plotted in the first panel of \Cref{fig: STORM convergence}.
+This value is plotted in the first panel of Figure~\ref{fig: STORM convergence}.
 Once this threshold becomes less than 1, we can start reducing the number of pixels instead of just continual refinement, as seen in the right-hand panel after around 30 iterations.
 
-\begin{figure}[H]\centering
+	\begin{figure}\centering
 		\includegraphics[width=.82\textwidth]{lasso2_convergence}
@@
 Pixel width is scaled $[0,1]$ rather than $[0,\SI{6.4}{\micro\meter}]$.}\label{fig: STORM convergence}
-\end{figure}
-\begin{figure}\centering
-	\includegraphics[width=.77\textwidth]{STORM_recon}
+
+		\vspace*{\floatsep}
+
+		\includegraphics[width=.73\textwidth]{STORM_recon}
 		\caption{Processed results of the STORM dataset.
-Top left: Lasso optimisation with \Cref{alg: refining FISTA}.
+Top left: Lasso optimisation with Algorithm~\ref{alg: refining FISTA}.
 Top right: Comparison with ThunderSTORM plugin.
@@
 Other variants of FISTA, such as the `greedy' implementation used here or the traditional Forward-Backward algorithm, should also be receptive to the analysis performed here.
-Furthermore, it would also interesting to attempt to replicate this refinement argument to extend the primal-dual algorithm proposed by \citet{Chambolle2011} or the Douglas-Rachford algorithm proposed by \citet{Douglas1956}.
-
-\bibliographystyle{apalike}\bibliography{references} % alpha is also a decent style
+Furthermore, it would also interesting to attempt to replicate this refinement argument to extend the primal-dual algorithm \cite{Chambolle2011} or the Douglas-Rachford algorithm \cite{Douglas1956}.
+
+	\begin{acknowledgements}
+		R.T.
+acknowledges funding from EPSRC grant EP/L016516/1 for the Cambridge Centre for Analysis, and the ANR CIPRESSI project grant ANR-19-CE48-0017-01 of the French Agence Nationale de la Recherche.
+Most of this work was done while A.C.
+was still in CMAP, CNRS and Ecole Polytechnique, Institut Polytechnique de Paris, Palaiseau, France.
+	\end{acknowledgements}
+	\begingroup
+	\bibliography{references}
+	\endgroup
 	\appendix
 	\section{Proofs for FISTA convergence}\label{app: FISTA convergence}
-This section contains all of the statements and proofs of the results contained in \Cref{sec: FISTA convergence}.
+	This section contains all of the statements and proofs of the results contained in Section~\ref{sec: FISTA convergence}.
+\edit{}{Recall that the subspaces $\spcf0^n\subset\F H$ satisfy \eqref{eq: refining subspace definition}.}
 
@@
 
-\begin{theorem}[\Cref{thm: one step FISTA}]\label{app:thm: one step FISTA}
+	\begin{theorem}[Lemma~\ref{thm: one step FISTA}]\label{app:thm: one step FISTA}
 		\Paste{thm: one step FISTA}
 		\begin{equation}
-		\vart1_{n}^2(\Func0(\varf0_{n}) - \Func0(\varf2_n)) - (\vart1_{n}^2-\vart1_{n})(\Func0(\varf0_{n-1})-\Func0(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.\label{app:eq: one-step FISTA}
+			\Paste{thm:eq: one step FISTA}
+			\label{app:eq: one-step FISTA}
 		\end{equation}
@@
 	\begin{proof}
-	Modifying \cite[Theorem 2]{Chambolle2015}, for $n\geq1$ we apply \Cref{thm: descent lemma} with $\bar{\varf0} = \bar{\varf0}_{n-1}$ and $\varf2 = (1-\frac{1}{\vart1_{n}})\varf0_{n-1} + \frac{1}{\vart1_{n}}\varf2_n$.
+		Modifying \cite[\edit{Theorem 2}{Thm 3.2}]{Chambolle2015}, for $n\geq1$ we apply Lemma~\ref{thm: descent lemma} with $\bar{\varf0} = \bar{\varf0}_{n-1}$ and $\varf2 = (1-\frac{1}{t_{n}})\varf0_{n-1} + \frac{1}{t_{n}}\varf2_n\edit{}{\in\spcf0^n}$.
 This gives
 		\begin{equation}
-		\Func0(\varf0_{n}) + \tfrac12\norm{\tfrac{1}{\vart1_{n}}\varf1_{n}-\tfrac{1}{\vart1_{n}}\varf2_n}^2 \leq \Func0\left((1-\tfrac{1}{\vart1_{n}})\varf0_{n-1}+\tfrac{1}{\vart1_{n}}\varf2_n\right) + \tfrac12\norm{\tfrac{1}{\vart1_{n}}\varf1_{n-1}-\tfrac{1}{\vart1_{n}}\varf2_n}^2.
-	\end{equation}
-	By the convexity of $\Func0$, this reduces to
-	\begin{align}
-		\Func0(\varf0_{n}) - \Func0(\varf2_n) - (1-\tfrac{1}{\vart1_{n}})[\Func0(\varf0_{n-1})-\Func0(\varf2_n)] &\leq \tfrac1{2\vart1_{n}^2}\norm{\varf1_{n-1}-\varf2_n}^2 - \tfrac1{2\vart1_{n}^2}\norm{\varf1_{n}-\varf2_n}^2
-		\\ &= \tfrac1{2\vart1_{n}^2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \tfrac1{\vart1_{n}^2}\IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.
-	\end{align}
-\end{proof}
-
-\begin{theorem}[\Cref{thm: mini FISTA convergence}]\label{app:thm: mini FISTA convergence}
+			\op{E}(\varf0_{n}) + \tfrac12\norm{\tfrac{1}{t_{n}}\varf1_{n}-\tfrac{1}{t_{n}}\varf2_n}^2 \leq \op{E}\left((1-\tfrac{1}{t_{n}})\varf0_{n-1}+\tfrac{1}{t_{n}}\varf2_n\right) + \tfrac12\norm{\tfrac{1}{t_{n}}\varf1_{n-1}-\tfrac{1}{t_{n}}\varf2_n}^2.
+		\end{equation}
+		By the convexity of $\op{E}$, this reduces to
+		\begin{equation}
+			\op{E}(\varf0_{n}) - \op{E}(\varf2_n) - (1-\tfrac{1}{t_{n}})[\op{E}(\varf0_{n-1})-\op{E}(\varf2_n)] \leq \tfrac1{2t_{n}^2}\norm{\varf1_{n-1}-\varf2_n}^2 - \tfrac1{2t_{n}^2}\norm{\varf1_{n}-\varf2_n}^2 = \tfrac1{2t_{n}^2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \tfrac1{t_{n}^2}\IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.
+		\end{equation}
+		\edit{}{Multiplying through by $t_n^2$ gives the desired inequality.}
+		\qed\end{proof}
+
+	\begin{theorem}[Theorem~\ref{thm: mini FISTA convergence}]\label{app:thm: mini FISTA convergence}
 		\Paste{thm: mini FISTA convergence}
-	\begin{multline}\label{app:eq: FISTA inequality}
-		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \Func0_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
-		\\ + \sum^N_{n=1} \vart1_n\Func0_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
-	\end{multline}
+		\begin{equation}\label{app:eq: FISTA inequality}
+			\Paste{thm:eq: mini FISTA convergence}
+		\end{equation}
 	\end{theorem}
 	\begin{proof}
-	\Cref{app:thm: mini FISTA convergence} is just a summation of \eqref{app:eq: one-step FISTA} over all $n=1,\ldots,N$.
-To see this: first add and subtract $\Func0(\varf0^*)$ to each term on the left-hand side to convert $\Func0$ to $\Func0_0$, then move $\Func0_0(\varf2_n)$ to the right-hand side.
+		Theorem~\ref{app:thm: mini FISTA convergence} is just a summation of \eqref{app:eq: one-step FISTA} over all $n=1,\ldots,N$.
+To see this: first add and subtract $\edit{\op{E}(\varf0^*)}{\Emin}$ to each term on the left-hand side to convert $\op{E}$ to $\op{E}_0$, then move $\op{E}_0(\varf2_n)$ to the right-hand side.
 Now \eqref{app:eq: one-step FISTA} becomes
 		\begin{equation}
-		\vart1_n^2\Func0_0(\varf0_n) - (\vart1_n^2-\vart1_n)\Func0_0(\varf0_{n-1}) \leq \vart1_n\Func0_0(\varf2_n) + \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_n}^2\right] + \IP{\varf1_n-\varf1_{n-1}}{\varf2_n}.
+			t_n^2\op{E}_0(\varf0_n) - (t_n^2-t_n)\op{E}_0(\varf0_{n-1}) \leq t_n\op{E}_0(\varf2_n) + \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_n}^2\right] + \IP{\varf1_n-\varf1_{n-1}}{\varf2_n}. 
 		\end{equation}
@@
 		\begin{equation}
-		\vart1_N^2\Func0_0(\varf0_N) + \sum_{n=1}^{N-1}(\underbrace{\vart1_n^2-\vart1_{n+1}^2+\vart1_{n+1}}_{=\rho_n})\Func0_0(\varf0_n) \leq \frac{\norm{\varf1_0}^2-\norm{\varf1_N}^2}{2} + \sum_{n=1}^N \vart1_n\Func0_0(\varf2_n)+\IP{\varf1_n-\varf1_{n-1}}{\varf2_n}.
+			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}(\underbrace{t_n^2-t_{n+1}^2+t_{n+1}}_{=\rho_n})\op{E}_0(\varf0_n) \leq \frac{\norm{\varf1_0}^2-\norm{\varf1_N}^2}{2} + \sum_{n=1}^N t_n\op{E}_0(\varf2_n)+\IP{\varf1_n-\varf1_{n-1}}{\varf2_n}.
 		\end{equation}
@@
 		\end{equation}
-	Noting that $\varf1_0=\varf0_0$, the previous two equations combine to prove the statement of \Cref{app:thm: mini FISTA convergence}.
-\end{proof}
-
-\noindent The following lemma is used to produce a sharper estimate on sequences $\vart1_n$.
+		Noting that $\varf1_0=\varf0_0$, the previous two equations combine to prove the statement of Theorem~\ref{app:thm: mini FISTA convergence}.
+		\qed\end{proof}
+
+	The following lemma is used to produce a sharper estimate on sequences $t_n$.
 	\begin{lemma}\label{app: tn upper bound}
-	If $\rho_n=\vart1_{n}^2-\vart1_{n+1}^2+\vart1_{n+1}\geq0$, $\vart1_n\geq 1$ for all $n\in\F N$ then $\vart1_n\leq n-1 +\vart1_1$.
+		If $\rho_n=t_{n}^2-t_{n+1}^2+t_{n+1}\geq0$, $t_n\geq 1$ for all $n\in\F N$ then $t_n\leq n-1 +t_1$.
 	\end{lemma}
@@
 		\begin{equation}
-		\vart1_n^2 -\vart1_n \leq \vart1_{n-1}^2 \leq (n-2+\vart1_1)^2 = (n-1+\vart1_1)^2 -2(n-1+\vart1_1) + 1.
-	\end{equation}
-	Assuming the contradiction, if $\vart1_n> n-1+\vart1_1$ then the above equation simplifies to $n-1+\vart1_1 < 1$. However, $\vart1_1\geq 1$ implying that $n<1$ which completes the contradiction.
-\end{proof}
-
-\begin{lemma}[\Cref{thm: mini exponential FISTA convergence}]\label{app:thm: mini exponential FISTA convergence}
+			t_n^2 -t_n \leq t_{n-1}^2 \leq (n-2+t_1)^2 = (n-1+t_1)^2 -2(n-1+t_1) + 1.
+		\end{equation}
+		Assuming the contradiction, if $t_n> n-1+t_1$ then the above equation simplifies to $n-1+t_1 < 1$. However, $t_1\geq 1$ implying that $n<1$ which completes the contradiction.
+		\qed\end{proof}
+
+	\begin{lemma}[Lemma~\ref{thm: mini exponential FISTA convergence}]\label{app:thm: mini exponential FISTA convergence}
 		\Paste{thm: mini exponential FISTA convergence}
+		\begin{equation}
+			\Paste{thm:eq: mini exponential FISTA convergence}
+		\end{equation}
+		\Paste{thm:end: mini exponential FISTA convergence}
 	\end{lemma}
@@
 		This is just a telescoping of the right-hand side of \eqref{app:eq: FISTA inequality} with the introduction of $n_k$ and simplification $\varf2_n = \tilde{\varf2}_k$,
-	\begin{multline}
-		\tfrac12\norm{\varf2_N}^2 + \sum^N_{n=1} \vart1_n\Func0_0(\Pi_n\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n} = \tfrac12\norm{\tilde{\varf2}_K}^2 + \sum_{n=n_K}^N\vart1_n\Func0_0(\tilde{\varf2}_K)
-		\\+ \sum_{k=1}^K\sum_{n=n_{k-1}}^{n_k-1}\vart1_n\Func0_0(\tilde{\varf2}_{k-1}) 
+		\begin{equation}
+			\tfrac12\norm{\varf2_N}^2 + \sum^N_{n=1} t_n\op{E}_0(\tens{\Pi}_n\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n} = \tfrac12\norm{\tilde{\varf2}_K}^2 + \sum_{n=n_K}^Nt_n\op{E}_0(\tilde{\varf2}_K)
+			+ \sum_{k=1}^K\sum_{n=n_{k-1}}^{n_k-1}t_n\op{E}_0(\tilde{\varf2}_{k-1}) 
 			+ \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}.
-	\end{multline}
-	By \Cref{app: tn upper bound}, $\vart1_n\leq n$ so we can further simplify
-	$$\sum_{n=\vars3}^{\vars4-1}\vart1_n \leq \sum_{n=\vars3}^{\vars4-1}n = (\vars4-\vars3)\frac{\vars4-1+\vars3}{2} \leq \frac{\vars4^2-\vars3^2}{2}$$
+		\end{equation}
+		By Lemma~\ref{app: tn upper bound}, $t_n\leq n$ so we can further simplify
+		$$\sum_{n=\vars3}^{\vars4-1}t_n \leq \sum_{n=\vars3}^{\vars4-1}n = (\vars4-\vars3)\frac{\vars4-1+\vars3}{2} \leq \frac{\vars4^2-\vars3^2}{2}$$
 		to get the required bound.
-\end{proof}
+		\qed\end{proof}
 
 	\subsection{Proof for Step 4}
-\begin{lemma}[\Cref{thm: sufficiently fast}]\label{app:thm: sufficiently fast}
+	\begin{lemma}[Lemma~\ref{thm: sufficiently fast}]\label{app:thm: sufficiently fast}
 		\Paste{thm: sufficiently fast}
@@
 	\begin{proof}
-	Starting from \Cref{app:thm: mini exponential FISTA convergence} we get
-	\begin{align}
-		\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\Func0_0(\tilde{\varf2}_K) + \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\Func0_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}
-		\\& \leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2}{2}\Func0_0(\tilde{\varf2}_K) \notag
-		\\&\hspace{100pt}+\sum_{k=1}^K \frac{n_k^2}{2}\Func0_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}+\tilde{\varf2}_{k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}.
+		Starting from Lemma~\ref{app:thm: mini exponential FISTA convergence} we have
+		\begin{align}
+			t_N^2\op{E}_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\op{E}_0(\tilde{\varf2}_K) \notag
+			\\&\hspace{70pt}+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\op{E}_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}
+			\\& \leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2}{2}\op{E}_0(\tilde{\varf2}_K) \notag
+			\\&\hspace{40pt}+\sum_{k=1}^K \frac{n_k^2}{2}\op{E}_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}+\tilde{\varf2}_{k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}.
 		\end{align}
@@
 			\begin{align}
-			\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim \vars3_{\Varf0}^{2K} + (N+1)^2\vars3_{\Func0}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\Func0}^{-k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + \vars3_{\Varf0}^{2k}
+				t_N^2\op{E}_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim \vars3_{\Varf0}^{2K} + (N+1)^2\vars3_{\op{E}}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\op{E}}^{-k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + \vars3_{\Varf0}^{2k}
 				\\&\leq C_1\left[\vars3_{\Varf0}^{2K+2} + \sum_{k=1}^{K}\vars3_{\Varf0}^{2k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\right]
@@
 			\begin{align}
-			\vart1_N^2\Func0_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim 1 + (N+1)^2\vars3_{\Func0}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\Func0}^{-k} + (\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + 1)b_k
+				t_N^2\op{E}_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim 1 + (N+1)^2\vars3_{\op{E}}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\op{E}}^{-k} + (\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + 1)b_k
 				\\&\leq C_1\left[1 + \sum_{k=1}^{K}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\vars4_k\right]
@@
 		\begin{equation}
-			\vart1_N^2\Func0_0(\varf0_N) \leq \frac{C_2^2}{2}\vars3_{\Varf0}^{2K}
+			t_N^2\op{E}_0(\varf0_N) \leq \frac{C_2^2}{2}\vars3_{\Varf0}^{2K}
 		\end{equation}
 		for all $N<n_K-1$.
-\end{proof}
+		\qed\end{proof}
 
 	\subsection{Proof for Step 5}
-\begin{lemma}[\Cref{thm: sufficiently slow}]\label{app:thm: sufficiently slow}
+	\begin{lemma}[Lemma~\ref{thm: sufficiently slow}]\label{app:thm: sufficiently slow}
 		\Paste{thm: sufficiently slow}
@@
 		\begin{equation}
-		\log N^2 \geq \log C + K\left(\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2\right)
+			\log N^2 \geq \log C + K\left(\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2\right)
 		\end{equation}
@@
 			\vars3_{\Varf0}^{2K} = \exp(K\log \vars3_{\Varf0}^2)
-		\leq \exp\left(\log N^2\frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2} - \frac{\log C\log \vars3_{\Varf0}^2}{\log \vars3_{\Func0} + \log \vars3_{\Varf0}^2}\right)
+			\leq \exp\left(\log N^2\frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2} - \frac{\log C\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2}\right)
 		\end{equation}
 		as required.
-\end{proof}
+		\qed\end{proof}
 
 	\subsection{Proofs for Step 6}
-\begin{theorem}[\Cref{thm: stronger exponential FISTA convergence}]\label{app:thm: stronger exponential FISTA convergence}
+	\begin{theorem}[Theorem~\ref{thm: stronger exponential FISTA convergence}]\label{app:thm: stronger exponential FISTA convergence}
 		\Paste{thm: stronger exponential FISTA convergence}
@@
 	\begin{proof}
-	To apply \Cref{app:thm: sufficiently fast}, we need
-	\begin{equation}
-		n_k^2\lesssim \splitln{(\vars3_{\Func0}\vars3_{\Varf0}^2)^k}{\vars3_{\Varf0}>1}{k^{-2}\vars3_{\Func0}^k}{\vars3_{\Varf0}=1}, \qquad \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^{k}, \qquad \text{ and } \Func0_0(\tilde{\varf2}_k)\lesssim \vars3_{\Func0}^{-k}
+		To apply Lemma~\ref{app:thm: sufficiently fast}, we need
+		\begin{equation}
+			n_k^2\lesssim \splitln{(\vars3_{\op{E}}\vars3_{\Varf0}^2)^k}{\vars3_{\Varf0}>1}{k^{-2}\vars3_{\op{E}}^k}{\vars3_{\Varf0}=1}, \qquad \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^{k}, \qquad \text{ and } \op{E}_0(\tilde{\varf2}_k)\lesssim \vars3_{\op{E}}^{-k}
 		\end{equation}
@@
 		\begin{equation}
-		\Func0_0(\tilde{\varf2}_k) = \min_{\varf0\in\spcf0^{n_k}}\Func0_0(\varf0) \leq\Func0_0(\varf0_{n_k-1}) \lesssim \vars3_{\Func0}^{-k}.
-	\end{equation}
-	Therefore, the result of \Cref{app:thm: sufficiently fast} gives
-	\begin{equation}
-		\Func0_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{\vart1_N^2} \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}.
+			\op{E}_0(\tilde{\varf2}_k) = \min_{\varf0\in\spcf0^{n_k}}\op{E}_0(\varf0) \leq\op{E}_0(\varf0_{n_k-1}) \lesssim \vars3_{\op{E}}^{-k}.
+		\end{equation}
+		Therefore, the result of Lemma~\ref{app:thm: sufficiently fast} gives
+		\begin{equation}
+			\op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{t_N^2} \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}.
 		\end{equation}
 		In the case $\vars3_{\Varf0}=1$, this is already the optimal rate and therefore sharp.
-If this were sharp for general $\vars3_{\Varf0}$ and $\Func0$, then we gain nothing by refining early (increasing $K$ for fixed $N$) however, we can at least guarantee that refining early does not lose the optimal rate.
-
-	If we fix $N^2\lesssim (\vars3_{\Func0}\vars3_{\Varf0}^2)^k$, then
-	\begin{equation}
-		\min_{n\leq N} \Func0_0(\varf0_n)\lesssim \splitln{\vars3_{\Func0}^{-k}}{N>n_k}{ \sfrac{\vars3_{\Varf0}^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_{\Varf0}^{2k},\vars3_{\Varf0}^{2k}) \lesssim N^{-2(1-\kappa)}
+If this were sharp for general $\vars3_{\Varf0}$ and $\op{E}$, then we gain nothing by refining early (increasing $K$ for fixed $N$) however, we can at least guarantee that refining early does not lose the optimal rate.
+
+		If we fix $N^2\lesssim (\vars3_{\op{E}}\vars3_{\Varf0}^2)^k$, then
+		\begin{equation}
+			\min_{n\leq N} \op{E}_0(\varf0_n)\lesssim \splitln{\vars3_{\op{E}}^{-k}}{N>n_k}{ \frac{\vars3_{\Varf0}^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_{\Varf0}^{2k},\vars3_{\Varf0}^{2k}) \lesssim N^{-2(1-\kappa)}
 		\end{equation}
 		as required.
-\end{proof}
-
-\begin{lemma}[\Cref{thm: practical refinement criteria}]\label{app:thm: practical refinement criteria}
+		\qed\end{proof}
+
+	\begin{lemma}[Lemma~\ref{thm: practical refinement criteria}]\label{app:thm: practical refinement criteria}
 		\Paste{thm: practical refinement criteria}
@@
 	\begin{proof}
-	The proof is simply to justify that the conditions of \Cref{app:thm: stronger exponential FISTA convergence} are met for all refinement criteria described here.
+		The proof is simply to justify that the conditions of Theorem~\ref{app:thm: stronger exponential FISTA convergence} are met for all refinement criteria described here.
 $\norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k$ is enforced at every step and condition (2) guarantees the back-stop condition on $n_k$.
 
-	To complete the requirements of \Cref{app:thm: stronger exponential FISTA convergence}, we first need to show inductively that $\Func0_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\Func0}^{-k}$, then it follows that $\Func0_0(\varf0_{n_k-1})\leq C\vars3_{\Func0}^{-k}$.
-To be explicit, when $\Func0$ has bounded sublevel sets, assume that the bound for $\{\varf0\in\F H\st \Func0(\varf0)\leq \Func0(\varf0_0)\}$ is $R>0$.
-
-	For (2) and (5) the decay of $\Func0_0(\tilde{\varf2}_{k-1})$ is already assumed but otherwise we need to perform the formal induction.
-Assume $\Func0_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\Func0}^{1-k}$, then for each remaining adaptive criterion:
+		To complete the requirements of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, we first need to show inductively that $\op{E}_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\op{E}}^{-k}$, then it follows that $\op{E}_0(\varf0_{n_k-1})\leq C\vars3_{\op{E}}^{-k}$.
+To be explicit, when $\op{E}$ has bounded sublevel sets, assume that the bound for $\{\varf0\in\F H\st \op{E}(\varf0)\leq \op{E}(\varf0_0)\}$ is $R>0$.
+
+		For (2) and (5) the decay of $\op{E}_0(\tilde{\varf2}_{k-1})$ is already assumed but otherwise we need to perform the formal induction.
+Assume $\op{E}_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\op{E}}^{1-k}$, then for each remaining adaptive criterion:
 		\begin{itemize}
-		\item[(1)] $\Func0_0(\tilde{\varf2}_k)\leq \Func0_0(\varf0_{k})\leq\vars1 \vars3_{\Func0}^{-k}$ by definition, the induction holds if $C\geq \vars1$.
-		\item[(3)] $\Func0_0(\tilde{\varf2}_k)\leq \Func0_0(\varf0_{k})\leq\frac{\vars1}{1-\vars1}\Func0_0(\tilde{\varf2}_{k-1})$, the induction holds if $\vars1\leq \frac{1}{1+\vars3_{\Func0}}$.
-		\item[(4)] $\Func0_0(\tilde{\varf2}_k)\leq \Func0_0(\varf0_{k}) \leq \IP{\partial\Func0(\varf0_{k})}{\varf0_{n_k-1}-\varf0^*} \leq 2R\vars1\vars3_{\Func0}^{-k}$, the induction holds for $C\geq 2R\vars1$.
+			\item[(1)] $\op{E}_0(\tilde{\varf2}_k)\leq \op{E}_0(\varf0_{k})\leq\vars1 \vars3_{\op{E}}^{-k}$ by definition, the induction holds if $C\geq \vars1$.
+			\item[(3)] $\op{E}_0(\tilde{\varf2}_k)\leq \op{E}_0(\varf0_{k})\leq\frac{\vars1}{1-\vars1}\op{E}_0(\tilde{\varf2}_{k-1})$, the induction holds if $\vars1\leq \frac{1}{1+\vars3_{\op{E}}}$.
+			\item[(4)] $\op{E}_0(\tilde{\varf2}_k)\leq \op{E}_0(\varf0_{k}) \leq \IP{\edit{\partial\op{E}(\varf0_{k})}{\varf1}}{\varf0_{n_k-1}-\varf0^*} \leq 2R\vars1\vars3_{\op{E}}^{-k}$\edit{}{ for each $\varf1\in\partial\op{E}(\varf0_{k})$}, the induction holds for $C\geq 2R\vars1$.
 		\end{itemize}
 		In each case, with $C$ sufficiently large, the induction holds.
-Now we can return to the precise condition of \Cref{app:thm: stronger exponential FISTA convergence}, $\Func0_0(\varf0_{n_k-1}) \leq C'\vars3_{\Func0}^{-k}$.
+Now we can return to the precise condition of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, $\op{E}_0(\varf0_{n_k-1}) \leq C'\vars3_{\op{E}}^{-k}$.
 Assume true for $k-1$.
@@
 		\begin{itemize}
-		\item[(1)] $\Func0_0(\varf0_{k})\leq\vars1 \vars3_{\Func0}^{-k}$ is by definition.
-		\item[(2)] $\Func0_0(\varf0_{k})\leq\vars1 \vars3_{\Func0}^{-k} + \Func0_0(\tilde{\varf2}_{k-1})$ requires $C'\geq \vars1+\vars3_{\Func0}C$.
-		\item[(3)] $\Func0_0(\varf0_{k})\leq\frac{\vars1}{1-\vars1}\Func0_0(\tilde{\varf2}_{k-1})$ requires $C'\geq \frac{\vars1}{1-\vars1}C$.
-		\item[(4)] $\Func0_0(\varf0_{k}) \leq 2R\vars1\vars3_{\Func0}^{-k}$, the induction holds for large $C'$.
-		\item[(5)] $\Func0_0(\varf0_{k})\leq 2R\vars1\vars3_{\Func0}^{-k} + \Func0_0(\tilde{\varf2}_{k-1})$, the induction holds for large $C'\geq 2R\vars1+C$.
+			\item[(1)] $\op{E}_0(\varf0_{k})\leq\vars1 \vars3_{\op{E}}^{-k}$ is by definition.
+			\item[(2)] $\op{E}_0(\varf0_{k})\leq\vars1 \vars3_{\op{E}}^{-k} + \op{E}_0(\tilde{\varf2}_{k-1})$ requires $C'\geq \vars1+\vars3_{\op{E}}C$.
+			\item[(3)] $\op{E}_0(\varf0_{k})\leq\frac{\vars1}{1-\vars1}\op{E}_0(\tilde{\varf2}_{k-1})$ requires $C'\geq \frac{\vars1}{1-\vars1}C$.
+			\item[(4)] $\op{E}_0(\varf0_{k}) \leq 2R\vars1\vars3_{\op{E}}^{-k}$, the induction holds for large $C'$.
+			\item[(5)] $\op{E}_0(\varf0_{k})\leq 2R\vars1\vars3_{\op{E}}^{-k} + \op{E}_0(\tilde{\varf2}_{k-1})$, the induction holds for large $C'\geq 2R\vars1+C$.
 		\end{itemize}
-	This completes the requirements of \Cref{app:thm: stronger exponential FISTA convergence}, therefore also this proof.
-\end{proof}
-
-\section{Proof of \texorpdfstring{\Cref{thm: generic a_U and a_E}}{rates for general finite element spaces}}\label{app: generic a_U and a_E}
-The proof of \Cref{thm: generic a_U and a_E} is the result of the following three lemmas.
-The first, \Cref{app:thm: generic a_U bound}, is a general quantification of the equivalence between $L^q$ and $L^2$ norms on finite dimensional sub-spaces.
+		This completes the requirements of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, therefore also this proof.
+		\qed\end{proof}
+
+	\section{Proof of \texorpdfstring{Theorem~\ref{thm: generic a_U and a_E}}{rates for general finite element spaces}}\label{app: generic a_U and a_E}
+	The proof of Theorem~\ref{thm: generic a_U and a_E} is the result of the following three lemmas.
+The first, Lemma~\ref{app:thm: generic a_U bound}, is a general quantification of the equivalence between $L^q$ and $L^2$ norms on finite dimensional sub-spaces.
 A special case occurs when $q=1$ because the dual norm is a supremum rather than an integral.
-In \Cref{app:thm: specific a_U bound}, this locality is exploited by finite element spaces, which we assumed had a basis with local support.
-\Cref{app:thm: generic a_E bound} then performs the computations for the $\vars3_{\Func0}$ constant depending on the smoothness properties of $\Func0$.
+In Lemma~\ref{app:thm: specific a_U bound}, this locality is exploited by finite element spaces, which we assumed had a basis with local support.
+Lemma~\ref{app:thm: generic a_E bound} then performs the computations for the $\vars3_{\op{E}}$ constant depending on the smoothness properties of $\op{E}$.
 
@@
 		Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
-Let $\tilde{\spcf0}\subset \spcf0\cap\F H$ be a finite dimensional subspace with orthonormal basis $\{e_j\st j=1,\ldots,\op{dim}(\tilde{\spcf0})\}\subset\tilde{\spcf0}$ and orthogonal projection $\Pi\colon\F H\to\tilde{\spcf0}$.
-If these conditions hold, then:
+Let $\tilde{\spcf0}\subset \edit{\spcf0\cap}{}\F H$ be a finite dimensional subspace with orthonormal basis $\{e_j\st j=1,\ldots,\op{dim}(\tilde{\spcf0})\}\subset\tilde{\spcf0}$ and orthogonal projection $\tens{\Pi}\colon\F H\to\tilde{\spcf0}$.
+If these conditions hold:
 		\begin{itemize}
-		\item if $q\geq 2$, then $$\norm{\Pi\varf2} \lesssim \Norm{\varf2}, $$
+			\item if $q\geq 2$, then $$\norm{\tens{\Pi}\varf2} \lesssim \Norm{\varf2}, $$
 			\item otherwise, if $e_j\in \spcf0^*$, then
 			\begin{equation}
-			\norm{\Pi\varf2} \leq \sqrt{\op{dim}(\tilde{\spcf0})}\max_j\Norm{e_j}_*\Norm{\varf2},
+				\norm{\tens{\Pi}\varf2} \leq \sqrt{\op{dim}(\tilde{\spcf0})}\max_{j\leq \op{dim}(\tilde{\spcf0})}\Norm{e_j}_*\Norm{\varf2},
 			\end{equation}
@@
 			\begin{equation}
-			\norm{\Pi\varf2} \lesssim \sqrt C\max_j\norm{e_j}_{L^\infty}\Norm{\varf2}
+				\norm{\tens{\Pi}\varf2} \lesssim \sqrt C\max_{j\leq\op{dim}(\tilde{\spcf0})}\norm{e_j}_{\infty}\Norm{\varf2}
 			\end{equation}
@@
 		\begin{equation}
-		\norm{\Pi\varf2}^2 \leq \norm{\varf2}^2 = \norm{\varf2}_2^2 = \norm{\varf2^2}_1 \lesssim \norm{\varf2}_q^2 \lesssim \Norm{\varf2}^2.
+			\norm{\tens{\Pi}\varf2}^2 \leq \norm{\varf2}^2 = \norm{\varf2}_2^2 = \norm{\varf2^2}_1 \lesssim \norm{\varf2}_q^2 \lesssim \Norm{\varf2}^2.
 		\end{equation}
@@
 		\begin{equation}
-		\norm{\Pi\varf2} = \frac{\IP{\Pi\varf2}{\Pi\varf2}}{\norm{\Pi\varf2}} = \frac{\IP{\Pi\varf2}{\varf2}}{\norm{\Pi\varf2}} \leq \frac{\Norm{\Pi\varf2}_*}{\norm{\Pi\varf2}}\Norm{\varf2},
-	\end{equation}
-	therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\tilde{\spcf0}$. Switching to the given basis, for $\varf0 = \sum_j \varx3_je_j$ we have
+			\norm{\tens{\Pi}\varf2} = \frac{\IP{\tens{\Pi}\varf2}{\tens{\Pi}\varf2}}{\norm{\tens{\Pi}\varf2}} = \frac{\IP{\tens{\Pi}\varf2}{\varf2}}{\norm{\tens{\Pi}\varf2}} \leq \frac{\Norm{\tens{\Pi}\varf2}_*}{\norm{\tens{\Pi}\varf2}}\Norm{\varf2},
+		\end{equation}
+		therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\tilde{\spcf0}$.
+Switching to the given basis, for $\varf0 = \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} \varx3_je_j$ we have
 		\begin{align}
 			\norm{\varf0}^2 &= \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} \varx3_j^2 = \norm{\vvarx3}_{\ell^2}^2,
-		\\\Norm{\varf0}_*&\leq \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} |\varx3_j|\Norm{e_j}_* \leq \max_j\Norm{e_j}_*\norm{\vvarx3}_{\ell^1},
-		\\\implies \frac{\Norm{\varf0}_*}{\norm{\varf0}} &\leq \max_j\Norm{e_j}_*\frac{\norm{\vvarx3}_{\ell^1}}{\norm{\vvarx3}_{\ell^2}} \leq \max_j\Norm{e_j}_*\sqrt{\op{dim}(\tilde{\spcf0})}.
+			\\\Norm{\varf0}_*&\leq \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} |\varx3_j|\Norm{e_j}_* \leq \max_{j\leq\op{dim}(\tilde{\spcf0})} \Norm{e_j}_*\norm{\vvarx3}_{\ell^1},
+			\\\implies \frac{\Norm{\varf0}_*}{\norm{\varf0}} &\leq \max_{j\leq \op{dim}(\tilde{\spcf0})}\Norm{e_j}_*\frac{\norm{\vvarx3}_{\ell^1}}{\norm{\vvarx3}_{\ell^2}} \leq \max_{j\leq \op{dim}(\tilde{\spcf0})}\Norm{e_j}_*\sqrt{\op{dim}(\tilde{\spcf0})}.
 		\end{align}
@@
 		\begin{equation}
-		\norm{\Pi\varf2} = \frac{\IP{\Pi\varf2}{\varf2}}{\norm{\Pi\varf2}} \leq \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\norm{\varf2}_1\lesssim  \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\norm{\varf2}_q \lesssim \frac{\norm{\Pi\varf2}_{\infty}}{\norm{\Pi\varf2}}\Norm{\varf2}.
+			\norm{\tens{\Pi}\varf2} = \frac{\IP{\tens{\Pi}\varf2}{\varf2}}{\norm{\tens{\Pi}\varf2}} \leq \frac{\norm{\tens{\Pi}\varf2}_{\infty}}{\norm{\tens{\Pi}\varf2}}\norm{\varf2}_1\lesssim  \frac{\norm{\tens{\Pi}\varf2}_{\infty}}{\norm{\tens{\Pi}\varf2}}\norm{\varf2}_q \lesssim \frac{\norm{\tens{\Pi}\varf2}_{\infty}}{\norm{\tens{\Pi}\varf2}}\Norm{\varf2}.
 		\end{equation}
@@
 Essentially, with an extra smoothness assumption on $e_j$, we can reduce the dimension of the problem to $\op{dim}(\tilde{\spcf0})=C $ and use the previous result.
-\end{proof}
+		\qed\end{proof}
 
@@
 		Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
-Let $(\tilde{\spcf0}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces with orthogonal projections $\tilde\Pi_k\colon\F H\to\tilde{\spcf0}^k $.
+Let $(\tilde{\spcf0}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces with orthogonal projections $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k $.
 If $q\geq 2$,
-	$$\norm{\tilde\Pi_k\varf2} \lesssim \Norm{\varf2}, $$
+		$$\norm{\tilde{\tens{\Pi}}_k\varf2} \lesssim \Norm{\varf2}, $$
 		otherwise,
-	$$\norm{\tilde\Pi_k\varf2} \lesssim \sqrt{\op{dim}(\tilde{\spcf0}^0)}\meshsize^{-\frac{kd}{2}}\Norm{\varf2} $$
+		$$\norm{\tilde{\tens{\Pi}}_k\varf2} \lesssim \sqrt{\op{dim}(\tilde{\spcf0}^0)}\meshsize^{-\frac{kd}{2}}\Norm{\varf2} $$
 		uniformly for all $\varf2\in \F H$.
@@
 	\begin{proof}
-	Most of the conditions of \Cref{app:thm: generic a_U bound} are already satisfied.
+		Most of the conditions of Lemma~\ref{app:thm: generic a_U bound} are already satisfied.
 Denote $C=\op{dim}(\tilde{\spcf0^0})$ and $\{e_j\st j\in[C]\}$ the standard orthonormal basis of $\tilde{\spcf0}^0$.
-The scaling properties of $\meshsize$-refining finite element spaces guarantee that the value of $C$ satisfies the conditions of \Cref{app:thm: generic a_U bound} and a basis of $\tilde{\spcf0}^k$ is given by
+The scaling properties of $\meshsize$-refining finite element spaces guarantee that the value of $C$ satisfies the conditions of Lemma~\ref{app:thm: generic a_U bound} and a basis of $\tilde{\spcf0}^k$ is given by
 		\begin{equation}
@@
 
-	We now compute the scaling constant in \Cref{app:thm: generic a_U bound}:
+		We now compute the scaling constant in Lemma~\ref{app:thm: generic a_U bound}:
 		\begin{equation}
@@
 		\end{equation}
-	This value is independent of $j$ and gives the desired bound as a result of \Cref{app:thm: generic a_U bound}.
-\end{proof}
+		This value is independent of $j$ and gives the desired bound as a result of Lemma~\ref{app:thm: generic a_U bound}.
+		\qed\end{proof}
 
 	\begin{lemma}\label{app:thm: generic a_E bound}
-	Let $(\tilde{\spcf0}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\varf2}^k=\argmin_{\varf0\in\tilde{\spcf0}^k}\Func0(\varf0)$.
+		Let $(\tilde{\spcf0}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\varf2}^k=\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)$.
 		\begin{enumerate}
-		\item If $\Func0$ is $\Norm\cdot$-Lipschitz at $\varf0^*$, then
-		$\Func0(\tilde{\varf2}^k)-\Func0(\varf0^*) \lesssim \meshsize^p\Norm{\varf0^*}.$
-		\item If $\Func0$ is $\Norm\cdot$-smooth at $\varf0^*$, then 
-		$\Func0(\tilde{\varf2}^k)-\Func0(\varf0^*) \lesssim \meshsize^{2p}\Norm{\varf0^*}.$
-		\item If $\func1$ is $\Norm\cdot$-Lipschitz at $\varf0^*$ and 
-		$$\min_{\varf2\in\tilde{\spcf0}^k}\left\{\Norm{\varf2-\varf0^*}\st \func2(\varf2)\leq \func2(\varf0^*)\right\} \lesssim \min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*}$$
+			\item If $\op{E}$ is $\Norm\cdot$-Lipschitz at $\varf0^*$, then
+			$\op{E}(\tilde{\varf2}^k)-\op{E}(\varf0^*) \lesssim \meshsize^p\Norm{\varf0^*}.$
+			\item If $\op{E}$ is $\Norm\cdot$-smooth at $\varf0^*$, then 
+			$\op{E}(\tilde{\varf2}^k)-\op{E}(\varf0^*) \lesssim \meshsize^{2p}\Norm{\varf0^*}.$
+			\item If $\op{f}$ is $\Norm\cdot$-Lipschitz at $\varf0^*$ and 
+			$$\min_{\varf2\in\tilde{\spcf0}^k}\left\{\Norm{\varf2-\varf0^*}\st \op{g}(\varf2)\leq \op{g}(\varf0^*)\right\} \lesssim \min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*}$$
 			uniformly for $k\in\F N$, then
-		$\Func0(\tilde{\varf2}^k)-\Func0(\varf0^*) \lesssim \meshsize^p\Norm{\varf0^*}.$
+			$\op{E}(\tilde{\varf2}^k)-\op{E}(\varf0^*) \lesssim \meshsize^p\Norm{\varf0^*}.$
 		\end{enumerate}
@@
 		\begin{gather}
-		\Func0(\varf2)-\Func0(\varf0^*) \leq \op{Lip}(\Func0)\Norm{\varf2-\varf0^*},
-		\\\Func0(\varf2)-\Func0(\varf0^*) \leq \IP{\partial \Func0(\varf2)}{(\varf2-\varf0^*)} = \IP{\nabla \Func0(\varf2)-\nabla \Func0(\varf0^*)}{ \varf2-\varf0^*} \leq \op{Lip}(\nabla F)\Norm{\varf2-\varf0^*}^2,
-		\\\Func0(\varf2)-\Func0(\varf0^*) \leq \func1(\varf2)-\func1(\varf0^*) \leq \op{Lip}(\func1)\Norm{\varf2-\varf0^*}.
+			\op{E}(\varf2)-\op{E}(\varf0^*) \leq \op{Lip}(\op{E})\Norm{\varf2-\varf0^*},
+			\\\op{E}(\varf2)-\op{E}(\varf0^*) \leq \IP{\nabla\op{E}(\varf2)}{\varf2-\varf0^*} = \IP{\nabla \op{E}(\varf2)-\nabla \op{E}(\varf0^*)}{ \varf2-\varf0^*} \leq \op{Lip}(\nabla F)\Norm{\varf2-\varf0^*}^2,
+			\\\op{E}(\varf2)-\op{E}(\varf0^*) \leq \op{f}(\varf2)-\op{f}(\varf0^*) \leq \op{Lip}(\op{f})\Norm{\varf2-\varf0^*}.
 		\end{gather}
 		Minimising over the right-hand side over $\varf2$ and substituting the definition of order gives the desired result.
-\end{proof}
+		\qed\end{proof}
 
 	\section{Operator norms for numerical examples}
-\begin{theorem}[\Cref{thm: norm bound examples}]\label{app:thm: norm bound examples}
+	\begin{theorem}[Theorem~\ref{thm: norm bound examples}]\label{app:thm: norm bound examples}
 		\Paste{thm: norm bound examples}
 	\end{theorem}
-\begin{proof}[Proof case 1:]
-	From \Cref{thm: norm bound L2} we have 
-	\begin{equation}
-		(\A\A^*)_{i,j} = \IP{\1_{\F{\Varx0}_i}}{\1_{\F{\Varx0}_j}} = |\F{\Varx0}_i\cap \F{\Varx0}_j| = \splitln{|\F{\Varx0}_i|}{i=j}{0}{i\neq j}.
-	\end{equation}
-	Therefore, $\A\A^*$ is a diagonal matrix and $\norm{\A\A^*}_{\ell^2\to\ell^2} = \max_j |\F{\Varx0}_j|$ completes the result.
-\end{proof}
-
-\begin{proof}[Proof case 2:]
+	\begin{proof}[case 1]
+		From Lemma~\ref{thm: norm bound L2} we have 
+		\begin{equation}
+			(\A\A^*)_{i,j} = \IP{\1_{\F{X}_i}}{\1_{\F{X}_j}} = |\F{X}_i\cap \F{X}_j| = \splitln{|\F{X}_i|}{i=j}{0}{i\neq j}.
+		\end{equation}
+		Therefore, $\A\A^*$ is a diagonal matrix and $\norm{\A\A^*}_{\ell^2\to\ell^2} = \max_{j\in[m]} |\F{X}_j|$ completes the result.
+		\qed\end{proof}
+
+	\begin{proof}[case 2]
 		$\vard1_j$ are not necessarily orthogonal however $|\IP{\vard1_i}{\vard1_j}|\leq 1$ therefore we can estimate
@@
 		\end{equation}
-	Now looking to apply \Cref{thm: norm bound smoothness}, note $\norm{\nabla^k\vard1_j}_\infty \leq \Vars3^k$, therefore
+		Now looking to apply Lemma~\ref{thm: norm bound smoothness}, note $\norm{\nabla^k\vard1_j}_\infty \leq \Vars3^k$, therefore
 		\begin{align}
@@
 		\end{align}
-\end{proof}
-
-\begin{proof}[Proof case 3:]
+		\qed\end{proof}
+
+	\begin{proof}[case 3]
 		In the Gaussian case, we build our approximations around the idea that sums of Gaussians should converge very quickly.
@@
 Computing the inner products gives
-	\begin{multline}
-		\IP{\vard1_i}{\vard1_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vvarx0-\vvarx0_i|^2}{2\sigma^2}-\tfrac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right) \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right)
-		\\= (4\pi\sigma^2)^{-\frac d2} \exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right).
-	\end{multline}
+		\begin{equation}
+			\IP{\vard1_i}{\vard1_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vvarx0-\vvarx0_i|^2}{2\sigma^2}-\tfrac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right) \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right).
+		\end{equation}
 		Estimating the operator norm,
@@
 		This is a nice approximation because it factorises simply over dimensions.
-	Applying the results from \Cref{thm: norm bound smoothness}, note
+		Applying the results from Lemma~\ref{thm: norm bound smoothness}, note
 		$$\begin{array}{rll}
@@
 			as $|\hat{\vvarx0}|\leq \delta$ and $p$ has non-negative coefficients. 
-	\end{proof}
-
-	Now, continuing the proof of \Cref{app:thm: norm bound examples}, for $\hat m=\sqrt[d]{m}$, $\delta=\frac{\sqrt{d}}{2}$ and $J=\{\vec{j}\in\F Z^d \st \norm{\vec{j}}_{\ell^\infty}\leq 2\hat m\}$, \Cref{app: exp sum bound} bounds
+			\qed\end{proof}
+
+		Now, continuing the proof of Theorem~\ref{app:thm: norm bound examples}, for $\hat m=\sqrt[d]{m}$, $\delta=\frac{\sqrt{d}}{2}$ and $J=\{\vec{j}\in\F Z^d \st \norm{\vec{j}}_{\ell^\infty}\leq 2\hat m\}$, Lemma~\ref{app: exp sum bound} bounds
 		\begin{align*}
@@
 		for all $\vvarx0\in\Domain$. In a worst case, this is $O(2^dm)$ time complexity however the summands all decay faster than exponentially and so should converge very quickly.	
-\end{proof}
+		\qed\end{proof}
 

### 2021-08-05 response.tex
minor update

@@
 As in your comment, if one has coercivity then the convergence is clear.
-FISTA is known to converge weakly in the Hilbert-space setting, these guarantees are likely to hold here with the added adaptivity although we have not performed the analysis as it is still a relatively special case.
-A key component of this is the result $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, in general we do not even expect this quantity to be bounded.
-It's not clear whether we can leverage the Hilbert-norm structures of FISTA to gain convergence in the Banach space.
+More generally, FISTA is known to converge weakly in the Hilbert-space setting.
+This is also likely to hold with our algorithm when the minimiser is in $\F H$ but we have not performed the analysis as it is still a relatively special case.
+A key component of the proof is the bound $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, in general we do not even expect this quantity to be bounded.
+It's not clear whether we can leverage the Hilbert-norm structures of FISTA to gain any convergence in the Banach space.
+
+	\todo{Not sure if this is the right level of detail.}
 
@@
 At the moment it's perhaps a bit confusing, figures (1,2,3,4,7,9) show (both, discrete, continuous, continuous, discrete, continuous) respectively.
-It might be simpler just to show the continuous gap after Figure 1 (which compares both).}
+It might be simpler to show only the continuous gap except in Figure 1 (which compares both).}
 \end{enumerate}

### 2021-08-05 paper.tex
minor update

@@
 The only change in our own implementation is to translate the support to $[-\tfrac12,\tfrac12]^2$.
-We briefly remark that the tree structuring of wavelets is not novel and appears more frequently in the Bayesian inverse problems literature \cite{Castillo2019}.
+We briefly remark that the tree structuring of wavelets is not novel and appears more frequently in the Bayesian inverse problems literature \cite{Castillo2019,Kekkonen2021}.
 

### 2021-09-07 response.tex
Typos and updated figures

@@
 
-	\item \review{On page 18, the authors state: Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms}
+	\item \review{On page 18, the authors state: ``Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.''}
 
@@
 
-	The convergence displayed in Figure 2 is relative to the discretised problem, rather than the continuous one.
-The behaviour for the continuous gap is shown in Figure 3 (for two of the algorithms from Figure 2).
-Figure 2 shows that the nonadaptive schemes reach high precision very quickly, but Figure 3 indicates that this does not correlate with accuracy.
+	We have updated Figure 2 to show both discrete and continuous gaps to improve clarity.
+The old Figure 2 only plotted the discrete gap which showed convergence to stationarity rather than necessarily an `accurate solution'.
+If we measure accuracy in terms of the continuous gap (the value 0.1 in this case), you are correct that the nonadaptive scheme reaches high precision for the set accuracy level.
+In practice, this may mean that the adaptive reconstruction has more values which are approximately but not exactly 0.
 
-	\todo{I could include extra continuous gap (like Figure 1) panels?
-Or just show continuous gap?
-At the moment it's perhaps a bit confusing, figures (1,2,3,4,7,9) show (both, discrete, continuous, continuous, discrete, continuous) respectively.
-It might be simpler to show only the continuous gap except in Figure 1 (which compares both).}
+	\todo{What point is being made here? Have they just been confused about different `accuracy' metrics in the two plots? Should I add a comment on precision in the text?}
 \end{enumerate}

### 2021-09-07 paper.tex
Typos and updated figures

@@
 \newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
-\renewcommand{\sfrac}[2]{\,^{#1}\!\!/\!_{#2}}
 \newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}
@@
 	\begin{abstract}
-		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever the optimisation domain is contained in a suitable Hilbert space.
+		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever the \edit{optimisation domain}{optimiser} is contained in a suitable Hilbert space.
 We propose a modified algorithm where each iteration is performed in a subspace, and that subspace is allowed to change at every iteration.
@@
 	\begin{itemize}
-		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{the minimum is not achieved.
+		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved.
 For example, in Lasso discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}.
@@
 	\subsection{Outline}
-	This chapter is organised as follows.
+	This work is organised as follows.
 Section~\ref{sec: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, Algorithm~\ref{alg: refining FISTA}.
 The main theoretical contribution of this work is the convergence analysis of Algorithm~\ref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in Section~\ref{sec: recipe}, then we state the specific results in the case of FISTA in Section~\ref{sec: FISTA convergence}.
-The main results are Theorems~\ref{thm: exponential FISTA convergence}/~\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.
-
-	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation.
+The main results are Theorems~\ref{thm: exponential FISTA convergence}/\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.
+
+	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} \edit{}{in Banach spaces }and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation.
 In particular, we describe how to choose efficient refining discretisations to approximate \edit{$\varf0^*$}{$\Emin$}, estimate the convergence of $\op{E}$, and identify the support of \edit{$\varf0^*$}{the minimiser}.
@@
 The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$.
-If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{classical} algorithm.
+If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{original} algorithm.
 
@@
 	\end{equation}
-	for any norm $\Norm\cdot$.}
+	for any specified norm $\Norm\cdot$.}
 
@@
 		\end{equation}
-		for $\varf2_n \in \argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$.
+		for any $\varf2_n \in \argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$.
 The similarities to \eqref{eq: classical FISTA} are clear.
-If $\spcf0^n=\spcf0$, then we have $\varf2_n=\edit{\varf0^*}{\varf2_0}$ and the two estimates agree.
+If $\spcf0^n=\edit{\spcf0}{\F H}$, then we have $\varf2_n=\edit{\varf0^*}{\varf2_0\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the two estimates agree.
 These extra terms quantify the robustness to changing of discretisation.
@@
 If the subspaces refine too quickly, then the influence of \edit{$\norm{\varf0^*}=\infty$}{$\norm{\varf0_n}\to\infty$} will slow the rate of convergence.
-If the resolution is too coarse then we are overfitting to the discrete minimiser, but if the resolution is too fine then convergence of the energy is slow.
+If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow.
 Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of
@@
 Lemma~\ref{thm: mini exponential FISTA convergence} shows that a sufficient condition is
-		$$\edit{}{\varf0_{n_k-1}}\in\spcf0^{n_k}\subset\spcf0^{n_k+1}\subset\ldots\subset\spcf0^{n_{k+1}-1}.$$
+		$$\edit{}{\varf0_{n_k-1}\in}\spcf0^{n_k}\subset\spcf0^{n_k+1}\subset\ldots\subset\spcf0^{n_{k+1}-1}.$$
 		Convergence is most stable if the approximation spaces $\spcf0^n$ satisfy a monotone inclusion, breaking the monotonicity requires more care.
@@
 			Fix a sequence of subspaces $(\spcf0^n\edit{\subset\spcf0\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$.
-Let $\varf0_n$ and $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA}.
-			Then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have
+Let $\varf0_n$ and $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA}, then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have
 		}
@@
 On the other hand, suppose one of the pixels of the discretisation is $[\varx0_0-\meshsize,\varx0_0+\meshsize]$, then
-	$$\tens{\Pi}_n\varf0^*\left(\varx0_0+\sfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varx0-\vars5)^2d\varx0 = \varx0_0 < \varx0_0+\sfrac\meshsize2.$$
+	$$\tens{\Pi}_n\varf0^*\left(\varx0_0+\tfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varx0-\vars5)^2d\varx0 = \varx0_0 < \varx0_0+\tfrac\meshsize2.$$
 	In particular $\tens{\Pi}_n\varf0^* \notin\F D$ therefore $\op{E}(\tens{\Pi}_n\varf0^*) = \infty$.
@@
 If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of subspaces.
-This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\spcf0^n}$ rather than the desired function $\op{E}|_{\spcf0}$.
+This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\spcf0^n}$ rather than the desired function $\op{E}|_{\F H}$.
 Combining the assumptions given by Definition~\ref{def: exp subspaces} and the result of Lemma~\ref{thm: mini exponential FISTA convergence}, the following lemma proves the convergence of Algorithm~\ref{alg: refining FISTA} provided that the refinement times $n_k$ are sufficiently small (i.e.
@@
 		This is equivalent to Lemma~\ref{thm: sufficiently fast} after the assumptions on $n_k$.
-		\item If $\spcf0$ is finite dimensional, then the $\vars3_{\Varf0}=1$ is almost trivially satisfied.
+		\item If $\edit{\spcf0}{\F H}$ is finite dimensional, then the $\vars3_{\Varf0}=1$ is almost trivially satisfied.
 Norms in finite dimensions are equivalent and any discretisation can be achieved with a finite number of refinements (i.e.
@@
 	While Theorem~\ref{thm: exponential FISTA convergence} also allows for spatial adaptivity, we will simplify the requirements to a form which seems more practical for implementation and also allows for temporal adaptivity.
-We make the assumption that the choice of $n_k$ depends only on the value $\op{E}(u^{n_k-1})$ and therefore make $u^{n_k-1}$ the root of our requirements.
-Lemma~\ref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\op{E}_0(\varf0^{n_k-1})\lesssim \vars3_{\op{E}}^{-k}$.
+We make the assumption that the choice of $n_k$ depends only on the value $\op{E}(u_{n_k-1})$ and therefore make $u_{n_k-1}$ the root of our requirements.
+Lemma~\ref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\op{E}_0(\varf0_{n_k-1})\lesssim \vars3_{\op{E}}^{-k}$.
 However, the value of $\op{E}_0$ may be hard to estimate and so we retain a `backstop' condition which guarantees that convergence is no slower than the rate given by Theorem~\ref{thm: exponential FISTA convergence}.
@@
 			\end{enumerate}
-			\edit{}{If, furthermore, there exists a Banach space $(\spcf0,\Norm\cdot)$ with $\spcf0\supset\F H$, then it is also sufficient that:}
+			\edit{}{If, furthermore, there exists a Banach space $(\spcf0,\Norm\cdot)$ with $\spcf0\supset\F H$ and the sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded, then it is also sufficient that:}
 			\begin{enumerate}\setcounter{enumi}{3}
-				\item Small continuous gradient refinement: $ \Norm{\partial\op{E}(\varf0_k)}_*\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded.
-				\item Small discrete gradient refinement: $\op{E}_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $\Norm{\tens{\Pi}_k\partial\op{E}(\varf0_k)}_*\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded.
+				\item Small continuous gradient refinement: $ \Norm{\partial\op{E}(\varf0_k)}_*\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
+				\item Small discrete gradient refinement: $\op{E}_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $\Norm{\tens{\Pi}_k\partial\op{E}(\varf0_k)}_*\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
 			\end{enumerate}
@@
 If the total number of refinements is finite (i.e.
-$\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$) then $\vars3_{\Varf0} = 1$.
+$\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$), then $\vars3_{\Varf0} = 1$.
 This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}.
@@
 	\begin{definition}
-		Suppose $\spcf0\subset L^p(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$\edit{}{ with sufficiently smooth boundary}.
+		Suppose $\spcf0\subset L^q(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$\edit{}{ with sufficiently smooth boundary}.
 We say that $\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$ is a \emph{mesh} if
@@
 In this case we choose $\tilde{\spcf0}^k$ to be the span of all piecewise constant functions on a mesh of squares with maximum side length $2^{-k}$ (i.e.
-$\meshsize=\sfrac12$).
+$\meshsize=\tfrac12$).
 
@@
 	\begin{equation}
-		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1.
+		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
 	\end{equation}
@@
 This accounts for using the weaker topology of $\C M(\Domain)$ rather than $L^1(\Domain)$.
-In Section~\ref{sec: smoothing operators} we will show two practical examples were this (semi)norm is accurately computable.
+In Section~\ref{sec: smoothing operators} we will show two practical examples where this (semi)norm is accurately computable.
 
@@
 infinite vectors with finitely many non-zeros.
-The key change in analysis from the continuous case is $\varf0^*\in\ell^2(\R)$, which leads to $\vars3_{\Varf0}=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\op{E}}$ or any additional properties of $\A$.
+The key change in analysis from the continuous case is $\norm{\varf0^*}<\infty$, which leads to $\vars3_{\Varf0}=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\op{E}}$ or any additional properties of $\A$.
 The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence} hold trivially.
@@
 	Heuristically, we will use strong convexity of $\op{E}^*$ and smoothness of $\A^*$ to quantify the statement:
-	$$ \text{if}\quad \op{E}(\varf0_n) + \op{E}^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st |[\A^*\vvard0_n](\vvarx0)|\ll \mu\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
+	$$ \text{if}\quad \op{E}(\varf0_n) + \op{E}^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st \mu - |[\A^*\vvard0_n](\vvarx0)|\ll 1\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
 	First we use the strong convexity of $\op{E}^*$, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible then
@@
 	\begin{equation}
-		|[\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\op{E}(\varf0_n)+\op{E}^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq: support equation}
+		|[\tens{\Pi}_n\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\op{E}(\varf0_n)+\op{E}^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq: support equation}
 	\end{equation}
@@
 	\begin{itemize}
-		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the quantity $\op{E}(\varf0_n)-\op{E}(\varf0^*)$, the more relevant quantity here is $\op{E}^*(\vars2_0\vvard0_n)+\op{E}(\varf0^*)$ for which there is no proven rate.
-		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
+		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the quantity $\op{E}(\varf0_n)-\op{E}(\varf0^*)$, the more relevant quantity here is $\op{E}^*(\vars2_0\vvard0_n)+\op{E}(\varf0^*)$ for which there is no proven rate of convergence.
+		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence for $\op{E}(\varf0_n)$, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
 	\end{itemize}
@@
 Lemma~\ref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\op{E}_0(\varf0_n)$ so it is this monotone estimate which is plotted.
-To clarify, as $\op{E}(\varf0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\op{E}_0(\varf0_n) \approx \min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2_0\vvard0_{n'})$.
+As $\op{E}(\varf0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\op{E}_0(\varf0_n) \approx \min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2_0\vvard0_{n'})$.
 Another quantity of interest is minimisation of the discrete Lasso energy $\min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2\vvard0_{n'})$ which will be referred to as the `discrete gap'.
-Note that for the adaptive schemes the discrete gap may not monotonic as the discrete dual problem changes with $N$.
+Note that for the adaptive schemes the discrete gap may not be monotonic as the discrete dual problem changes with $N$.
 
@@
 zeroth order Taylor approximations of $\A^*\vvard0_n$ on pixel $\domain_i^n$.
-This was found to be an efficient method of selecting pixels for refinement based on quantities which had already been computed.
+This was found to be an efficient method of selecting pixels for refinement using quantities which had already been computed.
 Note briefly that this greedy strategy directly targets uncertainty, refinements also happen outside of the support of $u_n$ to guarantee that this is representative of $\varf0^*$.
@@
 		\includegraphics[width=.84\textwidth]{lasso_convergence_short}
-		\caption{Discrete convergence of different algorithms.
+		\caption{\edit{Discrete }{}Convergence plots for solving 1D problems with different algorithms.
 `Adaptive' methods use Algorithm~\ref{alg: refining FISTA} with fewer than 1024 pixels and the remaining methods use a uniform discretisation of 1024 pixels.}\label{fig: convergence with method}
@@
 		\includegraphics[width=.85\textwidth]{haar_convergence_short}
-		\caption{Discrete convergence of different implementations of Algorithm~\ref{alg: refining FISTA} with an unlimited number of pixels.}\label{fig: haar convergence}
+		\caption{\edit{Discrete }{}Convergence of different implementations of Algorithm~\ref{alg: refining FISTA} with an unlimited number of pixels.}\label{fig: haar convergence}
 
@@
 
-	Figure~\ref{fig: STORM convergence} shows slightly faster convergence than $n^{-\sfrac23}$ predicted by \eqref{eq: Lasso resolution rate} in dimension $d=2$.
+	Figure~\ref{fig: STORM convergence} shows slightly faster convergence than $n^{-2/3}$ predicted by \eqref{eq: Lasso resolution rate} in dimension $d=2$.
 In this example we also implement the suggestion of Section~\ref{sec: support detection} to remove pixels outside of the support of $\varf0^*$.
@@
 	\begin{equation}
-		\vars2_0\norm{\tens{\Pi}_n\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq 1-\frac{\op{threshold}}{\mu}
+		\vars2_0 \norm{ \tens{\Pi}_n\A^*\vvard0_n }_{L^\infty(\domain_i^n)} \leq (1-\op{threshold}_n)\mu
 	\end{equation}
 	guarantees that $\domain_i^n\cap\op{supp}(\varf0^*) = \emptyset$.
-This value is plotted in the first panel of Figure~\ref{fig: STORM convergence}.
-Once this threshold becomes less than 1, we can start reducing the number of pixels instead of just continual refinement, as seen in the right-hand panel after around 30 iterations.
+This threshold is plotted in the first panel of Figure~\ref{fig: STORM convergence}.
+Once the value becomes less than 1, we can start reducing the number of pixels instead of continual refinement, as seen in the right-hand panel after around 30 iterations.
 
@@
 
-	An interesting observation over all of the adaptive Lasso examples is that the classical oscillatory behaviour of FISTA has not occurred.
+	An interesting observation over all of the adaptive Lasso examples is that the standard oscillatory behaviour of FISTA has not occurred.
 With the monotone gaps plotted, oscillatory convergence should correspond to a piecewise constant descending gap.

### 2021-09-22 paper.tex
A few notes to improve

@@
 \newcommand{\Emin}[1][\varf0]{\inf_{#1\in\F H}\op{E}(#1)}
+\newcommand{\todo}[1]{{\color{red}#1}}
 
@@
 	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$.
-\edit{}{We denote the orthogonal projection operators $\tens{\Pi}_n\colon\F H\to\spcf0^n$ such that $\tens{\Pi}_n\varf0-\varf0 \perp \varf1$ for all $\varf0\in\F H$, $\varf1\in\spcf0^n$.}
+\edit{}{We denote the orthogonal projection operators $\tens{\Pi}_n\colon\F H\to\spcf0^n$ such that $\tens{\Pi}_n\varf0-\varf0 \perp \varf1$ for all $\varf0\in\F H$, $\varf1\in\spcf0^n$.
+\todo{Finite dimensional?}}
 
@@
 	\end{lemma}
+\todo{check this}
 	\noindent This is exactly the result of \cite{Chambolle2015} applied to the function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$.
@@
 
-	\begin{lemma}[{\edit{analogous to }{}\cite[\edit{Theorem 2}{(17)}]{Chambolle2015}, \cite[\edit{Theorem 1}{Lmma 4.1}]{Beck2009}}]\label{thm: one step FISTA}
+	\begin{lemma}[{\edit{analogous to }{}\cite[\edit{Theorem 2}{(17)}]{Chambolle2015}, \cite[\edit{Theorem 1}{Lemma 4.1}]{Beck2009}}]\label{thm: one step FISTA}
 		\Copy{thm: one step FISTA}{
@@
 		\begin{equation}
-			\Paste{thm:eq: one step FISTA}
+			t_{n}^2(\op{E}(\varf0_{n}) - \op{E}(\varf2_n)) - (t_{n}^2-t_{n})(\op{E}(\varf0_{n-1})-\op{E}(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.
 			\label{app:eq: one-step FISTA}

### 2021-09-24 response.tex
First edits for Antonin, removed ortho projection

@@
 
-	\todo{Not sure if this is the right level of detail.}
-
 	\item \review{On page 9, line 27 the authors require $\Omega$ to be a compact set.
@@
 
-	We have avoided non-smooth misfit terms because they are not so convenient for the FISTA framework, one might use a primal-dual or ADMM algorithm to avoid solving a least-squares problem on every iteration.
-For smooth misfits, you are quite right that most of Sections 6 and 7 can be generalised.
-The main difference is that the dual problem is very simple for quadratic misfits.
-If it is hard to compute $E_0(u_n)$, then one has to rely on the subdifferential for the a posteriori refinement strategy.
-
-	\todo{I'm not sure what is being requested here.
-Is he asking for another numerical example?
-We could change the data fidelity for the Wavelet example quite easily?
-I'm actually struggling to think of another common smooth data fidelity which isn't Entropy-smoothed OT...}
+	You are right, we can also consider alternative misfits.
+We have replaced the wavelet example with a (Huber-smoothed) robust $\ell^1$ penalty as we only explicitly required the gradient and Lipschitz constant for computations.
 
@@
 
-	Thank you for noticing this mistake.
+	Thank you for noticing this typo.
 
@@
 	We have updated Figure 2 to show both discrete and continuous gaps to improve clarity.
-The old Figure 2 only plotted the discrete gap which showed convergence to stationarity rather than necessarily an `accurate solution'.
-If we measure accuracy in terms of the continuous gap (the value 0.1 in this case), you are correct that the nonadaptive scheme reaches high precision for the set accuracy level.
-In practice, this may mean that the adaptive reconstruction has more values which are approximately but not exactly 0.
-
-	\todo{What point is being made here? Have they just been confused about different `accuracy' metrics in the two plots? Should I add a comment on precision in the text?}
+The point of Figure 2 (and 3) is to demonstrate the accuracy of our theoretical rate predictions.
+While the initial rate of convergence is faster for the nonadaptive schemes, Figure 4 confirms that this does not translate to a large practical improvement.
 \end{enumerate}
@@
 We are very sorry that you found our manuscript so difficult to read.
-We have tried to extrapolate your comments to also make changes to the rest of the document.
-To address your first comments we have removed much of the emphasis on the Banach space $\F U$ so that most computations are clearly in the Hilbert space.
+You were right, the former foundations were not rigorous enough.
+We have rewritten these sections in line with your suggestion of removing the emphasis on the Banach space.
+The analysis of the algorithm in the first half of the manuscript is now performed without mention of a Banach space.
+Consequently, we also realised that the orthogonal projection was not needed at all, and we now allow $U^n$ to be subsets of $\F H$ rather than subspaces.
 The Banach space setting is reserved for examples discussed in Sections 5 to 7.

### 2021-09-24 paper.tex
First edits for Antonin, removed ortho projection

@@
 \newcommand{\Emin}[1][\varf0]{\inf_{#1\in\F H}\op{E}(#1)}
-\newcommand{\todo}[1]{{\color{red}#1}}
 
@@
 %\renewcommand{\edit}[2]{#2}
+\newcommand{\todo}[1]{{\color{red}#1}}
 
@@
 	\begin{abstract}
-		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever the \edit{optimisation domain}{optimiser} is contained in a suitable Hilbert space.
-We propose a modified algorithm where each iteration is performed in a subspace, and that subspace is allowed to change at every iteration.
-Analytically, this allows us to guarantee convergence in a Banach space setting, although at a reduced rate depending on the conditioning of the specific problem.
-Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.
+		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever \edit{the optimisation domain}{a minimiser} is contained in a suitable Hilbert space.
+We propose a modified algorithm where each iteration is performed in a \edit{subspace, and that subspace is allowed to change at every iteration}{subset which is allowed to change at every iteration}.
+\edit{Analytically, this allows us to guarantee convergence in a Banach space setting}{Sufficient conditions are provided for guaranteed convergence}, although at a reduced rate depending on the conditioning of the specific problem.
+\edit{Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.}{These conditions have a natural interpretation when a minimiser exists in an underlying Banach space.
+A typical example is the Lasso problem where we provide detailed theoretical and numerical analysis.}
 	\end{abstract}
@@
 
-	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining }{closed }subspaces $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n=0,1,\ldots$.
-The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$.
+	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n=0,1,\ldots$.
+The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\spcf0^n$.
 If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{original} algorithm.
@@
 	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$.
-\edit{}{We denote the orthogonal projection operators $\tens{\Pi}_n\colon\F H\to\spcf0^n$ such that $\tens{\Pi}_n\varf0-\varf0 \perp \varf1$ for all $\varf0\in\F H$, $\varf1\in\spcf0^n$.
-\todo{Finite dimensional?}}
+\edit{}{Note in particular we need the argmin to be non-empty.
+For this we will assume $\spcf0^n$ are locally compact, for example finite dimensional.}
 
@@
 
-	\begin{algorithm}\caption{Refining subspace FISTA}\label{alg: refining FISTA}
+	\begin{algorithm}\caption{Refining \edit{subspace}{subset} FISTA}\label{alg: refining FISTA}
 		\centering
@@
 	\begin{adaptiveStep}\label{step: step 1 stability}
-		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting subspaces $\spcf0^n$.
+		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting \edit{subspaces}{subsets} $\spcf0^n$.
 In the notation of Algorithm~\ref{alg: refining FISTA}, Theorem~\ref{thm: mini FISTA convergence} shows that
@@
 If that mesh sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$.
-The integer $n_k$ should then be the time when the mesh has refined $k$ times.
+The integer $n_k$ should then be the time when the mesh has refined $k$ times.\edit{}{ Another canonical choice would be $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq \vars3_{\Varf0}^k\}$.
+The exponential scaling is less natural, but leads to better convergence guarantees.}
 
@@
 	\begin{adaptiveStep}\label{step: step 3 convergence bound}
-		In this step we combine the FISTA stability estimate with the subspace approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$.
+		In this step we combine the FISTA stability estimate with the \edit{subspace}{subset} approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$.
 For example, if $\spcf0^n$ is of the form
@@
 		In Step~\ref{step: step 3 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor.
-In particular, it is equivalent to run Algorithm~\ref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed subspace $\spcf0^N$.
+In particular, it is equivalent to run Algorithm~\ref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed \edit{subspace}{subset} $\spcf0^N$.
 The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\op{E}_0(\varf0_N)\lesssim \norm{\varf0_0-\varf2_N}^2 = O(\vars3_{\Varf0}^{2K})$ for $N\leq n_K$.
@@
 		The result of Step~\ref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate.
-If the subspaces refine too quickly, then the influence of \edit{$\norm{\varf0^*}=\infty$}{$\norm{\varf0_n}\to\infty$} will slow the rate of convergence.
+If the \edit{subspaces refine}{subsets grow} too quickly, then the influence of \edit{$\norm{\varf0^*}=\infty$}{$\norm{\varf0_n}\to\infty$} will slow the rate of convergence.
 If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow.
@@
 The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely.
-
-	\edit{}{Throughout this section we consider a sequence of subspaces $\spcf0^n$ which generate the iterates $\varf0_n$ in Algorithm~\ref{alg: refining FISTA} satisfying
+	\edit{}{Throughout this section we consider a sequence $(\spcf0^n)_{n\in\F N}$ which generate the iterates $(\varf0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} satisfying
 	\begin{equation}\label{eq: refining subspace definition}
-			\spcf0^n\subset\F H \text{ for } n\in\F N \qquad\text{such that}\qquad \spcf0^n \text{ is closed and }\varf0_n\in\spcf0^{n+1}\text{ for all }n\in\F N
-		\end{equation}
-		with orthogonal projections $\tens{\Pi}_n\colon\F H\to\spcf0^n$.
-	}
+		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{are closed, convex, locally compact subsets for all }\quad n\in\F N.
+	\end{equation}}
 
@@
 			\edit{\\\centerline{$\displaystyle \op{E}(\varf0) + \tfrac12\norm{\varf0-\tens{\Pi}_n\varf2}^2 \leq \op{E}(\tens{\Pi}_n\varf2) + \tfrac12\norm{\bar{\varf0}-\tens{\Pi}_n\varf2}^2.$}}{
-			$$\op{E}(\varf0) + \tfrac12\norm{\varf0-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\tens{\Pi}_n\bar{\varf0}-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\bar{\varf0}-\varf2}^2.$$}
+			$$\op{E}(\varf0) + \tfrac12\norm{\varf0-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\bar{\varf0}-\varf2}^2.$$}
 			\edit{where $\tens{\Pi}_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.}{}
@@
 	\end{lemma}
-\todo{check this}
-	\noindent This is exactly the result of \cite{Chambolle2015} applied to the function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$.
+	\noindent This is exactly the result of \cite{Chambolle2015} on the \edit{subspace}{subset} $\spcf0^n$.
 Applying Lemma~\ref{thm: descent lemma} to the iterates from Algorithm~\ref{alg: refining FISTA} gives a more explicit inequality.
@@
 		\Copy{thm: mini FISTA convergence}{
-			Fix a sequence of subspaces $(\spcf0^n\edit{\subset\spcf0\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$.
+			Fix a sequence of \edit{subspaces}{subsets} $(\spcf0^n\edit{\subset\spcf0\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$.
 Let $\varf0_n$ and $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA}, then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have
@@
 	\noindent The proof is given in Theorem~\ref{app:thm: mini FISTA convergence}.
-This result is the key approximation for showing convergence of FISTA with refining subspaces.
+This result is the key approximation for showing convergence of FISTA with \edit{refining subspaces}{growing subsets}.
 In the classical setting, we have $\spcf0^n\edit{=\spcf0}{}=\F H$, $\varf2_n\edit{=\varf0^*}{\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the extra terms on the right-hand side collapse to 0.
 
-	\edit{The}{If there exists a minimiser $\varf0^*\in\argmin_{\varf0\in\F H}\op{E}(\varf0)$, then the } natural choice in \eqref{eq: FISTA inequality} is $\varf2_n=\tens{\Pi}_n\varf0^*$, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\varf0^*)=\infty$ and so this inequality becomes useless.
-For example, if $\op{f}(\varf0) = \norm{\varf0}_{\edit{2}{L^2([0,1])}}^2$, $\op{g}$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$, and $\spcf0^n$ is a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$.
+	\edit{The}{If there exists a minimiser $\varf0^*\in\argmin_{\varf0\in\F H}\op{E}(\varf0)$, then the } natural choice in \eqref{eq: FISTA inequality} is $\varf2_n=\tens{\Pi}_n\varf0^*$\edit{}{ for some projection $\tens{\Pi}_n\colon\F H\to\spcf0^n$}, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\varf0^*)=\infty$ and so this inequality becomes useless.
+For example, if $\op{f}(\varf0) = \norm{\varf0}_{\edit{2}{L^2([0,1])}}^2$, $\op{g}$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$, and \edit{$\spcf0^n$ is}{$\tens{\Pi}_n$ is the $L^2$ projection onto} a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$.
 On the other hand, suppose one of the pixels of the discretisation is $[\varx0_0-\meshsize,\varx0_0+\meshsize]$, then
@@
 The choice $\varf2_n=\argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$ is much more robust and allows us to apply Algorithm~\ref{alg: refining FISTA} more broadly.
-The penalty for this flexibility is a more complicated analysis, each time the subspace changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.
+The penalty for this flexibility is a more complicated analysis, each time the \edit{subspace}{subset} changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.
 
@@
 	\begin{definition}\label{def: exp subspaces}
-		Fix $\vars3_{\Varf0},\vars3_{\op{E}}\geq 1$ and a sequence of \edit{subspaces $(\tilde{\spcf0}^k\subset\F H\cap\spcf0)_{k\in\F N}$}{closed subspaces $\tilde{\spcf0}^k\subset\F H$}.
+		Fix $\vars3_{\Varf0},\vars3_{\op{E}}\geq 1$ and a sequence of \edit{subspaces $(\tilde{\spcf0}^k\subset\F H\cap\spcf0)_{k\in\F N}$}{closed subsets $\tilde{\spcf0}^k\subset\F H$}.
 We say that $(\tilde{\spcf0}^k)_{k\in\F N}$ is a \emph{$(\vars3_{\Varf0},\vars3_{\op{E}})$-discretisation for $\op{E}$} if
@@
 	uniformly in $n$.
-If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of subspaces.
+If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of \edit{subspaces}{subsets}.
 This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\spcf0^n}$ rather than the desired function $\op{E}|_{\F H}$.
@@
 		\Copy{thm: stronger exponential FISTA convergence}{
-			Let $(\spcf0^n\subset\F H\edit{\cap\spcf0}{})_{n\in\F N}$ be a sequence of subspaces \edit{}{satisfying \eqref{eq: refining subspace definition} }and $n_k\in\F N$ a monotone increasing sequence such that
+			Let $(\spcf0^n\subset\F H\edit{\cap\spcf0}{})_{n\in\F N}$ be a sequence of \edit{subspaces}{subsets satisfying \eqref{eq: refining subspace definition} }and $n_k\in\F N$ a monotone increasing sequence such that
 			$$ \tilde{\spcf0}^k \coloneqq \spcf0^{n_k}\edit{\ni \varf0_{n_k-1}}{}, \qquad \tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
@@
 		\Copy{thm: practical refinement criteria}{
-			Let $(\tilde{\spcf0}^k)_{k\in\F N}$ be a sequence of subspaces with some points $\varf0_k\in \tilde{\spcf0}^k$ and $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)$.
+			Let $(\tilde{\spcf0}^k)_{k\in\F N}$ be a sequence of \edit{subspaces}{subsets} with some points $\varf0_k\in \tilde{\spcf0}^k$ and $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)$.
 Suppose that $\norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k$.
@@
 			\begin{enumerate}\setcounter{enumi}{3}
-				\item Small continuous gradient refinement: $ \Norm{\partial\op{E}(\varf0_k)}_*\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
-				\item Small discrete gradient refinement: $\op{E}_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $\Norm{\tens{\Pi}_k\partial\op{E}(\varf0_k)}_*\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
+				\item Small continuous gradient refinement: $ \edit{\Norm{\partial\op{E}(\varf0_k)}_*}{\inf_{\varf1\in\partial\op{E}(\varf0_k)}\Norm{\varf1}_*}\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
+				\item Small discrete gradient refinement: $\op{E}_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $\edit{\Norm{\tens{\Pi}_k\partial\op{E}(\varf0_k)}_*}{\sup_{\varf0,\tilde{\varf0}\in \tilde{\spcf0}^k}\inf_{\varf1\in\partial\op{E}(\varf0_k)}\frac{|\IP{v}{\varf0-\tilde{\varf0}}|}{\Norm{\varf0-\tilde{\varf0}}}}\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
 			\end{enumerate}
@@
 Cases (1), (3), and (4) justify that any choice of $\tilde{\spcf0}^k\ni\varf0_k$ (or $\varf0_{n_k-1}$ in Theorem~\ref{thm: stronger exponential FISTA convergence}) satisfies the required conditions.
-In cases (2) and (5), $\varf0_k$ is sufficient to choose the refinement time $n_k$ but not the subspace $\tilde{\spcf0}^k$.
+In cases (2) and (5), $\varf0_k$ is sufficient to choose the refinement time $n_k$ but not the \edit{subspace}{subset} $\tilde{\spcf0}^k$.
 In these cases one could, for example, choose $\tilde{\spcf0}^k$ to be a uniform discretisation with apriori estimates.
@@
 This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}.
-In this section we give explicit computations of $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subspaces $(\tilde{\spcf0}^n)_{n\in\F N}$ will be finite dimensional finite-element--like spaces, as defined below.
+In this section we give explicit computations of $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subsets $(\tilde{\spcf0}^n)_{n\in\F N}$ will be finite dimensional finite-element--like spaces, as defined below.
 	}
@@
 	\end{definition}
-	We note that any piecewise polynomial finite element space can be used to form a $\meshsize$-refining sequence of subspaces.
+	We note that any piecewise polynomial finite element \edit{}{(or spline)} space can be used to form a $\meshsize$-refining sequence of subspaces.
 Wavelets with a compactly supported basis behave like a multi-resolution finite element space as there is always overlap in the supports of basis vectors.
@@
 
-	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\norm\cdot_1$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$.
+	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$.
 This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$,
@@
 	\end{equation}
-	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. For any $\varf2\in\tilde{\spcf0}^k$ such that $\Norm{\varf2}\leq \Norm{\varf0^*}$, we compute
-	\begin{align}
-		\op{E}(\varf2)-\op{E}(\varf0^*) &=  \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0^*-\data}_{\ell^2}^2 + \mu\left(\Norm{\varf2}-\Norm{\varf0^*}\right)
-		\\&\leq \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0^*-\data}_{\ell^2}^2
-		\\&= \ip{[\tfrac12\A(\varf2+\varf0^*)-\data]}{\A(\varf2-\varf0^*)}
-		\\&\leq \max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0^*-\data}_{\ell^2})\norm{\A(\varf2-\varf0^*)}_{\ell^2} 
-		\\&\leq \sqrt{2\op{E}(\varf2)}\norm{\A(\varf2-\varf0^*)}_{\ell^2}.
+	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$.
+\edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing.
+Therefore }
+	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
+	\begin{align}
+		\op{E}(\varf2)-\op{E}(\varf0) &=  \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
+		\\&\leq \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2
+		\\&= \ip{[\tfrac12\A(\varf2+\varf0)-\data]}{\A(\varf2-\varf0)}
+		\\&\leq \max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})\norm{\A(\varf2-\varf0)}_{\ell^2}
+		\\&\leq \sqrt{2\max(\op{E}(\varf2), \op{E}(\varf0))}\norm{\A(\varf2-\varf0)}_{\ell^2}.
 	\end{align}
@@
 		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
-	}{Piecewise constant projection is $L^1$-bounded therefore we can extend $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ by the Hahn-Banach theorem.
-Choosing $\varf2=\tilde{\tens{\Pi}}_k\varf0^*$ gives
-	\begin{align}
-		\op{E}(\varf2)-\op{E}(\varf0^*) &\lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2}
-		\\&= \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0^*}
-		\\&\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0^*}
-		\\&\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0^*}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0^*}
+	}{This norm further simplifies with
+	\begin{align}
+		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
+		 &= \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
+		\\&\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
+		\\&\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
 	\end{align}}
 	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.
+\edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$.
+		Combining these estimates gives 
+		\begin{equation}
+			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}|\A^*|_{\ell^2\to C^1}\Norm{\varf0^*}.
+		\end{equation}}
 
@@
 	This section contains all of the statements and proofs of the results contained in Section~\ref{sec: FISTA convergence}.
-\edit{}{Recall that the subspaces $\spcf0^n\subset\F H$ satisfy \eqref{eq: refining subspace definition}.}
+\edit{}{Recall that the subsets $\spcf0^n\subset\F H$ satisfy \eqref{eq: refining subspace definition}.}
 
@@
 	\begin{proof}
-		Modifying \cite[\edit{Theorem 2}{Thm 3.2}]{Chambolle2015}, for $n\geq1$ we apply Lemma~\ref{thm: descent lemma} with $\bar{\varf0} = \bar{\varf0}_{n-1}$ and $\varf2 = (1-\frac{1}{t_{n}})\varf0_{n-1} + \frac{1}{t_{n}}\varf2_n\edit{}{\in\spcf0^n}$.
-This gives
+		Modifying \cite[\edit{Theorem 2}{Thm 3.2}]{Chambolle2015}, for $n\geq1$ we apply Lemma~\ref{thm: descent lemma} with $\bar{\varf0} = \bar{\varf0}_{n-1}$ and $\varf2 = (1-\frac{1}{t_{n}})\varf0_{n-1} + \frac{1}{t_{n}}\varf2_n$.
+\edit{}{By \eqref{eq: refining subspace definition}, $\varf0_{n-1}\in\spcf0^n$ is convex so $\varf2\in \spcf0^n$.
+}This gives
 		\begin{equation}
@@
 		\begin{equation}
-			\tfrac12\norm{\varf2_N}^2 + \sum^N_{n=1} t_n\op{E}_0(\tens{\Pi}_n\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n} = \tfrac12\norm{\tilde{\varf2}_K}^2 + \sum_{n=n_K}^Nt_n\op{E}_0(\tilde{\varf2}_K)
+			\tfrac12\norm{\varf2_N}^2 + \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n} = \tfrac12\norm{\tilde{\varf2}_K}^2 + \sum_{n=n_K}^Nt_n\op{E}_0(\tilde{\varf2}_K) 
 			+ \sum_{k=1}^K\sum_{n=n_{k-1}}^{n_k-1}t_n\op{E}_0(\tilde{\varf2}_{k-1}) 
@@
 		Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
-Let $\tilde{\spcf0}\subset \edit{\spcf0\cap}{}\F H$ be a finite dimensional subspace with orthonormal basis $\{e_j\st j=1,\ldots,\op{dim}(\tilde{\spcf0})\}\subset\tilde{\spcf0}$ and orthogonal projection $\tens{\Pi}\colon\F H\to\tilde{\spcf0}$.
+Let $\spcf0\subset \edit{\spcf0\cap}{}\F H$ be a finite dimensional subspace with orthonormal basis $\{e_j\st j=1,\ldots,\op{dim}(\spcf0)\}\subset\spcf0$ and orthogonal projection $\tens{\Pi}\colon\F H\to\spcf0$.
 If these conditions hold:
@@
 			\begin{equation}
-				\norm{\tens{\Pi}\varf2} \leq \sqrt{\op{dim}(\tilde{\spcf0})}\max_{j\leq \op{dim}(\tilde{\spcf0})}\Norm{e_j}_*\Norm{\varf2},
+				\norm{\tens{\Pi}\varf2} \leq \sqrt{\op{dim}(\spcf0)}\max_{j\leq \op{dim}(\spcf0)}\Norm{e_j}_*\Norm{\varf2},
 			\end{equation}
@@
 			\begin{equation}
-				\norm{\tens{\Pi}\varf2} \lesssim \sqrt C\max_{j\leq\op{dim}(\tilde{\spcf0})}\norm{e_j}_{\infty}\Norm{\varf2}
+				\norm{\tens{\Pi}\varf2} \lesssim \sqrt C\max_{j\leq\op{dim}(\spcf0)}\norm{e_j}_{\infty}\Norm{\varf2}
 			\end{equation}
@@
 		\end{equation}
-		therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\tilde{\spcf0}$.
-Switching to the given basis, for $\varf0 = \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} \varx3_je_j$ we have
-		\begin{align}
-			\norm{\varf0}^2 &= \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} \varx3_j^2 = \norm{\vvarx3}_{\ell^2}^2,
-			\\\Norm{\varf0}_*&\leq \sum_{j=1}^{\op{dim}(\tilde{\spcf0})} |\varx3_j|\Norm{e_j}_* \leq \max_{j\leq\op{dim}(\tilde{\spcf0})} \Norm{e_j}_*\norm{\vvarx3}_{\ell^1},
-			\\\implies \frac{\Norm{\varf0}_*}{\norm{\varf0}} &\leq \max_{j\leq \op{dim}(\tilde{\spcf0})}\Norm{e_j}_*\frac{\norm{\vvarx3}_{\ell^1}}{\norm{\vvarx3}_{\ell^2}} \leq \max_{j\leq \op{dim}(\tilde{\spcf0})}\Norm{e_j}_*\sqrt{\op{dim}(\tilde{\spcf0})}.
+		therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\spcf0$. Switching to the given basis, for $\varf0 = \sum_{j=1}^{\op{dim}(\spcf0)} \varx3_je_j$ we have
+		\begin{align}
+			\norm{\varf0}^2 &= \sum_{j=1}^{\op{dim}(\spcf0)} \varx3_j^2 = \norm{\vvarx3}_{\ell^2}^2,
+			\\\Norm{\varf0}_*&\leq \sum_{j=1}^{\op{dim}(\spcf0)} |\varx3_j|\Norm{e_j}_* \leq \max_{j\leq\op{dim}(\spcf0)} \Norm{e_j}_*\norm{\vvarx3}_{\ell^1},
+			\\\implies \frac{\Norm{\varf0}_*}{\norm{\varf0}} &\leq \max_{j\leq \op{dim}(\spcf0)}\Norm{e_j}_*\frac{\norm{\vvarx3}_{\ell^1}}{\norm{\vvarx3}_{\ell^2}} \leq \max_{j\leq \op{dim}(\spcf0)}\Norm{e_j}_*\sqrt{\op{dim}(\spcf0)}.
 		\end{align}
@@
 		This inequality holds for all $\mu>1$ therefore also for $\mu=1$.
-Essentially, with an extra smoothness assumption on $e_j$, we can reduce the dimension of the problem to $\op{dim}(\tilde{\spcf0})=C $ and use the previous result.
+Essentially, with an extra smoothness assumption on $e_j$, we can reduce the dimension of the problem to $\op{dim}(\spcf0)=C $ and use the previous result.
 	\qed\end{proof}

### 2021-09-24 code/ada_haar.py

@@ -10,7 +10,7 @@ from haar_bin import (Radon_to_sparse_matrix, Radon_update_sparse_matrix, _small
                       _FP_leaf, _FP_wave2leaf, _BP_leaf, _BP_leaf2wave)
 from matplotlib import pyplot as plt
 from numpy import (array, empty, sqrt, zeros, isscalar, array_equal, concatenate,
-                   cos, sin, pi, log, nanmin, nanmax, log2)
+                   cos, sin, pi, log, nanmin, nanmax, log2, random)
 from anytree import Node, RenderTree, PreOrderIter, PostOrderIter
 from algorithms import shrink, stopping_criterion, faster_FISTA, \
     _makeVid, FB, Norm, FISTA
@@ -1129,7 +1129,7 @@ class Haar2Sino(op):
                          extent=[self.angles.min(), self.angles.max(), self.grid.min(), self.grid.max()], **kwargs)
 
 
-def Haar_tomo(A, data, alpha, iters=None, prnt=True, plot=True, vid=None, algorithm='Greedy'):
+def Haar_tomo(A, data, alpha, huber, iters=None, prnt=True, plot=True, vid=None, algorithm='Greedy'):
     '''
     min 1/2|Pu-d|_2^2 + alpha*|Wu|_1
 
@@ -1152,6 +1152,27 @@ def Haar_tomo(A, data, alpha, iters=None, prnt=True, plot=True, vid=None, algori
     pms = {'i':0, 'eps':1e-18, 'refineI':2}
     recon = Haar_2D(0, Haar_space(1, dim=2))
     A.update(recon.FS)
+    
+    from numba import vectorize
+    @vectorize(identity=0, nopython=True)
+    def Huber(x):
+        x = abs(x)
+        if x < huber:
+            return x * x / (2 * huber)
+        else:
+            return x - .5 * huber
+    @vectorize(identity=0, nopython=True)
+    def Huber_grad(x):
+        if abs(x) < huber:
+            return x / huber
+        elif x > 0:
+            return 1
+        else:
+            return -1
+#     @vectorize(identity=0, nopython=True)
+#     def Huber(x): return .5 * x * x
+#     @vectorize(identity=0, nopython=True)
+#     def Huber_grad(x): return x
 
     def residual(u): return A(u) - data
 
[…]

### 2021-09-24 response.tex
Small updates to response

@@
 We have replaced the wavelet example with a (Huber-smoothed) robust $\ell^1$ penalty as we only explicitly required the gradient and Lipschitz constant for computations.
+	\todo{Maybe too much work to rewrite?}
 
@@
 
-	As suggested, we now state that $\F U^n$ are closed in (9) and re-referenced throughout the document.
+	As suggested, we now state that $\F U^n$ are closed in (10) and re-referenced throughout the document.
 The mention of $\F U$ on page 1 is now just a reference to the Lasso example introduced in a later section.
@@
 
-	The projections $\Pi_n$ are now defined only on $\F H$.
+	The projections $\Pi_n$ are now used only on $\F H$.
 
@@
 
-	As commented before, we define $\Pi_n$ on $\F H$ to remove the ambiguity.
+	As commented before, we define $\Pi_n$ on $\F H$ to remove any ambiguity.
 
@@
 
-	Lemma 1 has now been modified to have $w\in \F U^n$. Equation (9) also has the assumption $u_{n-1}\in \F U^n$, instead of the suggested $\F U^{n-1}\subset \F U^n$.
+	Lemma 1 has now been modified to have $w\in \F U^n$. Equation (10) also has the assumption $u_{n-1}\in \F U^n$, instead of the suggested $\F U^{n-1}\subset \F U^n$.
 

### 2021-09-26 paper.tex
Generalised from Lasso to L1 reconstruction

@@
 \edit{Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.}{These conditions have a natural interpretation when a minimiser exists in an underlying Banach space.
-A typical example is the Lasso problem where we provide detailed theoretical and numerical analysis.}
+Typical examples are L1-penalised reconstructions where we provide detailed theoretical and numerical analysis.}
 	\end{abstract}
@@
 		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved.
-For example, in Lasso discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}.
+For example, in \edit{Lasso}{L1 penalised reconstructions} discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}.
 The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
@@
 $\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$), then $\vars3_{\Varf0} = 1$.
-This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}.
+This holds for most finite dimensional problems as well as the countable example discussed in detail in Section~\ref{sec: Lasso definition}.
 In this section we give explicit computations of $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subsets $(\tilde{\spcf0}^n)_{n\in\F N}$ will be finite dimensional finite-element--like spaces, as defined below.
@@
 
-	\section{Lasso minimisation}\label{sec: Lasso definition}
-	We now focus on the specific example of Lasso which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}.
-We consider three forms of Lasso which will be referred to as continuous, countable, and discrete Lasso depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
+	\section{\edit{Lasso}{L1 penalised} minimisation}\label{sec: Lasso definition}
+	We now focus on the specific example of \edit{Lasso}{L1 penalised optimisation} which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}.
+We consider three forms \edit{of Lasso}{} which will be referred to as the continuous, countable, and discrete \edit{Lasso}{problem} depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
 In each case, the energy can be written as
 	\begin{equation}\label{eq: Lasso energy}
-		\op{E}(\varf0) = \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu\Norm{\varf0}
+		\op{E}(\varf0) = \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu\Norm{\varf0}
 	\end{equation}
 	for some $\A\colon \spcf0\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$.
-\edit{}{In the continuous-space case, we require $\A^*\colon\R^m\to C(\Domain)$.
+\edit{}{We assume $\op{f}\in C^1(\R^m)$ is convex with $\nabla\op{f}$ 1-Lipschitz and locally bounded, and in the continuous-space case, we require $\A^*\colon\R^m\to C(\Domain)$.
 }Let $\varf0^*\in\argmin_{\varf0\in\spcf0}\op{E}(\varf0)$.
@@
 	\begin{align}
-		\op{E}(\varf2)-\op{E}(\varf0) &=  \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
-		\\&\leq \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2
-		\\&= \ip{[\tfrac12\A(\varf2+\varf0)-\data]}{\A(\varf2-\varf0)}
-		\\&\leq \max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})\norm{\A(\varf2-\varf0)}_{\ell^2}
-		\\&\leq \sqrt{2\max(\op{E}(\varf2), \op{E}(\varf0))}\norm{\A(\varf2-\varf0)}_{\ell^2}.
+		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
+		\\&= \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
+		\\&\lesssim_{\edit{}{\op{E}(\varf2)}} \edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{}\norm{\A(\varf2-\varf0)}_{\ell^2}.
 	\end{align}
@@
 	}{This norm further simplifies with
-	\begin{align}
+	\begin{multline}
 		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
-		 &= \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
-		\\&\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
-		\\&\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
-	\end{align}}
+		 = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
+		\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
+		\\\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
+	\end{multline}}
 	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.
@@
 
-	For countable Lasso we consider discretisation subspaces of the form 
+	For countable \edit{Lasso}{dimensions} we consider discretisation subspaces of the form 
 	$$\tilde{\spcf0}^k = \{\varf0\in \ell^1(\R) \st i\notin J_k\implies \varf0_i=0\}$$ for some sets $J_k\subset\F N$, i.e.
@@
 	\subsubsection{Bounds for discretised functionals}\label{sec: bound discrete}
-	We start by computing estimates for discretised Lasso.
-This covers the cases when either continuous/countable Lasso is projected onto $\spcf0^n$, or $\spcf0$ is finite dimensional.
+	We start by computing estimates for discretised \edit{Lasso}{energies}.
+This covers the cases when either the continuous/countable \edit{Lasso}{energy} is projected onto $\spcf0^n$, or $\spcf0$ is finite dimensional.
 For notation we will use the continuous case, to recover the other cases just replace continuous indexing with discrete (i.e.
@@
 	Let $\tens{\Pi}_n\colon\F H\to\spcf0^n$ denote the orthogonal projection.
-For Lasso, the discretised function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$ is equivalent to replacing $\varf0$ with $\tens{\Pi}_n\varf0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.
+\edit{For Lasso}{In our case}, the discretised function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$ is equivalent to replacing $\varf0$ with $\tens{\Pi}_n\varf0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.
 
@@
 	\begin{align}
-		\partial_n \op{E}(\tens{\Pi}_n\varf0_n)(\vvarx0) &= [\tens{\Pi}_n\A^*(\A\varf0_n-\data)](\vvarx0) + \begin{cases}
+		\partial_n \op{E}(\tens{\Pi}_n\varf0_n)(\vvarx0) &= [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)](\vvarx0) + \begin{cases}
 			\{+\mu\} & \varf0_n(\vvarx0)>0 \\ [-\mu,\mu] & \varf0_n(\vvarx0)=0 
@@
 		\end{cases} 
-		\\&\eqqcolon [\tens{\Pi}_n\A^*(\A\varf0_n-\data)](\vvarx0) + \mu\tens{\Pi}_n\sign(\varf0_n(\vvarx0))
+		\\&\eqqcolon [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)](\vvarx0) + \mu\tens{\Pi}_n\sign(\varf0_n(\vvarx0))
 	\end{align}
@@
 	\begin{align}
-		\Norm{\partial_n \op{E}(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\min\left\{|\varf1| \st \varf1\in \tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0) +  \mu\sign(\varf0_n(\vvarx0))\right\}
+		\Norm{\partial_n \op{E}(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\min\left\{|\varf1| \st \varf1\in \tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0) +  \mu\sign(\varf0_n(\vvarx0))\right\}
 		\\&= \max_{\vvarx0\in\Domain}\begin{cases}
-			|[\tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
-			\\|[\tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
-			\\\max\left(|[\tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
+			|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
+			\\|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
+			\\\max\left(|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
 		\end{cases}
@@
 	\begin{align}
-		\min_{\varf0\in \spcf0^n} \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu\Norm{\varf0} &= \min_{\varf0\in\F H}\max_{\vvard0\in\R^m} \ip{(\A\tens{\Pi}_n\varf0-\data)}{ \vvard0} +\mu\Norm{\tens{\Pi}_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
-		\\&= \max_{\vvard0\in\R^m}\min_{\varf0\in\F H} \ip{(\A\tens{\Pi}_n\varf0-\data)}{\vvard0} +\mu\Norm{\tens{\Pi}_n\varf0} -\tfrac12\norm{\vvard0}_{\ell^2}^2
-		\\&= \max_{\vvard0\in\R^m} \splitln{-\ip{\data}{\vvard0} -\tfrac12\norm{\vvard0}_{\ell^2}^2}{\qquad\Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu}{-\infty}{\qquad\text{else}}
-		\\&= -\min_{\vvard0\in\R^m} \underbrace{\tfrac12\norm{\vvard0}_{\ell^2}^2+\ip{\data}{\vvard0}}_{\eqqcolon \op{E}^*(\vvard0)}  + \chi(\Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu).
+		\min_{\varf0\in \spcf0^n} \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu\Norm{\varf0} &= \min_{\varf0\in\F H}\max_{\vvard0\in\R^m} \ip{(\A\tens{\Pi}_n\varf0-\data)}{ \vvard0} +\mu\Norm{\tens{\Pi}_n\varf0} -\edit{\tfrac12\norm{\vvard0}_{\ell^2}^2}{\op{f}^*(\vvard0)}
+		\\&= \max_{\vvard0\in\R^m}\min_{\varf0\in\F H} \ip{(\A\tens{\Pi}_n\varf0-\data)}{\vvard0} +\mu\Norm{\tens{\Pi}_n\varf0} -\edit{\tfrac12\norm{\vvard0}_{\ell^2}^2}{\op{f}^*(\vvard0)}
+		\\&= \max_{\vvard0\in\R^m} \splitln{-\ip{\data}{\vvard0} -\edit{\tfrac12\norm{\vvard0}_{\ell^2}^2}{\op{f}^*(\vvard0)}}{\qquad\Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu}{-\infty}{\qquad\text{else}}
+		\\&= -\min_{\vvard0\in\R^m} \underbrace{\edit{\tfrac12\norm{\vvard0}_{\ell^2}^2}{\op{f}^*(\vvard0)}+\ip{\data}{\vvard0}}_{\eqqcolon \op{E}^*(\vvard0)}  + \chi(\Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu).
 	\end{align}
@@
 	\begin{equation}
-		\vvard0^* = \A\varf0^*-\data.
+		\edit{}{\A\varf0^*-\data\in\partial\op{f}^*(\vvard0^*),\qquad\text{or equivalently}\qquad}
+		\vvard0^* = \edit{}{\nabla\op{f}}(\A\varf0^*-\data).
 	\end{equation}
@@
 	\begin{equation}
-		\vvard0_n\coloneqq \A\varf0_n - \data, \qquad \op{E}(\varf0)-\min_{\varf0'\in\spcf0^n}\op{E}(\varf0') \leq \op{E}(\varf0) +\min_{\vars2\geq 0}\left\{\op{E}^*(\vars2\vvard0_n) \st \vars2 \Norm{\tens{\Pi}_n\A^*\vvard0_n}_*\leq \mu\right\}
-	\end{equation}
-	with optimal choice
+		\vvard0_n\coloneqq \edit{}{\nabla\op{f}}(\A\varf0_n - \data), \qquad \op{E}(\varf0)-\min_{\varf0'\in\spcf0^n}\op{E}(\varf0') \leq \op{E}(\varf0) +\edit{\min_{\vars2\geq 0}\{}{}\op{E}^*(\vars2\vvard0_n) \edit{\st \vars2 \Norm{\tens{\Pi}_n\A^*\vvard0_n}_*\leq \mu\}}{}
+	\end{equation}
+	\edit{with optimal choice}{for some $0\leq \vars2\leq\frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vvard0_n}_*}$. In the case $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$, one can use the optimal choice}
 	\begin{equation}
@@
 	\end{equation}
-	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\varf0_n) = \frac12\norm{\vvard0_n}_{\ell^2}^2$ and $\tens{\Pi}_n\nabla\op{f}(\varf0_n) = \tens{\Pi}_n\A^*\vvard0_n$ are easily computable, therefore $\vars2$ and $\op{E}(\varf0_n) +\op{E}^*(\vars2\vvard0_n)$ are also easy to compute.
+	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\A\varf0_n-\data)\edit{ = \frac12\norm{\vvard0_n}_{\ell^2}^2}{}$ and $\tens{\Pi}_n\nabla\op{f}(\A\varf0_n-\data)\edit{ = \tens{\Pi}_n\A^*\vvard0_n}{}$ are easily computable, therefore $\vars2$ and $\op{E}(\varf0_n) +\op{E}^*(\vars2\vvard0_n)$ are also easy to compute.
 
@@
 		\end{cases}
-		\\ \op{E}_0(\varf0_n) &\leq \op{E}(\varf0_n) + \op{E}(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right)
-	\end{align}
-	where $\vvard0_n = \A\varf0_n-\data\in\R^m$ is always exactly computable.
+		\\ \op{E}_0(\varf0_n) &\leq \op{E}(\varf0_n) + \op{E}(\vars2_0\vvard0_n), \qquad \vars2_0\edit{=\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right)}{\in\left[0,\frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right]}
+	\end{align}
+	where $\vvard0_n = \edit{}{\nabla\op{f}}(\A\varf0_n-\data)\in\R^m$ is always exactly computable.
 
@@
 	\subsubsection{Bounds for continuous functionals}\label{sec: bound continuous}
-	Finally we extend the results of Section~\ref{sec: bound discrete} to continuous Lasso. Similar to the countable case, the exact formulae can be written down immediately:
+	Finally we extend the results of Section~\ref{sec: bound discrete} to continuous \edit{Lasso}{problems}. Similar to the countable case, the exact formulae can be written down immediately:
 	\begin{align}
@@
 		\end{cases}
-		\\ \op{E}_0(\varf0_n) &\leq \op{E}(\varf0_n) + \op{E}(\vars2_0\vvard0_n), \qquad \vars2_0=\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right).
+		\\ \op{E}_0(\varf0_n) &\leq \op{E}(\varf0_n) + \op{E}(\vars2_0\vvard0_n), \qquad \vars2_0\edit{=\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right)}{\in\left[0,\frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right]}.
 	\end{align}
@@
 
-	The bounds presented here for continuous Lasso emphasise the twinned properties required for adaptive mesh optimisation.
+	The bounds presented here for continuous \edit{Lasso}{problems} emphasise the twinned properties required for adaptive mesh optimisation.
 The mesh should be refined greedily to the structures of $\varf0^*$, but also must be sufficiently uniform to provide a good estimate for $\op{E}(\varf0^*)$.
@@
 	\subsection{Support detection}\label{sec: support detection}
-	The main motivation for using Lasso in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\varf0^*$ is also provably close to the `true' support \cite{Duval2017a,Poon2018}.
+	The main motivation for using \edit{Lasso}{L1 penalties} in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\varf0^*$ is also provably close to the `true' support \cite{Duval2017a,Poon2018}.
 If $\varf0_n\approx \varf0^*$ in the appropriate sense, then we should also be able to quantify the statement $\op{supp}(\varf0_n)\approx\op{supp}(\varf0^*)$.
@@
 	$$ \text{if}\quad \op{E}(\varf0_n) + \op{E}^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st \mu - |[\A^*\vvard0_n](\vvarx0)|\ll 1\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
-	First we use the strong convexity of $\op{E}^*$, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible then
+	\edit{First we use the strong convexity of $\op{E}^*$}{Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex.
+\todo{Is there a reference for this?
+I can't find it in Rockafellar.} Therefore}, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible, then
 	\begin{equation}
@@
 	\subsection{Operator norms}\label{sec: smoothing operators}
-	For numerical implementation of Lasso, we are required to accurately estimate several operator norms of $\A$.
+	For numerical implementation of \edit{Lasso}{\eqref{eq: Lasso energy}}, we are required to accurately estimate several operator norms of $\A$.
 For $\op{f}$ to be 1-Lipschitz we must divide by $|\A\A^*|_{\ell^2\to\ell^2}$, and the adaptivity described in Sections~\ref{sec: continuous lasso rate}, \ref{sec: bound continuous}, and~\ref{sec: support detection} requires the values of $|\A^*|_{\ell^2\to L^\infty}$, $|\A^*|_{\ell^2\to C^1}$, and $|\A^*|_{\ell^2\to C^2}$.
@@
 	\section{Numerical examples}\label{sec: numerics}
-	We present four numerical Lasso examples.
+	We present four numerical \edit{Lasso }{}examples.
 The first two are in 1D to demonstrate the performance of different variants of Algorithm~\ref{alg: refining FISTA}, both with and without adaptivity.
@@
 
-	The next example is 2D reconstruction from Radon or X-ray data with wavelet-sparsity.
+	The next example is 2D reconstruction from Radon or X-ray data with wavelet-sparsity\edit{}{ and a robust data fidelity}.
 As the forward operator is not sufficiently smooth, we must optimise in $\ell^1(\R)$ which naturally leads to the choice of a wavelet basis.
@@
 
-	In this section, the main aim is to minimise the exact Lasso energy $\op{E}_0(\varf0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
+	In this section, the main aim is to minimise the exact \edit{Lasso }{}energy $\op{E}_0(\varf0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
 Lemma~\ref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\op{E}_0(\varf0_n)$ so it is this monotone estimate which is plotted.
 As $\op{E}(\varf0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\op{E}_0(\varf0_n) \approx \min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2_0\vvard0_{n'})$.
-Another quantity of interest is minimisation of the discrete Lasso energy $\min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2\vvard0_{n'})$ which will be referred to as the `discrete gap'.
+Another quantity of interest is minimisation of the discrete \edit{Lasso }{}energy $\min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2\vvard0_{n'})$ which will be referred to as the `discrete gap'.
 Note that for the adaptive schemes the discrete gap may not be monotonic as the discrete dual problem changes with $N$.
@@
 	\subsection{1D continuous Lasso}\label{sec: 1D Lasso examples}
-	In this example we choose $\spcf0=\C M([0,1])$ and $\A\colon \spcf0\to \R^{30}$ with either random Fourier kernels:
+	In this example we choose $\spcf0=\C M([0,1])$\edit{}{, $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$} and $\A\colon \spcf0\to \R^{30}$ with either random Fourier kernels:
 	\begin{equation}
@@
 
-	Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.
-There are many methods designed to minimise the continuous Lasso energy in \eqref{eq: Lasso energy} (c.f.
+	Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.\edit{There are many methods designed to minimise the continuous Lasso energy in \eqref{eq: Lasso energy}}{For this choice of $\op{f}$, we call \eqref{eq: Lasso energy} the continuous Lasso problem, for which there are many numerical methods} (c.f.
 \cite{Bredies2013,Castro2016,Boyd2017,Catala2019}) however, most \edit{}{require} the solution of a non-convex problem.
@@
 
-	\subsection{2D wavelet Lasso}\label{sec: wavelet examples}
+	\subsection{2D \edit{wavelet Lasso}{robust sparse wavelet reconstruction}}\label{sec: wavelet examples}
 	In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{X}^I_i$ where 
@@
 	$\A$ is not smooth, therefore we can't bound $|\A^*|_{C^k}$ for $k>0$, and so we must look to minimise over $\ell^1$ rather than $L^1$.
-The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the Lasso form:
-	\begin{equation}
-		\min_{\varf0\in \spcf0} \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu \norm{\tens{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \tfrac12\norm{\A\tens{W}\hat{\varf0}-\data}_{\ell^2}^2 + \mu \norm{\hat{\varf0}}_{\ell^1}.
+The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the \edit{Lasso}{} form \edit{}{of \eqref{eq: Lasso energy}}:
+	\begin{equation}
+		\min_{\varf0\in \spcf0} \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu \norm{\tens{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \edit{\tfrac12\norm{\A\tens{W}\hat{\varf0}-\data}_{\ell^2}^2}{\op{f}(\A\tens{W}\hat{\varf0}-\data)} + \mu \norm{\hat{\varf0}}_{\ell^1}.
 	\end{equation}
 	The minimisers are related by $\varf0^* = \tens{W}\hat{\varf0}^*$ and, for wavelet bases, $\tens{W}$ is orthonormal so $\norm{\A\tens{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$. 
+	\edit{}{ In this example we consider the smoothed robust fidelity 
+		\begin{equation}
+			\op{f}(\vvard0) = \sum_{i=1}^m \splitln{10^{-4}|\vard0_i|}{|\vard0_i|\geq10^{-4}}{\tfrac12|\vard0_i|^2+\tfrac12 10^{-8}}{\text{else}} \approx 10^{-4}\norm{\vvard0}_{\ell^1}.
+		\end{equation}
+	\todo{Reference for robust fidelity?}
+	}	
 	From Section~\ref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\tens{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$.
@@
 	We consider two phantoms where the ground-truth is either a binary disc or the Shepp-Logan phantom.
-No noise is added to the Shepp-Logan data but \SI{5}{\percent} Gaussian white noise is added to the disc data.
+No noise is added to the Shepp-Logan data but \SI{5}{\percent} \edit{Gaussian white}{Laplace distributed} noise is added to the disc data.
 This is visualised in Figure~\ref{fig: haar data}.
@@
 		\includegraphics[width=.85\textwidth]{haar_data}
-		\caption{Phantoms and data used for wavelet-sparse tomography optimisation.
-The Shepp-Logan data is exact but the data for the disc-phantom has \SI{5}{\percent}\ Gaussian white noise.
+		\caption{Phantoms\edit{ and}{,} data \edit{used }{and reconstructions }for wavelet-sparse tomography optimisation.
+The Shepp-Logan data is exact but the data for the disc-phantom has \SI{5}{\percent}\ \edit{Gaussian white}{Laplace distributed} noise.
 Without noise the data would be uniform with respect to the angle.}\label{fig: haar data}
@@
 Readers are directed to the references \cite{Sage2015,Sage2019,Schermelleh2019} for further details.
-The Lasso formulation has previously been shown to be effective in the context of STORM \cite{Huang2017,Denoyelle2019}.
+The Lasso formulation \edit{}{($\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$) }has previously been shown to be effective in the context of STORM \cite{Huang2017,Denoyelle2019}.
 

### 2021-09-26 code/ada_haar.py

@@ -950,13 +950,13 @@ class Haar_2D(Haar):
 
         return self.copy(x)
 
-    def plot(self, level, ax=None, update=False, **kwargs):
-        y = self.discretise(level).T
+    def plot(self, level, ax=None, update=False, origin='lower', extent=[0, 1, 0, 1], **kwargs):
+        y = self.discretise(level)
         if update:
             assert ax is not None
             return ax.set_data(y)
         ax = ax if ax is not None else plt
-        return ax.imshow(y, origin='lower', extent=[0, 1, 0, 1], **kwargs)
+        return ax.imshow(y, origin=origin, extent=extent, **kwargs)
 
     def plot_tree(self, level=5, max_ticks=200, ax=None, spatial=True, update=False, **kwargs):
         ax = ax if ax is not None else plt.gca()
@@ -1158,17 +1158,18 @@ def Haar_tomo(A, data, alpha, huber, iters=None, prnt=True, plot=True, vid=None,
     def Huber(x):
         x = abs(x)
         if x < huber:
-            return x * x / (2 * huber)
+            return .5 * x * x
         else:
-            return x - .5 * huber
+            return huber * (x - .5 * huber)
     @vectorize(identity=0, nopython=True)
     def Huber_grad(x):
         if abs(x) < huber:
-            return x / huber
+            return x
         elif x > 0:
-            return 1
+            return huber
         else:
-            return -1
+            return -huber
+    alpha = alpha * huber
 #     @vectorize(identity=0, nopython=True)
 #     def Huber(x): return .5 * x * x
 #     @vectorize(identity=0, nopython=True)

### 2021-09-29 response.tex
Response to Antonin's comments

@@
 More generally, FISTA is known to converge weakly in the Hilbert-space setting.
-This is also likely to hold with our algorithm when the minimiser is in $\F H$ but we have not performed the analysis as it is still a relatively special case.
+This is also likely to hold with our algorithm when the minimiser is in $\F H$, but we have not verified this special case.
 A key component of the proof is the bound $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, in general we do not even expect this quantity to be bounded.
 It's not clear whether we can leverage the Hilbert-norm structures of FISTA to gain any convergence in the Banach space.
+In the LASSO case we know that the sequence is bounded in the L1 norm, so a subsequence must converge weakly, however, it's still unclear how to upgrade from convergence of a sub-sequence to full convergence.
 
@@
 	You are right, we can also consider alternative misfits.
-We have replaced the wavelet example with a (Huber-smoothed) robust $\ell^1$ penalty as we only explicitly required the gradient and Lipschitz constant for computations.
-	\todo{Maybe too much work to rewrite?}
+We have replaced the wavelet example in Section 7.2 with a (Huber-smoothed) robust $\ell^1$ penalty as we only explicitly required the gradient and Lipschitz constant for computations.
+This also led to a number of small updates to the analysis in Section 6 to generalise to a non-quadratic misfit.
 
@@
 The analysis of the algorithm in the first half of the manuscript is now performed without mention of a Banach space.
-Consequently, we also realised that the orthogonal projection was not needed at all, and we now allow $U^n$ to be subsets of $\F H$ rather than subspaces.
+Consequently, we also realised that the orthogonal projection was not required either, we now allow $U^n$ to be subsets of $\F H$ rather than subspaces.
 The Banach space setting is reserved for examples discussed in Sections 5 to 7.

### 2021-09-30 paper.tex
typo

@@
 		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\spcf0^n$.
-To do so, we construct a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
+\edit{}{The idea is that $\spcf0^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\varf0\in\spcf0^n}\op{E}(\varf0) \to \inf_{\varf0\in\F H}\op{E}(\varf0)$.
+A canonical example might be $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq n\}$.} \edit{To do so, we construct}{To quantify the balance between a growing Hilbert norm and improving estimate of $\op{E}$, we introduce} a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
 		\begin{equation}
@@
 		\end{equation}
-		The choice of exponential scaling is very natural if we consider the $\spcf0^n$ to be the subspace of functions discretised on a uniform mesh.
-If that mesh sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$.
-The integer $n_k$ should then be the time when the mesh has refined $k$ times.\edit{}{ Another canonical choice would be $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq \vars3_{\Varf0}^k\}$.
-The exponential scaling is less natural, but leads to better convergence guarantees.}
-
+		\edit{}{The expanding balls example would become $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq \vars3_{\Varf0}^k\}$, and $\vars3_{\op{E}}$ reflects the smoothness of $\op{E}$ with respect to the Hilbert norm.} The choice of exponential scaling is \edit{very}{more} natural if we consider the $\spcf0^n$ to be the subspace of functions discretised on a uniform mesh.
+If that mesh is sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$.
+The integer $n_k$ should then be the time when the mesh has refined $k$ times.
+%
 		\edit{The value of $\vars3_{\Varf0}$ is dictated by the smoothness of the norm of $\spcf0$ with respect to that of $\F H$.
 If $\norm{\varf0^*}<\infty$, then the value is $\vars3_{\Varf0}=1$, otherwise there is some damage to the rate of convergence generated by this factor.
-On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ at the point $\varf0^*$.}{Suppose $\F H$ is contained in a Banach space $(\spcf0,\Norm\cdot)$ such that $\Norm{\varf2_n}\lesssim 1$, then $\vars3_{\Varf0}$ reflects the smoothness between the two norms.
-If $\vars3_{\Varf0}>1$, then we cannot guarantee the original $n^{-2}$ rate of convergence.
-On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ (measured in $\Norm\cdot$) near minimisers.} %
-		If an efficient basis is used, then $\vars3_{\op{E}}$ is large. The trade-off between $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$ dictates the final convergence rate of the algorithm.
+On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ at the point $\varf0^*$.}{The value $\vars3_{\Varf0}$ reflects the smoothness of the chosen basis measured in $\F H$, and $\vars3_{\op{E}}$ is a measure of efficiency with respect to the structure of $\op{E}$.} %
+		If an efficient basis is used, then $\vars3_{\op{E}}$ is large.
+The trade-off between $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$ dictates the final convergence rate of the algorithm.
+\edit{}{If $\vars3_{\Varf0}>1$, then we cannot guarantee the original $n^{-2}$ rate of convergence.}
 	\end{adaptiveStep}
@@
 
-	\section{\edit{Lasso}{L1 penalised} minimisation}\label{sec: Lasso definition}
-	We now focus on the specific example of \edit{Lasso}{L1 penalised optimisation} which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}.
+	\section{L1 penalised reconstruction}\label{sec: Lasso definition}
+	\edit{We now focus on the specific example of Lasso}{The canonical example for FISTA is the LASSO problem with a quadratic data fidelity and L1 regularisation.
+In this section we develop the necessary analytical tools for the variant with general smooth fidelity term} which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}.
 We consider three forms \edit{of Lasso}{} which will be referred to as the continuous, countable, and discrete \edit{Lasso}{problem} depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
@@
 	for some $\A\colon \spcf0\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$.
-\edit{}{We assume $\op{f}\in C^1(\R^m)$ is convex with $\nabla\op{f}$ 1-Lipschitz and locally bounded, and in the continuous-space case, we require $\A^*\colon\R^m\to C(\Domain)$.
+\edit{}{We assume $\op{f}\in C^1(\R^m)$ is convex with $\nabla\op{f}$ 1-Lipschitz, and in the continuous-space case, we require $\A^*\colon\R^m\to C^1([0,1]^d)$.
 }Let $\varf0^*\in\argmin_{\varf0\in\spcf0}\op{E}(\varf0)$.
@@
 		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
-		\\&= \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
-		\\&\lesssim_{\edit{}{\op{E}(\varf2)}} \edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{}\norm{\A(\varf2-\varf0)}_{\ell^2}.
+		\\&\leq \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
+		\\&\leq\edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{\left[\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2} + \norm{\A(\varf2-\varf0^*)}_{\ell^2}\right]}\norm{\A(\varf2-\varf0)}_{\ell^2}.
 	\end{align}
@@
 		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
-	}{This norm further simplifies with
+	}{Clearly $\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2}$ is a constant, the second term is bounded by
+	\begin{equation}
+	\norm{\A(\varf2-\varf0^*)}_{\ell^2} = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{\A^*\vvarx3}{\varf2-\varf0^*} \leq \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} |\A^*\vvarx3|_{L^\infty}\Norm{\varf2-\varf0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\varf0}+\Norm{\varf0^*}).
+	\end{equation}
+	Similarly, the final term can be approximated by
 	\begin{multline}
@@
 		\begin{equation}
-			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}|\A^*|_{\ell^2\to C^1}\Norm{\varf0^*}.
+			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}.
 		\end{equation}}
@@
 	$$ \text{if}\quad \op{E}(\varf0_n) + \op{E}^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st \mu - |[\A^*\vvard0_n](\vvarx0)|\ll 1\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
-	\edit{First we use the strong convexity of $\op{E}^*$}{Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex.
-\todo{Is there a reference for this?
-I can't find it in Rockafellar.} Therefore}, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible, then
+	\edit{First we use the strong convexity of $\op{E}^*$}{Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex \cite[Chapter 10, Thm.
+4.2.2]{Hiriart2013}.
+Therefore}, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible, then
 	\begin{equation}
@@
 
-	\subsection{1D continuous Lasso}\label{sec: 1D Lasso examples}
+	\subsection{1D continuous LASSO}\label{sec: 1D Lasso examples}
 	In this example we choose $\spcf0=\C M([0,1])$\edit{}{, $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$} and $\A\colon \spcf0\to \R^{30}$ with either random Fourier kernels:
@@
 
-	Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.\edit{There are many methods designed to minimise the continuous Lasso energy in \eqref{eq: Lasso energy}}{For this choice of $\op{f}$, we call \eqref{eq: Lasso energy} the continuous Lasso problem, for which there are many numerical methods} (c.f.
+	Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.\edit{There are many methods designed to minimise the continuous LASSO energy in \eqref{eq: Lasso energy}}{For this choice of $\op{f}$, we call \eqref{eq: Lasso energy} the continuous LASSO problem, for which there are many numerical methods} (c.f.
 \cite{Bredies2013,Castro2016,Boyd2017,Catala2019}) however, most \edit{}{require} the solution of a non-convex problem.
@@
 		\includegraphics[width=.84\textwidth]{lasso_ndofs_convergence}
-		\caption{Rates of continuous/discrete gap convergence for different Lasso algorithms with 128, 256, or 512 pixels.
+		\caption{Rates of continuous/discrete gap convergence for different LASSO algorithms with 128, 256, or 512 pixels.
 The `adaptive' method uses the proposed algorithm.
@@
 	The minimisers are related by $\varf0^* = \tens{W}\hat{\varf0}^*$ and, for wavelet bases, $\tens{W}$ is orthonormal so $\norm{\A\tens{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$. 
-	\edit{}{ In this example we consider the smoothed robust fidelity 
+	\edit{}{ In this example we consider the smoothed robust fidelity \cite{Rosset2007}
 		\begin{equation}
@@
 		\end{equation}
-	\todo{Reference for robust fidelity?}
 	}	
@@
 
-	\subsection{2D continuous Lasso}
+	\subsection{2D continuous LASSO}
 	Our final application is a super-resolution/de-blurring inverse problem from biological microscopy.
@@
 Readers are directed to the references \cite{Sage2015,Sage2019,Schermelleh2019} for further details.
-The Lasso formulation \edit{}{($\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$) }has previously been shown to be effective in the context of STORM \cite{Huang2017,Denoyelle2019}.
+The LASSO formulation \edit{}{($\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$) }has previously been shown to be effective in the context of STORM \cite{Huang2017,Denoyelle2019}.
 
 	Here we use a simulated dataset provided as part of the 2016 SMLM challenge\footnote{\url{http://bigwww.epfl.ch/smlm/challenge2016/datasets/MT4.N2.HD/Data/data.html}} for benchmarking software in this application.
-The corresponding Lasso formulation is
+The corresponding LASSO formulation is
 	\begin{equation}
@@
 The adaptive scheme used fewer than $10^4$ pixels per frame, a fixed discretisation with equivalent resolution of \SI{1.3}{\nano\meter} would have required more than $3\cdot10^6$ per frame.
-Lasso is compared with ThunderSTORM \cite{Ovesny2014}, a popular ImageJ plugin \cite{Schindelin2012} which finds the location of signal using Fourier filtering.
+LASSO is compared with ThunderSTORM \cite{Ovesny2014}, a popular ImageJ plugin \cite{Schindelin2012} which finds the location of signal using Fourier filtering.
 The performance of ThunderSTORM was rated very highly in the initial SMLM challenge \cite{Sage2015}.
 Both methods compared here demonstrate the key structures of the reconstruction, however, both are sensitive to tuning parameters.
-In this examples, Lasso has possibly recovered too little signal and ThunderSTORM contains spurious signal.
+In this examples, LASSO has possibly recovered too little signal and ThunderSTORM contains spurious signal.
 
@@
 		\caption{Processed results of the STORM dataset.
-Top left: Lasso optimisation with Algorithm~\ref{alg: refining FISTA}.
+Top left: LASSO optimisation with Algorithm~\ref{alg: refining FISTA}.
 Top right: Comparison with ThunderSTORM plugin.
@@
 
-	An interesting observation over all of the adaptive Lasso examples is that the standard oscillatory behaviour of FISTA has not occurred.
+	An interesting observation over all of the adaptive LASSO examples is that the standard oscillatory behaviour of FISTA has not occurred.
 With the monotone gaps plotted, oscillatory convergence should correspond to a piecewise constant descending gap.

### 2021-10-03 paper.tex
Updated Haar example and code

@@
 
-	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n=0,1,\ldots$.
+	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n\in\F N$.
 The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\spcf0^n$.
-If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{original} algorithm.
+If $\spcf0^n\edit{=\spcf0}{}=\F H$, then we recover the \edit{standard FISTA}{original} algorithm.
+\edit{}{More generally, the idea is that $\spcf0^n$ are `growing', for example $\spcf0^n\subset\spcf0^{n+1}$, but this assumption is not necessary in most of the results.}
 
@@
 The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely.
-	\edit{}{Throughout this section we consider a sequence $(\spcf0^n)_{n\in\F N}$ which generate the iterates $(\varf0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} satisfying
+	\edit{}{Throughout this section we consider a sequence $(\spcf0^n)_{n\in\F N}$ which generate the iterates $(\varf0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} such that
 	\begin{equation}\label{eq: refining subspace definition}
-		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{are closed, convex, locally compact subsets for all }\quad n\in\F N.
+		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{where }\spcf0^n\text{ is a closed, convex, locally compact subset for all } n\in\F N.
 	\end{equation}}
@@
 		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
-	}{Clearly $\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2}$ is a constant, the second term is bounded by
+	}{Clearly $\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2}$ is a constant. For the second term, recall $\Norm{\varf2}\leq \Norm{\varf0}$, therefore we can bound
 	\begin{equation}
@@
 	\begin{equation}
-		\F{X}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{50},-\tfrac12+\tfrac{i}{50}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I \quad \text{ for } i,I=1,2,\ldots,50.
-	\end{equation}
-	This is not exactly in the form analysed by Theorem~\ref{thm: norm bound examples}, however only the sets $\{\F{X}^I_i\st i\in[50]\}$ for each $I$ are disjoint, therefore we apply Theorem~\ref{thm: norm bound examples} block-wise to estimate
-	\begin{equation}
-		\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[50]} |\F{X}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[50]} \int_{\F{X}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[50]}\ (\A\1)_{i,I}}\;.
+		\F{X}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{100},-\tfrac12+\tfrac{i}{100}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I
+	\end{equation}
+	for $i=1,\ldots,50$, $I=1,\ldots,100$.
+	This is not exactly in the form analysed by Theorem~\ref{thm: norm bound examples}, however only the sets $\{\F{X}^I_i\st i\in[100]\}$ for each $I$ are disjoint, therefore we apply Theorem~\ref{thm: norm bound examples} block-wise to estimate
+	\begin{equation}
+		\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[100]} |\F{X}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[100]} \int_{\F{X}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[100]}\ (\A\1)_{i,I}}\;.
 	\end{equation}
@@
 	We consider two phantoms where the ground-truth is either a binary disc or the Shepp-Logan phantom.
-No noise is added to the Shepp-Logan data but \SI{5}{\percent} \edit{Gaussian white}{Laplace distributed} noise is added to the disc data.
-This is visualised in Figure~\ref{fig: haar data}.
-All optimisations shown will be spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$.
+\edit{No noise is added to the Shepp-Logan data but 5\% Gaussian white noise is added to the disc data.}{Both examples are corrupted with \SI{2}{\percent} Laplace distributed noise.} This is visualised in Figure~\ref{fig: haar data}.
+All optimisations shown are spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$.
 The gradient metric shown throughout is the $\ell^2$ norm.
@@
 In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower.
+\edit{}{Interestingly, in both examples the $a=20$ variant uses half as many wavelets as the Greedy variant, and therefore converges slightly faster in time.
+}
 
@@
 		\caption{Phantoms\edit{ and}{,} data \edit{used }{and reconstructions }for wavelet-sparse tomography optimisation.
-The Shepp-Logan data is exact but the data for the disc-phantom has \SI{5}{\percent}\ \edit{Gaussian white}{Laplace distributed} noise.
-Without noise the data would be uniform with respect to the angle.}\label{fig: haar data}
+\edit{The Shepp-Logan data is exact but the data for the disc-phantom has}{Both examples are corrupted with} \SI{2}{\percent}\ \edit{Gaussian white}{Laplace distributed} noise.
+}\label{fig: haar data}
 

### 2021-10-03 code/ada_haar.py

@@ -4,47 +4,44 @@ Created on 7 Sep 2020
 @author: Rob Tovey
 '''
 
-from haar_bin import (Radon_to_sparse_matrix, Radon_update_sparse_matrix, _smallgrad, 
-                      _discretise1D, _from_discrete1D, _discretise2D, _from_discrete2D,
+from haar_bin import (Radon_to_sparse_matrix, Radon_update_sparse_matrix, _smallgrad,
                       len_intersect, line_intersect_square, jit, prange, __pparams,
-                      _FP_leaf, _FP_wave2leaf, _BP_leaf, _BP_leaf2wave)
+                      _FP_tomo, _BP_tomo, _gradF)
 from matplotlib import pyplot as plt
-from numpy import (array, empty, sqrt, zeros, isscalar, array_equal, concatenate,
-                   cos, sin, pi, log, nanmin, nanmax, log2, random)
-from anytree import Node, RenderTree, PreOrderIter, PostOrderIter
+from numpy import (array, empty, sqrt, zeros, cos, sin, pi, nanmin, nanmax, ones, random, log2)
+from anytree import Node, PreOrderIter
 from algorithms import shrink, stopping_criterion, faster_FISTA, \
     _makeVid, FB, Norm, FISTA
-from pymorton import interleave
-from lasso import op
+from lasso import op, sparse_matvec
+from adaptive_spaces import Haar_FS as Haar_space, Haar_function as Haar
 from scipy.sparse import csr_matrix
 
-@jit(['void(F[:],F[:],F[:],I[:,:],b1[:],F[:])'.replace('F', 'f8').replace('I', 'i4')], **__pparams)
-def _unknown_grad_denoising(r, grid, L, dof_map, is_leaf, out):
+
+@jit(**__pparams)
+def _unknown_grad_denoising(r, grid, L, dof_map, isleaf, out):
     '''
     df/du_j = sum_I <w_j,k_I>r_I
     Orthogonality of k_I gives:
     |df/du_j|^2 <= sum_I |w_j|^2 |k_I 1_{supp(w_j)}|^2 |r_I|^2
                  = sum_I |k_I 1_{supp(w_j)}|^2 |r_I|^2
     '''
-
     for i in prange(dof_map.shape[0]):
-        if is_leaf[i]:
+        if isleaf[i]:
             # only leaves have errors
-            j = dof_map[i]
[…]

### 2021-10-03 code/adaptive_spaces.py

@@ -7,14 +7,14 @@ import numpy as np
 from matplotlib import pyplot as plt
 from matplotlib.ticker import FixedLocator
 from numba import jit, prange
+from numpy import log2
+from numba.typed import List
 __params = {'nopython':True, 'parallel':False, 'fastmath':True, 'cache':True}
 __pparams = __params.copy(); __pparams['parallel'] = True
 __cparams = __params.copy(); __cparams['cache'] = False
 EPS, FTYPE = 1e-25, 'float64'
 
-# region ########################################
-# Numba wrapping of pymorton
-# endregion #####################################
+pass  # Numba wrapping of pymorton
 
 from pymorton import __part1by1, __part1by2, __unpart1by1, __unpart1by2
 pm_p1b1, pm_p1b2, pm_u1b1, pm_u1b2 = [jit()(f) for f in (__part1by1, __part1by2, __unpart1by1, __unpart1by2)]
@@ -42,9 +42,9 @@ def deinterleave3(i, j, k, out):
     out[2] = pm_u1b2(k) >> 2
 
 
-# region ########################################
-# Adaptive meshing
-# endregion #####################################
+pass  # Adaptive meshing
+
+
 class adaptive_mesh:  # odl RectPartition
 
     def __init__(self, init=0, dim=1, coarse_level=5, _parent=None):
@@ -61,20 +61,23 @@ class adaptive_mesh:  # odl RectPartition
         self.coarse_level = coarse_level
 
         # TODO: this needs better stability/robustness/utilisation
+        # Tracks which mesh is the 'newest'
         self.parent = _parent
         self.age = 0 if _parent is None else _parent.age + 1
 
         self.__buf = [np.zeros([1] * dim, dtype='int32'), np.zeros([1, dim], dtype='int32')]
 
-        if type(init) is int:
+        # dof_map[i] = (x,y,...,h) position and size of pixel i
+        # h = minimum pixel size
+        if type(init) is int:  # produce uniform mesh with <init> refinements
             self.dof_map = np.array([(0,) * dim + (1,)], dtype=FTYPE)
             self.h = 1
             for _ in range(init):
                 self.refine()
-        elif init.shape[0] == 0:
+        elif init.shape[0] == 0:  # empty initialisation, only 1 big pixel
             self.dof_map = np.array([(0,) * dim + (1,)], dtype=FTYPE)
             self.h = 1
-        else:
[…]

### 2021-10-03 code/haar_bin.py

@@ -3,161 +3,18 @@ Created on 9 Apr 2020
 
 @author: Rob
 '''
-from numba import jit, prange, i4, i8, f8
+from numba import jit, prange
 from numpy import array, sqrt
 _PARALLEL = True
 __params = {'nopython':True, 'parallel':False, 'fastmath':True, 'cache':True, 'boundscheck':False}
 __pparams = __params.copy(); __pparams['parallel'] = True
-__cparams = __params.copy(); __cparams['cache'] = False
 
-_compiled = {}
 
-@jit(['F(F,F,F,F)'.replace('F', 'f8')], **__params)
+@jit(**__params)
 def len_intersect(x0, x1, y0, y1): return max(min(x1, y1) - max(x0, y0), 0)
 
 
-@jit(**__cparams)
-def _discretise1D(value, arr, dof_map, level, out):
-    if arr.shape[0] == 0:
-        out[:] = value
-        return
-
-    i = 2  # skip root and first child
-    while i < dof_map.shape[0]:
-        if dof_map[i, 0] == level + 1:
-            break
-        i += 1
-
-    scale, N = 2 ** ((level - 1) / 2), out.shape[0] // 2
-    _discretise1D(value - scale * arr[0], arr[1:i], dof_map[1:i],
-                     level + 1, out[:N])
-    _discretise1D(value + scale * arr[0], arr[i:], dof_map[i:],
-                     level + 1, out[N:])
-
-
-@jit(**__cparams)
-def _from_discrete1D(arr, dof_map, level, out):
-    if arr.shape[0] == 1:
-        out[:] = 0
-        return arr[0] * 2.** (1 - level)
-    elif arr.shape[0] == 0:
-        out[:] = 0
-        return 0
-    elif out.shape[0] == 0:
-        value = 0
-        for i in range(arr.size):
-            value += arr[i]
-        return value / arr.size * 2.** (1 - level)
-
-    i = 2  # skip root and first child
-    while i < dof_map.shape[0]:
-        if dof_map[i, 0] == level + 1:
-            break
-        i += 1
-
-    scale, N = 2 ** ((level - 1) / 2), arr.shape[0] // 2
-    value0 = _from_discrete1D(arr[:N], dof_map[1:i], level + 1, out[1:i])
-    value1 = _from_discrete1D(arr[N:], dof_map[i:], level + 1, out[i:])
-
-    out[0] = scale * (-value0 + value1)
[…]

### 2021-10-03 code/lasso.py

@@ -20,8 +20,8 @@ from numpy import (empty, array, zeros, isscalar, log, pi, sqrt, log10,
 from scipy.sparse import csr_matrix
 from numpy.linalg import norm
 from matplotlib import pyplot as plt
-from sparse_bin import (jit, FTYPE, ker2mat1, ker2mat2, ker2func1, ker2func2, ker2meshmat2,
-    ker2meshfunc2, _blur_coarse)
+from sparse_bin import jit, FTYPE, _blur_coarse
+from sparse_ops import func, kernelMap, op, ker2meshmat2, ker2meshfunc2, sparse_matvec
 from math import (exp as c_exp, erf as c_erf, sin as c_sin, cos as c_cos, sqrt as c_sqrt, floor)
 from algorithms import (stopping_criterion, faster_FISTA, _makeVid,
     FB, shrink, shrink_vec, FISTA)
@@ -109,196 +109,6 @@ class const_plus_func(Array):
             assert len(like) == 2
             c, f = like[0], self.f.copy(like[1])
         return const_plus_func(c, f)
-
-
-class func:
-
-    def __init__(self, y, handles):
-        self.y = y
-        self.func = handles
-        self.__norm = {}
-
-    # Evaluate the function on the mesh depending on flag:
-    #    default: evaluate average per pixel
-    #    flag=1: evaluate at midpoint per pixel
-    #    flag=2: evaluate gradiant at midpoint per pixel
-    def discretise(self, dof_map, flag=0):
-        if flag == 2 and dof_map.shape[1] > 2:
-            out = empty((dof_map.shape[0], dof_map.shape[1] - 1), dtype=FTYPE)
-        else:
-            out = empty(dof_map.shape[0], dtype=FTYPE)
-
-        if flag == 1:
-            self.func['eval_mesh'](out, self.y, dof_map)
-        elif flag == 2:
-            self.func['grad_mesh'](out, self.y, dof_map)
-        else:
-            self.func['av_mesh'](out, self.y, dof_map)
-        return out
-
-    # Return upper bound of |d^kf|_\infty
-    def norm(self, k):
-        if k not in self.__norm:
-            self.__norm[k] = self.func['norm'](self.y, k)
-        return self.__norm[k]
-
-    # Estimate |f|_\infty given mesh
-    def max_abs(self, dof_map):
-        out = empty(dof_map.shape[0], dtype=FTYPE)
-        self.func['max_abs'](out, self.y, dof_map, self.norm(2))
-        return out
-
[…]

### 2021-10-03 code/sparse_bin.py

@@ -5,7 +5,6 @@ Created on 4 Jun 2020
 '''
 from numba import jit, prange
 from math import sqrt as c_sqrt
-_PARALLEL = True
 __params = {'nopython':True, 'parallel':False, 'fastmath':True, 'cache':True}
 __pparams = __params.copy(); __pparams['parallel'] = True
 EPS, FTYPE = 1e-25, 'float64'
@@ -62,669 +61,4 @@ def _merge2D(old, old_DM, OLD, OLD_DM, new, new_DM):
         I += 1; j += 1
 
     return j
-
-__params = __params.copy(); __params['cache'] = False
-__pparams = __pparams.copy(); __pparams['cache'] = False; __pparams['parallel'] = _PARALLEL
-# def jit(*args, **kwargs): return lambda a: a
-
-
-def ker2func1(base_eval, base_grad, base_int):
-
-    ##################################################
-    # r(t) = sum y_j ker_j(t)
-    ##################################################
-    # Pixel-wise functions
-    @jit(**__params)
-    def eval_int(y, p0, p1):
-        ''' v = int_{p0}^{p1} r(t) dt '''
-        v = 0
-        for j in range(y.size):
-            v += y[j] * base_int(j, p0, p1)
-        return v
-
-    @jit(**__params)
-    def eval_mid(y, p0, p1):
-        ''' v = r((p0+p1)/2) '''
-        p = .5 * (p0 + p1)
-        v = 0
-        for j in range(y.size):
-            v += y[j] * base_eval(j, p)
-        return v
-
-    @jit(**__params)
-    def eval_grad(y, p):
-        ''' v[i] = \partial_i r(p) '''
-        v = 0
-        for j in range(y.size):
-            v += y[j] * base_grad(j, p)
-        return v
-
-    ##################################################
-    # mesh functions
-    @jit(**__pparams)
-    def int_mesh(v, y, dof_map):
-        ''' v[i] = \int_i0^i1 r(t) dt '''
-        for i in prange(dof_map.shape[0]):
-            v[i] = eval_int(y, dof_map[i, 0], dof_map[i, 0] + dof_map[i, 1])
-
-    @jit(**__pparams)
-    def av_mesh(v, y, dof_map):
[…]

### 2021-10-05 response.tex
New results and explanation

@@
 
-	This has been clarified in the text, now equations (15) and (21)-(24).
+	This has been clarified in the text, now equations (15) and (20)-(21).
 The $\lVert\cdot\rVert_\infty$ only appears as the dual-norm of our ${\vert\kern-0.25ex\vert\kern-0.25ex\vert \cdot \vert\kern-0.25ex\vert\kern-0.25ex\vert}$.
@@
 Consequently, we also realised that the orthogonal projection was not required either, we now allow $U^n$ to be subsets of $\F H$ rather than subspaces.
-The Banach space setting is reserved for examples discussed in Sections 5 to 7.
+The Banach space setting is reserved for examples discussed in Section 5 onwards.
 
@@
 
-	We apologise for the mistake, the numbering has now been updated.
+	We apologise for the mistake, the numbering has now been corrected.
 

### 2021-10-05 paper.tex
New results and explanation

@@
 	\end{lemma}
-	\noindent This is exactly the result of \cite{Chambolle2015} on the \edit{subspace}{subset} $\spcf0^n$.
+	\noindent The proof is exactly the same as in \cite{Chambolle2015} on the \edit{subspace}{subset} $\spcf0^n$.
 Applying Lemma~\ref{thm: descent lemma} to the iterates from Algorithm~\ref{alg: refining FISTA} gives a more explicit inequality.
@@
 All optimisations shown are spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$.
-The gradient metric shown throughout is the $\ell^2$ norm.
+The gradient metric shown throughout is the $\ell^\infty$ norm.
 Motivated by \eqref{eq: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ to ensure that
@@
 	for all $j$ and $n$ (i.e. so that the continuous gradient is less than 10 times the discrete gradient).
-
-	The first numerical results shown in Figure~\ref{fig: haar convergence} compare the same adaptive algorithms as shown in Figure~\ref{fig: convergence with method}.
+	\edit{}{We do not expect wavelet regularisation to have state-of-the-art performance in the examples of Figure~\ref{fig: haar data}.
+What they demonstrate is the preference Haar wavelets have to align large discontinuities with a coarse grid, even when the discretisation is allowed to be as fine as necessary.
+There is an average of $2\cdot10^6$ wavelet coefficients in each discretised reconstruction, although the higher frequencies have much smaller intensities.
+In limited data scenarios, wavelet regularisation automatically selects a local `resolution' which reflects the quality of data.
+Particularly in the Shepp-Logan reconstruction, we see that the outer ring is detected with a finer precision than the dark interior ellipses.}
+
+	The first numerical results shown in Figure~\ref{fig: haar convergence} compare the same adaptive FISTA variants as shown in Figure~\ref{fig: convergence with method}.
 In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower.

### 2021-10-05 response.tex
edited response

@@
 \begin{enumerate}
-	\item \review{The authors base much of the analysis on the objective function and its convergence properties \ldots it would be interesting to know how the solutions $w_n$ converge for the various versions of FISTA.}
+	\item \review{The authors base much of the analysis on the objective function and its convergence properties \ldots it would be interesting to know how the solutions $u_n$ converge for the various versions of FISTA.}
 
@@
 As in your comment, if one has coercivity then the convergence is clear.
-More generally, FISTA is known to converge weakly in the Hilbert-space setting.
-This is also likely to hold with our algorithm when the minimiser is in $\F H$, but we have not verified this special case.
-A key component of the proof is the bound $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, in general we do not even expect this quantity to be bounded.
-It's not clear whether we can leverage the Hilbert-norm structures of FISTA to gain any convergence in the Banach space.
-In the LASSO case we know that the sequence is bounded in the L1 norm, so a subsequence must converge weakly, however, it's still unclear how to upgrade from convergence of a sub-sequence to full convergence.
+Similarly, if one has compact sub-levelsets (e.g.
+LASSO), then one has convergence of a sub-sequence.
+
+	In the general Hilbert space setting we know FISTA iterates converge weakly (for certain variants).
+The same result is likely to hold with our adaptivity when the minimiser is in $\F H$, although we haven't verified this special case.
+The standard proof (e.g.
+[10]) relies on the bound $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, i.e.
+vanishing stepsize in the Hilbert norm, but in general we only expect this quantity to be bounded.
+It's not clear whether we can adapt the argument to gain any convergence in the Banach space.
 

### 2021-10-05 paper.tex
edited response

@@
 	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$.
-\edit{}{Note in particular we need the argmin to be non-empty.
-For this we will assume $\spcf0^n$ are locally compact, for example finite dimensional.}
+\edit{}{Closed subsets of $\F H$ are locally weakly compact, therefore this argmin is always non-empty.}
 
@@
 	\begin{equation}\label{eq: refining subspace definition}
-		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{where }\spcf0^n\text{ is a closed, convex, locally compact subset for all } n\in\F N.
+		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{where }\spcf0^n\text{ is a closed, convex subset for all } n\in\F N.
 	\end{equation}}
@@
 	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$.
-\edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing.
-Therefore }
+\edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing, therefore }
 	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have

### 2021-10-06 response.tex
update

@@
 	We thank the reviewer for their suggestion but it seems quite challenging to make a general statement.
-As in your comment, if one has coercivity then the convergence is clear.
-Similarly, if one has compact sub-levelsets (e.g.
-LASSO), then one has convergence of a sub-sequence.
+As in your comment, if one has coercivity then the sequence convergences strongly.
+Similarly, if one has (weakly) compact sub-levelsets, such as in the LASSO examples, then a sub-sequence converges (weakly).
 
-	In the general Hilbert space setting we know FISTA iterates converge weakly (for certain variants).
-The same result is likely to hold with our adaptivity when the minimiser is in $\F H$, although we haven't verified this special case.
-The standard proof (e.g.
-[10]) relies on the bound $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, i.e.
-vanishing stepsize in the Hilbert norm, but in general we only expect this quantity to be bounded.
-It's not clear whether we can adapt the argument to gain any convergence in the Banach space.
+	Of course there are variants of FISTA that guarantee weak convergence in the Hilbert space setting without any further coercivity or compactness assumptions.
+It is likely that the same arguments (e.g.
+[10]) can be made for our adaptive algorithm in a Hilbert space, although we haven't verified this special case.
+It is beyond the scope of this work to extend these results into the generalised setting and at the moment the question does not appear to be trivial.
 
@@
 The analysis of the algorithm in the first half of the manuscript is now performed without mention of a Banach space.
-Consequently, we also realised that the orthogonal projection was not required either, we now allow $U^n$ to be subsets of $\F H$ rather than subspaces.
+Consequently, we also realised that the subspace structure and orthogonal projection were not required either.
+We now allow $U^n$ to be closed convex subsets of $\F H$.
 The Banach space setting is reserved for examples discussed in Section 5 onwards.

### 2021-10-13 response.tex
Added Data statement section

@@
 \documentclass[12pt]{article}
-\usepackage[cm]{fullpage}
+\usepackage[in]{fullpage}
 \usepackage{amsmath,amsfonts,color}
@@
 \newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
-\newcommand{\todo}[1]{{\color{red} #1}}
 
@@
 \author{Antonin Chambolle and Robert Tovey}
-\date{\todo{31st October 2021}}
+\date{7th October 2021}
 
@@
 	You are right, we can also consider alternative misfits.
-We have replaced the wavelet example in Section 7.2 with a (Huber-smoothed) robust $\ell^1$ penalty as we only explicitly required the gradient and Lipschitz constant for computations.
-This also led to a number of small updates to the analysis in Section 6 to generalise to a non-quadratic misfit.
+We have replaced the wavelet example in Section 7.2 with a (Huber-smoothed) robust $\ell^1$ penalty.
+This also led to a number of small updates to the analysis in Section 6 to generalise for a non-quadratic misfit.
 

### 2021-10-13 paper.tex
Added new reference
Added Data statement section

@@
 
+% Define `data availability' environment like acknowledgement
+\def\datavname{Data availability statement}%
+\def\datav{\par\addvspace{17pt}\small\rmfamily
+	\trivlist\if!\datavname!\item[]\else
+	\item[\hskip\labelsep
+	{\bfseries\datavname}]\fi}
+\def\enddatav{\endtrivlist\addvspace{6pt}}
+\newenvironment{dataavailability}{\begin{datav}}
+	{\end{datav}}
+
 \usepackage{amsmath,enumitem,datetime,xfrac,fix-cm,color,multirow,siunitx}
@@
 \usepackage{algorithm,algpseudocode}
-\graphicspath{{Figures/}}
+%\graphicspath{{Figures/}}
 \DeclareGraphicsExtensions{.pdf,.png}
@@
 \DeclareMathOperator{\sign}{sign}
-\newcommand{\Emin}[1][\varf0]{\inf_{#1\in\F H}\op{E}(#1)}
+\newcommand{\Emin}[1][\var0]{\inf_{#1\in\F H}\op{E}(#1)}
 
@@
 
-% TODO: get rid of this stuff...
 \usepackage{clipboard}\newclipboard{aFEMclipboard}
+\newcommand{\data}{\eta}
+\newcommand{\Domain}{\Omega}\newcommand{\domain}{\omega}
+\newcommand{\diam}{\op{diam}}
+\newcommand{\meshsize}{h}
+
 \usepackage{xstring}
-\newcommand*{\varf}[1]{%
+% Function variable names
+\newcommand*{\var}[1]{%
 	\IfEqCase{#1}{%
@@
 }
-\newcommand*{\Varf}[1]{%
-	\IfEqCase{#1}{%
-		{0}{U}%
-		{1}{V}%
-		{2}{W}%
-	}[u#1]%
-}
-\newcommand*{\spcf}[1]{%
-	\IfEqCase{#1}{%
-		{0}{\F{U}}%
-		{1}{\F{V}}%
-		{2}{\F{W}}%
-	}[\F{U}#1]%
-}
-\newcommand*{\vard}[1]{%
-	\IfEqCase{#1}{%
-		{0}{\varphi}%
-		{1}{\psi}%
-	}[\varphi #1]%
-}
-\newcommand*{\varx}[1]{%
-	\IfEqCase{#1}{%
-		{0}{x}%
-		{1}{y}%
-		{2}{z}%
-		{3}{r}%
-	}[x#1]%
-}
+% Scalar and vector variable names
 \newcommand*{\vars}[1]{%
@@
 }
-\newcommand*{\Vars}[1]{%
-	\IfEqCase{#1}{%
-		{0}{\mathrm{A}}%
-		{1}{\mathrm{B}}%
-		{2}{\Gamma}%
-		{3}{A}%
-		{4}{B}%
-		{5}{C}%
-	}[K#1]%
-}
-\newcommand{\data}{\eta}
-\newcommand{\Domain}{\Omega}\newcommand{\domain}{\omega}
-\newcommand{\diam}{\op{diam}}
-\newcommand{\meshsize}{h}
-
-% vector forms
-\newcommand*{\vvarx}[1]{\vec{\varx{#1}}}
 \newcommand*{\vvars}[1]{\vec{\vars{#1}}}
-\newcommand*{\vvard}[1]{\vec{\vard{#1}}}
 
@@
 \newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
-%\renewcommand{\edit}[2]{#2}
-\newcommand{\todo}[1]{{\color{red}#1}}
+\renewcommand{\edit}[2]{#2}
+%\newcommand{\todo}[1]{{\color{red}#1}}
 
@@
 	\begin{equation}\label{eq: min F = fD+fC}
-		\edit{u^* \in \argmin_{\varf0\in\F H}\op{E}(\varf0)}{\Emin}  \qquad\text{such that}\qquad \op{E}(\varf0)\coloneqq \op{f}(\varf0) + \op{g}(\varf0),
+		\edit{u^* \in \argmin_{\var0\in\F H}\op{E}(\var0)}{\Emin}  \qquad\text{such that}\qquad \op{E}(\var0)\coloneqq \op{f}(\var0) + \op{g}(\var0),
 	\end{equation}
 	where $\op{f}\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\op{g}\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
-The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$.
-It has been shown that $\op{E}(\varf0_n) - \edit{\op{E}(u^*)}{\Emin}$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}.
+The iterates of the FISTA algorithm will be denoted $\var0_n\in\F H$.
+It has been shown that $\op{E}(\var0_n) - \edit{\op{E}(u^*)}{\Emin}$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}.
 Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \cite{Tao2016,Liang2017,Alamo2019}.
@@
 	\begin{itemize}
-		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved.
-For example, in \edit{Lasso}{L1 penalised reconstructions} discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}.
+		\item we extend the convergence results to the case \edit{$\var0^*\in\bar{\F H}\setminus\F H$ where $\F{U}\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved.
+For example, in \edit{Lasso}{L1 penalised reconstructions} discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\F{U}\supset\F H$ such that $\Emin = \min_{\var0\in\F{U}}\op{E}(\var0)$ is achieved in $\F{U}\setminus\F H$}.
 The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
-		\item we allow for adaptive discretisation such that $\varf0_n\in\spcf0^n\subset\F H$.
+		\item we allow for adaptive discretisation such that $\var0_n\in\F{U}^n\subset\F H$.
 With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence.
@@
 The permitted refinement steps are also more broad in our work.
+\cite{}{Very recent work in \cite{Yu2021} proposes a `Multilevel FISTA' algorithm which allows similar coarse-to-fine refinement strategies, although only a finite number.
+We also allow for non-uniform refinement with a posteriori strategies.}
 
@@
 The main theoretical contribution of this work is the convergence analysis of Algorithm~\ref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in Section~\ref{sec: recipe}, then we state the specific results in the case of FISTA in Section~\ref{sec: FISTA convergence}.
-The main results are Theorems~\ref{thm: exponential FISTA convergence}/\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.
+The main results are Theorems~\ref{thm: exponential FISTA convergence}/\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\F{U}^n$ respectively.
 
 	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} \edit{}{in Banach spaces }and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation.
-In particular, we describe how to choose efficient refining discretisations to approximate \edit{$\varf0^*$}{$\Emin$}, estimate the convergence of $\op{E}$, and identify the support of \edit{$\varf0^*$}{the minimiser}.
+In particular, we describe how to choose efficient refining discretisations to approximate \edit{$\var0^*$}{$\Emin$}, estimate the convergence of $\op{E}$, and identify the support of \edit{$\var0^*$}{the minimiser}.
 The numerical results in Section~\ref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.
@@
 	\section{Definitions and notation}\label{sec: prelims}
-	\edit{We consider optimisation of \eqref{eq: min F = fD+fC} over two spaces, the Banach space $(\spcf0,\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
-	\\\centerline{$\displaystyle \exists\varf0^*\in \spcf0 \quad\st\quad \op{E}(\varf0^*) = \min_{\varf0\in\spcf0}\op{E}(\varf0) = \inf_{\varf0\in\F H}\op{E}(\varf0).$}
+	\edit{We consider optimisation of \eqref{eq: min F = fD+fC} over two spaces, the Banach space $(\F{U},\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
+	\\\centerline{$\displaystyle \exists\var0^*\in \F{U} \quad\st\quad \op{E}(\var0^*) = \min_{\var0\in\F{U}}\op{E}(\var0) = \inf_{\var0\in\F H}\op{E}(\var0).$}
 	Furthermore, define the translated energy
-	\\\centerline{$\displaystyle \op{E}_0\colon\spcf0\cup\F H\to \R,\qquad \op{E}_0(\varf0) \coloneqq \op{E}(\varf0)-\op{E}(\varf0^*).$}
-	Note that the value of $\op{E}_0$ is uniquely defined, even if $\varf0^*$ may not be.%
+	\\\centerline{$\displaystyle \op{E}_0\colon\F{U}\cup\F H\to \R,\qquad \op{E}_0(\var0) \coloneqq \op{E}(\var0)-\op{E}(\var0^*).$}
+	Note that the value of $\op{E}_0$ is uniquely defined, even if $\var0^*$ may not be.%
 	\\}{%
@@
 	\begin{equation}
-		\op{E}_0\colon\F H\to \R,\qquad \op{E}_0(\varf0) \coloneqq \op{E}(\varf0)-\Emin[\tilde{\varf0}].
+		\op{E}_0\colon\F H\to \R,\qquad \op{E}_0(\var0) \coloneqq \op{E}(\var0)-\Emin[\tilde{\var0}].
 	\end{equation}
@@
 
-	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n\in\F N$.
-The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\spcf0^n$.
-If $\spcf0^n\edit{=\spcf0}{}=\F H$, then we recover the \edit{standard FISTA}{original} algorithm.
-\edit{}{More generally, the idea is that $\spcf0^n$ are `growing', for example $\spcf0^n\subset\spcf0^{n+1}$, but this assumption is not necessary in most of the results.}
+	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\F{U}^n\subset \edit{\F{U}\cap}{}\F H$ for $n\in\F N$.
+The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\F{U}^n$.
+If $\F{U}^n\edit{=\F{U}}{}=\F H$, then we recover the \edit{standard FISTA}{original} algorithm.
+\edit{}{More generally, the idea is that $\F{U}^n$ are `growing', for example $\F{U}^n\subset\F{U}^{n+1}$, but this assumption is not necessary in most of the results.}
 
@@
 	\begin{equation}
-		\norm{\nabla\op{f}(\varf0)- \nabla\op{f}(\varf1)} \leq \norm{\varf0-\varf1}
-	\end{equation}
-	for all $\varf0,\varf1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
-	\begin{equation}
-		\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \op{g}(\varf0)
-	\end{equation}
-	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$.
+		\norm{\nabla\op{f}(\var0)- \nabla\op{f}(\var1)} \leq \norm{\var0-\var1}
+	\end{equation}
+	for all $\var0,\var1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
+	\begin{equation}
+		\argmin_{\var0\in\tilde{\F{U}}}\tfrac12\norm{\var0-\var1}^2 + \op{g}(\var0)
+	\end{equation}
+	is exactly computable for all $\var1\in\F H$ and all $\tilde{\F{U}}\in\{\F{U}^n\}_{n=0}^\infty$.
 \edit{}{Closed subsets of $\F H$ are locally weakly compact, therefore this argmin is always non-empty.}
@@
 	\edit{Finally we introduce the concept of an orthogonal projection in the setting of this work.
-For a subspace $\spcf0^n\subset\spcf0\cap\F H$ we define the orthogonal projection $\tens{\Pi}_n\colon (\spcf0^n)^*\to \spcf0^n$ to be any extension of the function such that
-	\\\centerline{$\IP{\tens{\Pi}_n\varf0}{\varf1} = \IP{\varf0}{\varf1} \text{ for all } \varf0\in(\spcf0^n)^*, \ \varf1\in\spcf0^n.$}
-	This definition is non-standard as we view $(\spcf0^n)^*$ embedded in $\spcf0$.
-Note that $\spcf0^n\subset\F H$ implies that $(\spcf0^n)^*\supset\F H$, therefore $\tens{\Pi}_n$ is an extension of the classical orthogonal projection.
-It is convenient to allow an extension here because $\spcf0$ may be bigger than $\F H$, $(\spcf0^n)^*$ is the largest space such that $\tens{\Pi}_n$ is sufficiently well-defined.
+For a subspace $\F{U}^n\subset\F{U}\cap\F H$ we define the orthogonal projection $\tens{\Pi}_n\colon (\F{U}^n)^*\to \F{U}^n$ to be any extension of the function such that
+	\\\centerline{$\IP{\tens{\Pi}_n\var0}{\var1} = \IP{\var0}{\var1} \text{ for all } \var0\in(\F{U}^n)^*, \ \var1\in\F{U}^n.$}
+	This definition is non-standard as we view $(\F{U}^n)^*$ embedded in $\F{U}$.
+Note that $\F{U}^n\subset\F H$ implies that $(\F{U}^n)^*\supset\F H$, therefore $\tens{\Pi}_n$ is an extension of the classical orthogonal projection.
+It is convenient to allow an extension here because $\F{U}$ may be bigger than $\F H$, $(\F{U}^n)^*$ is the largest space such that $\tens{\Pi}_n$ is sufficiently well-defined.
 Beyond this, the Hahn-Banach theorem may allow the domain of $\tens{\Pi}_n$ to be extended further, but the definition is no longer unique.
-For example, in 1D the value of $\IP{\delta_0}{\frac{1}{\sqrt[4]{\varx0}}}$ is not well-defined, but the value of $\IP{\delta_0}{\1_{[0,1]}}$ can be chosen to be consistent with some sequence of molifiers.
-To account for this possibility, we shall state that the domain of $\tens{\Pi}_n$ is $\bar{(\spcf0^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.}{}
+For example, in 1D the value of $\IP{\delta_0}{\frac{1}{\sqrt[4]{x}}}$ is not well-defined, but the value of $\IP{\delta_0}{\1_{[0,1]}}$ can be chosen to be consistent with some sequence of molifiers.
+To account for this possibility, we shall state that the domain of $\tens{\Pi}_n$ is $\bar{(\F{U}^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.}{}
 
@@
 	\begin{equation}
-		\Norm{\partial\op{E}(\varf0)} \coloneqq \inf_{\varf1\in\partial\op{E}(\varf0)}\Norm{\varf1}
+		\Norm{\partial\op{E}(\var0)} \coloneqq \inf_{\var1\in\partial\op{E}(\var0)}\Norm{\var1}
 	\end{equation}
@@
 		\begin{algorithmic}[1]
-			\State Choose $(\spcf0^n)_{n\in\F N}$, $\varf0_0\in \spcf0^0$ and some FISTA stepsize choice $(t_n)_{n\in\F N}$
-			\State $\varf1_0\gets \varf0_0, n\gets0$
+			\State Choose $(\F{U}^n)_{n\in\F N}$, $\var0_0\in \F{U}^0$ and some FISTA stepsize choice $(t_n)_{n\in\F N}$
+			\State $\var1_0\gets \var0_0, n\gets0$
 			\Repeat
-			\State $\bar{\varf0}_n \gets (1-\tfrac{1}{t_n})\varf0_n + \tfrac{1}{t_n}\varf1_n$
-			\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \op{f}(\bar{\varf0}_n)}^2+\op{g}(\varf0)$ \Comment{Only modification, $\spcf0^{n+1}\subset \spcf0$}
-			\State $\varf1_{n+1} \gets (1-t_n)\varf0_n + t_n\varf0_{n+1}$
+			\State $\bar{\var0}_n \gets (1-\tfrac{1}{t_n})\var0_n + \tfrac{1}{t_n}\var1_n$
+			\State $\displaystyle \var0_{n+1} \gets \argmin_{\var0\in \F{U}^{n+1}} \tfrac12\norm{\var0-\bar{\var0}_n+\nabla \op{f}(\bar{\var0}_n)}^2+\op{g}(\var0)$ \Comment{Only modification, $\F{U}^{n+1}\subset \F{U}$}
+			\State $\var1_{n+1} \gets (1-t_n)\var0_n + t_n\var0_{n+1}$
 			\State $n\gets n+1$
@@
 	\begin{equation}\label{eq: classical FISTA}
-		t_N^2\op{E}_0(\varf0_N) + \sum^{N-1}_{n=1}\rho_n\op{E}_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf0^*}^2 \leq \tfrac12\norm{\varf0_0-\varf0^*}^2
+		t_N^2\op{E}_0(\var0_N) + \sum^{N-1}_{n=1}\rho_n\op{E}_0(\var0_n) + \tfrac12\norm{\var1_N-\var0^*}^2 \leq \tfrac12\norm{\var0_0-\var0^*}^2
 	\end{equation}
@@
 	\begin{adaptiveStep}\label{step: step 1 stability}
-		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting \edit{subspaces}{subsets} $\spcf0^n$.
+		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting \edit{subspaces}{subsets} $\F{U}^n$.
 In the notation of Algorithm~\ref{alg: refining FISTA}, Theorem~\ref{thm: mini FISTA convergence} shows that
 		\begin{equation}\label{eq: mini FISTA convergence}
-			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf2_N}^2 \leq \tfrac12\norm{\varf0_0-\varf2_0}^2 +\tfrac{\norm{\varf2_N}^2-\norm{\varf2_0}^2}2 
-			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}
-		\end{equation}
-		for any $\varf2_n \in \argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$.
+			t_N^2\op{E}_0(\var0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\var0_n) + \tfrac12\norm{\var1_N-\var2_N}^2 \leq \tfrac12\norm{\var0_0-\var2_0}^2 +\tfrac{\norm{\var2_N}^2-\norm{\var2_0}^2}2 
+			+ \sum^N_{n=1} t_n\op{E}_0(\var2_n) + \IP{\var1_{n-1}}{\var2_{n-1}-\var2_n}
+		\end{equation}
+		for any $\var2_n \in \argmin_{\var0\in\F{U}^n}\op{E}(\var0)$.
 The similarities to \eqref{eq: classical FISTA} are clear.
-If $\spcf0^n=\edit{\spcf0}{\F H}$, then we have $\varf2_n=\edit{\varf0^*}{\varf2_0\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the two estimates agree.
+If $\F{U}^n=\edit{\F{U}}{\F H}$, then we have $\var2_n=\edit{\var0^*}{\var2_0\in\argmin_{\var0\in\F H}\op{E}(\var0)}$ and the two estimates agree.
 These extra terms quantify the robustness to changing of discretisation.
@@
 	\begin{adaptiveStep}\label{step: step 2 smoothness}
-		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\spcf0^n$.
-\edit{}{The idea is that $\spcf0^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\varf0\in\spcf0^n}\op{E}(\varf0) \to \inf_{\varf0\in\F H}\op{E}(\varf0)$.
-A canonical example might be $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq n\}$.} \edit{To do so, we construct}{To quantify the balance between a growing Hilbert norm and improving estimate of $\op{E}$, we introduce} a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
-		\begin{equation}
-			n\leq n_k \implies \norm{\varf2_n} \lesssim \vars3_{\Varf0}^k, \qquad n\geq n_k \implies \op{E}_0(\varf2_n) \lesssim \vars3_{\op{E}}^{-k}.
-		\end{equation}
-		\edit{}{The expanding balls example would become $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq \vars3_{\Varf0}^k\}$, and $\vars3_{\op{E}}$ reflects the smoothness of $\op{E}$ with respect to the Hilbert norm.} The choice of exponential scaling is \edit{very}{more} natural if we consider the $\spcf0^n$ to be the subspace of functions discretised on a uniform mesh.
+		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\F{U}^n$.
+\edit{}{The idea is that $\F{U}^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\var0\in\F{U}^n}\op{E}(\var0) \to \inf_{\var0\in\F H}\op{E}(\var0)$.
+A canonical example might be $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq n\}$.} \edit{To do so, we construct}{To quantify the balance between a growing Hilbert norm and improving estimate of $\op{E}$, we introduce} a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_U,\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
+		\begin{equation}
+			n\leq n_k \implies \norm{\var2_n} \lesssim \vars3_U^k, \qquad n\geq n_k \implies \op{E}_0(\var2_n) \lesssim \vars3_{\op{E}}^{-k}.
+		\end{equation}
+		\edit{}{The expanding balls example would become $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq \vars3_U^k\}$, and $\vars3_{\op{E}}$ reflects the smoothness of $\op{E}$ with respect to the Hilbert norm.} The choice of exponential scaling is \edit{very}{more} natural if we consider the $\F{U}^n$ to be the subspace of functions discretised on a uniform mesh.
 If that mesh is sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$.
@@
 %
-		\edit{The value of $\vars3_{\Varf0}$ is dictated by the smoothness of the norm of $\spcf0$ with respect to that of $\F H$.
-If $\norm{\varf0^*}<\infty$, then the value is $\vars3_{\Varf0}=1$, otherwise there is some damage to the rate of convergence generated by this factor.
-On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ at the point $\varf0^*$.}{The value $\vars3_{\Varf0}$ reflects the smoothness of the chosen basis measured in $\F H$, and $\vars3_{\op{E}}$ is a measure of efficiency with respect to the structure of $\op{E}$.} %
+		\edit{The value of $\vars3_U$ is dictated by the smoothness of the norm of $\F{U}$ with respect to that of $\F H$.
+If $\norm{\var0^*}<\infty$, then the value is $\vars3_U=1$, otherwise there is some damage to the rate of convergence generated by this factor.
+On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ at the point $\var0^*$.}{The value $\vars3_U$ reflects the smoothness of the chosen basis measured in $\F H$, and $\vars3_{\op{E}}$ is a measure of efficiency with respect to the structure of $\op{E}$.} %
 		If an efficient basis is used, then $\vars3_{\op{E}}$ is large.
-The trade-off between $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$ dictates the final convergence rate of the algorithm.
-\edit{}{If $\vars3_{\Varf0}>1$, then we cannot guarantee the original $n^{-2}$ rate of convergence.}
+The trade-off between $\vars3_{\op{E}}$ and $\vars3_U$ dictates the final convergence rate of the algorithm.
+\edit{}{If $\vars3_U>1$, then we cannot guarantee the original $n^{-2}$ rate of convergence.}
 	\end{adaptiveStep}
@@
 	\begin{adaptiveStep}\label{step: step 3 convergence bound}
-		In this step we combine the FISTA stability estimate with the \edit{subspace}{subset} approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$.
-For example, if $\spcf0^n$ is of the form
-		$$ \spcf0^{n_k} = \spcf0^{n_k+1} = \ldots = \spcf0^{n_{k+1}-1},$$
+		In this step we combine the FISTA stability estimate with the \edit{subspace}{subset} approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\op{E}}$ and $\vars3_U$.
+For example, if $\F{U}^n$ is of the form
+		$$ \F{U}^{n_k} = \F{U}^{n_k+1} = \ldots = \F{U}^{n_{k+1}-1},$$
 		then many terms on the right-hand side of \eqref{eq: mini FISTA convergence} telescope to 0.
@@
 		In Step~\ref{step: step 3 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor.
-In particular, it is equivalent to run Algorithm~\ref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed \edit{subspace}{subset} $\spcf0^N$.
-The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\op{E}_0(\varf0_N)\lesssim \norm{\varf0_0-\varf2_N}^2 = O(\vars3_{\Varf0}^{2K})$ for $N\leq n_K$.
-Lemma~\ref{thm: sufficiently fast} shows that Algorithm~\ref{alg: refining FISTA} can achieve the same order of approximation, so long as $\spcf0^n$ refine sufficiently quickly, i.e.
+In particular, it is equivalent to run Algorithm~\ref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed \edit{subspace}{subset} $\F{U}^N$.
+The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\op{E}_0(\var0_N)\lesssim \norm{\var0_0-\var2_N}^2 = O(\vars3_U^{2K})$ for $N\leq n_K$.
+Lemma~\ref{thm: sufficiently fast} shows that Algorithm~\ref{alg: refining FISTA} can achieve the same order of approximation, so long as $\F{U}^n$ refine sufficiently quickly, i.e.
 $n_k$ are sufficiently small.
@@
 		The result of Step~\ref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate.
-If the \edit{subspaces refine}{subsets grow} too quickly, then the influence of \edit{$\norm{\varf0^*}=\infty$}{$\norm{\varf0_n}\to\infty$} will slow the rate of convergence.
+If the \edit{subspaces refine}{subsets grow} too quickly, then the influence of \edit{$\norm{\var0^*}=\infty$}{$\norm{\var0_n}\to\infty$} will slow the rate of convergence.
 If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow.
 Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of
-		$$ \op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
-		for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\op{E}}$.
-In particular, if \edit{$\varf0^*\in\F H$}{the minimum is attained in $\F H$,} then we recover the classical rate with $\kappa=0$.
+		$$ \op{E}_0(\var0_N) \lesssim \frac{\vars3_U^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
+		for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_U,\vars3_{\op{E}}$.
+In particular, if \edit{$\var0^*\in\F H$}{the minimum is attained in $\F H$,} then we recover the classical rate with $\kappa=0$.
 	\end{adaptiveStep}
@@
 	\begin{adaptiveStep}\label{step: step 6 adaptivity}
-		Up to this point we have implicitly focused on the case where $\spcf0^n$ (and $n_k$) are chosen a priori.
+		Up to this point we have implicitly focused on the case where $\F{U}^n$ (and $n_k$) are chosen a priori.
 Here we emphasise some of the challenges which are faced when extending results to allow for greedy adaptivity.
@@
 Lemma~\ref{thm: mini exponential FISTA convergence} shows that a sufficient condition is
-		$$\edit{}{\varf0_{n_k-1}\in}\spcf0^{n_k}\subset\spcf0^{n_k+1}\subset\ldots\subset\spcf0^{n_{k+1}-1}.$$
-		Convergence is most stable if the approximation spaces $\spcf0^n$ satisfy a monotone inclusion, breaking the monotonicity requires more care.
+		$$\edit{}{\var0_{n_k-1}\in}\F{U}^{n_k}\subset\F{U}^{n_k+1}\subset\ldots\subset\F{U}^{n_{k+1}-1}.$$
+		Convergence is most stable if the approximation spaces $\F{U}^n$ satisfy a monotone inclusion, breaking the monotonicity requires more care.
 
 		Adaptively choosing the time of refinement is more challenging due to the non-descent property of FISTA.
-The idea is that $\spcf0^n$ should be refined as soon as the value $\op{E}(\varf0_n)$ is sufficiently close to $\op{E}(\varf2_n)$.
+The idea is that $\F{U}^n$ should be refined as soon as the value $\op{E}(\var0_n)$ is sufficiently close to $\op{E}(\var2_n)$.
 This is analysed in Theorem~\ref{thm: stronger exponential FISTA convergence} (sufficient conditions in Lemma~\ref{thm: practical refinement criteria}) which shows convergence results of the form
-		$$ \min_{n\leq N}\op{E}_0(\varf0_n) \lesssim \frac{N^{2\kappa}}{N^2}$$
+		$$ \min_{n\leq N}\op{E}_0(\var0_n) \lesssim \frac{N^{2\kappa}}{N^2}$$
 		for all $N\in\F N$, with the same $\kappa\in[0,1)$ from Step~\ref{step: step 5 sufficiently slow}.
-The penalty for accelerating the refinement time is a potential loss of stability in $\op{E}(\varf0_n)$, however, the asymptotic rate is equivalent and this behaviour has not been seen in numerical experiments.
+The penalty for accelerating the refinement time is a potential loss of stability in $\op{E}(\var0_n)$, however, the asymptotic rate is equivalent and this behaviour has not been seen in numerical experiments.
 	\end{adaptiveStep}
@@
 The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely.
-	\edit{}{Throughout this section we consider a sequence $(\spcf0^n)_{n\in\F N}$ which generate the iterates $(\varf0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} such that
+	\edit{}{Throughout this section we consider a sequence $(\F{U}^n)_{n\in\F N}$ which generate the iterates $(\var0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} such that
 	\begin{equation}\label{eq: refining subspace definition}
-		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{where }\spcf0^n\text{ is a closed, convex subset for all } n\in\F N.
+		\var0^{n-1}\in\F{U}^n\subset\F H \quad\text{where }\F{U}^n\text{ is a closed, convex subset for all } n\in\F N.
 	\end{equation}}
@@
 		\Copy{thm: descent lemma}{
-			Suppose $\nabla \op{f}$ is 1-Lipschitz, for any $\bar{\varf0}\in \edit{\spcf0^{n}}{\F H}$ define
-			$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \op{f}(\bar{\varf0})}^2+\op{g}(\varf0).$$
-			Then, for all $\varf2\in\edit{\bar{(\spcf0^n)^*}\supset\F H}{\spcf0^n}$, we have
-			\edit{\\\centerline{$\displaystyle \op{E}(\varf0) + \tfrac12\norm{\varf0-\tens{\Pi}_n\varf2}^2 \leq \op{E}(\tens{\Pi}_n\varf2) + \tfrac12\norm{\bar{\varf0}-\tens{\Pi}_n\varf2}^2.$}}{
-			$$\op{E}(\varf0) + \tfrac12\norm{\varf0-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\bar{\varf0}-\varf2}^2.$$}
-			\edit{where $\tens{\Pi}_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.}{}
+			Suppose $\nabla \op{f}$ is 1-Lipschitz, for any $\bar{\var0}\in \edit{\F{U}^{n}}{\F H}$ define
+			$$ \var0 \coloneqq \argmin_{\var0\in \F{U}^{n}} \tfrac12\norm{\var0-\bar{\var0}+\nabla \op{f}(\bar{\var0})}^2+\op{g}(\var0).$$
+			Then, for all $\var2\in\edit{\bar{(\F{U}^n)^*}\supset\F H}{\F{U}^n}$, we have
+			\edit{\\\centerline{$\displaystyle \op{E}(\var0) + \tfrac12\norm{\var0-\tens{\Pi}_n\var2}^2 \leq \op{E}(\tens{\Pi}_n\var2) + \tfrac12\norm{\bar{\var0}-\tens{\Pi}_n\var2}^2.$}}{
+			$$\op{E}(\var0) + \tfrac12\norm{\var0-\var2}^2 \leq \op{E}(\var2) + \tfrac12\norm{\bar{\var0}-\var2}^2.$$}
+			\edit{where $\tens{\Pi}_n\colon\bar{(\F{U}^n)^*}\to\F{U}^n$ is the orthogonal projection.}{}
 		}
 	\end{lemma}
-	\noindent The proof is exactly the same as in \cite{Chambolle2015} on the \edit{subspace}{subset} $\spcf0^n$.
+	\noindent The proof is exactly the same as in \cite{Chambolle2015} on the \edit{subspace}{subset} $\F{U}^n$.
 Applying Lemma~\ref{thm: descent lemma} to the iterates from Algorithm~\ref{alg: refining FISTA} gives a more explicit inequality.
@@
 		\Copy{thm: one step FISTA}{
-			Let \edit{$\spcf0^n\subset\F H\cap\spcf0$, }{}$\varf2_n\in\spcf0^n$ be chosen arbitrarily and $\varf0_n$/$\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA} for all $n\in\F N$.
+			Let \edit{$\F{U}^n\subset\F H\cap\F{U}$, }{}$\var2_n\in\F{U}^n$ be chosen arbitrarily and $\var0_n$/$\var1_n$ be generated by Algorithm~\ref{alg: refining FISTA} for all $n\in\F N$.
 			For all $n\in\F N$, it holds that}
 		\begin{equation}\Copy{thm:eq: one step FISTA}{
-			t_{n}^2(\op{E}(\varf0_{n}) - \op{E}(\varf2_n)) - (t_{n}^2-t_{n})(\op{E}(\varf0_{n-1})-\op{E}(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.}\label{eq: one-step FISTA}
+			t_{n}^2(\op{E}(\var0_{n}) - \op{E}(\var2_n)) - (t_{n}^2-t_{n})(\op{E}(\var0_{n-1})-\op{E}(\var2_n)) \leq \tfrac1{2}\left[\norm{\var1_{n-1}}^2-\norm{\var1_{n}}^2\right] + \IP{\var1_{n}-\var1_{n-1}}{\var2_n}.}\label{eq: one-step FISTA}
 		\end{equation}
 	\end{lemma}
-	\noindent The proof is given in Theorem~\ref{app:thm: one step FISTA} and is a result of the convexity of $\op{E}$ for a well chosen $\varf2$ in Lemma~\ref{thm: descent lemma}.
+	\noindent The proof is given in Theorem~\ref{app:thm: one step FISTA} and is a result of the convexity of $\op{E}$ for a well chosen $\var2$ in Lemma~\ref{thm: descent lemma}.
 
@@
 		\Copy{thm: mini FISTA convergence}{
-			Fix a sequence of \edit{subspaces}{subsets} $(\spcf0^n\edit{\subset\spcf0\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$.
-Let $\varf0_n$ and $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA}, then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have
+			Fix a sequence of \edit{subspaces}{subsets} $(\F{U}^n\edit{\subset\F{U}\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\var0_0\in \F{U}^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$.
+Let $\var0_n$ and $\var1_n$ be generated by Algorithm~\ref{alg: refining FISTA}, then, for any choice of $\var2_n\in\F{U}^n$ and $N\in\F N$ we have
 		}
 		\begin{equation}\label{eq: FISTA inequality}\Copy{thm:eq: mini FISTA convergence}{
-			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
-			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
+			t_N^2\op{E}_0(\var0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\var0_n) + \frac{\norm{\var1_N-\var2_N}^2}{2} \leq \frac{\norm{\var0_0-\var2_0}^2-\norm{\var2_0}^2+\norm{\var2_N}^2}{2}
+			+ \sum^N_{n=1} t_n\op{E}_0(\var2_n) + \IP{\var1_{n-1}}{\var2_{n-1}-\var2_n}.
 		}\end{equation}
@@
 This result is the key approximation for showing convergence of FISTA with \edit{refining subspaces}{growing subsets}.
-In the classical setting, we have $\spcf0^n\edit{=\spcf0}{}=\F H$, $\varf2_n\edit{=\varf0^*}{\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the extra terms on the right-hand side collapse to 0.
-
-	\edit{The}{If there exists a minimiser $\varf0^*\in\argmin_{\varf0\in\F H}\op{E}(\varf0)$, then the } natural choice in \eqref{eq: FISTA inequality} is $\varf2_n=\tens{\Pi}_n\varf0^*$\edit{}{ for some projection $\tens{\Pi}_n\colon\F H\to\spcf0^n$}, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\varf0^*)=\infty$ and so this inequality becomes useless.
-For example, if $\op{f}(\varf0) = \norm{\varf0}_{\edit{2}{L^2([0,1])}}^2$, $\op{g}$ is the indicator on the set $\F D=\{\varf0\in L^1([0,1])\st \varf0(\varx0) \geq \varx0\}$, and \edit{$\spcf0^n$ is}{$\tens{\Pi}_n$ is the $L^2$ projection onto} a set of piecewise constant functions, then $\varf0^*=\varx0\mapsto \varx0$.
-On the other hand, suppose one of the pixels of the discretisation is $[\varx0_0-\meshsize,\varx0_0+\meshsize]$, then
-	$$\tens{\Pi}_n\varf0^*\left(\varx0_0+\tfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varf0^*(\varx0)-\vars5)^2d\varx0 = \argmin_{\vars5\in\R}\int_{\varx0_0-\meshsize}^{\varx0_0+\meshsize}(\varx0-\vars5)^2d\varx0 = \varx0_0 < \varx0_0+\tfrac\meshsize2.$$
-	In particular $\tens{\Pi}_n\varf0^* \notin\F D$ therefore $\op{E}(\tens{\Pi}_n\varf0^*) = \infty$.
-The choice $\varf2_n=\argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$ is much more robust and allows us to apply Algorithm~\ref{alg: refining FISTA} more broadly.
-The penalty for this flexibility is a more complicated analysis, each time the \edit{subspace}{subset} changes, the system receives a `shock' proportional to $\norm{\varf2_{n}-\varf2_{n+1}}$.
+In the classical setting, we have $\F{U}^n\edit{=\F{U}}{}=\F H$, $\var2_n\edit{=\var0^*}{\in\argmin_{\var0\in\F H}\op{E}(\var0)}$ and the extra terms on the right-hand side collapse to 0.
+
+	\edit{The}{If there exists a minimiser $\var0^*\in\argmin_{\var0\in\F H}\op{E}(\var0)$, then the } natural choice in \eqref{eq: FISTA inequality} is $\var2_n=\tens{\Pi}_n\var0^*$\edit{}{ for some projection $\tens{\Pi}_n\colon\F H\to\F{U}^n$}, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\var0^*)=\infty$ and so this inequality becomes useless.
+For example, if $\op{f}(\var0) = \norm{\var0}_{\edit{2}{L^2([0,1])}}^2$, $\op{g}$ is the indicator on the set $\F D=\{\var0\in L^1([0,1])\st \var0(x) \geq x\}$, and \edit{$\F{U}^n$ is}{$\tens{\Pi}_n$ is the $L^2$ projection onto} a set of piecewise constant functions, then $\var0^*=x\mapsto x$.
+On the other hand, suppose one of the pixels of the discretisation is $[x_0-\meshsize,x_0+\meshsize]$, then
+	$$\tens{\Pi}_n\var0^*\left(x_0+\tfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{x_0-\meshsize}^{x_0+\meshsize}(\var0^*(x)-\vars5)^2dx = \argmin_{\vars5\in\R}\int_{x_0-\meshsize}^{x_0+\meshsize}(x-\vars5)^2dx = x_0 < x_0+\tfrac\meshsize2.$$
+	In particular $\tens{\Pi}_n\var0^* \notin\F D$ therefore $\op{E}(\tens{\Pi}_n\var0^*) = \infty$.
+The choice $\var2_n=\argmin_{\var0\in\F{U}^n}\op{E}(\var0)$ is much more robust and allows us to apply Algorithm~\ref{alg: refining FISTA} more broadly.
+The penalty for this flexibility is a more complicated analysis, each time the \edit{subspace}{subset} changes, the system receives a `shock' proportional to $\norm{\var2_{n}-\var2_{n+1}}$.
 
@@
 The following lemma minimises the growth of the `constant' as a function of $N$ by partially telescoping the sum on the right-hand side.
-Before progressing to the content of Step~\ref{step: step 3 convergence bound}, we will first formalise the definition of the constants $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ introduced in Step~\ref{step: step 2 smoothness}.
+Before progressing to the content of Step~\ref{step: step 3 convergence bound}, we will first formalise the definition of the constants $\vars3_U$ and $\vars3_{\op{E}}$ introduced in Step~\ref{step: step 2 smoothness}.
 	\begin{definition}\label{def: exp subspaces}
-		Fix $\vars3_{\Varf0},\vars3_{\op{E}}\geq 1$ and a sequence of \edit{subspaces $(\tilde{\spcf0}^k\subset\F H\cap\spcf0)_{k\in\F N}$}{closed subsets $\tilde{\spcf0}^k\subset\F H$}.
-We say that $(\tilde{\spcf0}^k)_{k\in\F N}$ is a \emph{$(\vars3_{\Varf0},\vars3_{\op{E}})$-discretisation for $\op{E}$} if
-		$$ \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k \qquad\text{and}\qquad \op{E}_0(\tilde{\varf2}_k) \lesssim \vars3_{\op{E}}^{-k} $$
-		for all $k\in\F N$ and some choice $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)$.
+		Fix $\vars3_U,\vars3_{\op{E}}\geq 1$ and a sequence of \edit{subspaces $(\tilde{\F{U}}^k\subset\F H\cap\F{U})_{k\in\F N}$}{closed subsets $\tilde{\F{U}}^k\subset\F H$}.
+We say that $(\tilde{\F{U}}^k)_{k\in\F N}$ is a \emph{$(\vars3_U,\vars3_{\op{E}})$-discretisation for $\op{E}$} if
+		$$ \norm{\tilde{\var2}_k}\lesssim \vars3_U^k \qquad\text{and}\qquad \op{E}_0(\tilde{\var2}_k) \lesssim \vars3_{\op{E}}^{-k} $$
+		for all $k\in\F N$ and some choice $\tilde{\var2}_k\in\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.
 	\end{definition}
@@
 		\Copy{thm: mini exponential FISTA convergence}{
-			Let $\varf0_n$, $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA} \edit{}{with $(\spcf0^n)_{n\in\F N}$ satisfying \eqref{eq: refining subspace definition}}, $(n_k\in\F N)_{k\in\F N}$ be a monotone increasing sequence, and choose
-			$$\tilde{\varf2}_k \in \spcf0^{n_k} \cap \spcf0^{n_k+1}\cap \ldots \cap \spcf0^{n_{k+1}-1}$$
+			Let $\var0_n$, $\var1_n$ be generated by Algorithm~\ref{alg: refining FISTA} \edit{}{with $(\F{U}^n)_{n\in\F N}$ satisfying \eqref{eq: refining subspace definition}}, $(n_k\in\F N)_{k\in\F N}$ be a monotone increasing sequence, and choose
+			$$\tilde{\var2}_k \in \F{U}^{n_k} \cap \F{U}^{n_k+1}\cap \ldots \cap \F{U}^{n_{k+1}-1}$$
 			for each $k\in\F N$. If such a sequence exists, then for all $K\in\F N$, $n_K\leq N<n_{K+1}$ we have
@@
 			\begin{multline*}\Copy{thm:eq: mini exponential FISTA convergence}{
-				t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \frac{\norm{\varf1_N-\tilde{\varf2}_K}^2}{2} \leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\op{E}_0(\tilde{\varf2}_K) \\+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\op{E}_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}}
+				t_N^2\op{E}_0(\var0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\var0_n) + \frac{\norm{\var1_N-\tilde{\var2}_K}^2}{2} \leq C + \frac{\norm{\tilde{\var2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\op{E}_0(\tilde{\var2}_K) \\+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\op{E}_0(\tilde{\var2}_{k-1}) + \IP{\var1_{n_k-1}}{\tilde{\var2}_k-\tilde{\var2}_{k+1}}}
 			\end{multline*}
 		\Copy{thm:end: mini exponential FISTA convergence}{
-			where $C = \frac{\norm{\varf0_0-\tilde{\varf2}_0}^2-\norm{\tilde{\varf2}_0}^2}{2}$.
+			where $C = \frac{\norm{\var0_0-\tilde{\var2}_0}^2-\norm{\tilde{\var2}_0}^2}{2}$.
 		}
@@
 The introduction of $n_k$ has greatly compressed the expression of Theorem~\ref{thm: mini FISTA convergence}.
-On the right-hand side, we now only consider $\op{E}_0$ evaluated on the sequence $\tilde{\varf2}_k$ and there are $K$ elements to the sum rather than $N$.
+On the right-hand side, we now only consider $\op{E}_0$ evaluated on the sequence $\tilde{\var2}_k$ and there are $K$ elements to the sum rather than $N$.
 
 	\subsection{Refinement without overfitting}
-	The aim of Step~\ref{step: step 4 sufficiently fast} is to show that $n$ iterations of Algorithm~\ref{alg: refining FISTA} is no slower (up to a constant factor) than $n$ iterations of classical FISTA on the space $\spcf0^n$.
+	The aim of Step~\ref{step: step 4 sufficiently fast} is to show that $n$ iterations of Algorithm~\ref{alg: refining FISTA} is no slower (up to a constant factor) than $n$ iterations of classical FISTA on the space $\F{U}^n$.
 In other words, we would like to ensure that
 	\begin{equation}
-		\op{E}(\varf0_n) - \min_{\varf0\in\spcf0^n}\op{E}(\varf0) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)}^2}{n^2}
+		\op{E}(\var0_n) - \min_{\var0\in\F{U}^n}\op{E}(\var0) \lesssim \frac{\norm{\var0_0-\argmin_{\var0\in\F{U}^n}\op{E}(\var0)}^2}{n^2}
 	\end{equation}
@@
 If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of \edit{subspaces}{subsets}.
-This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\spcf0^n}$ rather than the desired function $\op{E}|_{\F H}$.
+This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\F{U}^n}$ rather than the desired function $\op{E}|_{\F H}$.
 Combining the assumptions given by Definition~\ref{def: exp subspaces} and the result of Lemma~\ref{thm: mini exponential FISTA convergence}, the following lemma proves the convergence of Algorithm~\ref{alg: refining FISTA} provided that the refinement times $n_k$ are sufficiently small (i.e.
-$\spcf0^n$ grows sufficiently quickly).
+$\F{U}^n$ grows sufficiently quickly).
 
@@
 		\Copy{thm: sufficiently fast}{
-			Suppose $\spcf0^n,\ \varf0_n,\ \varf1_n$ and $n_k$ satisfy the conditions of Lemma~\ref{thm: mini exponential FISTA convergence} and $(\tilde{\spcf0}^k)_{k\in\F N}$ forms an $(\vars3_{\Varf0},\vars3_{\op{E}})$-discretisation for $\op{E}$ with
-			$$\tilde{\varf2}_k\in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)\right]\cap\spcf0^{n_k}\cap\spcf0^{n_k+1}\cap\ldots\cap\spcf0^{n_{k+1}-1}.$$
+			Suppose $\F{U}^n,\ \var0_n,\ \var1_n$ and $n_k$ satisfy the conditions of Lemma~\ref{thm: mini exponential FISTA convergence} and $(\tilde{\F{U}}^k)_{k\in\F N}$ forms an \\$(\vars3_U,\vars3_{\op{E}})$-discretisation for $\op{E}$ with
+			$$\tilde{\var2}_k\in \left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]\cap\F{U}^{n_k}\cap\F{U}^{n_k+1}\cap\ldots\cap\F{U}^{n_{k+1}-1}.$$
 			If either:
 			\begin{itemize}
-				\item $\vars3_{\Varf0}>1$ and $n_k^2\lesssim \vars3_{\op{E}}^k\vars3_{\Varf0}^{2k}$,
-				\item or $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty,$
+				\item $\vars3_U>1$ and $n_k^2\lesssim \vars3_{\op{E}}^k\vars3_U^{2k}$,
+				\item or $\vars3_U=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty,$
 			\end{itemize}
 			then
-			$$ \op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}\qquad \text{for all}\qquad n_K\leq N< n_{K+1}.$$
+			$$ \op{E}_0(\var0_N) \lesssim \frac{\vars3_U^{2K}}{N^2}\qquad \text{for all}\qquad n_K\leq N< n_{K+1}.$$
 		}
@@
 	\begin{itemize}
-		\item The convergence guarantee for $N$ iterations of classical FISTA in the space $\spcf0^N$ is 
-		$$ \op{E}_0(\varf0_N) \lesssim \frac{\norm{\varf0_0-\argmin_{\varf0\in\spcf0^N}\op{E}(\varf0)}^2}{N^2} + \min_{\varf0\in\spcf0^N}\op{E}_0(\varf0) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} + \vars3_{\op{E}}^{-K}.$$
+		\item The convergence guarantee for $N$ iterations of classical FISTA in the space $\F{U}^N$ is 
+		$$ \op{E}_0(\var0_N) \lesssim \frac{\norm{\var0_0-\argmin_{\var0\in\F{U}^N}\op{E}(\var0)}^2}{N^2} + \min_{\var0\in\F{U}^N}\op{E}_0(\var0) \lesssim \frac{\vars3_U^{2K}}{N^2} + \vars3_{\op{E}}^{-K}.$$
 		This is equivalent to Lemma~\ref{thm: sufficiently fast} after the assumptions on $n_k$.
-		\item If $\edit{\spcf0}{\F H}$ is finite dimensional, then the $\vars3_{\Varf0}=1$ is almost trivially satisfied.
+		\item If $\edit{\F{U}}{\F H}$ is finite dimensional, then the $\vars3_U=1$ is almost trivially satisfied.
 Norms in finite dimensions are equivalent and any discretisation can be achieved with a finite number of refinements (i.e.
@@
 	\subsection{Convergence rate}
-	In Lemma~\ref{thm: sufficiently fast} we show that $\op{E}(\varf0_n)$ converges at a rate depending on $k$ and $n$, so long as $k$ grows sufficiently quickly.
+	In Lemma~\ref{thm: sufficiently fast} we show that $\op{E}(\var0_n)$ converges at a rate depending on $k$ and $n$, so long as $k$ grows sufficiently quickly.
 On the other hand, as $k$ grows, the rate becomes worse and so we need to also put a lower limit on the growth of $n_k$.
-The following lemma completes Step~\ref{step: step 5 sufficiently slow} by computing the global convergence rate of $\op{E}_0(\varf0_n)$ when $k$ grows at the minimum rate which is consistent with Lemma~\ref{thm: sufficiently fast}.
-
-	As a special case, note that if $\vars3_{\Varf0}=1$ then Lemma~\ref{thm: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate.
+The following lemma completes Step~\ref{step: step 5 sufficiently slow} by computing the global convergence rate of $\op{E}_0(\var0_n)$ when $k$ grows at the minimum rate which is consistent with Lemma~\ref{thm: sufficiently fast}.
+
+	As a special case, note that if $\vars3_U=1$ then Lemma~\ref{thm: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate.
 This is in fact a special case of that shown in \cite[Prop 3.3]{Aujol2015}.
-If \edit{$\varf0^*\in\F H$}{the minimum is achieved in $\F H$}, then it is not possible to refine `too quickly' and the following lemma is not needed.
+If \edit{$\var0^*\in\F H$}{the minimum is achieved in $\F H$}, then it is not possible to refine `too quickly' and the following lemma is not needed.
 
@@
 		\Copy{thm: sufficiently slow}{
-			Suppose $\varf0_n$ and $n_k$ are sequences satisfying 
-			$$\op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \vars3_{\op{E}}^K\vars3_{\Varf0}^{2K},$$
+			Suppose $\var0_n$ and $n_k$ are sequences satisfying 
+			$$\op{E}_0(\var0_N) \lesssim \frac{\vars3_U^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \vars3_{\op{E}}^K\vars3_U^{2K},$$
 			then 
-			$$\op{E}_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2}.$$}
+			$$\op{E}_0(\var0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2}.$$}
 	\end{lemma}
@@
 	\subsubsection{FISTA convergence with a priori discretisation}
-	We can summarise Lemmas~\ref{thm: mini exponential FISTA convergence} to~\ref{thm: sufficiently slow} into a single theorem stating the convergence guarantees when $\spcf0^n$ and $n_k$ are chosen a priori.
+	We can summarise Lemmas~\ref{thm: mini exponential FISTA convergence} to~\ref{thm: sufficiently slow} into a single theorem stating the convergence guarantees when $\F{U}^n$ and $n_k$ are chosen a priori.
 	\begin{theorem}\label{thm: exponential FISTA convergence}
 		\Copy{thm: exponential FISTA convergence}{
-			Let $(\tilde{\spcf0}^k)_{k\in\F N}$ be an $(\vars3_{\Varf0},\vars3_{\op{E}})$-discretisation for $\op{E}$ and choose any $\spcf0^n$ \edit{}{satisfying \eqref{eq: refining subspace definition} }such that
-			$$ \tilde{\spcf0}^k = \spcf0^{n_k}, \qquad \tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
-			for all $k\in\F N$. Compute $\varf0_n$ and $\varf1_n$ by Algorithm~\ref{alg: refining FISTA}.
+			Let $(\tilde{\F{U}}^k)_{k\in\F N}$ be an $(\vars3_U,\vars3_{\op{E}})$-discretisation for $\op{E}$ and choose any $\F{U}^n$ \edit{}{satisfying \eqref{eq: refining subspace definition} }such that 
+			$$ \tilde{\F{U}}^k = \F{U}^{n_k}, \qquad \tilde{\var2}_k \in \left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}$$
+			for all $k\in\F N$. Compute $\var0_n$ and $\var1_n$ by Algorithm~\ref{alg: refining FISTA}.
 
@@
 			\begin{itemize}
-				\item $\vars3_{\Varf0}>1$ and $n_k^2\simeq \vars3_{\op{E}}^k\vars3_{\Varf0}^{2k}$, or
-				\item $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$,
+				\item $\vars3_U>1$ and $n_k^2\simeq \vars3_{\op{E}}^k\vars3_U^{2k}$, or
+				\item $\vars3_U=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty$,
 			\end{itemize}
 			then
-			$$\op{E}_0(\varf0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2} \qquad \text{uniformly for } N\in\F N.$$
+			$$\op{E}_0(\var0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2} \qquad \text{uniformly for } N\in\F N.$$
 		}
 	\end{theorem}
-	\noindent This theorem is very easy to implement numerically and requires very little knowledge of how to estimate $\op{E}_0(\varf0_n)$.
-So long as $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ can be computed analytically, choosing $\tilde{\spcf0}^k$ to be uniform discretisations and $\tilde{\spcf0}^k = \spcf0^{n_k}=\ldots= \spcf0^{n_{k+1}-1}$ will achieve the stated convergence rate.
+	\noindent This theorem is very easy to implement numerically and requires very little knowledge of how to estimate $\op{E}_0(\var0_n)$.
+So long as $\vars3_U$ and $\vars3_{\op{E}}$ can be computed analytically, choosing $\tilde{\F{U}}^k$ to be uniform discretisations and $\tilde{\F{U}}^k = \F{U}^{n_k}=\ldots= \F{U}^{n_{k+1}-1}$ will achieve the stated convergence rate.
 
 	\subsubsection{FISTA convergence with adaptivity}
-	There are two properties of the sequence $(\spcf0^n)_{n\in\F N}$ which we may wish to decide adaptively: the refinement times $n_k$ and the discretising spaces $\{\spcf0^n \st n_k\leq n<n_{k+1}\}$.
+	There are two properties of the sequence $(\F{U}^n)_{n\in\F N}$ which we may wish to decide adaptively: the refinement times $n_k$ and the discretising spaces $\{\F{U}^n \st n_k\leq n<n_{k+1}\}$.
 We will refer to these as temporal and spatial adaptivity respectively.
@@
 	Lemma~\ref{thm: sufficiently fast} gives a sufficient condition on $n_k$ for converging at the rate $O(N^{2(\kappa-1)})$, but it is not necessary. Indeed for $n\leq n_k$ the result shows 
-	$$\op{E}_0(\varf0_n) \geq \min_{\varf0\in\spcf0^n}\op{E}_0(\varf0) = O(\vars3_{\op{E}}^{-k}) = O(n^{2(\kappa-1)})$$
+	$$\op{E}_0(\var0_n) \geq \min_{\var0\in\F{U}^n}\op{E}_0(\var0) = O(\vars3_{\op{E}}^{-k}) = O(n^{2(\kappa-1)})$$
 	which suggests that to converge faster than $n^{2(\kappa-1)}$ requires choosing smaller $n_k$.
@@
 On the other hand, choice of spatial adaptivity has no impact on rate but can impact computational efficiency.
-It will be permitted to use greedy discretisation techniques so long as each collection $\{\spcf0^n \st n_k\leq n<n_{k+1}\}$ satisfies a monotonicity condition.
+It will be permitted to use greedy discretisation techniques so long as each collection $\{\F{U}^n \st n_k\leq n<n_{k+1}\}$ satisfies a monotonicity condition.
 
@@
 We make the assumption that the choice of $n_k$ depends only on the value $\op{E}(u_{n_k-1})$ and therefore make $u_{n_k-1}$ the root of our requirements.
-Lemma~\ref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\op{E}_0(\varf0_{n_k-1})\lesssim \vars3_{\op{E}}^{-k}$.
+Lemma~\ref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\op{E}_0(\var0_{n_k-1})\lesssim \vars3_{\op{E}}^{-k}$.
 However, the value of $\op{E}_0$ may be hard to estimate and so we retain a `backstop' condition which guarantees that convergence is no slower than the rate given by Theorem~\ref{thm: exponential FISTA convergence}.
-The only constraints on spatial adaptivity are the monotone inclusion properties, $\varf0_n\in\spcf0^{n+1}$ and existence of $\tilde{\varf2}_k$.
+The only constraints on spatial adaptivity are the monotone inclusion properties, $\var0_n\in\F{U}^{n+1}$ and existence of $\tilde{\var2}_k$.
 This is confirmed by the following theorem.
@@
 		\Copy{thm: stronger exponential FISTA convergence}{
-			Let $(\spcf0^n\subset\F H\edit{\cap\spcf0}{})_{n\in\F N}$ be a sequence of \edit{subspaces}{subsets satisfying \eqref{eq: refining subspace definition} }and $n_k\in\F N$ a monotone increasing sequence such that
-			$$ \tilde{\spcf0}^k \coloneqq \spcf0^{n_k}\edit{\ni \varf0_{n_k-1}}{}, \qquad \tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}$$
+			Let $(\F{U}^n\subset\F H\edit{\cap\F{U}}{})_{n\in\F N}$ be a sequence of \edit{subspaces}{subsets satisfying \eqref{eq: refining subspace definition} }and $n_k\in\F N$ a monotone increasing sequence such that
+			$$ \tilde{\F{U}}^k \coloneqq \F{U}^{n_k}\edit{\ni \var0_{n_k-1}}{}, \qquad \tilde{\var2}_k \in \left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}$$
 			for all $k\in\F N$.
-			Compute $\varf0_n$ and $\varf1_n$ by Algorithm~\ref{alg: refining FISTA}.
-
-			\bigbreak\noindent Suppose there exist $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that either:
+			Compute $\var0_n$ and $\var1_n$ by Algorithm~\ref{alg: refining FISTA}.
+
+			\bigbreak\noindent Suppose there exist $\vars3_U,\vars3_{\op{E}}\geq1$ such that either:
 			\begin{itemize}
-				\item $\vars3_{\Varf0}>1$ and $n_k^2\lesssim \vars3_{\op{E}}^k\vars3_{\Varf0}^{2k}$, or
-				\item $\vars3_{\Varf0}=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$
+				\item $\vars3_U>1$ and $n_k^2\lesssim \vars3_{\op{E}}^k\vars3_U^{2k}$, or
+				\item $\vars3_U=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty$
 			\end{itemize}
 			and both
-			$$ \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k \qquad\text{and}\qquad \op{E}_0(\varf0_{n_K-1}) \lesssim \vars3_{\op{E}}^{-K}.$$
+			$$ \norm{\tilde{\var2}_k}\lesssim \vars3_U^k \qquad\text{and}\qquad \op{E}_0(\var0_{n_K-1}) \lesssim \vars3_{\op{E}}^{-K}.$$
 			Whenever these conditions on $n_k$ are satisfied, then
-			$$\min_{n\leq N}\op{E}_0(\varf0_n) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2}$$
+			$$\min_{n\leq N}\op{E}_0(\var0_n) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2}$$
 			uniformly for $N\in\F N$.
@@
 If we directly compare Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence}, we note that the convergence rate is the same in both theorems but the price for better adaptivity (i.e.
-relaxed $(\vars3_{\Varf0},\vars3_{\op{E}})$ assumptions) is a slightly weaker stability guarantee (now convergence of $\min_{n\leq N}\op{E}_0(\varf0_n)$).
-In Theorem~\ref{thm: exponential FISTA convergence}, as in the original FISTA algorithm, the sequence $\op{E}(\varf0_n)$ is not monotone but the magnitude of oscillation is guaranteed to decay in time.
+relaxed $(\vars3_U,\vars3_{\op{E}})$ assumptions) is a slightly weaker stability guarantee (now convergence of $\min_{n\leq N}\op{E}_0(\var0_n)$).
+In Theorem~\ref{thm: exponential FISTA convergence}, as in the original FISTA algorithm, the sequence $\op{E}(\var0_n)$ is not monotone but the magnitude of oscillation is guaranteed to decay in time.
 This behaviour is lost in Theorem~\ref{thm: stronger exponential FISTA convergence} although it still holds on a subsequence.
@@
 	\begin{equation}
-		\tilde{\varf2}_k \in \left[\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)\right]\cap\spcf0^{n_k+1} \cap\ldots\cap \spcf0^{n_{k+1}-1}\cap\ldots\cap \spcf0^N
-	\end{equation}
-	is sufficient to restore the stronger last-iterate guarantee on $\op{E}_0(\varf0_N)$. Again, monotonicity of $\spcf0^n$ corresponds with improved stability of Algorithm~\ref{alg: refining FISTA}.
-
-	To enable a more practical implementation of Theorem~\ref{thm: stronger exponential FISTA convergence}, the following lemma describes several refinement time strategies which provide sufficient condition for $\op{E}_0(\varf0_n) \lesssim \vars3_{\op{E}}^{-k}$.
+		\tilde{\var2}_k \in \left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}\cap\ldots\cap \F{U}^N
+	\end{equation}
+	is sufficient to restore the stronger last-iterate guarantee on $\op{E}_0(\var0_N)$. Again, monotonicity of $\F{U}^n$ corresponds with improved stability of Algorithm~\ref{alg: refining FISTA}.
+
+	To enable a more practical implementation of Theorem~\ref{thm: stronger exponential FISTA convergence}, the following lemma describes several refinement time strategies which provide sufficient condition for $\op{E}_0(\var0_n) \lesssim \vars3_{\op{E}}^{-k}$.
 	\begin{lemma}\label{thm: practical refinement criteria}
 		\Copy{thm: practical refinement criteria}{
-			Let $(\tilde{\spcf0}^k)_{k\in\F N}$ be a sequence of \edit{subspaces}{subsets} with some points $\varf0_k\in \tilde{\spcf0}^k$ and $\tilde{\varf2}_k\in\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)$.
-Suppose that $\norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k$.
-Any of the following conditions are sufficient to show that $\{\tilde{\spcf0}^k\}$ is an $(\vars3_{\Varf0},\vars3_{\op{E}})$-discretisation for $\op{E}$:
+			Let $(\tilde{\F{U}}^k)_{k\in\F N}$ be a sequence of \edit{subspaces}{subsets} with some points $\var0_k\in \tilde{\F{U}}^k$ and $\tilde{\var2}_k\in\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.
+Suppose that $\norm{\tilde{\var2}_k}\lesssim \vars3_U^k$.
+Any of the following conditions are sufficient to show that $\{\tilde{\F{U}}^k\}$ is an $(\vars3_U,\vars3_{\op{E}})$-discretisation for $\op{E}$:
 			\begin{enumerate}
-				\item Small continuous gap refinement: $ \op{E}_0(\varf0_k)\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
-				\item Small discrete gap refinement: $\op{E}_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $ \op{E}_0(\varf0_k)-\op{E}_0(\tilde{\varf2}_{k-1})\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
-				\item Small relative gap refinement: $ \op{E}_0(\varf0_k) - \op{E}_0(\tilde{\varf2}_{k-1}) \leq \vars1\op{E}_0(\varf0_k)$ for all $k\in\F N$, some $0<\vars1\leq \frac{1}{1+\vars3_{\op{E}}}$.
+				\item Small continuous gap refinement: $ \op{E}_0(\var0_k)\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+				\item Small discrete gap refinement: $\op{E}_0(\tilde{\var2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $ \op{E}_0(\var0_k)-\op{E}_0(\tilde{\var2}_{k-1})\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+				\item Small relative gap refinement: $ \op{E}_0(\var0_k) - \op{E}_0(\tilde{\var2}_{k-1}) \leq \vars1\op{E}_0(\var0_k)$ for all $k\in\F N$, some $0<\vars1\leq \frac{1}{1+\vars3_{\op{E}}}$.
 			\end{enumerate}
-			\edit{}{If, furthermore, there exists a Banach space $(\spcf0,\Norm\cdot)$ with $\spcf0\supset\F H$ and the sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded, then it is also sufficient that:}
+			\edit{}{If, furthermore, there exists a Banach space $(\F{U},\Norm\cdot)$ with $\F{U}\supset\F H$ and the sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded, then it is also sufficient that:}
 			\begin{enumerate}\setcounter{enumi}{3}
-				\item Small continuous gradient refinement: $ \edit{\Norm{\partial\op{E}(\varf0_k)}_*}{\inf_{\varf1\in\partial\op{E}(\varf0_k)}\Norm{\varf1}_*}\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
-				\item Small discrete gradient refinement: $\op{E}_0(\tilde{\varf2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $\edit{\Norm{\tens{\Pi}_k\partial\op{E}(\varf0_k)}_*}{\sup_{\varf0,\tilde{\varf0}\in \tilde{\spcf0}^k}\inf_{\varf1\in\partial\op{E}(\varf0_k)}\frac{|\IP{v}{\varf0-\tilde{\varf0}}|}{\Norm{\varf0-\tilde{\varf0}}}}\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
+				\item Small continuous gradient refinement: $ \edit{\Norm{\partial\op{E}(\var0_k)}_*}{\inf_{\var1\in\partial\op{E}(\var0_k)}\Norm{\var1}_*}\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
+				\item Small discrete gradient refinement: $\op{E}_0(\tilde{\var2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $\edit{\Norm{\tens{\Pi}_k\partial\op{E}(\var0_k)}_*}{\sup_{\var0,\tilde{\var0}\in \tilde{\F{U}}^k}\inf_{\var1\in\partial\op{E}(\var0_k)}\frac{|\IP{v}{\var0-\tilde{\var0}}|}{\Norm{\var0-\tilde{\var0}}}}\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
 			\end{enumerate}
@@
 The refinement criteria described by Lemma~\ref{thm: practical refinement criteria} can be split into two groups.
-Cases (1), (3), and (4) justify that any choice of $\tilde{\spcf0}^k\ni\varf0_k$ (or $\varf0_{n_k-1}$ in Theorem~\ref{thm: stronger exponential FISTA convergence}) satisfies the required conditions.
-In cases (2) and (5), $\varf0_k$ is sufficient to choose the refinement time $n_k$ but not the \edit{subspace}{subset} $\tilde{\spcf0}^k$.
-In these cases one could, for example, choose $\tilde{\spcf0}^k$ to be a uniform discretisation with apriori estimates.
+Cases (1), (3), and (4) justify that any choice of $\tilde{\F{U}}^k\ni\var0_k$ (or $\var0_{n_k-1}$ in Theorem~\ref{thm: stronger exponential FISTA convergence}) satisfies the required conditions.
+In cases (2) and (5), $\var0_k$ is sufficient to choose the refinement time $n_k$ but not the \edit{subspace}{subset} $\tilde{\F{U}}^k$.
+In these cases one could, for example, choose $\tilde{\F{U}}^k$ to be a uniform discretisation with apriori estimates.
 
@@
 Typically, gradient norms (in (4) and (5)) should be easier to estimate than function gaps because they only require local knowledge rather than global, i.e.
-$\partial\op{E}(\varf0_n)$ rather than an estimate of $\edit{\op{E}(\varf0^*)}{\Emin}$.
+$\partial\op{E}(\var0_n)$ rather than an estimate of $\edit{\op{E}(\var0^*)}{\Emin}$.
 Implicitly, the global information comes from an extra condition on $\op{E}$ to assert that sublevel sets are bounded.
@@
 	\edit{In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, Algorithm~\ref{alg: refining FISTA} is much more broadly applicable.
-Here we justify this claim by demonstrating that the constants $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ can be easily computed in many examples.
-	The cases where $\spcf0$ is finite or countable dimensional are quite straight forward.
+Here we justify this claim by demonstrating that the constants $\vars3_U$ and $\vars3_{\op{E}}$ can be easily computed in many examples.
+	The cases where $\F{U}$ is finite or countable dimensional are quite straight forward.
 If the total number of refinements is finite (i.e.
-$\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$) then $\vars3_{\Varf0} = 1$.
+$\F{U}^n = \F{U}^N$ for all $n\geq N$, some $N\in\F N$) then $\vars3_U = 1$.
 This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}.
-The examples considered here have $\F H = L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ where $\{\tilde{\spcf0}^n\st n\in\F N\}$ are finite dimensional finite-element--like spaces.
-We will now clarify exactly what is meant by these properties and then demonstrate that they are sufficient to find simple formulae for the values $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$.
+The examples considered here have $\F H = L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ where $\{\tilde{\F{U}}^n\st n\in\F N\}$ are finite dimensional finite-element--like spaces.
+We will now clarify exactly what is meant by these properties and then demonstrate that they are sufficient to find simple formulae for the values $\vars3_U$ and $\vars3_{\op{E}}$.
 }{
-	We consider the main use of Algorithm~\ref{alg: refining FISTA} to be where there exists a Banach space $(\spcf0,\Norm\cdot)$ such that $\spcf0\supset\F H$ and
-	$$\inf_{\varf0\in\F H} \op{E}(\varf0) = \min_{\varf0\in\spcf0}\op{E}(\varf0) = \op{E}(\varf0^*)$$
-	for some $\varf0^*\in\spcf0$.
+	We consider the main use of Algorithm~\ref{alg: refining FISTA} to be where there exists a Banach space $(\F{U},\Norm\cdot)$ such that $\F{U}\supset\F H$ and
+	$$\inf_{\var0\in\F H} \op{E}(\var0) = \min_{\var0\in\F{U}}\op{E}(\var0) = \op{E}(\var0^*)$$
+	for some $\var0^*\in\F{U}$.
 The cases where $\F H$ has finite or countable dimension are quite straightforward.
 If the total number of refinements is finite (i.e.
-$\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$), then $\vars3_{\Varf0} = 1$.
+$\F{U}^n = \F{U}^N$ for all $n\geq N$, some $N\in\F N$), then $\vars3_U = 1$.
 This holds for most finite dimensional problems as well as the countable example discussed in detail in Section~\ref{sec: Lasso definition}.
-In this section we give explicit computations of $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subsets $(\tilde{\spcf0}^n)_{n\in\F N}$ will be finite dimensional finite-element--like spaces, as defined below.
+In this section we give explicit computations of $\vars3_U$ and $\vars3_{\op{E}}$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subsets $(\tilde{\F{U}}^n)_{n\in\F N}$ will be finite dimensional finite-element--like spaces, as defined below.
 	}
@@
 	\begin{definition}
-		Suppose $\spcf0\subset L^q(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$\edit{}{ with sufficiently smooth boundary}.
+		Suppose $\F{U}\subset L^q(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$\edit{}{ with sufficiently smooth boundary}.
 We say that $\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$ is a \emph{mesh} if
@@
 		for all $i$ and $j$.
-We say that $\tilde{\spcf0}^k\subset \edit{\spcf0\cap}{}\F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\varf0\in\tilde{\spcf0}^k$ there exists $\varf0_i^k\in\tilde{\spcf0}^k$ such that
-		$$\supp(\varf0_i^k)\subset \bar{\domain_i^k}, \qquad \varf0(\vvarx0) = \varf0^k_i(\vvarx0) \qquad \text{ for a.e. }\vvarx0\in\domain_i^k, \text{ all } i\in\F N.$$
-
-		We say that a sequence of finite element subspaces $(\tilde{\spcf0}^k)_{k=0}^\infty$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\spcf0}^0\cap L^\infty(\Domain)$ such that for any $\varf0_i^k\in\tilde{\spcf0}^k$ with $\supp(\varf0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
-		$$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \varf0_i^k(\vvarx0) = \sum_{j=1}^N\vars2_je_j(\vars0 \vvarx0+\vvars1) \quad \text{ for a.e.
-}\vvarx0\in\domain_i^k, \quad \supp(e_j(\vars0\cdot+\vvars1))\subset\bar{\domain_i^k}.
+We say that $\tilde{\F{U}}^k\subset \edit{\F{U}\cap}{}\F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\var0\in\tilde{\F{U}}^k$ there exists $\var0_i^k\in\tilde{\F{U}}^k$ such that
+		$$\supp(\var0_i^k)\subset \bar{\domain_i^k}, \qquad \var0(\vec{x}) = \var0^k_i(\vec{x}) \qquad \text{ for a.e. }\vec{x}\in\domain_i^k, \text{ all } i\in\F N.$$
+
+		We say that a sequence of finite element subspaces $(\tilde{\F{U}}^k)_{k=0}^\infty$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\F{U}}^0\cap L^\infty(\Domain)$ such that for any $\var0_i^k\in\tilde{\F{U}}^k$ with $\supp(\var0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
+		$$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \var0_i^k(\vec{x}) = \sum_{j=1}^N\vars2_je_j(\vars0 \vec{x}+\vvars1) \quad \text{ for a.e.
+}\vec{x}\in\domain_i^k, \quad \supp(e_j(\vars0\cdot+\vvars1))\subset\bar{\domain_i^k}.
 $$
 
-		We say that $(\tilde{\spcf0}^k)_k$ is \emph{of order $p$} if
-		$$\min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*} \lesssim_{\varf0^*} \meshsize^{kp}.$$
-		We allow the implicit constant to have any dependence on $\varf0^*$ so long as it is finite. For example, in the case of Sobolev spaces we would expect an inequality of the form
-		$\min_{\varf2\in\tilde{\spcf0}^k}\norm{\varf2-\varf0^*}_{W^{0,q}} \lesssim \meshsize^{kp}\norm{\varf0^*}_{W^{p,q}}$ \cite{Strang1972}.
+		We say that $(\tilde{\F{U}}^k)_k$ is \emph{of order $p$} if
+		$$\min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*} \lesssim_{\var0^*} \meshsize^{kp}.$$
+		We allow the implicit constant to have any dependence on $\var0^*$ so long as it is finite. For example, in the case of Sobolev spaces we would expect an inequality of the form
+		$\min_{\var2\in\tilde{\F{U}}^k}\norm{\var2-\var0^*}_{W^{0,q}} \lesssim \meshsize^{kp}\norm{\var0^*}_{W^{p,q}}$ \cite{Strang1972}.
 	\end{definition}
@@
 		Suppose $\F H= L^2(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$\edit{}{ with sufficiently smooth boundary} and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
-If $(\tilde{\spcf0}^k)_k$ is a sequence of $\meshsize$-refining finite element spaces of order $p$ then
+If $(\tilde{\F{U}}^k)_k$ is a sequence of $\meshsize$-refining finite element spaces of order $p$ then
 		\begin{align*}
-			\vars3_{\Varf0} &\leq \splitln{1}{q\geq 2}{\sqrt{\meshsize^{-d}}}{q<2},
+			\vars3_U &\leq \splitln{1}{q\geq 2}{\sqrt{\meshsize^{-d}}}{q<2},
 			& \vars3_{\op{E}} &\geq \begin{cases}
-				\meshsize^{-p} & \op{E} \text{ is $\Norm\cdot$-Lipschitz at }\varf0^*
-				\\\meshsize^{-2p} & \op{E} \text{ is $\Norm\cdot$-smooth at }\varf0^*
+				\meshsize^{-p} & \op{E} \text{ is $\Norm\cdot$-Lipschitz at }\var0^*
+				\\\meshsize^{-2p} & \op{E} \text{ is $\Norm\cdot$-smooth at }\var0^*
 			\end{cases}\ .
 		\end{align*}
-		If $\op{g}$ is not Lipschitz at $\varf0^*$ but $\op{f}$ is $\Norm\cdot$-Lipschitz and 
-		$$\min_{\varf2\in\tilde{\spcf0}^k}\left\{\Norm{\varf2-\varf0^*}\st \op{g}(\varf2)\leq \op{g}(\varf0^*)\right\} \lesssim \min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*},$$
+		If $\op{g}$ is not Lipschitz at $\var0^*$ but $\op{f}$ is $\Norm\cdot$-Lipschitz and 
+		$$\min_{\var2\in\tilde{\F{U}}^k}\left\{\Norm{\var2-\var0^*}\st \op{g}(\var2)\leq \op{g}(\var0^*)\right\} \lesssim \min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*},$$
 		then, again, $\vars3_{\op{E}}\geq\meshsize^{-p}$.
@@
 	The proof of this theorem is in Appendix~\ref{app: generic a_U and a_E}.
-The main take-home for this theorem is that the computation of $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\op{E}$.
+The main take-home for this theorem is that the computation of $\vars3_U$ and $\vars3_{\op{E}}$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\op{E}$.
 The only non-trivial case is when $\op{g}$ is not smooth enough to estimate directly.
-So long as $\tilde{\spcf0}^k$ are sufficiently dense in sublevel sets of $\op{g}$, the smoothness of $\op{f}$ is sufficient to give a convergence rate.
+So long as $\tilde{\F{U}}^k$ are sufficiently dense in sublevel sets of $\op{g}$, the smoothness of $\op{f}$ is sufficient to give a convergence rate.
 
@@
 In this section we develop the necessary analytical tools for the variant with general smooth fidelity term} which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}.
-We consider three forms \edit{of Lasso}{} which will be referred to as the continuous, countable, and discrete \edit{Lasso}{problem} depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
+We consider three forms \edit{of Lasso}{} which will be referred to as the continuous, countable, and discrete \edit{Lasso}{problem} depending on whether the space $\F{U}$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
 In each case, the energy can be written as
 	\begin{equation}\label{eq: Lasso energy}
-		\op{E}(\varf0) = \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu\Norm{\varf0}
-	\end{equation}
-	for some $\A\colon \spcf0\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$.
+		\op{E}(\var0) = \edit{\tfrac12\norm{\A\var0-\data}_{\ell^2}^2}{\op{f}(\A\var0-\data)} + \mu\Norm{\var0}
+	\end{equation}
+	for some $\A\colon \F{U}\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$.
 \edit{}{We assume $\op{f}\in C^1(\R^m)$ is convex with $\nabla\op{f}$ 1-Lipschitz, and in the continuous-space case, we require $\A^*\colon\R^m\to C^1([0,1]^d)$.
-}Let $\varf0^*\in\argmin_{\varf0\in\spcf0}\op{E}(\varf0)$.
+}Let $\var0^*\in\argmin_{\var0\in\F{U}}\op{E}(\var0)$.
 
 	The aim of this section is to develop all of the necessary tools for implementing Algorithm~\ref{alg: refining FISTA} on the energy \eqref{eq: Lasso energy} using the convergence guarantees of either Theorem~\ref{thm: exponential FISTA convergence} or Theorem~\ref{thm: stronger exponential FISTA convergence}.
-This includes computing the rates $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$, estimating the continuous gap $\op{E}_0(\varf0_n)$, and developing an efficient refinement choice for $\spcf0^n$.
+This includes computing the rates $\vars3_U$ and $\vars3_{\op{E}}$, estimating the continuous gap $\op{E}_0(\var0_n)$, and developing an efficient refinement choice for $\F{U}^n$.
 
 	\subsection{Continuous case}\label{sec: continuous lasso rate}
-	We start by estimating rates in the case $\spcf0=\C M(\Domain)$ where $\Domain =[0,1]^d$.
-In this case we choose $\tilde{\spcf0}^k$ to be the span of all piecewise constant functions on a mesh of squares with maximum side length $2^{-k}$ (i.e.
+	We start by estimating rates in the case $\F{U}=\C M(\Domain)$ where $\Domain =[0,1]^d$.
+In this case we choose $\tilde{\F{U}}^k$ to be the span of all piecewise constant functions on a mesh of squares with maximum side length $2^{-k}$ (i.e.
 $\meshsize=\tfrac12$).
 
-	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$.
-This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$,
-	\begin{equation}
-		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
+	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_U=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$.
+This can be seen because for any $\var0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$,
+	\begin{equation}
+		\Norm{\var0-\delta} = \sup_{\varphi\in C(\Domain), \norm{\varphi}_{L^\infty}\leq 1} \IP{\varphi}{\var0-\delta} = \Norm{\var0}+\Norm{\delta} \geq 1 = \meshsize^0.
 	\end{equation}
 	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$.
-\edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing, therefore }
-	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
-	\begin{align}
-		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
-		\\&\leq \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
-		\\&\leq\edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{\left[\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2} + \norm{\A(\varf2-\varf0^*)}_{\ell^2}\right]}\norm{\A(\varf2-\varf0)}_{\ell^2}.
-	\end{align}
-	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
-	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
+\edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\F{U}}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing, therefore }
+	for any $\var0\in\F H$, $\var2\coloneqq \tilde{\tens{\Pi}}_k\var0\in\tilde{\F{U}}^k$ we have
+	\begin{align}
+		\op{E}(\var2)-\op{E}(\var0) &= \edit{\tfrac12\norm{\A\var2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\var0-\data}_{\ell^2}^2}{\op{f}(\A\var2-\data)-\op{f}(\A\var0-\data)} + \mu\left(\Norm{\var2}-\Norm{\var0}\right)
+		\\&\leq \ip{\nabla \op{f}(\A\var2-\data)}{\A(\var2-\var0)}
+		\\&\leq\edit{\max(\norm{\A\var2-\data}_{\ell^2},\norm{\A\var0-\data}_{\ell^2})}{\left[\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2} + \norm{\A(\var2-\var0^*)}_{\ell^2}\right]}\norm{\A(\var2-\var0)}_{\ell^2}.
+	\end{align}
+	\edit{Choosing $\var2 = \tilde{\tens{\Pi}}_k\var0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F{U}\to\tilde{\F{U}}^k$ gives
+	\\\centerline{$\displaystyle\op{E}(\var2)-\op{E}(\var0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\var0^*-\var0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\var0^*}.$}
 	Expanding the operator norm further,
 	\\\centerline{$\displaystyle
-		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}}
+		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vec{r}\in\R^m}\max_{\vec{x}\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vec{r}](\vec{x})-[\A^*\vec{r}](\vec{x})|}{\norm{\vec{r}}_{\ell^2}} \leq \sup_{\vec{r}\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vec{r}]}_{L^\infty}}{\norm{\vec{r}}_{\ell^2}}
 		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
-	}{Clearly $\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2}$ is a constant. For the second term, recall $\Norm{\varf2}\leq \Norm{\varf0}$, therefore we can bound
-	\begin{equation}
-	\norm{\A(\varf2-\varf0^*)}_{\ell^2} = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{\A^*\vvarx3}{\varf2-\varf0^*} \leq \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} |\A^*\vvarx3|_{L^\infty}\Norm{\varf2-\varf0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\varf0}+\Norm{\varf0^*}).
+	}{Clearly $\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2}$ is a constant. For the second term, recall $\Norm{\var2}\leq \Norm{\var0}$, therefore we can bound
+	\begin{equation}
+	\norm{\A(\var2-\var0^*)}_{\ell^2} = \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} \IP{\A^*\vec{r}}{\var2-\var0^*} \leq \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} |\A^*\vec{r}|_{L^\infty}\Norm{\var2-\var0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\var0}+\Norm{\var0^*}).
 	\end{equation}
@@
 	\begin{multline}
-		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
-		 = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
-		\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
-		\\\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
+		\norm{\A(\tilde{\tens{\Pi}}_k\var0-\var0)}_{\ell^2}
+		 = \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vec{r}}{\var0}
+		\leq \sup_{\vec{r}\in\R^m}\max_{\vec{x}\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vec{r}](\vec{x})-[\A^*\vec{r}](\vec{x})|\:\norm{\vec{r}}_{\ell^2}^{-1}\Norm{\var0}
+		\\\leq \sup_{\vec{r}\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vec{r}]}_{L^\infty}\: \norm{\vec{r}}_{\ell^2}^{-1} \Norm{\var0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\var0}
 	\end{multline}}
 	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.
-\edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$.
+\edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\var0^*_j\in\F H$ such that $\var0^*_j\rightharpoonup\var0^*$ and $\lim_{j\to\infty}\op{E}(\var0^*_j)=\op{E}(\var0^*)$.
 		Combining these estimates gives 
 		\begin{equation}
-			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}.
+			\inf_{\var2\in\tilde{\F{U}}^k} \op{E}(\var2)-\op{E}(\var0^*) = \lim_{j\to\infty} \inf_{\var2\in\tilde{\F{U}}^k} \op{E}(\var2)-\op{E}(\var0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\var0_j^*)-\op{E}(\var0_j^*) \lesssim 2^{-k}.
 		\end{equation}}
@@
 	\begin{equation}\label{eq: Lasso energy rate}
-		\kappa = \frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2} = \frac{d}{1+d} \quad \implies \quad \op{E}_0(\varf0_n) \lesssim n^{-2(1-\kappa)} = n^{-\frac{2}{1+d}}.
-	\end{equation}
-	This rate can be used to infer the required resolution at each iteration, in particular on iteration $n$ with $n^2\simeq (\vars3_{\op{E}}\vars3_{\Varf0}^2)^k$ we expect the resolution to be
+		\kappa = \frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2} = \frac{d}{1+d} \quad \implies \quad \op{E}_0(\var0_n) \lesssim n^{-2(1-\kappa)} = n^{-\frac{2}{1+d}}.
+	\end{equation}
+	This rate can be used to infer the required resolution at each iteration, in particular on iteration $n$ with $n^2\simeq (\vars3_{\op{E}}\vars3_U^2)^k$ we expect the resolution to be
 	\begin{equation}\label{eq: Lasso resolution rate}
-		2^{-k} = \left(\vars3_{\op{E}}\vars3_{\Varf0}^2\right)^{\frac{k}{1+d}} \simeq n^{-\frac{2}{1+d}}.
+		2^{-k} = \left(\vars3_{\op{E}}\vars3_U^2\right)^{\frac{k}{1+d}} \simeq n^{-\frac{2}{1+d}}.
 	\end{equation}
@@
 	\subsection{Countable and discrete case}
-	We now extend the rate computations to the case when $\spcf0=\ell^1(\R)$, or a finite dimensional subspace.
-The key fact here is that, even when $\spcf0$ is infinite dimensional, it is known (e.g.
-\cite[\edit{Theorem 2}{Thm 6}]{Unser2016} and \cite[\edit{Corollary 2}{Cor 3.8}]{Boyer2019}) that $\varf0^*$ can be chosen to have at most $m$ non-zeros.
-If this is the case, then $\varf0^*\in \ell^2(\R)$; this makes the analysis much simpler than in the continuous case.
+	We now extend the rate computations to the case when $\F{U}=\ell^1(\R)$, or a finite dimensional subspace.
+The key fact here is that, even when $\F{U}$ is infinite dimensional, it is known (e.g.
+\cite[\edit{Theorem 2}{Thm 6}]{Unser2016} and \cite[\edit{Corollary 2}{Cor 3.8}]{Boyer2019}) that $\var0^*$ can be chosen to have at most $m$ non-zeros.
+If this is the case, then $\var0^*\in \ell^2(\R)$; this makes the analysis much simpler than in the continuous case.
 In this subsection we will ignore the discrete case as a simple sub-case of the countable.
@@
 	For countable \edit{Lasso}{dimensions} we consider discretisation subspaces of the form 
-	$$\tilde{\spcf0}^k = \{\varf0\in \ell^1(\R) \st i\notin J_k\implies \varf0_i=0\}$$ for some sets $J_k\subset\F N$, i.e.
+	$$\tilde{\F{U}}^k = \{\var0\in \ell^1(\R) \st i\notin J_k\implies \var0_i=0\}$$ for some sets $J_k\subset\F N$, i.e.
 infinite vectors with finitely many non-zeros.
-The key change in analysis from the continuous case is $\norm{\varf0^*}<\infty$, which leads to $\vars3_{\Varf0}=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\op{E}}$ or any additional properties of $\A$.
+The key change in analysis from the continuous case is $\norm{\var0^*}<\infty$, which leads to $\vars3_U=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\op{E}}$ or any additional properties of $\A$.
 The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence} hold trivially.
@@
 	We start by computing estimates for discretised \edit{Lasso}{energies}.
-This covers the cases when either the continuous/countable \edit{Lasso}{energy} is projected onto $\spcf0^n$, or $\spcf0$ is finite dimensional.
+This covers the cases when either the continuous/countable \edit{Lasso}{energy} is projected onto $\F{U}^n$, or $\F{U}$ is finite dimensional.
 For notation we will use the continuous case, to recover the other cases just replace continuous indexing with discrete (i.e.
-$\varf0(\vvarx0) \leadsto \varf0_i$).
-
-	Let $\tens{\Pi}_n\colon\F H\to\spcf0^n$ denote the orthogonal projection.
-\edit{For Lasso}{In our case}, the discretised function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$ is equivalent to replacing $\varf0$ with $\tens{\Pi}_n\varf0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.
+$\var0(\vec{x}) \leadsto \var0_i$).
+
+	Let $\tens{\Pi}_n\colon\F H\to\F{U}^n$ denote the orthogonal projection.
+\edit{For Lasso}{In our case}, the discretised function $\var0\mapsto\op{E}(\tens{\Pi}_n\var0)$ is equivalent to replacing $\var0$ with $\tens{\Pi}_n\var0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.
 
 	\paragraph{Discrete gradient}
-	We can use $\tens{\Pi}_n$ to compute the discrete subdifferential at $\varf0_n\in\spcf0^n$:
-	\begin{align}
-		\partial_n \op{E}(\tens{\Pi}_n\varf0_n)(\vvarx0) &= [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)](\vvarx0) + \begin{cases}
-			\{+\mu\} & \varf0_n(\vvarx0)>0 \\ [-\mu,\mu] & \varf0_n(\vvarx0)=0 
-			\\\{-\mu\} & \varf0_n(\vvarx0)<0 
+	We can use $\tens{\Pi}_n$ to compute the discrete subdifferential at $\var0_n\in\F{U}^n$:
+	\begin{align}
+		\partial_n \op{E}(\tens{\Pi}_n\var0_n)(\vec{x}) &= [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)](\vec{x}) + \begin{cases}
+			\{+\mu\} & \var0_n(\vec{x})>0 \\ [-\mu,\mu] & \var0_n(\vec{x})=0 
+			\\\{-\mu\} & \var0_n(\vec{x})<0 
 		\end{cases} 
-		\\&\eqqcolon [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)](\vvarx0) + \mu\tens{\Pi}_n\sign(\varf0_n(\vvarx0))
+		\\&\eqqcolon [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)](\vec{x}) + \mu\tens{\Pi}_n\sign(\var0_n(\vec{x}))
 	\end{align}
@@
 	\begin{align}
-		\Norm{\partial_n \op{E}(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\min\left\{|\varf1| \st \varf1\in \tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0) +  \mu\sign(\varf0_n(\vvarx0))\right\}
-		\\&= \max_{\vvarx0\in\Domain}\begin{cases}
-			|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
-			\\|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
-			\\\max\left(|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
+		\Norm{\partial_n \op{E}(\var0_n)}_* &= \max_{\vec{x}\in\Domain}\min\left\{|\var1| \st \var1\in \tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)(\vec{x}) +  \mu\sign(\var0_n(\vec{x}))\right\}
+		\\&= \max_{\vec{x}\in\Domain}\begin{cases}
+			|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)(\vec{x}) + \mu| & \var0_n(\vec{x})>0
+			\\|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)(\vec{x}) - \mu| & \var0_n(\vec{x})<0
+			\\\max\left(|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)(\vec{x})| - \mu, 0\right) & \var0_n(\vec{x}) = 0
 		\end{cases}
@@
 	\paragraph{Discrete gap}
-	We now move on to the discrete gap, $\op{E}(\varf0_n)-\min_{\varf0\in\spcf0^n}\op{E}(\varf0)$. This can be computed with a dual representation (e.g. \cite{Duval2017a}),
-	\begin{align}
-		\min_{\varf0\in \spcf0^n} \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu\Norm{\varf0} &= \min_{\varf0\in\F H}\max_{\vvard0\in\R^m} \ip{(\A\tens{\Pi}_n\varf0-\data)}{ \vvard0} +\mu\Norm{\tens{\Pi}_n\varf0} -\edit{\tfrac12\norm{\vvard0}_{\ell^2}^2}{\op{f}^*(\vvard0)}
-		\\&= \max_{\vvard0\in\R^m}\min_{\varf0\in\F H} \ip{(\A\tens{\Pi}_n\varf0-\data)}{\vvard0} +\mu\Norm{\tens{\Pi}_n\varf0} -\edit{\tfrac12\norm{\vvard0}_{\ell^2}^2}{\op{f}^*(\vvard0)}
-		\\&= \max_{\vvard0\in\R^m} \splitln{-\ip{\data}{\vvard0} -\edit{\tfrac12\norm{\vvard0}_{\ell^2}^2}{\op{f}^*(\vvard0)}}{\qquad\Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu}{-\infty}{\qquad\text{else}}
-		\\&= -\min_{\vvard0\in\R^m} \underbrace{\edit{\tfrac12\norm{\vvard0}_{\ell^2}^2}{\op{f}^*(\vvard0)}+\ip{\data}{\vvard0}}_{\eqqcolon \op{E}^*(\vvard0)}  + \chi(\Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu).
+	We now move on to the discrete gap, $\op{E}(\var0_n)-\min_{\var0\in\F{U}^n}\op{E}(\var0)$. This can be computed with a dual representation (e.g. \cite{Duval2017a}),
+	\begin{align}
+		\min_{\var0\in \F{U}^n} \edit{\tfrac12\norm{\A\var0-\data}_{\ell^2}^2}{\op{f}(\A\var0-\data)} + \mu\Norm{\var0} &= \min_{\var0\in\F H}\max_{\vec{\varphi}\in\R^m} \ip{(\A\tens{\Pi}_n\var0-\data)}{ \vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\edit{\tfrac12\norm{\vec{\varphi}}_{\ell^2}^2}{\op{f}^*(\vec{\varphi})}
+		\\&= \max_{\vec{\varphi}\in\R^m}\min_{\var0\in\F H} \ip{(\A\tens{\Pi}_n\var0-\data)}{\vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\edit{\tfrac12\norm{\vec{\varphi}}_{\ell^2}^2}{\op{f}^*(\vec{\varphi})}
+		\\&= \max_{\vec{\varphi}\in\R^m} \splitln{-\ip{\data}{\vec{\varphi}} -\edit{\tfrac12\norm{\vec{\varphi}}_{\ell^2}^2}{\op{f}^*(\vec{\varphi})}}{\qquad\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu}{-\infty}{\qquad\text{else}}
+		\\&= -\min_{\vec{\varphi}\in\R^m} \underbrace{\edit{\tfrac12\norm{\vec{\varphi}}_{\ell^2}^2}{\op{f}^*(\vec{\varphi})}+\ip{\data}{\vec{\varphi}}}_{\eqqcolon \op{E}^*(\vec{\varphi})}  + \chi(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu).
 	\end{align}
@@
 	\begin{equation}
-		\op{E}(\varf0) - \min_{\varf0\in\spcf0^n}\op{E}(\varf0) = \op{E}(\varf0) + \min_{\vvard0\in\R^m\st \Norm{\tens{\Pi}_n\A^*\vvard0}_*\leq \mu} \op{E}^*(\vvard0) \leq \op{E}(\varf0) + \op{E}^*(\vvard0)
-	\end{equation}
-	for any feasible $\vvard0\in\R^m$. We further derive the criticality condition, if $(\varf0^*,\vvard0^*)$ is a saddle point, then
-	\begin{equation}
-		\edit{}{\A\varf0^*-\data\in\partial\op{f}^*(\vvard0^*),\qquad\text{or equivalently}\qquad}
-		\vvard0^* = \edit{}{\nabla\op{f}}(\A\varf0^*-\data).
+		\op{E}(\var0) - \min_{\var0\in\F{U}^n}\op{E}(\var0) = \op{E}(\var0) + \min_{\vec{\varphi}\in\R^m\st \Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu} \op{E}^*(\vec{\varphi}) \leq \op{E}(\var0) + \op{E}^*(\vec{\varphi})
+	\end{equation}
+	for any feasible $\vec{\varphi}\in\R^m$. We further derive the criticality condition, if $(\var0^*,\vec{\varphi}^*)$ is a saddle point, then
+	\begin{equation}
+		\edit{}{\A\var0^*-\data\in\partial\op{f}^*(\vec{\varphi}^*),\qquad\text{or equivalently}\qquad}
+		\vec{\varphi}^* = \edit{}{\nabla\op{f}}(\A\var0^*-\data).
 	\end{equation}
@@
 
-	Given $\varf0_n\in \spcf0^n$, the optimality condition motivates a simple rule for choosing $\vvard0$:
-	\begin{equation}
-		\vvard0_n\coloneqq \edit{}{\nabla\op{f}}(\A\varf0_n - \data), \qquad \op{E}(\varf0)-\min_{\varf0'\in\spcf0^n}\op{E}(\varf0') \leq \op{E}(\varf0) +\edit{\min_{\vars2\geq 0}\{}{}\op{E}^*(\vars2\vvard0_n) \edit{\st \vars2 \Norm{\tens{\Pi}_n\A^*\vvard0_n}_*\leq \mu\}}{}
-	\end{equation}
-	\edit{with optimal choice}{for some $0\leq \vars2\leq\frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vvard0_n}_*}$. In the case $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$, one can use the optimal choice}
-	\begin{equation}
-		\vars2 =\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vvard0_n}_*}\right)\right).
-	\end{equation}
-	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\A\varf0_n-\data)\edit{ = \frac12\norm{\vvard0_n}_{\ell^2}^2}{}$ and $\tens{\Pi}_n\nabla\op{f}(\A\varf0_n-\data)\edit{ = \tens{\Pi}_n\A^*\vvard0_n}{}$ are easily computable, therefore $\vars2$ and $\op{E}(\varf0_n) +\op{E}^*(\vars2\vvard0_n)$ are also easy to compute.
+	Given $\var0_n\in \F{U}^n$, the optimality condition motivates a simple rule for choosing $\vec{\varphi}$:
+	\begin{equation}
+		\vec{\varphi}_n\coloneqq \edit{}{\nabla\op{f}}(\A\var0_n - \data), \qquad \op{E}(\var0)-\min_{\var0'\in\F{U}^n}\op{E}(\var0') \leq \op{E}(\var0) +\edit{\min_{\vars2\geq 0}\{}{}\op{E}^*(\vars2\vec{\varphi}_n) \edit{\st \vars2 \Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*\leq \mu\}}{}
+	\end{equation}
+	\edit{with optimal choice}{for some $0\leq \vars2\leq\frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*}$. In the case $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$, one can use the optimal choice}
+	\begin{equation}
+		\vars2 =\max\left(0, \min\left(\frac{-\ip{\data}{\vec{\varphi}_n}}{\norm{\vec{\varphi}_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*}\right)\right).
+	\end{equation}
+	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\A\var0_n-\data)\edit{ = \frac12\norm{\vec{\varphi}_n}_{\ell^2}^2}{}$ and $\tens{\Pi}_n\nabla\op{f}(\A\var0_n-\data)\edit{ = \tens{\Pi}_n\A^*\vec{\varphi}_n}{}$ are easily computable, therefore $\vars2$ and $\op{E}(\var0_n) +\op{E}^*(\vars2\vec{\varphi}_n)$ are also easy to compute.
 
 	\subsubsection{Bounds for countable functionals}
-	Extending the results of Section~\ref{sec: bound discrete} to $\spcf0=\ell^1(\R)$ is analytically very simple but computationally relies heavily on the specific choice of $\A$.
-The computations of \edit{gradients}{subdifferentials} and gaps carry straight over replacing $\tens{\Pi}_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\spcf0^n = \{\varf0\in\ell^1\st i\notin J_n\implies \varf0_i=0\}$.
+	Extending the results of Section~\ref{sec: bound discrete} to $\F{U}=\ell^1(\R)$ is analytically very simple but computationally relies heavily on the specific choice of $\A$.
+The computations of \edit{gradients}{subdifferentials} and gaps carry straight over replacing $\tens{\Pi}_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\F{U}^n = \{\var0\in\ell^1\st i\notin J_n\implies \var0_i=0\}$.
 In particular,
 	\begin{align}
-		\Norm{\partial\op{E}(\varf0_n)}_* &= \max_{i\in\F N}\begin{cases}
-			|[\A^*\vvard0_n]_i + \mu| & [\varf0_n]_i>0
-			\\|[\A^*\vvard0_n]_i - \mu| & [\varf0_n]_i<0
-			\\\max\left(|[\A^*\vvard0_n]_i| - \mu, 0\right) & [\varf0_n]_i = 0
+		\Norm{\partial\op{E}(\var0_n)}_* &= \max_{i\in\F N}\begin{cases}
+			|[\A^*\vec{\varphi}_n]_i + \mu| & [\var0_n]_i>0
+			\\|[\A^*\vec{\varphi}_n]_i - \mu| & [\var0_n]_i<0
+			\\\max\left(|[\A^*\vec{\varphi}_n]_i| - \mu, 0\right) & [\var0_n]_i = 0
 		\end{cases}
-		\\ \op{E}_0(\varf0_n) &\leq \op{E}(\varf0_n) + \op{E}(\vars2_0\vvard0_n), \qquad \vars2_0\edit{=\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right)}{\in\left[0,\frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right]}
-	\end{align}
-	where $\vvard0_n = \edit{}{\nabla\op{f}}(\A\varf0_n-\data)\in\R^m$ is always exactly computable.
+		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\edit{=\max\left(0, \min\left(\frac{-\ip{\data}{\vec{\varphi}_n}}{\norm{\vec{\varphi}_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right)\right)}{\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]}
+	\end{align}
+	where $\vec{\varphi}_n = \edit{}{\nabla\op{f}}(\A\var0_n-\data)\in\R^m$ is always exactly computable.
 
 	In the countable case, the sets $J_n$ give a clear partition into known/unknown values in these definitions.
-For $i\in J_n$ the computation is the same as in Section~\ref{sec: bound discrete}, then for $i\notin J_n$ we know $[\varf0_n]_i=0$ which simplifies the remaining computations.
+For $i\in J_n$ the computation is the same as in Section~\ref{sec: bound discrete}, then for $i\notin J_n$ we know $[\var0_n]_i=0$ which simplifies the remaining computations.
 This leads to:
 	\begin{align}
-		\Norm{\partial\op{E}(\varf0_n)}_* &= \max\left(\max_{i\in J_n}|[\partial\op{E}(\varf0_n)]_i|,\ \sup_{i\notin J_n} |[\partial\op{E}(\varf0_n)]_i|\right)
-		\\&= \max\left(\Norm{\partial_n\op{E}(\varf0_n)}_*,\ \sup_{i\notin J_n} |[\A^*\vvard0_n]_i|-\mu\right)
-		\\ \Norm{\A^*\vvard0_n}_* &= \max\left(\max_{i\in J_n}|[\A^*\vvard0_n]_i|,\ \sup_{i\notin J_n} |[\A^*\vvard0_n]_i|\right)
-		\\ &= \max\left(\Norm{\tens{\Pi}_n\A^*\vvard0_n}_*,\ \sup_{i\notin J_n} |[\A^*\vvard0_n]_i|\right).
-	\end{align}
-	Both estimates only rely on an upper bound of $\max_{i\notin J_n} |[\A^*\vvard0_n]_i|$. One example computing this value is seen in Section~\ref{sec: wavelet examples}.
+		\Norm{\partial\op{E}(\var0_n)}_* &= \max\left(\max_{i\in J_n}|[\partial\op{E}(\var0_n)]_i|,\ \sup_{i\notin J_n} |[\partial\op{E}(\var0_n)]_i|\right)
+		\\&= \max\left(\Norm{\partial_n\op{E}(\var0_n)}_*,\ \sup_{i\notin J_n} |[\A^*\vec{\varphi}_n]_i|-\mu\right)
+		\\ \Norm{\A^*\vec{\varphi}_n}_* &= \max\left(\max_{i\in J_n}|[\A^*\vec{\varphi}_n]_i|,\ \sup_{i\notin J_n} |[\A^*\vec{\varphi}_n]_i|\right)
+		\\ &= \max\left(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*,\ \sup_{i\notin J_n} |[\A^*\vec{\varphi}_n]_i|\right).
+	\end{align}
+	Both estimates only rely on an upper bound of $\max_{i\notin J_n} |[\A^*\vec{\varphi}_n]_i|$. One example computing this value is seen in Section~\ref{sec: wavelet examples}.
 
@@
 	\begin{align}
-		\Norm{\partial\op{E}(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\begin{cases}
-			|[\A^*\vvard0_n](\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
-			\\|[\A^*\vvard0_n](\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
-			\\\max\left(|[\A^*\vvard0_n](\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
+		\Norm{\partial\op{E}(\var0_n)}_* &= \max_{\vec{x}\in\Domain}\begin{cases}
+			|[\A^*\vec{\varphi}_n](\vec{x}) + \mu| & \var0_n(\vec{x})>0
+			\\|[\A^*\vec{\varphi}_n](\vec{x}) - \mu| & \var0_n(\vec{x})<0
+			\\\max\left(|[\A^*\vec{\varphi}_n](\vec{x})| - \mu, 0\right) & \var0_n(\vec{x}) = 0
 		\end{cases}
-		\\ \op{E}_0(\varf0_n) &\leq \op{E}(\varf0_n) + \op{E}(\vars2_0\vvard0_n), \qquad \vars2_0\edit{=\max\left(0, \min\left(\frac{-\ip{\data}{\vvard0_n}}{\norm{\vvard0_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right)\right)}{\in\left[0,\frac{\mu}{\Norm{\A^*\vvard0_n}_*}\right]}.
-	\end{align}
-	If these quantities are not analytically tractable then we use the mesh $\F M^n$ corresponding to $\spcf0^n$ to decompose the bounds:
-	\begin{align}
-		\Norm{\partial \op{E}(\varf0_n)}_* &= \max_{\domain_i^n\in\F M^n} \begin{cases}
-			\norm{\A^*\vvard0_n + \mu}_{L^\infty(\domain_i^n)} & \varf0_n|_{\domain_i^n} > 0
-			\\\norm{\A^*\vvard0_n - \mu}_{L^\infty(\domain_i^n)} & \varf0_n|_{\domain_i^n} < 0
-			\\\max(0, \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}-\mu) & \varf0_n|_{\domain_i^n} = 0
+		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\edit{=\max\left(0, \min\left(\frac{-\ip{\data}{\vec{\varphi}_n}}{\norm{\vec{\varphi}_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right)\right)}{\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]}.
+	\end{align}
+	If these quantities are not analytically tractable then we use the mesh $\F M^n$ corresponding to $\F{U}^n$ to decompose the bounds:
+	\begin{align}
+		\Norm{\partial \op{E}(\var0_n)}_* &= \max_{\domain_i^n\in\F M^n} \begin{cases}
+			\norm{\A^*\vec{\varphi}_n + \mu}_{L^\infty(\domain_i^n)} & \var0_n|_{\domain_i^n} > 0
+			\\\norm{\A^*\vec{\varphi}_n - \mu}_{L^\infty(\domain_i^n)} & \var0_n|_{\domain_i^n} < 0
+			\\\max(0, \norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)}-\mu) & \var0_n|_{\domain_i^n} = 0
 		\end{cases}
-		\\ \Norm{\A^*\vvard0_n}_* &= \max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}.
-	\end{align}
-	Now, both estimates rely on cell-wise supremum norms of $\A^*\vvard0_n$ which we have assumed is sufficiently smooth.
+		\\ \Norm{\A^*\vec{\varphi}_n}_* &= \max_{\domain_i^n\in\F M^n} \norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)}.
+	\end{align}
+	Now, both estimates rely on cell-wise supremum norms of $\A^*\vec{\varphi}_n$ which we have assumed is sufficiently smooth.
 We will therefore use a cell-wise Taylor expansion to provide a simple and accurate estimate.
-For instance, let $\vvarx0_i$ be the midpoint of the square $\domain_i^n$, then
+For instance, let $\vec{x}_i$ be the midpoint of the square $\domain_i^n$, then
 	\begin{equation}\label{eq: Taylor approximation}
-		\norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)} \leq |[\A^*\vvard0_n](\vvarx0_i)| + \frac{\op{diam}(\domain_i^n)}{2}|[\nabla\A^*\vvard0_n](\vvarx0_i)| + \frac{\op{diam}(\domain_i^n)^2}{8}|\A^*\vvard0_n|_{C^2}.
-	\end{equation}
-	In this work we chose a first order expansion because we are looking for extrema of $\A^*\vvard0_n$, i.e. we are most interested in the squares $\domain_i^n$ such that 
-	\begin{equation}
-		|[\A^*\vvard0_n](\vvarx0_i)| \approx \mu, \qquad |[\nabla\A^*\vvard0_n](\vvarx0_i)| \approx 0, \qquad [\nabla^2\A^*\vvard0_n](\vvarx0_i) \preceq 0. 
-	\end{equation}
-	A zeroth order expansion would be optimally inefficient (approximating $|[\nabla\A^*\vvard0_n](\vvarx0_i)|$ with $|\A^*\vvard0_n|_{C^1}$) and a second order expansion would possibly be more elegant but harder to implement.
+		\norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)} \leq |[\A^*\vec{\varphi}_n](\vec{x}_i)| + \frac{\op{diam}(\domain_i^n)}{2}|[\nabla\A^*\vec{\varphi}_n](\vec{x}_i)| + \frac{\op{diam}(\domain_i^n)^2}{8}|\A^*\vec{\varphi}_n|_{C^2}.
+	\end{equation}
+	In this work we chose a first order expansion because we are looking for extrema of $\A^*\vec{\varphi}_n$, i.e. we are most interested in the squares $\domain_i^n$ such that 
+	\begin{equation}
+		|[\A^*\vec{\varphi}_n](\vec{x}_i)| \approx \mu, \qquad |[\nabla\A^*\vec{\varphi}_n](\vec{x}_i)| \approx 0, \qquad [\nabla^2\A^*\vec{\varphi}_n](\vec{x}_i) \preceq 0. 
+	\end{equation}
+	A zeroth order expansion would be optimally inefficient (approximating $|[\nabla\A^*\vec{\varphi}_n](\vec{x}_i)|$ with $|\A^*\vec{\varphi}_n|_{C^1}$) and a second order expansion would possibly be more elegant but harder to implement.
 We found that a first order expansion was simple and efficient.
@@
 	The bounds presented here for continuous \edit{Lasso}{problems} emphasise the twinned properties required for adaptive mesh optimisation.
-The mesh should be refined greedily to the structures of $\varf0^*$, but also must be sufficiently uniform to provide a good estimate for $\op{E}(\varf0^*)$.
+The mesh should be refined greedily to the structures of $\var0^*$, but also must be sufficiently uniform to provide a good estimate for $\op{E}(\var0^*)$.
 This is a classical exploitation/exploration trade-off; exploiting visible structure whilst searching for other structures which are not yet visible.
@@
 	\subsection{Support detection}\label{sec: support detection}
-	The main motivation for using \edit{Lasso}{L1 penalties} in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\varf0^*$ is also provably close to the `true' support \cite{Duval2017a,Poon2018}.
-If $\varf0_n\approx \varf0^*$ in the appropriate sense, then we should also be able to quantify the statement $\op{supp}(\varf0_n)\approx\op{supp}(\varf0^*)$.
+	The main motivation for using \edit{Lasso}{L1 penalties} in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\var0^*$ is also provably close to the `true' support \cite{Duval2017a,Poon2018}.
+If $\var0_n\approx \var0^*$ in the appropriate sense, then we should also be able to quantify the statement $\op{supp}(\var0_n)\approx\op{supp}(\var0^*)$.
 Such methods are referred to as \emph{safe screening} rules \cite{ElGhaoui2010} which gradually identify the support and allow the optimisation algorithm to constrain parts of the reconstruction to 0.
@@
 
-	The support of $\varf0^*$ has already been characterised very precisely \cite{Duval2017a,Poon2018}.
-In particular, the support is at most $m$ distinct points and are a subset of $\{ \vvarx0\in\Domain \st |\A^*\vvard0^*|(\vvarx0) = \mu\} $ (an equivalent statement holds for the countable case).
-Less formally, this can also be seen from the the \edit{gradient}{subdifferential} computations in Section~\ref{sec: Lasso gap and gradient}, for all $\vvarx0\in\supp(\varf0^*)$ we have
-	\begin{equation}
-		0\in \partial \op{E}(\varf0^*)(\vvarx0) = [\A^*\vvard0^*](\vvarx0) + \mu\sign(\varf0^*(\vvarx0)).
+	The support of $\var0^*$ has already been characterised very precisely \cite{Duval2017a,Poon2018}.
+In particular, the support is at most $m$ distinct points and are a subset of $\{ \vec{x}\in\Domain \st |\A^*\vec{\varphi}^*|(\vec{x}) = \mu\} $ (an equivalent statement holds for the countable case).
+Less formally, this can also be seen from the the \edit{gradient}{subdifferential} computations in Section~\ref{sec: Lasso gap and gradient}, for all $\vec{x}\in\supp(\var0^*)$ we have
+	\begin{equation}
+		0\in \partial \op{E}(\var0^*)(\vec{x}) = [\A^*\vec{\varphi}^*](\vec{x}) + \mu\sign(\var0^*(\vec{x})).
 	\end{equation}
@@
 	Heuristically, we will use strong convexity of $\op{E}^*$ and smoothness of $\A^*$ to quantify the statement:
-	$$ \text{if}\quad \op{E}(\varf0_n) + \op{E}^*(\vars2_0 \vvard0_n) \approx 0 \quad \text{then}\quad \left\{\vvarx0\st \mu - |[\A^*\vvard0_n](\vvarx0)|\ll 1\right\} \subset\{\vvarx0 \st \varf0^*(\vvarx0)=0\}.$$
+	$$ \text{if}\quad \op{E}(\var0_n) + \op{E}^*(\vars2_0 \vec{\varphi}_n) \approx 0 \quad \text{then}\quad \left\{\vec{x}\st \mu - |[\A^*\vec{\varphi}_n](\vec{x})|\ll 1\right\} \subset\{\vec{x} \st \var0^*(\vec{x})=0\}.$$
 	\edit{First we use the strong convexity of $\op{E}^*$}{Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex \cite[Chapter 10, Thm.
 4.2.2]{Hiriart2013}.
-Therefore}, if $\vars2_0\vvard0_n$ and $\vvard0^*$ are both dual-feasible, then
-	\begin{equation}
-		\tfrac12\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}^2 \leq \op{E}^*(\vars2_0\vvard0_n) - \op{E}^*(\vvard0^*) = \op{E}^*(\vars2_0\vvard0_n) + \op{E}(\varf0^*) \leq \op{E}^*(\vars2_0\vvard0_n) + \op{E}(\varf0_n),
-	\end{equation}
-	which gives an easily computable bound on $\norm{\vars2_0\vvard0_n-\vvard0^*}_{\ell^2}$. Now we estimate $\A^*\vvard0_n$ on the support of $\varf0^*$:
-	\begin{align}
-		\min_{\vvarx0\in\supp(\varf0^*)} |[\tens{\Pi}_n\A^*\vvard0_n](\vvarx0)| &\geq \min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0_n](\vvarx0)|
-		\\&= \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vars2_0 \vvard0_n](\vvarx0)|
-		\\&\geq \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} |[\A^*\vvard0^*](\vvarx0)| - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
-		\\&= \vars2_0^{-1}\min_{\vvarx0\in\supp(\varf0^*)} \mu - |[\A^*\vars2_0 \vvard0_n-\A^*\vvard0^*](\vvarx0)|
-		\\&\geq \vars2_0^{-1}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vvard0_n-\vvard0^*}_{\ell^2}\right).
+Therefore}, if $\vars2_0\vec{\varphi}_n$ and $\vec{\varphi}^*$ are both dual-feasible, then
+	\begin{equation}
+		\tfrac12\norm{\vars2_0\vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}^2 \leq \op{E}^*(\vars2_0\vec{\varphi}_n) - \op{E}^*(\vec{\varphi}^*) = \op{E}^*(\vars2_0\vec{\varphi}_n) + \op{E}(\var0^*) \leq \op{E}^*(\vars2_0\vec{\varphi}_n) + \op{E}(\var0_n),
+	\end{equation}
+	which gives an easily computable bound on $\norm{\vars2_0\vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}$. Now we estimate $\A^*\vec{\varphi}_n$ on the support of $\var0^*$:
+	\begin{align}
+		\min_{\vec{x}\in\supp(\var0^*)} |[\tens{\Pi}_n\A^*\vec{\varphi}_n](\vec{x})| &\geq \min_{\vec{x}\in\supp(\var0^*)} |[\A^*\vec{\varphi}_n](\vec{x})|
+		\\&= \vars2_0^{-1}\min_{\vec{x}\in\supp(\var0^*)} |[\A^*\vars2_0 \vec{\varphi}_n](\vec{x})|
+		\\&\geq \vars2_0^{-1}\min_{\vec{x}\in\supp(\var0^*)} |[\A^*\vec{\varphi}^*](\vec{x})| - |[\A^*\vars2_0 \vec{\varphi}_n-\A^*\vec{\varphi}^*](\vec{x})|
+		\\&= \vars2_0^{-1}\min_{\vec{x}\in\supp(\var0^*)} \mu - |[\A^*\vars2_0 \vec{\varphi}_n-\A^*\vec{\varphi}^*](\vec{x})|
+		\\&\geq \vars2_0^{-1}\left(\mu - |\A^*|_{\ell^2\to L^\infty}\norm{\vars2_0 \vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}\right).
 	\end{align}
@@
 	\begin{equation}
-		|[\tens{\Pi}_n\A^*\vars2_0\vvard0_n](\vvarx0)|< \mu - \sqrt{2(\op{E}(\varf0_n)+\op{E}^*(\vars2_0\vvard0_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \varf0^*(\vvarx0)= 0.\label{eq: support equation}
-	\end{equation}
-	This equation is valid when $\vvarx0$ is either a continuous or countable index, the only distinction is to switch to $\ell^\infty$ in the norm of $\A^*$.
+		|[\tens{\Pi}_n\A^*\vars2_0\vec{\varphi}_n](\vec{x})|< \mu - \sqrt{2(\op{E}(\var0_n)+\op{E}^*(\vars2_0\vec{\varphi}_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \var0^*(\vec{x})= 0.\label{eq: support equation}
+	\end{equation}
+	This equation is valid when $\vec{x}$ is either a continuous or countable index, the only distinction is to switch to $\ell^\infty$ in the norm of $\A^*$.
 To make the equivalent statement on the discretised problem, simply replace $\vars2_0$ with $\vars2$ and $\A^*$ with $\tens{\Pi}_n\A^*$.
@@
 	\begin{itemize}
-		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the quantity $\op{E}(\varf0_n)-\op{E}(\varf0^*)$, the more relevant quantity here is $\op{E}^*(\vars2_0\vvard0_n)+\op{E}(\varf0^*)$ for which there is no proven rate of convergence.
-		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence for $\op{E}(\varf0_n)$, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
+		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the quantity $\op{E}(\var0_n)-\op{E}(\var0^*)$, the more relevant quantity here is $\op{E}^*(\vars2_0\vec{\varphi}_n)+\op{E}(\var0^*)$ for which there is no proven rate of convergence.
+		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence for $\op{E}(\var0_n)$, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
 	\end{itemize}
@@
 	We start by specifying the structure of $\A$.
-By continuity of $\A$, there must exist kernels $\vard1_j\in \F H\cap\spcf0^*$ such that $(\A\varf0)_j = \IP{\vard1_j}{\varf0}$ for all $\varf0\in \F H\cup\spcf0$, $j=1,\ldots,m$.
+By continuity of $\A$, there must exist kernels $\psi_j\in \F H\cap\F{U}^*$ such that $(\A\var0)_j = \IP{\psi_j}{\var0}$ for all $\var0\in \F H\cup\F{U}$, $j=1,\ldots,m$.
 In this form, the adjoint can be written precisely, $\A^*\colon\R^m\to \F H$ by
 	\begin{equation}
-		[\A^*\vvarx3](\vvarx0) = \sum_{j=1}^m \varx3_j\vard1_j(\vvarx0) \qquad \text{ for all }\vvarx0\in\Domain,\ \vvarx3\in\R^m.
+		[\A^*\vec{r}](\vec{x}) = \sum_{j=1}^m r_j\psi_j(\vec{x}) \qquad \text{ for all }\vec{x}\in\Domain,\ \vec{r}\in\R^m.
 	\end{equation}
@@
 	\begin{lemma}\label{thm: norm bound L2}
-		If $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in \F H$ for $j\in[m]$, then
+		If $\A\colon \F H \to \R^m$ has kernels $\psi_j\in \F H$ for $j\in[m]$, then
 		$ \norm{\A^*\A} = \norm{\A\A^*} $
-		where $\A\A^*\in\R^{m\times m}$ has entries $(\A\A^*)_{i,j} = \IP{\vard1_i}{\vard1_j}$
+		where $\A\A^*\in\R^{m\times m}$ has entries $(\A\A^*)_{i,j} = \IP{\psi_i}{\psi_j}$
 		and the matrix norm is the standard spectral norm.
@@
 This shows that $ \norm{\A^*\A} = \norm{\A\A^*} $.
-To compute the entries of $\A\A^*\colon\R^m\to\R^m$, observe that for any $\vvarx3\in\R^m$
-		\begin{equation}
-			(\A\A^*\vvarx3)_i = \IP{\vard1_i}{\A^*\vvarx3} = \IP{\vard1_i}{\sum_{j=1}^m\varx3_j\vard1_j} = \sum_{j=1}^m \IP{\vard1_i}{\vard1_j}\varx3_j
+To compute the entries of $\A\A^*\colon\R^m\to\R^m$, observe that for any $\vec{r}\in\R^m$
+		\begin{equation}
+			(\A\A^*\vec{r})_i = \IP{\psi_i}{\A^*\vec{r}} = \IP{\psi_i}{\sum_{j=1}^mr_j\psi_j} = \sum_{j=1}^m \IP{\psi_i}{\psi_j}r_j
 		\end{equation}
@@
 	\begin{lemma}\label{thm: norm bound smoothness}
-		If $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in L^2(\Domain)\cap C^k(\Domain)$ for $j\in[m]$, then for all $\frac1q+\frac1{q^*}=1$, $q\in[1,\infty]$, we have
-		\begin{align}
-			|\A^*\vvarx3|_{C^k}&\coloneqq \sup_{\vvarx0\in\Domain} |\nabla^k[\A^*\vvarx3]|(\vvarx0) \leq \sup_{\vvarx0\in\Domain}\norm{(\nabla^k\vard1_j(\vvarx0))_{j=1}^m}_{\ell^{q^*}}\norm{\vvarx3}_{\ell^q},
-			\\ |\A^*|_{\ell^2\to C^k}&\coloneqq \sup_{\norm{\vvarx3}_{\ell^2}\leq 1} |\A^*\vvarx3|_{C^k} \leq \sup_{\vvarx0\in\Domain}\norm{(\nabla^k\vard1_j(\vvarx0))_{j=1}^m}_{\ell^{q^*}}\times \splitln{1}{q\geq 2}{\sqrt{m^{2-q}}}{q<2}.
+		If $\A\colon \F H \to \R^m$ has kernels $\psi_j\in L^2(\Domain)\cap C^k(\Domain)$ for $j\in[m]$, then for all $\frac1q+\frac1{q^*}=1$, $q\in[1,\infty]$, we have
+		\begin{align}
+			|\A^*\vec{r}|_{C^k}&\coloneqq \sup_{\vec{x}\in\Domain} |\nabla^k[\A^*\vec{r}]|(\vec{x}) \leq \sup_{\vec{x}\in\Domain}\norm{(\nabla^k\psi_j(\vec{x}))_{j=1}^m}_{\ell^{q^*}}\norm{\vec{r}}_{\ell^q},
+			\\ |\A^*|_{\ell^2\to C^k}&\coloneqq \sup_{\norm{\vec{r}}_{\ell^2}\leq 1} |\A^*\vec{r}|_{C^k} \leq \sup_{\vec{x}\in\Domain}\norm{(\nabla^k\psi_j(\vec{x}))_{j=1}^m}_{\ell^{q^*}}\times \splitln{1}{q\geq 2}{\sqrt{m^{2-q}}}{q<2}.
 		\end{align}
@@
 		For the first inequality, we apply the H\"older inequality on $\R^m$:
-		$$ |\nabla^k[\A^*\vvarx3]|(\vvarx0) = \left|\sum_{j=1}^m\nabla^k\vard1_j(\vvarx0)\varx3_j\right|
-		\leq \left(\sum_{j=1}^m|\nabla^k\vard1_j(\vvarx0)|^{q^*}\right)^{\frac{1}{q^*}}\norm{\vvarx3}_{\ell^q} = \norm{(\nabla^k\vard1_j(\vvarx0))_j}_{\ell^{q^*}}\norm{\vvarx3}_{\ell^q}\;.$$
-		For the second inequality, if $q\geq2$ and $\sum_{j=1}^m \varx3_j^2\leq 1$, then $|\varx3_j|\leq 1$ for all $j$ and $\norm{\vvarx3}_{\ell^q}^q\leq \norm{\vvarx3}_{\ell^2}^2\leq 1$.
-If $q<2$ and $\norm{\vvarx3}_{\ell^2}\leq 1$, then we again use H\"older's inequality:
-		$$\sum_{j=1}^m \varx3_j^q \leq \Big(\sum_{j=1}^m 1^{Q^*}\Big)^{\frac1{Q^*}} \Big(\sum_{j=1}^m \varx3_j^{qQ}\Big)^{\frac1{Q}} \leq m^{\frac{2-q}{2}}$$
+		$$ |\nabla^k[\A^*\vec{r}]|(\vec{x}) = \left|\sum_{j=1}^m\nabla^k\psi_j(\vec{x})r_j\right|
+		\leq \left(\sum_{j=1}^m|\nabla^k\psi_j(\vec{x})|^{q^*}\right)^{\frac{1}{q^*}}\norm{\vec{r}}_{\ell^q} = \norm{(\nabla^k\psi_j(\vec{x}))_j}_{\ell^{q^*}}\norm{\vec{r}}_{\ell^q}\;.$$
+		For the second inequality, if $q\geq2$ and $\sum_{j=1}^m r_j^2\leq 1$, then $|r_j|\leq 1$ for all $j$ and $\norm{\vec{r}}_{\ell^q}^q\leq \norm{\vec{r}}_{\ell^2}^2\leq 1$.
+If $q<2$ and $\norm{\vec{r}}_{\ell^2}\leq 1$, then we again use H\"older's inequality:
+		$$\sum_{j=1}^m r_j^q \leq \Big(\sum_{j=1}^m 1^{Q^*}\Big)^{\frac1{Q^*}} \Big(\sum_{j=1}^m r_j^{qQ}\Big)^{\frac1{Q}} \leq m^{\frac{2-q}{2}}$$
 		for $Q = \frac2q$.
@@
 
-	\subsubsection{Specific examples}
+	\edit{
 	We now present explicit examples of the computations in both Lemmas~\ref{thm: norm bound smoothness} and~\ref{thm: norm bound L2} for the numerical results in Section~\ref{sec: numerics}.
-These examples are common in practical applications and we show the result of Theorem~\ref{thm: norm bound examples} in the main text to demonstrate that, while sometimes hard to compute by hand, the constants can estimated accurately in an efficient manner.
-	\begin{theorem}\label{thm: norm bound examples}
-		\Copy{thm: norm bound examples}{
-			Suppose $\A\colon \F H \to \R^m$ has kernels $\vard1_j\in L^\infty([0,1]^d)$ for $j\in[m]$.
-			\begin{enumerate}
-				\item[Case 1:] If $\vard1_j(\vvarx0) = \splitln{1}{\vvarx0\in \F{X}_j}{0}{\text{ else}}$ for some collection $\F{X}_j\subset\Domain$ such that $\F{X}_i\cap \F{X}_j = \emptyset$ for all $i\neq j$, then
-				$$\norm{\A}_{L^2\to\ell^2} = \max_{j\in[m]} \sqrt{|\F{X}_j|}.$$
-
-				\item[Case 2:] If $\vard1_j(\vvarx0) = \cos(\ip{\vvars3_j}{\vvarx0})$ for some frequencies $\vvars3_j\in\R^d$ with $|\vvars3_j|\leq \Vars3$, then
-				$$\norm{\A}_{L^2\to\ell^2} \leq \sqrt{m}, \qquad |\A^*\vvarx3|_{C^k}\leq m^{1-\frac1q}\Vars3^k\norm{\vvarx3}_q, \qquad |\A^*|_{\ell^2\to C^k}\leq \sqrt{m}\Vars3^k$$
-				for all $\vvarx3\in\R^m$ and $q\in[1,\infty]$.
-
-				\item[Case 3:] Suppose $\vard1_j(\vvarx0) = (2\pi\sigma^2)^{-\frac{d}{2}}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right)$ for some regular mesh $\vvarx0_j\in[0,1]^d$ and separation $\Delta$.
-i.e.
-				$$\{\vvarx0_j\st j\in[m]\} = \{\vvarx0_0 + (j_1\Delta,\ldots,j_d\Delta)\st j_i\in[\hat m]\}$$
-				for some $\vvarx0_0\in\R^d$, $\hat m\coloneqq\sqrt[d]{m}$. For all $\frac1q + \frac{1}{q^*} = 1$, $q\in(1,\infty]$, we have
-				\begin{align}
-					\norm{\A}_{L^2\to\ell^2} &\leq \bigg((4\pi\sigma^2)^{-\frac 12}\sum_{j=-2\hat m,\ldots,2\hat m}\exp(-\tfrac{\Delta^2}{4\sigma^2}j^2)\bigg)^d,
-					\\ |\A^*\vvarx3|_{C^0} &\leq (2\pi\sigma^2)^{-\frac{d}{2}}\bigg(\sum_{\vec j\in J}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}}\norm{\vvarx3}_q,
-					\\ |\A^*\vvarx3|_{C^1} &\leq \frac{(2\pi\sigma^2)^{-\frac{d}{2}}}{\sigma}\frac{\Delta}{\sigma}\bigg(\sum_{\vec j\in J}(|\vec j|+\delta)^{q^*}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}}\norm{\vvarx3}_q,
-					\\ |\A^*\vvarx3|_{C^2} &\leq \frac{(2\pi\sigma^2)^{-\frac{d}{2}}}{\sigma^2} \bigg(\sum_{\vec j\in J} \left(1+\tfrac{\Delta^2}{\sigma^2}(|\vec j|+\delta)^2\right)^{q^*}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}} \norm{\vvarx3}_q,
-				\end{align}
-				where $\delta= \frac{\sqrt d}{2}$ and $J=\{\vec j\in\F Z^d \st \norm{\vec j}_{\ell^\infty}\leq 2\hat m\}$.
-The case for $q=1$ can be inferred from the standard limit of $\norm\cdot_{{q^*}}\to \norm\cdot_{\infty}$ for $q^*\to\infty$.
-			\end{enumerate}
-		}
-	\end{theorem}
-
-	The sharpest method for estimating these norms is of course to compute them.
-This is most cumbersome for Gaussian kernels, however, the sums converge faster than exponentially and so the computational burden should be very small.
+These examples are common in practical applications and we show the result of Theorem~5 in the main text to demonstrate that, while sometimes hard to compute by hand, the constants can estimated accurately in an efficient manner.
+	\\\bf{Theorem 5}
+		---- Original text moved to Theorem~\ref{thm: norm bound examples}. ----
+	\\\vspace{10pt}
+
+	\\The sharpest method for estimating these norms is of course to compute them.
+This is most cumbersome for Gaussian kernels, however, the sums converge faster than exponentially and so the computational burden should be very small.}{
+	The examples in Section~\ref{sec: numerics} require explicit computations of the expressions in Lemmas~\ref{thm: norm bound smoothness} and~\ref{thm: norm bound L2}.
+These computations are provided in Theorem~\ref{thm: norm bound examples}}
 
@@
 
-	In this section, the main aim is to minimise the exact \edit{Lasso }{}energy $\op{E}_0(\varf0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
-Lemma~\ref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\op{E}_0(\varf0_n)$ so it is this monotone estimate which is plotted.
-As $\op{E}(\varf0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\op{E}_0(\varf0_n) \approx \min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2_0\vvard0_{n'})$.
-Another quantity of interest is minimisation of the discrete \edit{Lasso }{}energy $\min_{n\leq N}\op{E}(\varf0_n) + \min_{n'\leq n}\op{E}^*(\vars2\vvard0_{n'})$ which will be referred to as the `discrete gap'.
+	In this section, the main aim is to minimise the exact \edit{Lasso }{}energy $\op{E}_0(\var0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
+Lemma~\ref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\op{E}_0(\var0_n)$ so it is this monotone estimate which is plotted.
+As $\op{E}(\var0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\op{E}_0(\var0_n) \approx \min_{n\leq N}\op{E}(\var0_n) + \min_{n'\leq n}\op{E}^*(\vars2_0\vec{\varphi}_{n'})$.
+Another quantity of interest is minimisation of the discrete \edit{Lasso }{}energy $\min_{n\leq N}\op{E}(\var0_n) + \min_{n'\leq n}\op{E}^*(\vars2\vec{\varphi}_{n'})$ which will be referred to as the `discrete gap'.
 Note that for the adaptive schemes the discrete gap may not be monotonic as the discrete dual problem changes with $N$.
@@
 	\subsection{1D continuous LASSO}\label{sec: 1D Lasso examples}
-	In this example we choose $\spcf0=\C M([0,1])$\edit{}{, $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$} and $\A\colon \spcf0\to \R^{30}$ with either random Fourier kernels:
-	\begin{equation}
-		(\A\varf0)_j = \int_0^1\cos(\vars3_j\varx0)\varf0(\varx0), \qquad \vars3_j\sim \op{Uniform}[-100,100],\ j=1,2,\ldots,30,\ \mu =0.02, 
+	In this example we choose $\F{U}=\C M([0,1])$\edit{}{, $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$} and $\A\colon \F{U}\to \R^{30}$ with either random Fourier kernels:
+	\begin{equation}
+		(\A\var0)_j = \int_0^1\cos(\vars3_jx)\var0(x), \qquad \vars3_j\sim \op{Uniform}[-100,100],\ j=1,2,\ldots,30,\ \mu =0.02, 
 	\end{equation}
@@
 	\begin{equation}
-		(\A\varf0)_j = (2\pi\sigma^2)^{-\frac12}\int_0^1\exp\left(-\frac{(\varx0-(j-1)\Delta)^2}{2\sigma^2}\right)\varf0(\varx0), \quad \sigma=0.12,\ \Delta = \tfrac1{29},\ j=1,2,\ldots,30,\ \mu=0.06.
+		(\A\var0)_j = (2\pi\sigma^2)^{-\frac12}\int_0^1\exp\left(-\frac{(x-(j-1)\Delta)^2}{2\sigma^2}\right)\var0(x), \quad \sigma=0.12,\ \Delta = \tfrac1{29},\ j=1,2,\ldots,30,\ \mu=0.06.
 	\end{equation}
@@
 \cite{Bredies2013,Castro2016,Boyd2017,Catala2019}) however, most \edit{}{require} the solution of a non-convex problem.
-We have focused on CBP because it approximates $\varf0^*$ through a convex discrete optimisation problem which is asymptotically exact in the limit $\meshsize\to0$.
+We have focused on CBP because it approximates $\var0^*$ through a convex discrete optimisation problem which is asymptotically exact in the limit $\meshsize\to0$.
 It can also be optimised with FISTA which allows for direct comparison with the uniform and adaptive mesh approaches.
 The idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen \cite{Ekanadham2011,Duval2017b}.
-If $\varf0^*$ has only one Dirac spike in each pixel, then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.
-
-	As shown in Section~\ref{sec: Lasso definition}, in 1D we have $\vars3_{\Varf0} = \vars3_{\op{E}} = 2$.
-The estimates given in \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\op{E}_0(\varf0_n)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$.
-To achieve these rates, we implement a refinement criterion from Lemma~\ref{thm: practical refinement criteria} with guarantee of $\op{E}_0(\varf0_{n_k-1})\lesssim 2^{-k}$ using the estimates made in Section~\ref{sec: Lasso gap and gradient}.
-We choose subspaces $\spcf0^n$ to approximately enforce
-	\begin{equation}
-		\op{E}(\varf0_n) + \op{E}^*(\vars2_0\vvard0_n) \leq 2(\op{E}(\varf0_n) + \op{E}^*(\vars2\vvard0_n)),
+If $\var0^*$ has only one Dirac spike in each pixel, then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.
+
+	As shown in Section~\ref{sec: Lasso definition}, in 1D we have $\vars3_U = \vars3_{\op{E}} = 2$.
+The estimates given in \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\op{E}_0(\var0_n)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$.
+To achieve these rates, we implement a refinement criterion from Lemma~\ref{thm: practical refinement criteria} with guarantee of $\op{E}_0(\var0_{n_k-1})\lesssim 2^{-k}$ using the estimates made in Section~\ref{sec: Lasso gap and gradient}.
+We choose subspaces $\F{U}^n$ to approximately enforce
+	\begin{equation}
+		\op{E}(\var0_n) + \op{E}^*(\vars2_0\vec{\varphi}_n) \leq 2(\op{E}(\var0_n) + \op{E}^*(\vars2\vec{\varphi}_n)),
 	\end{equation}
@@
 	\begin{equation}
-		\op{E}^*(\vars2_0\vvard0_n) = \tfrac12\norm{\vars2_0\vvard0_n}^2 + \vars2_0\ip{\data}{\vvard0_n} = \frac{\vars2_0}{\vars2}\left(\frac{\vars2_0}{\vars2}\tfrac12\norm{\vars2\vvard0_n}^2 + \vars2\ip{\data}{\vvard0_n}\right) \approx \frac{\vars2_0}{\vars2} \op{E}^*(\vars2\vvard0_n).
+		\op{E}^*(\vars2_0\vec{\varphi}_n) = \tfrac12\norm{\vars2_0\vec{\varphi}_n}^2 + \vars2_0\ip{\data}{\vec{\varphi}_n} = \frac{\vars2_0}{\vars2}\left(\frac{\vars2_0}{\vars2}\tfrac12\norm{\vars2\vec{\varphi}_n}^2 + \vars2\ip{\data}{\vec{\varphi}_n}\right) \approx \frac{\vars2_0}{\vars2} \op{E}^*(\vars2\vec{\varphi}_n).
 	\end{equation}
@@
 	\begin{equation}
-		\frac{\vars2_0}{\vars2} \approx \frac{\Norm{\A^*\vvard0_n}_*}{\Norm{\tens{\Pi}_n\A^*\vvard0_n}_*} = \frac{\max_{\domain_i^n\in\F M^n} \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{\max_{\domain_i^n\in\F M^n} |\tens{\Pi}_n\A^*\vvard0_n(\domain_i^n)|} \approx \max_{\domain_i^n\in\F M^n}\frac{ \norm{\A^*\vvard0_n}_{L^\infty(\domain_i^n)}}{|\tens{\Pi}_n\A^*\vvard0_n(\domain_i^n)|}
+		\frac{\vars2_0}{\vars2} \approx \frac{\Norm{\A^*\vec{\varphi}_n}_*}{\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*} = \frac{\max_{\domain_i^n\in\F M^n} \norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)}}{\max_{\domain_i^n\in\F M^n} |\tens{\Pi}_n\A^*\vec{\varphi}_n(\domain_i^n)|} \approx \max_{\domain_i^n\in\F M^n}\frac{ \norm{\A^*\vec{\varphi}_n}_{L^\infty(\domain_i^n)}}{|\tens{\Pi}_n\A^*\vec{\varphi}_n(\domain_i^n)|}
 	\end{equation}
 	is the maximum ratio of second vs.
-zeroth order Taylor approximations of $\A^*\vvard0_n$ on pixel $\domain_i^n$.
+zeroth order Taylor approximations of $\A^*\vec{\varphi}_n$ on pixel $\domain_i^n$.
 This was found to be an efficient method of selecting pixels for refinement using quantities which had already been computed.
-Note briefly that this greedy strategy directly targets uncertainty, refinements also happen outside of the support of $u_n$ to guarantee that this is representative of $\varf0^*$.
+Note briefly that this greedy strategy directly targets uncertainty, refinements also happen outside of the support of $u_n$ to guarantee that this is representative of $\var0^*$.
 Such refinement is necessary to avoid critical points of $\op{E}$ which are not global minimisers.
@@
 	\paragraph{Comparison of discretisation methods}
-	In Figure~\ref{fig: convergence with ndofs} we compare the three core approaches: fixed uniform
+	In Fig.~\ref{fig: convergence with ndofs} we compare the three core approaches: fixed uniform
 	discretisation, adaptive discretisation, and CBP.
@@
 	\begin{figure}\centering
-		\includegraphics[width=.84\textwidth]{lasso_ndofs_convergence}
+		\includegraphics[width=.86\textwidth]{lasso_ndofs_convergence}
 		\caption{Rates of continuous/discrete gap convergence for different LASSO algorithms with 128, 256, or 512 pixels.
@@
 
-		\includegraphics[width=.84\textwidth]{lasso_convergence_short}
+		\includegraphics[width=.86\textwidth]{lasso_convergence_short}
 		\caption{\edit{Discrete }{}Convergence plots for solving 1D problems with different algorithms.
@@
 	\paragraph{Comparison of FISTA variants}
-	Figure~\ref{fig: convergence with method} compares many methods with either fixed or adaptive discretisations.
+	Fig.~\ref{fig: convergence with method} compares many methods with either fixed or adaptive discretisations.
 Each adaptive scheme is allowed up to 1024 pixels and each uniform discretisation uses exactly 1024.
@@
 In this example CBP used the greedy FISTA implementation which gave faster observed convergence.
-Figure~\ref{fig: convergence with method} compares the discrete gaps because it is the accurate metric for fixed discretisations, and for the adaptive discretisation it should also be an accurate predictor of the continuous gap.
+Fig.~\ref{fig: convergence with method} compares the discrete gaps because it is the accurate metric for fixed discretisations, and for the adaptive discretisation it should also be an accurate predictor of the continuous gap.
 
@@
 	\paragraph{Comparison of fixed and adaptive discretisation}
-	Motivated by the findings in Figure~\ref{fig: convergence with method}, we now look more closely at the performance of the $a=20$ and the greedy FISTA schemes.
+	Motivated by the findings in Fig.~\ref{fig: convergence with method}, we now look more closely at the performance of the $a=20$ and the greedy FISTA schemes.
 We have analytical results for the former but the latter typically performs the best for non-adaptive optimisation and is never worse than $a=20$ in the adaptive setting.
@@
 The fixed discretisations use 1024 pixels (i.e.
-constant pixel size of $2^{-10}$ in Figure~\ref{fig: comparison with iteration}) and the adaptive discretisation starts with two pixels with an upper limit of 1024.
+constant pixel size of $2^{-10}$ in Fig.~\ref{fig: comparison with iteration}) and the adaptive discretisation starts with two pixels with an upper limit of 1024.
 As expected, the fixed discretisation starts with a smaller continuous gap before plateauing to a sub-optimal gap around $\op{E}_0=0.1$.
 
-	Figure~\ref{fig: comparison with iteration} shows convergence of pixel size and continuous gap with respect to number of iterations.
-Figure~\ref{fig: comparison with time} shows the more practical attributes of continuous gap and number of pixels against execution time.
+	Fig.~\ref{fig: comparison with iteration} shows convergence of pixel size and continuous gap with respect to number of iterations.
+Fig.~\ref{fig: comparison with time} shows the more practical attributes of continuous gap and number of pixels against execution time.
 We see that the adaptive discretisation is consistently capable of computing lower energies with fewer pixels and in less time than the uniform discretisation.
@@
 
-	Suppose that the numerical aim is to find a function $\varf0_n$ with $\op{E}_0(\varf0_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.
+	Suppose that the numerical aim is to find a function $\var0_n$ with $\op{E}_0(\var0_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.
 For $n\in[10^3,10^4]$, in both problems, the adaptive schemes coincide with the fixed schemes in both energy and minimum pixel size.
@@
 	\begin{figure}\centering
-		\includegraphics[width=.84\textwidth]{lasso_reduced_convergence}
+		\includegraphics[width=.86\textwidth]{lasso_reduced_convergence}
 		\caption{Continuous convergence of adaptive (coarse-to-fine pixel size) compared with uniform discretisation (constant pixel size) with respect to number of iterations.
@@
 
-		\includegraphics[width=.84\textwidth]{lasso_convergence_time}
+		\includegraphics[width=.86\textwidth]{lasso_convergence_time}
 		\caption{Continuous convergence of adaptive compared with uniform discretisation with respect to wall-clock time and total number of pixels (memory requirement).}\label{fig: comparison with time}
@@
 	\begin{equation}
-		\F{X}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{100},-\tfrac12+\tfrac{i}{100}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I
+		\F{X}_i^I = \left\{\vec{x}\in[-\tfrac12,\tfrac12]^2\st \ip{\vec{x}}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{100},-\tfrac12+\tfrac{i}{100}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I
 	\end{equation}
@@
 	\begin{equation}
-		\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[100]} |\F{X}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[100]} \int_{\F{X}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[100]}\ (\A\1)_{i,I}}\;.
+		\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[100]} |\F{X}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[100]} \int_{\F{X}^I_i}1d\vec{x}}= \sqrt{\sum_{I\in[50]}\max_{i\in[100]}\ (\A\1)_{i,I}}\;.
 	\end{equation}
@@
 	\begin{equation}
-		\min_{\varf0\in \spcf0} \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu \norm{\tens{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \edit{\tfrac12\norm{\A\tens{W}\hat{\varf0}-\data}_{\ell^2}^2}{\op{f}(\A\tens{W}\hat{\varf0}-\data)} + \mu \norm{\hat{\varf0}}_{\ell^1}.
-	\end{equation}
-	The minimisers are related by $\varf0^* = \tens{W}\hat{\varf0}^*$ and, for wavelet bases, $\tens{W}$ is orthonormal so $\norm{\A\tens{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$. 
+		\min_{\var0\in \F{U}} \edit{\tfrac12\norm{\A\var0-\data}_{\ell^2}^2}{\op{f}(\A\var0-\data)} + \mu \norm{\tens{W}^{-1}\var0}_{\ell^1} = \min_{\hat{\var0}\in\ell^1(\R)} \edit{\tfrac12\norm{\A\tens{W}\hat{\var0}-\data}_{\ell^2}^2}{\op{f}(\A\tens{W}\hat{\var0}-\data)} + \mu \norm{\hat{\var0}}_{\ell^1}.
+	\end{equation}
+	The minimisers are related by $\var0^* = \tens{W}\hat{\var0}^*$ and, for wavelet bases, $\tens{W}$ is orthonormal so $\norm{\A\tens{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$. 
 	\edit{}{ In this example we consider the smoothed robust fidelity \cite{Rosset2007}
 		\begin{equation}
-			\op{f}(\vvard0) = \sum_{i=1}^m \splitln{10^{-4}|\vard0_i|}{|\vard0_i|\geq10^{-4}}{\tfrac12|\vard0_i|^2+\tfrac12 10^{-8}}{\text{else}} \approx 10^{-4}\norm{\vvard0}_{\ell^1}.
+			\op{f}(\vec{\varphi}) = \sum_{i=1}^m \splitln{10^{-4}|\varphi_i|}{|\varphi_i|\geq10^{-4}}{\tfrac12|\varphi_i|^2+\tfrac12 10^{-8}}{\text{else}} \approx 10^{-4}\norm{\vec{\varphi}}_{\ell^1}.
 		\end{equation}
 	}	
-	From Section~\ref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\tens{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$.
+	From Section~\ref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\tens{W}^\top \A^*\vec{\varphi}_n]_j|$ for all $j\notin J_n$.
 If $\tens{W}$ is a wavelet transformation then its columns, $w_j\in L^2$, are simply the wavelets themselves and we can use the bound
 	\begin{equation}
-		|\IP{w_j}{\A^*\vvard0_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vvard0_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vvard0_n}_{L^2}\leq \norm{\1_{\F{X}} \A^*\vvard0_n}_{L^2}
+		|\IP{w_j}{\A^*\vec{\varphi}_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vec{\varphi}_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vec{\varphi}_n}_{L^2}\leq \norm{\1_{\F{X}} \A^*\vec{\varphi}_n}_{L^2}
 	\end{equation}
@@
 This perspective comes from the multi-resolution interpretation of wavelets.
-An example is seen in Figure~\ref{fig: wavelet tree} for 1D Haar wavelets, $w_{j,k}(\varx0) = \sqrt{2}^k\vard1(2^{k}\varx0-j)$ where $\vard1 = \1_{[0,1)} - \1_{[-1,0)}$.
+An example is seen in Fig.~\ref{fig: wavelet tree} for 1D Haar wavelets, $w_{j,k}(x) = \sqrt{2}^k\psi(2^{k}x-j)$ where $\psi = \1_{[0,1)} - \1_{[-1,0)}$.
 
@@
 	\begin{align}
-		\Norm{\partial \op{E}(\varf0_n)}_* &=\max\left(\Norm{\partial_n\op{E}(\varf0_n)}_*, \max_{j\notin J_n} |\IP{w_j}{\A^*\vvard0_n}| -\mu \right) \\&\leq\max\left(\Norm{\partial_n\op{E}(\varf0_n)}_*, \max_{j\in \op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu \right).\label{eq: wavelet error metric}
+		\Norm{\partial \op{E}(\var0_n)}_* &=\max\left(\Norm{\partial_n\op{E}(\var0_n)}_*, \max_{j\notin J_n} |\IP{w_j}{\A^*\vec{\varphi}_n}| -\mu \right) \\&\leq\max\left(\Norm{\partial_n\op{E}(\var0_n)}_*, \max_{j\in \op{leaf}(J_n)} \norm{\1_{\supp(w_j)}\A^*\vec{\varphi}_n}_{L^2} -\mu \right).\label{eq: wavelet error metric}
 	\end{align}
@@
 	We consider two phantoms where the ground-truth is either a binary disc or the Shepp-Logan phantom.
-\edit{No noise is added to the Shepp-Logan data but 5\% Gaussian white noise is added to the disc data.}{Both examples are corrupted with \SI{2}{\percent} Laplace distributed noise.} This is visualised in Figure~\ref{fig: haar data}.
-All optimisations shown are spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$.
+\edit{No noise is added to the Shepp-Logan data but 5\% Gaussian white noise is added to the disc data.}{Both examples are corrupted with \SI{2}{\percent} Laplace distributed noise.} This is visualised in Fig.~\ref{fig: haar data}.
+All optimisations shown are spatially adaptive using Haar wavelets and initialised with $\F{U}^0= \{x\mapsto c\st c\in\F R\}$.
 The gradient metric shown throughout is the $\ell^\infty$ norm.
 Motivated by \eqref{eq: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ to ensure that
-	$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\op{E}(\varf0_n)}_*$$
+	$$ \norm{\1_{\supp(w_j)}\A^*\vec{\varphi}_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\op{E}(\var0_n)}_*$$
 	for all $j$ and $n$ (i.e. so that the continuous gradient is less than 10 times the discrete gradient).
-	\edit{}{We do not expect wavelet regularisation to have state-of-the-art performance in the examples of Figure~\ref{fig: haar data}.
+	\edit{}{We do not expect wavelet regularisation to have state-of-the-art performance in the examples of Fig.~\ref{fig: haar data}.
 What they demonstrate is the preference Haar wavelets have to align large discontinuities with a coarse grid, even when the discretisation is allowed to be as fine as necessary.
@@
 
-	The first numerical results shown in Figure~\ref{fig: haar convergence} compare the same adaptive FISTA variants as shown in Figure~\ref{fig: convergence with method}.
+	The first numerical results shown in Fig.~\ref{fig: haar convergence} compare the same adaptive FISTA variants as shown in Fig.~\ref{fig: convergence with method}.
 In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower.
@@
 		\includegraphics[width=.85\textwidth]{haar_convergence_short}
-		\caption{\edit{Discrete }{}Convergence of different implementations of Algorithm~\ref{alg: refining FISTA} with an unlimited number of pixels.}\label{fig: haar convergence}
+		\caption{\edit{Discrete }{}Convergence of different implementations of Algorithm~\ref{alg: refining FISTA} with an unlimited number of pixels for sparse wavelet optimisation.}\label{fig: haar convergence}
 
@@
 	Our final application is a super-resolution/de-blurring inverse problem from biological microscopy.
-In mathematical terms, the observed data is a large number of sparse images which are corrupted by blurring and a large amount of noise, examples are seen in Figure~\ref{fig: STORM data}.
-The task is to compute the centres of the spikes of signal in each image and then re-combine into a single super-resolved image, as in Figure~\ref{fig: STORM results}.
+In mathematical terms, the observed data is a large number of sparse images which are corrupted by blurring and a large amount of noise, examples are seen in Fig.~\ref{fig: STORM data}.
+The task is to compute the centres of the spikes of signal in each image and then re-combine into a single super-resolved image, as in Fig.~\ref{fig: STORM results}.
 This technique is referred to as \emph{Single Molecule Localisation Microscopy} (SMLM), of which we consider the specific example of \emph{Stochastic Optical Reconstruction Microscopy} (STORM).
@@
 	\begin{equation}
-		(\A\varf0)_{i} = (2\pi\sigma^2)^{-1}\int_{[0,6.4]^2} \exp\left(-\frac{1}{2\sigma^2}\left|\vvarx0- \Delta\begin{pmatrix}i_1+\tfrac12 & i_2+\tfrac12\end{pmatrix}^\top \right|^2\right)\varf0(\vvarx0)\,d\vvarx0, \qquad \sigma=0.2,\ \Delta=0.1
-	\end{equation}
-	for $i_1,i_2 = 1,2,\ldots,64$ and $\spcf0=\C M([0,6.4]^2)$ with lengths in $\SI{}{\micro\meter}$.
-3020 frames are provided, examples of which are shown in Figure~\ref{fig: STORM data}.
+		(\A\var0)_{i} = (2\pi\sigma^2)^{-1}\int_{[0,6.4]^2} \exp\left(-\frac{1}{2\sigma^2}\left|\vec{x}- \Delta\begin{pmatrix}i_1+\tfrac12 & i_2+\tfrac12\end{pmatrix}^\top \right|^2\right)\var0(\vec{x})\,d\vec{x}, \qquad \sigma=0.2,\ \Delta=0.1
+	\end{equation}
+	for $i_1,i_2 = 1,2,\ldots,64$ and $\F{U}=\C M([0,6.4]^2)$ with lengths in $\SI{}{\micro\meter}$.
+3020 frames are provided, examples of which are shown in Fig.~\ref{fig: STORM data}.
 To process this dataset, image intensities were normalised to $[0,1]$ then a constant was subtracted to approximate 0-mean noise.
@@
 
-	Finally, all the reconstructions were summed and the result shown in Figure~\ref{fig: STORM results}.
+	Finally, all the reconstructions were summed and the result shown in Fig.~\ref{fig: STORM results}.
 The adaptive scheme used fewer than $10^4$ pixels per frame, a fixed discretisation with equivalent resolution of \SI{1.3}{\nano\meter} would have required more than $3\cdot10^6$ per frame.
@@
 
-	Figure~\ref{fig: STORM convergence} shows slightly faster convergence than $n^{-2/3}$ predicted by \eqref{eq: Lasso resolution rate} in dimension $d=2$.
-In this example we also implement the suggestion of Section~\ref{sec: support detection} to remove pixels outside of the support of $\varf0^*$.
+	Fig.~\ref{fig: STORM convergence} shows slightly faster convergence than $n^{-2/3}$ predicted by \eqref{eq: Lasso resolution rate} in dimension $d=2$.
+In this example we also implement the suggestion of Section~\ref{sec: support detection} to remove pixels outside of the support of $\var0^*$.
 From \eqref{eq: support equation}, any pixel $\domain_i^n$ satisfying
 	\begin{equation}
-		\vars2_0 \norm{ \tens{\Pi}_n\A^*\vvard0_n }_{L^\infty(\domain_i^n)} \leq (1-\op{threshold}_n)\mu
-	\end{equation}
-	guarantees that $\domain_i^n\cap\op{supp}(\varf0^*) = \emptyset$.
-This threshold is plotted in the first panel of Figure~\ref{fig: STORM convergence}.
+		\vars2_0 \norm{ \tens{\Pi}_n\A^*\vec{\varphi}_n }_{L^\infty(\domain_i^n)} \leq (1-\op{threshold}_n)\mu
+	\end{equation}
+	guarantees that $\domain_i^n\cap\op{supp}(\var0^*) = \emptyset$.
+This threshold is plotted in the first panel of Fig.~\ref{fig: STORM convergence}.
 Once the value becomes less than 1, we can start reducing the number of pixels instead of continual refinement, as seen in the right-hand panel after around 30 iterations.
@@
 	\end{acknowledgements}
-	\begingroup
+
+	\begin{dataavailability}
+		The synthetic STORM dataset was provided as part of the 2016 SMLM challenge, \url{http://bigwww.epfl.ch/smlm/challenge2016/datasets/MT4.N2.HD/Data/data.html}.
+The remaining examples used in this work can be generated with the supplementary code, \url{https://github.com/robtovey/2020SpatiallyAdaptiveFISTA}.
+	\end{dataavailability}
+
 	\bibliography{references}
-	\endgroup
 	\appendix
@@
 	This section contains all of the statements and proofs of the results contained in Section~\ref{sec: FISTA convergence}.
-\edit{}{Recall that the subsets $\spcf0^n\subset\F H$ satisfy \eqref{eq: refining subspace definition}.}
+\edit{}{Recall that the subsets $\F{U}^n\subset\F H$ satisfy \eqref{eq: refining subspace definition}.}
 
@@
 		\begin{equation}
-			t_{n}^2(\op{E}(\varf0_{n}) - \op{E}(\varf2_n)) - (t_{n}^2-t_{n})(\op{E}(\varf0_{n-1})-\op{E}(\varf2_n)) \leq \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.
+			t_{n}^2(\op{E}(\var0_{n}) - \op{E}(\var2_n)) - (t_{n}^2-t_{n})(\op{E}(\var0_{n-1})-\op{E}(\var2_n)) \leq \tfrac1{2}\left[\norm{\var1_{n-1}}^2-\norm{\var1_{n}}^2\right] + \IP{\var1_{n}-\var1_{n-1}}{\var2_n}.
 			\label{app:eq: one-step FISTA}
@@
 	\begin{proof}
-		Modifying \cite[\edit{Theorem 2}{Thm 3.2}]{Chambolle2015}, for $n\geq1$ we apply Lemma~\ref{thm: descent lemma} with $\bar{\varf0} = \bar{\varf0}_{n-1}$ and $\varf2 = (1-\frac{1}{t_{n}})\varf0_{n-1} + \frac{1}{t_{n}}\varf2_n$.
-\edit{}{By \eqref{eq: refining subspace definition}, $\varf0_{n-1}\in\spcf0^n$ is convex so $\varf2\in \spcf0^n$.
+		Modifying \cite[\edit{Theorem 2}{Thm 3.2}]{Chambolle2015}, for $n\geq1$ we apply Lemma~\ref{thm: descent lemma} with $\bar{\var0} = \bar{\var0}_{n-1}$ and $\var2 = (1-\frac{1}{t_{n}})\var0_{n-1} + \frac{1}{t_{n}}\var2_n$.
+\edit{}{By \eqref{eq: refining subspace definition}, $\var0_{n-1}\in\F{U}^n$ is convex so $\var2\in \F{U}^n$.
 }This gives
 		\begin{equation}
-			\op{E}(\varf0_{n}) + \tfrac12\norm{\tfrac{1}{t_{n}}\varf1_{n}-\tfrac{1}{t_{n}}\varf2_n}^2 \leq \op{E}\left((1-\tfrac{1}{t_{n}})\varf0_{n-1}+\tfrac{1}{t_{n}}\varf2_n\right) + \tfrac12\norm{\tfrac{1}{t_{n}}\varf1_{n-1}-\tfrac{1}{t_{n}}\varf2_n}^2.
+			\op{E}(\var0_{n}) + \tfrac12\norm{\tfrac{1}{t_{n}}\var1_{n}-\tfrac{1}{t_{n}}\var2_n}^2 \leq \op{E}\left((1-\tfrac{1}{t_{n}})\var0_{n-1}+\tfrac{1}{t_{n}}\var2_n\right) + \tfrac12\norm{\tfrac{1}{t_{n}}\var1_{n-1}-\tfrac{1}{t_{n}}\var2_n}^2.
 		\end{equation}
@@
 		\begin{equation}
-			\op{E}(\varf0_{n}) - \op{E}(\varf2_n) - (1-\tfrac{1}{t_{n}})[\op{E}(\varf0_{n-1})-\op{E}(\varf2_n)] \leq \tfrac1{2t_{n}^2}\norm{\varf1_{n-1}-\varf2_n}^2 - \tfrac1{2t_{n}^2}\norm{\varf1_{n}-\varf2_n}^2 = \tfrac1{2t_{n}^2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_{n}}^2\right] + \tfrac1{t_{n}^2}\IP{\varf1_{n}-\varf1_{n-1}}{\varf2_n}.
+			\op{E}(\var0_{n}) - \op{E}(\var2_n) - (1-\tfrac{1}{t_{n}})[\op{E}(\var0_{n-1})-\op{E}(\var2_n)] \leq \tfrac1{2t_{n}^2}\norm{\var1_{n-1}-\var2_n}^2 - \tfrac1{2t_{n}^2}\norm{\var1_{n}-\var2_n}^2 = \tfrac1{2t_{n}^2}\left[\norm{\var1_{n-1}}^2-\norm{\var1_{n}}^2\right] + \tfrac1{t_{n}^2}\IP{\var1_{n}-\var1_{n-1}}{\var2_n}.
 		\end{equation}
@@
 		Theorem~\ref{app:thm: mini FISTA convergence} is just a summation of \eqref{app:eq: one-step FISTA} over all $n=1,\ldots,N$.
-To see this: first add and subtract $\edit{\op{E}(\varf0^*)}{\Emin}$ to each term on the left-hand side to convert $\op{E}$ to $\op{E}_0$, then move $\op{E}_0(\varf2_n)$ to the right-hand side.
+To see this: first add and subtract $\edit{\op{E}(\var0^*)}{\Emin}$ to each term on the left-hand side to convert $\op{E}$ to $\op{E}_0$, then move $\op{E}_0(\var2_n)$ to the right-hand side.
 Now \eqref{app:eq: one-step FISTA} becomes
 		\begin{equation}
-			t_n^2\op{E}_0(\varf0_n) - (t_n^2-t_n)\op{E}_0(\varf0_{n-1}) \leq t_n\op{E}_0(\varf2_n) + \tfrac1{2}\left[\norm{\varf1_{n-1}}^2-\norm{\varf1_n}^2\right] + \IP{\varf1_n-\varf1_{n-1}}{\varf2_n}. 
+			t_n^2\op{E}_0(\var0_n) - (t_n^2-t_n)\op{E}_0(\var0_{n-1}) \leq t_n\op{E}_0(\var2_n) + \tfrac1{2}\left[\norm{\var1_{n-1}}^2-\norm{\var1_n}^2\right] + \IP{\var1_n-\var1_{n-1}}{\var2_n}. 
 		\end{equation}
@@
 		\begin{equation}
-			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}(\underbrace{t_n^2-t_{n+1}^2+t_{n+1}}_{=\rho_n})\op{E}_0(\varf0_n) \leq \frac{\norm{\varf1_0}^2-\norm{\varf1_N}^2}{2} + \sum_{n=1}^N t_n\op{E}_0(\varf2_n)+\IP{\varf1_n-\varf1_{n-1}}{\varf2_n}.
-		\end{equation}
-		This is almost in the desired form, however, we would like to flip the roles of $\varf1_n$/$\varf2_n$ in the final inner product term. Re-writing the right-hand side gives
-		\begin{equation}
-			\sum_{n=1}^N\IP{\varf1_n-\varf1_{n-1}}{\varf2_n} = \IP{\varf1_N}{\varf2_N} - \IP{\varf1_0}{\varf2_0}+ \sum_{n=1}^N\IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
-		\end{equation}
-		Noting that $\varf1_0=\varf0_0$, the previous two equations combine to prove the statement of Theorem~\ref{app:thm: mini FISTA convergence}.
+			t_N^2\op{E}_0(\var0_N) + \sum_{n=1}^{N-1}(\underbrace{t_n^2-t_{n+1}^2+t_{n+1}}_{=\rho_n})\op{E}_0(\var0_n) \leq \frac{\norm{\var1_0}^2-\norm{\var1_N}^2}{2} + \sum_{n=1}^N t_n\op{E}_0(\var2_n)+\IP{\var1_n-\var1_{n-1}}{\var2_n}.
+		\end{equation}
+		This is almost in the desired form, however, we would like to flip the roles of $\var1_n$/$\var2_n$ in the final inner product term. Re-writing the right-hand side gives
+		\begin{equation}
+			\sum_{n=1}^N\IP{\var1_n-\var1_{n-1}}{\var2_n} = \IP{\var1_N}{\var2_N} - \IP{\var1_0}{\var2_0}+ \sum_{n=1}^N\IP{\var1_{n-1}}{\var2_{n-1}-\var2_n}.
+		\end{equation}
+		Noting that $\var1_0=\var0_0$, the previous two equations combine to prove the statement of Theorem~\ref{app:thm: mini FISTA convergence}.
 		\qed\end{proof}
@@
 	\begin{proof}
-		This is just a telescoping of the right-hand side of \eqref{app:eq: FISTA inequality} with the introduction of $n_k$ and simplification $\varf2_n = \tilde{\varf2}_k$,
-		\begin{equation}
-			\tfrac12\norm{\varf2_N}^2 + \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n} = \tfrac12\norm{\tilde{\varf2}_K}^2 + \sum_{n=n_K}^Nt_n\op{E}_0(\tilde{\varf2}_K) 
-			+ \sum_{k=1}^K\sum_{n=n_{k-1}}^{n_k-1}t_n\op{E}_0(\tilde{\varf2}_{k-1}) 
-			+ \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}.
+		This is just a telescoping of the right-hand side of \eqref{app:eq: FISTA inequality} with the introduction of $n_k$ and simplification $\var2_n = \tilde{\var2}_k$,
+		\begin{equation}
+			\tfrac12\norm{\var2_N}^2 + \sum^N_{n=1} t_n\op{E}_0(\var2_n) + \IP{\var1_{n-1}}{\var2_{n-1}-\var2_n} = \tfrac12\norm{\tilde{\var2}_K}^2 + \sum_{n=n_K}^Nt_n\op{E}_0(\tilde{\var2}_K) 
+			+ \sum_{k=1}^K\sum_{n=n_{k-1}}^{n_k-1}t_n\op{E}_0(\tilde{\var2}_{k-1}) 
+			+ \IP{\var1_{n_k-1}}{\tilde{\var2}_k-\tilde{\var2}_{k+1}}.
 		\end{equation}
@@
 		\begin{align}
-			t_N^2\op{E}_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\op{E}_0(\tilde{\varf2}_K) \notag
-			\\&\hspace{70pt}+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\op{E}_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}
-			\\& \leq C + \frac{\norm{\tilde{\varf2}_K}^2}{2} + \frac{(N+1)^2}{2}\op{E}_0(\tilde{\varf2}_K) \notag
-			\\&\hspace{40pt}+\sum_{k=1}^K \frac{n_k^2}{2}\op{E}_0(\tilde{\varf2}_{k-1}) + \IP{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}+\tilde{\varf2}_{k-1}}{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}.
-		\end{align}
-		The inductive step now depends on the value of $\vars3_{\Varf0}$.
+			t_N^2\op{E}_0(\var0_N) + \tfrac12\norm{\var1_N-\tilde{\var2}_K}^2 &\leq C + \frac{\norm{\tilde{\var2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\op{E}_0(\tilde{\var2}_K) \notag
+			\\&\hspace{70pt}+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\op{E}_0(\tilde{\var2}_{k-1}) + \IP{\var1_{n_k-1}}{\tilde{\var2}_k-\tilde{\var2}_{k+1}}
+			\\& \leq C + \frac{\norm{\tilde{\var2}_K}^2}{2} + \frac{(N+1)^2}{2}\op{E}_0(\tilde{\var2}_K) \notag
+			\\&\hspace{40pt}+\sum_{k=1}^K \frac{n_k^2}{2}\op{E}_0(\tilde{\var2}_{k-1}) + \IP{\var1_{n_k-1}-\tilde{\var2}_{k-1}+\tilde{\var2}_{k-1}}{\tilde{\var2}_k-\tilde{\var2}_{k+1}}.
+		\end{align}
+		The inductive step now depends on the value of $\vars3_U$.
 		\begin{description}
-			\item[Case $\vars3_{\Varf0}>1$:] We simplify the inequality
-			\begin{align}
-				t_N^2\op{E}_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim \vars3_{\Varf0}^{2K} + (N+1)^2\vars3_{\op{E}}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\op{E}}^{-k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + \vars3_{\Varf0}^{2k}
-				\\&\leq C_1\left[\vars3_{\Varf0}^{2K+2} + \sum_{k=1}^{K}\vars3_{\Varf0}^{2k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\right]
-			\end{align}
-			for some $C_1>C$. Choose $C_2\geq \norm{\varf1_{n_1-1}-\tilde{\varf2}_{1-1}}\vars3_{\Varf0}^{-1}$ such that 
-			\begin{equation}
-				\frac12C_2^2 \geq \frac{C_1}{\vars3_{\Varf0}^2-1}(C_2+\vars3_{\Varf0}^2).
-			\end{equation}
-			Assume $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2\vars3_{\Varf0}^k$ for $1\leq k\leq K$ (trivially true for $K=1$), then for $N=n_{K+1}-1$ we have 
-			\begin{align}
-				\tfrac12\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}^2 &\leq C_1\left[\vars3_{\Varf0}^{2K+2} + \sum_{k=1}^{K}\vars3_{\Varf0}^{2k} + \vars3_{\Varf0}^{k}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\right]
-				\\&\leq C_1\left[\vars3_{\Varf0}^{2K+2} + (1+C_2)\frac{\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\right]
-				\\&\leq \frac{C_1\vars3_{\Varf0}^{2K+2}}{\vars3_{\Varf0}^2-1}\left(\vars3_{\Varf0}^2+C_2\right) \leq \tfrac12(C_2\vars3_{\Varf0}^{K+1})^2.
-			\end{align}
-
-			\item[Case $\vars3_{\Varf0}=1$:] Denote $\vars4_k = \norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}$ and note that $\norm{\tilde{\varf2}_{k-1}} \leq \norm{\tilde{\varf2}_{0}} + \sum_0^\infty \vars4_k\lesssim 1$.
+			\item[Case $\vars3_U>1$:] We simplify the inequality
+			\begin{align}
+				t_N^2\op{E}_0(\var0_N) + \tfrac12\norm{\var1_N-\tilde{\var2}_K}^2 &\lesssim \vars3_U^{2K} + (N+1)^2\vars3_{\op{E}}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\op{E}}^{-k} + \vars3_U^{k}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}} + \vars3_U^{2k}
+				\\&\leq C_1\left[\vars3_U^{2K+2} + \sum_{k=1}^{K}\vars3_U^{2k} + \vars3_U^{k}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\right]
+			\end{align}
+			for some $C_1>C$. Choose $C_2\geq \norm{\var1_{n_1-1}-\tilde{\var2}_{1-1}}\vars3_U^{-1}$ such that 
+			\begin{equation}
+				\frac12C_2^2 \geq \frac{C_1}{\vars3_U^2-1}(C_2+\vars3_U^2).
+			\end{equation}
+			Assume $\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\leq C_2\vars3_U^k$ for $1\leq k\leq K$ (trivially true for $K=1$), then for $N=n_{K+1}-1$ we have 
+			\begin{align}
+				\tfrac12\norm{\var1_{n_{K+1}-1}-\tilde{\var2}_K}^2 &\leq C_1\left[\vars3_U^{2K+2} + \sum_{k=1}^{K}\vars3_U^{2k} + \vars3_U^{k}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\right]
+				\\&\leq C_1\left[\vars3_U^{2K+2} + (1+C_2)\frac{\vars3_U^{2K+2}}{\vars3_U^2-1}\right]
+				\\&\leq \frac{C_1\vars3_U^{2K+2}}{\vars3_U^2-1}\left(\vars3_U^2+C_2\right) \leq \tfrac12(C_2\vars3_U^{K+1})^2.
+			\end{align}
+
+			\item[Case $\vars3_U=1$:] Denote $\vars4_k = \norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}$ and note that $\norm{\tilde{\var2}_{k-1}} \leq \norm{\tilde{\var2}_{0}} + \sum_0^\infty \vars4_k\lesssim 1$.
 We therefore bound
 			\begin{align}
-				t_N^2\op{E}_0(\varf0_N) + \tfrac12\norm{\varf1_N-\tilde{\varf2}_K}^2 &\lesssim 1 + (N+1)^2\vars3_{\op{E}}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\op{E}}^{-k} + (\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}} + 1)b_k
-				\\&\leq C_1\left[1 + \sum_{k=1}^{K}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\vars4_k\right]
-			\end{align}
-			for some $C_1>0$. Choose $C_2\geq \frac{\norm{\varf1_{n_1-1}-\tilde{\varf2}_{1-1}}}{\sum_0^\infty \vars4_k}$ such that 
+				t_N^2\op{E}_0(\var0_N) + \tfrac12\norm{\var1_N-\tilde{\var2}_K}^2 &\lesssim 1 + (N+1)^2\vars3_{\op{E}}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\op{E}}^{-k} + (\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}} + 1)b_k
+				\\&\leq C_1\left[1 + \sum_{k=1}^{K}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\vars4_k\right]
+			\end{align}
+			for some $C_1>0$. Choose $C_2\geq \frac{\norm{\var1_{n_1-1}-\tilde{\var2}_{1-1}}}{\sum_0^\infty \vars4_k}$ such that 
 			\begin{equation}
@@
 			\end{equation}
-			Assume $\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\leq C_2$ for $1\leq k\leq K$ (trivially true for $K=1$), then for $N=n_{K+1}-1$ we have 
-			\begin{equation}
-				\tfrac12\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}^2 \leq C_1\left[1 + \sum_{k=1}^{K}\norm{\varf1_{n_k-1}-\tilde{\varf2}_{k-1}}\vars4_k\right]
+			Assume $\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\leq C_2$ for $1\leq k\leq K$ (trivially true for $K=1$), then for $N=n_{K+1}-1$ we have 
+			\begin{equation}
+				\tfrac12\norm{\var1_{n_{K+1}-1}-\tilde{\var2}_K}^2 \leq C_1\left[1 + \sum_{k=1}^{K}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\vars4_k\right]
 				\leq C_1\left(1+C_2\sum_1^\infty\vars4_k\right) \leq \frac{C_2^2}{2}
@@
 		\end{description}
-		In both cases, the induction on $\norm{\varf1_{n_{K+1}-1}-\tilde{\varf2}_K}$ holds for all $K$ and we have 
-		\begin{equation}
-			t_N^2\op{E}_0(\varf0_N) \leq \frac{C_2^2}{2}\vars3_{\Varf0}^{2K}
+		In both cases, the induction on $\norm{\var1_{n_{K+1}-1}-\tilde{\var2}_K}$ holds for all $K$ and we have 
+		\begin{equation}
+			t_N^2\op{E}_0(\var0_N) \leq \frac{C_2^2}{2}\vars3_U^{2K}
 		\end{equation}
@@
 		\begin{equation}
-			\log N^2 \geq \log C + K\left(\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2\right)
+			\log N^2 \geq \log C + K\left(\log \vars3_{\op{E}} + \log \vars3_U^2\right)
 		\end{equation}
@@
 		\begin{equation}
-			\vars3_{\Varf0}^{2K} = \exp(K\log \vars3_{\Varf0}^2)
-			\leq \exp\left(\log N^2\frac{\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2} - \frac{\log C\log \vars3_{\Varf0}^2}{\log \vars3_{\op{E}} + \log \vars3_{\Varf0}^2}\right)
+			\vars3_U^{2K} = \exp(K\log \vars3_U^2)
+			\leq \exp\left(\log N^2\frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2} - \frac{\log C\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2}\right)
 		\end{equation}
@@
 		\begin{equation}
-			n_k^2\lesssim \splitln{(\vars3_{\op{E}}\vars3_{\Varf0}^2)^k}{\vars3_{\Varf0}>1}{k^{-2}\vars3_{\op{E}}^k}{\vars3_{\Varf0}=1}, \qquad \norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^{k}, \qquad \text{ and } \op{E}_0(\tilde{\varf2}_k)\lesssim \vars3_{\op{E}}^{-k}
-		\end{equation}
-		and $\sum_{k=1}^\infty\norm{\tilde{\varf2}_k-\tilde{\varf2}_{k+1}}<\infty$ when $\vars3_{\Varf0}=1$. The only one which is not directly assumed is easily verified,
-		\begin{equation}
-			\op{E}_0(\tilde{\varf2}_k) = \min_{\varf0\in\spcf0^{n_k}}\op{E}_0(\varf0) \leq\op{E}_0(\varf0_{n_k-1}) \lesssim \vars3_{\op{E}}^{-k}.
+			n_k^2\lesssim \splitln{(\vars3_{\op{E}}\vars3_U^2)^k}{\vars3_U>1}{k^{-2}\vars3_{\op{E}}^k}{\vars3_U=1}, \qquad \norm{\tilde{\var2}_k}\lesssim \vars3_U^{k}, \qquad \text{ and } \op{E}_0(\tilde{\var2}_k)\lesssim \vars3_{\op{E}}^{-k}
+		\end{equation}
+		and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty$ when $\vars3_U=1$. The only one which is not directly assumed is easily verified,
+		\begin{equation}
+			\op{E}_0(\tilde{\var2}_k) = \min_{\var0\in\F{U}^{n_k}}\op{E}_0(\var0) \leq\op{E}_0(\var0_{n_k-1}) \lesssim \vars3_{\op{E}}^{-k}.
 		\end{equation}
@@
 		\begin{equation}
-			\op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{t_N^2} \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2}.
-		\end{equation}
-		In the case $\vars3_{\Varf0}=1$, this is already the optimal rate and therefore sharp.
-If this were sharp for general $\vars3_{\Varf0}$ and $\op{E}$, then we gain nothing by refining early (increasing $K$ for fixed $N$) however, we can at least guarantee that refining early does not lose the optimal rate.
-
-		If we fix $N^2\lesssim (\vars3_{\op{E}}\vars3_{\Varf0}^2)^k$, then
-		\begin{equation}
-			\min_{n\leq N} \op{E}_0(\varf0_n)\lesssim \splitln{\vars3_{\op{E}}^{-k}}{N>n_k}{ \frac{\vars3_{\Varf0}^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_{\Varf0}^{2k},\vars3_{\Varf0}^{2k}) \lesssim N^{-2(1-\kappa)}
+			\op{E}_0(\var0_N) \lesssim \frac{\vars3_U^{2K}}{t_N^2} \lesssim \frac{\vars3_U^{2K}}{N^2}.
+		\end{equation}
+		In the case $\vars3_U=1$, this is already the optimal rate and therefore sharp.
+If this were sharp for general $\vars3_U$ and $\op{E}$, then we gain nothing by refining early (increasing $K$ for fixed $N$) however, we can at least guarantee that refining early does not lose the optimal rate.
+
+		If we fix $N^2\lesssim (\vars3_{\op{E}}\vars3_U^2)^k$, then
+		\begin{equation}
+			\min_{n\leq N} \op{E}_0(\var0_n)\lesssim \splitln{\vars3_{\op{E}}^{-k}}{N>n_k}{ \frac{\vars3_U^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_U^{2k},\vars3_U^{2k}) \lesssim N^{-2(1-\kappa)}
 		\end{equation}
@@
 		The proof is simply to justify that the conditions of Theorem~\ref{app:thm: stronger exponential FISTA convergence} are met for all refinement criteria described here.
-$\norm{\tilde{\varf2}_k}\lesssim \vars3_{\Varf0}^k$ is enforced at every step and condition (2) guarantees the back-stop condition on $n_k$.
-
-		To complete the requirements of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, we first need to show inductively that $\op{E}_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\op{E}}^{-k}$, then it follows that $\op{E}_0(\varf0_{n_k-1})\leq C\vars3_{\op{E}}^{-k}$.
-To be explicit, when $\op{E}$ has bounded sublevel sets, assume that the bound for $\{\varf0\in\F H\st \op{E}(\varf0)\leq \op{E}(\varf0_0)\}$ is $R>0$.
-
-		For (2) and (5) the decay of $\op{E}_0(\tilde{\varf2}_{k-1})$ is already assumed but otherwise we need to perform the formal induction.
-Assume $\op{E}_0(\tilde{\varf2}_{k-1}) \leq C\vars3_{\op{E}}^{1-k}$, then for each remaining adaptive criterion:
+$\norm{\tilde{\var2}_k}\lesssim \vars3_U^k$ is enforced at every step and condition (2) guarantees the back-stop condition on $n_k$.
+
+		To complete the requirements of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, we first need to show inductively that $\op{E}_0(\tilde{\var2}_{k-1}) \leq C\vars3_{\op{E}}^{-k}$, then it follows that $\op{E}_0(\var0_{n_k-1})\leq C\vars3_{\op{E}}^{-k}$.
+To be explicit, when $\op{E}$ has bounded sublevel sets, assume that the bound for $\{\var0\in\F H\st \op{E}(\var0)\leq \op{E}(\var0_0)\}$ is $R>0$.
+
+		For (2) and (5) the decay of $\op{E}_0(\tilde{\var2}_{k-1})$ is already assumed but otherwise we need to perform the formal induction.
+Assume $\op{E}_0(\tilde{\var2}_{k-1}) \leq C\vars3_{\op{E}}^{1-k}$, then for each remaining adaptive criterion:
 		\begin{itemize}
-			\item[(1)] $\op{E}_0(\tilde{\varf2}_k)\leq \op{E}_0(\varf0_{k})\leq\vars1 \vars3_{\op{E}}^{-k}$ by definition, the induction holds if $C\geq \vars1$.
-			\item[(3)] $\op{E}_0(\tilde{\varf2}_k)\leq \op{E}_0(\varf0_{k})\leq\frac{\vars1}{1-\vars1}\op{E}_0(\tilde{\varf2}_{k-1})$, the induction holds if $\vars1\leq \frac{1}{1+\vars3_{\op{E}}}$.
-			\item[(4)] $\op{E}_0(\tilde{\varf2}_k)\leq \op{E}_0(\varf0_{k}) \leq \IP{\edit{\partial\op{E}(\varf0_{k})}{\varf1}}{\varf0_{n_k-1}-\varf0^*} \leq 2R\vars1\vars3_{\op{E}}^{-k}$\edit{}{ for each $\varf1\in\partial\op{E}(\varf0_{k})$}, the induction holds for $C\geq 2R\vars1$.
+			\item[(1)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\var0_{k})\leq\vars1 \vars3_{\op{E}}^{-k}$ by definition, the induction holds if $C\geq \vars1$.
+			\item[(3)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\var0_{k})\leq\frac{\vars1}{1-\vars1}\op{E}_0(\tilde{\var2}_{k-1})$, the induction holds if $\vars1\leq \frac{1}{1+\vars3_{\op{E}}}$.
+			\item[(4)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\var0_{k}) \leq \IP{\edit{\partial\op{E}(\var0_{k})}{\var1}}{\var0_{n_k-1}-\var0^*} \leq 2R\vars1\vars3_{\op{E}}^{-k}$\edit{}{ for each $\var1\in\partial\op{E}(\var0_{k})$}, the induction holds for $C\geq 2R\vars1$.
 		\end{itemize}
 		In each case, with $C$ sufficiently large, the induction holds.
-Now we can return to the precise condition of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, $\op{E}_0(\varf0_{n_k-1}) \leq C'\vars3_{\op{E}}^{-k}$.
+Now we can return to the precise condition of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, $\op{E}_0(\var0_{n_k-1}) \leq C'\vars3_{\op{E}}^{-k}$.
 Assume true for $k-1$.
@@
 		\begin{itemize}
-			\item[(1)] $\op{E}_0(\varf0_{k})\leq\vars1 \vars3_{\op{E}}^{-k}$ is by definition.
-			\item[(2)] $\op{E}_0(\varf0_{k})\leq\vars1 \vars3_{\op{E}}^{-k} + \op{E}_0(\tilde{\varf2}_{k-1})$ requires $C'\geq \vars1+\vars3_{\op{E}}C$.
-			\item[(3)] $\op{E}_0(\varf0_{k})\leq\frac{\vars1}{1-\vars1}\op{E}_0(\tilde{\varf2}_{k-1})$ requires $C'\geq \frac{\vars1}{1-\vars1}C$.
-			\item[(4)] $\op{E}_0(\varf0_{k}) \leq 2R\vars1\vars3_{\op{E}}^{-k}$, the induction holds for large $C'$.
-			\item[(5)] $\op{E}_0(\varf0_{k})\leq 2R\vars1\vars3_{\op{E}}^{-k} + \op{E}_0(\tilde{\varf2}_{k-1})$, the induction holds for large $C'\geq 2R\vars1+C$.
+			\item[(1)] $\op{E}_0(\var0_{k})\leq\vars1 \vars3_{\op{E}}^{-k}$ is by definition.
+			\item[(2)] $\op{E}_0(\var0_{k})\leq\vars1 \vars3_{\op{E}}^{-k} + \op{E}_0(\tilde{\var2}_{k-1})$ requires $C'\geq \vars1+\vars3_{\op{E}}C$.
+			\item[(3)] $\op{E}_0(\var0_{k})\leq\frac{\vars1}{1-\vars1}\op{E}_0(\tilde{\var2}_{k-1})$ requires $C'\geq \frac{\vars1}{1-\vars1}C$.
+			\item[(4)] $\op{E}_0(\var0_{k}) \leq 2R\vars1\vars3_{\op{E}}^{-k}$, the induction holds for large $C'$.
+			\item[(5)] $\op{E}_0(\var0_{k})\leq 2R\vars1\vars3_{\op{E}}^{-k} + \op{E}_0(\tilde{\var2}_{k-1})$, the induction holds for large $C'\geq 2R\vars1+C$.
 		\end{itemize}
@@
 		Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
-Let $\spcf0\subset \edit{\spcf0\cap}{}\F H$ be a finite dimensional subspace with orthonormal basis $\{e_j\st j=1,\ldots,\op{dim}(\spcf0)\}\subset\spcf0$ and orthogonal projection $\tens{\Pi}\colon\F H\to\spcf0$.
+Let $\F{U}\subset \edit{\F{U}\cap}{}\F H$ be a finite dimensional subspace with orthonormal basis $\{e_j\st j=1,\ldots,\op{dim}(\F{U})\}\subset\F{U}$ and orthogonal projection $\tens{\Pi}\colon\F H\to\F{U}$.
 If these conditions hold:
 		\begin{itemize}
-			\item if $q\geq 2$, then $$\norm{\tens{\Pi}\varf2} \lesssim \Norm{\varf2}, $$
-			\item otherwise, if $e_j\in \spcf0^*$, then
-			\begin{equation}
-				\norm{\tens{\Pi}\varf2} \leq \sqrt{\op{dim}(\spcf0)}\max_{j\leq \op{dim}(\spcf0)}\Norm{e_j}_*\Norm{\varf2},
-			\end{equation}
-			\item otherwise, if $e_j\in L^\infty(\Domain)$ and $ |\{j:e_j(\vvarx0)\neq 0\}|\leq C$ for almost all $\vvarx0\in\Domain$, then
-			\begin{equation}
-				\norm{\tens{\Pi}\varf2} \lesssim \sqrt C\max_{j\leq\op{dim}(\spcf0)}\norm{e_j}_{\infty}\Norm{\varf2}
+			\item if $q\geq 2$, then $$\norm{\tens{\Pi}\var2} \lesssim \Norm{\var2}, $$
+			\item otherwise, if $e_j\in \F{U}^*$, then
+			\begin{equation}
+				\norm{\tens{\Pi}\var2} \leq \sqrt{\op{dim}(\F{U})}\max_{j\leq \op{dim}(\F{U})}\Norm{e_j}_*\Norm{\var2},
+			\end{equation}
+			\item otherwise, if $e_j\in L^\infty(\Domain)$ and $ |\{j:e_j(\vec{x})\neq 0\}|\leq C$ for almost all $\vec{x}\in\Domain$, then
+			\begin{equation}
+				\norm{\tens{\Pi}\var2} \lesssim \sqrt C\max_{j\leq\op{dim}(\F{U})}\norm{e_j}_{\infty}\Norm{\var2}
 			\end{equation}
 		\end{itemize}
-		uniformly for all $\varf2\in \F H$.
+		uniformly for all $\var2\in \F H$.
 	\end{lemma}
@@
 		\begin{equation}
-			\norm{\tens{\Pi}\varf2}^2 \leq \norm{\varf2}^2 = \norm{\varf2}_2^2 = \norm{\varf2^2}_1 \lesssim \norm{\varf2}_q^2 \lesssim \Norm{\varf2}^2.
+			\norm{\tens{\Pi}\var2}^2 \leq \norm{\var2}^2 = \norm{\var2}_2^2 = \norm{\var2^2}_1 \lesssim \norm{\var2}_q^2 \lesssim \Norm{\var2}^2.
 		\end{equation}
@@
 		\begin{equation}
-			\norm{\tens{\Pi}\varf2} = \frac{\IP{\tens{\Pi}\varf2}{\tens{\Pi}\varf2}}{\norm{\tens{\Pi}\varf2}} = \frac{\IP{\tens{\Pi}\varf2}{\varf2}}{\norm{\tens{\Pi}\varf2}} \leq \frac{\Norm{\tens{\Pi}\varf2}_*}{\norm{\tens{\Pi}\varf2}}\Norm{\varf2},
-		\end{equation}
-		therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\spcf0$. Switching to the given basis, for $\varf0 = \sum_{j=1}^{\op{dim}(\spcf0)} \varx3_je_j$ we have
-		\begin{align}
-			\norm{\varf0}^2 &= \sum_{j=1}^{\op{dim}(\spcf0)} \varx3_j^2 = \norm{\vvarx3}_{\ell^2}^2,
-			\\\Norm{\varf0}_*&\leq \sum_{j=1}^{\op{dim}(\spcf0)} |\varx3_j|\Norm{e_j}_* \leq \max_{j\leq\op{dim}(\spcf0)} \Norm{e_j}_*\norm{\vvarx3}_{\ell^1},
-			\\\implies \frac{\Norm{\varf0}_*}{\norm{\varf0}} &\leq \max_{j\leq \op{dim}(\spcf0)}\Norm{e_j}_*\frac{\norm{\vvarx3}_{\ell^1}}{\norm{\vvarx3}_{\ell^2}} \leq \max_{j\leq \op{dim}(\spcf0)}\Norm{e_j}_*\sqrt{\op{dim}(\spcf0)}.
+			\norm{\tens{\Pi}\var2} = \frac{\IP{\tens{\Pi}\var2}{\tens{\Pi}\var2}}{\norm{\tens{\Pi}\var2}} = \frac{\IP{\tens{\Pi}\var2}{\var2}}{\norm{\tens{\Pi}\var2}} \leq \frac{\Norm{\tens{\Pi}\var2}_*}{\norm{\tens{\Pi}\var2}}\Norm{\var2},
+		\end{equation}
+		therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\F{U}$. Switching to the given basis, for $\var0 = \sum_{j=1}^{\op{dim}(\F{U})} r_je_j$ we have
+		\begin{align}
+			\norm{\var0}^2 &= \sum_{j=1}^{\op{dim}(\F{U})} r_j^2 = \norm{\vec{r}}_{\ell^2}^2,
+			\\\Norm{\var0}_*&\leq \sum_{j=1}^{\op{dim}(\F{U})} |r_j|\Norm{e_j}_* \leq \max_{j\leq\op{dim}(\F{U})} \Norm{e_j}_*\norm{\vec{r}}_{\ell^1},
+			\\\implies \frac{\Norm{\var0}_*}{\norm{\var0}} &\leq \max_{j\leq \op{dim}(\F{U})}\Norm{e_j}_*\frac{\norm{\vec{r}}_{\ell^1}}{\norm{\vec{r}}_{\ell^2}} \leq \max_{j\leq \op{dim}(\F{U})}\Norm{e_j}_*\sqrt{\op{dim}(\F{U})}.
 		\end{align}
@@
 		\begin{equation}
-			\norm{\tens{\Pi}\varf2} = \frac{\IP{\tens{\Pi}\varf2}{\varf2}}{\norm{\tens{\Pi}\varf2}} \leq \frac{\norm{\tens{\Pi}\varf2}_{\infty}}{\norm{\tens{\Pi}\varf2}}\norm{\varf2}_1\lesssim  \frac{\norm{\tens{\Pi}\varf2}_{\infty}}{\norm{\tens{\Pi}\varf2}}\norm{\varf2}_q \lesssim \frac{\norm{\tens{\Pi}\varf2}_{\infty}}{\norm{\tens{\Pi}\varf2}}\Norm{\varf2}.
-		\end{equation}
-		This simplifies the equivalence constant because for any $\varf0 = \sum \varx3_je_j$ and $\mu>1$, there exists a set of points $\vvarx0\in\Domain$ with non-zero measure such that $\norm{\varf0}_\infty\leq \mu|\varf0(\vvarx0)|$.
+			\norm{\tens{\Pi}\var2} = \frac{\IP{\tens{\Pi}\var2}{\var2}}{\norm{\tens{\Pi}\var2}} \leq \frac{\norm{\tens{\Pi}\var2}_{\infty}}{\norm{\tens{\Pi}\var2}}\norm{\var2}_1\lesssim  \frac{\norm{\tens{\Pi}\var2}_{\infty}}{\norm{\tens{\Pi}\var2}}\norm{\var2}_q \lesssim \frac{\norm{\tens{\Pi}\var2}_{\infty}}{\norm{\tens{\Pi}\var2}}\Norm{\var2}.
+		\end{equation}
+		This simplifies the equivalence constant because for any $\var0 = \sum r_je_j$ and $\mu>1$, there exists a set of points $\vec{x}\in\Domain$ with non-zero measure such that $\norm{\var0}_\infty\leq \mu|\var0(\vec{x})|$.
 This gives
 		\begin{align}
-			\norm{\varf0}^2 &= \sum \varx3_j^2 \geq \sum_{e_j(\vvarx0)\neq 0} \varx3_j^2,
-			\\\norm{\varf0}_\infty& \leq \mu|\varf0(\vvarx0)| \leq \mu\sum_{e_j(\vvarx0)\neq 0} |\varx3_j|\norm{e_j}_\infty,
-			\\\implies \frac{\norm{\varf0}_\infty}{\norm{\varf0}} &\leq \mu\max_j\norm{e_j}_\infty\sqrt{C}.
+			\norm{\var0}^2 &= \sum r_j^2 \geq \sum_{e_j(\vec{x})\neq 0} r_j^2,
+			\\\norm{\var0}_\infty& \leq \mu|\var0(\vec{x})| \leq \mu\sum_{e_j(\vec{x})\neq 0} |r_j|\norm{e_j}_\infty,
+			\\\implies \frac{\norm{\var0}_\infty}{\norm{\var0}} &\leq \mu\max_j\norm{e_j}_\infty\sqrt{C}.
 		\end{align}
 		This inequality holds for all $\mu>1$ therefore also for $\mu=1$.
-Essentially, with an extra smoothness assumption on $e_j$, we can reduce the dimension of the problem to $\op{dim}(\spcf0)=C $ and use the previous result.
+Essentially, with an extra smoothness assumption on $e_j$, we can reduce the dimension of the problem to $\op{dim}(\F{U})=C $ and use the previous result.
 	\qed\end{proof}
@@
 		Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
-Let $(\tilde{\spcf0}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces with orthogonal projections $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k $.
+Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces with orthogonal projections $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\F{U}}^k $.
 If $q\geq 2$,
-		$$\norm{\tilde{\tens{\Pi}}_k\varf2} \lesssim \Norm{\varf2}, $$
+		$$\norm{\tilde{\tens{\Pi}}_k\var2} \lesssim \Norm{\var2}, $$
 		otherwise,
-		$$\norm{\tilde{\tens{\Pi}}_k\varf2} \lesssim \sqrt{\op{dim}(\tilde{\spcf0}^0)}\meshsize^{-\frac{kd}{2}}\Norm{\varf2} $$
-		uniformly for all $\varf2\in \F H$.
+		$$\norm{\tilde{\tens{\Pi}}_k\var2} \lesssim \sqrt{\op{dim}(\tilde{\F{U}}^0)}\meshsize^{-\frac{kd}{2}}\Norm{\var2} $$
+		uniformly for all $\var2\in \F H$.
 	\end{lemma}
@@
 		Most of the conditions of Lemma~\ref{app:thm: generic a_U bound} are already satisfied.
-Denote $C=\op{dim}(\tilde{\spcf0^0})$ and $\{e_j\st j\in[C]\}$ the standard orthonormal basis of $\tilde{\spcf0}^0$.
-The scaling properties of $\meshsize$-refining finite element spaces guarantee that the value of $C$ satisfies the conditions of Lemma~\ref{app:thm: generic a_U bound} and a basis of $\tilde{\spcf0}^k$ is given by
-		\begin{equation}
-			\left\{\vvarx0\mapsto\varf0_j(\vars0^{i,k}\vvarx0+\vvars1^{i,k}) \qquad\st\qquad i=1,\ldots,|\F M^k|,\ j=1,\ldots,C\right\}
+Denote $C=\op{dim}(\tilde{\F{U}^0})$ and $\{e_j\st j\in[C]\}$ the standard orthonormal basis of $\tilde{\F{U}}^0$.
+The scaling properties of $\meshsize$-refining finite element spaces guarantee that the value of $C$ satisfies the conditions of Lemma~\ref{app:thm: generic a_U bound} and a basis of $\tilde{\F{U}}^k$ is given by
+		\begin{equation}
+			\left\{\vec{x}\mapsto\var0_j(\vars0^{i,k}\vec{x}+\vvars1^{i,k}) \qquad\st\qquad i=1,\ldots,|\F M^k|,\ j=1,\ldots,C\right\}
 		\end{equation}
@@
 		\begin{equation}
-			\frac{\norm{\varf0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}_\infty}{\norm{\varf0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}} = \frac{\norm{\varf0_j}_\infty}{\sqrt{\int_{\domain_i^k} e_j(\vars0^{i,k} \vvarx0+\vvars1^{i,k})^2d\vvarx0}} = \frac{\norm{\varf0_j}_\infty}{\sqrt{\op{det}(\vars0^{i,k})^{-1}}} \lesssim \meshsize^{-\frac{kd}{2}}.
+			\frac{\norm{\var0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}_\infty}{\norm{\var0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}} = \frac{\norm{\var0_j}_\infty}{\sqrt{\int_{\domain_i^k} e_j(\vars0^{i,k} \vec{x}+\vvars1^{i,k})^2d\vec{x}}} = \frac{\norm{\var0_j}_\infty}{\sqrt{\op{det}(\vars0^{i,k})^{-1}}} \lesssim \meshsize^{-\frac{kd}{2}}.
 		\end{equation}
@@
 	\begin{lemma}\label{app:thm: generic a_E bound}
-		Let $(\tilde{\spcf0}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\varf2}^k=\argmin_{\varf0\in\tilde{\spcf0}^k}\op{E}(\varf0)$.
+		Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\var2}^k=\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.
 		\begin{enumerate}
-			\item If $\op{E}$ is $\Norm\cdot$-Lipschitz at $\varf0^*$, then
-			$\op{E}(\tilde{\varf2}^k)-\op{E}(\varf0^*) \lesssim \meshsize^p\Norm{\varf0^*}.$
-			\item If $\op{E}$ is $\Norm\cdot$-smooth at $\varf0^*$, then 
-			$\op{E}(\tilde{\varf2}^k)-\op{E}(\varf0^*) \lesssim \meshsize^{2p}\Norm{\varf0^*}.$
-			\item If $\op{f}$ is $\Norm\cdot$-Lipschitz at $\varf0^*$ and 
-			$$\min_{\varf2\in\tilde{\spcf0}^k}\left\{\Norm{\varf2-\varf0^*}\st \op{g}(\varf2)\leq \op{g}(\varf0^*)\right\} \lesssim \min_{\varf2\in\tilde{\spcf0}^k}\Norm{\varf2-\varf0^*}$$
+			\item If $\op{E}$ is $\Norm\cdot$-Lipschitz at $\var0^*$, then
+			$\op{E}(\tilde{\var2}^k)-\op{E}(\var0^*) \lesssim \meshsize^p\Norm{\var0^*}.$
+			\item If $\op{E}$ is $\Norm\cdot$-smooth at $\var0^*$, then 
+			$\op{E}(\tilde{\var2}^k)-\op{E}(\var0^*) \lesssim \meshsize^{2p}\Norm{\var0^*}.$
+			\item If $\op{f}$ is $\Norm\cdot$-Lipschitz at $\var0^*$ and 
+			$$\min_{\var2\in\tilde{\F{U}}^k}\left\{\Norm{\var2-\var0^*}\st \op{g}(\var2)\leq \op{g}(\var0^*)\right\} \lesssim \min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*}$$
 			uniformly for $k\in\F N$, then
-			$\op{E}(\tilde{\varf2}^k)-\op{E}(\varf0^*) \lesssim \meshsize^p\Norm{\varf0^*}.$
+			$\op{E}(\tilde{\var2}^k)-\op{E}(\var0^*) \lesssim \meshsize^p\Norm{\var0^*}.$
 		\end{enumerate}
@@
 		\begin{gather}
-			\op{E}(\varf2)-\op{E}(\varf0^*) \leq \op{Lip}(\op{E})\Norm{\varf2-\varf0^*},
-			\\\op{E}(\varf2)-\op{E}(\varf0^*) \leq \IP{\nabla\op{E}(\varf2)}{\varf2-\varf0^*} = \IP{\nabla \op{E}(\varf2)-\nabla \op{E}(\varf0^*)}{ \varf2-\varf0^*} \leq \op{Lip}(\nabla F)\Norm{\varf2-\varf0^*}^2,
-			\\\op{E}(\varf2)-\op{E}(\varf0^*) \leq \op{f}(\varf2)-\op{f}(\varf0^*) \leq \op{Lip}(\op{f})\Norm{\varf2-\varf0^*}.
+			\op{E}(\var2)-\op{E}(\var0^*) \leq \op{Lip}(\op{E})\Norm{\var2-\var0^*},
+			\\\op{E}(\var2)-\op{E}(\var0^*) \leq \IP{\nabla\op{E}(\var2)}{\var2-\var0^*} = \IP{\nabla \op{E}(\var2)-\nabla \op{E}(\var0^*)}{ \var2-\var0^*} \leq \op{Lip}(\nabla F)\Norm{\var2-\var0^*}^2,
+			\\\op{E}(\var2)-\op{E}(\var0^*) \leq \op{f}(\var2)-\op{f}(\var0^*) \leq \op{Lip}(\op{f})\Norm{\var2-\var0^*}.
 		\end{gather}
-		Minimising over the right-hand side over $\varf2$ and substituting the definition of order gives the desired result.
+		Minimising over the right-hand side over $\var2$ and substituting the definition of order gives the desired result.
 		\qed\end{proof}
@@
 	\section{Operator norms for numerical examples}
-	\begin{theorem}[Theorem~\ref{thm: norm bound examples}]\label{app:thm: norm bound examples}
-		\Paste{thm: norm bound examples}
+	\begin{theorem}\label{thm: norm bound examples}
+			Suppose $\A\colon \F H \to \R^m$ has kernels $\psi_j\in L^\infty([0,1]^d)$ for $j\in[m]$.
+		\begin{enumerate}
+			\item[Case 1:] If $\psi_j(\vec{x}) = \splitln{1}{\vec{x}\in \F{X}_j}{0}{\text{ else}}$ for some collection $\F{X}_j\subset\Domain$ such that $\F{X}_i\cap \F{X}_j = \emptyset$ for all $i\neq j$, then
+			$$\norm{\A}_{L^2\to\ell^2} = \max_{j\in[m]} \sqrt{|\F{X}_j|}.$$
+
+			\item[Case 2:] If $\psi_j(\vec{x}) = \cos(\ip{\vvars3_j}{\vec{x}})$ for some frequencies $\vvars3_j\in\R^d$ with $|\vvars3_j|\leq A$, then
+			$$\norm{\A}_{L^2\to\ell^2} \leq \sqrt{m}, \qquad |\A^*\vec{r}|_{C^k}\leq m^{1-\frac1q}A^k\norm{\vec{r}}_q, \qquad |\A^*|_{\ell^2\to C^k}\leq \sqrt{m}A^k$$
+			for all $\vec{r}\in\R^m$ and $q\in[1,\infty]$.
+
+			\item[Case 3:] Suppose $\psi_j(\vec{x}) = (2\pi\sigma^2)^{-\frac{d}{2}}\exp\left(-\frac{|\vec{x}-\vec{x}_j|^2}{2\sigma^2}\right)$ for some regular mesh $\vec{x}_j\in[0,1]^d$ and separation $\Delta$.
+i.e.
+			$$\{\vec{x}_j\st j\in[m]\} = \{\vec{x}_0 + (j_1\Delta,\ldots,j_d\Delta)\st j_i\in[\hat m]\}$$
+			for some $\vec{x}_0\in\R^d$, $\hat m\coloneqq\sqrt[d]{m}$. For all $\frac1q + \frac{1}{q^*} = 1$, $q\in(1,\infty]$, we have
+			\begin{align}
+				\norm{\A}_{L^2\to\ell^2} &\leq \bigg((4\pi\sigma^2)^{-\frac 12}\sum_{j=-2\hat m,\ldots,2\hat m}\exp(-\tfrac{\Delta^2}{4\sigma^2}j^2)\bigg)^d,
+				\\ |\A^*\vec{r}|_{C^0} &\leq (2\pi\sigma^2)^{-\frac{d}{2}}\bigg(\sum_{\vec j\in J}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}}\norm{\vec{r}}_q,
+				\\ |\A^*\vec{r}|_{C^1} &\leq \frac{(2\pi\sigma^2)^{-\frac{d}{2}}}{\sigma}\frac{\Delta}{\sigma}\bigg(\sum_{\vec j\in J}(|\vec j|+\delta)^{q^*}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}}\norm{\vec{r}}_q,
+				\\ |\A^*\vec{r}|_{C^2} &\leq \frac{(2\pi\sigma^2)^{-\frac{d}{2}}}{\sigma^2} \bigg(\sum_{\vec j\in J} \left(1+\tfrac{\Delta^2}{\sigma^2}(|\vec j|+\delta)^2\right)^{q^*}\exp\left(-\tfrac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec j|-\delta)^2\right)\bigg)^{\frac1{q^*}} \norm{\vec{r}}_q,
+			\end{align}
+			where $\delta= \frac{\sqrt d}{2}$ and $J=\{\vec j\in\F Z^d \st \norm{\vec j}_{\ell^\infty}\leq 2\hat m\}$.
+The case for $q=1$ can be inferred from the standard limit of $\norm\cdot_{{q^*}}\to \norm\cdot_{\infty}$ for $q^*\to\infty$.
+		\end{enumerate}
 	\end{theorem}
@@
 	\begin{proof}[case 2]
-		$\vard1_j$ are not necessarily orthogonal however $|\IP{\vard1_i}{\vard1_j}|\leq 1$ therefore we can estimate
+		$\psi_j$ are not necessarily orthogonal however $|\IP{\psi_i}{\psi_j}|\leq 1$ therefore we can estimate
 		\begin{equation}
@@
 		\end{equation}
-		Now looking to apply Lemma~\ref{thm: norm bound smoothness}, note $\norm{\nabla^k\vard1_j}_\infty \leq \Vars3^k$, therefore
-		\begin{align}
-			|\A^*\vvarx3|_{C^k}&\leq \Vars3^k m^{\frac1{q^*}}\norm{\vvarx3}_q = \Vars3^k m^{1-\frac1{q}}\norm{\vvarx3}_q,
-			\\|\A^*|_{\ell^2\to C^k} &\leq \Vars3^k \min_{q\in[1,\infty]}m^{1-\frac1q}\sqrt{m}^{\max(0,2-q)} = \sqrt{m}\Vars3^k.
+		Now looking to apply Lemma~\ref{thm: norm bound smoothness}, note $\norm{\nabla^k\psi_j}_\infty \leq A^k$, therefore
+		\begin{align}
+			|\A^*\vec{r}|_{C^k}&\leq A^k m^{\frac1{q^*}}\norm{\vec{r}}_q = A^k m^{1-\frac1{q}}\norm{\vec{r}}_q,
+			\\|\A^*|_{\ell^2\to C^k} &\leq A^k \min_{q\in[1,\infty]}m^{1-\frac1q}\sqrt{m}^{\max(0,2-q)} = \sqrt{m}A^k.
 		\end{align}
@@
 		\begin{equation}
-			\IP{\vard1_i}{\vard1_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vvarx0-\vvarx0_i|^2}{2\sigma^2}-\tfrac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right) \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vvarx0_i-\vvarx0_j|^2}{4\sigma^2}\right).
+			\IP{\psi_i}{\psi_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vec{x}-\vec{x}_i|^2}{2\sigma^2}-\tfrac{|\vec{x}-\vec{x}_j|^2}{2\sigma^2}\right) \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vec{x}_i-\vec{x}_j|^2}{4\sigma^2}\right).
 		\end{equation}
@@
 		\begin{align}
-			\norm{\A\A^*}_{\ell^2\to\ell^2}&\leq \norm{\A\A^*}_{\ell^\infty\to\ell^\infty} = \max_{i\in[m]} \sum_{j=1}^m |\IP{\vard1_i}{\vard1_j}| 
+			\norm{\A\A^*}_{\ell^2\to\ell^2}&\leq \norm{\A\A^*}_{\ell^\infty\to\ell^\infty} = \max_{i\in[m]} \sum_{j=1}^m |\IP{\psi_i}{\psi_j}| 
 			\\&= \max_{i\in[m]}(4\pi\sigma^2)^{-\frac d2}\sum_{j_1,\ldots,j_d\in[\hat m]} \exp\left(-\frac{(j_1\Delta-i_1\Delta)^2+\ldots+(j_d\Delta-i_d\Delta)^2}{4\sigma^2}\right)
@@
 		$$\begin{array}{rll}
-			\displaystyle |\vard1_j(\vvarx0)| &\displaystyle= \left|\vard1_j(\vvarx0)\right| &\displaystyle = (2\pi\sigma^2)^{-\frac d2}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
-			\\\displaystyle |\nabla\vard1_j(\vvarx0)| &\displaystyle= \left|\frac{\vvarx0-\vvarx0_j}{\sigma^2}\vard1_j(\vvarx0)\right| &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma}\frac{|\vvarx0-\vvarx0_j|}{\sigma}\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right),
-			\\|\nabla^2\vard1_j(\vvarx0)| &\displaystyle =\left|\frac1{\sigma^2} + \frac{(\vvarx0-\vvarx0_j)(\vvarx0-\vvarx0_j)^\top }{\sigma^4}\right|\vard1_j(\vvarx0) &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma^2}\left(1+\frac{|\vvarx0-\vvarx0_j|^2}{\sigma^2}\right)\exp\left(-\frac{|\vvarx0-\vvarx0_j|^2}{2\sigma^2}\right).
+			\displaystyle |\psi_j(\vec{x})| &\displaystyle= \left|\psi_j(\vec{x})\right| &\displaystyle = (2\pi\sigma^2)^{-\frac d2}\exp\left(-\frac{|\vec{x}-\vec{x}_j|^2}{2\sigma^2}\right),
+			\\\displaystyle |\nabla\psi_j(\vec{x})| &\displaystyle= \left|\frac{\vec{x}-\vec{x}_j}{\sigma^2}\psi_j(\vec{x})\right| &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma}\frac{|\vec{x}-\vec{x}_j|}{\sigma}\exp\left(-\frac{|\vec{x}-\vec{x}_j|^2}{2\sigma^2}\right),
+			\\|\nabla^2\psi_j(\vec{x})| &\displaystyle =\left|\frac1{\sigma^2} + \frac{(\vec{x}-\vec{x}_j)(\vec{x}-\vec{x}_j)^\top }{\sigma^4}\right|\psi_j(\vec{x}) &\displaystyle = \frac{(2\pi\sigma^2)^{-\frac d2}}{\sigma^2}\left(1+\frac{|\vec{x}-\vec{x}_j|^2}{\sigma^2}\right)\exp\left(-\frac{|\vec{x}-\vec{x}_j|^2}{2\sigma^2}\right).
 		\end{array}$$
@@
 		\begin{lemma}\label{app: exp sum bound}
-			Suppose $q>0$. If the polynomial $p(|\vvarx0|) = \sum p_k|\vvarx0|^k$ has non-negative coefficients and $\vvarx0\in[-m,m]^d$, then
-			$$\sum_{\norm{\vec{j}}_{\ell^\infty}\leq m} p(|\vec{j}-\vvarx0|)\exp\left(-\tfrac{q|\vec{j}-\vvarx0|^2}{2}\right)\leq \sum_{\norm{\vec{j}}_{\ell^\infty}\leq2m}p(|\vec{j}|+\delta)\exp\left(-\frac{q\max(0,|\vec{j}|-\delta)^2}{2}\right)$$
+			Suppose $q>0$. If the polynomial $p(|\vec{x}|) = \sum p_k|\vec{x}|^k$ has non-negative coefficients and $\vec{x}\in[-m,m]^d$, then
+			$$\sum_{\norm{\vec{j}}_{\ell^\infty}\leq m} p(|\vec{j}-\vec{x}|)\exp\left(-\tfrac{q|\vec{j}-\vec{x}|^2}{2}\right)\leq \sum_{\norm{\vec{j}}_{\ell^\infty}\leq2m}p(|\vec{j}|+\delta)\exp\left(-\frac{q\max(0,|\vec{j}|-\delta)^2}{2}\right)$$
 			where $\delta\coloneqq \frac{\sqrt{d}}{2}$ and $\vec{j}\in\F Z^d$.
@@
 		\begin{proof}
-			There exists $\hat{\vvarx0}\in[-\tfrac12,\tfrac12]^d$ such that $\vvarx0 + \hat{\vvarx0}\in\F Z^d$, therefore
+			There exists $\hat{\vec{x}}\in[-\tfrac12,\tfrac12]^d$ such that $\vec{x} + \hat{\vec{x}}\in\F Z^d$, therefore
 			\begin{align*}
-				\sum_{\norm{\vec{j}}_{\ell^\infty}\leq m} p(|\vec{j}-\vvarx0|)\exp\left(-\tfrac{q|\vec{j}-\vvarx0|^2}{2}\right) &= \sum_{\norm{\vec{j}}_{\ell^\infty}\leq m} p(|\vec{j}-(\vvarx0+\hat{\vvarx0})+\hat{\vvarx0}|)\exp\left(-\tfrac{q|\vec{j}-(\vvarx0+\hat{\vvarx0})+\hat{\vvarx0}|^2}{2}\right)
-				\\&\leq \sum_{\norm{\vec{j}}_{\ell^\infty}\leq2m} p(|\vec{j}+\hat{\vvarx0}|)\exp\left(-\tfrac{q|\vec{j}+\hat{\vvarx0}|^2}{2}\right)
+				\sum_{\norm{\vec{j}}_{\ell^\infty}\leq m} p(|\vec{j}-\vec{x}|)\exp\left(-\tfrac{q|\vec{j}-\vec{x}|^2}{2}\right) &= \sum_{\norm{\vec{j}}_{\ell^\infty}\leq m} p(|\vec{j}-(\vec{x}+\hat{\vec{x}})+\hat{\vec{x}}|)\exp\left(-\tfrac{q|\vec{j}-(\vec{x}+\hat{\vec{x}})+\hat{\vec{x}}|^2}{2}\right)
+				\\&\leq \sum_{\norm{\vec{j}}_{\ell^\infty}\leq2m} p(|\vec{j}+\hat{\vec{x}}|)\exp\left(-\tfrac{q|\vec{j}+\hat{\vec{x}}|^2}{2}\right)
 				\\&\leq \sum_{\substack{\vec{j}\in\F Z^d\\\norm{\vec{j}}_{\ell^\infty}\leq2m}} p(|\vec{j}|+\delta)\exp\left(-\tfrac{q\max(0,|\vec{j}|-\delta)^2}{2}\right)
 			\end{align*}
-			as $|\hat{\vvarx0}|\leq \delta$ and $p$ has non-negative coefficients. 
+			as $|\hat{\vec{x}}|\leq \delta$ and $p$ has non-negative coefficients. 
 			\qed\end{proof}
 
-		Now, continuing the proof of Theorem~\ref{app:thm: norm bound examples}, for $\hat m=\sqrt[d]{m}$, $\delta=\frac{\sqrt{d}}{2}$ and $J=\{\vec{j}\in\F Z^d \st \norm{\vec{j}}_{\ell^\infty}\leq 2\hat m\}$, Lemma~\ref{app: exp sum bound} bounds
+		Now, continuing the proof of Theorem~\ref{thm: norm bound examples}, for $\hat m=\sqrt[d]{m}$, $\delta=\frac{\sqrt{d}}{2}$ and $J=\{\vec{j}\in\F Z^d \st \norm{\vec{j}}_{\ell^\infty}\leq 2\hat m\}$, Lemma~\ref{app: exp sum bound} bounds
 		\begin{align*}
-			\sum_{j=1}^m |\vard1_j(\vvarx0)|^{q^*} &\leq (2\pi\sigma^2)^{-\frac{dq^*}{2}} \left[\sum_{\vec{j}\in J} \exp\left(-\frac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec{j}|-\delta)^2\right)\right]
-			\\\sum_{j=1}^m |\nabla\vard1_j(\vvarx0)|^{q^*} &\leq \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^{q^*}}\frac{\Delta^{q^*}}{\sigma^{q^*}} \left[\sum_{\vec{j}\in J} (|\vec{j}|+\delta)^{q^*}\exp\left(-\frac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec{j}|-\delta)^2\right)\right]
-			\\\sum_{j=1}^m |\nabla^2\vard1_j(\vvarx0)|^{q^*} &\leq \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^{2q^*}} \left[\sum_{\vec{j}\in J} \left(1+\frac{\Delta^2}{\sigma^2}(|\vec{j}|+\delta)^2\right)^{q^*}\exp\left(-\frac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec{j}|-\delta)^2\right)\right]
+			\sum_{j=1}^m |\psi_j(\vec{x})|^{q^*} &\leq (2\pi\sigma^2)^{-\frac{dq^*}{2}} \left[\sum_{\vec{j}\in J} \exp\left(-\frac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec{j}|-\delta)^2\right)\right]
+			\\\sum_{j=1}^m |\nabla\psi_j(\vec{x})|^{q^*} &\leq \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^{q^*}}\frac{\Delta^{q^*}}{\sigma^{q^*}} \left[\sum_{\vec{j}\in J} (|\vec{j}|+\delta)^{q^*}\exp\left(-\frac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec{j}|-\delta)^2\right)\right]
+			\\\sum_{j=1}^m |\nabla^2\psi_j(\vec{x})|^{q^*} &\leq \frac{(2\pi\sigma^2)^{-\frac{dq^*}{2}}}{\sigma^{2q^*}} \left[\sum_{\vec{j}\in J} \left(1+\frac{\Delta^2}{\sigma^2}(|\vec{j}|+\delta)^2\right)^{q^*}\exp\left(-\frac{q^*\Delta^2}{2\sigma^2}\max(0,|\vec{j}|-\delta)^2\right)\right]
 		\end{align*}
-		for all $\vvarx0\in\Domain$. In a worst case, this is $O(2^dm)$ time complexity however the summands all decay faster than exponentially and so should converge very quickly.	
+		for all $\vec{x}\in\Domain$. In a worst case, this is $O(2^dm)$ time complexity however the summands all decay faster than exponentially and so should converge very quickly.	
 		\qed\end{proof}

### 2022-01-25 response.tex
Second revision, first draft

@@
 \newcommand{\review}[1]{\texttt{\justify{#1}}}
+\newcommand{\todo}[1]{{\color{red}Todo: #1}}
 \newcommand{\F}[1]{\mathbb{#1}}
@@
 
-We would like to thank both the reviewers for their time and feedback. All changes are marked in the supplementary pdf and a detailed response to each reviewer is given below.
+We would like to thank both the reviewers again for their time and feedback. All changes are marked in the supplementary pdf and a detailed response to each reviewer is given below.
 
 \section{Detailed response to first reviewer}
+\review{If I had one more comment it would be that I find it somewhat odd the value of the paper's algorithm is presented ``for use with un-attained minima'' as the key theoretical novelty.
+As a point of critique: what does it mean to solve an optimization problem that doesn't have a solution?
+Do the solutions for the $U^n$-problems become meaningless asymptotically?
+Have the authors observed any odd behavior for large values of $n$?
+On the other hand, I think the authors sell themselves a bit short with the statement ``key theoretical novelty'' as the analysis could be useful for solving optimal control and PDE-constrained optimization problems with FISTA or related algorithms, where the interplay of mesh-size and algorithm convergence should always be taken into account.}
+
+Thank you for the constructive feedback.
+That paragraph in the introduction has been re-worded to take into account some of your points.
+In an abstract sense one can always attain minima by adding points to the space (e.g.
+$\operatorname{argmin} e^{-u} = \{\infty\}$), as you say, the challenge is to have some regularity guarantees so that the iterates themselves are not `meaningless'.
+The meaning of `meaningless' depends on the topology.
+In the Lasso example, the iterates are meaningless in both $L^2$ and $L^1$, but can be understood in the space of measures (or distributions).
+In this sense, we have never observed anything unexpected for large $n$.
+
+\section{Detailed response to second reviewer}
 
 \begin{enumerate}
-	\item \review{The authors base much of the analysis on the objective function and its convergence properties \ldots it would be interesting to know how the solutions $u_n$ converge for the various versions of FISTA.}
+	\item \review{Do you assume that the norms of $H$, $U$ are related? I.e., do you assume that there is $c>0$ such that $\lVert u\rVert_U\leq c\lVert u\rVert_H$? Please clarify this in the paper.}
 
-	We thank the reviewer for their suggestion but it seems quite challenging to make a general statement.
-As in your comment, if one has coercivity then the sequence convergences strongly.
-Similarly, if one has (weakly) compact sub-levelsets, such as in the LASSO examples, then a sub-sequence converges (weakly).
+	There is no such requirement between the spaces, this is now clarified after the bullet points in Section 1.
 
-	Of course there are variants of FISTA that guarantee weak convergence in the Hilbert space setting without any further coercivity or compactness assumptions.
-It is likely that the same arguments (e.g.
-[10]) can be made for our adaptive algorithm in a Hilbert space, although we haven't verified this special case.
-It is beyond the scope of this work to extend these results into the generalised setting and at the moment the question does not appear to be trivial.
+	\item \review{(7) $u^*$ was not defined here}
 
-	\item \review{On page 9, line 27 the authors require $\Omega$ to be a compact set.
-Perhaps I am overseeing something, but I would assume that the authors mean to say that $\Omega$ is a connected, open, and bounded set with sufficiently smooth boundary so that $\bar\Omega$ is compact.}
+	This has been clarified in the text, immediately above (7)
 
-	Thank you, we have made the suggested edit.
+	\item \review{Lemma 6: what is $|||\cdot|||_*$?}
 
-	\item \review{page 10 line 21 and 38 typos: Sectoin and although although}
+	In the statement of Lemma 6 we now clarify that this is the dual norm.
 
-	These typos have been corrected.
+	\item \review{Definition 2: What is $q$?
+Smoothness of boundary is not needed.
+What is $h$?
+A given constant in $(0,1)$?
+The coefficients $\alpha,\beta$ have to be independent of $u_i^k$, and rather should depend only on $\omega_i^k$.
+There is a stray $u^*$ in the inequality defining order $p$.
+Also $U\subset L^q$ restricts $q$ to $[1,2]$.}
 
-	\item \review{page 10 line 36: In the infinite-dimensional context, I think it is clear what the authors mean with $\lVert\cdot\rVert_1$.
-They clearly state it as TV in (15), but it is a bit misleading especially later when they use $\lVert\cdot\rVert_\infty$.}
+	Thank you for highlighting the errors in this definition.
+The values of $q$ and $h$ have been clarified.
+We have removed all mention of a particular basis, in response to your later comment, and clarified instead the general scaling properties (the $\alpha$ and $\beta$).
+You're right, the assumption $\F U\supset\F H$ was lazy and not what was intended.
+We only require $\F U$ to contain sub-levelsets of the energy, now clarified in the text.
+\todo{It now makes sense to consider $q>2$, even if Theorem 4 confirms that nothing is gained by doing so.}
 
-	This has been clarified in the text, now equations (15) and (20)-(21).
-The $\lVert\cdot\rVert_\infty$ only appears as the dual-norm of our ${\vert\kern-0.25ex\vert\kern-0.25ex\vert \cdot \vert\kern-0.25ex\vert\kern-0.25ex\vert}$.
+	While it will be most common for $(\alpha,\beta)$ to depend only on $\omega$, it is not necessary.
+One could imagine an example where each sub-domain supports elements which are translations/rescaling/rotations of an original master element and the angular resolution of rotations also refines as $k$ increases.
+The only important factor is the volume rescaling, which we have tried to emphasise in Definition 2.
 
-	\item \review{page 12 and elsewhere: $\partial E$ is usually referred to as the subdifferential. I suppose this depends on the literature source you use.}
+	\item \review{Theorem 4: I do not understand how Lemmas 14-16 proof the estimate of $a_U$.}
 
-	As suggested, we have switched to using the term `subdifferential' throughout the document.
+	You're absolutely right, Theorem 4 was not consistent with the lemmas in the appendix.
+We have kept the statement of Theorem 4 the same other than to remove the special case and remove the implicit assumption that $\tilde{\F U}^0$ was finite dimensional (previously part of Definition 2).
+We have also added a new lemma (Lemma 7) to improve clarity, it serves as a midpoint between Theorem 4 and Appendix B.
+The text in Appendix B now makes clear reference to Lemma 7 as part of the proof of Theorem 4.
 
-	\item \review{My only ``disappointment'' with the paper is that the theory is illustrated with LASSO.
-As a result, $E$ has a rather favorable structure.
-There are many examples, e.g., in robust statistics, where it would be more appropriate to use the $\ell^1$ norm instead of the $\ell^2$ norm for misfit.
-Since the favorable properties of the squared $\ell^2$-norm are often used in the derivations (bounds, constants, etc.
-in Section 6), I wonder how hard it would be to do the same for other relevant examples.}
+	\item \review{(15): $A$ has to be continuous on $H$ as well.}
 
-	You are right, we can also consider alternative misfits.
-We have replaced the wavelet example in Section 7.2 with a (Huber-smoothed) robust $\ell^1$ penalty.
-This also led to a number of small updates to the analysis in Section 6 to generalise for a non-quadratic misfit.
+	Old (15) is now (18). This is now emphasised in two places: Lemma 8 is referenced to confirm that $A$ is continuous, and we require that $|A|^2\nabla f$ is 1-Lipschitz.
 
-	\item \review{page 17, line 28: missing word? ``most require''?}
+	\item \review{page 11, paragraph below (21): Sublevel sets of $E$ are not compact, they are not even bounded without further conditions on $f$ ($f$ bounded from below would be sufficient).
+How do you construct the minimizing sequence in $H$?
+How does $E(u^*_j) \to E(u^*)$ follow?
+I think an assumption is needed to ensure that $A$ is sequentially weak-star continuous, i.e., $A = B^*$ where $B : \mathbb{R}^m \to C([0, 1]^d)$.}
 
-	Thank you for noticing this typo.
+	As suggested, we now assume that $f$ is bounded from below and include a comment on weak-star continuity.
+The general argument has been re-worked to have an explicit sequence $\tilde w_k$ in $H$.
+We no longer rely on the existence of a minimising sequence (other than the explicit $\tilde w_k$).
 
-	\item \review{On page 18, the authors state: ``Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.''}
+	\item \review{section 6.2: $l^1\subset l^2$ in the countable case. The sentence ``then $u^*\in l^2$ makes the analysis simpler'' makes no sense.}
 
-	\review{This is used to argue that the adaptive schemes are better as they require smaller problems, less memory and less time to get to this point.
-However, it would appear that Figure 2 indicates that if a sufficiently accurate solution were desired, instead of a point with $E_0(u_n)\leq 0.1$, then we would still need orders of magnitude of 10 more iterations to get to the same accuracy as the nonadaptive schemes.}
+	This comment has been expanded upon in the text. The key point is the problem behaves much more like a finite-dimensional problem than infinite.
 
-	We have updated Figure 2 to show both discrete and continuous gaps to improve clarity.
-The point of Figure 2 (and 3) is to demonstrate the accuracy of our theoretical rate predictions.
-While the initial rate of convergence is faster for the nonadaptive schemes, Figure 4 confirms that this does not translate to a large practical improvement.
-\end{enumerate}
+	\item \review{(25) What is $\partial_n E$?}
 
-\section{Detailed response to second reviewer}
-We are very sorry that you found our manuscript so difficult to read.
-You were right, the former foundations were not rigorous enough.
-We have rewritten these sections in line with your suggestion of removing the emphasis on the Banach space.
-The analysis of the algorithm in the first half of the manuscript is now performed without mention of a Banach space.
-Consequently, we also realised that the subspace structure and orthogonal projection were not required either.
-We now allow $U^n$ to be closed convex subsets of $\F H$.
-The Banach space setting is reserved for examples discussed in Section 5 onwards.
+	Old (25) is now (27). This refers to the derivative of $E$ on the subspace $\F U^n$, this is now clarified immediately above it in the text.
 
-\begin{enumerate}
-	\item \review{The main criticism is on section 2: In this section, there are no assumptions that relate $U$ and $H$.
-If $U=\bar{H}$ (closure in the norm of $U$?) like on page 1, then $H\subset U$, the subspaces $U_n$ are all subspaces of $H$, and $\Pi_n$ is the Riesz isomorphism on $U_n$, which should be the orthogonal projection of the the Riesz isomorphism on $H$ onto $U_n$.
-Here it is necessary that $U_n$ is a closed subspace.}
+	\item \review{Inequalities (61),(62) do not make sense: the quantities on the left and right-hand sides are equal.}
 
-	As suggested, we now state that $\F U^n$ are closed in (10) and re-referenced throughout the document.
-The mention of $\F U$ on page 1 is now just a reference to the Lasso example introduced in a later section.
+	It's not quite clear which equations are being referred to here.
+On the copy I see, the old (61),(62) are now (63),(64) which are equalities.
+The best match I can see are the current equations (61),(62) in Lemma 9.
+The first equation is just H\"older's inequality, there is no reason for it to be equality for general $r$.
+The second inequality comes from the equivalence of norms, $\frac{\lVert\cdot\rVert_q}{\lVert\cdot\rVert_2}$.
 
-	\item \review{If $H$ is not a subspace of $U$ then it is not clear that such a projection $\Pi_n$ exists at all.}
+	\todo{I don't understand this.
+(61),(62) are statements of Fourier/Gaussian data in numerics section, his next point is also on page 18 rather than 17.
+(51),(52) are in the long align environment in section 6.4 (support detection), those are plausible.
+(41),(42) are in section 6.3.2 (bounds for countable functions).
+(59),(60) are the two inequalities of Lemma 9.
+My best guess is this last pair (which are ironically now (61),(62)...).
+This is quite a patronising answer given the general standard of his questions thought.}
 
-	The projections $\Pi_n$ are now used only on $\F H$.
+	\item \review{page 17, last sentence of first paragraph: the problem is convex, hence all critical points are globally optimal.}
 
-	\item \review{I wonder, where in the paper the choice of the Banach space $U$ or the properties of $u^*$ matter.
-I have the impression that the results are all valid, if $U$ is removed from the paper and $E_0$ is defined as $E_0(u)=E(u)-\inf_{v\in H}E(v)$.
-Then the resulting algorithm tries to compute the infimum of $E$ on $H$ (which might not be attained).}
+	You're quite right, we meant criticality in the discrete sense. This has been corrected.
 
-	Thank you for the suggestion. As previously mentioned, the main introduction of $\F U$ is now postponed to around Section 5.
+	\item \review{Lemma 14: domains are open sets, so ``compact domain'' does not make sense.
+The assumptions already restrict $q$ to $[1, 2]$, so $q > 2$ is impossible.
+Clash of notations: $\mathbb U$ is used to denote a finite-dimensional subspace of $\mathbb H \subset \mathbb U$.
+How is the assumption $e_j \in \mathbb U^*$ meant?
+Quantifier ``$\forall j$'' is missing in items 2,3.
+The proof uses orthonormality of the basis vectors, this assumption is not mentioned in Section 5.
+It is also rather unconventional in the context of finite elements.
+The last sentence of the proof seems to be not belong to the proof.}
 
-	\item \review{The line (p2, l 54) defining $\Pi_n$ looks strange: the pairings $\langle\cdot,\cdot\rangle$ cannot both denote the inner product on $H$ as $u\in U_n^*$ might not be in $H$}
+	The old Lemma 14 is now Lemma 15.
+The domain is now assumed only to be bounded and $\tilde{\F{U}}$ is used as the subspace of $\F U$.
+We have removed the reference to orthonormal bases and the space $\F{U}^*$ which leads to a shorter and simpler result.
 
-	As commented before, we define $\Pi_n$ on $\F H$ to remove any ambiguity.
+	\item \review{Lemma 15: What does ``value of $C$ satisfies the conditions of Lemma 14'' mean?
+The proof of Lemma 15 seems to use the proof of Lemma 14 but not the result of Lemma 14.
+It should be $e_j$ in (115) instead of $u_j$ .
+Also what does ``we compute the scaling constant'' mean?
+The estimate (116) has to be performed for all elements of $\mathbb U^k$ not only for basis elements.}
 
-	\item \review{p.3: in what topology do you want to consider the closure of $U_n^*$? Why is that necessary at all?}
+	The old Lemma 15 is now Lemma 16. Again, you were quite right, we now make explicit use of Lemma 15. This combined with the removal of orthonormal bases leaves a much more direct proof.
 
-	As commented before, we define $\Pi_n$ on $\F H$ instead of $\F U_n^*$.
+	\item \review{Lemma 16: Exponent $k$ is missing in all estimates. What is $u^*$? How is the first inequality in (119) obtained?}
 
-	\item \review{These definitions clash in the proof of Lemma 1 (Thm 6): There $w\in U_n+U_{n-1}$ has to be mapped into $U_n^*$ to be able to apply Lemma 2.
-This happens by means of an unnamed mapping, lets call it $M$, with the property $\Pi_nMw=w$.
-Again it is not clear whether this mapping exists (under the very abstract setting without any relation between $U$, $H$ and $U_n$, $U_{n-1}$.
-I think the claimed inequality (68) is wrong if $U_{n-1}$ is not a subspace of $U_n$, as in that case some projections of $u_{n-1}$ onto $U_n$ have to appear in (68).}
-
-	Lemma 1 has now been modified to have $w\in \F U^n$. Equation (10) also has the assumption $u_{n-1}\in \F U^n$, instead of the suggested $\F U^{n-1}\subset \F U^n$.
-
-	\item \review{On page 1, the functions $f,g$ are defined on $H$ only}
-
-	The optimisation is now performed on $\F H$ only.
-
-	\item \review{Does (5) imply strong or weak lower semicontinuity of $g$?}
-
-	$g$ only needs to be weakly lower-semicontinuous for the existence of minimisers. This is now clarified further in the text (now equation (4)).
-
-	\item \review{Lemma 1: There is no Lemma 1 in [10]}
-
-	We apologise for the mistake, the numbering has now been corrected.
-
-	\item \review{Lemma 2 (and its proof): There is no Theorem 2 in [10], not even a theorem that somehow resembles the claimed inequality.
-Also there is no Theorem 1 in [3], at least not in the version of the paper that can be found on Amir Beck's homepage.}
-
-	Again, we apologise for these mistakes and have corrected the references.
-
-	\item \review{p. 5, line 47: should be $\lVert u\rVert_{L^2(0,1)}^2$.}
-
-	This has been modified in the text.
+	The old Lemma 16 is now Lemma 17. We have clarified that $u^*$ is a minimiser of $E$. The third case has been removed, so the old (119) has also been removed.
 \end{enumerate}

### 2022-01-25 paper.tex
Second revision, first draft

@@
 \usepackage{algorithm,algpseudocode}
-%\graphicspath{{Figures/}}
+\graphicspath{{Figures/}}
 \DeclareGraphicsExtensions{.pdf,.png}
@@
 \DeclareMathOperator{\sign}{sign}
+\newcommand{\diff}{\mathop{}\!\mathrm{d}}
 \newcommand{\Emin}[1][\var0]{\inf_{#1\in\F H}\op{E}(#1)}
+\newcommand{\aU}{a_{\op{U}}}\newcommand{\aE}{a_{\op{E}}}
+\newcommand{\aUaE}{$(\aU,\aE)$-minimising sequence of $\op{E}$}
 
@@
 \definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
-\newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
-\renewcommand{\edit}[2]{#2}
-%\newcommand{\todo}[1]{{\color{red}#1}}
+\newcommand{\edit}[3][1]{
+	\IfEq{#1}{2}{\def\mysecondvar{}}{\def\mysecondvar{#2}}% hide the deleted text?
+	\ifx\mysecondvar\empty{}\else{%
+		\IfEq{#1}{1}{%
+			\ifmmode%
+			\text{\color{red}\sout{\ensuremath{#2}}}%
+			\else%
+			{\color{red} \sout{#2}}%
+			\fi%
+		}{\color{red}#2}\ %
+	}\fi{\color{darkgreen}#3}}
+%\renewcommand{\edit}[3][1]{#3}
+\newcommand{\todo}[1]{{\color{orange}#1}}
 
@@
 	\begin{abstract}
-		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever \edit{the optimisation domain}{a minimiser} is contained in a suitable Hilbert space.
-We propose a modified algorithm where each iteration is performed in a \edit{subspace, and that subspace is allowed to change at every iteration}{subset which is allowed to change at every iteration}.
-\edit{Analytically, this allows us to guarantee convergence in a Banach space setting}{Sufficient conditions are provided for guaranteed convergence}, although at a reduced rate depending on the conditioning of the specific problem.
-\edit{Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.}{These conditions have a natural interpretation when a minimiser exists in an underlying Banach space.
-Typical examples are L1-penalised reconstructions where we provide detailed theoretical and numerical analysis.}
+		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever a minimiser is contained in a suitable Hilbert space.
+We propose a modified algorithm where each iteration is performed in a subset which is allowed to change at every iteration.
+Sufficient conditions are provided for guaranteed convergence, although at a reduced rate depending on the conditioning of the specific problem.
+These conditions have a natural interpretation when a minimiser exists in an underlying Banach space.
+Typical examples are L1-penalised reconstructions where we provide detailed theoretical and numerical analysis.
 	\end{abstract}
@@
 	\begin{equation}\label{eq: min F = fD+fC}
-		\edit{u^* \in \argmin_{\var0\in\F H}\op{E}(\var0)}{\Emin}  \qquad\text{such that}\qquad \op{E}(\var0)\coloneqq \op{f}(\var0) + \op{g}(\var0),
+		\Emin \qquad\text{such that}\qquad \op{E}(\var0)\coloneqq \op{f}(\var0) + \op{g}(\var0),
 	\end{equation}
@@
 The iterates of the FISTA algorithm will be denoted $\var0_n\in\F H$.
-It has been shown that $\op{E}(\var0_n) - \edit{\op{E}(u^*)}{\Emin}$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}.
+It has been shown that $\op{E}(\var0_n) - \Emin$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}.
 Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \cite{Tao2016,Liang2017,Alamo2019}.
 
-	The contribution of this work is a modified FISTA algorithm which achieves two key properties:
+\edit[0]{%
+	\sout{The contribution of this work is a modified FISTA algorithm which achieves two key properties:}
 	\begin{itemize}
-		\item we extend the convergence results to the case \edit{$\var0^*\in\bar{\F H}\setminus\F H$ where $\F{U}\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved.
-For example, in \edit{Lasso}{L1 penalised reconstructions} discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\F{U}\supset\F H$ such that $\Emin = \min_{\var0\in\F{U}}\op{E}(\var0)$ is achieved in $\F{U}\setminus\F H$}.
-The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
-		\item we allow for adaptive discretisation such that $\var0_n\in\F{U}^n\subset\F H$.
+		\item \sout{We extend the convergence results to the case where the minimum is not achieved.
+For example, in L1 penalised reconstructions discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\F{U}\supset\F H$ such that $\Emin = \min_{\var0\in\F{U}}\op{E}(\var0)$ is achieved in $\F{U}\setminus\F H$.
+The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.}
+		\item \sout{We allow for adaptive discretisation such that $\var0_n\in\F{U}^n\subset\F H$.
 With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence.
 In the Hilbert space setting this is the original $n^{-2}$ rate.
-In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation, both in measures of time and computer memory requirements.
+In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation, both in measures of time and computer memory requirements.}
 	\end{itemize}
-	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for \edit{the use outside of Hilbert spaces}{use with un-attained minima} is the key theoretical novelty.
+	\sout{There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for use with un-attained minima is the key theoretical novelty.}
+
+}{%
+	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, however, our interpretation is relatively novel.
+In particular, we emphasise the infinite-dimensional setting where errors come from `discretisation' (rather than random or decaying errors in $\F H$), which enables two new perspectives:
+	\begin{itemize}
+		\item Analytically, we prove new rates of convergence for FISTA when the minimum energy is not achieved (at least not in $\F H$).
+The exact rate can be computed by quantifying coercivity and regularity properties of $\op{E}$.
+If there isn't a minimiser in $\F H$, then this rate is strictly smaller than $n^{-2}$.
+
+		\item Numerically, we allow the optimisation domain to change on every iteration.
+This enables us to understand how FISTA behaves with adaptive discretisations.
+Adaptive finite-element methods are known to improve the efficiency of, for example, approximating the solutions of PDEs.
+Our analytical results show how to combine such tools with FISTA (without reducing the guaranteed rate of convergence), and our numerical results confirm much improved time and computer memory efficiency in the Lasso example (Section~\ref{sec: Lasso definition}).
+	\end{itemize}
+	All the examples in this work, discussed from Section~\ref{sec: general examples} onward, consider $\{\var0\in\F H\st \op{E}(\var0)<\infty\}$ to be contained in some ambient Banach space $\F{U}$.
+The idea is that FISTA provides a minimising sequence in $\F H\cap\F U$, but further properties like rate of convergence (of $\op{E}$ or iterates) must come from the topology of $\F{U}$.
+It will not be necessary for $\F H\hookrightarrow\F U$ to be a continuous embedding, nor in fact the full inclusion $\F H\subset\F U$.
+
+	\todo{Note to self: It is probably not very hard to imagine examples outside of a Banach space, you just need to find a metric space without the linear scaling.
+Examples outside of a metric space would be much harder.}
+}
+
 	Some other works for FISTA-like algorithms include \cite{Jiang2012,Villa2013}.
@@
 The permitted refinement steps are also more broad in our work.
-\cite{}{Very recent work in \cite{Yu2021} proposes a `Multilevel FISTA' algorithm which allows similar coarse-to-fine refinement strategies, although only a finite number.
-We also allow for non-uniform refinement with a posteriori strategies.}
+Very recent work in \cite{Yu2021} proposes a `Multilevel FISTA' algorithm which allows similar coarse-to-fine refinement strategies, although only a finite number.
+We also allow for non-uniform refinement with a posteriori strategies.
 
@@
 The main theoretical contribution of this work is the convergence analysis of Algorithm~\ref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in Section~\ref{sec: recipe}, then we state the specific results in the case of FISTA in Section~\ref{sec: FISTA convergence}.
-The main results are Theorems~\ref{thm: exponential FISTA convergence}/\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\F{U}^n$ respectively.
-
-	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} \edit{}{in Banach spaces }and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation.
-In particular, we describe how to choose efficient refining discretisations to approximate \edit{$\var0^*$}{$\Emin$}, estimate the convergence of $\op{E}$, and identify the support of \edit{$\var0^*$}{the minimiser}.
+The main results are Theorems~\ref{thm: exponential FISTA convergence}/\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA to cases with un-attained minima with uniform/adaptively chosen subspaces $\F{U}^n$ respectively.
+
+	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} in Banach spaces and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation.
+In particular, we describe how to choose efficient refining discretisations to approximate $\Emin$, estimate the convergence of $\op{E}$, and identify the support of the minimiser.
 The numerical results in Section~\ref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.
@@
 	\section{Definitions and notation}\label{sec: prelims}
-	\edit{We consider optimisation of \eqref{eq: min F = fD+fC} over two spaces, the Banach space $(\F{U},\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
-	\\\centerline{$\displaystyle \exists\var0^*\in \F{U} \quad\st\quad \op{E}(\var0^*) = \min_{\var0\in\F{U}}\op{E}(\var0) = \inf_{\var0\in\F H}\op{E}(\var0).$}
-	Furthermore, define the translated energy
-	\\\centerline{$\displaystyle \op{E}_0\colon\F{U}\cup\F H\to \R,\qquad \op{E}_0(\var0) \coloneqq \op{E}(\var0)-\op{E}(\var0^*).$}
-	Note that the value of $\op{E}_0$ is uniquely defined, even if $\var0^*$ may not be.%
-	\\}{%
 	We consider optimisation of \eqref{eq: min F = fD+fC} over a Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$ with the translated energy
@@
 	\end{equation}
-	}
-
-	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\F{U}^n\subset \edit{\F{U}\cap}{}\F H$ for $n\in\F N$.
-The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\F{U}^n$.
-If $\F{U}^n\edit{=\F{U}}{}=\F H$, then we recover the \edit{standard FISTA}{original} algorithm.
-\edit{}{More generally, the idea is that $\F{U}^n$ are `growing', for example $\F{U}^n\subset\F{U}^{n+1}$, but this assumption is not necessary in most of the results.}
+
+	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of closed convex subsets $\F{U}^n\subset \F H$ for $n\in\F N$.
+The only difference from standard FISTA is that on iteration $n$, all computations are performed in the subset $\F{U}^n$.
+If $\F{U}^n=\F H$, then we recover the original algorithm.
+More generally, the idea is that $\F{U}^n$ are `growing', for example $\F{U}^n\subset\F{U}^{n+1}$, but this assumption is not necessary in most of the results.
 
@@
 $\nabla\op{f}$ is 1-Lipschitz.
-To get the general statement of any of the results which follow, replace $\op{E}$ with $\frac{\op{E}}{L}$.\edit{ A more important distinction is to say that the properties of $\op{f}$ and $\op{g}$ are stated with respect to the Hilbert norm.}{} In particular,
+To get the general statement of any of the results which follow, replace $\op{E}$ with $\frac{\op{E}}{L}$.
+In particular,
 	\begin{equation}
@@
 	\end{equation}
-	for all $\var0,\var1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
+	for all $\var0,\var1\in\F H$ and $\op{g}$ is called `simple' if it is proper, convex, weakly lower-semicontinuous, and
 	\begin{equation}
@@
 	\end{equation}
-	is exactly computable for all $\var1\in\F H$ and all $\tilde{\F{U}}\in\{\F{U}^n\}_{n=0}^\infty$.
-\edit{}{Closed subsets of $\F H$ are locally weakly compact, therefore this argmin is always non-empty.}
+	is exactly computable for all $\var1\in\F H$ and all $\tilde{\F{U}}\in\{\F{U}^n\}_{n=0}^\infty$. Closed subsets of $\F H$ are locally weakly compact, therefore this argmin is always non-empty.
 
@@
 	\end{equation}
-
-	\edit{Finally we introduce the concept of an orthogonal projection in the setting of this work.
-For a subspace $\F{U}^n\subset\F{U}\cap\F H$ we define the orthogonal projection $\tens{\Pi}_n\colon (\F{U}^n)^*\to \F{U}^n$ to be any extension of the function such that
-	\\\centerline{$\IP{\tens{\Pi}_n\var0}{\var1} = \IP{\var0}{\var1} \text{ for all } \var0\in(\F{U}^n)^*, \ \var1\in\F{U}^n.$}
-	This definition is non-standard as we view $(\F{U}^n)^*$ embedded in $\F{U}$.
-Note that $\F{U}^n\subset\F H$ implies that $(\F{U}^n)^*\supset\F H$, therefore $\tens{\Pi}_n$ is an extension of the classical orthogonal projection.
-It is convenient to allow an extension here because $\F{U}$ may be bigger than $\F H$, $(\F{U}^n)^*$ is the largest space such that $\tens{\Pi}_n$ is sufficiently well-defined.
-Beyond this, the Hahn-Banach theorem may allow the domain of $\tens{\Pi}_n$ to be extended further, but the definition is no longer unique.
-For example, in 1D the value of $\IP{\delta_0}{\frac{1}{\sqrt[4]{x}}}$ is not well-defined, but the value of $\IP{\delta_0}{\1_{[0,1]}}$ can be chosen to be consistent with some sequence of molifiers.
-To account for this possibility, we shall state that the domain of $\tens{\Pi}_n$ is $\bar{(\F{U}^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.}{}
 
@@
 	\end{align*}
-	\edit{}{For $n\in\F N$ we use the abbreviation $[n] = \{1,2,\ldots,n\}$. When the subdifferential of $\op{E}$ is set-valued, we will use the short-hand
+	For $n\in\F N$ we use the abbreviation $[n] = \{1,2,\ldots,n\}$. When the subdifferential of $\op{E}$ is set-valued, we will use the short-hand
 	\begin{equation}
@@
 	\end{equation}
-	for any specified norm $\Norm\cdot$.}
-
-	\begin{algorithm}\caption{Refining \edit{subspace}{subset} FISTA}\label{alg: refining FISTA}
+	for any specified norm $\Norm\cdot$.
+
+	\begin{algorithm}\caption{Refining subset FISTA}\label{alg: refining FISTA}
 		\centering
@@
 	In this section we give an intuitive outline of the full proof for convergence of Algorithm~\ref{alg: refining FISTA} before giving formal theorems and proofs in the next section.
-First we recall the classical FISTA convergence guarantee given by \cite[\edit{Theorem 2}{Thm 3.1}]{Chambolle2015}:
+First we recall the classical FISTA convergence guarantee given by \cite[Thm 3.1]{Chambolle2015}\edit{:}{; if there exists $\var0^*\in \argmin_{\var0\in\F H}\op{E}(\var0)$, then}
 	\begin{equation}\label{eq: classical FISTA}
@@
 	\end{equation}
-	for some FISTA stepsize choice $t_N\simeq N$ and $\rho_n\geq0$.
+	for \edit{some $\var0^*\in \argmin_{\var0\in\F H}\op{E}(\var0)$, and}{any} FISTA stepsize choice $t_N\simeq N$ such that $\rho_n\geq0$.
 
@@
 	\begin{adaptiveStep}\label{step: step 1 stability}
-		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting \edit{subspaces}{subsets} $\F{U}^n$.
+		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting subsets $\F{U}^n$.
 In the notation of Algorithm~\ref{alg: refining FISTA}, Theorem~\ref{thm: mini FISTA convergence} shows that
@@
 		\end{equation}
-		for any $\var2_n \in \argmin_{\var0\in\F{U}^n}\op{E}(\var0)$.
+		for any $\var2_n \in \edit{\argmin_{\var0\in\F{U}^n}\op{E}(\var0)}{\F{U}^n}$.
 The similarities to \eqref{eq: classical FISTA} are clear.
-If $\F{U}^n=\edit{\F{U}}{\F H}$, then we have $\var2_n=\edit{\var0^*}{\var2_0\in\argmin_{\var0\in\F H}\op{E}(\var0)}$ and the two estimates agree.
-These extra terms quantify the robustness to changing of discretisation.
+If $\F{U}^n=\F H$, then we \edit{have}{can choose} $\var2_n=\edit{\var2_0\in\argmin_{\var0\in\F H}\op{E}(\var0)}{\var0^*}$ and the two estimates agree.
+These extra terms in \eqref{eq: mini FISTA convergence} quantify the robustness to changing of discretisation.
 	\end{adaptiveStep}
@@
 		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\F{U}^n$.
-\edit{}{The idea is that $\F{U}^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\var0\in\F{U}^n}\op{E}(\var0) \to \inf_{\var0\in\F H}\op{E}(\var0)$.
-A canonical example might be $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq n\}$.} \edit{To do so, we construct}{To quantify the balance between a growing Hilbert norm and improving estimate of $\op{E}$, we introduce} a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_U,\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
-		\begin{equation}
-			n\leq n_k \implies \norm{\var2_n} \lesssim \vars3_U^k, \qquad n\geq n_k \implies \op{E}_0(\var2_n) \lesssim \vars3_{\op{E}}^{-k}.
-		\end{equation}
-		\edit{}{The expanding balls example would become $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq \vars3_U^k\}$, and $\vars3_{\op{E}}$ reflects the smoothness of $\op{E}$ with respect to the Hilbert norm.} The choice of exponential scaling is \edit{very}{more} natural if we consider the $\F{U}^n$ to be the subspace of functions discretised on a uniform mesh.
+The idea is that $\F{U}^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\var0\in\F{U}^n}\op{E}(\var0) \to \inf_{\var0\in\F H}\op{E}(\var0)$.
+A canonical example might be $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq n\}$.
+To quantify the balance between a growing Hilbert norm and improving estimate of $\op{E}$, we introduce a secondary sequence $n_0 < n_1 < \ldots$ and constants $\aU,\aE\geq1$ such that for each $k\in\F N$
+		\begin{equation}\label{eq: first regularity}
+			n\leq n_k \implies \norm{\var2_n} \lesssim \aU^k, \qquad n\geq n_k \implies \op{E}_0(\var2_n) \lesssim \aE^{-k}.
+		\end{equation}
+		The expanding balls example would become $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq \aU^k\}$ for $n\in[n_k,n_{k+1})$, and $\aE$ reflects the smoothness of $\op{E}$.
+The choice of exponential scaling \edit{is more}{is introduced to improve stability of Algorithm~\ref{alg: refining FISTA}.
+It is} natural if we consider the $\F{U}^n$ to be the subspace of functions discretised on a uniform mesh.
 If that mesh is sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$.
-The integer $n_k$ should then be the time when the mesh has refined $k$ times.
-%
-		\edit{The value of $\vars3_U$ is dictated by the smoothness of the norm of $\F{U}$ with respect to that of $\F H$.
-If $\norm{\var0^*}<\infty$, then the value is $\vars3_U=1$, otherwise there is some damage to the rate of convergence generated by this factor.
-On the other hand, the value of $\vars3_{\op{E}}$ is dictated by the smoothness of $\op{E}$ at the point $\var0^*$.}{The value $\vars3_U$ reflects the smoothness of the chosen basis measured in $\F H$, and $\vars3_{\op{E}}$ is a measure of efficiency with respect to the structure of $\op{E}$.} %
-		If an efficient basis is used, then $\vars3_{\op{E}}$ is large.
-The trade-off between $\vars3_{\op{E}}$ and $\vars3_U$ dictates the final convergence rate of the algorithm.
-\edit{}{If $\vars3_U>1$, then we cannot guarantee the original $n^{-2}$ rate of convergence.}
+The integer $n_k$ is then the time at which the mesh has refined $k$ times.
+\edit{The value $\aU$ reflects the smoothness of the chosen basis, and $\aE$ is a measure of efficiency with respect to the structure of $\op{E}$.
+If an efficient basis is used, then $\aE$ is large.}{} The trade-off between $\aE$ and $\aU$ dictates the final convergence rate of the algorithm.
+If $\aU>1$, then we cannot guarantee the original $n^{-2}$ rate of convergence.
 	\end{adaptiveStep}
@@
 	\begin{adaptiveStep}\label{step: step 3 convergence bound}
-		In this step we combine the FISTA stability estimate with the \edit{subspace}{subset} approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\op{E}}$ and $\vars3_U$.
-For example, if $\F{U}^n$ is of the form
-		$$ \F{U}^{n_k} = \F{U}^{n_k+1} = \ldots = \F{U}^{n_{k+1}-1},$$
+		In this step we combine the FISTA stability estimate with the subset approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\aE$ and $\aU$.
+For example, if \edit{$\F{U}^n$ is of the form}{for each $k\in\F N$}
+		$$\edit{\F{U}^{n_k} = \F{U}^{n_k+1} = \ldots = \F{U}^{n_{k+1}-1}}{\var2_{n_k}=\var2_{n_k+1}=\ldots \var2_{n_{k+1}-1}},$$
 		then many terms on the right-hand side of \eqref{eq: mini FISTA convergence} telescope to 0.
-The result of this is presented in Lemma~\ref{thm: mini exponential FISTA convergence} but the moral is that the stability error in \eqref{eq: mini FISTA convergence} should scale in proportion to the $k$ (related to the resolution) rather than the total number of iterations $N$.
+The result of this is presented in Lemma~\ref{thm: mini exponential FISTA convergence}.
+The key idea is that the stability error in \eqref{eq: mini FISTA convergence} has $K\lesssim\log(N)$ terms, rather than $N$.
 	\end{adaptiveStep}
 
-	\paragraph{Step 4: Sufficiently fast refinement}
+	\paragraph{Step 4: Sufficiently fast \edit{refinement}{growth}}
 	\begin{adaptiveStep}\label{step: step 4 sufficiently fast}
 		In Step~\ref{step: step 3 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor.
-In particular, it is equivalent to run Algorithm~\ref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed \edit{subspace}{subset} $\F{U}^N$.
-The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\op{E}_0(\var0_N)\lesssim \norm{\var0_0-\var2_N}^2 = O(\vars3_U^{2K})$ for $N\leq n_K$.
-Lemma~\ref{thm: sufficiently fast} shows that Algorithm~\ref{alg: refining FISTA} can achieve the same order of approximation, so long as $\F{U}^n$ refine sufficiently quickly, i.e.
-$n_k$ are sufficiently small.
+In particular, it is equivalent to either run Algorithm~\ref{alg: refining FISTA} for $N$ iterations, or the classical FISTA algorithm for $N$ iterations on the fixed subset $\F{U}^N$.
+The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\op{E}_0(\var0_N)\lesssim \norm{\var0_0-\var2_N}^2 = O(\aU^{2K})$ for $N\leq n_K$.
+Lemma~\ref{thm: sufficiently fast} shows that Algorithm~\ref{alg: refining FISTA} can achieve the same order of approximation, so long as $\F{U}^n$ \edit{refine}{grow} sufficiently quickly (in particular $n_k^2\lesssim \aE^k\aU^{2k}$).
 	\end{adaptiveStep}
 
-	\paragraph{Step 5: Sufficiently slow refinement}
+	\paragraph{Step 5: Sufficiently slow \edit{refinement}{growth}}
 	\begin{adaptiveStep}\label{step: step 5 sufficiently slow}
 		The result of Step~\ref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate.
-If the \edit{subspaces refine}{subsets grow} too quickly, then the influence of \edit{$\norm{\var0^*}=\infty$}{$\norm{\var0_n}\to\infty$} will slow the rate of convergence.
-If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow.
-Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of
-		$$ \op{E}_0(\var0_N) \lesssim \frac{\vars3_U^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
-		for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_U,\vars3_{\op{E}}$.
-In particular, if \edit{$\var0^*\in\F H$}{the minimum is attained in $\F H$,} then we recover the classical rate with $\kappa=0$.
+If the subsets grow too quickly, then the influence of $\norm{\var0_n}\to\infty$ will slow the rate of convergence.
+\edit{If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow.}{If $k$ is too small (coarse discretisation), then we overfit to the discrete problem, but if $k$ is too large, then the energy converges slowly.} Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way ($n_k^2\simeq \aE^k\aU^{2k}$) for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of
+		$$ \op{E}_0(\var0_N) \lesssim \frac{\aU^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
+		for all $N\in\F N$ and \edit{some }{}$\kappa\edit{}{=\frac{2\log\aU}{\log\aE+2\log\aU}}\in[0,1)$\edit{ depending on $\aU,\aE$}{}.
+In particular, if the minimum is attained in $\F H$, then we recover the classical rate with $\kappa=0$.
 	\end{adaptiveStep}
@@
 		Up to this point we have implicitly focused on the case where $\F{U}^n$ (and $n_k$) are chosen a priori. 
-Here we emphasise some of the challenges which are faced when extending results to allow for greedy adaptivity.
+		\edit{Here we emphasise some of the challenges which are faced when extending results to allow for greedy adaptivity.
 
 		Spatial adaptivity is robust, so long as the scaling properties of Step~\ref{step: step 2 smoothness} are satisfied.
-The only other constraint is to ensure that the partial telescoping of Step~\ref{step: step 3 convergence bound} still holds.
-Lemma~\ref{thm: mini exponential FISTA convergence} shows that a sufficient condition is
-		$$\edit{}{\var0_{n_k-1}\in}\F{U}^{n_k}\subset\F{U}^{n_k+1}\subset\ldots\subset\F{U}^{n_{k+1}-1}.$$
+The only other constraint is to ensure that the partial telescoping of Step~\ref{step: step 3 convergence bound} still holds.%
+		}{%
+		The main challenge for adaptive choice of $\F{U}^n$ is to guarantee \eqref{eq: first regularity} from Step~\ref{step: step 2 smoothness} using a posteriori estimates.
+Combined with the partial telescoping requirement in Step~\ref{step: step 3 convergence bound}, a natural choice is $\var2_n=\var0_{n_k-1}$ for $n\in[n_k,n_{k+1}-1)$, i.e.
+the value of $n_k$ is chosen to be $n+1$ once the iterate $\var0_n$ is observed.
+		}
+		Theorem~\ref{thm: stronger exponential FISTA convergence} shows that a sufficient condition is
+		$$\var0_{n_k-1}\in\F{U}^{n_k}\cap\F{U}^{n_k+1}\cap\ldots\cap\F{U}^{n_{k+1}-1}\edit{.}{, \qquad \norm{\var0_{n_k-1}} \lesssim \aU^k, \quad\text{and}\quad \op{E}_0(\var0_{n_k-1}) \lesssim \aE^{-k}}$$
 		Convergence is most stable if the approximation spaces $\F{U}^n$ satisfy a monotone inclusion, breaking the monotonicity requires more care.
-
-		Adaptively choosing the time of refinement is more challenging due to the non-descent property of FISTA.
+		\edit{Adaptively choosing the time of refinement is more challenging due to the non-descent property of FISTA.
 The idea is that $\F{U}^n$ should be refined as soon as the value $\op{E}(\var0_n)$ is sufficiently close to $\op{E}(\var2_n)$.
-This is analysed in Theorem~\ref{thm: stronger exponential FISTA convergence} (sufficient conditions in Lemma~\ref{thm: practical refinement criteria}) which shows convergence results of the form
+This is analysed in Theorem~\ref{thm: stronger exponential FISTA convergence} (sufficient conditions in Lemma~\ref{thm: practical refinement criteria}) which shows convergence results of the form}{The only non-trivial property to verify is the energy gap  $\op{E}_0(\var0_n) = \op{E}(\var0_n)-\Emin$.
+Lemma~\ref{thm: practical refinement criteria}) proposes some sufficient conditions to guarantee the same overall rate of convergence as in Step~\ref{step: step 5 sufficiently slow},}
 		$$ \min_{n\leq N}\op{E}_0(\var0_n) \lesssim \frac{N^{2\kappa}}{N^2}$$
 		for all $N\in\F N$, with the same $\kappa\in[0,1)$ from Step~\ref{step: step 5 sufficiently slow}.
-The penalty for accelerating the refinement time is a potential loss of stability in $\op{E}(\var0_n)$, however, the asymptotic rate is equivalent and this behaviour has not been seen in numerical experiments.
+The penalty for accelerating the change of discretisation is a potential loss of stability or monotonicity in $\op{E}(\var0_n)$, although this behaviour has not been seen in numerical experiments.
 	\end{adaptiveStep}
@@
 The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely.
-	\edit{}{Throughout this section we consider a sequence $(\F{U}^n)_{n\in\F N}$ which generate the iterates $(\var0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} such that
+	Throughout this section we consider a sequence $(\F{U}^n)_{n\in\F N}$ which generate the iterates $(\var0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} such that
 	\begin{equation}\label{eq: refining subspace definition}
 		\var0^{n-1}\in\F{U}^n\subset\F H \quad\text{where }\F{U}^n\text{ is a closed, convex subset for all } n\in\F N.
-	\end{equation}}
+	\end{equation}
 
@@
 	We first wish to understand a single iteration of Algorithm~\ref{alg: refining FISTA}. This is done through the following two lemmas.
-	\begin{lemma}[equivalent to {\cite[Lemma \edit{1}{3.1}]{Chambolle2015}}]\label{thm: descent lemma}
+	\begin{lemma}[equivalent to {\cite[Lemma 3.1]{Chambolle2015}}]\label{thm: descent lemma}
 		\Copy{thm: descent lemma}{
-			Suppose $\nabla \op{f}$ is 1-Lipschitz, for any $\bar{\var0}\in \edit{\F{U}^{n}}{\F H}$ define
+			Suppose $\nabla \op{f}$ is 1-Lipschitz, for any $\bar{\var0}\in \F H$ define
 			$$ \var0 \coloneqq \argmin_{\var0\in \F{U}^{n}} \tfrac12\norm{\var0-\bar{\var0}+\nabla \op{f}(\bar{\var0})}^2+\op{g}(\var0).$$
-			Then, for all $\var2\in\edit{\bar{(\F{U}^n)^*}\supset\F H}{\F{U}^n}$, we have
-			\edit{\\\centerline{$\displaystyle \op{E}(\var0) + \tfrac12\norm{\var0-\tens{\Pi}_n\var2}^2 \leq \op{E}(\tens{\Pi}_n\var2) + \tfrac12\norm{\bar{\var0}-\tens{\Pi}_n\var2}^2.$}}{
-			$$\op{E}(\var0) + \tfrac12\norm{\var0-\var2}^2 \leq \op{E}(\var2) + \tfrac12\norm{\bar{\var0}-\var2}^2.$$}
-			\edit{where $\tens{\Pi}_n\colon\bar{(\F{U}^n)^*}\to\F{U}^n$ is the orthogonal projection.}{}
+			Then, for all $\var2\in\F{U}^n$, we have
+			$$\op{E}(\var0) + \tfrac12\norm{\var0-\var2}^2 \leq \op{E}(\var2) + \tfrac12\norm{\bar{\var0}-\var2}^2.$$
+
 		}
 	\end{lemma}
-	\noindent The proof is exactly the same as in \cite{Chambolle2015} on the \edit{subspace}{subset} $\F{U}^n$.
+	\noindent The proof is exactly the same as in \cite{Chambolle2015} on the subset $\F{U}^n$.
 Applying Lemma~\ref{thm: descent lemma} to the iterates from Algorithm~\ref{alg: refining FISTA} gives a more explicit inequality.
 
-	\begin{lemma}[{\edit{analogous to }{}\cite[\edit{Theorem 2}{(17)}]{Chambolle2015}, \cite[\edit{Theorem 1}{Lemma 4.1}]{Beck2009}}]\label{thm: one step FISTA}
+	\begin{lemma}[{\cite[(17)]{Chambolle2015}, \cite[Lemma 4.1]{Beck2009}}]\label{thm: one step FISTA}
 		\Copy{thm: one step FISTA}{
-			Let \edit{$\F{U}^n\subset\F H\cap\F{U}$, }{}$\var2_n\in\F{U}^n$ be chosen arbitrarily and $\var0_n$/$\var1_n$ be generated by Algorithm~\ref{alg: refining FISTA} for all $n\in\F N$.
+			Let $\var2_n\in\F{U}^n$ be chosen arbitrarily and $\var0_n$/$\var1_n$ be generated by Algorithm~\ref{alg: refining FISTA} for all $n\in\F N$.
 			For all $n\in\F N$, it holds that}
@@
 	\end{lemma}
-	\noindent The proof is given in Theorem~\ref{app:thm: one step FISTA} and is a result of the convexity of $\op{E}$ for a well chosen $\var2$ in Lemma~\ref{thm: descent lemma}.
+	\noindent The proof is given in Theorem~\ref{app:thm: one step FISTA} and is a result of the convexity of $\op{E}$ and $\F{U}_n$ for a well chosen $\var2$ in Lemma~\ref{thm: descent lemma}.
 
@@
 
-	\begin{theorem}[\edit{}{analogous to {\cite[Thm 3.2]{Chambolle2015}, \cite[Thm 4.1]{Beck2009}}}]\label{thm: mini FISTA convergence}
+	\begin{theorem}[analogous to {\cite[Thm 3.2]{Chambolle2015}, \cite[Thm 4.1]{Beck2009}}]\label{thm: mini FISTA convergence}
 		\Copy{thm: mini FISTA convergence}{
-			Fix a sequence of \edit{subspaces}{subsets} $(\F{U}^n\edit{\subset\F{U}\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\var0_0\in \F{U}^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$.
+			Fix a sequence of subsets $(\F{U}^n)_{n\in\F N}$ satisfying \eqref{eq: refining subspace definition}, arbitrary $\var0_0\in \F{U}^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$.
 Let $\var0_n$ and $\var1_n$ be generated by Algorithm~\ref{alg: refining FISTA}, then, for any choice of $\var2_n\in\F{U}^n$ and $N\in\F N$ we have
@@
 	\noindent The proof is given in Theorem~\ref{app:thm: mini FISTA convergence}.
-This result is the key approximation for showing convergence of FISTA with \edit{refining subspaces}{growing subsets}.
-In the classical setting, we have $\F{U}^n\edit{=\F{U}}{}=\F H$, $\var2_n\edit{=\var0^*}{\in\argmin_{\var0\in\F H}\op{E}(\var0)}$ and the extra terms on the right-hand side collapse to 0.
-
-	\edit{The}{If there exists a minimiser $\var0^*\in\argmin_{\var0\in\F H}\op{E}(\var0)$, then the } natural choice in \eqref{eq: FISTA inequality} is $\var2_n=\tens{\Pi}_n\var0^*$\edit{}{ for some projection $\tens{\Pi}_n\colon\F H\to\F{U}^n$}, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\var0^*)=\infty$ and so this inequality becomes useless.
-For example, if $\op{f}(\var0) = \norm{\var0}_{\edit{2}{L^2([0,1])}}^2$, $\op{g}$ is the indicator on the set $\F D=\{\var0\in L^1([0,1])\st \var0(x) \geq x\}$, and \edit{$\F{U}^n$ is}{$\tens{\Pi}_n$ is the $L^2$ projection onto} a set of piecewise constant functions, then $\var0^*=x\mapsto x$.
+This result is the key approximation for showing convergence of FISTA with growing subsets.
+In the classical setting, we have $\F{U}^n=\F H$, $\var2_n=\var2_0\in\argmin_{\var0\in\F H}\op{E}(\var0)$ and the extra terms on the right-hand side collapse to 0.
+
+	If there exists a minimiser $\var0^*\in\argmin_{\var0\in\F H}\op{E}(\var0)$, then the natural choice in \eqref{eq: FISTA inequality} is $\var2_n=\tens{\Pi}_n\var0^*$ for some projection $\tens{\Pi}_n\colon\F H\to\F{U}^n$, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\var0^*)=\infty$ and so this inequality becomes useless.
+For example, if $\op{f}(\var0) = \norm{\var0}_{L^2([0,1])}^2$, $\op{g}$ is the indicator on the set $\F D=\{\var0\in L^1([0,1])\st \var0(x) \geq x\}$, and $\tens{\Pi}_n$ is the $L^2$ projection onto a set of piecewise constant functions, then $\var0^*=x\mapsto x$.
 On the other hand, suppose one of the pixels of the discretisation is $[x_0-\meshsize,x_0+\meshsize]$, then
-	$$\tens{\Pi}_n\var0^*\left(x_0+\tfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{x_0-\meshsize}^{x_0+\meshsize}(\var0^*(x)-\vars5)^2dx = \argmin_{\vars5\in\R}\int_{x_0-\meshsize}^{x_0+\meshsize}(x-\vars5)^2dx = x_0 < x_0+\tfrac\meshsize2.$$
+	$$\tens{\Pi}_n\var0^*\left(x_0+\tfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{x_0-\meshsize}^{x_0+\meshsize}(\var0^*(x)-\vars5)^2\diff x = \argmin_{\vars5\in\R}\int_{x_0-\meshsize}^{x_0+\meshsize}(x-\vars5)^2\diff x = x_0 < x_0+\tfrac\meshsize2.$$
 	In particular $\tens{\Pi}_n\var0^* \notin\F D$ therefore $\op{E}(\tens{\Pi}_n\var0^*) = \infty$.
 The choice $\var2_n=\argmin_{\var0\in\F{U}^n}\op{E}(\var0)$ is much more robust and allows us to apply Algorithm~\ref{alg: refining FISTA} more broadly.
-The penalty for this flexibility is a more complicated analysis, each time the \edit{subspace}{subset} changes, the system receives a `shock' proportional to $\norm{\var2_{n}-\var2_{n+1}}$.
+The penalty for this flexibility is a more complicated analysis; each time the subset changes, because $\var1_n\in\F{U}_n$, the system receives a `shock' proportional to $\norm{\var1_n}\norm{\var2_{n}-\tens{\Pi}_n\var2_{n+1}}$.
 
@@
 The following lemma minimises the growth of the `constant' as a function of $N$ by partially telescoping the sum on the right-hand side.
-Before progressing to the content of Step~\ref{step: step 3 convergence bound}, we will first formalise the definition of the constants $\vars3_U$ and $\vars3_{\op{E}}$ introduced in Step~\ref{step: step 2 smoothness}.
+Before progressing to the content of Step~\ref{step: step 3 convergence bound}, we will first formalise the definition of the constants $\aU$ and $\aE$ introduced in Step~\ref{step: step 2 smoothness}.
 	\begin{definition}\label{def: exp subspaces}
-		Fix $\vars3_U,\vars3_{\op{E}}\geq 1$ and a sequence of \edit{subspaces $(\tilde{\F{U}}^k\subset\F H\cap\F{U})_{k\in\F N}$}{closed subsets $\tilde{\F{U}}^k\subset\F H$}.
-We say that $(\tilde{\F{U}}^k)_{k\in\F N}$ is a \emph{$(\vars3_U,\vars3_{\op{E}})$-discretisation for $\op{E}$} if
-		$$ \norm{\tilde{\var2}_k}\lesssim \vars3_U^k \qquad\text{and}\qquad \op{E}_0(\tilde{\var2}_k) \lesssim \vars3_{\op{E}}^{-k} $$
-		for all $k\in\F N$ and some choice $\tilde{\var2}_k\in\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.
+		Fix $\aU,\aE\geq 1$ and a sequence \edit{of closed subsets $\tilde{\F{U}}^k\subset\F H$}{$\tilde{\var2}_k\in\F H$}.
+We say that $(\edit{\tilde{\F{U}}^k}{\tilde{\var2}_k})_{k\in\F N}$ is an \emph{\edit{$(\aU,\aE)$-discretisation for $\op{E}$}{\aUaE\ }} if
+		$$ \norm{\tilde{\var2}_k}\lesssim \aU^k \qquad\text{and}\qquad \op{E}_0(\tilde{\var2}_k) \lesssim \aE^{-k} $$
+		for all $k\in\F N$\edit{ and some choice $\tilde{\var2}_k\in\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$}{}.
 	\end{definition}
@@
 		\Copy{thm: mini exponential FISTA convergence}{
-			Let $\var0_n$, $\var1_n$ be generated by Algorithm~\ref{alg: refining FISTA} \edit{}{with $(\F{U}^n)_{n\in\F N}$ satisfying \eqref{eq: refining subspace definition}}, $(n_k\in\F N)_{k\in\F N}$ be a monotone increasing sequence, and choose
+			Let $\var0_n$, $\var1_n$ be generated by Algorithm~\ref{alg: refining FISTA} with $(\F{U}^n)_{n\in\F N}$ satisfying \eqref{eq: refining subspace definition}, $(n_k\in\F N)_{k\in\F N}$ be a monotone increasing sequence, and choose
 			$$\tilde{\var2}_k \in \F{U}^{n_k} \cap \F{U}^{n_k+1}\cap \ldots \cap \F{U}^{n_{k+1}-1}$$
@@
 			\begin{multline*}\Copy{thm:eq: mini exponential FISTA convergence}{
-				t_N^2\op{E}_0(\var0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\var0_n) + \frac{\norm{\var1_N-\tilde{\var2}_K}^2}{2} \leq C + \frac{\norm{\tilde{\var2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\op{E}_0(\tilde{\var2}_K) \\+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\op{E}_0(\tilde{\var2}_{k-1}) + \IP{\var1_{n_k-1}}{\tilde{\var2}_k-\tilde{\var2}_{k+1}}}
+				t_N^2\op{E}_0(\var0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\var0_n) + \frac{\norm{\var1_N-\tilde{\var2}_K}^2}{2} \leq C + \frac{\norm{\tilde{\var2}_K}^2}{2} + \frac{(N+1)^2-n_K^2}{2}\op{E}_0(\tilde{\var2}_K) \\+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\op{E}_0(\tilde{\var2}_{k-1}) + \IP{\var1_{n_k-1}}{\tilde{\var2}_{k-1}-\tilde{\var2}_k}}
 			\end{multline*}
@@
 	\end{lemma}
+
 	\noindent The proof is given in Lemma~\ref{app:thm: mini exponential FISTA convergence}.
@@
 	\begin{equation}
-		\op{E}(\var0_n) - \min_{\var0\in\F{U}^n}\op{E}(\var0) \lesssim \frac{\norm{\var0_0-\argmin_{\var0\in\F{U}^n}\op{E}(\var0)}^2}{n^2}
+		\op{E}(\var0_n) - \min_{\var0\in\F{U}^n}\op{E}(\var0) \lesssim \frac{\norm{\var0_0-\edit{\argmin_{\var0\in\F{U}^n}\op{E}(\var0)}{\tilde{\var2}_k}}^2}{n^2}
 	\end{equation}
 	uniformly in $n$.
-If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of \edit{subspaces}{subsets}.
+If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of subsets.
 This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\F{U}^n}$ rather than the desired function $\op{E}|_{\F H}$.
@@
 		\Copy{thm: sufficiently fast}{
-			Suppose $\F{U}^n,\ \var0_n,\ \var1_n$ and $n_k$ satisfy the conditions of Lemma~\ref{thm: mini exponential FISTA convergence} and $(\tilde{\F{U}}^k)_{k\in\F N}$ forms an \\$(\vars3_U,\vars3_{\op{E}})$-discretisation for $\op{E}$ with
-			$$\tilde{\var2}_k\in \left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]\cap\F{U}^{n_k}\cap\F{U}^{n_k+1}\cap\ldots\cap\F{U}^{n_{k+1}-1}.$$
+			Suppose $\F{U}^n,\ \var0_n,\ \var1_n$ and $n_k$ satisfy the conditions of Lemma~\ref{thm: mini exponential FISTA convergence} and $(\edit{\tilde{\F{U}}^k}{\tilde{\var2}_k})_{k\in\F N}$ forms an \\\edit{$(\aU,\aE)$-discretisation for $\op{E}$}{\aUaE\ } with
+			$$\tilde{\var2}_k\in \edit{\left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]\cap}{}\F{U}^{n_k}\cap\F{U}^{n_k+1}\cap\ldots\cap\F{U}^{n_{k+1}-1}.$$
 			If either:
 			\begin{itemize}
-				\item $\vars3_U>1$ and $n_k^2\lesssim \vars3_{\op{E}}^k\vars3_U^{2k}$,
-				\item or $\vars3_U=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty,$
+				\item $\aU>1$ and $n_k^2\lesssim \aE^k\aU^{2k}$,
+				\item or $\aU=1$, $\sum_{k=1}^\infty n_k^2\aE^{-k}<\infty$, and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty,$
 			\end{itemize}
 			then
-			$$ \op{E}_0(\var0_N) \lesssim \frac{\vars3_U^{2K}}{N^2}\qquad \text{for all}\qquad n_K\leq N< n_{K+1}.$$
+			$$ \op{E}_0(\var0_N) \lesssim \frac{\aU^{2K}}{N^2}\qquad \text{for all}\qquad n_K\leq N< n_{K+1}.$$
 		}
@@
 		\item The convergence guarantee for $N$ iterations of classical FISTA in the space $\F{U}^N$ is 
-		$$ \op{E}_0(\var0_N) \lesssim \frac{\norm{\var0_0-\argmin_{\var0\in\F{U}^N}\op{E}(\var0)}^2}{N^2} + \min_{\var0\in\F{U}^N}\op{E}_0(\var0) \lesssim \frac{\vars3_U^{2K}}{N^2} + \vars3_{\op{E}}^{-K}.$$
+		$$ \op{E}_0(\var0_N) \lesssim \frac{\norm{\var0_0-\edit{\argmin_{\var0\in\F{U}^N}\op{E}(\var0)}{\tilde{\var2}_K}}^2}{N^2} + \min_{\var0\in\F{U}^N}\op{E}_0(\var0) \lesssim \frac{\aU^{2K}}{N^2} + \aE^{-K}.$$
 		This is equivalent to Lemma~\ref{thm: sufficiently fast} after the assumptions on $n_k$.
-		\item If $\edit{\F{U}}{\F H}$ is finite dimensional, then the $\vars3_U=1$ is almost trivially satisfied.
+		\item If $\F H$ is finite dimensional, then the $\aU=1$ is almost trivially satisfied.
 Norms in finite dimensions are equivalent and any discretisation can be achieved with a finite number of refinements (i.e.
@@
 
-	As a special case, note that if $\vars3_U=1$ then Lemma~\ref{thm: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate.
+	As a special case, note that if $\aU=1$ then Lemma~\ref{thm: sufficiently fast} already gives the optimal $O(N^{-2})$ convergence rate.
 This is in fact a special case of that shown in \cite[Prop 3.3]{Aujol2015}.
-If \edit{$\var0^*\in\F H$}{the minimum is achieved in $\F H$}, then it is not possible to refine `too quickly' and the following lemma is not needed.
+If the minimum is achieved in $\F H$, then it is not possible to refine `too quickly' and the following lemma is not needed.
 
@@
 			Suppose $\var0_n$ and $n_k$ are sequences satisfying 
-			$$\op{E}_0(\var0_N) \lesssim \frac{\vars3_U^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \vars3_{\op{E}}^K\vars3_U^{2K},$$
+			$$\op{E}_0(\var0_N) \lesssim \frac{\aU^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \aE^K\aU^{2K},$$
 			then 
-			$$\op{E}_0(\var0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2}.$$}
+			$$\op{E}_0(\var0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \aU^2}{\log \aE + \log \aU^2}.$$}
 	\end{lemma}
@@
 		\Copy{thm: exponential FISTA convergence}{
-			Let $(\tilde{\F{U}}^k)_{k\in\F N}$ be an $(\vars3_U,\vars3_{\op{E}})$-discretisation for $\op{E}$ and choose any $\F{U}^n$ \edit{}{satisfying \eqref{eq: refining subspace definition} }such that 
-			$$ \tilde{\F{U}}^k = \F{U}^{n_k}, \qquad \tilde{\var2}_k \in \left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}$$
+			Let $(\edit{\tilde{\F{U}}^k}{\tilde{\var2}_k})_{k\in\F N}$ be an \edit{$(\aU,\aE)$-discretisation for $\op{E}$}{\aUaE\ } and choose any $\F{U}^n$ satisfying \eqref{eq: refining subspace definition} such that
+			$$ \edit{\tilde{\F{U}}^k = \F{U}^{n_k}, \qquad}{} \tilde{\var2}_k \in \edit{\left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]}{\F{U}^{n_k}}\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}$$
 			for all $k\in\F N$. Compute $\var0_n$ and $\var1_n$ by Algorithm~\ref{alg: refining FISTA}.
@@
 			\begin{itemize}
-				\item $\vars3_U>1$ and $n_k^2\simeq \vars3_{\op{E}}^k\vars3_U^{2k}$, or
-				\item $\vars3_U=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty$,
+				\item $\aU>1$ and $n_k^2\simeq \aE^k\aU^{2k}$, or
+				\item $\aU=1$, $\sum_{k=1}^\infty n_k^2\aE^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty$,
 			\end{itemize}
 			then
-			$$\op{E}_0(\var0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2} \qquad \text{uniformly for } N\in\F N.$$
+			$$\op{E}_0(\var0_N) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \aU^2}{\log \aE + \log \aU^2} \qquad \text{uniformly for } N\in\F N.$$
 		}
 	\end{theorem}
-	\noindent This theorem is very easy to implement numerically and requires very little knowledge of how to estimate $\op{E}_0(\var0_n)$.
-So long as $\vars3_U$ and $\vars3_{\op{E}}$ can be computed analytically, choosing $\tilde{\F{U}}^k$ to be uniform discretisations and $\tilde{\F{U}}^k = \F{U}^{n_k}=\ldots= \F{U}^{n_{k+1}-1}$ will achieve the stated convergence rate.
+	\noindent \edit{}{Analytically, this theorem gives new rates of convergence for FISTA when the minimiser is not achieved in the Hilbert space.
+Indeed for the original algorithm ($\F{U}^n=\F H$), if $\var0=0$ for simplicity and $(\tilde{\var2}_k)_{k\in\F N}$ is \emph{any} \aUaE\ exists, the result of Lemma~\ref{thm: mini exponential FISTA convergence} is
+	\begin{equation}\label{eq: slow exact FISTA}
+		\op{E}_0(\var0_N) \leq \inf_{\var2\in\F H} \frac{\norm{\var2}^2+N^2\op{E}_0(\var2)}{2t_N^2} \leq \min_{k\in\F N} \frac{\norm{\tilde{\var2}_k}^2+N^2\op{E}_0(\tilde{\var2}_k)}{2t_N^2} \lesssim \min_{k\in\F N} \frac{\aU^{2k}+N^2\aE^{-k}}{N^2}\lesssim N^{-2(1-\kappa)}.
+	\end{equation}
+	In this sense, we could say that $\op{E}$ converges at the rate $N^{-2(1-\kappa)}$ if and only if such a sequence exists. Nothing is lost (or gained) by choosing $\F{U}_n\subsetneq\F H$.}
+
+	\edit{This theorem is very easy to implement numerically}{Numerically, it is easy to implement the strategy of Theorem~\ref{thm: exponential FISTA convergence}} and requires very little knowledge of how to estimate $\op{E}_0(\var0_n)$.
+So long as $\aU$ and $\aE$ can be computed analytically, \edit{choosing $\tilde{\F{U}}^k$ to be uniform discretisations and $\tilde{\F{U}}^k = \F{U}^{n_k}=\ldots= \F{U}^{n_{k+1}-1}$ will}{one can choose $\tilde{\var2}_k$ implicitly to be the discrete minimisers of some `uniform' discretisations (e.g.
+$\F{U}^n=\{\norm{\var0}\leq k\}$ or finite element spaces with uniform mesh) to} achieve the stated convergence rate.
 
@@
 	Lemma~\ref{thm: sufficiently fast} gives a sufficient condition on $n_k$ for converging at the rate $O(N^{2(\kappa-1)})$, but it is not necessary. Indeed for $n\leq n_k$ the result shows 
-	$$\op{E}_0(\var0_n) \geq \min_{\var0\in\F{U}^n}\op{E}_0(\var0) = O(\vars3_{\op{E}}^{-k}) = O(n^{2(\kappa-1)})$$
+	$$\op{E}_0(\var0_n) \geq \min_{\var0\in\F{U}^n}\op{E}_0(\var0) = O(\aE^{-k}) = O(n^{2(\kappa-1)})$$
 	which suggests that to converge faster than $n^{2(\kappa-1)}$ requires choosing smaller $n_k$.
-As an example, in Section~\ref{sec: wavelet examples} we will see Algorithm~\ref{alg: refining FISTA} can converge at a linear rate, although this is not possible without adaptive refinement times.
+As an example, in Section~\ref{sec: wavelet examples} we will see Algorithm~\ref{alg: refining FISTA} can converge at a near-linear rate, although this is not possible without adaptive refinement times.
 On the other hand, choice of spatial adaptivity has no impact on rate but can impact computational efficiency.
-It will be permitted to use greedy discretisation techniques so long as each collection $\{\F{U}^n \st n_k\leq n<n_{k+1}\}$ satisfies a monotonicity condition.
-
-	While Theorem~\ref{thm: exponential FISTA convergence} also allows for spatial adaptivity, we will simplify the requirements to a form which seems more practical for implementation and also allows for temporal adaptivity.
-We make the assumption that the choice of $n_k$ depends only on the value $\op{E}(u_{n_k-1})$ and therefore make $u_{n_k-1}$ the root of our requirements.
-Lemma~\ref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\op{E}_0(\var0_{n_k-1})\lesssim \vars3_{\op{E}}^{-k}$.
+It will be permitted to use greedy discretisation techniques so long as it is sufficient to estimate $\op{E}_0(\var0_n)$ accurately.
+
+	Theorem~\ref{thm: exponential FISTA convergence} already allows for spatial adaptivity, so we focus on temporal adaptivity.
+Lemma~\ref{thm: sufficiently fast} suggests that a good refinement time strategy is to choose $n_k$ to be the minimal integer such that $\op{E}_0(\var0_{n_k-1})\lesssim \aE^{-k}$.
 However, the value of $\op{E}_0$ may be hard to estimate and so we retain a `backstop' condition which guarantees that convergence is no slower than the rate given by Theorem~\ref{thm: exponential FISTA convergence}.
-The only constraints on spatial adaptivity are the monotone inclusion properties, $\var0_n\in\F{U}^{n+1}$ and existence of $\tilde{\var2}_k$.
-This is confirmed by the following theorem.
+\edit{This is confirmed by}{In the non-classical case of $\aU>1$, we provide} the following theorem.
 	\begin{theorem}\label{thm: stronger exponential FISTA convergence}
 		\Copy{thm: stronger exponential FISTA convergence}{
-			Let $(\F{U}^n\subset\F H\edit{\cap\F{U}}{})_{n\in\F N}$ be a sequence of \edit{subspaces}{subsets satisfying \eqref{eq: refining subspace definition} }and $n_k\in\F N$ a monotone increasing sequence such that
-			$$ \tilde{\F{U}}^k \coloneqq \F{U}^{n_k}\edit{\ni \var0_{n_k-1}}{}, \qquad \tilde{\var2}_k \in \left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}$$
+			Let $(\F{U}^n\subset\F H)_{n\in\F N}$ be a sequence of subsets satisfying \eqref{eq: refining subspace definition}\edit{}{, $(\tilde{\var2}_k)_{k\in\F N}$ an \aUaE,} and $n_k\in\F N$ a monotone increasing sequence such that
+			$$ \edit{\tilde{\F{U}}^k \coloneqq \F{U}^{n_k}, \qquad}{} \tilde{\var2}_k \in \edit{\left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]}{\F{U}^{n_k}}\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}$$
 			for all $k\in\F N$.
@@
 
-			\bigbreak\noindent Suppose there exist $\vars3_U,\vars3_{\op{E}}\geq1$ such that either:
+			\edit[0]{\bigbreak\noindent \sout{Suppose there exist $\aU,\aE\geq1$ such that either:}
 			\begin{itemize}
-				\item $\vars3_U>1$ and $n_k^2\lesssim \vars3_{\op{E}}^k\vars3_U^{2k}$, or
-				\item $\vars3_U=1$, $\sum_{k=1}^\infty n_k^2\vars3_{\op{E}}^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty$
+				\item \sout{$\aU>1$ and $n_k^2\lesssim \aE^k\aU^{2k}$, or}
+				\item \sout{$\aU=1$, $\sum_{k=1}^\infty n_k^2\aE^{-k}<\infty$ and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty$}
 			\end{itemize}
-			and both
-			$$ \norm{\tilde{\var2}_k}\lesssim \vars3_U^k \qquad\text{and}\qquad \op{E}_0(\var0_{n_K-1}) \lesssim \vars3_{\op{E}}^{-K}.$$
-			Whenever these conditions on $n_k$ are satisfied, then
-			$$\min_{n\leq N}\op{E}_0(\var0_n) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2}$$
+			\sout{and both}
+			$$ \norm{\tilde{\var2}_k}\lesssim \aU^k \qquad\text{and}\qquad \op{E}_0(\var0_{n_k-1}) \lesssim \aE^{-k}.$$
+			\sout{Whenever these conditions on $n_k$ are satisfied, }}{If $\aU>1$, $\aE\geq1$, and $n_k^2\lesssim \aE^k\aU^{2k}$, }then
+			$$\min_{n\leq N}\op{E}_0(\var0_n) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \aU^2}{\log \aE + \log \aU^2}$$
 			uniformly for $N\in\F N$.
@@
 If we directly compare Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence}, we note that the convergence rate is the same in both theorems but the price for better adaptivity (i.e.
-relaxed $(\vars3_U,\vars3_{\op{E}})$ assumptions) is a slightly weaker stability guarantee (now convergence of $\min_{n\leq N}\op{E}_0(\var0_n)$).
+only an upper bound on $n_k$) is a slightly weaker stability guarantee (now convergence of $\min_{n\leq N}\op{E}_0(\var0_n)$).
 In Theorem~\ref{thm: exponential FISTA convergence}, as in the original FISTA algorithm, the sequence $\op{E}(\var0_n)$ is not monotone but the magnitude of oscillation is guaranteed to decay in time.
-This behaviour is lost in Theorem~\ref{thm: stronger exponential FISTA convergence} although it still holds on a subsequence.
+This behaviour is lost in Theorem~\ref{thm: stronger exponential FISTA convergence}.
 Although we do not prove it here, it can be shown that the stronger condition
 	\begin{equation}
-		\tilde{\var2}_k \in \left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}\cap\ldots\cap \F{U}^N
+		\tilde{\var2}_k \in \edit{\left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]}{\F{U}^{n_k}}\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}\cap\ldots\cap \F{U}^N
 	\end{equation}
@@
 
-	To enable a more practical implementation of Theorem~\ref{thm: stronger exponential FISTA convergence}, the following lemma describes several refinement time strategies which provide sufficient condition for $\op{E}_0(\var0_n) \lesssim \vars3_{\op{E}}^{-k}$.
+	To enable a more practical implementation of Theorem~\ref{thm: stronger exponential FISTA convergence}, the following lemma describes several refinement time strategies which provide sufficient condition for $\op{E}_0(\edit{\var0_n}{\tilde{\var2}_k}) \lesssim \aE^{-k}$.
 	\begin{lemma}\label{thm: practical refinement criteria}
 		\Copy{thm: practical refinement criteria}{
-			Let $(\tilde{\F{U}}^k)_{k\in\F N}$ be a sequence of \edit{subspaces}{subsets} with some points $\var0_k\in \tilde{\F{U}}^k$ and $\tilde{\var2}_k\in\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.
-Suppose that $\norm{\tilde{\var2}_k}\lesssim \vars3_U^k$.
-Any of the following conditions are sufficient to show that $\{\tilde{\F{U}}^k\}$ is an $(\vars3_U,\vars3_{\op{E}})$-discretisation for $\op{E}$:
+			Let \edit{$(\tilde{\F{U}}^k)_{k\in\F N}$ be a sequence of subsets with some points $\var0_k\in \tilde{\F{U}}^k$ and $\tilde{\var2}_k\in\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.
+Suppose that }{$(\tilde{\var2}_k)_{k\in\F N}$ be a sequence in $\F H$ with} $\norm{\tilde{\var2}_k}\lesssim \aU^k$.
+\edit{}{Suppose that $\tilde{\var2}_k\in\tilde{\F U}^k\coloneqq\F{U}^{n_k}$ and denote $\op{E}_0(\tilde{\F{U}}^k) \coloneqq \inf_{\var0\in\tilde{\F U}^k}\op{E}_0(\var0)$.
+}Any of the following conditions are sufficient to show that $\edit{\{\tilde{\F{U}}^k\}}{\tilde{\var2}_k}$ is an \edit{$(\aU,\aE)$-discretisation for $\op{E}$}{\aUaE}:
 			\begin{enumerate}
-				\item Small continuous gap refinement: $ \op{E}_0(\var0_k)\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
-				\item Small discrete gap refinement: $\op{E}_0(\tilde{\var2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $ \op{E}_0(\var0_k)-\op{E}_0(\tilde{\var2}_{k-1})\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$.
-				\item Small relative gap refinement: $ \op{E}_0(\var0_k) - \op{E}_0(\tilde{\var2}_{k-1}) \leq \vars1\op{E}_0(\var0_k)$ for all $k\in\F N$, some $0<\vars1\leq \frac{1}{1+\vars3_{\op{E}}}$.
+				\item Small continuous gap refinement: $ \op{E}_0(\edit{\var0_k}{\tilde{\var2}_k})\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+				\item Small discrete gap refinement: $\op{E}_0(\edit{\tilde{\var2}_k}{\tilde{\F{U}}^k})\leq \vars1\aE^{-k}$ and $ \op{E}_0(\edit{\var0_k}{\tilde{\var2}_k})-\op{E}_0(\edit{\tilde{\var2}_{k-1}}{\tilde{\F{U}}^{k-1}})\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+				\item Small relative gap refinement: $ \op{E}_0(\edit{\var0_k}{\tilde{\var2}_k}) - \op{E}_0(\edit{\tilde{\var2}_{k-1}}{\tilde{\F{U}}^{k-1}}) \leq \vars1\op{E}_0(\edit{\var0_k}{\tilde{\var2}_k})$ for all $k\in\F N$, some $0<\vars1\leq \frac{1}{1+\aE}$.
 			\end{enumerate}
-			\edit{}{If, furthermore, there exists a Banach space $(\F{U},\Norm\cdot)$ with $\F{U}\supset\F H$ and the sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded, then it is also sufficient that:}
+			\edit{If}{Suppose}, furthermore, there exists a Banach space $(\F{U},\Norm\cdot)$ with $\F{U}\supset\F H$ and \edit{}{dual-norm $\Norm\cdot_*$.
+If} the sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded, then it is also sufficient that:
 			\begin{enumerate}\setcounter{enumi}{3}
-				\item Small continuous gradient refinement: $ \edit{\Norm{\partial\op{E}(\var0_k)}_*}{\inf_{\var1\in\partial\op{E}(\var0_k)}\Norm{\var1}_*}\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
-				\item Small discrete gradient refinement: $\op{E}_0(\tilde{\var2}_k)\leq \vars1\vars3_{\op{E}}^{-k}$ and $\edit{\Norm{\tens{\Pi}_k\partial\op{E}(\var0_k)}_*}{\sup_{\var0,\tilde{\var0}\in \tilde{\F{U}}^k}\inf_{\var1\in\partial\op{E}(\var0_k)}\frac{|\IP{v}{\var0-\tilde{\var0}}|}{\Norm{\var0-\tilde{\var0}}}}\leq \vars1\vars3_{\op{E}}^{-k}$ for all $k\in\F N$, some $\vars1>0$\edit{, and sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded}{}.
+				\item Small continuous gradient refinement: $ \inf_{\var1\in\partial\op{E}(\edit{\var0_k}{\tilde{\var2}_k})}\Norm{\var1}_*\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+				\item Small discrete gradient refinement: $\op{E}_0(\edit{\tilde{\var2}_k}{\tilde{\F{U}}^k})\leq \vars1\aE^{-k}$ and $\sup_{\var0,\tilde{\var0}\in \tilde{\F{U}}^k}\inf_{\var1\in\partial\op{E}(\var0_k)}\frac{|\IP{v}{\var0-\tilde{\var0}}|}{\Norm{\var0-\tilde{\var0}}}\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
 			\end{enumerate}
@@
 The refinement criteria described by Lemma~\ref{thm: practical refinement criteria} can be split into two groups.
-Cases (1), (3), and (4) justify that any choice of $\tilde{\F{U}}^k\ni\var0_k$ (or $\var0_{n_k-1}$ in Theorem~\ref{thm: stronger exponential FISTA convergence}) satisfies the required conditions.
-In cases (2) and (5), $\var0_k$ is sufficient to choose the refinement time $n_k$ but not the \edit{subspace}{subset} $\tilde{\F{U}}^k$.
-In these cases one could, for example, choose $\tilde{\F{U}}^k$ to be a uniform discretisation with apriori estimates.
+Cases (1), (3), and (4) justify that any choice of \edit{$\tilde{\F{U}}^k\ni\var0_k$ (or $\var0_{n_k-1}$ in Theorem~\ref{thm: stronger exponential FISTA convergence})}{$\F{U}^{n_k}$ containing $\tilde{\var2}_k$} satisfies the required conditions.
+In cases (2) and (5), $\edit{\var0_k}{\tilde{\var2}_k}$ is sufficient to choose the refinement time $n_k$ but not the subset $\tilde{\F{U}}^k$.
+In these cases one could, for example, choose $\tilde{\F{U}}^k$ to be a uniform discretisation with a priori estimates.
 
@@
 Typically, gradient norms (in (4) and (5)) should be easier to estimate than function gaps because they only require local knowledge rather than global, i.e.
-$\partial\op{E}(\var0_n)$ rather than an estimate of $\edit{\op{E}(\var0^*)}{\Emin}$.
+$\partial\op{E}(\var0_n)$ rather than an estimate of $\Emin$.
 Implicitly, the global information comes from an extra condition on $\op{E}$ to assert that sublevel sets are bounded.
@@
 	\section{General examples}\label{sec: general examples}
-	\edit{In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, Algorithm~\ref{alg: refining FISTA} is much more broadly applicable.
-Here we justify this claim by demonstrating that the constants $\vars3_U$ and $\vars3_{\op{E}}$ can be easily computed in many examples.
-	The cases where $\F{U}$ is finite or countable dimensional are quite straight forward.
-If the total number of refinements is finite (i.e.
-$\F{U}^n = \F{U}^N$ for all $n\geq N$, some $N\in\F N$) then $\vars3_U = 1$.
-This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}.
-The examples considered here have $\F H = L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ where $\{\tilde{\F{U}}^n\st n\in\F N\}$ are finite dimensional finite-element--like spaces.
-We will now clarify exactly what is meant by these properties and then demonstrate that they are sufficient to find simple formulae for the values $\vars3_U$ and $\vars3_{\op{E}}$.
-}{
-	We consider the main use of Algorithm~\ref{alg: refining FISTA} to be where there exists a Banach space $(\F{U},\Norm\cdot)$ such that $\F{U}\supset\F H$ and
+	We consider the main use of Algorithm~\ref{alg: refining FISTA} to be where there exists a Banach space $(\F{U},\Norm\cdot)$ such that $\F{U}\supset\edit{\F H}{\{\var0\in\F{H}\st\op{E}(\var0)<\infty\}}$ and
 	$$\inf_{\var0\in\F H} \op{E}(\var0) = \min_{\var0\in\F{U}}\op{E}(\var0) = \op{E}(\var0^*)$$
 	for some $\var0^*\in\F{U}$.
-The cases where $\F H$ has finite or countable dimension are quite straightforward.
-If the total number of refinements is finite (i.e.
-$\F{U}^n = \F{U}^N$ for all $n\geq N$, some $N\in\F N$), then $\vars3_U = 1$.
+The cases where $\F H$ has finite or countable dimension are quite straightforward; if the total number of refinements is finite (i.e.
+$\F{U}^n = \F{U}^N$ for all $n\geq N$, some $N\in\F N$), then $\aU = 1$.
 This holds for most finite dimensional problems as well as the countable example discussed in detail in Section~\ref{sec: Lasso definition}.
-In this section we give explicit computations of $\vars3_U$ and $\vars3_{\op{E}}$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subsets $(\tilde{\F{U}}^n)_{n\in\F N}$ will be finite dimensional finite-element--like spaces, as defined below.
-	}
-
-	\begin{definition}
-		Suppose $\F{U}\subset L^q(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$\edit{}{ with sufficiently smooth boundary}.
+In this section we give explicit computations of $\aU$ and $\aE$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subsets $\F{U}^n$ will be finite dimensional finite-element--like spaces, as defined below.
+
+	\begin{definition}\label{def: finite element space}
+		Suppose \edit{}{$\norm\cdot_q\lesssim \Norm\cdot$ (i.e.
+}$\F{U}\subset L^q(\Domain)$\edit{}{)} for some \edit{}{$q\in[1,\infty]$ and }connected, bounded domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{}.
 We say that $\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$ is a \emph{mesh} if
-		$$\domain_i^k\subset\Domain \qquad\text{and} \qquad |\domain_i^k\cap\domain^k_j| = 0$$
-		for all $i$ and $j$.
-We say that $\tilde{\F{U}}^k\subset \edit{\F{U}\cap}{}\F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\var0\in\tilde{\F{U}}^k$ there exists $\var0_i^k\in\tilde{\F{U}}^k$ such that
-		$$\supp(\var0_i^k)\subset \bar{\domain_i^k}, \qquad \var0(\vec{x}) = \var0^k_i(\vec{x}) \qquad \text{ for a.e. }\vec{x}\in\domain_i^k, \text{ all } i\in\F N.$$
-
-		We say that a sequence of finite element subspaces $(\tilde{\F{U}}^k)_{k=0}^\infty$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\F{U}}^0\cap L^\infty(\Domain)$ such that for any $\var0_i^k\in\tilde{\F{U}}^k$ with $\supp(\var0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
-		$$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \var0_i^k(\vec{x}) = \sum_{j=1}^N\vars2_je_j(\vars0 \vec{x}+\vvars1) \quad \text{ for a.e.
+		$$\edit{\domain_i^k\subset}{\bigcup_{\domain\in\F M^k}\domain = } \Domain \qquad\text{and} \qquad |\edit{\domain_i^k\cap\domain^k_j}{\domain\cap\domain'}| = 0\qquad \text{for all \edit{$i$ and $j$}{$\domain,\domain'\in\F M^k,\ \domain\neq\domain'$}.}$$
+		We say that $\tilde{\F{U}}^k\subset \F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\tilde{\var0}\in\tilde{\F{U}}^k$ \edit{there exists $\var0_i^k\in\tilde{\F{U}}^k$ such that
+		\\$\supp(\var0_i^k)\subset \bar{\domain_i^k}, \qquad \tilde{\var0}(\vec{x}) = \var0^k_i(\vec{x}) \qquad \text{ for a.e. }\vec{x}\in\domain_i^k, \text{ all } i\in\F N.$\\}{%
+		$$\forall\domain\in\F M^k \qquad \exists \var0|_\domain\in \tilde{\F{U}}^k \quad\text{such that}\quad \op{supp}(\var0|_\domain)\subset\bar{\domain}\quad\text{and}\quad\text{for a.e.
+}\vec{x}\in\domain,\ \tilde{\var0}(\vec{x})=\var0|_\domain(\vec{x}).$$
+		}
+
+		\edit{We}{Moreover, for $\meshsize\in(0,1)$, we} say that the sequence $(\tilde{\F{U}}^k)_{k\in\F N}$ is \emph{$\meshsize$-refining} if there exists \edit{a basis $\{e_1, \ldots,e_N\}\subset\tilde{\F{U}}^0\cap L^\infty(\Domain)$ such that for any $\var0_i^k\in\tilde{\F{U}}^k$ with $\supp(\var0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
+		\\$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \var0_i^k(\vec{x}) = \sum_{j=1}^N\vars2_je_j(\vars0 \vec{x}+\vvars1) \quad \text{ for a.e.
 }\vec{x}\in\domain_i^k, \quad \supp(e_j(\vars0\cdot+\vvars1))\subset\bar{\domain_i^k}.
+$\\}{%
+		$c_\alpha>0$ such that for each $\tilde{\var0}\in\tilde{\F{U}}^k$ and $\domain\in\F M^k$,
+		$$ \exists (\var0,\alpha,\vec\beta)\in\tilde{\F U}^0\times\R^{d\times d}\times\R^d \quad \text{such that}\quad \op{det}(\alpha)\geq c_\alpha\meshsize^{kd} \quad\text{and}\quad \forall\vec{x}\in\Domain,\ \var0(\vec x) = \var0|_\domain(\alpha \vec{x}+\vec\beta).
 $$
-
-		We say that $(\tilde{\F{U}}^k)_k$ is \emph{of order $p$} if
-		$$\min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*} \lesssim_{\var0^*} \meshsize^{kp}.$$
-		We allow the implicit constant to have any dependence on $\var0^*$ so long as it is finite. For example, in the case of Sobolev spaces we would expect an inequality of the form
-		$\min_{\var2\in\tilde{\F{U}}^k}\norm{\var2-\var0^*}_{W^{0,q}} \lesssim \meshsize^{kp}\norm{\var0^*}_{W^{p,q}}$ \cite{Strang1972}.
+		}
+
+		We say that $(\tilde{\F{U}}^k)_k$ is \emph{of order $p$} if \edit{}{for any $\var0^*\in\argmin_{\var0\in\F U}\op{E}(\var0)$ there exists a sequence $(\tilde{\var2}_k)_{k\in\F N}$ such that}
+		\begin{equation}\label{eq: projection of u*}
+			\edit{\min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*} \lesssim_{\var0^*} \meshsize^{kp}}{\forall k\in\F N, \qquad\tilde{\var2}_k\in\tilde{\F U}^k  \quad\text{and}\quad \Norm{\tilde{\var2}_k-\var0^*}\lesssim_{\var0^*} \meshsize^{kp}}.
+		\end{equation}
+
+		We allow the implicit constant to have any dependence on $\var0^*$ so long as it is finite.
+For example, in the case of Sobolev spaces we would expect an inequality of the form $\edit{\min_{\var2\in\tilde{\F{U}}^k}\norm{\var2-\var0^*}_{W^{0,2}}}{\norm{\tilde{\var2}_k-\var0^*}_{W^{0,2}}} \lesssim \meshsize^{kp}\norm{\var0^*}_{W^{p,2}}$ \cite{Strang1972}.
 	\end{definition}
-	We note that any piecewise polynomial finite element \edit{}{(or spline)} space can be used to form a $\meshsize$-refining sequence of subspaces.
+
+	We note that any piecewise polynomial finite element (or spline) space can be used to form a $\meshsize$-refining sequence of subspaces.
 Wavelets with a compactly supported basis behave like a multi-resolution finite element space as there is always overlap in the supports of basis vectors.
@@
 Both of these exceptions are important and could be accounted for with further analysis but we focus on the more standard finite element case.
-The following theorem shows that all finite element spaces achieve the same basic rates of convergence in Algorithm~\ref{alg: refining FISTA}, depending on the particular properties of $\Norm\cdot$ and $\op{E}$.
+	\edit{The following theorem shows that all finite element spaces achieve the same basic rates of convergence in Algorithm~\ref{alg: refining FISTA}, depending on the particular properties of $\Norm\cdot$ and $\op{E}$.}{In order to align these discretisation estimates with the assumptions of Theorems~\ref{thm: exponential FISTA convergence} and \ref{thm: stronger exponential FISTA convergence}, we make the following observation.
+	\begin{lemma}\label{thm: pq to p'q'}
+		Fix $\var0^*\in\argmin_{\var0\in\F U}\op{E}(\var0)$ and $p',q'>0$. If a sequence $\tilde{\var2}_k\in\F H$ satisfies
+		$$ \norm{\tilde{\var2}_k}\lesssim \meshsize^{-kq'} \quad\text{and}\quad\op{E}(\tilde{\var2}_k) - \op{E}(\var0^*)\lesssim \meshsize^{kp'},$$
+		then $(\tilde{\var2}_k)_{k\in\F N}$ is an \aUaE\ for $\aU=\meshsize^{-q'}$ and $\aE=\meshsize^{-p'}$.
+	\end{lemma}
+	This is precisely rewriting the statement of Definition~\ref{def: exp subspaces} into terms of resolution and approximation properties.
+The following theorem shows how to link $p$ and $q$ from Definition~\ref{def: finite element space} with $p'$ and $q'$ from Lemma~\ref{thm: pq to p'q'}.
+	}
+
 	\begin{theorem}\label{thm: generic a_U and a_E}
-		Suppose $\F H= L^2(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$\edit{}{ with sufficiently smooth boundary} and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
-If $(\tilde{\F{U}}^k)_k$ is a sequence of $\meshsize$-refining finite element spaces of order $p$ then
+		Suppose $\F H= L^2(\Domain)$ for some connected, bounded domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{} and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
+\edit{If}{For $p\geq0$ and $\meshsize\in(0,1)$, if} $(\tilde{\F{U}}^k)_{k\in\F N}$ is a sequence of $\meshsize$-refining finite element spaces of order $p$, then \edit{}{$(\tilde{\var2}_k)_{k\in\F N}$ is an \aUaE\ for}
 		\begin{align*}
-			\vars3_U &\leq \splitln{1}{q\geq 2}{\sqrt{\meshsize^{-d}}}{q<2},
-			& \vars3_{\op{E}} &\geq \begin{cases}
-				\meshsize^{-p} & \op{E} \text{ is $\Norm\cdot$-Lipschitz at }\var0^*
-				\\\meshsize^{-2p} & \op{E} \text{ is $\Norm\cdot$-smooth at }\var0^*
-			\end{cases}\ .
+			\aU &\leq \splitln{1}{\text{if }q\geq 2,}{\sqrt{\meshsize^{-d}}}{q<2 \edit{}{\text{ and }\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_\infty}{\norm{\var0}}<\infty},}
+			& \aE &\geq \begin{cases}
+				\meshsize^{-2p} & \text{if }\op{E} \text{ is $\Norm\cdot$-smooth at }\var0^*,
+				\\\meshsize^{-p}\qquad & \text{if }\op{E} \text{ is $\Norm\cdot$-Lipschitz at }\var0^*,
+				\\ 1 &\text{otherwise.}
+			\end{cases}
 		\end{align*}
-		If $\op{g}$ is not Lipschitz at $\var0^*$ but $\op{f}$ is $\Norm\cdot$-Lipschitz and 
-		$$\min_{\var2\in\tilde{\F{U}}^k}\left\{\Norm{\var2-\var0^*}\st \op{g}(\var2)\leq \op{g}(\var0^*)\right\} \lesssim \min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*},$$
-		then, again, $\vars3_{\op{E}}\geq\meshsize^{-p}$.
+		\edit{If $\op{g}$ is not Lipschitz at $\var0^*$ but $\op{f}$ is $\Norm\cdot$-Lipschitz and 
+		\\$\min_{\var2\in\tilde{\F{U}}^k}\left\{\Norm{\var2-\var0^*}\st \op{g}(\var2)\leq \op{g}(\var0^*)\right\} \lesssim \min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*},$\\
+		then, again, $\aE\geq\meshsize^{-p}$.}{}
 	\end{theorem}
 	The proof of this theorem is in Appendix~\ref{app: generic a_U and a_E}.
-The main take-home for this theorem is that the computation of $\vars3_U$ and $\vars3_{\op{E}}$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\op{E}$.
-The only non-trivial case is when $\op{g}$ is not smooth enough to estimate directly.
-So long as $\tilde{\F{U}}^k$ are sufficiently dense in sublevel sets of $\op{g}$, the smoothness of $\op{f}$ is sufficient to give a convergence rate.
+\edit{}{Note that $\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_\infty}{\norm{\var0}}$ is finite whenever $\tilde{\F{U}}^0\subset L^\infty(\Domain)$ is finite dimensional, so this is not a very strong assumption.} The main take-home for this theorem is that the computation of $\aU$ and $\aE$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\op{E}$.
+\edit{The only non-trivial case is when $\op{g}$ is not smooth enough to estimate directly.
+So long as $\tilde{\F{U}}^k$ are sufficiently dense in sublevel sets of $\op{g}$, the smoothness of $\op{f}$ is sufficient to give a convergence rate.}{}
 
@@
 	\section{L1 penalised reconstruction}\label{sec: Lasso definition}
-	\edit{We now focus on the specific example of Lasso}{The canonical example for FISTA is the LASSO problem with a quadratic data fidelity and L1 regularisation.
-In this section we develop the necessary analytical tools for the variant with general smooth fidelity term} which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}.
-We consider three forms \edit{of Lasso}{} which will be referred to as the continuous, countable, and discrete \edit{Lasso}{problem} depending on whether the space $\F{U}$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively.
-In each case, the energy can be written as
+	The canonical example for FISTA is the LASSO problem with a quadratic data fidelity and L1 regularisation.
+In this section we develop the necessary analytical tools for the variant with general smooth fidelity term which will be used for numerical results in Section~\ref{sec: numerics}.
+We consider three forms  which will be referred to as the continuous, countable, and discrete problem depending on whether the space $\F{U}$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or \edit{finite dimensional}{$\R^M$} respectively.
+\edit{}{Let $\A\colon\F{U}\cup\F{H}\to\R^m$ be a linear operator represented by the kernels $\psi_j\in\F{U}^*\cap\F{H}$ such that
+	\begin{equation}\label{eq: kernels of A}
+		\forall \var0\in\F{U}\cup\F{H},\ j=1,\ldots,m,\qquad (\A\var0)_j = \IP{\psi_j}{\var0}.
+	\end{equation}
+	In particular, for the discrete (respectively countable) case we have $\psi_j\in\R^M$ (resp.
+$\ell^2(\R)$).
+In the continuous case we will require the additional smoothness $\psi_j\in C^1([0,1]^d)$.
+In Section~\ref{sec: smoothing operators} we will formally define and estimate several operator semi-norms for $\A$ of this form, for example Lemma~\ref{thm: norm bound L2} confirms that $\A$ is continuous on $\F{H}$ (i.e.
+$\norm{\A}<\infty$).} In each case, the energy \edit{can be}{we consider is} written as
 	\begin{equation}\label{eq: Lasso energy}
-		\op{E}(\var0) = \edit{\tfrac12\norm{\A\var0-\data}_{\ell^2}^2}{\op{f}(\A\var0-\data)} + \mu\Norm{\var0}
-	\end{equation}
-	for some $\A\colon \F{U}\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$.
-\edit{}{We assume $\op{f}\in C^1(\R^m)$ is convex with $\nabla\op{f}$ 1-Lipschitz, and in the continuous-space case, we require $\A^*\colon\R^m\to C^1([0,1]^d)$.
-}Let $\var0^*\in\argmin_{\var0\in\F{U}}\op{E}(\var0)$.
+		\op{E}(\var0) = \op{f}(\A\var0-\data) + \mu\Norm{\var0}
+	\end{equation}
+	for some \edit{$\A\colon \F{U}\to\R^m$ and }{}$\mu>0$ where $\Norm\cdot=\norm\cdot_1$.
+We assume $\op{f}\in C^1(\R^m)$ is convex\edit{ with}{, bounded from below, and} $\edit{\nabla\op{f}}{(\norm{\A}^2\nabla\op{f})}$ is 1-Lipschitz\edit{, and in the continuous-space case we also require $\A^*\colon\R^m\to C^1([0,1]^d)$}{}.
+	Let $\var0^*\in\argmin_{\var0\in\F{U}}\op{E}(\var0)$\edit{}{, which is non-empty so long as $\psi_j\in C$ (i.e. $\A$ is sequentially weak-star continuous)}.
 
 	The aim of this section is to develop all of the necessary tools for implementing Algorithm~\ref{alg: refining FISTA} on the energy \eqref{eq: Lasso energy} using the convergence guarantees of either Theorem~\ref{thm: exponential FISTA convergence} or Theorem~\ref{thm: stronger exponential FISTA convergence}.
-This includes computing the rates $\vars3_U$ and $\vars3_{\op{E}}$, estimating the continuous gap $\op{E}_0(\var0_n)$, and developing an efficient refinement choice for $\F{U}^n$.
+This includes computing the rates $\aU$ and $\aE$, estimating the continuous gap $\op{E}_0(\var0_n)$, and developing an efficient refinement choice for $\F{U}^n$.
 
@@
 In this case we choose $\tilde{\F{U}}^k$ to be the span of all piecewise constant functions on a mesh of squares with maximum side length $2^{-k}$ (i.e.
-$\meshsize=\tfrac12$).
-
-	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_U=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$.
-This can be seen because for any $\var0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$,
+$\meshsize=\tfrac12$) \edit{}{and $$\tilde{\var2}_k\coloneqq \sum_{\domain\in\F M^k}\frac{\var0^*(\domain)}{|\domain|}\1_\domain\quad\text{where}\quad\1_\domain(\vec x)=\splitln{1}{\vec{x}\in\domain}{0}{\text{else}}.$$
+	By construction $\tilde{\var2}\in\tilde{\F{U}}^k$, however note that for any $\var0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
 	\begin{equation}
@@
 	\end{equation}
-	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$.
-\edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\F{U}}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing, therefore }
-	for any $\var0\in\F H$, $\var2\coloneqq \tilde{\tens{\Pi}}_k\var0\in\tilde{\F{U}}^k$ we have
-	\begin{align}
-		\op{E}(\var2)-\op{E}(\var0) &= \edit{\tfrac12\norm{\A\var2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\var0-\data}_{\ell^2}^2}{\op{f}(\A\var2-\data)-\op{f}(\A\var0-\data)} + \mu\left(\Norm{\var2}-\Norm{\var0}\right)
-		\\&\leq \ip{\nabla \op{f}(\A\var2-\data)}{\A(\var2-\var0)}
-		\\&\leq\edit{\max(\norm{\A\var2-\data}_{\ell^2},\norm{\A\var0-\data}_{\ell^2})}{\left[\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2} + \norm{\A(\var2-\var0^*)}_{\ell^2}\right]}\norm{\A(\var2-\var0)}_{\ell^2}.
-	\end{align}
-	\edit{Choosing $\var2 = \tilde{\tens{\Pi}}_k\var0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F{U}\to\tilde{\F{U}}^k$ gives
-	\\\centerline{$\displaystyle\op{E}(\var2)-\op{E}(\var0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\var0^*-\var0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\var0^*}.$}
-	Expanding the operator norm further,
-	\\\centerline{$\displaystyle
-		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vec{r}\in\R^m}\max_{\vec{x}\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vec{r}](\vec{x})-[\A^*\vec{r}](\vec{x})|}{\norm{\vec{r}}_{\ell^2}} \leq \sup_{\vec{r}\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vec{r}]}_{L^\infty}}{\norm{\vec{r}}_{\ell^2}}
-		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
-	}{Clearly $\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2}$ is a constant. For the second term, recall $\Norm{\var2}\leq \Norm{\var0}$, therefore we can bound
-	\begin{equation}
-	\norm{\A(\var2-\var0^*)}_{\ell^2} = \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} \IP{\A^*\vec{r}}{\var2-\var0^*} \leq \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} |\A^*\vec{r}|_{L^\infty}\Norm{\var2-\var0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\var0}+\Norm{\var0^*}).
-	\end{equation}
-	Similarly, the final term can be approximated by
-	\begin{multline}
+	Because of this, } application of Theorem~\ref{thm: generic a_U and a_E} gives $\aU=2^{\frac d2}$ \edit{although  $\Norm\cdot$ is too strong a metric and only results in}{but only} $\aE\geq1$.
+	\edit{This can be seen because for any $\var0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
+	\\$\Norm{\var0-\delta} = \sup_{\varphi\in C(\Domain), \norm{\varphi}_{L^\infty}\leq 1} \IP{\varphi}{\var0-\delta} = \Norm{\var0}+\Norm{\delta} \geq 1 = \meshsize^0.$}{}
+	To improve our estimate of $\aE$ requires additional assumptions on $\A$.
+Note that \edit{the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\F{U}}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing}{$\Norm{\tilde{\var2}_k}=\sum_{\domain\in\F M^k}|\var0^*(\domain)|\leq \Norm{\var0^*}$}, therefore \edit{for any $\var0\in\F H$, $\var2\coloneqq \tilde{\tens{\Pi}}_k\var0\in\tilde{\F{U}}^k$}{} we have
+	\begin{align}
+		\op{E}(\edit{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) &= \op{f}(\A\edit{\var2}{\tilde{\var2}_k}-\data)-\op{f}(\A\var0^*-\data) + \mu\left(\Norm{\edit{\var2}{\tilde{\var2}_k}}-\Norm{\var0^*}\right)
+		\\&\leq \ip{\nabla \op{f}(\A\edit{\var2}{\tilde{\var2}_k}-\data)}{\A(\edit{\var2}{\tilde{\var2}_k}-\var0^*)}
+		\\&\leq\left[\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2} + \edit{}{\norm{\A}^{-2}}\norm{\A(\edit{\var2}{\tilde{\var2}_k}-\var0^*)}_{\ell^2}\right]\norm{\A(\edit{\var2}{\tilde{\var2}_k}-\var0^*)}_{\ell^2}.
+	\end{align}
+	Clearly $\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2}$ is a constant. \edit[0]{\sout{For the second term, recall $\Norm{\var2}\leq \Norm{\var0}$, therefore we can bound
+	\\$\norm{\A(\var2-\var0^*)}_{\ell^2} = \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} \IP{\A^*\vec{r}}{\var2-\var0^*} \leq \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} |\A^*\vec{r}|_{L^\infty}\Norm{\var2-\var0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\var0}+\Norm{\var0^*}).$\\
+	Similarly, the final term can be approximated by}
+	\begin{multline*}
 		\norm{\A(\tilde{\tens{\Pi}}_k\var0-\var0)}_{\ell^2}
@@
 		\\\leq \sup_{\vec{r}\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vec{r}]}_{L^\infty}\: \norm{\vec{r}}_{\ell^2}^{-1} \Norm{\var0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\var0}
-	\end{multline}}
-	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.
-\edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\var0^*_j\in\F H$ such that $\var0^*_j\rightharpoonup\var0^*$ and $\lim_{j\to\infty}\op{E}(\var0^*_j)=\op{E}(\var0^*)$.
+	\end{multline*}
+	\sout{where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.
+Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\var0^*_j\in\F H$ such that $\var0^*_j\rightharpoonup\var0^*$ and $\lim_{j\to\infty}\op{E}(\var0^*_j)=\op{E}(\var0^*)$.
 	Combining these estimates gives 
-		\begin{equation}
-			\inf_{\var2\in\tilde{\F{U}}^k} \op{E}(\var2)-\op{E}(\var0^*) = \lim_{j\to\infty} \inf_{\var2\in\tilde{\F{U}}^k} \op{E}(\var2)-\op{E}(\var0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\var0_j^*)-\op{E}(\var0_j^*) \lesssim 2^{-k}.
-		\end{equation}}
-
-	This computation confirms two things, firstly that the scaling constant is indeed $\vars3_{\op{E}} = 2$, and secondly that the required smoothness to achieve a good rate with Algorithm~\ref{alg: refining FISTA} is that $\A^*\colon\R^m\to C^1(\Domain)$ is a bounded operator.
+	\\$\inf_{\var2\in\tilde{\F{U}}^k} \op{E}(\var2)-\op{E}(\var0^*) = \lim_{j\to\infty} \inf_{\var2\in\tilde{\F{U}}^k} \op{E}(\var2)-\op{E}(\var0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\var0_j^*)-\op{E}(\var0_j^*) \lesssim 2^{-k}.$}
+	}{%
+	For the other term, note that for all $\vec{r}\in\R^m$, denote $\varphi\coloneqq\A^*\vec{r}$, then 
+	\begin{multline}
+		\ip{\vec r}{\A(\tilde{\var2}_k-\var0^*)} = \IP{\varphi}{\tilde{\var2}_k-\var0^*} = 
+		\sum_{\domain\in\F M^k}\int_\domain \varphi(\vec{x}) \diff[\tilde{\var2}_k-\var0^*] 
+		= \sum_{\domain\in\F M^k}|\domain|^{-1}\iint_\domain [\varphi(\vec{x}) - \varphi(\vec{y})] \diff\vec{x}\diff\var0^*(\vec{y}) 
+		\\\leq \max_{\domain\in\F M^k}\op{diam}(\domain)\norm{\nabla\varphi}_\infty\Norm{\var0^*}.
+	\end{multline}
+	This gives the estimate
+	\begin{equation}
+		\norm{\A(\tilde{\var2}_k-\var0^*)}_{\ell^2} = \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} \IP{\A^*\vec{r}}{\tilde{\var2}_k-\var0^*} \leq \sqrt{d}2^{-k}\Norm{\var0^*}\sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1}\norm{\nabla[\A^*\vec{r}]}_{L^\infty}.
+	\end{equation}
+	This last term we denote the semi-norm $|\A^*|_{\ell^2\to C^1}$ which is shown to be finite in Section~\ref{sec: smoothing operators}.
+For now, assuming that $|\A^*|_{\ell^2\to C^1}<\infty$, we conclude that $\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*)\lesssim 2^{-k}$.}
+
+	This computation confirms two things, firstly that the scaling constant is indeed $\aE = 2$, and secondly that the required smoothness to achieve a good rate with Algorithm~\ref{alg: refining FISTA} is that $\A^*\colon\R^m\to C^1(\Domain)$ is a bounded operator.
 This accounts for using the weaker topology of $\C M(\Domain)$ rather than $L^1(\Domain)$.
-In Section~\ref{sec: smoothing operators} we will show two practical examples where this (semi)norm is accurately computable.
+In Section~\ref{sec: smoothing operators} we will show two practical examples where this seminorm is accurately computable.
 
@@
 	\begin{equation}\label{eq: Lasso energy rate}
-		\kappa = \frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2} = \frac{d}{1+d} \quad \implies \quad \op{E}_0(\var0_n) \lesssim n^{-2(1-\kappa)} = n^{-\frac{2}{1+d}}.
-	\end{equation}
-	This rate can be used to infer the required resolution at each iteration, in particular on iteration $n$ with $n^2\simeq (\vars3_{\op{E}}\vars3_U^2)^k$ we expect the resolution to be
+		\kappa = \frac{\log \aU^2}{\log \aE + \log \aU^2} = \frac{d}{1+d} \quad \implies \quad \op{E}_0(\var0_n) \lesssim n^{-2(1-\kappa)} = n^{-\frac{2}{1+d}}.
+	\end{equation}
+	This rate can be used to infer the required resolution at each iteration, in particular on iteration $n$ with $n^2\simeq (\aE\aU^2)^k$ we expect the resolution to be
 	\begin{equation}\label{eq: Lasso resolution rate}
-		2^{-k} = \left(\vars3_{\op{E}}\vars3_U^2\right)^{\frac{k}{1+d}} \simeq n^{-\frac{2}{1+d}}.
+		2^{-k} = \left(\aE\aU^2\right)^{\frac{k}{1+d}} \simeq n^{-\frac{2}{1+d}}.
 	\end{equation}
@@
 The key fact here is that, even when $\F{U}$ is infinite dimensional, it is known (e.g.
-\cite[\edit{Theorem 2}{Thm 6}]{Unser2016} and \cite[\edit{Corollary 2}{Cor 3.8}]{Boyer2019}) that $\var0^*$ can be chosen to have at most $m$ non-zeros.
-If this is the case, then $\var0^*\in \ell^2(\R)$; this makes the analysis much simpler than in the continuous case.
-In this subsection we will ignore the discrete case as a simple sub-case of the countable.
-
-	For countable \edit{Lasso}{dimensions} we consider discretisation subspaces of the form 
+\cite[Thm 6]{Unser2016} and \cite[Cor 3.8]{Boyer2019}) that \edit{}{there exists} $\var0^*\edit{}{\in\argmin_{\var0\in\F{U}}\op{E}(\var0)}$ \edit{can be chosen to have}{with} at most $m$ non-zeros.
+If this is the case, then $\var0^*\in \ell^2(\R)$\edit{;}{, indeed $\norm{\var0^*}_{\ell^2}\leq\sqrt{m}\norm{\var0^*}_{\ell^1}$.
+} This makes the \edit{analysis}{estimates of $\aE/\aU$} much simpler than in the continuous case\edit{}{ as we can stay in the finite-dimensional Hilbert-space setting}.
+
+	For countable dimensions we consider discretisation subspaces of the form 
 	$$\tilde{\F{U}}^k = \{\var0\in \ell^1(\R) \st i\notin J_k\implies \var0_i=0\}$$ for some sets $J_k\subset\F N$, i.e.
 infinite vectors with finitely many non-zeros.
-The key change in analysis from the continuous case is $\norm{\var0^*}<\infty$, which leads to $\vars3_U=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\op{E}}$ or any additional properties of $\A$.
+The key change in analysis from the continuous case is $\norm{\var0^*}<\infty$, which leads to $\aU=1$ and the expected optimal rate of $n^{-2}$, independent of $\aE$ or any additional properties of $\A$.
 The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence} hold trivially.
@@
 	\subsection{Refinement metrics}\label{sec: Lasso gap and gradient}
-	Lemma~\ref{thm: practical refinement criteria} shows that adaptive refinement can be performed based on estimates of the function gap or the \edit{gradient}{subdifferential}.
+	Lemma~\ref{thm: practical refinement criteria} shows that adaptive refinement can be performed based on estimates of the function gap or the subdifferential.
 In this subsection we provide estimates for these values which can be easily computed.
@@
 	\subsubsection{Bounds for discretised functionals}\label{sec: bound discrete}
-	We start by computing estimates for discretised \edit{Lasso}{energies}.
-This covers the cases when either the continuous/countable \edit{Lasso}{energy} is projected onto $\F{U}^n$, or $\F{U}$ is finite dimensional.
+	We start by computing estimates for discretised energies.
+This covers the cases when either the continuous/countable energy is projected onto $\F{U}^n$, or $\F{U}$ is finite dimensional.
 For notation we will use the continuous case, to recover the other cases just replace continuous indexing with discrete (i.e.
@@
 	Let $\tens{\Pi}_n\colon\F H\to\F{U}^n$ denote the orthogonal projection.
-\edit{For Lasso}{In our case}, the discretised function $\var0\mapsto\op{E}(\tens{\Pi}_n\var0)$ is equivalent to replacing $\var0$ with $\tens{\Pi}_n\var0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.
+\edit{}{We consider the discretised function $\op{E}|_{\F{U}^n}\colon \F{U}^n\to\R$ and its subdifferential $\partial_n\op{E}(\cdot) = \tens{\Pi}_n\partial\op{E}(\cdot)$.} In our case, the \edit{discretised function $\var0\mapsto\op{E}(\tens{\Pi}_n\var0)$}{behaviour of $\op{E}|_{\F{U}^n}$} is equivalent to replacing $\var0$ with $\tens{\Pi}_n\var0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.
 
@@
 	\begin{align}
-		\partial_n \op{E}(\tens{\Pi}_n\var0_n)(\vec{x}) &= [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)](\vec{x}) + \begin{cases}
+		\partial_n \op{E}(\var0_n)(\vec{x}) &= [\tens{\Pi}_n\A^*\nabla\op{f}(\A\var0_n-\data)](\vec{x}) + \begin{cases}
 			\{+\mu\} & \var0_n(\vec{x})>0 \\ [-\mu,\mu] & \var0_n(\vec{x})=0 
@@
 		\end{cases} 
-		\\&\eqqcolon [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)](\vec{x}) + \mu\tens{\Pi}_n\sign(\var0_n(\vec{x}))
+		\\&\eqqcolon [\tens{\Pi}_n\A^*\nabla\op{f}(\A\var0_n-\data)](\vec{x}) + \mu\tens{\Pi}_n\sign(\var0_n(\vec{x}))
 	\end{align}
@@
 	\begin{align}
-		\Norm{\partial_n \op{E}(\var0_n)}_* &= \max_{\vec{x}\in\Domain}\min\left\{|\var1| \st \var1\in \tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)(\vec{x}) +  \mu\sign(\var0_n(\vec{x}))\right\}
+		\Norm{\partial_n \op{E}(\var0_n)}_* &= \max_{\vec{x}\in\Domain}\min\left\{|\var1| \st \var1\in \tens{\Pi}_n\A^*\nabla\op{f}(\A\var0_n-\data)(\vec{x}) +  \mu\tens{\Pi}_n\sign(\var0_n(\vec{x}))\right\}
 		\\&= \max_{\vec{x}\in\Domain}\begin{cases}
-			|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)(\vec{x}) + \mu| & \var0_n(\vec{x})>0
-			\\|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)(\vec{x}) - \mu| & \var0_n(\vec{x})<0
-			\\\max\left(|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\var0_n-\data)(\vec{x})| - \mu, 0\right) & \var0_n(\vec{x}) = 0
+			|[\tens{\Pi}_n\A^*\nabla\op{f}(\A\var0_n-\data)(\vec{x}) + \mu| & \var0_n(\vec{x})>0
+			\\|[\tens{\Pi}_n\A^*\nabla\op{f}(\A\var0_n-\data)(\vec{x}) - \mu| & \var0_n(\vec{x})<0
+			\\\max\left(|[\tens{\Pi}_n\A^*\nabla\op{f}(\A\var0_n-\data)(\vec{x})| - \mu, 0\right) & \var0_n(\vec{x}) = 0
 		\end{cases}
@@
 	\begin{align}
-		\min_{\var0\in \F{U}^n} \edit{\tfrac12\norm{\A\var0-\data}_{\ell^2}^2}{\op{f}(\A\var0-\data)} + \mu\Norm{\var0} &= \min_{\var0\in\F H}\max_{\vec{\varphi}\in\R^m} \ip{(\A\tens{\Pi}_n\var0-\data)}{ \vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\edit{\tfrac12\norm{\vec{\varphi}}_{\ell^2}^2}{\op{f}^*(\vec{\varphi})}
-		\\&= \max_{\vec{\varphi}\in\R^m}\min_{\var0\in\F H} \ip{(\A\tens{\Pi}_n\var0-\data)}{\vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\edit{\tfrac12\norm{\vec{\varphi}}_{\ell^2}^2}{\op{f}^*(\vec{\varphi})}
-		\\&= \max_{\vec{\varphi}\in\R^m} \splitln{-\ip{\data}{\vec{\varphi}} -\edit{\tfrac12\norm{\vec{\varphi}}_{\ell^2}^2}{\op{f}^*(\vec{\varphi})}}{\qquad\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu}{-\infty}{\qquad\text{else}}
-		\\&= -\min_{\vec{\varphi}\in\R^m} \underbrace{\edit{\tfrac12\norm{\vec{\varphi}}_{\ell^2}^2}{\op{f}^*(\vec{\varphi})}+\ip{\data}{\vec{\varphi}}}_{\eqqcolon \op{E}^*(\vec{\varphi})}  + \chi(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu).
+		\min_{\var0\in \F{U}^n} \op{f}(\A\var0-\data) + \mu\Norm{\var0} &= \min_{\var0\in\F H}\max_{\vec{\varphi}\in\R^m} \ip{(\A\tens{\Pi}_n\var0-\data)}{ \vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\op{f}^*(\vec{\varphi})
+		\\&= \max_{\vec{\varphi}\in\R^m}\min_{\var0\in\F H} \ip{(\A\tens{\Pi}_n\var0-\data)}{\vec{\varphi}} +\mu\Norm{\tens{\Pi}_n\var0} -\op{f}^*(\vec{\varphi})
+		\\&= \max_{\vec{\varphi}\in\R^m} \splitln{-\ip{\data}{\vec{\varphi}} -\op{f}^*(\vec{\varphi})}{\qquad\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu}{-\infty}{\qquad\text{else}}
+		\\&= -\min_{\vec{\varphi}\in\R^m} \underbrace{\op{f}^*(\vec{\varphi})+\ip{\data}{\vec{\varphi}}}_{\eqqcolon \op{E}^*(\vec{\varphi})}  + \chi(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu).
 	\end{align}
@@
 	\begin{equation}
-		\edit{}{\A\var0^*-\data\in\partial\op{f}^*(\vec{\varphi}^*),\qquad\text{or equivalently}\qquad}
-		\vec{\varphi}^* = \edit{}{\nabla\op{f}}(\A\var0^*-\data).
+		\A\var0^*-\data\in\partial\op{f}^*(\vec{\varphi}^*),\qquad\text{or equivalently}\qquad
+		\vec{\varphi}^* = \nabla\op{f}(\A\var0^*-\data).
 	\end{equation}
@@
 	\begin{equation}
-		\vec{\varphi}_n\coloneqq \edit{}{\nabla\op{f}}(\A\var0_n - \data), \qquad \op{E}(\var0)-\min_{\var0'\in\F{U}^n}\op{E}(\var0') \leq \op{E}(\var0) +\edit{\min_{\vars2\geq 0}\{}{}\op{E}^*(\vars2\vec{\varphi}_n) \edit{\st \vars2 \Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*\leq \mu\}}{}
-	\end{equation}
-	\edit{with optimal choice}{for some $0\leq \vars2\leq\frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*}$. In the case $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$, one can use the optimal choice}
+		\vec{\varphi}_n\coloneqq \nabla\op{f}(\A\var0_n - \data), \qquad \op{E}(\var0)-\min_{\var0'\in\F{U}^n}\op{E}(\var0') \leq \op{E}(\var0) +\op{E}^*(\vars2\vec{\varphi}_n)
+	\end{equation}
+	for some $0\leq \vars2\leq\frac{\mu}{\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*}$. In the case $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$, one can use the optimal choice
 	\begin{equation}
@@
 	\end{equation}
-	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\A\var0_n-\data)\edit{ = \frac12\norm{\vec{\varphi}_n}_{\ell^2}^2}{}$ and $\tens{\Pi}_n\nabla\op{f}(\A\var0_n-\data)\edit{ = \tens{\Pi}_n\A^*\vec{\varphi}_n}{}$ are easily computable, therefore $\vars2$ and $\op{E}(\var0_n) +\op{E}^*(\vars2\vec{\varphi}_n)$ are also easy to compute.
+	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\A\var0_n-\data)$ and $\tens{\Pi}_n\nabla\op{f}(\A\var0_n-\data)$ are easily computable, therefore $\vars2$ and $\op{E}(\var0_n) +\op{E}^*(\vars2\vec{\varphi}_n)$ are also easy to compute.
 
@@
 	Extending the results of Section~\ref{sec: bound discrete} to $\F{U}=\ell^1(\R)$ is analytically very simple but computationally relies heavily on the specific choice of $\A$.
-The computations of \edit{gradients}{subdifferentials} and gaps carry straight over replacing $\tens{\Pi}_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\F{U}^n = \{\var0\in\ell^1\st i\notin J_n\implies \var0_i=0\}$.
+The computations of subdifferentials and gaps carry straight over replacing $\tens{\Pi}_n$ with the identity and adding the sets $J_n\subset\F N$ which define $\F{U}^n = \{\var0\in\ell^1\st i\notin J_n\implies \var0_i=0\}$.
 In particular,
@@
 		\end{cases}
-		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\edit{=\max\left(0, \min\left(\frac{-\ip{\data}{\vec{\varphi}_n}}{\norm{\vec{\varphi}_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right)\right)}{\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]}
-	\end{align}
-	where $\vec{\varphi}_n = \edit{}{\nabla\op{f}}(\A\var0_n-\data)\in\R^m$ is always exactly computable.
+		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^*(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]
+	\end{align}
+	where $\vec{\varphi}_n = \nabla\op{f}(\A\var0_n-\data)\in\R^m$ is always exactly computable.
 
@@
 	\subsubsection{Bounds for continuous functionals}\label{sec: bound continuous}
-	Finally we extend the results of Section~\ref{sec: bound discrete} to continuous \edit{Lasso}{problems}. Similar to the countable case, the exact formulae can be written down immediately:
+	Finally we extend the results of Section~\ref{sec: bound discrete} to continuous problems. Similar to the countable case, the exact formulae can be written down immediately:
 	\begin{align}
@@
 		\end{cases}
-		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\edit{=\max\left(0, \min\left(\frac{-\ip{\data}{\vec{\varphi}_n}}{\norm{\vec{\varphi}_n}_{\ell^2}^2}, \frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right)\right)}{\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]}.
+		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^*(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right].
 	\end{align}
@@
 
-	The bounds presented here for continuous \edit{Lasso}{problems} emphasise the twinned properties required for adaptive mesh optimisation.
+	The bounds presented here for continuous problems emphasise the twinned properties required for adaptive mesh optimisation.
 The mesh should be refined greedily to the structures of $\var0^*$, but also must be sufficiently uniform to provide a good estimate for $\op{E}(\var0^*)$.
@@
 	\subsection{Support detection}\label{sec: support detection}
-	The main motivation for using \edit{Lasso}{L1 penalties} in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\var0^*$ is also provably close to the `true' support \cite{Duval2017a,Poon2018}.
+	The main motivation for using L1 penalties in applications is because it recovers sparse signals, in the case of compressed sensing the support of $\var0^*$ is also provably close to the `true' support \cite{Duval2017a,Poon2018}.
 If $\var0_n\approx \var0^*$ in the appropriate sense, then we should also be able to quantify the statement $\op{supp}(\var0_n)\approx\op{supp}(\var0^*)$.
@@
 In particular, the support is at most $m$ distinct points and are a subset of $\{ \vec{x}\in\Domain \st |\A^*\vec{\varphi}^*|(\vec{x}) = \mu\} $ (an equivalent statement holds for the countable case).
-Less formally, this can also be seen from the the \edit{gradient}{subdifferential} computations in Section~\ref{sec: Lasso gap and gradient}, for all $\vec{x}\in\supp(\var0^*)$ we have
+Less formally, this can also be seen from the the subdifferential computations in Section~\ref{sec: Lasso gap and gradient}, for all $\vec{x}\in\supp(\var0^*)$ we have
 	\begin{equation}
@@
 	$$ \text{if}\quad \op{E}(\var0_n) + \op{E}^*(\vars2_0 \vec{\varphi}_n) \approx 0 \quad \text{then}\quad \left\{\vec{x}\st \mu - |[\A^*\vec{\varphi}_n](\vec{x})|\ll 1\right\} \subset\{\vec{x} \st \var0^*(\vec{x})=0\}.$$
-	\edit{First we use the strong convexity of $\op{E}^*$}{Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex \cite[Chapter 10, Thm.
+	Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex \cite[Chapter 10, Thm.
 4.2.2]{Hiriart2013}.
-Therefore}, if $\vars2_0\vec{\varphi}_n$ and $\vec{\varphi}^*$ are both dual-feasible, then
+Therefore, if $\vars2_0\vec{\varphi}_n$ and $\vec{\varphi}^*$ are both dual-feasible, then
 	\begin{equation}
@@
 	\begin{equation}
-		|[\tens{\Pi}_n\A^*\vars2_0\vec{\varphi}_n](\vec{x})|< \mu - \sqrt{2(\op{E}(\var0_n)+\op{E}^*(\vars2_0\vec{\varphi}_n))}|\A^*|_{\ell^2\to L^\infty} \qquad \implies \qquad \var0^*(\vec{x})= 0.\label{eq: support equation}
+		|[\tens{\Pi}_n\A^*\vars2_0\vec{\varphi}_n](\vec{x})|< \vars2_0^{-1}\left(\mu - \sqrt{2(\op{E}(\var0_n)+\op{E}^*(\vars2_0\vec{\varphi}_n))}|\A^*|_{\ell^2\to L^\infty}\right) \qquad \implies \qquad \var0^*(\vec{x})= 0.\label{eq: support equation}
 	\end{equation}
@@
 	\subsection{Operator norms}\label{sec: smoothing operators}
-	For numerical implementation of \edit{Lasso}{\eqref{eq: Lasso energy}}, we are required to accurately estimate several operator norms of $\A$.
+	For numerical implementation of \eqref{eq: Lasso energy}, we are required to accurately estimate several operator norms of $\A$.
 For $\op{f}$ to be 1-Lipschitz we must divide by $|\A\A^*|_{\ell^2\to\ell^2}$, and the adaptivity described in Sections~\ref{sec: continuous lasso rate}, \ref{sec: bound continuous}, and~\ref{sec: support detection} requires the values of $|\A^*|_{\ell^2\to L^\infty}$, $|\A^*|_{\ell^2\to C^1}$, and $|\A^*|_{\ell^2\to C^2}$.
@@
 
-	\edit{
-	We now present explicit examples of the computations in both Lemmas~\ref{thm: norm bound smoothness} and~\ref{thm: norm bound L2} for the numerical results in Section~\ref{sec: numerics}.
-These examples are common in practical applications and we show the result of Theorem~5 in the main text to demonstrate that, while sometimes hard to compute by hand, the constants can estimated accurately in an efficient manner.
-	\\\bf{Theorem 5}
-		---- Original text moved to Theorem~\ref{thm: norm bound examples}. ----
-	\\\vspace{10pt}
-
-	\\The sharpest method for estimating these norms is of course to compute them.
-This is most cumbersome for Gaussian kernels, however, the sums converge faster than exponentially and so the computational burden should be very small.}{
 	The examples in Section~\ref{sec: numerics} require explicit computations of the expressions in Lemmas~\ref{thm: norm bound smoothness} and~\ref{thm: norm bound L2}.
-These computations are provided in Theorem~\ref{thm: norm bound examples}}
+These computations are provided in Theorem~\ref{thm: norm bound examples}
 
 	\section{Numerical examples}\label{sec: numerics}
-	We present four numerical \edit{Lasso }{}examples.
+	We present four numerical examples.
 The first two are in 1D to demonstrate the performance of different variants of Algorithm~\ref{alg: refining FISTA}, both with and without adaptivity.
@@
 
-	The next example is 2D reconstruction from Radon or X-ray data with wavelet-sparsity\edit{}{ and a robust data fidelity}.
+	The next example is 2D reconstruction from Radon or X-ray data with wavelet-sparsity and a robust data fidelity.
 As the forward operator is not sufficiently smooth, we must optimise in $\ell^1(\R)$ which naturally leads to the choice of a wavelet basis.
@@
 
-	In this section, the main aim is to minimise the exact \edit{Lasso }{}energy $\op{E}_0(\var0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
+	In this section, the main aim is to minimise the exact energy $\op{E}_0(\var0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
 Lemma~\ref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\op{E}_0(\var0_n)$ so it is this monotone estimate which is plotted.
 As $\op{E}(\var0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\op{E}_0(\var0_n) \approx \min_{n\leq N}\op{E}(\var0_n) + \min_{n'\leq n}\op{E}^*(\vars2_0\vec{\varphi}_{n'})$.
-Another quantity of interest is minimisation of the discrete \edit{Lasso }{}energy $\min_{n\leq N}\op{E}(\var0_n) + \min_{n'\leq n}\op{E}^*(\vars2\vec{\varphi}_{n'})$ which will be referred to as the `discrete gap'.
+Another quantity of interest is minimisation of the discrete energy $\min_{n\leq N}\op{E}(\var0_n) + \min_{n'\leq n}\op{E}^*(\vars2\vec{\varphi}_{n'})$ which will be referred to as the `discrete gap'.
 Note that for the adaptive schemes the discrete gap may not be monotonic as the discrete dual problem changes with $N$.
@@
 	\subsection{1D continuous LASSO}\label{sec: 1D Lasso examples}
-	In this example we choose $\F{U}=\C M([0,1])$\edit{}{, $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$} and $\A\colon \F{U}\to \R^{30}$ with either random Fourier kernels:
-	\begin{equation}
-		(\A\var0)_j = \int_0^1\cos(\vars3_jx)\var0(x), \qquad \vars3_j\sim \op{Uniform}[-100,100],\ j=1,2,\ldots,30,\ \mu =0.02, 
+	In this example we choose $\F{U}=\C M([0,1])$, $\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$ and $\A\colon \F{U}\to \R^{30}$ with either random Fourier kernels:
+	\begin{equation}
+		(\A\var0)_j = \int_0^1\cos(\vars3_jx)\diff\var0(x), \qquad \vars3_j\sim \op{Uniform}[-100,100],\ j=1,2,\ldots,30,\ \mu =0.02, 
 	\end{equation}
@@
 	\begin{equation}
-		(\A\var0)_j = (2\pi\sigma^2)^{-\frac12}\int_0^1\exp\left(-\frac{(x-(j-1)\Delta)^2}{2\sigma^2}\right)\var0(x), \quad \sigma=0.12,\ \Delta = \tfrac1{29},\ j=1,2,\ldots,30,\ \mu=0.06.
-	\end{equation}
-
-	Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.\edit{There are many methods designed to minimise the continuous LASSO energy in \eqref{eq: Lasso energy}}{For this choice of $\op{f}$, we call \eqref{eq: Lasso energy} the continuous LASSO problem, for which there are many numerical methods} (c.f.
-\cite{Bredies2013,Castro2016,Boyd2017,Catala2019}) however, most \edit{}{require} the solution of a non-convex problem.
+		(\A\var0)_j = (2\pi\sigma^2)^{-\frac12}\int_0^1\exp\left(-\frac{(x-(j-1)\Delta)^2}{2\sigma^2}\right)\diff\var0(x), \quad \sigma=0.12,\ \Delta = \tfrac1{29},\ j=1,2,\ldots,30,\ \mu=0.06.
+	\end{equation}
+
+	Several variants of FISTA are compared for these examples but the key alternative shown here is the CBP discretisation.
+For this choice of $\op{f}$, we call \eqref{eq: Lasso energy} the continuous LASSO problem, for which there are many numerical methods (c.f.
+\cite{Bredies2013,Castro2016,Boyd2017,Catala2019}) however, most require the solution of a non-convex problem.
 We have focused on CBP because it approximates $\var0^*$ through a convex discrete optimisation problem which is asymptotically exact in the limit $\meshsize\to0$.
@@
 
-	As shown in Section~\ref{sec: Lasso definition}, in 1D we have $\vars3_U = \vars3_{\op{E}} = 2$.
+	As shown in Section~\ref{sec: Lasso definition}, in 1D we have $\aU = \aE = 2$.
 The estimates given in \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\op{E}_0(\var0_n)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$.
@@
 Note briefly that this greedy strategy directly targets uncertainty, refinements also happen outside of the support of $u_n$ to guarantee that this is representative of $\var0^*$.
-Such refinement is necessary to avoid critical points of $\op{E}$ which are not global minimisers.
+Such refinement is necessary to avoid \edit{critical points}{discrete minimisers} of $\op{E}$ which are not global minimisers.
 
@@
 		\includegraphics[width=.86\textwidth]{lasso_convergence_short}
-		\caption{\edit{Discrete }{}Convergence plots for solving 1D problems with different algorithms.
+		\caption{Convergence plots for solving 1D problems with different algorithms.
 `Adaptive' methods use Algorithm~\ref{alg: refining FISTA} with fewer than 1024 pixels and the remaining methods use a uniform discretisation of 1024 pixels.}\label{fig: convergence with method}
@@
 		\item During the initial `slow' phase, adaptive and fixed discretisations appear to achieve very similar (discrete) convergence rates.
-The coarse-to-fine adaptivity is not slower than fixed discretisations in this regime.
+The coarse-to-fine adaptivity is not slower than fixed discretisations in this regime\edit{}{, consistent with \eqref{eq: slow exact FISTA}}.
 		\item Lemma~\ref{thm: practical refinement criteria} accurately predicts the $\frac1n$ rate of the adaptive methods, mirrored in the fixed discretisations.
@@
 
-	\subsection{2D \edit{wavelet Lasso}{robust sparse wavelet reconstruction}}\label{sec: wavelet examples}
+	\subsection{2D robust sparse wavelet reconstruction}\label{sec: wavelet examples}
 	In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{X}^I_i$ where 
@@
 	\begin{equation}
-		\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[100]} |\F{X}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[100]} \int_{\F{X}^I_i}1d\vec{x}}= \sqrt{\sum_{I\in[50]}\max_{i\in[100]}\ (\A\1)_{i,I}}\;.
+		\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[100]} |\F{X}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[100]} \int_{\F{X}^I_i}1\diff\vec{x}}= \sqrt{\sum_{I\in[50]}\max_{i\in[100]}\ (\A\1)_{i,I}}\;.
 	\end{equation}
 	$\A$ is not smooth, therefore we can't bound $|\A^*|_{C^k}$ for $k>0$, and so we must look to minimise over $\ell^1$ rather than $L^1$.
-The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the \edit{Lasso}{} form \edit{}{of \eqref{eq: Lasso energy}}:
-	\begin{equation}
-		\min_{\var0\in \F{U}} \edit{\tfrac12\norm{\A\var0-\data}_{\ell^2}^2}{\op{f}(\A\var0-\data)} + \mu \norm{\tens{W}^{-1}\var0}_{\ell^1} = \min_{\hat{\var0}\in\ell^1(\R)} \edit{\tfrac12\norm{\A\tens{W}\hat{\var0}-\data}_{\ell^2}^2}{\op{f}(\A\tens{W}\hat{\var0}-\data)} + \mu \norm{\hat{\var0}}_{\ell^1}.
+The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the  form of \eqref{eq: Lasso energy}:
+	\begin{equation}
+		\min_{\var0\in \F{U}} \op{f}(\A\var0-\data) + \mu \norm{\tens{W}^{-1}\var0}_{\ell^1} = \min_{\hat{\var0}\in\ell^1(\R)} \op{f}(\A\tens{W}\hat{\var0}-\data) + \mu \norm{\hat{\var0}}_{\ell^1}.
 	\end{equation}
 	The minimisers are related by $\var0^* = \tens{W}\hat{\var0}^*$ and, for wavelet bases, $\tens{W}$ is orthonormal so $\norm{\A\tens{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$. 
-	\edit{}{ In this example we consider the smoothed robust fidelity \cite{Rosset2007}
+	 In this example we consider the smoothed robust fidelity \cite{Rosset2007}
 		\begin{equation}
@@
 		\end{equation}
-	}	
 	From Section~\ref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\tens{W}^\top \A^*\vec{\varphi}_n]_j|$ for all $j\notin J_n$.
@@
 	\paragraph{Continuous gradient estimate}
-	In Section~\ref{sec: 1D Lasso examples} we used the continuous gap as a measure for convergence, for wavelets we will use the continuous \edit{gradient}{subdifferential}.
-With the tree structure we can easily adapt the results of Section~\ref{sec: Lasso gap and gradient} to estimate \edit{gradients}{subdifferentials} (or function gaps).
+	In Section~\ref{sec: 1D Lasso examples} we used the continuous gap as a measure for convergence, for wavelets we will use the continuous subdifferential.
+With the tree structure we can easily adapt the results of Section~\ref{sec: Lasso gap and gradient} to estimate subdifferentials (or function gaps).
 In particular,
@@
 	We consider two phantoms where the ground-truth is either a binary disc or the Shepp-Logan phantom.
-\edit{No noise is added to the Shepp-Logan data but 5\% Gaussian white noise is added to the disc data.}{Both examples are corrupted with \SI{2}{\percent} Laplace distributed noise.} This is visualised in Fig.~\ref{fig: haar data}.
+Both examples are corrupted with \SI{2}{\percent} Laplace distributed noise.
+This is visualised in Fig.~\ref{fig: haar data}.
 All optimisations shown are spatially adaptive using Haar wavelets and initialised with $\F{U}^0= \{x\mapsto c\st c\in\F R\}$.
@@
 	for all $j$ and $n$ (i.e. so that the continuous gradient is less than 10 times the discrete gradient).
-	\edit{}{We do not expect wavelet regularisation to have state-of-the-art performance in the examples of Fig.~\ref{fig: haar data}.
+	We do not expect wavelet regularisation to have state-of-the-art performance in the examples of Fig.~\ref{fig: haar data}.
 What they demonstrate is the preference Haar wavelets have to align large discontinuities with a coarse grid, even when the discretisation is allowed to be as fine as necessary.
@@
 In limited data scenarios, wavelet regularisation automatically selects a local `resolution' which reflects the quality of data.
-Particularly in the Shepp-Logan reconstruction, we see that the outer ring is detected with a finer precision than the dark interior ellipses.}
+Particularly in the Shepp-Logan reconstruction, we see that the outer ring is detected with a finer precision than the dark interior ellipses.
 
@@
 In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower.
-\edit{}{Interestingly, in both examples the $a=20$ variant uses half as many wavelets as the Greedy variant, and therefore converges slightly faster in time.
-}
+Interestingly, in both examples the $a=20$ variant uses half as many wavelets as the Greedy variant, and therefore converges slightly faster in time.
 
@@
 		\includegraphics[width=.85\textwidth]{haar_data}
-		\caption{Phantoms\edit{ and}{,} data \edit{used }{and reconstructions }for wavelet-sparse tomography optimisation.
-\edit{The Shepp-Logan data is exact but the data for the disc-phantom has}{Both examples are corrupted with} \SI{2}{\percent}\ \edit{Gaussian white}{Laplace distributed} noise.
-}\label{fig: haar data}
+		\caption{Phantoms, data and reconstructions for wavelet-sparse tomography optimisation. Both examples are corrupted with \SI{2}{\percent}\ Laplace distributed noise. }\label{fig: haar data}
 
@@
 		\includegraphics[width=.85\textwidth]{haar_convergence_short}
-		\caption{\edit{Discrete }{}Convergence of different implementations of Algorithm~\ref{alg: refining FISTA} with an unlimited number of pixels for sparse wavelet optimisation.}\label{fig: haar convergence}
+		\caption{Convergence of different implementations of Algorithm~\ref{alg: refining FISTA} with an unlimited number of pixels for sparse wavelet optimisation.}\label{fig: haar convergence}
 
@@
 Readers are directed to the references \cite{Sage2015,Sage2019,Schermelleh2019} for further details.
-The LASSO formulation \edit{}{($\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$) }has previously been shown to be effective in the context of STORM \cite{Huang2017,Denoyelle2019}.
+The LASSO formulation ($\op{f}(\cdot)=\frac12\norm{\cdot}_{\ell^2}^2$) has previously been shown to be effective in the context of STORM \cite{Huang2017,Denoyelle2019}.
 
@@
 	\begin{equation}
-		(\A\var0)_{i} = (2\pi\sigma^2)^{-1}\int_{[0,6.4]^2} \exp\left(-\frac{1}{2\sigma^2}\left|\vec{x}- \Delta\begin{pmatrix}i_1+\tfrac12 & i_2+\tfrac12\end{pmatrix}^\top \right|^2\right)\var0(\vec{x})\,d\vec{x}, \qquad \sigma=0.2,\ \Delta=0.1
+		(\A\var0)_{i} = (2\pi\sigma^2)^{-1}\int_{[0,6.4]^2} \exp\left(-\frac{1}{2\sigma^2}\left|\vec{x}- \Delta\begin{pmatrix}i_1+\tfrac12 & i_2+\tfrac12\end{pmatrix}^\top \right|^2\right)\var0(\vec{x})\diff\vec{x}, \qquad \sigma=0.2,\ \Delta=0.1
 	\end{equation}
@@
 	This section contains all of the statements and proofs of the results contained in Section~\ref{sec: FISTA convergence}.
-\edit{}{Recall that the subsets $\F{U}^n\subset\F H$ satisfy \eqref{eq: refining subspace definition}.}
+Recall that the subsets $\F{U}^n\subset\F H$ satisfy \eqref{eq: refining subspace definition}.
 
@@
 	\begin{proof}
-		Modifying \cite[\edit{Theorem 2}{Thm 3.2}]{Chambolle2015}, for $n\geq1$ we apply Lemma~\ref{thm: descent lemma} with $\bar{\var0} = \bar{\var0}_{n-1}$ and $\var2 = (1-\frac{1}{t_{n}})\var0_{n-1} + \frac{1}{t_{n}}\var2_n$.
-\edit{}{By \eqref{eq: refining subspace definition}, $\var0_{n-1}\in\F{U}^n$ is convex so $\var2\in \F{U}^n$.
-}This gives
+		Modifying \cite[Thm 3.2]{Chambolle2015}, for $n\geq1$ we apply Lemma~\ref{thm: descent lemma} with $\bar{\var0} = \bar{\var0}_{n-1}$ and $\var2 = (1-\frac{1}{t_{n}})\var0_{n-1} + \frac{1}{t_{n}}\var2_n$.
+By \eqref{eq: refining subspace definition}, $\var0_{n-1}\in\F{U}^n$ is convex so $\var2\in \F{U}^n$.
+This gives
 		\begin{equation}
@@
 		\end{equation}
-		\edit{}{Multiplying through by $t_n^2$ gives the desired inequality.}
+		Multiplying through by $t_n^2$ gives the desired inequality.
 		\qed\end{proof}
@@
 		Theorem~\ref{app:thm: mini FISTA convergence} is just a summation of \eqref{app:eq: one-step FISTA} over all $n=1,\ldots,N$.
-To see this: first add and subtract $\edit{\op{E}(\var0^*)}{\Emin}$ to each term on the left-hand side to convert $\op{E}$ to $\op{E}_0$, then move $\op{E}_0(\var2_n)$ to the right-hand side.
+To see this: first add and subtract $\Emin$ to each term on the left-hand side to convert $\op{E}$ to $\op{E}_0$, then move $\op{E}_0(\var2_n)$ to the right-hand side.
 Now \eqref{app:eq: one-step FISTA} becomes
@@
 			+ \sum_{k=1}^K\sum_{n=n_{k-1}}^{n_k-1}t_n\op{E}_0(\tilde{\var2}_{k-1}) 
-			+ \IP{\var1_{n_k-1}}{\tilde{\var2}_k-\tilde{\var2}_{k+1}}.
+			+ \IP{\var1_{n_k-1}}{\tilde{\var2}_{k-1}-\tilde{\var2}_k}.
 		\end{equation}
@@
 			\\&\hspace{70pt}+ \sum_{k=1}^K \frac{n_k^2-n_{k-1}^2}{2}\op{E}_0(\tilde{\var2}_{k-1}) + \IP{\var1_{n_k-1}}{\tilde{\var2}_k-\tilde{\var2}_{k+1}}
-			\\& \leq C + \frac{\norm{\tilde{\var2}_K}^2}{2} + \frac{(N+1)^2}{2}\op{E}_0(\tilde{\var2}_K) \notag
-			\\&\hspace{40pt}+\sum_{k=1}^K \frac{n_k^2}{2}\op{E}_0(\tilde{\var2}_{k-1}) + \IP{\var1_{n_k-1}-\tilde{\var2}_{k-1}+\tilde{\var2}_{k-1}}{\tilde{\var2}_k-\tilde{\var2}_{k+1}}.
-		\end{align}
-		The inductive step now depends on the value of $\vars3_U$.
+			\\& \leq C + \frac{\norm{\tilde{\var2}_K}^2}{2} + \frac{n_{K+1}^2}{2}\op{E}_0(\tilde{\var2}_K) \notag
+			\\&\hspace{40pt}+\sum_{k=1}^K \frac{n_k^2}{2}\op{E}_0(\tilde{\var2}_{k-1}) + \IP{\var1_{n_k-1}-\tilde{\var2}_{k-1}+\tilde{\var2}_{k-1}}{{\tilde{\var2}_{k-1}-\tilde{\var2}_k}}.
+		\end{align}
+		The inductive step now depends on the value of $\aU$.
 		\begin{description}
-			\item[Case $\vars3_U>1$:] We simplify the inequality
-			\begin{align}
-				t_N^2\op{E}_0(\var0_N) + \tfrac12\norm{\var1_N-\tilde{\var2}_K}^2 &\lesssim \vars3_U^{2K} + (N+1)^2\vars3_{\op{E}}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\op{E}}^{-k} + \vars3_U^{k}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}} + \vars3_U^{2k}
-				\\&\leq C_1\left[\vars3_U^{2K+2} + \sum_{k=1}^{K}\vars3_U^{2k} + \vars3_U^{k}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\right]
-			\end{align}
-			for some $C_1>C$. Choose $C_2\geq \norm{\var1_{n_1-1}-\tilde{\var2}_{1-1}}\vars3_U^{-1}$ such that 
-			\begin{equation}
-				\frac12C_2^2 \geq \frac{C_1}{\vars3_U^2-1}(C_2+\vars3_U^2).
-			\end{equation}
-			Assume $\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\leq C_2\vars3_U^k$ for $1\leq k\leq K$ (trivially true for $K=1$), then for $N=n_{K+1}-1$ we have 
-			\begin{align}
-				\tfrac12\norm{\var1_{n_{K+1}-1}-\tilde{\var2}_K}^2 &\leq C_1\left[\vars3_U^{2K+2} + \sum_{k=1}^{K}\vars3_U^{2k} + \vars3_U^{k}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\right]
-				\\&\leq C_1\left[\vars3_U^{2K+2} + (1+C_2)\frac{\vars3_U^{2K+2}}{\vars3_U^2-1}\right]
-				\\&\leq \frac{C_1\vars3_U^{2K+2}}{\vars3_U^2-1}\left(\vars3_U^2+C_2\right) \leq \tfrac12(C_2\vars3_U^{K+1})^2.
-			\end{align}
-
-			\item[Case $\vars3_U=1$:] Denote $\vars4_k = \norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}$ and note that $\norm{\tilde{\var2}_{k-1}} \leq \norm{\tilde{\var2}_{0}} + \sum_0^\infty \vars4_k\lesssim 1$.
+			\item[Case $\aU>1$:] We simplify the inequality
+			\begin{align}
+				t_N^2\op{E}_0(\var0_N) + \tfrac12\norm{\var1_N-\tilde{\var2}_K}^2 &\lesssim \aU^{2K} + n_{K+1}^2\aE^{-K} + \sum_{k=1}^{K}n_k^2\aE^{-k} + \aU^{k}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}} + \aU^{2k}
+				\\&\leq C_1\left[\aU^{2K+2} + \sum_{k=1}^{K}\aU^{2k} + \aU^{k}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\right]
+			\end{align}
+			for some $C_1>C$. Choose $C_2\geq \norm{\var1_{n_1-1}-\tilde{\var2}_{1-1}}\aU^{-1}$ such that 
+			\begin{equation}
+				\frac12C_2^2 \geq \frac{C_1}{\aU^2-1}(C_2+\aU^2).
+			\end{equation}
+			Assume $\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\leq C_2\aU^k$ for $1\leq k\leq K$ (trivially true for $K=1$), then for $N=n_{K+1}-1$ we have 
+			\begin{align}
+				\tfrac12\norm{\var1_{n_{K+1}-1}-\tilde{\var2}_K}^2 &\leq C_1\left[\aU^{2K+2} + \sum_{k=1}^{K}\aU^{2k} + \aU^{k}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\right]
+				\\&\leq C_1\left[\aU^{2K+2} + (1+C_2)\frac{\aU^{2K+2}}{\aU^2-1}\right]
+				\\&\leq \frac{C_1\aU^{2K+2}}{\aU^2-1}\left(\aU^2+C_2\right) \leq \tfrac12(C_2\aU^{K+1})^2.
+			\end{align}
+
+			\item[Case $\aU=1$:] Denote $\vars4_k = \norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}$ and note that $\norm{\tilde{\var2}_{k-1}} \leq \norm{\tilde{\var2}_{0}} + \sum_0^\infty \vars4_k\lesssim 1$.
 We therefore bound
 			\begin{align}
-				t_N^2\op{E}_0(\var0_N) + \tfrac12\norm{\var1_N-\tilde{\var2}_K}^2 &\lesssim 1 + (N+1)^2\vars3_{\op{E}}^{-K} + \sum_{k=1}^{K}n_k^2\vars3_{\op{E}}^{-k} + (\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}} + 1)b_k
-				\\&\leq C_1\left[1 + \sum_{k=1}^{K}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\vars4_k\right]
+				t_N^2\op{E}_0(\var0_N) + \tfrac12\norm{\var1_N-\tilde{\var2}_K}^2 &\lesssim 1 + n_{K+1}^2\aE^{-K} + \sum_{k=1}^{K}n_k^2\aE^{-k} + (\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}} + 1)b_k
+				\\&\leq C_1\left[1 + \sum_{k=1}^{K}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\vars4_{k-1}\right]
 			\end{align}
@@
 			\begin{equation}
-				\frac12C_2^2 \geq C_1\left(1+C_2\sum_1^\infty\vars4_k\right).
+				\frac12C_2^2 \geq C_1\left(1+C_2\sum_0^\infty\vars4_k\right).
 			\end{equation}
@@
 			\begin{equation}
-				\tfrac12\norm{\var1_{n_{K+1}-1}-\tilde{\var2}_K}^2 \leq C_1\left[1 + \sum_{k=1}^{K}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\vars4_k\right]
-				\leq C_1\left(1+C_2\sum_1^\infty\vars4_k\right) \leq \frac{C_2^2}{2}
+				\tfrac12\norm{\var1_{n_{K+1}-1}-\tilde{\var2}_K}^2 \leq C_1\left[1 + \sum_{k=1}^{K}\norm{\var1_{n_k-1}-\tilde{\var2}_{k-1}}\vars4_{k-1}\right]
+				\leq C_1\left(1+C_2\sum_0^\infty\vars4_k\right) \leq \frac{C_2^2}{2}
 			\end{equation}
@@
 		\begin{equation}
-			t_N^2\op{E}_0(\var0_N) \leq \frac{C_2^2}{2}\vars3_U^{2K}
+			t_N^2\op{E}_0(\var0_N) \leq \frac{C_2^2}{2}\aU^{2K}
 		\end{equation}
@@
 		\begin{equation}
-			\log N^2 \geq \log C + K\left(\log \vars3_{\op{E}} + \log \vars3_U^2\right)
+			\log N^2 \geq \log C + K\left(\log \aE + \log \aU^2\right)
 		\end{equation}
@@
 		\begin{equation}
-			\vars3_U^{2K} = \exp(K\log \vars3_U^2)
-			\leq \exp\left(\log N^2\frac{\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2} - \frac{\log C\log \vars3_U^2}{\log \vars3_{\op{E}} + \log \vars3_U^2}\right)
+			\aU^{2K} = \exp(K\log \aU^2)
+			\leq \exp\left(\log N^2\frac{\log \aU^2}{\log \aE + \log \aU^2} - \frac{\log C\log \aU^2}{\log \aE + \log \aU^2}\right)
 		\end{equation}
@@
 		\begin{equation}
-			n_k^2\lesssim \splitln{(\vars3_{\op{E}}\vars3_U^2)^k}{\vars3_U>1}{k^{-2}\vars3_{\op{E}}^k}{\vars3_U=1}, \qquad \norm{\tilde{\var2}_k}\lesssim \vars3_U^{k}, \qquad \text{ and } \op{E}_0(\tilde{\var2}_k)\lesssim \vars3_{\op{E}}^{-k}
-		\end{equation}
-		and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty$ when $\vars3_U=1$. The only one which is not directly assumed is easily verified,
-		\begin{equation}
-			\op{E}_0(\tilde{\var2}_k) = \min_{\var0\in\F{U}^{n_k}}\op{E}_0(\var0) \leq\op{E}_0(\var0_{n_k-1}) \lesssim \vars3_{\op{E}}^{-k}.
+			n_k^2\lesssim \splitln{(\aE\aU^2)^k}{\aU>1}{k^{-2}\aE^k}{\aU=1}, \qquad \norm{\tilde{\var2}_k}\lesssim \aU^{k}, \qquad \text{ and } \op{E}_0(\tilde{\var2}_k)\lesssim \aE^{-k}
+		\end{equation}
+		and $\sum_{k=1}^\infty\norm{\tilde{\var2}_k-\tilde{\var2}_{k+1}}<\infty$ when $\aU=1$. The only one which is not directly assumed is easily verified,
+		\begin{equation}
+			\op{E}_0(\tilde{\var2}_k) = \min_{\var0\in\F{U}^{n_k}}\op{E}_0(\var0) \leq\op{E}_0(\var0_{n_k-1}) \lesssim \aE^{-k}.
 		\end{equation}
@@
 		\begin{equation}
-			\op{E}_0(\var0_N) \lesssim \frac{\vars3_U^{2K}}{t_N^2} \lesssim \frac{\vars3_U^{2K}}{N^2}.
-		\end{equation}
-		In the case $\vars3_U=1$, this is already the optimal rate and therefore sharp.
-If this were sharp for general $\vars3_U$ and $\op{E}$, then we gain nothing by refining early (increasing $K$ for fixed $N$) however, we can at least guarantee that refining early does not lose the optimal rate.
-
-		If we fix $N^2\lesssim (\vars3_{\op{E}}\vars3_U^2)^k$, then
-		\begin{equation}
-			\min_{n\leq N} \op{E}_0(\var0_n)\lesssim \splitln{\vars3_{\op{E}}^{-k}}{N>n_k}{ \frac{\vars3_U^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\vars3_U^{2k},\vars3_U^{2k}) \lesssim N^{-2(1-\kappa)}
+			\op{E}_0(\var0_N) \lesssim \frac{\aU^{2K}}{t_N^2} \lesssim \frac{\aU^{2K}}{N^2}.
+		\end{equation}
+		In the case $\aU=1$, this is already the optimal rate and therefore sharp.
+If this were sharp for general $\aU$ and $\op{E}$, then we gain nothing by refining early (increasing $K$ for fixed $N$) however, we can at least guarantee that refining early does not lose the optimal rate.
+
+		If we fix $N^2\lesssim (\aE\aU^2)^k$, then
+		\begin{equation}
+			\min_{n\leq N} \op{E}_0(\var0_n)\lesssim \splitln{\aE^{-k}}{N>n_k}{ \frac{\aU^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\aU^{2k},\aU^{2k}) \lesssim N^{-2(1-\kappa)}
 		\end{equation}
@@
 		The proof is simply to justify that the conditions of Theorem~\ref{app:thm: stronger exponential FISTA convergence} are met for all refinement criteria described here.
-$\norm{\tilde{\var2}_k}\lesssim \vars3_U^k$ is enforced at every step and condition (2) guarantees the back-stop condition on $n_k$.
-
-		To complete the requirements of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, we first need to show inductively that $\op{E}_0(\tilde{\var2}_{k-1}) \leq C\vars3_{\op{E}}^{-k}$, then it follows that $\op{E}_0(\var0_{n_k-1})\leq C\vars3_{\op{E}}^{-k}$.
+$\norm{\tilde{\var2}_k}\lesssim \aU^k$ is enforced at every step and condition (2) guarantees the back-stop condition on $n_k$.
+
+		To complete the requirements of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, we first need to show inductively that $\op{E}_0(\tilde{\var2}_{k-1}) \leq C\aE^{-k}$, then it follows that $\op{E}_0(\var0_{n_k-1})\leq C\aE^{-k}$.
 To be explicit, when $\op{E}$ has bounded sublevel sets, assume that the bound for $\{\var0\in\F H\st \op{E}(\var0)\leq \op{E}(\var0_0)\}$ is $R>0$.
@@
 		For (2) and (5) the decay of $\op{E}_0(\tilde{\var2}_{k-1})$ is already assumed but otherwise we need to perform the formal induction.
-Assume $\op{E}_0(\tilde{\var2}_{k-1}) \leq C\vars3_{\op{E}}^{1-k}$, then for each remaining adaptive criterion:
+Assume $\op{E}_0(\tilde{\var2}_{k-1}) \leq C\aE^{1-k}$, then for each remaining adaptive criterion:
 		\begin{itemize}
-			\item[(1)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\var0_{k})\leq\vars1 \vars3_{\op{E}}^{-k}$ by definition, the induction holds if $C\geq \vars1$.
-			\item[(3)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\var0_{k})\leq\frac{\vars1}{1-\vars1}\op{E}_0(\tilde{\var2}_{k-1})$, the induction holds if $\vars1\leq \frac{1}{1+\vars3_{\op{E}}}$.
-			\item[(4)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\var0_{k}) \leq \IP{\edit{\partial\op{E}(\var0_{k})}{\var1}}{\var0_{n_k-1}-\var0^*} \leq 2R\vars1\vars3_{\op{E}}^{-k}$\edit{}{ for each $\var1\in\partial\op{E}(\var0_{k})$}, the induction holds for $C\geq 2R\vars1$.
+			\item[(1)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\var0_{k})\leq\vars1 \aE^{-k}$ by definition, the induction holds if $C\geq \vars1$.
+			\item[(3)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\var0_{k})\leq\frac{\vars1}{1-\vars1}\op{E}_0(\tilde{\var2}_{k-1})$, the induction holds if $\vars1\leq \frac{1}{1+\aE}$.
+			\item[(4)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\var0_{k}) \leq \IP{\var1}{\var0_{n_k-1}-\var0^*} \leq 2R\vars1\aE^{-k}$ for each $\var1\in\partial\op{E}(\var0_{k})$, the induction holds for $C\geq 2R\vars1$.
 		\end{itemize}
 		In each case, with $C$ sufficiently large, the induction holds.
-Now we can return to the precise condition of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, $\op{E}_0(\var0_{n_k-1}) \leq C'\vars3_{\op{E}}^{-k}$.
+Now we can return to the precise condition of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, $\op{E}_0(\var0_{n_k-1}) \leq C'\aE^{-k}$.
 Assume true for $k-1$.
@@
 		\begin{itemize}
-			\item[(1)] $\op{E}_0(\var0_{k})\leq\vars1 \vars3_{\op{E}}^{-k}$ is by definition.
-			\item[(2)] $\op{E}_0(\var0_{k})\leq\vars1 \vars3_{\op{E}}^{-k} + \op{E}_0(\tilde{\var2}_{k-1})$ requires $C'\geq \vars1+\vars3_{\op{E}}C$.
+			\item[(1)] $\op{E}_0(\var0_{k})\leq\vars1 \aE^{-k}$ is by definition.
+			\item[(2)] $\op{E}_0(\var0_{k})\leq\vars1 \aE^{-k} + \op{E}_0(\tilde{\var2}_{k-1})$ requires $C'\geq \vars1+\aE C$.
 			\item[(3)] $\op{E}_0(\var0_{k})\leq\frac{\vars1}{1-\vars1}\op{E}_0(\tilde{\var2}_{k-1})$ requires $C'\geq \frac{\vars1}{1-\vars1}C$.
-			\item[(4)] $\op{E}_0(\var0_{k}) \leq 2R\vars1\vars3_{\op{E}}^{-k}$, the induction holds for large $C'$.
-			\item[(5)] $\op{E}_0(\var0_{k})\leq 2R\vars1\vars3_{\op{E}}^{-k} + \op{E}_0(\tilde{\var2}_{k-1})$, the induction holds for large $C'\geq 2R\vars1+C$.
+			\item[(4)] $\op{E}_0(\var0_{k}) \leq 2R\vars1\aE^{-k}$, the induction holds for large $C'$.
+			\item[(5)] $\op{E}_0(\var0_{k})\leq 2R\vars1\aE^{-k} + \op{E}_0(\tilde{\var2}_{k-1})$, the induction holds for large $C'\geq 2R\vars1+C$.
 		\end{itemize}
@@
 	\section{Proof of \texorpdfstring{Theorem~\ref{thm: generic a_U and a_E}}{rates for general finite element spaces}}\label{app: generic a_U and a_E}
-	The proof of Theorem~\ref{thm: generic a_U and a_E} is the result of the following three lemmas.
-The first, Lemma~\ref{app:thm: generic a_U bound}, is a general quantification of the equivalence between $L^q$ and $L^2$ norms on finite dimensional sub-spaces.
-A special case occurs when $q=1$ because the dual norm is a supremum rather than an integral.
-In Lemma~\ref{app:thm: specific a_U bound}, this locality is exploited by finite element spaces, which we assumed had a basis with local support.
-Lemma~\ref{app:thm: generic a_E bound} then performs the computations for the $\vars3_{\op{E}}$ constant depending on the smoothness properties of $\op{E}$.
-
-	\begin{lemma}\label{app:thm: generic a_U bound}
-		Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
-Let $\F{U}\subset \edit{\F{U}\cap}{}\F H$ be a finite dimensional subspace with orthonormal basis $\{e_j\st j=1,\ldots,\op{dim}(\F{U})\}\subset\F{U}$ and orthogonal projection $\tens{\Pi}\colon\F H\to\F{U}$.
-If these conditions hold:
-		\begin{itemize}
-			\item if $q\geq 2$, then $$\norm{\tens{\Pi}\var2} \lesssim \Norm{\var2}, $$
-			\item otherwise, if $e_j\in \F{U}^*$, then
-			\begin{equation}
-				\norm{\tens{\Pi}\var2} \leq \sqrt{\op{dim}(\F{U})}\max_{j\leq \op{dim}(\F{U})}\Norm{e_j}_*\Norm{\var2},
-			\end{equation}
-			\item otherwise, if $e_j\in L^\infty(\Domain)$ and $ |\{j:e_j(\vec{x})\neq 0\}|\leq C$ for almost all $\vec{x}\in\Domain$, then
-			\begin{equation}
-				\norm{\tens{\Pi}\var2} \lesssim \sqrt C\max_{j\leq\op{dim}(\F{U})}\norm{e_j}_{\infty}\Norm{\var2}
-			\end{equation}
-		\end{itemize}
-		uniformly for all $\var2\in \F H$.
+	\edit[2]{}{First we recall the setting of Definition~\ref{def: finite element space}, fix: $p\geq0$, $q\in[1,\infty]$, $\meshsize\in(0,1)$, $N\in\F N$, connected and bounded domain $\Domain\subset\R^d$, and $\var0^*\in\argmin_{\var0\in\F U}\op{E}(\var0)$.
+We assume that $\F H=L^2(\Domain)$, $\norm{\cdot}_q\lesssim\Norm\cdot$, and there exist spaces $(\tilde{\F U}^k)_{k\in\F N}$ with $\tilde{\F{U}}^k\subset \F{U}\cap L^\infty(\Domain)$ containing a sequence $(\tilde{\var2}_k\in \tilde{\F U}^k)_{k\in\F N}$ such that $\Norm{\tilde{\var2}_k - \var0^*} \lesssim \meshsize^{kp}$.
+Furthermore, there exists constant $c_\alpha>0$ and finite partitions $\F M^k=\{\domain_1^k,\domain_2^k,\ldots\}$ of $\Domain$ such that:
+	\begin{equation}\label{eq: decomposition property}
+		\forall (\tilde{\var0},\domain)\in\tilde{\F{U}}^k\times\F M^k,\quad \exists (\var0,\alpha,\vec\beta)\in\tilde{\F U}^0\times\R^{d\times d}\times\R^d \quad \text{such that}\quad \op{det}(\alpha)\geq c_\alpha\meshsize^{kd} \quad\text{and}\quad \forall\vec{x}\in\Domain,\ \var0(\vec x) = \splitln{\tilde{\var0}(\alpha \vec{x}+\vec\beta)\qquad}{\text{if }\alpha \vec{x}+\vec\beta\in\domain,}{0}{\text{else.}}
+	\end{equation}
+
+	In this section, these assumptions will be summarised simply by saying that $\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space}.
+	}
+	\edit[2]{The proof of Theorem~\ref{thm: generic a_U and a_E} is}{We prove Theorem~\ref{thm: generic a_U and a_E} as a consequence of Lemma~\ref{thm: pq to p'q'}, namely we compute exponents $p',q'$ with $\aU=\meshsize^{-q'}$ and $\aE=\meshsize^{-p'}$.
+These values are computed as} the result of the following three lemmas.
+The first, Lemma~\ref{app:thm: generic a_U bound}, is a quantification of the equivalence between $L^q$ and $L^2$ norms on \edit[2]{finite dimensional}{general} sub-spaces.
+\edit[2]{A special case occurs when $q=1$ because the dual norm is a supremum rather than an integral.
+In Lemma~\ref{app:thm: specific a_U bound}, this locality is exploited by finite element spaces, which we assumed had a basis with local support.}{Lemma~\ref{app:thm: specific a_U bound} applies this result to finite-element spaces to compute the value of $q'$.
+Finally, }
+	Lemma~\ref{app:thm: generic a_E bound} then performs the computations for \edit[2]{the $\aE$ constant}{$p'$} depending on the smoothness properties of $\op{E}$.
+
+	\begin{lemma}[Equivalence of norms for fixed $k$]\label{app:thm: generic a_U bound}
+		Suppose $\F H= L^2(\Domain)$ for some \edit{compact}{connected, bounded} domain $\Domain\subset\R^d$ and $\norm\cdot_q\edit{\lesssim}{\leq C} \Norm\cdot$ for some $q\in[1,\infty]$\edit{}{, $C>0$}. 
+		\edit[2]{Let $\F{U}\subset \F H$ be a finite dimensional subspace with orthonormal basis $\{\var0_j\st j=1,\ldots,\op{dim}(\tilde{\F{U}})\}$ and orthogonal projection $\tens{\Pi}\colon\F H\to\F{U}$.
+If these conditions hold:}{For any linear subspace $\tilde{\F{U}}\subset \F{U}\cap L^\infty(\Domain)$ and $\tilde{\var2}\in\tilde{\F U}$,}
+
+		\edit[2]{\begin{enumerate}
+			\item If $q\geq 2$, then $$\edit{\norm{\tens{\Pi}\var2} \lesssim \Norm{\var2}}{\norm{\tilde{\var2}}\leq \sqrt{|\Domain|}\norm{\tilde{\var2}}_q \lesssim \Norm{\tilde{\var2}}}, $$
+			\item otherwise, if $\var0_j\in \F{U}^*$, then
+			$$\norm{\tens{\Pi}\var2} \leq \sqrt{\op{dim}(\tilde{\F{U}})}\max_{j\leq \op{dim}(\tilde{\F{U}})}\Norm{\var0_j}_*\Norm{\var2}\quad\Norm{\var0_j}= \sup_{\var0\in\F{U}\cap\F{H}}\frac{\IP{\var0_j}{\var0}}{\norm{\var0}},$$
+			\item otherwise, if $\var0_j\in L^\infty(\Domain)$ and $ |\{j:\var0_j(\vec{x})\neq 0\}|\leq N$ for almost every $\vec{x}\in\Domain$, then
+			$$ \norm{\tens{\Pi}\var2} \leq |\Domain|\sqrt N\max_{j\leq\op{dim}(\tilde{\F{U}})}\norm{\var0_j}_\infty\norm{\var2}_q $$
+		\end{enumerate}}
+		{\begin{equation}
+			\norm{\tilde{\var2}}\leq \sup_{\var0,\tilde{\var0}\in\tilde{\F{U}}}\frac{\IP{\var0}{\tilde{\var0}}}{\norm{\var0}\, \Norm{\tilde{\var0}}}\Norm{\tilde{\var2}} \quad\text{where}\quad \sup_{\var0,\tilde{\var0}\in\tilde{\F{U}}}\frac{\IP{\var0}{\tilde{\var0}}}{\norm{\var0}\, \Norm{\tilde{\var0}}} \leq C^{-1}\splitln{|\Domain|^{\frac12-\frac1q}}{\text{ if }q\geq 2\text{, otherwise}}{|\Domain|^{1-\frac1q}\sup_{\var0\in\tilde{\F{U}}}\norm{\var0}_\infty/\norm{\var0}\qquad}{\text{ if }q\in[1,2).}
+		\end{equation}}
+		\edit[2]{uniformly for all $\var2\in\F H$.}{}
 	\end{lemma}
 	\begin{proof}	
-		The first statement for $q\geq 2$ is from H\"older's inequality combined with the fact that compact domains have finite volume,
+		\edit[2]{The first statement for $q\geq 2$ is from H\"older's inequality combined with the fact that compact domains have finite volume,
 		\begin{equation}
@@
 		\end{equation}
-		therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\F{U}$. Switching to the given basis, for $\var0 = \sum_{j=1}^{\op{dim}(\F{U})} r_je_j$ we have
-		\begin{align}
-			\norm{\var0}^2 &= \sum_{j=1}^{\op{dim}(\F{U})} r_j^2 = \norm{\vec{r}}_{\ell^2}^2,
-			\\\Norm{\var0}_*&\leq \sum_{j=1}^{\op{dim}(\F{U})} |r_j|\Norm{e_j}_* \leq \max_{j\leq\op{dim}(\F{U})} \Norm{e_j}_*\norm{\vec{r}}_{\ell^1},
-			\\\implies \frac{\Norm{\var0}_*}{\norm{\var0}} &\leq \max_{j\leq \op{dim}(\F{U})}\Norm{e_j}_*\frac{\norm{\vec{r}}_{\ell^1}}{\norm{\vec{r}}_{\ell^2}} \leq \max_{j\leq \op{dim}(\F{U})}\Norm{e_j}_*\sqrt{\op{dim}(\F{U})}.
+		therefore it is sufficient to bound $\frac{\Norm\cdot_*}{\norm\cdot}$ on the subspace $\tilde{\F{U}}$.
+Switching to the given basis, for $\var0 = \sum_{j=1}^{\op{dim}(\tilde{\F{U}})} r_j\var0_j$ we have
+		\begin{align}
+			\norm{\var0}^2 &= \sum_{j=1}^{\op{dim}(\tilde{\F{U}})} r_j^2 = \norm{\vec{r}}_{\ell^2}^2,
+			\\\Norm{\var0}_*&\leq \sum_{j=1}^{\op{dim}(\tilde{\F{U}})} |r_j|\Norm{\var0_j}_* \leq \max_{j\leq\op{dim}(\tilde{\F{U}})} \Norm{\var0_j}_*\norm{\vec{r}}_{\ell^1},
+			\\\implies \frac{\Norm{\var0}_*}{\norm{\var0}} &\leq \max_{j\leq \op{dim}(\tilde{\F{U}})}\Norm{\var0_j}_*\frac{\norm{\vec{r}}_{\ell^1}}{\norm{\vec{r}}_{\ell^2}} \leq \max_{j\leq \op{dim}(\tilde{\F{U}})}\Norm{\var0_j}_*\sqrt{\op{dim}(\tilde{\F{U}})}.
 		\end{align}
@@
 		\end{equation}
-		This simplifies the equivalence constant because for any $\var0 = \sum r_je_j$ and $\mu>1$, there exists a set of points $\vec{x}\in\Domain$ with non-zero measure such that $\norm{\var0}_\infty\leq \mu|\var0(\vec{x})|$.
+		This simplifies the equivalence constant because for any $\var0 = \sum r_j\var0_j$ and $\mu>1$, there exists a set of points $\vec{x}\in\Domain$ with non-zero measure such that $\norm{\var0}_\infty\leq \mu|\var0(\vec{x})|$.
 This gives
 		\begin{align}
-			\norm{\var0}^2 &= \sum r_j^2 \geq \sum_{e_j(\vec{x})\neq 0} r_j^2,
-			\\\norm{\var0}_\infty& \leq \mu|\var0(\vec{x})| \leq \mu\sum_{e_j(\vec{x})\neq 0} |r_j|\norm{e_j}_\infty,
-			\\\implies \frac{\norm{\var0}_\infty}{\norm{\var0}} &\leq \mu\max_j\norm{e_j}_\infty\sqrt{C}.
-		\end{align}
+			\norm{\var0}^2 &= \sum r_j^2 \geq \sum_{\var0_j(\vec{x})\neq 0} r_j^2,
+			\\\norm{\var0}_\infty \leq \mu|\var0(\vec{x})| &\leq \mu\sum_{\var0_j(\vec{x})\neq 0} |r_j|\norm{\var0_j}_\infty.
+		\end{align}
+		$\implies \frac{\norm{\var0}_\infty}{\norm{\var0}} \leq \mu\max_j\norm{e_j}_\infty\sqrt{N}.$
 		This inequality holds for all $\mu>1$ therefore also for $\mu=1$. 
-Essentially, with an extra smoothness assumption on $e_j$, we can reduce the dimension of the problem to $\op{dim}(\F{U})=C $ and use the previous result.
+		Essentially, with an extra smoothness assumption on $\var0_j$, we have reduced the dimension of the problem to $\op{dim}(\tilde{\F{U}})=N $ and then used the previous result.
+	}{%
+		The first statement of the result is by definition, for each $\tilde{\var2}\in\tilde{\F{U}}$
+		$$ \norm{\tilde{\var2}} = \frac{\IP{\tilde{\var2}}{\tilde{\var2}}}{\norm{\tilde{\var2}}} \leq \sup_{\var0\in\tilde{\F{U}}} \frac{\IP{\var0}{\tilde{\var2}}}{\norm{\var0}\,\Norm{\tilde{\var2}}}\Norm{\tilde{\var2}} \leq \sup_{\var0,\tilde{\var0}\in\tilde{\F{U}}} \frac{\IP{\var0}{\tilde{\var0}}}{\norm{\var0}\,\Norm{\tilde{\var0}}}\Norm{\tilde{\var2}}.
+$$
+		Recall $\Norm\cdot\geq C^{-1}\norm\cdot_q$. To go further we use H\"older's inequality. If $\frac1q+\frac{1}{q^*}=1$, then for any $\var0,\tilde{\var0}\in\tilde{\F U}$
+		\begin{equation}
+			\frac{\IP{\var0}{\tilde{\var0}}}{\norm{\var0}\,\Norm{\tilde{\var0}}} \leq C^{-1}\frac{\IP{\var0}{\tilde{\var0}}}{\norm{\var0}\,\norm{\tilde{\var0}}_q} 
+			\leq C^{-1}\frac{\norm{\var0}_{q^*}}{\norm{\var0}}.
+		\end{equation}
+		If $q\geq2$ we use H\"older's inequality a second time:
+		\begin{equation}
+			\int_\Domain |\var0(\vec x)|^{\frac{q}{q-1}}\diff\vec{x} \leq \left(\int_\Domain 1\diff\vec{x}\right)^{1-\frac{q}{2(q-1)}}\left(\int_\Domain |\var0(\vec x)|^2\diff\vec{x}\right)^{\frac{q}{2(q-1)}} = \left(|\Domain|^{\frac{1}{2} -\frac{1}{q}}\norm{\var0}\right)^{\frac{q}{q-1}}.
+		\end{equation}
+		This confirms the inequality when $q\geq2$. If $q<2$, we can simply upper bound $\norm\cdot_{q^*}\leq |\Domain|^{\frac1{q^*}}\norm\cdot_\infty$ as required.
+	}
 	\qed\end{proof}
@@
 	\begin{lemma}\label{app:thm: specific a_U bound}
-		Suppose $\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
+		Suppose \edit[2]{$\F H= L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
 Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces with orthogonal projections $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\F{U}}^k $.
-If $q\geq 2$,
-		$$\norm{\tilde{\tens{\Pi}}_k\var2} \lesssim \Norm{\var2}, $$
-		otherwise,
-		$$\norm{\tilde{\tens{\Pi}}_k\var2} \lesssim \sqrt{\op{dim}(\tilde{\F{U}}^0)}\meshsize^{-\frac{kd}{2}}\Norm{\var2} $$
-		uniformly for all $\var2\in \F H$.
+If $q\geq 2$,}{$\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space} , then}
+		$$ \norm{\edit{\tilde{\tens{\Pi}}_k\var2}{\tilde{\var2}_k}} \lesssim \splitln{\edit{\Norm{\var2}}{1}}{\text{if }q\geq2, \text{ or}}{\edit{\sqrt{N}\Norm{\var2}}{}\meshsize^{-\frac{kd}{2}} \qquad}{\text{ if }1\leq q<2,\ \edit{}{\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_\infty}{\norm{\var0}}<\infty}.} \edit{}{\quad\text{in particular, }\quad q' = \splitln{0}{q\geq2}{-\frac{d}{2}}{1\leq q<2.}}$$
 	\end{lemma}
@@
 		Most of the conditions of Lemma~\ref{app:thm: generic a_U bound} are already satisfied.
-Denote $C=\op{dim}(\tilde{\F{U}^0})$ and $\{e_j\st j\in[C]\}$ the standard orthonormal basis of $\tilde{\F{U}}^0$.
-The scaling properties of $\meshsize$-refining finite element spaces guarantee that the value of $C$ satisfies the conditions of Lemma~\ref{app:thm: generic a_U bound} and a basis of $\tilde{\F{U}}^k$ is given by
-		\begin{equation}
-			\left\{\vec{x}\mapsto\var0_j(\vars0^{i,k}\vec{x}+\vvars1^{i,k}) \qquad\st\qquad i=1,\ldots,|\F M^k|,\ j=1,\ldots,C\right\}
-		\end{equation}
+\edit{}{Furthermore observe that $\Norm{\tilde{\var2}_k}\lesssim \Norm{\var0^*}+\meshsize^{kp}\lesssim 1$.
+For the $q\geq2$ case, this is already sufficient to conclude $\norm{\tilde{\var2}_k}\lesssim 1$ from Lemma~\ref{app:thm: generic a_U bound}, as required.}
+
+		\edit[2]{Denote $N=\op{dim}(\tilde{\F{U}^0})$ and let $\{e_j\st j\in[N]\}$ be an orthonormal basis of $\tilde{\F{U}}^0$.
+The scaling properties of $\meshsize$-refining finite element spaces guarantee that the value of $N$ satisfies the conditions of Lemma~\ref{app:thm: generic a_U bound} and a basis of $\tilde{\F{U}}^k$ is given by	$\left\{\vec{x}\mapsto\var0_j(\vars0^{i,k}\vec{x}+\vvars1^{i,k}) \qquad\st\qquad i=1,\ldots,|\F M^k|,\ j=1,\ldots,N\right\}$\\
 		for some $\vars0^{i,k}\in\R^{d\times d}$, and $\vvars1^{i,k}\in\R^d$ such that $0<\op{det}(\vars0^{i,k})\lesssim \meshsize^{-kd}$.
@@
 		We now compute the scaling constant in Lemma~\ref{app:thm: generic a_U bound}:
-		\begin{equation}
-			\frac{\norm{\var0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}_\infty}{\norm{\var0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}} = \frac{\norm{\var0_j}_\infty}{\sqrt{\int_{\domain_i^k} e_j(\vars0^{i,k} \vec{x}+\vvars1^{i,k})^2d\vec{x}}} = \frac{\norm{\var0_j}_\infty}{\sqrt{\op{det}(\vars0^{i,k})^{-1}}} \lesssim \meshsize^{-\frac{kd}{2}}.
-		\end{equation}
+		$\frac{\norm{\var0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}_\infty}{\norm{\var0_j(\vars0^{i,k}\cdot+\vvars1^{i,k})}} = \frac{\norm{\var0_j}_\infty}{\sqrt{\int_{\domain_i^k} e_j(\vars0^{i,k} \vec{x}+\vvars1^{i,k})^2\diff\vec{x}}} = \frac{\norm{\var0_j}_\infty}{\sqrt{\op{det}(\vars0^{i,k})^{-1}}} \lesssim \meshsize^{-\frac{kd}{2}}.$\\
 		This value is independent of $j$ and gives the desired bound as a result of Lemma~\ref{app:thm: generic a_U bound}.
+	}{%
+		For the case $q<2$, from Lemma~\ref{app:thm: generic a_U bound} recall that we are required to bound
+		\begin{equation}
+			\sup_{\tilde{\var0}\in\tilde{\F{U}}^k}\frac{\norm{\tilde{\var0}}_\infty}{\norm{\tilde{\var0}}} = \sup_{\tilde{\var0}\in\tilde{\F{U}}^k}\max_{\domain\in\F M^k} \frac{\norm{\tilde{\var0}}_{L^\infty(\domain)}}{\norm{\tilde{\var0}}_{L^2(\Domain)}} \leq \sup_{\tilde{\var0}\in\tilde{\F{U}}^k}\max_{\domain\in\F M^k} \frac{\norm{\tilde{\var0}}_{L^\infty(\domain)}}{\norm{\tilde{\var0}}_{L^2(\domain)}}.
+		\end{equation}
+		However, due to the decomposition property \eqref{eq: decomposition property}, for each $\domain\in\F M^k$ and $\tilde{\var0}\in\tilde{\F{U}}^k$ there exists $(\var0,\alpha,\vec\beta)\in\tilde{\F{U}}^0\times\R^{d\times d}\times\R^d$ such that
+		\begin{equation}
+			\norm{\var0}_\infty = \norm{\tilde{\var0}}_{L^\infty(\domain)},\qquad  \norm{\var0}^2 = \int_\Domain |\var0(\vec x)|^2\diff\vec{x} = \int_{\alpha\vec x+\vec\beta\in\domain} |\tilde{\var0}(\alpha\vec x+\vec\beta)|^2\diff\vec{x} = \op{det}(\alpha)^{-1}\norm{\tilde{\var0}}_{L^2(\domain)}^2.
+		\end{equation}
+		Combining these two equations confirms $\norm{\tilde{\var2}_k} \lesssim \sqrt{\op{det}(\alpha)^{-1}} \leq c_\alpha^{-\frac12}\meshsize^{-\frac{kd}{2}}$ as required.
+		} 		
 		\qed\end{proof}
@@
 	\begin{lemma}\label{app:thm: generic a_E bound}
-		Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\var2}^k=\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.
+		\edit[2]{Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\var2}_k=\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.}{Suppose $\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space} and $\var0^*$ the minimiser of $E$ such that $\Norm{\tilde{\var2}_k-\var0^*}\lesssim \meshsize^{kp}$.}
 		\begin{enumerate}
 			\item If $\op{E}$ is $\Norm\cdot$-Lipschitz at $\var0^*$, then
-			$\op{E}(\tilde{\var2}^k)-\op{E}(\var0^*) \lesssim \meshsize^p\Norm{\var0^*}.$
+			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{kp}\edit[2]{\Norm{\var0^*}}{}$\edit{}{ (i.e. $p'=p$)}.
 			\item If $\op{E}$ is $\Norm\cdot$-smooth at $\var0^*$, then 
-			$\op{E}(\tilde{\var2}^k)-\op{E}(\var0^*) \lesssim \meshsize^{2p}\Norm{\var0^*}.$
-			\item If $\op{f}$ is $\Norm\cdot$-Lipschitz at $\var0^*$ and 
+			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{2kp}\edit[2]{\Norm{\var0^*}}{}$\edit{}{ (i.e. $p'=2p$)}.
+			\edit[2]{\item If $\op{f}$ is $\Norm\cdot$-Lipschitz at $\var0^*$ and 
 			$$\min_{\var2\in\tilde{\F{U}}^k}\left\{\Norm{\var2-\var0^*}\st \op{g}(\var2)\leq \op{g}(\var0^*)\right\} \lesssim \min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*}$$
 			uniformly for $k\in\F N$, then
-			$\op{E}(\tilde{\var2}^k)-\op{E}(\var0^*) \lesssim \meshsize^p\Norm{\var0^*}.$
+			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^p\Norm{\var0^*}.$}{}
 		\end{enumerate}
@@
 	\begin{proof}
-		Each statement is by definition, observe
+		\edit{Each statement is}{Both statements are true} by definition, observe
 		\begin{gather}
-			\op{E}(\var2)-\op{E}(\var0^*) \leq \op{Lip}(\op{E})\Norm{\var2-\var0^*},
-			\\\op{E}(\var2)-\op{E}(\var0^*) \leq \IP{\nabla\op{E}(\var2)}{\var2-\var0^*} = \IP{\nabla \op{E}(\var2)-\nabla \op{E}(\var0^*)}{ \var2-\var0^*} \leq \op{Lip}(\nabla F)\Norm{\var2-\var0^*}^2,
-			\\\op{E}(\var2)-\op{E}(\var0^*) \leq \op{f}(\var2)-\op{f}(\var0^*) \leq \op{Lip}(\op{f})\Norm{\var2-\var0^*}.
+			\op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) \leq \op{Lip}(\op{E})\Norm{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*},
+			\\\op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) \leq \IP{\nabla\op{E}(\var2)}{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*} = \IP{\nabla \op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\nabla \op{E}(\var0^*)}{ \edit[2]{\var2}{\tilde{\var2}_k}-\var0^*} \leq \op{Lip}(\nabla\op{E})\Norm{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*}^2\edit[2]{,
+			\\\op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) \leq \op{f}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{f}(\var0^*) \leq \op{Lip}(\op{f})\Norm{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*}}{}.
 		\end{gather}
-		Minimising over the right-hand side over $\var2$ and substituting the definition of order gives the desired result.
+		\edit[2]{Minimising over the right-hand side over $\var2$ and substituting the definition of order gives the desired result.}{The proof is concluded by using the approximation bounds of $\tilde{\var2}_k$ in Definition~\ref{def: finite element space}.}
 		\qed\end{proof}
@@
 		\begin{equation}
-			\IP{\psi_i}{\psi_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vec{x}-\vec{x}_i|^2}{2\sigma^2}-\tfrac{|\vec{x}-\vec{x}_j|^2}{2\sigma^2}\right) \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vec{x}_i-\vec{x}_j|^2}{4\sigma^2}\right).
+			\IP{\psi_i}{\psi_j} = (2\pi\sigma^2)^{-d}\int_{[0,1]^d} \exp\left(-\tfrac{|\vec{x}-\vec{x}_i|^2}{2\sigma^2}-\tfrac{|\vec{x}-\vec{x}_j|^2}{2\sigma^2}\right)\diff\vec{x} \leq (2\pi\sigma^2)^{-d}(\pi\sigma^2)^{\frac{d}{2}}\exp\left(-\tfrac{|\vec{x}_i-\vec{x}_j|^2}{4\sigma^2}\right).
 		\end{equation}

### 2022-01-27 response.tex
General update

@@
 
-We would like to thank both the reviewers again for their time and feedback. All changes are marked in the supplementary pdf and a detailed response to each reviewer is given below.
+We would like to thank both the reviewers again for their time and feedback.
+A detailed response to each reviewer's comments is given below.
+All new text is marked in the manuscript and all deletions outside of the appendix.
+In particular, the statements of Theorem 7 and Lemmas 14-17 have changed so the proofs are now irrelevant.
+Changes to the theorems are fully annotated, the original proofs are hidden.
+
+We have also made one change which was not in response to the comments of the reviewer.
+It became clear to us that the statement of Definition 1 is much more natural as a property of the sequence $w_n$ rather than the sets $\F{U}^n$.
+Morally, we assume the existence of a `nice' minimising sequence rather than asserting that $w_n$ must be minimisers in $\F{U}^n$.
+Documenting the changes which are longer than one line:
+\begin{itemize}
+	\item At the end of page 4, emphasis is shifted towards the choice of sequence $w_n$
+	\item Definition 1 has been updated
+	\item At the top of page 8, the relaxation of Definition 1 allows an extra observation. In particular, the choice $\F{U}^n=\F H$ is now valid in Theorems 2 and 3.
+	\item In Theorem 3 we now have the specific choice $\tilde{w}_k = u_{n_k-1}$. The old $a_U=1$ is removed leading to a much simpler proof in the appendix.
+	\item The notation of Lemma 6 (and its proof in Lemma 14) has changed without changing the result, namely $(u_k,E(\tilde{w}_k))\mapsto (\tilde{w}_k, E(\tilde{\F{U}}^k))$.
+	\item The proof of Theorem 3 (i.e. Theorem 7) is now much simpler.
+\end{itemize}
 
@@
 
-	It's not quite clear which equations are being referred to here.
-On the copy I see, the old (61),(62) are now (63),(64) which are equalities.
-The best match I can see are the current equations (61),(62) in Lemma 9.
-The first equation is just H\"older's inequality, there is no reason for it to be equality for general $r$.
-The second inequality comes from the equivalence of norms, $\frac{\lVert\cdot\rVert_q}{\lVert\cdot\rVert_2}$.
-
-	\todo{I don't understand this.
-(61),(62) are statements of Fourier/Gaussian data in numerics section, his next point is also on page 18 rather than 17.
-(51),(52) are in the long align environment in section 6.4 (support detection), those are plausible.
-(41),(42) are in section 6.3.2 (bounds for countable functions).
-(59),(60) are the two inequalities of Lemma 9.
-My best guess is this last pair (which are ironically now (61),(62)...).
-This is quite a patronising answer given the general standard of his questions thought.}
+	Please can the reviewer clarify this point?
+The old (61-62) are now (63-64) which are equalities.
+There was a pair of inequalities (59-60), now (61-62), but they are simply statements of H\"older's inequality which we cannot expect to be sharp in general.
 

### 2022-01-27 paper.tex
General update

@@
 	where $\op{f}\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\op{g}\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
-The iterates of the FISTA algorithm will be denoted $\var0_n\in\F H$.
+\edit{}{Throughout this work we assume that $\op{E}$ is bounded below so that the infimum is finite.
+}The iterates of the FISTA algorithm will be denoted $\var0_n\in\F H$.
 It has been shown that $\op{E}(\var0_n) - \Emin$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}.
@@
 		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\F{U}^n$.
-The idea is that $\F{U}^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\var0\in\F{U}^n}\op{E}(\var0) \to \inf_{\var0\in\F H}\op{E}(\var0)$.
-A canonical example might be $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq n\}$.
-To quantify the balance between a growing Hilbert norm and improving estimate of $\op{E}$, we introduce a secondary sequence $n_0 < n_1 < \ldots$ and constants $\aU,\aE\geq1$ such that for each $k\in\F N$
+\edit{The idea is that $\F{U}^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\var0\in\F{U}^n}\op{E}(\var0) \to \inf_{\var0\in\F H}\op{E}(\var0)$.
+A canonical example might be $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq n\}$.}{The idea is that there is a sequence $\var2_n\in\F{U}^n$, $n\in\F N$ such that $\norm{\var2_n}$ grows slowly and $\op{E}_0(\var2_n)$ decreases quickly.} To quantify \edit{the}{this} balance\edit{ between a growing Hilbert norm and improving estimate of $\op{E}$}{}, we introduce a secondary sequence $n_0 < n_1 < \ldots$ and constants $\aU,\aE\geq1$ such that for each $k\in\F N$
 		\begin{equation}\label{eq: first regularity}
@@
 		\end{equation}
-		The expanding balls example would become $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq \aU^k\}$ for $n\in[n_k,n_{k+1})$, and $\aE$ reflects the smoothness of $\op{E}$.
+		\edit{The expanding balls example would become}{A canonical example would be} $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq \aU^k\}$ for $n\in[n_k,n_{k+1})$, then $\aE$ reflects the smoothness of $\op{E}$.
 The choice of exponential scaling \edit{is more}{is introduced to improve stability of Algorithm~\ref{alg: refining FISTA}.
@@
 For example, if \edit{$\F{U}^n$ is of the form}{for each $k\in\F N$}
-		$$\edit{\F{U}^{n_k} = \F{U}^{n_k+1} = \ldots = \F{U}^{n_{k+1}-1}}{\var2_{n_k}=\var2_{n_k+1}=\ldots \var2_{n_{k+1}-1}},$$
+		$$\edit{\F{U}^{n_k} = \F{U}^{n_k+1} = \ldots = \F{U}^{n_{k+1}-1}}{\var2_{n}= \var2_{n_k} \text{ for each } n=n_k,n_k+1,\ldots,n_{k+1}-1},$$
 		then many terms on the right-hand side of \eqref{eq: mini FISTA convergence} telescope to 0.
 The result of this is presented in Lemma~\ref{thm: mini exponential FISTA convergence}.
-The key idea is that the stability error in \eqref{eq: mini FISTA convergence} has $K\lesssim\log(N)$ terms, rather than $N$.
+The key idea is that the stability error in \eqref{eq: mini FISTA convergence} has $K\edit{\lesssim\log}{\ll} N$ terms, rather than $N$.
 	\end{adaptiveStep}
@@
 If the subsets grow too quickly, then the influence of $\norm{\var0_n}\to\infty$ will slow the rate of convergence.
-\edit{If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow.}{If $k$ is too small (coarse discretisation), then we overfit to the discrete problem, but if $k$ is too large, then the energy converges slowly.} Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way ($n_k^2\simeq \aE^k\aU^{2k}$) for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of
+\edit{If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow.}{If $n_k$ is too large, then we overfit to the discrete problem, but if $n_k$ is too small, then FISTA converges slowly.} Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way ($n_k^2\simeq \aE^k\aU^{2k}$) for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of
 		$$ \op{E}_0(\var0_N) \lesssim \frac{\aU^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
@@
 		The main challenge for adaptive choice of $\F{U}^n$ is to guarantee \eqref{eq: first regularity} from Step~\ref{step: step 2 smoothness} using a posteriori estimates.
-Combined with the partial telescoping requirement in Step~\ref{step: step 3 convergence bound}, a natural choice is $\var2_n=\var0_{n_k-1}$ for $n\in[n_k,n_{k+1}-1)$, i.e.
+Combined with the partial telescoping requirement in Step~\ref{step: step 3 convergence bound}, a natural choice is $\var2_n=\var0_{n_k-1}$ for $n\in[n_k,n_{k+1})$, i.e.
 the value of $n_k$ is chosen to be $n+1$ once the iterate $\var0_n$ is observed.
@@
 This is analysed in Theorem~\ref{thm: stronger exponential FISTA convergence} (sufficient conditions in Lemma~\ref{thm: practical refinement criteria}) which shows convergence results of the form}{The only non-trivial property to verify is the energy gap  $\op{E}_0(\var0_n) = \op{E}(\var0_n)-\Emin$.
-Lemma~\ref{thm: practical refinement criteria}) proposes some sufficient conditions to guarantee the same overall rate of convergence as in Step~\ref{step: step 5 sufficiently slow},}
+Lemma~\ref{thm: practical refinement criteria} proposes some sufficient conditions to guarantee the same overall rate of convergence as in Step~\ref{step: step 5 sufficiently slow},}
 		$$ \min_{n\leq N}\op{E}_0(\var0_n) \lesssim \frac{N^{2\kappa}}{N^2}$$
@@
 		This is equivalent to Lemma~\ref{thm: sufficiently fast} after the assumptions on $n_k$.
-		\item If $\F H$ is finite dimensional, then the $\aU=1$ is almost trivially satisfied.
+		\item If $\F H$ is finite dimensional, then the condition $\aU=1$ is almost trivially satisfied.
 Norms in finite dimensions are equivalent and any discretisation can be achieved with a finite number of refinements (i.e.
@@
 			Suppose $\var0_n$ and $n_k$ are sequences satisfying 
-			$$\op{E}_0(\var0_N) \lesssim \frac{\aU^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \aE^K\aU^{2K},$$
+			$$\forall n_K\leq N< n_{K+1},\ \op{E}_0(\var0_N) \lesssim \frac{\aU^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \aE^K\aU^{2K},$$
 			then 
@@
 		\Copy{thm: stronger exponential FISTA convergence}{
-			Let $(\F{U}^n\subset\F H)_{n\in\F N}$ be a sequence of subsets satisfying \eqref{eq: refining subspace definition}\edit{}{, $(\tilde{\var2}_k)_{k\in\F N}$ an \aUaE,} and $n_k\in\F N$ a monotone increasing sequence such that
-			$$ \edit{\tilde{\F{U}}^k \coloneqq \F{U}^{n_k}, \qquad}{} \tilde{\var2}_k \in \edit{\left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]}{\F{U}^{n_k}}\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}$$
+			Let $(\F{U}^n\subset\F H)_{n\in\F N}$ be a sequence of subsets satisfying \eqref{eq: refining subspace definition} \edit{and}{, compute $\var0_n$ and $\var1_n$ by Algorithm~\ref{alg: refining FISTA}.
+Suppose that there exists a monotone increasing sequence } $n_k\in\F N$ \edit{a monotone increasing sequence }{}such that
+			$$ \edit{\tilde{\F{U}}^k \coloneqq \F{U}^{n_k}, \qquad \tilde{\var2}_k \in \left[\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)\right]}{\tilde{\var2}_k\coloneqq \var0_{n_k-1}\in\F{U}^{n_k}}\cap\F{U}^{n_k+1} \cap\ldots\cap \F{U}^{n_{k+1}-1}$$
 			for all $k\in\F N$.
-			Compute $\var0_n$ and $\var1_n$ by Algorithm~\ref{alg: refining FISTA}.
+			\edit{Compute $\var0_n$ and $\var1_n$ by Algorithm~\ref{alg: refining FISTA}.}{}
 
@@
 			$$ \norm{\tilde{\var2}_k}\lesssim \aU^k \qquad\text{and}\qquad \op{E}_0(\var0_{n_k-1}) \lesssim \aE^{-k}.$$
-			\sout{Whenever these conditions on $n_k$ are satisfied, }}{If $\aU>1$, $\aE\geq1$, and $n_k^2\lesssim \aE^k\aU^{2k}$, }then
+			\sout{Whenever these conditions on $n_k$ are satisfied, }}{If $(\tilde{\var2}_k)_{k\in\F N}$ is an \aUaE\ with $\aU>1$ and $n_k^2\lesssim \aE^k\aU^{2k}$, }then
 			$$\min_{n\leq N}\op{E}_0(\var0_n) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \aU^2}{\log \aE + \log \aU^2}$$
@@
 				\item Small discrete gap refinement: $\op{E}_0(\edit{\tilde{\var2}_k}{\tilde{\F{U}}^k})\leq \vars1\aE^{-k}$ and $ \op{E}_0(\edit{\var0_k}{\tilde{\var2}_k})-\op{E}_0(\edit{\tilde{\var2}_{k-1}}{\tilde{\F{U}}^{k-1}})\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
-				\item Small relative gap refinement: $ \op{E}_0(\edit{\var0_k}{\tilde{\var2}_k}) - \op{E}_0(\edit{\tilde{\var2}_{k-1}}{\tilde{\F{U}}^{k-1}}) \leq \vars1\op{E}_0(\edit{\var0_k}{\tilde{\var2}_k})$ for all $k\in\F N$, some $0<\vars1\leq \frac{1}{1+\aE}$.
+				\edit[2]{\item Small relative gap refinement: $ \op{E}_0(\edit{\var0_k}{\tilde{\var2}_k}) - \op{E}_0(\edit{\tilde{\var2}_{k-1}}{\tilde{\F{U}}^{k-1}}) \leq \vars1\op{E}_0(\edit{\var0_k}{\tilde{\var2}_k})$ for all $k\in\F N$, some $0<\vars1\leq \frac{1}{1+\aE}$.}{}
 			\end{enumerate}
-			\edit{If}{Suppose}, furthermore, there exists a Banach space $(\F{U},\Norm\cdot)$ with $\F{U}\supset\F H$ and \edit{}{dual-norm $\Norm\cdot_*$.
-If} the sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded, then it is also sufficient that:
-			\begin{enumerate}\setcounter{enumi}{3}
-				\item Small continuous gradient refinement: $ \inf_{\var1\in\partial\op{E}(\edit{\var0_k}{\tilde{\var2}_k})}\Norm{\var1}_*\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
-				\item Small discrete gradient refinement: $\op{E}_0(\edit{\tilde{\var2}_k}{\tilde{\F{U}}^k})\leq \vars1\aE^{-k}$ and $\sup_{\var0,\tilde{\var0}\in \tilde{\F{U}}^k}\inf_{\var1\in\partial\op{E}(\var0_k)}\frac{|\IP{v}{\var0-\tilde{\var0}}|}{\Norm{\var0-\tilde{\var0}}}\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+			\edit{If}{Otherwise, suppose} there exists a Banach space $(\F{U},\Norm\cdot)$ \edit{with $\F{U}\supset\F H$}{which contains each $\tilde{\F{U}}^k$, $\sup_{k\in\F N}\Norm{\tilde{\var2}_k}<\infty$,} and the sublevel sets of $\op{E}$ are $\Norm\cdot$-bounded, then it is also sufficient that:
+			\begin{enumerate}\setcounter{enumi}{2}
+				\item Small continuous gradient refinement: $ \inf_{\var1\in\partial\op{E}(\edit{\var0_k}{\tilde{\var2}_k})}\edit{\Norm{\var1}_*}{\sup_{\var0\in\F{U}} \frac{|\IP{\var1}{\var0}|}{\Norm{\var0}}}\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+				\item Small discrete gradient refinement: $\op{E}_0(\edit{\tilde{\var2}_k}{\tilde{\F{U}}^k})\leq \vars1\aE^{-k}$ and $\sup_{\var0,\tilde{\var2}\in \tilde{\F{U}}^k}\inf_{\var1\in\partial\op{E}(\edit{\var0_k}{\tilde{\var2}_k})}\frac{|\IP{v}{\var0-\tilde{\var2}}|}{\Norm{\var0-\tilde{\var2}}}\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
 			\end{enumerate}
@@
 }$\F{U}\subset L^q(\Domain)$\edit{}{)} for some \edit{}{$q\in[1,\infty]$ and }connected, bounded domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{}.
-We say that $\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$ is a \emph{mesh} if
-		$$\edit{\domain_i^k\subset}{\bigcup_{\domain\in\F M^k}\domain = } \Domain \qquad\text{and} \qquad |\edit{\domain_i^k\cap\domain^k_j}{\domain\cap\domain'}| = 0\qquad \text{for all \edit{$i$ and $j$}{$\domain,\domain'\in\F M^k,\ \domain\neq\domain'$}.}$$
-		We say that $\tilde{\F{U}}^k\subset \F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\tilde{\var0}\in\tilde{\F{U}}^k$ \edit{there exists $\var0_i^k\in\tilde{\F{U}}^k$ such that
-		\\$\supp(\var0_i^k)\subset \bar{\domain_i^k}, \qquad \tilde{\var0}(\vec{x}) = \var0^k_i(\vec{x}) \qquad \text{ for a.e. }\vec{x}\in\domain_i^k, \text{ all } i\in\F N.$\\}{%
-		$$\forall\domain\in\F M^k \qquad \exists \var0|_\domain\in \tilde{\F{U}}^k \quad\text{such that}\quad \op{supp}(\var0|_\domain)\subset\bar{\domain}\quad\text{and}\quad\text{for a.e.
-}\vec{x}\in\domain,\ \tilde{\var0}(\vec{x})=\var0|_\domain(\vec{x}).$$
-		}
-
-		\edit{We}{Moreover, for $\meshsize\in(0,1)$, we} say that the sequence $(\tilde{\F{U}}^k)_{k\in\F N}$ is \emph{$\meshsize$-refining} if there exists \edit{a basis $\{e_1, \ldots,e_N\}\subset\tilde{\F{U}}^0\cap L^\infty(\Domain)$ such that for any $\var0_i^k\in\tilde{\F{U}}^k$ with $\supp(\var0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
+We say that \edit{$\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$}{a collection of subdomains $\F M$} is a \emph{mesh} if
+		$$\edit{\domain_i^k\subset}{\bigcup_{\domain\in\F M}\domain = } \Domain \qquad\text{and} \qquad |\edit{\domain_i^k\cap\domain^k_j}{\domain\cap\domain'}| = 0\qquad \text{for all \edit{$i$ and $j$}{$\domain,\domain'\in\F M,\ \domain\neq\domain'$}.}$$
+		\edit{We say that $\tilde{\F{U}}^k\subset \F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\tilde{\var0}\in\tilde{\F{U}}^k$ there exists $\var0_i^k\in\tilde{\F{U}}^k$ such that
+		\\$\supp(\var0_i^k)\subset \bar{\domain_i^k}, \qquad \tilde{\var0}(\vec{x}) = \var0^k_i(\vec{x}) \qquad \text{ for a.e. }\vec{x}\in\domain_i^k, \text{ all } i\in\F N.$\\
+		We say that the sequence $(\tilde{\F{U}}^k)_{k\in\F N}$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\F{U}}^0\cap L^\infty(\Domain)$ such that for any $\var0_i^k\in\tilde{\F{U}}^k$ with $\supp(\var0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that
 		\\$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \var0_i^k(\vec{x}) = \sum_{j=1}^N\vars2_je_j(\vars0 \vec{x}+\vvars1) \quad \text{ for a.e.
@@
 $\\}{%
-		$c_\alpha>0$ such that for each $\tilde{\var0}\in\tilde{\F{U}}^k$ and $\domain\in\F M^k$,
-		$$ \exists (\var0,\alpha,\vec\beta)\in\tilde{\F U}^0\times\R^{d\times d}\times\R^d \quad \text{such that}\quad \op{det}(\alpha)\geq c_\alpha\meshsize^{kd} \quad\text{and}\quad \forall\vec{x}\in\Domain,\ \var0(\vec x) = \var0|_\domain(\alpha \vec{x}+\vec\beta).
+		Furthermore, we say a sequence of meshes $(\F M^k)_{k\in\F N}$ is \emph{consistent} if there exists $\domain_0\in\F{M}^0$ such that
+		$$ \forall\domain\in\F{M}^k \quad \exists (\vars0_\domain,\vvars1_\domain)\in\R^{d\times d}\times\R^d \quad\text{such that}\quad \vec{x}\in\domain_0\iff \vars0_\domain\vec{x}+\vvars1_\domain\in\domain.
 $$
-		}
-
+		Fix $\meshsize\in(0,1)$, linear subspaces $\tilde{\F{U}}^k\subset\F{H}$ and consistent meshes $\F M^k$.
+We say that the sequence $(\tilde{\F{U}}^k)_{k\in\F N}$ is an \emph{$\meshsize$-refining sequence of finite element spaces} if there exists $c_{\vars0}>0$ such that:
+		$$ \forall (\tilde{\var0},\domain)\in(\tilde{\F{U}}^k,\F{M}^k),\quad \op{det}(\vars0_\domain)\geq c_{\vars0}\meshsize^{kd} \quad\text{and}\quad \exists \var0\in\tilde{\F U}^0 \quad\text{such that}\quad \forall\vec{x}\in\domain_0,\ \var0(\vec{x})=\tilde{\var0}(\vars0_\domain\vec{x}+\vvars1_\domain).$$}
 		We say that $(\tilde{\F{U}}^k)_k$ is \emph{of order $p$} if \edit{}{for any $\var0^*\in\argmin_{\var0\in\F U}\op{E}(\var0)$ there exists a sequence $(\tilde{\var2}_k)_{k\in\F N}$ such that}
@@
 	\end{lemma}
-	This is precisely rewriting the statement of Definition~\ref{def: exp subspaces} into terms of resolution and approximation properties.
-The following theorem shows how to link $p$ and $q$ from Definition~\ref{def: finite element space} with $p'$ and $q'$ from Lemma~\ref{thm: pq to p'q'}.
+	This is precisely rewriting the statement of Definition~\ref{def: exp subspaces} into terms of resolution $\meshsize$.
+The following theorem links $p$ and $q$ from Definition~\ref{def: finite element space} with $p'$ and $q'$ from Lemma~\ref{thm: pq to p'q'}.
 	}
@@
 		\begin{align*}
-			\aU &\leq \splitln{1}{\text{if }q\geq 2,}{\sqrt{\meshsize^{-d}}}{q<2 \edit{}{\text{ and }\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_\infty}{\norm{\var0}}<\infty},}
+			\aU &\leq \splitln{1}{\text{if }q\geq 2,}{\sqrt{\meshsize^{-d}}}{q<2 \edit{}{\text{ and }\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_{L^\infty(\domain_0)}}{\norm{\var0}_{L^2(\domain_0)}}<\infty},}
 			& \aE &\geq \begin{cases}
@@
 	The proof of this theorem is in Appendix~\ref{app: generic a_U and a_E}.
-\edit{}{Note that $\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_\infty}{\norm{\var0}}$ is finite whenever $\tilde{\F{U}}^0\subset L^\infty(\Domain)$ is finite dimensional, so this is not a very strong assumption.} The main take-home for this theorem is that the computation of $\aU$ and $\aE$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\op{E}$.
+\edit{}{Note that $\sup_{\var0\in\tilde{\F{U}}^0}\norm{\var0}_{L^\infty(\domain_0)}\norm{\var0}_{L^2(\domain_0)}^{-1}$ is finite whenever $\tilde{\F{U}}^0\subset L^\infty(\Domain)$ is finite dimensional, so this is not a very strong assumption.} The main take-home for this theorem is that the computation of $\aU$ and $\aE$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\op{E}$.
 \edit{The only non-trivial case is when $\op{g}$ is not smooth enough to estimate directly.
@@
 We assume $\op{f}\in C^1(\R^m)$ is convex\edit{ with}{, bounded from below, and} $\edit{\nabla\op{f}}{(\norm{\A}^2\nabla\op{f})}$ is 1-Lipschitz\edit{, and in the continuous-space case we also require $\A^*\colon\R^m\to C^1([0,1]^d)$}{}.
-	Let $\var0^*\in\argmin_{\var0\in\F{U}}\op{E}(\var0)$\edit{}{, which is non-empty so long as $\psi_j\in C$ (i.e. $\A$ is sequentially weak-star continuous)}.
+	Let $\var0^*\in\argmin_{\var0\in\F{U}}\op{E}(\var0)$\edit{}{, which is non-empty so long as $\psi_j\in C([0,1]^d)$, i.e. $\A$ is sequentially weak-star continuous}.
 
@@
 	\begin{proof}
-		The proof is direct computation,
-		\begin{equation}
-			\log N^2 \geq \log C + K\left(\log \aE + \log \aU^2\right)
-		\end{equation}
-		which leads to
-		\begin{equation}
-			\aU^{2K} = \exp(K\log \aU^2)
-			\leq \exp\left(\log N^2\frac{\log \aU^2}{\log \aE + \log \aU^2} - \frac{\log C\log \aU^2}{\log \aE + \log \aU^2}\right)
-		\end{equation}
+		The proof is direct computation,\edit[2]{\\$\log N^2 \geq \log C + K\left(\log \aE + \log \aU^2\right)$\\
+			which leads to \\$ \aU^{2K} = \exp(K\log \aU^2)
+			\leq \exp\left(\log N^2\frac{\log \aU^2}{\log \aE + \log \aU^2} - \frac{\log C\log \aU^2}{\log \aE + \log \aU^2}\right)$\\}{ note that
+		\begin{equation}\label{eq: aEaU^kappa}
+			(\aE\aU^2)^\kappa = \exp\left(\kappa\log(\aE\aU^2)\right) = \exp(\log\aU^2) = \aU^2,
+		\end{equation}
+		therefore 
+		\begin{equation}
+			\aU^{2K} = \left((\aE\aU^2)^K\right)^\kappa \lesssim n_K^{2\kappa} \leq N^{2\kappa},
+		\end{equation}
+		so $\op{E}_0(\var0_N)\lesssim N^{-2(1-\kappa)}$}
 		as required.
@@
 	\begin{proof}
-		To apply Lemma~\ref{app:thm: sufficiently fast}, we need
+		\edit[2]{To apply Lemma~\ref{app:thm: sufficiently fast}, we need
 		\begin{equation}
@@
 		If we fix $N^2\lesssim (\aE\aU^2)^k$, then
-		\begin{equation}
-			\min_{n\leq N} \op{E}_0(\var0_n)\lesssim \splitln{\aE^{-k}}{N>n_k}{ \frac{\aU^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\aU^{2k},\aU^{2k}) \lesssim N^{-2(1-\kappa)}
-		\end{equation}
+		\\$ \min_{n\leq N} \op{E}_0(\var0_n)\lesssim \splitln{\aE^{-k}}{N>n_k}{ \frac{\aU^{2k}}{N^2}}{N\leq n_k} \lesssim N^{-2}\max(\aU^{2k},\aU^{2k}) \lesssim N^{-2(1-\kappa)}$\\}{
+		Let $C>0$ satisfy $n_k^2\leq C\aE^k\aU^{2k}$ for each $k\in\F N$.
+Fix $N>C$ and choose $k$ such that $C\aE^{k-1}\aU^{2k-2}\leq N<C\aE^k\aU^{2k}$.
+By construction, and using the equality from \eqref{eq: aEaU^kappa}, we have
+		\begin{equation}
+			\min_{n\leq N}\op{E}_0(\var0_N)\leq \op{E}_0(\tilde{\var2}_{k-1}) \lesssim \aE^{-k} = (\aE\aU^2)^{-k(1-\kappa)}<C^{\kappa-1}N^{-2(1-\kappa)}
+		\end{equation}
+		}
 		as required.
@@
 	\begin{proof}
-		The proof is simply to justify that the conditions of Theorem~\ref{app:thm: stronger exponential FISTA convergence} are met for all refinement criteria described here.
-$\norm{\tilde{\var2}_k}\lesssim \aU^k$ is enforced at every step and condition (2) guarantees the back-stop condition on $n_k$.
-
+		\edit[2]{The proof is simply to justify that the conditions of Theorem~\ref{app:thm: stronger exponential FISTA convergence} are met for all refinement criteria described here.
+The condition $\norm{\tilde{\var2}_k}\lesssim \aU^k$ is enforced at every step and condition (2) guarantees the back-stop condition on $n_k$.
 		To complete the requirements of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, we first need to show inductively that $\op{E}_0(\tilde{\var2}_{k-1}) \leq C\aE^{-k}$, then it follows that $\op{E}_0(\var0_{n_k-1})\leq C\aE^{-k}$.
@@
 		This completes the requirements of Theorem~\ref{app:thm: stronger exponential FISTA convergence}, therefore also this proof.
+		}{The conditions for $\aU$ in Definition~\ref{def: exp subspaces} are already met, it remains to be shown that $\op{E}_0(\tilde{\var2}_{k}) \leq C\aE^{-k}$ for some fixed $C>0$.
+For cases (3) and (4), fix $R>0$ such that both $\{\tilde{\var2}_k\}_{k\in\F N}$ and the sublevel set $ \{\var0\in\F{U}\st\op{E}_0(\var0)\leq 1+\vars1\} $ are contained in the ball of radius $R$.
+Any minimising sequences of $\op{E}$ in $\F{U}$ or $\tilde{\F{U}}^k$ are contained in this ball.
+We can therefore compute $C$ in each case:
+			\begin{itemize}
+				\item[(1)] $\op{E}_0(\tilde{\var2}_k)\leq \vars1\aE^{-k}$, so $C=\vars1$ suffices.
+				\item[(2)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\tilde{\F{U}}^k) + \vars1\aE^{-k} \leq (\aE +1)\beta\aE^{-k}$, so $C=(\aE +1)\beta$ suffices.
+				\item[(3)] $\op{E}(\tilde{\var2}_k)-\op{E}(\var0)\leq \inf_{\var1\in\partial\op{E}(\tilde{\var2}_k)}\leq 2R\vars1\aE^{-k}$ for any $\var0\in\F{U}$ with $\Norm{\var0}\leq R$.
+Maximising over $\var0$ gives $C=2R\vars1$
+				\item[(4)] $\op{E}_0(\tilde{\var2}_k)-\op{E}_0(\var0)\leq \inf_{\var1\in\partial\op{E}(\tilde{\var2}_k)}\leq 2R\vars1\aE^{-k}$ for any $\var0\in\tilde{\F{U}}^k$ with $\Norm{\var0}\leq R$, therefore $\op{E}_0(\tilde{\var2}_k) \leq \op{E}_0(\tilde{\F{U}}^k) + 2R\vars1\aE^{-k}$ and $C=(1+2R)\vars1$.
+			\end{itemize}
+			This completes the requirements of Definition~\ref{def: exp subspaces}.
+		}
 		\qed\end{proof}
@@
 We assume that $\F H=L^2(\Domain)$, $\norm{\cdot}_q\lesssim\Norm\cdot$, and there exist spaces $(\tilde{\F U}^k)_{k\in\F N}$ with $\tilde{\F{U}}^k\subset \F{U}\cap L^\infty(\Domain)$ containing a sequence $(\tilde{\var2}_k\in \tilde{\F U}^k)_{k\in\F N}$ such that $\Norm{\tilde{\var2}_k - \var0^*} \lesssim \meshsize^{kp}$.
-Furthermore, there exists constant $c_\alpha>0$ and finite partitions $\F M^k=\{\domain_1^k,\domain_2^k,\ldots\}$ of $\Domain$ such that:
-	\begin{equation}\label{eq: decomposition property}
-		\forall (\tilde{\var0},\domain)\in\tilde{\F{U}}^k\times\F M^k,\quad \exists (\var0,\alpha,\vec\beta)\in\tilde{\F U}^0\times\R^{d\times d}\times\R^d \quad \text{such that}\quad \op{det}(\alpha)\geq c_\alpha\meshsize^{kd} \quad\text{and}\quad \forall\vec{x}\in\Domain,\ \var0(\vec x) = \splitln{\tilde{\var0}(\alpha \vec{x}+\vec\beta)\qquad}{\text{if }\alpha \vec{x}+\vec\beta\in\domain,}{0}{\text{else.}}
-	\end{equation}
-
+Furthermore, there exists constant $c_\alpha>0$ and meshes $\F M^k$ such that:
+	\begin{gather}
+		\exists\domain_0\in\F{M}^0\quad\text{such that}\quad \forall\domain\in\F{M}^k \quad \exists (\vars0_\domain,\vvars1_\domain)\in\R^{d\times d}\times\R^d \quad\text{such that}\quad \vec{x}\in\domain_0\iff \vars0_\domain\vec{x}+\vvars1_\domain\in\domain, \qquad\text{ and}
+		\\\forall (\tilde{\var0},\domain)\in\tilde{\F{U}}^k\times\F M^k,\quad \exists \var0\in\tilde{\F U}^0 \quad \text{such that}\quad \op{det}(\alpha_\domain)\geq c_\alpha\meshsize^{kd} \quad\text{and}\quad \forall\vec{x}\in\domain_0,\ \var0(\vec x) = \tilde{\var0}(\alpha_\domain \vec{x}+\vec\beta_\domain).
+\label{eq: decomposition property}
+	\end{gather}
 	In this section, these assumptions will be summarised simply by saying that $\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space}.
@@
 If $q\geq 2$,}{$\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space} , then}
-		$$ \norm{\edit{\tilde{\tens{\Pi}}_k\var2}{\tilde{\var2}_k}} \lesssim \splitln{\edit{\Norm{\var2}}{1}}{\text{if }q\geq2, \text{ or}}{\edit{\sqrt{N}\Norm{\var2}}{}\meshsize^{-\frac{kd}{2}} \qquad}{\text{ if }1\leq q<2,\ \edit{}{\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_\infty}{\norm{\var0}}<\infty}.} \edit{}{\quad\text{in particular, }\quad q' = \splitln{0}{q\geq2}{-\frac{d}{2}}{1\leq q<2.}}$$
+		$$ \norm{\edit{\tilde{\tens{\Pi}}_k\var2}{\tilde{\var2}_k}} \lesssim \splitln{\edit{\Norm{\var2}}{1}}{\text{if }q\geq2, \text{ or}}{\edit{\sqrt{N}\Norm{\var2}}{}\meshsize^{-\frac{kd}{2}} \qquad}{\text{ if }1\leq q<2,\ \edit{}{\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_{L^\infty(\domain_0)}}{\norm{\var0}_{L^2(\domain_0)}}<\infty}.} \edit{}{\quad\text{in particular, }\quad q' = \splitln{0}{q\geq2}{-\frac{d}{2}}{1\leq q<2.}}$$
 	\end{lemma}
@@
 		\begin{equation}
-			\sup_{\tilde{\var0}\in\tilde{\F{U}}^k}\frac{\norm{\tilde{\var0}}_\infty}{\norm{\tilde{\var0}}} = \sup_{\tilde{\var0}\in\tilde{\F{U}}^k}\max_{\domain\in\F M^k} \frac{\norm{\tilde{\var0}}_{L^\infty(\domain)}}{\norm{\tilde{\var0}}_{L^2(\Domain)}} \leq \sup_{\tilde{\var0}\in\tilde{\F{U}}^k}\max_{\domain\in\F M^k} \frac{\norm{\tilde{\var0}}_{L^\infty(\domain)}}{\norm{\tilde{\var0}}_{L^2(\domain)}}.
-		\end{equation}
-		However, due to the decomposition property \eqref{eq: decomposition property}, for each $\domain\in\F M^k$ and $\tilde{\var0}\in\tilde{\F{U}}^k$ there exists $(\var0,\alpha,\vec\beta)\in\tilde{\F{U}}^0\times\R^{d\times d}\times\R^d$ such that
-		\begin{equation}
-			\norm{\var0}_\infty = \norm{\tilde{\var0}}_{L^\infty(\domain)},\qquad  \norm{\var0}^2 = \int_\Domain |\var0(\vec x)|^2\diff\vec{x} = \int_{\alpha\vec x+\vec\beta\in\domain} |\tilde{\var0}(\alpha\vec x+\vec\beta)|^2\diff\vec{x} = \op{det}(\alpha)^{-1}\norm{\tilde{\var0}}_{L^2(\domain)}^2.
-		\end{equation}
-		Combining these two equations confirms $\norm{\tilde{\var2}_k} \lesssim \sqrt{\op{det}(\alpha)^{-1}} \leq c_\alpha^{-\frac12}\meshsize^{-\frac{kd}{2}}$ as required.
+			\sup_{\tilde{\var0}\in\tilde{\F{U}}^k}\frac{\norm{\tilde{\var0}}_\infty}{\norm{\tilde{\var0}}} = \sup_{\tilde{\var0}\in\tilde{\F{U}}^k}\sup_{\domain\in\F M^k} \frac{\norm{\tilde{\var0}}_{L^\infty(\domain)}}{\norm{\tilde{\var0}}_{L^2(\Domain)}} \leq \sup_{\tilde{\var0}\in\tilde{\F{U}}^k}\sup_{\domain\in\F M^k} \frac{\norm{\tilde{\var0}}_{L^\infty(\domain)}}{\norm{\tilde{\var0}}_{L^2(\domain)}}.
+		\end{equation}
+		However, due to the decomposition property \eqref{eq: decomposition property}, for each $\domain\in\F M^k$ and $\tilde{\var0}\in\tilde{\F{U}}^k$ there exists $\var0\in\tilde{\F{U}}^0$ such that
+		\begin{equation}
+			\norm{\var0}_{L^\infty(\domain_0)} = \norm{\tilde{\var0}}_{L^\infty(\domain)},\qquad  \norm{\var0}_{L^2(\domain_0)}^2 = \int_\Domain |\var0(\vec x)|^2\diff\vec{x} = \int_{\domain_0} |\tilde{\var0}(\alpha\vec x+\vec\beta)|^2\diff\vec{x} = \op{det}(\alpha)^{-1}\norm{\tilde{\var0}}_{L^2(\domain)}^2.
+		\end{equation}
+		Combining these two equations with the assumed bound on $\frac{\norm{\var0}_{L^\infty(\domain_0)}}{\norm{\var0}_{L^2(\domain_0)}}$ confirms $\norm{\tilde{\var2}_k} \lesssim \sqrt{\op{det}(\alpha)^{-1}} \leq c_\alpha^{-\frac12}\meshsize^{-\frac{kd}{2}}$ as required.
 		} 		

### 2022-02-07 response.tex
Update to response letter

@@
 \renewcommand{\ULthickness}{1.0pt}
-\newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
+\newcommand{\edit}[2]{{\color{red}\sout{#1}}{\color{darkgreen}#2}}
 
@@
 All new text is marked in the manuscript and all deletions outside of the appendix.
-In particular, the statements of Theorem 7 and Lemmas 14-17 have changed so the proofs are now irrelevant.
+In particular, the statements of Theorem 7 and Lemmas 14-17 have changed so the old proofs are now irrelevant.
 Changes to the theorems are fully annotated, the original proofs are hidden.
@@
 	\item At the top of page 8, the relaxation of Definition 1 allows an extra observation. In particular, the choice $\F{U}^n=\F H$ is now valid in Theorems 2 and 3.
-	\item In Theorem 3 we now have the specific choice $\tilde{w}_k = u_{n_k-1}$. The old $a_U=1$ is removed leading to a much simpler proof in the appendix.
+	\item In Theorem 3 we now have the specific choice $\tilde{w}_k = u_{n_k-1}$. The old $a_U=1$ case is covered by the updated Theorem 2, leading to a much simpler proof of Theorem 3 in the appendix.
 	\item The notation of Lemma 6 (and its proof in Lemma 14) has changed without changing the result, namely $(u_k,E(\tilde{w}_k))\mapsto (\tilde{w}_k, E(\tilde{\F{U}}^k))$.
-	\item The proof of Theorem 3 (i.e. Theorem 7) is now much simpler.
 \end{itemize}
@@
 That paragraph in the introduction has been re-worded to take into account some of your points.
-In an abstract sense one can always attain minima by adding points to the space (e.g.
-$\operatorname{argmin} e^{-u} = \{\infty\}$), as you say, the challenge is to have some regularity guarantees so that the iterates themselves are not `meaningless'.
-The meaning of `meaningless' depends on the topology.
+In answer to your questions, in an abstract sense one can always `attain' minima by adding points to (i.e.
+`completing') the space.
+As you say, the challenge is to have some regularity guarantees so that the iterates themselves are not `meaningless', but the meaning of meaningless depends on the topology.
+
+A simple 1D example, if $E(u) = e^{-u}$ for $u\geq0$, then numerically I get $u_n\approx 4\log(n)$.
+Clearly $|u_n-\infty|\not\to0$, but in a `weak sense', certainly $u_n\to\infty$.
+This seems to be representative of the general behaviour.
 In the Lasso example, the iterates are meaningless in both $L^2$ and $L^1$, but can be understood in the space of measures (or distributions).
 In this sense, we have never observed anything unexpected for large $n$.
+Unfortunately this behaviour can't be understood from the values of $a_E$ and $a_U$ alone.
 
 \section{Detailed response to second reviewer}
+Thank you for such detailed comments, they have definitely greatly improved the quality of this manuscript. We are sorry that this has required so much work from you in the process.
 
@@
 
-	There is no such requirement between the spaces, this is now clarified after the bullet points in Section 1.
+	There is no such requirement between the spaces, this is now clarified after the bullet points in Section 1:
+	\begin{quote}
+		\edit{}{All the examples in this work, discussed from Section~5 onward, consider $\{u\in\F H: E(u)<\infty\}$ to be contained in some ambient Banach space $\F{U}$.
+The idea is that FISTA provides a minimising sequence in $\F H\cap\F U$, but further properties like rate of convergence (of $E$ or the iterates) must come from the topology of $\F{U}$.
+It will not be necessary for $\F H\hookrightarrow\F U$ to be a continuous embedding, nor in fact the full inclusion $\F H\subset\F U$.}
+	\end{quote}
 
@@
 
-	This has been clarified in the text, immediately above (7)
+	This has been clarified in the text, immediately above (7):
+	\begin{quote}\edit{}{if there exists $u^*\in \operatorname{argmin}_{u\in\F H}{E}(u)$,\ldots}\end{quote}
 
@@
 
-	In the statement of Lemma 6 we now clarify that this is the dual norm.
+	We now use the explicit definition in Lemma 6.
 
@@
 The values of $q$ and $h$ have been clarified.
-We have removed all mention of a particular basis, in response to your later comment, and clarified instead the general scaling properties (the $\alpha$ and $\beta$).
+We have removed all mention of a particular basis, in response to your later comment, and clarified instead the general scaling properties (the $\alpha$ and $\beta$ dependent on $\omega$).
 You're right, the assumption $\F U\supset\F H$ was lazy and not what was intended.
 We only require $\F U$ to contain sub-levelsets of the energy, now clarified in the text.
-\todo{It now makes sense to consider $q>2$, even if Theorem 4 confirms that nothing is gained by doing so.}
-
-	While it will be most common for $(\alpha,\beta)$ to depend only on $\omega$, it is not necessary.
-One could imagine an example where each sub-domain supports elements which are translations/rescaling/rotations of an original master element and the angular resolution of rotations also refines as $k$ increases.
-The only important factor is the volume rescaling, which we have tried to emphasise in Definition 2.
+It now makes sense to consider $q>2$, even if Theorem 4 confirms that nothing is gained by doing so.
 
@@
 We have also added a new lemma (Lemma 7) to improve clarity, it serves as a midpoint between Theorem 4 and Appendix B.
-The text in Appendix B now makes clear reference to Lemma 7 as part of the proof of Theorem 4.
+The text in Appendix B also makes reference to Lemma 7 as part of the proof of Theorem 4.
 
@@
 
-	Old (15) is now (18). This is now emphasised in two places: Lemma 8 is referenced to confirm that $A$ is continuous, and we require that $|A|^2\nabla f$ is 1-Lipschitz.
+	Old (15) is now (18). The assumptions on $A$, including continuity on $\F H$, are now just above (18).
 
@@
 
-	As suggested, we now assume that $f$ is bounded from below and include a comment on weak-star continuity.
-The general argument has been re-worked to have an explicit sequence $\tilde w_k$ in $H$.
-We no longer rely on the existence of a minimising sequence (other than the explicit $\tilde w_k$).
+	As suggested, we now assume that $f$ is bounded from below and include a reference to justify that minimisers exist when $A^*$ maps into $C([0,1]^d)$.
+The general argument has been re-worked to have an explicit sequence $\tilde w_k$ in $H$ (approximately (19-24)).
+We no longer rely on the existence of a minimising sequence, other than the explicit choice of $\tilde w_k$ which we prove is minimising.
 
@@
 	This comment has been expanded upon in the text. The key point is the problem behaves much more like a finite-dimensional problem than infinite.
+	\begin{quote}
+		If this is the case, then $u^*\in \ell^2(\F R)$\edit{}{, indeed $\|u^*\|_{\ell^2}\leq\sqrt{m}\|u^*\|_{\ell^1}$.
+} This makes the \edit{analysis}{estimates of $a_E/a_U$} much simpler than in the continuous case\edit{}{ as we can stay in the finite-dimensional Hilbert-space setting}.
+	\end{quote}
 
@@
 	Old (25) is now (27). This refers to the derivative of $E$ on the subspace $\F U^n$, this is now clarified immediately above it in the text.
+	\begin{quote}
+		\edit{}{We consider the discretised function $E|_{\F{U}^n}\colon \F{U}^n\to\F R$ and its subdifferential $\partial_nE(\cdot) = \Pi_n\partial E(\cdot)$ on $\F{U}^n$.} 
+	\end{quote}
 
@@
 	Please can the reviewer clarify this point?
-The old (61-62) are now (63-64) which are equalities.
-There was a pair of inequalities (59-60), now (61-62), but they are simply statements of H\"older's inequality which we cannot expect to be sharp in general.
+The old (61-62) are now (60-61) which are equalities.
+There was a pair of inequalities (59-60), now (58-59), but they are simply statements of H\"older's inequality.
 
@@
 	You're quite right, we meant criticality in the discrete sense. This has been corrected.
+	\begin{quote}
+		Such refinement is necessary to avoid \edit{critical points}{discrete minimisers} of $E$ which are not global minimisers.
+	\end{quote}
 
@@
 	The old Lemma 14 is now Lemma 15.
-The domain is now assumed only to be bounded and $\tilde{\F{U}}$ is used as the subspace of $\F U$.
-We have removed the reference to orthonormal bases and the space $\F{U}^*$ which leads to a shorter and simpler result.
+The domain is now assumed only to be bounded and $\tilde{\F{U}}$ is used as the (finite dimensional) subspace of $\F U$.
+We have removed the reference to orthonormal bases and the space $\F{U}^*$, which leads to a shorter and simpler result.
 
@@
 
-	The old Lemma 15 is now Lemma 16. Again, you were quite right, we now make explicit use of Lemma 15. This combined with the removal of orthonormal bases leaves a much more direct proof.
+	The old Lemma 15 is now Lemma 16.
+Again, you were quite right, we now make explicit use of Lemma 15.
+This combined with the removal of orthonormal bases leaves a much more direct proof.
+Equation (115) has been removed.
+The closest approximation of the old (116) is now (105) which indeed considers all $u$ and $\tilde{u}$.
+The values of $C$ and a new $c_\alpha$ (the scaling constant) have been defined explicitly to aid clarity.
 
@@
 
-	The old Lemma 16 is now Lemma 17. We have clarified that $u^*$ is a minimiser of $E$. The third case has been removed, so the old (119) has also been removed.
+	The old Lemma 16 is now Lemma 17.
+We have clarified that $u^*$ is a minimiser of $E$ satisfying the appropriate approximation bounds.
+The third case has been removed, so the old (119) has also been removed.
 \end{enumerate}

### 2022-02-07 paper.tex
Update to response letter

@@
 \definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
-\newcommand{\edit}[3][1]{
+\newcommand{\edit}[3][1]{%
 	\IfEq{#1}{2}{\def\mysecondvar{}}{\def\mysecondvar{#2}}% hide the deleted text?
@@
 	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, however, our interpretation is relatively novel.
-In particular, we emphasise the infinite-dimensional setting where errors come from `discretisation' (rather than random or decaying errors in $\F H$), which enables two new perspectives:
+In particular, we emphasise the infinite-dimensional setting where errors come from `discretisation', rather than random or decaying errors in $\F H$, which enables two new perspectives:
 	\begin{itemize}
@@
 The exact rate can be computed by quantifying coercivity and regularity properties of $\op{E}$.
-If there isn't a minimiser in $\F H$, then this rate is strictly smaller than $n^{-2}$.
+If there isn't a minimiser in $\F H$, then this rate is strictly slower than $n^{-2}$.
 
@@
 Adaptive finite-element methods are known to improve the efficiency of, for example, approximating the solutions of PDEs.
-Our analytical results show how to combine such tools with FISTA (without reducing the guaranteed rate of convergence), and our numerical results confirm much improved time and computer memory efficiency in the Lasso example (Section~\ref{sec: Lasso definition}).
+Our analytical results show how to combine such tools with FISTA without reducing the guaranteed rate of convergence, and our numerical results confirm much improved time and computer memory efficiency in the Lasso example (Section~\ref{sec: Lasso definition}).
 	\end{itemize}
 	All the examples in this work, discussed from Section~\ref{sec: general examples} onward, consider $\{\var0\in\F H\st \op{E}(\var0)<\infty\}$ to be contained in some ambient Banach space $\F{U}$.
-The idea is that FISTA provides a minimising sequence in $\F H\cap\F U$, but further properties like rate of convergence (of $\op{E}$ or iterates) must come from the topology of $\F{U}$.
+The idea is that FISTA provides a minimising sequence in $\F H\cap\F U$, but further properties like rate of convergence (of $\op{E}$ or the iterates) must come from the topology of $\F{U}$.
 It will not be necessary for $\F H\hookrightarrow\F U$ to be a continuous embedding, nor in fact the full inclusion $\F H\subset\F U$.
-
-	\todo{Note to self: It is probably not very hard to imagine examples outside of a Banach space, you just need to find a metric space without the linear scaling.
-Examples outside of a metric space would be much harder.}
 }
@@
 Of particular note, our stability estimate for FISTA  in Theorem~\ref{thm: mini FISTA convergence} is very similar to \cite[Prop 2]{Schmidt2011} and \cite[Prop 3.3]{Aujol2015}.
-This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations.
+This is then used to analyse the convergence properties in our more general Banach space setting, but where all sources of inexactness come from subspace approximations.
 The ideas in \cite{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\op{g}$.
@@
 	\begin{adaptiveStep}\label{step: step 4 sufficiently fast}
-		In Step~\ref{step: step 3 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor.
+		In Step~\ref{step: step 3 convergence bound} we develop a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor.
 In particular, it is equivalent to either run Algorithm~\ref{alg: refining FISTA} for $N$ iterations, or the classical FISTA algorithm for $N$ iterations on the fixed subset $\F{U}^N$.
@@
 		Theorem~\ref{thm: stronger exponential FISTA convergence} shows that a sufficient condition is
-		$$\var0_{n_k-1}\in\F{U}^{n_k}\cap\F{U}^{n_k+1}\cap\ldots\cap\F{U}^{n_{k+1}-1}\edit{.}{, \qquad \norm{\var0_{n_k-1}} \lesssim \aU^k, \quad\text{and}\quad \op{E}_0(\var0_{n_k-1}) \lesssim \aE^{-k}}$$
+		$$\var0_{n_k-1}\in\F{U}^{n_k}\cap\F{U}^{n_k+1}\cap\ldots\cap\F{U}^{n_{k+1}-1}\edit{}{, \qquad \norm{\var0_{n_k-1}} \lesssim \aU^k, \quad\text{and}\quad \op{E}_0(\var0_{n_k-1}) \lesssim \aE^{-k}}.$$
 		Convergence is most stable if the approximation spaces $\F{U}^n$ satisfy a monotone inclusion, breaking the monotonicity requires more care.
@@
 	\noindent The proof is given in Theorem~\ref{app:thm: mini FISTA convergence}.
-This result is the key approximation for showing convergence of FISTA with growing subsets.
+This result is the key approximation for showing convergence of FISTA with changing subsets.
 In the classical setting, we have $\F{U}^n=\F H$, $\var2_n=\var2_0\in\argmin_{\var0\in\F H}\op{E}(\var0)$ and the extra terms on the right-hand side collapse to 0.
@@
 	\end{equation}
-	uniformly in $n$.
+	uniformly for $n\in[n_k,n_{k+1})$.
 If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of subsets.
@@
 	\begin{itemize}
-		\item The convergence guarantee for $N$ iterations of classical FISTA in the space $\F{U}^N$ is 
+		\item The convergence guarantee for $N\in[n_K,n_{K+1})$ iterations of classical FISTA in the space $\F{U}^N$ is 
 		$$ \op{E}_0(\var0_N) \lesssim \frac{\norm{\var0_0-\edit{\argmin_{\var0\in\F{U}^N}\op{E}(\var0)}{\tilde{\var2}_K}}^2}{N^2} + \min_{\var0\in\F{U}^N}\op{E}_0(\var0) \lesssim \frac{\aU^{2K}}{N^2} + \aE^{-K}.$$
@@
 			Suppose $\var0_n$ and $n_k$ are sequences satisfying 
-			$$\forall n_K\leq N< n_{K+1},\ \op{E}_0(\var0_N) \lesssim \frac{\aU^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \aE^K\aU^{2K},$$
+			$$\forall N\in[n_K, n_{K+1}),\ \op{E}_0(\var0_N) \lesssim \frac{\aU^{2K}}{N^2} \qquad\text{where} \qquad  n_K^2\gtrsim \aE^K\aU^{2K},$$
 			then 
@@
 	\end{theorem}
-	\noindent \edit{}{Analytically, this theorem gives new rates of convergence for FISTA when the minimiser is not achieved in the Hilbert space.
-Indeed for the original algorithm ($\F{U}^n=\F H$), if $\var0=0$ for simplicity and $(\tilde{\var2}_k)_{k\in\F N}$ is \emph{any} \aUaE\ exists, the result of Lemma~\ref{thm: mini exponential FISTA convergence} is
+	\noindent \edit{}{Analytically, this theorem gives new rates of convergence for FISTA when the minimiser is not achieved in $\F H$.
+Indeed for the original algorithm ($\F{U}^n=\F H$), if $\var0_0=0$ for simplicity and $(\tilde{\var2}_k)_{k\in\F N}$ is \emph{any} \aUaE\ exists, the result of Lemma~\ref{thm: mini exponential FISTA convergence} is
 	\begin{equation}\label{eq: slow exact FISTA}
@@
 	\end{equation}
-	In this sense, we could say that $\op{E}$ converges at the rate $N^{-2(1-\kappa)}$ if and only if such a sequence exists. Nothing is lost (or gained) by choosing $\F{U}_n\subsetneq\F H$.}
+	In this sense, we could say that $\op{E}$ converges at the rate $N^{-2(1-\kappa)}$ if and only if such a sequence exists.
+Nothing is lost (or gained) analytically by choosing $\F{U}_n\subsetneq\F H$.}
 
@@
 
-	Lemma~\ref{thm: sufficiently fast} gives a sufficient condition on $n_k$ for converging at the rate $O(N^{2(\kappa-1)})$, but it is not necessary. Indeed for $n\leq n_k$ the result shows 
-	$$\op{E}_0(\var0_n) \geq \min_{\var0\in\F{U}^n}\op{E}_0(\var0) = O(\aE^{-k}) = O(n^{2(\kappa-1)})$$
+	Lemma~\ref{thm: sufficiently fast} gives a sufficient condition on $n_k$ for converging at the rate $O(N^{2(\kappa-1)})$, but it is not necessary. Indeed for $n\leq n_k$ we have
+	$$\op{E}_0(\var0_n) \geq \min_{\var0\in\F{U}^n}\op{E}_0(\var0) = O(\aE^{-k}) = O(n^{2(\kappa-1)}),$$
 	which suggests that to converge faster than $n^{2(\kappa-1)}$ requires choosing smaller $n_k$.
@@
 	\noindent The proof is given in Theorem~\ref{app:thm: stronger exponential FISTA convergence}.
-If we directly compare Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence}, we note that the convergence rate is the same in both theorems but the price for better adaptivity (i.e.
+If we directly compare Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence}, \edit{}{both are a direct result of Lemma~\ref{thm: sufficiently fast} assuming a specific choice of $n_k$ or $\tilde{\var2}_k$ respectively.} We note that the convergence rate is the same in both theorems but the price for better adaptivity (i.e.
 only an upper bound on $n_k$) is a slightly weaker stability guarantee (now convergence of $\min_{n\leq N}\op{E}_0(\var0_n)$).
@@
 
-	To enable a more practical implementation of Theorem~\ref{thm: stronger exponential FISTA convergence}, the following lemma describes several refinement time strategies which provide sufficient condition for $\op{E}_0(\edit{\var0_n}{\tilde{\var2}_k}) \lesssim \aE^{-k}$.
+	To enable a more practical implementation of Theorem~\ref{thm: stronger exponential FISTA convergence}, the following lemma describes several refinement strategies which provide sufficient condition for $\op{E}_0(\edit{\var0_n}{\tilde{\var2}_k}) \lesssim \aE^{-k}$.
 	\begin{lemma}\label{thm: practical refinement criteria}
@@
 			\begin{enumerate}\setcounter{enumi}{2}
-				\item Small continuous gradient refinement: $ \inf_{\var1\in\partial\op{E}(\edit{\var0_k}{\tilde{\var2}_k})}\edit{\Norm{\var1}_*}{\sup_{\var0\in\F{U}} \frac{|\IP{\var1}{\var0}|}{\Norm{\var0}}}\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
+				\item Small continuous gradient refinement: $\edit{}{\sup_{\var0\in\F{U}}} \inf_{\var1\in\partial\op{E}(\edit{\var0_k}{\tilde{\var2}_k})}\edit{\Norm{\var1}_*}{} \frac{|\IP{\var1}{\var0}|}{\Norm{\var0}}\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
 				\item Small discrete gradient refinement: $\op{E}_0(\edit{\tilde{\var2}_k}{\tilde{\F{U}}^k})\leq \vars1\aE^{-k}$ and $\sup_{\var0,\tilde{\var2}\in \tilde{\F{U}}^k}\inf_{\var1\in\partial\op{E}(\edit{\var0_k}{\tilde{\var2}_k})}\frac{|\IP{v}{\var0-\tilde{\var2}}|}{\Norm{\var0-\tilde{\var2}}}\leq \vars1\aE^{-k}$ for all $k\in\F N$, some $\vars1>0$.
@@
 }$\F{U}\subset L^q(\Domain)$\edit{}{)} for some \edit{}{$q\in[1,\infty]$ and }connected, bounded domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{}.
-We say that \edit{$\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$}{a collection of subdomains $\F M$} is a \emph{mesh} if
+We say that \edit{$\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$}{a collection $\F M$} is a \emph{mesh} if
 		$$\edit{\domain_i^k\subset}{\bigcup_{\domain\in\F M}\domain = } \Domain \qquad\text{and} \qquad |\edit{\domain_i^k\cap\domain^k_j}{\domain\cap\domain'}| = 0\qquad \text{for all \edit{$i$ and $j$}{$\domain,\domain'\in\F M,\ \domain\neq\domain'$}.}$$
@@
 $$
-		Fix $\meshsize\in(0,1)$, linear subspaces $\tilde{\F{U}}^k\subset\F{H}$ and consistent meshes $\F M^k$.
+		Fix $\meshsize\in(0,1)$, linear subspaces $\tilde{\F{U}}^k\subset\F{H}$, and consistent meshes $\F M^k$.
 We say that the sequence $(\tilde{\F{U}}^k)_{k\in\F N}$ is an \emph{$\meshsize$-refining sequence of finite element spaces} if there exists $c_{\vars0}>0$ such that:
@@
 Wavelets with a compactly supported basis behave like a multi-resolution finite element space as there is always overlap in the supports of basis vectors.
-Similarly, a Fourier basis does satisfy the scaling properties but each basis vector has global support.
+Similarly, a Fourier basis does satisfy the scaling properties, but each basis vector has global support.
 Both of these exceptions are important and could be accounted for with further analysis but we focus on the more standard finite element case.
-	\edit{The following theorem shows that all finite element spaces achieve the same basic rates of convergence in Algorithm~\ref{alg: refining FISTA}, depending on the particular properties of $\Norm\cdot$ and $\op{E}$.}{In order to align these discretisation estimates with the assumptions of Theorems~\ref{thm: exponential FISTA convergence} and \ref{thm: stronger exponential FISTA convergence}, we make the following observation.
+	\edit{The following theorem shows that all finite element spaces achieve the same basic rates of convergence in Algorithm~\ref{alg: refining FISTA}, depending on the particular properties of $\Norm\cdot$ and $\op{E}$.}{In order to align these discretisation properties with the assumptions of Theorems~\ref{thm: exponential FISTA convergence} and \ref{thm: stronger exponential FISTA convergence}, we make the following observation.
 	\begin{lemma}\label{thm: pq to p'q'}
@@
 		Suppose $\F H= L^2(\Domain)$ for some connected, bounded domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{} and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$.
-\edit{If}{For $p\geq0$ and $\meshsize\in(0,1)$, if} $(\tilde{\F{U}}^k)_{k\in\F N}$ is a sequence of $\meshsize$-refining finite element spaces of order $p$, then \edit{}{$(\tilde{\var2}_k)_{k\in\F N}$ is an \aUaE\ for}
+\edit{If}{For $p\geq0$ and $\meshsize\in(0,1)$, if} $(\tilde{\F{U}}^k)_{k\in\F N}$ is an $\meshsize$-refining sequence of finite element spaces of order $p$, then \edit{}{$(\tilde{\var2}_k)_{k\in\F N}$ is an \aUaE\ for}
 		\begin{align*}
@@
 We consider three forms  which will be referred to as the continuous, countable, and discrete problem depending on whether the space $\F{U}$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or \edit{finite dimensional}{$\R^M$} respectively.
-\edit{}{Let $\A\colon\F{U}\cup\F{H}\to\R^m$ be a linear operator represented by the kernels $\psi_j\in\F{U}^*\cap\F{H}$ such that
+\edit{}{Let $\A\colon\F{U}\cap\F{H}\to\R^m$ be a linear operator represented by the kernels $\psi_j\in\F{H}$ such that
 	\begin{equation}\label{eq: kernels of A}
-		\forall \var0\in\F{U}\cup\F{H},\ j=1,\ldots,m,\qquad (\A\var0)_j = \IP{\psi_j}{\var0}.
-	\end{equation}
-	In particular, for the discrete (respectively countable) case we have $\psi_j\in\R^M$ (resp.
-$\ell^2(\R)$).
-In the continuous case we will require the additional smoothness $\psi_j\in C^1([0,1]^d)$.
-In Section~\ref{sec: smoothing operators} we will formally define and estimate several operator semi-norms for $\A$ of this form, for example Lemma~\ref{thm: norm bound L2} confirms that $\A$ is continuous on $\F{H}$ (i.e.
-$\norm{\A}<\infty$).} In each case, the energy \edit{can be}{we consider is} written as
+		\forall \var0\in\F{U}\cap\F{H},\ j=1,\ldots,m,\qquad (\A\var0)_j = \IP{\psi_j}{\var0}.
+	\end{equation}
+	In the continuous case we will assume the additional smoothness $\psi_j\in C^1([0,1]^d)$.
+In Section~\ref{sec: smoothing operators} we will formally define and estimate several operator semi-norms for $\A$ of this form, for example Lemma~\ref{thm: norm bound L2} confirms that $\A$ is continuous on $\F{H}$ (without loss of generality $\norm{\A}\leq 1$).} In each case, the energy \edit{can be}{we consider is} written as
 	\begin{equation}\label{eq: Lasso energy}
@@
 	for some \edit{$\A\colon \F{U}\to\R^m$ and }{}$\mu>0$ where $\Norm\cdot=\norm\cdot_1$.
-We assume $\op{f}\in C^1(\R^m)$ is convex\edit{ with}{, bounded from below, and} $\edit{\nabla\op{f}}{(\norm{\A}^2\nabla\op{f})}$ is 1-Lipschitz\edit{, and in the continuous-space case we also require $\A^*\colon\R^m\to C^1([0,1]^d)$}{}.
-	Let $\var0^*\in\argmin_{\var0\in\F{U}}\op{E}(\var0)$\edit{}{, which is non-empty so long as $\psi_j\in C([0,1]^d)$, i.e. $\A$ is sequentially weak-star continuous}.
+We assume $\op{f}\in C^1(\R^m)$ is convex\edit{ with}{, bounded from below, and} $\nabla\op{f}$ is 1-Lipschitz\edit{, and in the continuous-space case we also require $\A^*\colon\R^m\to C^1([0,1]^d)$}{}.
+	Let $\var0^*\in\argmin_{\var0\in\F{U}}\op{E}(\var0)$\edit{}{, which is non-empty so long as $\psi_j\in C([0,1]^d)$, see the proof of \cite[Prop. 3.1]{Bredies2013} when $\op{f}$ is quadratic.}.
 
@@
 		\\&\leq \ip{\nabla \op{f}(\A\edit{\var2}{\tilde{\var2}_k}-\data)}{\A(\edit{\var2}{\tilde{\var2}_k}-\var0^*)}
-		\\&\leq\left[\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2} + \edit{}{\norm{\A}^{-2}}\norm{\A(\edit{\var2}{\tilde{\var2}_k}-\var0^*)}_{\ell^2}\right]\norm{\A(\edit{\var2}{\tilde{\var2}_k}-\var0^*)}_{\ell^2}.
+		\\&\leq\left[\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2} + \norm{\A(\edit{\var2}{\tilde{\var2}_k}-\var0^*)}_{\ell^2}\right]\norm{\A(\edit{\var2}{\tilde{\var2}_k}-\var0^*)}_{\ell^2}.
 	\end{align}
@@
 	}{%
-	For the other term, note that for all $\vec{r}\in\R^m$, denote $\varphi\coloneqq\A^*\vec{r}$, then 
-	\begin{multline}
+	For the other term, for all $\vec{r}\in\R^m$ denote $\varphi\coloneqq\A^*\vec{r}$, then note that
+	\begin{equation}
 		\ip{\vec r}{\A(\tilde{\var2}_k-\var0^*)} = \IP{\varphi}{\tilde{\var2}_k-\var0^*} = 
 		\sum_{\domain\in\F M^k}\int_\domain \varphi(\vec{x}) \diff[\tilde{\var2}_k-\var0^*] 
-		= \sum_{\domain\in\F M^k}|\domain|^{-1}\iint_\domain [\varphi(\vec{x}) - \varphi(\vec{y})] \diff\vec{x}\diff\var0^*(\vec{y}) 
-		\\\leq \max_{\domain\in\F M^k}\op{diam}(\domain)\norm{\nabla\varphi}_\infty\Norm{\var0^*}.
-	\end{multline}
-	This gives the estimate
+		= \sum_{\domain\in\F M^k}|\domain|^{-1}\iint_{\domain^2} [\varphi(\vec{x}) - \varphi(\vec{y})] \diff\vec{x}\diff\var0^*(\vec{y}).
+	\end{equation}
+	With the pointwise bound $|\varphi(\vec{x}) - \varphi(\vec{y})|\leq \op{diam}(\domain)\norm{\nabla\varphi}_{L^\infty} = \sqrt{d}2^{-k}\norm{\nabla[\A^*\vec r]}_{L^\infty}$, we deduce the estimate
 	\begin{equation}
@@
 	\end{equation}
-	This last term we denote the semi-norm $|\A^*|_{\ell^2\to C^1}$ which is shown to be finite in Section~\ref{sec: smoothing operators}.
-For now, assuming that $|\A^*|_{\ell^2\to C^1}<\infty$, we conclude that $\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*)\lesssim 2^{-k}$.}
-
-	This computation confirms two things, firstly that the scaling constant is indeed $\aE = 2$, and secondly that the required smoothness to achieve a good rate with Algorithm~\ref{alg: refining FISTA} is that $\A^*\colon\R^m\to C^1(\Domain)$ is a bounded operator.
+	In Lemma~\ref{thm: norm bound smoothness} we will show that this last term, which we denote the semi-norm $|\A^*|_{\ell^2\to C^1}$, is bounded by $\sqrt{m}\max_{j\in[m]}\norm{\nabla\Psi_j}_\infty$.
+We conclude that $\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*)\lesssim 2^{-k}$.}
+	In particular, this computation confirms two things.
+Firstly that the scaling constant is $\aE = 2$, and secondly that the required smoothness to achieve a good rate with Algorithm~\ref{alg: refining FISTA} is that $\A^*\colon\R^m\to C^1(\Domain)$ is a bounded operator.
 This accounts for using the weaker topology of $\C M(\Domain)$ rather than $L^1(\Domain)$.
-In Section~\ref{sec: smoothing operators} we will show two practical examples where this seminorm is accurately computable.
+\edit{In Section~\ref{sec: smoothing operators} we will show two practical examples where this seminorm is accurately computable.}{}
 
@@
 infinite vectors with finitely many non-zeros.
-The key change in analysis from the continuous case is $\norm{\var0^*}<\infty$, which leads to $\aU=1$ and the expected optimal rate of $n^{-2}$, independent of $\aE$ or any additional properties of $\A$.
-The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence} hold trivially.
+The key change in analysis from the continuous case is $\norm{\var0^*}<\infty$, so $\aU=1$ and the expected rate of $n^{-2}$, independent of $\aE$ or any additional properties of $\A$.
+The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$, the remaining conditions of Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence} hold trivially.
 
@@
 	Let $\tens{\Pi}_n\colon\F H\to\F{U}^n$ denote the orthogonal projection.
-\edit{}{We consider the discretised function $\op{E}|_{\F{U}^n}\colon \F{U}^n\to\R$ and its subdifferential $\partial_n\op{E}(\cdot) = \tens{\Pi}_n\partial\op{E}(\cdot)$.} In our case, the \edit{discretised function $\var0\mapsto\op{E}(\tens{\Pi}_n\var0)$}{behaviour of $\op{E}|_{\F{U}^n}$} is equivalent to replacing $\var0$ with $\tens{\Pi}_n\var0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.
+\edit{}{We consider the discretised function $\op{E}|_{\F{U}^n}\colon \F{U}^n\to\R$ and its subdifferential $\partial_n\op{E}(\cdot) = \tens{\Pi}_n\partial\op{E}(\cdot)$ on $\F{U}^n$.} In our case, the \edit{discretised function $\var0\mapsto\op{E}(\tens{\Pi}_n\var0)$}{behaviour of $\op{E}|_{\F{U}^n}$} is equivalent to replacing $\var0$ with $\tens{\Pi}_n\var0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.
 
@@
 	\begin{align}
-		\Norm{\partial_n \op{E}(\var0_n)}_* &= \max_{\vec{x}\in\Domain}\min\left\{|\var1| \st \var1\in \tens{\Pi}_n\A^*\nabla\op{f}(\A\var0_n-\data)(\vec{x}) +  \mu\tens{\Pi}_n\sign(\var0_n(\vec{x}))\right\}
+		\Norm{\partial_n \op{E}(\var0_n)}_* &= \max_{\vec{x}\in\Domain}\min_{\var1}\left\{|\var1| \st \var1\in \tens{\Pi}_n\A^*\nabla\op{f}(\A\var0_n-\data)(\vec{x}) +  \mu\tens{\Pi}_n\sign(\var0_n(\vec{x}))\right\}
 		\\&= \max_{\vec{x}\in\Domain}\begin{cases}
@@
 		\Norm{\partial\op{E}(\var0_n)}_* &= \max\left(\max_{i\in J_n}|[\partial\op{E}(\var0_n)]_i|,\ \sup_{i\notin J_n} |[\partial\op{E}(\var0_n)]_i|\right)
-		\\&= \max\left(\Norm{\partial_n\op{E}(\var0_n)}_*,\ \sup_{i\notin J_n} |[\A^*\vec{\varphi}_n]_i|-\mu\right)
+		= \max\left(\Norm{\partial_n\op{E}(\var0_n)}_*,\ \sup_{i\notin J_n} |[\A^*\vec{\varphi}_n]_i|-\mu\right)
 		\\ \Norm{\A^*\vec{\varphi}_n}_* &= \max\left(\max_{i\in J_n}|[\A^*\vec{\varphi}_n]_i|,\ \sup_{i\notin J_n} |[\A^*\vec{\varphi}_n]_i|\right)
-		\\ &= \max\left(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*,\ \sup_{i\notin J_n} |[\A^*\vec{\varphi}_n]_i|\right).
+		\hspace{19pt}= \max\left(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}_n}_*,\ \sup_{i\notin J_n} |[\A^*\vec{\varphi}_n]_i|\right).
 	\end{align}
@@
 	\end{align}
-	If these quantities are not analytically tractable then we use the mesh $\F M^n$ corresponding to $\F{U}^n$ to decompose the bounds:
+	If these quantities are not analytically tractable, then we use the mesh $\F M^n$ corresponding to $\F{U}^n$ to decompose the bounds:
 	\begin{align}
@@
 	\end{align}
-	Now, both estimates rely on cell-wise supremum norms of $\A^*\vec{\varphi}_n$ which we have assumed is sufficiently smooth.
-We will therefore use a cell-wise Taylor expansion to provide a simple and accurate estimate.
-For instance, let $\vec{x}_i$ be the midpoint of the square $\domain_i^n$, then
+	Now, both estimates rely on pixel-wise supremum norms of $\A^*\vec{\varphi}_n$ which we have assumed is sufficiently smooth.
+We will therefore use a pixel-wise Taylor expansion to provide a simple and accurate estimate.
+For instance, let $\vec{x}_i$ be the midpoint of the pixel $\domain_i^n$, then
 	\begin{equation}\label{eq: Taylor approximation}
@@
 	Heuristically, we will use strong convexity of $\op{E}^*$ and smoothness of $\A^*$ to quantify the statement:
-	$$ \text{if}\quad \op{E}(\var0_n) + \op{E}^*(\vars2_0 \vec{\varphi}_n) \approx 0 \quad \text{then}\quad \left\{\vec{x}\st \mu - |[\A^*\vec{\varphi}_n](\vec{x})|\ll 1\right\} \subset\{\vec{x} \st \var0^*(\vec{x})=0\}.$$
+	$$ \text{if}\quad \op{E}(\var0_n) + \op{E}^*(\vars2_0 \vec{\varphi}_n) \approx 0 \quad \text{then}\quad \left\{\vec{x}\st |[\A^*\vec{\varphi}_n](\vec{x})|\ll \mu\right\} \subset\{\vec{x} \st \var0^*(\vec{x})=0\}.$$
 	Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex \cite[Chapter 10, Thm.
@@
 	\subsection{Operator norms}\label{sec: smoothing operators}
-	For numerical implementation of \eqref{eq: Lasso energy}, we are required to accurately estimate several operator norms of $\A$.
-For $\op{f}$ to be 1-Lipschitz we must divide by $|\A\A^*|_{\ell^2\to\ell^2}$, and the adaptivity described in Sections~\ref{sec: continuous lasso rate}, \ref{sec: bound continuous}, and~\ref{sec: support detection} requires the values of $|\A^*|_{\ell^2\to L^\infty}$, $|\A^*|_{\ell^2\to C^1}$, and $|\A^*|_{\ell^2\to C^2}$.
+	For numerical implementation of \eqref{eq: Lasso energy}, we are required to accurately estimate several operator norms of $\A$\edit{}{ of the form in \eqref{eq: kernels of A}.
+In particular, there are kernels $\psi_j\in\F H$ such that $(\A \var0)_j=\IP{\psi_j}{\var0}$ for each $j\in[m]$}.
+	\edit{For $\op{f}$ to be 1-Lipschitz we must normalise by}{Verifying that $\norm{\A}\leq1$ can be performed by computing} $|\A\A^*|_{\ell^2\to\ell^2}$, and the adaptivity described in Sections~\ref{sec: continuous lasso rate}, \ref{sec: bound continuous}, and~\ref{sec: support detection} requires the values of $|\A^*|_{\ell^2\to L^\infty}$, $|\A^*|_{\ell^2\to C^1}$, and $|\A^*|_{\ell^2\to C^2}$.
 The aim for this section is to provide estimates of these norms and seminorms for the numerical examples presented in Section~\ref{sec: numerics}.
 
+	\edit{
 	We start by specifying the structure of $\A$.
@@
 In this form, the adjoint can be written precisely, $\A^*\colon\R^m\to \F H$ by
-	\begin{equation}
-		[\A^*\vec{r}](\vec{x}) = \sum_{j=1}^m r_j\psi_j(\vec{x}) \qquad \text{ for all }\vec{x}\in\Domain,\ \vec{r}\in\R^m.
-	\end{equation}
-
-	The following lemma allows for exact computation of the operator norm of $\A$, as needed to ensure that $\op{f}$ is 1-Lipschitz.
+	\\$ [\A^*\vec{r}](\vec{x}) = \sum_{j=1}^m r_j\psi_j(\vec{x}) \qquad \text{ for all }\vec{x}\in\Domain,\ \vec{r}\in\R^m.$}{}
+
+	The following lemma allows for exact computation of the operator norm of $\A$\edit{, as needed to ensure that $\op{f}$ is 1-Lipschitz}{}.
 	\begin{lemma}\label{thm: norm bound L2}
@@
 	If $\norm{\A^*\A}$ is not analytically tractable, then Lemma~\ref{thm: norm bound L2} enables it to be computed using standard finite dimensional methods.
-The operator $\A\A^*$ is always finite dimensional and can be computed without discretisation error.
+The operator $\A\A^*$ is always finite dimensional, and can be computed without discretisation error.
 
@@
 
-	The examples in Section~\ref{sec: numerics} require explicit computations of the expressions in Lemmas~\ref{thm: norm bound smoothness} and~\ref{thm: norm bound L2}.
-These computations are provided in Theorem~\ref{thm: norm bound examples}
+	The examples in Section~\ref{sec: numerics} require explicit computations of the expressions in Lemmas~\ref{thm: norm bound L2} and~\ref{thm: norm bound smoothness}.
+These computations are provided\edit{}{\ in the appendix,} Theorem~\ref{thm: norm bound examples}.
 
@@
 	The next example is 2D reconstruction from Radon or X-ray data with wavelet-sparsity and a robust data fidelity.
-As the forward operator is not sufficiently smooth, we must optimise in $\ell^1(\R)$ which naturally leads to the choice of a wavelet basis.
+As the forward operator is not sufficiently smooth, we must optimise in $\ell^1(\R)$, which naturally leads to the choice of a wavelet basis.
 
@@
 
-	The code to reproduce these examples can be found on github\footnote{\href{https://github.com/robtovey/2020SpatiallyAdaptiveFISTA}{https://github.com/robtovey/2020SpatiallyAdaptiveFISTA}}.
+	The code to reproduce these examples can be found online\footnote{\href{https://github.com/robtovey/2020SpatiallyAdaptiveFISTA}{https://github.com/robtovey/2020SpatiallyAdaptiveFISTA}}.
 
@@
 The idea is that for a fixed mesh, the kernels of $\A$ are expanded to first order on each pixel and a particular first order basis is also chosen \cite{Ekanadham2011,Duval2017b}.
-If $\var0^*$ has only one Dirac spike in each pixel, then the zeroth order information should correspond to the mass of the spike and additional first order information should determine the location.
+If $\var0^*$ has only one Dirac spike in each pixel, then the zeroth order information should correspond to the mass of the spike, and additional first order information should determine the location.
 
@@
 We choose subspaces $\F{U}^n$ to approximately enforce
-	\begin{equation}
+	\begin{equation}\label{eq: less than double gap bound}
 		\op{E}(\var0_n) + \op{E}^*(\vars2_0\vec{\varphi}_n) \leq 2(\op{E}(\var0_n) + \op{E}^*(\vars2\vec{\varphi}_n)),
@@
 The adaptive discretisation is started with one pixel and limited to 128, 256, or 512 pixels while the fixed and CBP discretisations have uniform discretisations with the maximum number of pixels.
-We observe:
+The main observations are:
 	\begin{itemize}
@@
 		\item With Fourier kernels the uniform piecewise constant discretisation is more efficient than CBP but in the Gaussian case this is reversed.
-This suggests that the performance of CBP depends highly on the smoothness of $\A$.
+This suggests that the performance of CBP depends on the smoothness of $\A$.
 		\item The discrete gaps for non-adaptive optimisation behave as is common for FISTA, initial convergence is polynomial until a locally linear regime activates \cite{Tao2016}.
 CBP is always slower to converge than the piecewise constant discretisation.
-		\item The adaptive refinement criterion succeeds in keeping the continuous/discrete gaps close for all $n$.
+		\item The adaptive refinement criterion succeeds in keeping the continuous/discrete gaps close for all $n$\edit{}{, i.e. \eqref{eq: less than double gap bound}}.
 	\end{itemize}
@@
 Fig.~\ref{fig: convergence with method} compares the discrete gaps because it is the accurate metric for fixed discretisations, and for the adaptive discretisation it should also be an accurate predictor of the continuous gap.
-
-	The key observations are:
+	The main observations are:
 	\begin{itemize}
@@
 		\item During the initial `slow' phase, adaptive and fixed discretisations appear to achieve very similar (discrete) convergence rates.
-The coarse-to-fine adaptivity is not slower than fixed discretisations in this regime\edit{}{, consistent with \eqref{eq: slow exact FISTA}}.
+The coarse-to-fine adaptivity is not slower than fixed discretisations in this regime.
 		\item Lemma~\ref{thm: practical refinement criteria} accurately predicts the $\frac1n$ rate of the adaptive methods, mirrored in the fixed discretisations.
-This suggests that high-resolution discretisations are also initially limited by this $\frac1n$ rate before entering the asymptotic regime.
-		\item The fastest FISTA algorithm is consistently the greedy variant, although $a=20$ is very comparable.
+This suggests that high-resolution discretisations are also initially limited by this $\frac1n$ rate before entering the asymptotic regime\edit{}{, consistent with \eqref{eq: slow exact FISTA}}.
+		\item The fastest FISTA stepsize choice is consistently the greedy variant, although $a=20$ is very comparable.
 	\end{itemize}
@@
 	Motivated by the findings in Fig.~\ref{fig: convergence with method}, we now look more closely at the performance of the $a=20$ and the greedy FISTA schemes.
-We have analytical results for the former but the latter typically performs the best for non-adaptive optimisation and is never worse than $a=20$ in the adaptive setting.
-The question is whether it is faster/more efficient to use the proposed adaptive scheme or to use a classical scheme at sufficiently high uniform resolution.
+We have convergence results for the former, but the latter typically performs the best for non-adaptive optimisation and is never worse than $a=20$ in the adaptive setting.
+The question is whether it is faster/more efficient to use the proposed adaptive scheme, or to use a classical scheme at sufficiently high uniform resolution.
 The fixed discretisations use 1024 pixels (i.e.
@@
 	\end{equation}
-	for $i=1,\ldots,50$, $I=1,\ldots,100$.
-	This is not exactly in the form analysed by Theorem~\ref{thm: norm bound examples}, however only the sets $\{\F{X}^I_i\st i\in[100]\}$ for each $I$ are disjoint, therefore we apply Theorem~\ref{thm: norm bound examples} block-wise to estimate
+	for $i=\in[100]$, $I\in[50]$.
+	This is not exactly in the form analysed by Theorem~\ref{thm: norm bound examples}, only the sets $\{\F{X}^I_i\st i\in[100]\}$ for each $I$ are disjoint, therefore we apply Theorem~\ref{thm: norm bound examples} block-wise to estimate
 	\begin{equation}
@@
 	for all $\F{X}\supset \supp(w_j)$.
-	In the case of the Radon transform, we can compute the left-hand side explicitly for the finitely many $j\in J_n$ but we wish to use the right-hand side in a structured way to avoid computing the infinitely many $j\notin J_n$.
+	In the case of the Radon transform, we can compute the left-hand side explicitly for the finitely many $j\in J_n$, but we wish to use the right-hand side in a structured way to avoid computing the infinitely many $j\notin J_n$.
 To do this, we will take a geometrical perspective on the construction of wavelets to view them in a tree format.
@@
 Lines indicate the median value over 3020 STORM frames.
-Shaded regions indicate the \SIrange{25}{75}{\percent} inter-quartile range.
+Shaded regions indicate the \SIrange{25}{75}{\percent} interquartile range.
 Pixel width is scaled $[0,1]$ rather than $[0,\SI{6.4}{\micro\meter}]$.}\label{fig: STORM convergence}
@@
 This rate also seems to be a good predictor for all variants of FISTA tested, although this is yet to be proven.
-Surprisingly, even the classical methods with a fixed discretisation initially seem limited to the slower adaptive rate for small $n$.
+Even the classical methods with a fixed discretisation\edit{}{ are} initially\edit{ seem}{} limited to the slower adaptive rate for small $n$.
 
@@
 		\end{equation}
-		This is almost in the desired form, however, we would like to flip the roles of $\var1_n$/$\var2_n$ in the final inner product term. Re-writing the right-hand side gives
+		The final step is to flip the roles of $\var1_n$/$\var2_n$ in the final inner product term. Re-writing the right-hand side gives
 		\begin{equation}
@@
 		\end{description}
-		In both cases, the induction on $\norm{\var1_{n_{K+1}-1}-\tilde{\var2}_K}$ holds for all $K$ and we have 
-		\begin{equation}
-			t_N^2\op{E}_0(\var0_N) \leq \frac{C_2^2}{2}\aU^{2K}
-		\end{equation}
-		for all $N<n_K-1$.
+		In both cases, the induction on $\norm{\var1_{n_{K+1}-1}-\tilde{\var2}_K}$ holds for all $K$, and we have $t_N^2\op{E}_0(\var0_N) \leq \frac12C_2^2\aU^{2K}$ for all $N<n_K-1$.
 		\qed\end{proof}
@@
 				\item[(2)] $\op{E}_0(\tilde{\var2}_k)\leq \op{E}_0(\tilde{\F{U}}^k) + \vars1\aE^{-k} \leq (\aE +1)\beta\aE^{-k}$, so $C=(\aE +1)\beta$ suffices.
-				\item[(3)] $\op{E}(\tilde{\var2}_k)-\op{E}(\var0)\leq \inf_{\var1\in\partial\op{E}(\tilde{\var2}_k)}\leq 2R\vars1\aE^{-k}$ for any $\var0\in\F{U}$ with $\Norm{\var0}\leq R$.
+				\item[(3)] $\op{E}_0(\tilde{\var2}_k)-\op{E}_0(\var0)\leq \inf_{\var1\in\partial\op{E}(\tilde{\var2}_k)}\IP{\var1}{\tilde{\var2}_k-\var0}\leq 2R\vars1\aE^{-k}$ for any $\var0\in\F{U}$ with $\Norm{\var0}\leq R$.
 Maximising over $\var0$ gives $C=2R\vars1$
-				\item[(4)] $\op{E}_0(\tilde{\var2}_k)-\op{E}_0(\var0)\leq \inf_{\var1\in\partial\op{E}(\tilde{\var2}_k)}\leq 2R\vars1\aE^{-k}$ for any $\var0\in\tilde{\F{U}}^k$ with $\Norm{\var0}\leq R$, therefore $\op{E}_0(\tilde{\var2}_k) \leq \op{E}_0(\tilde{\F{U}}^k) + 2R\vars1\aE^{-k}$ and $C=(1+2R)\vars1$.
+				\item[(4)] $\op{E}_0(\tilde{\var2}_k)-\op{E}_0(\var0)\leq \inf_{\var1\in\partial\op{E}(\tilde{\var2}_k)}\IP{\var1}{\tilde{\var2}_k-\var0}\leq 2R\vars1\aE^{-k}$ for any $\var0\in\tilde{\F{U}}^k$ with $\Norm{\var0}\leq R$, so $\op{E}_0(\tilde{\var2}_k) \leq \op{E}_0(\tilde{\F{U}}^k) + 2R\vars1\aE^{-k}$ and $C=(1+2R)\vars1$.
 			\end{itemize}
@@
 	}{%
-		The first statement of the result is by definition, for each $\tilde{\var2}\in\tilde{\F{U}}$
+		The first statement of the result is by definition, for each $\tilde{\var2}\in\tilde{\F{U}}\subset L^\infty(\Domain)\subset \F H$ we have
 		$$ \norm{\tilde{\var2}} = \frac{\IP{\tilde{\var2}}{\tilde{\var2}}}{\norm{\tilde{\var2}}} \leq \sup_{\var0\in\tilde{\F{U}}} \frac{\IP{\var0}{\tilde{\var2}}}{\norm{\var0}\,\Norm{\tilde{\var2}}}\Norm{\tilde{\var2}} \leq \sup_{\var0,\tilde{\var0}\in\tilde{\F{U}}} \frac{\IP{\var0}{\tilde{\var0}}}{\norm{\var0}\,\Norm{\tilde{\var0}}}\Norm{\tilde{\var2}}.
@@
 		\begin{equation}
-			\int_\Domain |\var0(\vec x)|^{\frac{q}{q-1}}\diff\vec{x} \leq \left(\int_\Domain 1\diff\vec{x}\right)^{1-\frac{q}{2(q-1)}}\left(\int_\Domain |\var0(\vec x)|^2\diff\vec{x}\right)^{\frac{q}{2(q-1)}} = \left(|\Domain|^{\frac{1}{2} -\frac{1}{q}}\norm{\var0}\right)^{\frac{q}{q-1}}.
+			\int_\Domain |\var0(\vec x)|^{q^*}\diff\vec{x} \leq \left(\int_\Domain 1\diff\vec{x}\right)^{1-q^*/2}\left(\int_\Domain |\var0(\vec x)|^2\diff\vec{x}\right)^{q^*/2} = \left(|\Domain|^{\frac{1}{2} -\frac{1}{q}}\norm{\var0}\right)^{q^*}.
 		\end{equation}
@@
 Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces with orthogonal projections $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\F{U}}^k $.
-If $q\geq 2$,}{$\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space} , then}
-		$$ \norm{\edit{\tilde{\tens{\Pi}}_k\var2}{\tilde{\var2}_k}} \lesssim \splitln{\edit{\Norm{\var2}}{1}}{\text{if }q\geq2, \text{ or}}{\edit{\sqrt{N}\Norm{\var2}}{}\meshsize^{-\frac{kd}{2}} \qquad}{\text{ if }1\leq q<2,\ \edit{}{\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_{L^\infty(\domain_0)}}{\norm{\var0}_{L^2(\domain_0)}}<\infty}.} \edit{}{\quad\text{in particular, }\quad q' = \splitln{0}{q\geq2}{-\frac{d}{2}}{1\leq q<2.}}$$
+If $q\geq 2$,}{$\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space} , then
+		\begin{enumerate}
+			\item If $q\geq 2$, then $\norm{\tilde{\var2}_k} \lesssim 1$ (i.e. $q'=0$).
+			\item If $q<2$ and $\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_{L^\infty(\domain_0)}}{\norm{\var0}_{L^2(\domain_0)}}<\infty$, then $\norm{\tilde{\var2}_k} \lesssim \meshsize^{-\frac{kd}{2}}$ (i.e.
+$q'=-\frac d2$).
+		\end{enumerate}
+		}
 	\end{lemma}
@@
 	\begin{lemma}\label{app:thm: generic a_E bound}
-		\edit[2]{Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\var2}_k=\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.}{Suppose $\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space} and $\var0^*$ the minimiser of $E$ such that $\Norm{\tilde{\var2}_k-\var0^*}\lesssim \meshsize^{kp}$.}
+		\edit[2]{Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\var2}_k=\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.}{Suppose $\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space} and $\var0^*$ is the minimiser of $E$ such that $\Norm{\tilde{\var2}_k-\var0^*}\lesssim \meshsize^{kp}$.}
 		\begin{enumerate}
 			\item If $\op{E}$ is $\Norm\cdot$-Lipschitz at $\var0^*$, then
-			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{kp}\edit[2]{\Norm{\var0^*}}{}$\edit{}{ (i.e. $p'=p$)}.
+			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{kp}\edit[2]{\Norm{\var0^*}}{}$ \edit{}{ (i.e. $p'=p$)}.
 			\item If $\op{E}$ is $\Norm\cdot$-smooth at $\var0^*$, then 
-			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{2kp}\edit[2]{\Norm{\var0^*}}{}$\edit{}{ (i.e. $p'=2p$)}.
+			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{2kp}\edit[2]{\Norm{\var0^*}}{}$ \edit{}{ (i.e. $p'=2p$)}.
 			\edit[2]{\item If $\op{f}$ is $\Norm\cdot$-Lipschitz at $\var0^*$ and 
@@
 	\begin{proof}
-		\edit{Each statement is}{Both statements are true} by definition, observe
+		\edit[2]{Each statement is}{Both statements are direct} by definition, observe
 		\begin{gather}
@@
 	\end{theorem}
-	\begin{proof}[case 1]
+	\begin{proof}[Case 1.]
 		From Lemma~\ref{thm: norm bound L2} we have 
@@
 
-	\begin{proof}[case 2]
+	\begin{proof}[Case 2.]
 		$\psi_j$ are not necessarily orthogonal however $|\IP{\psi_i}{\psi_j}|\leq 1$ therefore we can estimate
@@
 
-	\begin{proof}[case 3]
+	\begin{proof}[Case 3.]
 		In the Gaussian case, we build our approximations around the idea that sums of Gaussians should converge very quickly.

### 2022-03-10 paper.tex
General update

@@
 	\end{equation}
-	where $\op{f}\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\op{g}\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
+	\edit{}{for a Hilbert space $\F H$ }where $\op{f}\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\op{g}\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
 \edit{}{Throughout this work we assume that $\op{E}$ is bounded below so that the infimum is finite.
 }The iterates of the FISTA algorithm will be denoted $\var0_n\in\F H$.
-It has been shown that $\op{E}(\var0_n) - \Emin$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}.
+\edit{It }{If, moreover the infimum is achieved, it }has been shown that $\op{E}(\var0_n) - \Emin$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}.
 Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \cite{Tao2016,Liang2017,Alamo2019}.
@@
 }{%
+	In this work we address the case where the minimiser possibly fails to exist or lies in a larger space where $\F H$ is dense.
 There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, however, our interpretation is relatively novel.
@@
 			\State $n\gets n+1$
-			\Until{converged}
+			\Until{a stopping criterion is met}
 		\end{algorithmic}
@@
 	\end{align}
-	Clearly $\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2}$ is a constant. \edit[0]{\sout{For the second term, recall $\Norm{\var2}\leq \Norm{\var0}$, therefore we can bound
+	\edit{}{as $\op{f}$ is convex with 1-Lipschitz gradient.} Clearly $\norm{\nabla\op{f}(\A\var0^*-\data)}_{\ell^2}$ is a constant.
+\edit[0]{\sout{For the second term, recall $\Norm{\var2}\leq \Norm{\var0}$, therefore we can bound
 	\\$\norm{\A(\var2-\var0^*)}_{\ell^2} = \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} \IP{\A^*\vec{r}}{\var2-\var0^*} \leq \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} |\A^*\vec{r}|_{L^\infty}\Norm{\var2-\var0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\var0}+\Norm{\var0^*}).$\\
 	Similarly, the final term can be approximated by}
-	\begin{multline*}
-		\norm{\A(\tilde{\tens{\Pi}}_k\var0-\var0)}_{\ell^2}
+	\\\sout{$ \norm{\A(\tilde{\tens{\Pi}}_k\var0-\var0)}_{\ell^2}
 		 = \sup_{\vec{r}\in\R^m}\norm{\vec{r}}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vec{r}}{\var0}
-		\leq \sup_{\vec{r}\in\R^m}\max_{\vec{x}\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vec{r}](\vec{x})-[\A^*\vec{r}](\vec{x})|\:\norm{\vec{r}}_{\ell^2}^{-1}\Norm{\var0}
-		\\\leq \sup_{\vec{r}\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vec{r}]}_{L^\infty}\: \norm{\vec{r}}_{\ell^2}^{-1} \Norm{\var0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\var0}
-	\end{multline*}
+		\leq \sup_{\vec{r}\in\R^m}\max_{\vec{x}\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vec{r}](\vec{x})-[\A^*\vec{r}](\vec{x})|\:\norm{\vec{r}}_{\ell^2}^{-1}\Norm{\var0}$}
+	\\\hspace*{80pt} \sout{$\leq \sup_{\vec{r}\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vec{r}]}_{L^\infty}\: \norm{\vec{r}}_{\ell^2}^{-1} \Norm{\var0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\var0}$
+	}\\
 	\sout{where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$.
@@
 	\end{equation}
-	In Lemma~\ref{thm: norm bound smoothness} we will show that this last term, which we denote the semi-norm $|\A^*|_{\ell^2\to C^1}$, is bounded by $\sqrt{m}\max_{j\in[m]}\norm{\nabla\Psi_j}_\infty$.
+	In Lemma~\ref{thm: norm bound smoothness} we will show that this last term, which we denote the semi-norm $|\A^*|_{\ell^2\to C^1}$, is bounded by \\$\sqrt{m}\max_{j\in[m]}\norm{\nabla\Psi_j}_\infty$.
 We conclude that $\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*)\lesssim 2^{-k}$.}
@@
 		\\&= \max_{\vec{\varphi}\in\R^m} \splitln{-\ip{\data}{\vec{\varphi}} -\op{f}^*(\vec{\varphi})}{\qquad\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu}{-\infty}{\qquad\text{else}}
-		\\&= -\min_{\vec{\varphi}\in\R^m} \underbrace{\op{f}^*(\vec{\varphi})+\ip{\data}{\vec{\varphi}}}_{\eqqcolon \op{E}^*(\vec{\varphi})}  + \chi(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu).
+		\\&= -\min_{\vec{\varphi}\in\R^m} \underbrace{\op{f}^*(\vec{\varphi})+\ip{\data}{\vec{\varphi}}}_{\eqqcolon \op{E}^\dag(\vec{\varphi})} + \chi(\Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu).
 	\end{align}
@@
 	\begin{equation}
-		\op{E}(\var0) - \min_{\var0\in\F{U}^n}\op{E}(\var0) = \op{E}(\var0) + \min_{\vec{\varphi}\in\R^m\st \Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu} \op{E}^*(\vec{\varphi}) \leq \op{E}(\var0) + \op{E}^*(\vec{\varphi})
+		\op{E}(\var0) - \min_{\var0\in\F{U}^n}\op{E}(\var0) = \op{E}(\var0) + \min_{\vec{\varphi}\in\R^m\st \Norm{\tens{\Pi}_n\A^*\vec{\varphi}}_*\leq \mu} \op{E}^\dag(\vec{\varphi}) \leq \op{E}(\var0) + \op{E}^\dag(\vec{\varphi})
 	\end{equation}
@@
 	\end{equation}
-	We remark briefly that it is more conventional to include the constraint in the definition of $\op{E}^*$.
-We choose to omit it here to highlight that it is only the constraint which changes between the discrete and continuous cases; $\op{E}^*$ will remain the same.
+	We remark briefly that \edit{it is more conventional to include the constraint in the definition of $\op{E}^\dag$}{$\op{E}^\dag$ should be thought of as the dual of $\op{E}$ but without the constraint}.
+We choose to omit it here to highlight that it is only the constraint which changes between the discrete and continuous cases; the value of $\op{E}^\dag$ will remain the same.
 
@@
 	\begin{equation}
-		\vec{\varphi}_n\coloneqq \nabla\op{f}(\A\var0_n - \data), \qquad \op{E}(\var0)-\min_{\var0'\in\F{U}^n}\op{E}(\var0') \leq \op{E}(\var0) +\op{E}^*(\vars2\vec{\varphi}_n)
+		\vec{\varphi}_n\coloneqq \nabla\op{f}(\A\var0_n - \data), \qquad \op{E}(\var0)-\min_{\var0'\in\F{U}^n}\op{E}(\var0') \leq \op{E}(\var0) +\op{E}^\dag(\vars2\vec{\varphi}_n)
 	\end{equation}
@@
 	\end{equation}
-	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\A\var0_n-\data)$ and $\tens{\Pi}_n\nabla\op{f}(\A\var0_n-\data)$ are easily computable, therefore $\vars2$ and $\op{E}(\var0_n) +\op{E}^*(\vars2\vec{\varphi}_n)$ are also easy to compute.
+	To apply Algorithm~\ref{alg: refining FISTA}, we are assuming that both $\op{f}(\A\var0_n-\data)$ and $\tens{\Pi}_n\nabla\op{f}(\A\var0_n-\data)$ are easily computable, therefore $\vars2$ and $\op{E}(\var0_n) +\op{E}^\dag(\vars2\vec{\varphi}_n)$ are also easy to compute.
 
@@
 		\end{cases}
-		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^*(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]
+		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^\dag(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]
 	\end{align}
@@
 		\end{cases}
-		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^*(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right].
+		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^\dag(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right].
 	\end{align}
@@
 
-	Heuristically, we will use strong convexity of $\op{E}^*$ and smoothness of $\A^*$ to quantify the statement:
-	$$ \text{if}\quad \op{E}(\var0_n) + \op{E}^*(\vars2_0 \vec{\varphi}_n) \approx 0 \quad \text{then}\quad \left\{\vec{x}\st |[\A^*\vec{\varphi}_n](\vec{x})|\ll \mu\right\} \subset\{\vec{x} \st \var0^*(\vec{x})=0\}.$$
+	Heuristically, we will use strong convexity of $\op{E}^\dag$ and smoothness of $\A^*$ to quantify the statement:
+	$$ \text{if}\quad \op{E}(\var0_n) + \op{E}^\dag(\vars2_0 \vec{\varphi}_n) \approx 0 \quad \text{then}\quad \left\{\vec{x}\st |[\A^*\vec{\varphi}_n](\vec{x})|\ll \mu\right\} \subset\{\vec{x} \st \var0^*(\vec{x})=0\}.$$
 	Recall that $\nabla\op{f}$ is 1-Lipschitz if and only if $\op{f}^*$ is 1-strongly convex \cite[Chapter 10, Thm.
@@
 	\begin{equation}
-		\tfrac12\norm{\vars2_0\vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}^2 \leq \op{E}^*(\vars2_0\vec{\varphi}_n) - \op{E}^*(\vec{\varphi}^*) = \op{E}^*(\vars2_0\vec{\varphi}_n) + \op{E}(\var0^*) \leq \op{E}^*(\vars2_0\vec{\varphi}_n) + \op{E}(\var0_n),
+		\tfrac12\norm{\vars2_0\vec{\varphi}_n-\vec{\varphi}^*}_{\ell^2}^2 \leq \op{E}^\dag(\vars2_0\vec{\varphi}_n) - \op{E}^\dag(\vec{\varphi}^*) = \op{E}^\dag(\vars2_0\vec{\varphi}_n) + \op{E}(\var0^*) \leq \op{E}^\dag(\vars2_0\vec{\varphi}_n) + \op{E}(\var0_n),
 	\end{equation}
@@
 	\begin{equation}
-		|[\tens{\Pi}_n\A^*\vars2_0\vec{\varphi}_n](\vec{x})|< \vars2_0^{-1}\left(\mu - \sqrt{2(\op{E}(\var0_n)+\op{E}^*(\vars2_0\vec{\varphi}_n))}|\A^*|_{\ell^2\to L^\infty}\right) \qquad \implies \qquad \var0^*(\vec{x})= 0.\label{eq: support equation}
+		|[\tens{\Pi}_n\A^* \vec{\varphi}_n](\vec{x})|< \vars2_0^{-1}\left(\mu - \sqrt{2(\op{E}(\var0_n)+\op{E}^\dag(\vars2_0\vec{\varphi}_n))}|\A^*|_{\ell^2\to L^\infty}\right) \qquad \implies \qquad \var0^*(\vec{x})= 0.\label{eq: support equation}
 	\end{equation}
@@
 	\begin{itemize}
-		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the quantity $\op{E}(\var0_n)-\op{E}(\var0^*)$, the more relevant quantity here is $\op{E}^*(\vars2_0\vec{\varphi}_n)+\op{E}(\var0^*)$ for which there is no proven rate of convergence.
+		\item The convergence guarantee from Theorem~\ref{thm: exponential FISTA convergence} is for the primal gap $\op{E}(\var0_n)-\op{E}(\var0^*)$, \edit{the more relevant quantity here is}{rather than the primal-dual gap} $\op{E}(\var0_n)+\op{E}^\dag(\vars2_0\vec{\varphi}_n)$ \edit{for which there is no proven rate of convergence.
+}{used here.
+Although there is no guaranteed rate for the primal-dual gap, it is much more easily computable than the primal gap.}
 		\item In Section~\ref{sec: continuous lasso rate}, $|\A^*|_{\ell^2\to C^1}<\infty$ was required to compute a rate of convergence for $\op{E}(\var0_n)$, but only $|\A^*|_{\ell^2\to L^\infty}<\infty$ is needed to estimate the support.
@@
 	\subsection{Operator norms}\label{sec: smoothing operators}
-	For numerical implementation of \eqref{eq: Lasso energy}, we are required to accurately estimate several operator norms of $\A$\edit{}{ of the form in \eqref{eq: kernels of A}.
+	For numerical implementation of \eqref{eq: Lasso energy}, we are required to accurately estimate several operator norms of $\A$ \edit{}{of the form in \eqref{eq: kernels of A}.
 In particular, there are kernels $\psi_j\in\F H$ such that $(\A \var0)_j=\IP{\psi_j}{\var0}$ for each $j\in[m]$}.
@@
 Lemma~\ref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\op{E}_0(\var0_n)$ so it is this monotone estimate which is plotted.
-As $\op{E}(\var0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\op{E}_0(\var0_n) \approx \min_{n\leq N}\op{E}(\var0_n) + \min_{n'\leq n}\op{E}^*(\vars2_0\vec{\varphi}_{n'})$.
-Another quantity of interest is minimisation of the discrete energy $\min_{n\leq N}\op{E}(\var0_n) + \min_{n'\leq n}\op{E}^*(\vars2\vec{\varphi}_{n'})$ which will be referred to as the `discrete gap'.
+As $\op{E}(\var0^*)$ is not known exactly, we always use the estimate $\min_{n\leq N}\op{E}_0(\var0_n) \approx \min_{n\leq N}\op{E}(\var0_n) + \min_{n'\leq n}\op{E}^\dag(\vars2_0\vec{\varphi}_{n'})$.
+Another quantity of interest is minimisation of the discrete energy $\min_{n\leq N}\op{E}(\var0_n) + \min_{n'\leq n}\op{E}^\dag(\vars2\vec{\varphi}_{n'})$ which will be referred to as the `discrete gap'.
 Note that for the adaptive schemes the discrete gap may not be monotonic as the discrete dual problem changes with $N$.
@@
 	\begin{equation}\label{eq: less than double gap bound}
-		\op{E}(\var0_n) + \op{E}^*(\vars2_0\vec{\varphi}_n) \leq 2(\op{E}(\var0_n) + \op{E}^*(\vars2\vec{\varphi}_n)),
+		\op{E}(\var0_n) + \op{E}^\dag(\vars2_0\vec{\varphi}_n) \leq 2(\op{E}(\var0_n) + \op{E}^\dag(\vars2\vec{\varphi}_n)),
 	\end{equation}
@@
 	\begin{equation}
-		\op{E}^*(\vars2_0\vec{\varphi}_n) = \tfrac12\norm{\vars2_0\vec{\varphi}_n}^2 + \vars2_0\ip{\data}{\vec{\varphi}_n} = \frac{\vars2_0}{\vars2}\left(\frac{\vars2_0}{\vars2}\tfrac12\norm{\vars2\vec{\varphi}_n}^2 + \vars2\ip{\data}{\vec{\varphi}_n}\right) \approx \frac{\vars2_0}{\vars2} \op{E}^*(\vars2\vec{\varphi}_n).
+		\op{E}^\dag(\vars2_0\vec{\varphi}_n) = \tfrac12\norm{\vars2_0\vec{\varphi}_n}^2 + \vars2_0\ip{\data}{\vec{\varphi}_n} = \frac{\vars2_0}{\vars2}\left(\frac{\vars2_0}{\vars2}\tfrac12\norm{\vars2\vec{\varphi}_n}^2 + \vars2\ip{\data}{\vec{\varphi}_n}\right) \approx \frac{\vars2_0}{\vars2} \op{E}^\dag(\vars2\vec{\varphi}_n).
 	\end{equation}
@@
 		\item The fastest FISTA stepsize choice is consistently the greedy variant, although $a=20$ is very comparable.
+		\item \edit{}{While each adaptive algorithm is allowed to use up to 1024 pixels, in Fig.~\ref{fig: convergence with method} the most used was 235.}
 	\end{itemize}
@@
 
-	Fig.~\ref{fig: STORM convergence} shows slightly faster convergence than $n^{-2/3}$ predicted by \eqref{eq: Lasso resolution rate} in dimension $d=2$.
+	Fig.~\ref{fig: STORM convergence} shows \edit{that convergence is}{various convergence metrics for the adaptive reconstructions.
+The magenta line in the first panel shows that the continuous gap converges }slightly faster than the $n^{-2/3}$ predicted by \eqref{eq: Lasso resolution rate} in dimension $d=2$.
 In this example we also implement the suggestion of Section~\ref{sec: support detection} to remove pixels outside of the support of $\var0^*$.
@@
 	guarantees that $\domain_i^n\cap\op{supp}(\var0^*) = \emptyset$.
-This threshold is plotted in the first panel of Fig.~\ref{fig: STORM convergence}.
-Once the value becomes less than 1, we can start reducing the number of pixels instead of continual refinement, as seen in the right-hand panel after around 30 iterations.
+This threshold is plotted in red in the first panel of Fig.~\ref{fig: STORM convergence}.
+Once the value becomes less than 1, we can start reducing the number of pixels instead of continual refinement\edit{, as seen in the right-hand panel}{.
+We see that the resolution decreases steadily (second panel), but the total number of pixels (final panel) stops increasing }after around 30 iterations.
 

### 2022-03-10 paper.tex
added local-Lipschitz comment

@@
 			& \aE &\geq \begin{cases}
-				\meshsize^{-2p} & \text{if }\op{E} \text{ is $\Norm\cdot$-smooth at }\var0^*,
+				\meshsize^{-2p} & \text{if }\nabla\op{E} \text{ is $\Norm\cdot$-Lipschitz at }\var0^*,
 				\\\meshsize^{-p}\qquad & \text{if }\op{E} \text{ is $\Norm\cdot$-Lipschitz at }\var0^*,
@@
 \edit{The only non-trivial case is when $\op{g}$ is not smooth enough to estimate directly.
-So long as $\tilde{\F{U}}^k$ are sufficiently dense in sublevel sets of $\op{g}$, the smoothness of $\op{f}$ is sufficient to give a convergence rate.}{}
+So long as $\tilde{\F{U}}^k$ are sufficiently dense in sublevel sets of $\op{g}$, the smoothness of $\op{f}$ is sufficient to give a convergence rate.}{We also briefly remark that the Lipschitz constants in this lemma do not need to be valid globally, only on the sequence $\tilde{\var2}_k$.
+The same result holds under a local-Lipschitz assumption, for example on the ball of radius $\sup_{k\in\F N}\Norm{\tilde{\var2}_k}$ which is finite whenever $p\geq0$.}
 
@@
 			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{kp}\edit[2]{\Norm{\var0^*}}{}$ \edit{}{ (i.e. $p'=p$)}.
-			\item If $\op{E}$ is $\Norm\cdot$-smooth at $\var0^*$, then 
+			\item If $\nabla\op{E}$ is $\Norm\cdot$-Lipschitz at $\var0^*$, then 
 			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{2kp}\edit[2]{\Norm{\var0^*}}{}$ \edit{}{ (i.e. $p'=2p$)}.

### 2022-03-14 response.tex
New fig and final edits

@@
 Morally, we assume the existence of a `nice' minimising sequence rather than asserting that $w_n$ must be minimisers in $\F{U}^n$.
-Documenting the changes which are longer than one line:
+Highlighting the changes which are longer than one line:
 \begin{itemize}
@@
 A simple 1D example, if $E(u) = e^{-u}$ for $u\geq0$, then numerically I get $u_n\approx 4\log(n)$.
-Clearly $|u_n-\infty|\not\to0$, but in a `weak sense', certainly $u_n\to\infty$.
+Clearly $|u_n-\infty|\not\to0$, but in a `weaker sense', certainly $u_n\to\infty$.
 This seems to be representative of the general behaviour.
-In the Lasso example, the iterates are meaningless in both $L^2$ and $L^1$, but can be understood in the space of measures (or distributions).
-In this sense, we have never observed anything unexpected for large $n$.
+In the Lasso example, the convergence of iterates is meaningless in both $L^2$ and $L^1$, but can be understood in the space of measures.
+In this sense, we have never observed anything unexpected for large $n$, the iterates do converge to tall/thin Dirac-like functions.
 Unfortunately this behaviour can't be understood from the values of $a_E$ and $a_U$ alone.
@@
 
+	\begin{quote}
+		\edit{}{Let $A\colon\F{U}\cap\F{H}\to\F R^m$ be a linear operator represented by the kernels $\psi_j\in\F{H}$ such that 
+		\begin{equation*}\label{eq: kernels of A}
+			\forall u\in\F{U}\cap\F{H},\ j=1,\ldots,m,\qquad (Au)_j = \langle \psi_j, u\rangle.
+		\end{equation*}
+		In the continuous case we will assume the additional smoothness $\psi_j\in C^1([0,1]^d)$.
+In Section~6.5 we will formally define and estimate several operator semi-norms for $A$ of this form, for example Lemma~8 confirms that $A$ is continuous on $\F{H}$ (without loss of generality $\|A\|\leq 1$).}
+	\end{quote}
+
 	\item \review{page 11, paragraph below (21): Sublevel sets of $E$ are not compact, they are not even bounded without further conditions on $f$ ($f$ bounded from below would be sufficient).
@@
 The old (61-62) are now (60-61) which are equalities.
-There was a pair of inequalities (59-60), now (58-59), but they are simply statements of H\"older's inequality.
+There was a pair of inequalities (59-60), now (58-59), but they do not seem to fit the comment.
+They are just statements of H\"older's inequality.
 

### 2022-03-14 paper.tex
New fig and final edits

@@
 	\section{Definitions and notation}\label{sec: prelims}
-	We consider optimisation of \eqref{eq: min F = fD+fC} over a Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$ with the translated energy
-	\begin{equation}
-		\op{E}_0\colon\F H\to \R,\qquad \op{E}_0(\var0) \coloneqq \op{E}(\var0)-\Emin[\tilde{\var0}].
-	\end{equation}
+	We consider optimisation of \eqref{eq: min F = fD+fC} over a Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$.
+In the more analytical section (Sections~\ref{sec: recipe} and \ref{sec: FISTA convergence}) it will be more convenient to use the translated energy
+	\begin{equation}
+		\op{E}_0\colon\F H\to \R,\qquad \op{E}_0(\var0) \coloneqq \op{E}(\var0)-\Emin[\tilde{\var0}]
+	\end{equation}
+	so that $\inf_{\var0\in\F{H}}\op{E}_0(\var0) = 0$, although access to this function is not assumed for numerical examples.
 
@@
 			\State $n\gets n+1$
-			\Until{a stopping criterion is met}
+			\Until{some stopping criterion is met}
 		\end{algorithmic}
@@
 	In this section we give an intuitive outline of the full proof for convergence of Algorithm~\ref{alg: refining FISTA} before giving formal theorems and proofs in the next section.
-First we recall the classical FISTA convergence guarantee given by \cite[Thm 3.1]{Chambolle2015}\edit{:}{; if there exists $\var0^*\in \argmin_{\var0\in\F H}\op{E}(\var0)$, then}
+First we recall the classical FISTA convergence guarantee given by \cite[Thm 3.1]{Chambolle2015}\edit{:}{; if there exists $\var0^*\in \argmin_{\var0\in\F H}\op{E}_0(\var0)$, then}
 	\begin{equation}\label{eq: classical FISTA}
@@
 	\end{equation}
-	for \edit{some $\var0^*\in \argmin_{\var0\in\F H}\op{E}(\var0)$, and}{any} FISTA stepsize choice $t_N\simeq N$ such that $\rho_n\geq0$.
+	for \edit{some $\var0^*\in \argmin_{\var0\in\F H}\op{E}_0(\var0)$, and}{any} FISTA stepsize choice $t_N\simeq N$ such that $\rho_n\geq0$.
 
@@
 		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\F{U}^n$.
-\edit{The idea is that $\F{U}^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\var0\in\F{U}^n}\op{E}(\var0) \to \inf_{\var0\in\F H}\op{E}(\var0)$.
+\edit{The idea is that $\F{U}^n$ are locally compact, so that minimisers are achieved, but `growing' so that $\min_{\var0\in\F{U}^n}\op{E}_0(\var0) \to \inf_{\var0\in\F H}\op{E}_0(\var0)$.
 A canonical example might be $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq n\}$.}{The idea is that there is a sequence $\var2_n\in\F{U}^n$, $n\in\F N$ such that $\norm{\var2_n}$ grows slowly and $\op{E}_0(\var2_n)$ decreases quickly.} To quantify \edit{the}{this} balance\edit{ between a growing Hilbert norm and improving estimate of $\op{E}$}{}, we introduce a secondary sequence $n_0 < n_1 < \ldots$ and constants $\aU,\aE\geq1$ such that for each $k\in\F N$
@@
 		\end{equation}
-		\edit{The expanding balls example would become}{A canonical example would be} $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq \aU^k\}$ for $n\in[n_k,n_{k+1})$, then $\aE$ reflects the smoothness of $\op{E}$.
+		\edit{The expanding balls example would become}{A canonical example would be} $\F{U}^n=\{\var0\in\F H\st \norm{\var0}\leq \aU^k\}$ for $n\in[n_k,n_{k+1})$, then $\aE$ reflects the smoothness of $\op{E}_0$.
 The choice of exponential scaling \edit{is more}{is introduced to improve stability of Algorithm~\ref{alg: refining FISTA}.
@@
 		\edit{Adaptively choosing the time of refinement is more challenging due to the non-descent property of FISTA.
-The idea is that $\F{U}^n$ should be refined as soon as the value $\op{E}(\var0_n)$ is sufficiently close to $\op{E}(\var2_n)$.
+The idea is that $\F{U}^n$ should be refined as soon as the value $\op{E}_0(\var0_n)$ is sufficiently close to $\op{E}_0(\var2_n)$.
 This is analysed in Theorem~\ref{thm: stronger exponential FISTA convergence} (sufficient conditions in Lemma~\ref{thm: practical refinement criteria}) which shows convergence results of the form}{The only non-trivial property to verify is the energy gap  $\op{E}_0(\var0_n) = \op{E}(\var0_n)-\Emin$.
@@
 		for all $N\in\F N$, with the same $\kappa\in[0,1)$ from Step~\ref{step: step 5 sufficiently slow}.
-The penalty for accelerating the change of discretisation is a potential loss of stability or monotonicity in $\op{E}(\var0_n)$, although this behaviour has not been seen in numerical experiments.
+The penalty for accelerating the change of discretisation is a potential loss of stability or monotonicity in $\op{E}_0(\var0_n)$, although this behaviour has not been seen in numerical experiments.
 	\end{adaptiveStep}
@@
 			Then, for all $\var2\in\F{U}^n$, we have
-			$$\op{E}(\var0) + \tfrac12\norm{\var0-\var2}^2 \leq \op{E}(\var2) + \tfrac12\norm{\bar{\var0}-\var2}^2.$$
+			$$\op{E}_0(\var0) + \tfrac12\norm{\var0-\var2}^2 \leq \op{E}_0(\var2) + \tfrac12\norm{\bar{\var0}-\var2}^2.$$
 
@@
 		\begin{equation}\Copy{thm:eq: one step FISTA}{
-			t_{n}^2(\op{E}(\var0_{n}) - \op{E}(\var2_n)) - (t_{n}^2-t_{n})(\op{E}(\var0_{n-1})-\op{E}(\var2_n)) \leq \tfrac1{2}\left[\norm{\var1_{n-1}}^2-\norm{\var1_{n}}^2\right] + \IP{\var1_{n}-\var1_{n-1}}{\var2_n}.}\label{eq: one-step FISTA}
+			t_{n}^2(\op{E}_0(\var0_{n}) - \op{E}_0(\var2_n)) - (t_{n}^2-t_{n})(\op{E}_0(\var0_{n-1})-\op{E}_0(\var2_n)) \leq \tfrac1{2}\left[\norm{\var1_{n-1}}^2-\norm{\var1_{n}}^2\right] + \IP{\var1_{n}-\var1_{n-1}}{\var2_n}.}\label{eq: one-step FISTA}
 		\end{equation}
 	\end{lemma}
-	\noindent The proof is given in Theorem~\ref{app:thm: one step FISTA} and is a result of the convexity of $\op{E}$ and $\F{U}_n$ for a well chosen $\var2$ in Lemma~\ref{thm: descent lemma}.
+	\noindent The proof is given in Theorem~\ref{app:thm: one step FISTA} and is a result of the convexity of $\op{E}_0$ and $\F{U}_n$ for a well chosen $\var2$ in Lemma~\ref{thm: descent lemma}.
 
@@
 This result is the key approximation for showing convergence of FISTA with changing subsets.
-In the classical setting, we have $\F{U}^n=\F H$, $\var2_n=\var2_0\in\argmin_{\var0\in\F H}\op{E}(\var0)$ and the extra terms on the right-hand side collapse to 0.
-
-	If there exists a minimiser $\var0^*\in\argmin_{\var0\in\F H}\op{E}(\var0)$, then the natural choice in \eqref{eq: FISTA inequality} is $\var2_n=\tens{\Pi}_n\var0^*$ for some projection $\tens{\Pi}_n\colon\F H\to\F{U}^n$, however, there are simple counter-examples which give $\op{E}(\tens{\Pi}_n\var0^*)=\infty$ and so this inequality becomes useless.
+In the classical setting, we have $\F{U}^n=\F H$, $\var2_n=\var2_0\in\argmin_{\var0\in\F H}\op{E}_0(\var0)$ and the extra terms on the right-hand side collapse to 0.
+
+	If there exists a minimiser $\var0^*\in\argmin_{\var0\in\F H}\op{E}_0(\var0)$, then the natural choice in \eqref{eq: FISTA inequality} is $\var2_n=\tens{\Pi}_n\var0^*$ for some projection $\tens{\Pi}_n\colon\F H\to\F{U}^n$, however, there are simple counter-examples which give $\op{E}_0(\tens{\Pi}_n\var0^*)=\infty$ and so this inequality becomes useless.
 For example, if $\op{f}(\var0) = \norm{\var0}_{L^2([0,1])}^2$, $\op{g}$ is the indicator on the set $\F D=\{\var0\in L^1([0,1])\st \var0(x) \geq x\}$, and $\tens{\Pi}_n$ is the $L^2$ projection onto a set of piecewise constant functions, then $\var0^*=x\mapsto x$.
@@
 	$$\tens{\Pi}_n\var0^*\left(x_0+\tfrac\meshsize2\right) = \argmin_{\vars5\in\R}\int_{x_0-\meshsize}^{x_0+\meshsize}(\var0^*(x)-\vars5)^2\diff x = \argmin_{\vars5\in\R}\int_{x_0-\meshsize}^{x_0+\meshsize}(x-\vars5)^2\diff x = x_0 < x_0+\tfrac\meshsize2.$$
-	In particular $\tens{\Pi}_n\var0^* \notin\F D$ therefore $\op{E}(\tens{\Pi}_n\var0^*) = \infty$.
-The choice $\var2_n=\argmin_{\var0\in\F{U}^n}\op{E}(\var0)$ is much more robust and allows us to apply Algorithm~\ref{alg: refining FISTA} more broadly.
+	In particular $\tens{\Pi}_n\var0^* \notin\F D$ therefore $\op{E}_0(\tens{\Pi}_n\var0^*) = \infty$.
+The choice $\var2_n=\argmin_{\var0\in\F{U}^n}\op{E}_0(\var0)$ is much more robust and allows us to apply Algorithm~\ref{alg: refining FISTA} more broadly.
 The penalty for this flexibility is a more complicated analysis; each time the subset changes, because $\var1_n\in\F{U}_n$, the system receives a `shock' proportional to $\norm{\var1_n}\norm{\var2_{n}-\tens{\Pi}_n\var2_{n+1}}$.
@@
 	\begin{equation}
-		\op{E}(\var0_n) - \min_{\var0\in\F{U}^n}\op{E}(\var0) \lesssim \frac{\norm{\var0_0-\edit{\argmin_{\var0\in\F{U}^n}\op{E}(\var0)}{\tilde{\var2}_k}}^2}{n^2}
+		\op{E}_0(\var0_n) = \op{E}(\var0_n) - \min_{\var0\in\F{U}^n}\op{E}(\var0) \lesssim \frac{\norm{\var0_0-\edit{\argmin_{\var0\in\F{U}^n}\op{E}(\var0)}{\tilde{\var2}_k}}^2}{n^2}
 	\end{equation}
@@
 If this condition is not satisfied, then it indicates that computational effort has been wasted by a poor choice of subsets.
-This can be interpreted as an overfitting to the discretisation of $\op{E}|_{\F{U}^n}$ rather than the desired function $\op{E}|_{\F H}$.
+This can be interpreted as an overfitting to the discretisation of $\op{E}_0|_{\F{U}^n}$ rather than the desired function $\op{E}_0|_{\F H}$.
 Combining the assumptions given by Definition~\ref{def: exp subspaces} and the result of Lemma~\ref{thm: mini exponential FISTA convergence}, the following lemma proves the convergence of Algorithm~\ref{alg: refining FISTA} provided that the refinement times $n_k$ are sufficiently small (i.e.
@@
 	\subsection{Convergence rate}
-	In Lemma~\ref{thm: sufficiently fast} we show that $\op{E}(\var0_n)$ converges at a rate depending on $k$ and $n$, so long as $k$ grows sufficiently quickly.
+	In Lemma~\ref{thm: sufficiently fast} we show that $\op{E}_0(\var0_n)$ converges at a rate depending on $k$ and $n$, so long as $k$ grows sufficiently quickly.
 On the other hand, as $k$ grows, the rate becomes worse and so we need to also put a lower limit on the growth of $n_k$.
@@
 	\end{equation}
-	In this sense, we could say that $\op{E}$ converges at the rate $N^{-2(1-\kappa)}$ if and only if such a sequence exists.
+	In this sense, we could say that $\op{E}_0$ converges at the rate $N^{-2(1-\kappa)}$ if and only if such a sequence exists.
 Nothing is lost (or gained) analytically by choosing $\F{U}_n\subsetneq\F H$.}
@@
 			\sout{Whenever these conditions on $n_k$ are satisfied, }}{If $(\tilde{\var2}_k)_{k\in\F N}$ is an \aUaE\ with $\aU>1$ and $n_k^2\lesssim \aE^k\aU^{2k}$, }then
-			$$\min_{n\leq N}\op{E}_0(\var0_n) \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \aU^2}{\log \aE + \log \aU^2}$$
+			$$\min_{n\leq N}\op{E}_0(\var0_n) = \min_{n\leq N} \op{E}(\var0_n) - \Emin \lesssim \frac{1}{N^{2(1-\kappa)}}\qquad \text{ where } \qquad \kappa = \frac{\log \aU^2}{\log \aE + \log \aU^2}$$
 			uniformly for $N\in\F N$.
@@
 only an upper bound on $n_k$) is a slightly weaker stability guarantee (now convergence of $\min_{n\leq N}\op{E}_0(\var0_n)$).
-In Theorem~\ref{thm: exponential FISTA convergence}, as in the original FISTA algorithm, the sequence $\op{E}(\var0_n)$ is not monotone but the magnitude of oscillation is guaranteed to decay in time.
+In Theorem~\ref{thm: exponential FISTA convergence}, as in the original FISTA algorithm, the sequence $\op{E}_0(\var0_n)$ is not monotone but the magnitude of oscillation is guaranteed to decay in time.
 This behaviour is lost in Theorem~\ref{thm: stronger exponential FISTA convergence}.
@@
 	\begin{equation}\label{eq: Lasso energy rate}
-		\kappa = \frac{\log \aU^2}{\log \aE + \log \aU^2} = \frac{d}{1+d} \quad \implies \quad \op{E}_0(\var0_n) \lesssim n^{-2(1-\kappa)} = n^{-\frac{2}{1+d}}.
+		\kappa = \frac{\log \aU^2}{\log \aE + \log \aU^2} = \frac{d}{1+d} \quad \implies \quad \op{E}(\var0_n)-\Emin \lesssim n^{-2(1-\kappa)} = n^{-\frac{2}{1+d}}.
 	\end{equation}
@@
 		\end{cases}
-		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^\dag(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]
+		\\ \op{E}(\var0_n)-\Emin &\leq \op{E}(\var0_n) + \op{E}^\dag(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right]
 	\end{align}
@@
 		\end{cases}
-		\\ \op{E}_0(\var0_n) &\leq \op{E}(\var0_n) + \op{E}^\dag(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right].
+		\\ \op{E}(\var0_n)-\Emin &\leq \op{E}(\var0_n) + \op{E}^\dag(\vars2_0\vec{\varphi}_n), \qquad \vars2_0\in\left[0,\frac{\mu}{\Norm{\A^*\vec{\varphi}_n}_*}\right].
 	\end{align}
@@
 
-	In this section, the main aim is to minimise the exact energy $\op{E}_0(\var0_n)$ and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
+	In this section, the main aim is to minimise $\op{E}_0(\var0_n) = \op{E}(\var0_n)-\op{E}(\var0^*)$, and so this will be our main metric for the success of an algorithm, referred to as the `continuous gap'.
 Lemma~\ref{thm: practical refinement criteria} only provides guarantees on the values of $\min_{n\leq N}\op{E}_0(\var0_n)$ so it is this monotone estimate which is plotted.
@@
 	As shown in Section~\ref{sec: Lasso definition}, in 1D we have $\aU = \aE = 2$.
-The estimates given in \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\op{E}_0(\var0_n)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$.
-To achieve these rates, we implement a refinement criterion from Lemma~\ref{thm: practical refinement criteria} with guarantee of $\op{E}_0(\var0_{n_k-1})\lesssim 2^{-k}$ using the estimates made in Section~\ref{sec: Lasso gap and gradient}.
+The estimates given in \eqref{eq: Lasso energy rate} and \eqref{eq: Lasso resolution rate} in dimension $d=1$ predict that the adaptive energy will decay at a rate of $\op{E}(\var0_n)-\op{E}(\var0^*)\lesssim\frac1n$ so long as the pixel size also decreases at a rate of $\meshsize\sim\frac1n$.
+To achieve these rates, we implement a refinement criterion from Lemma~\ref{thm: practical refinement criteria} with guarantee of $\op{E}(\var0_{n_k-1})-\op{E}(\var0^*)\lesssim 2^{-k}$ using the estimates made in Section~\ref{sec: Lasso gap and gradient}.
 We choose subspaces $\F{U}^n$ to approximately enforce
@@
 	\begin{figure}\centering
-		\includegraphics[width=.86\textwidth]{lasso_ndofs_convergence}
+		\includegraphics[width=.9\textwidth]{lasso_ndofs_convergence}
 		\caption{Rates of continuous/discrete gap convergence for different LASSO algorithms with 128, 256, or 512 pixels.
@@
 
-		\includegraphics[width=.86\textwidth]{lasso_convergence_short}
+		\includegraphics[width=.9\textwidth]{lasso_convergence_short}
 		\caption{Convergence plots for solving 1D problems with different algorithms.
 `Adaptive' methods use Algorithm~\ref{alg: refining FISTA} with fewer than 1024 pixels and the remaining methods use a uniform discretisation of 1024 pixels.}\label{fig: convergence with method}
+
+		\vspace*{\floatsep}
+
+		\includegraphics[width=.9\textwidth]{lasso_1D_recons}
+		\caption{Example reconstruction from the algorithms considered in Fig.~\ref{fig: convergence with method}.
+Pixel boundaries are indicated on the $x$-axis and the filtering method of Section~\ref{sec: support detection} allows us to exclude the red shaded regions from $\op{supp}(u^*)$.
+Values on the $y$-axis are normalised to units of mass, i.e.
+a Dirac mass would have height 1.}\label{fig: example recon}
 	\end{figure}
@@
 Each adaptive scheme is allowed up to 1024 pixels and each uniform discretisation uses exactly 1024.
-The `Greedy FISTA' implementation was proposed by in \cite{Liang2018} and we include the adaptive variant despite a lack of convergence proof.
+\edit{}{An example of each reconstruction method is shown in Fig.~\ref{fig: example recon}.
+The adaptive method better identifies the support of $u^*$ and clearly localises pixels on that support.
+The reconstruction with uniform grid fails to provably identify the support of $\var0^*$, despite having found a qualitatively accurate discrete minimiser.} The `Greedy FISTA' implementation was proposed by in \cite{Liang2018} and we include the adaptive variant despite a lack of convergence proof.
 The remaining FISTA algorithms use a FISTA time step of $t_n = \frac{n+a-1}{a}$ for the given value of $a$, as proposed in \cite{Chambolle2015}.
@@
 constant pixel size of $2^{-10}$ in Fig.~\ref{fig: comparison with iteration}) and the adaptive discretisation starts with two pixels with an upper limit of 1024.
-As expected, the fixed discretisation starts with a smaller continuous gap before plateauing to a sub-optimal gap around $\op{E}_0=0.1$.
+As expected, the fixed discretisation starts with a smaller continuous gap before plateauing to a sub-optimal gap around $\op{E}=\op{E}(\var0^*) + 0.1$.
 
@@
 
-	Suppose that the numerical aim is to find a function $\var0_n$ with $\op{E}_0(\var0_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.
+	Suppose that the numerical aim is to find a function $\var0_n$ with $\op{E}(\var0_n)-\op{E}(\var0^*)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.
 For $n\in[10^3,10^4]$, in both problems, the adaptive schemes coincide with the fixed schemes in both energy and minimum pixel size.

### 2022-03-14 code/ada_haar.py

@@ -65,8 +65,9 @@ def _unknown_grad_tomo(res, g, slope, centre, dof_map, isleaf, out):
                         break
                     elif g[k + 1] > t - r:
                         value += res[j, k] ** 2 * abs(
-                            line_intersect_square(g[k + 1] * slope[j, 1], -g[k + 1] * slope[j, 0], slope[j], b0x, b0y, b1x, b1y)
-                            -line_intersect_square(g[k] * slope[j, 1], -g[k] * slope[j, 0], slope[j], b0x, b0y, b1x, b1y))
+                            line_intersect_square(g[k + 1] * slope[j, 1], -g[k + 1] *
+                                                  slope[j, 0], slope[j], b0x, b0y, b1x, b1y)
+                            - line_intersect_square(g[k] * slope[j, 1], -g[k] * slope[j, 0], slope[j], b0x, b0y, b1x, b1y))
 
                 big_value += sqrt(value)
             out[i] = big_value
@@ -98,7 +99,7 @@ def wavelet_children(tree, *ind, parent=None):
 
 
 def copy_tree(tree):
-    new = {i:wavelet_node(*i) for i in tree}
+    new = {i: wavelet_node(*i) for i in tree}
 
     for i in tree:
         root = (0,) * len(i)
@@ -181,13 +182,13 @@ def Haar_denoising(n_points, alpha, iters=None, prnt=True, plot=True, vid=None, 
 
     data = random.rand(n_points)
 
-    pms = {'i':0, 'eps':1e-18}
+    pms = {'i': 0, 'eps': 1e-18}
     recon = Haar(0, Haar_space(2, dim=1))
 
     def residual(u):
         return array([u.x[0, 0] * sqrt(L[j])
-                      +interval_integral(grid[j:j + 2], u.x[1:], u.dof_map) / sqrt(L[j]) - data[j]
-             for j in range(n_points)], dtype='float64')
+                      + interval_integral(grid[j:j + 2], u.x[1:], u.dof_map) / sqrt(L[j]) - data[j]
+                      for j in range(n_points)], dtype='float64')
 
     def energy(u):
         refine(u, True)
@@ -207,7 +208,7 @@ def Haar_denoising(n_points, alpha, iters=None, prnt=True, plot=True, vid=None, 
             if supp0 < x[1] and supp1 > x[0]:
                 midpoint, scale = .5 * (supp0 + supp1), (.5 / h) ** .5
                 value += scale * arr[i, 0] * (len_intersect(midpoint, supp1, x[0], x[1])
[…]

### 2022-03-14 code/adaptive_spaces.py

@@ -3,20 +3,20 @@ Created on 7 Sep 2020
 
 @author: Rob Tovey
 '''
+from pymorton import __part1by1, __part1by2, __unpart1by1, __unpart1by2
 import numpy as np
 from matplotlib import pyplot as plt
 from matplotlib.ticker import FixedLocator
 from numba import jit, prange
 from numpy import log2
 from numba.typed import List
-__params = {'nopython':True, 'parallel':False, 'fastmath':True, 'cache':True}
+__params = {'nopython': True, 'parallel': False, 'fastmath': True, 'cache': True}
 __pparams = __params.copy(); __pparams['parallel'] = True
 __cparams = __params.copy(); __cparams['cache'] = False
 EPS, FTYPE = 1e-25, 'float64'
 
 pass  # Numba wrapping of pymorton
 
-from pymorton import __part1by1, __part1by2, __unpart1by1, __unpart1by2
 pm_p1b1, pm_p1b2, pm_u1b1, pm_u1b2 = [jit()(f) for f in (__part1by1, __part1by2, __unpart1by1, __unpart1by2)]
 
 
@@ -131,7 +131,7 @@ class adaptive_mesh:  # odl RectPartition
         scale = 2 ** coarse_level
 
         coarse_map = np.empty((scale,) * self.dim + (2,), dtype=int)
-        coarse_map[...,:] = self.size, -1  # identify areas with no pixels
+        coarse_map[..., :] = self.size, -1  # identify areas with no pixels
 
         self._fine2coarse(dof_map, coarse_map, 1 / scale)
         return coarse_map
@@ -502,7 +502,7 @@ class adaptive_func:  # odl DiscretizedSpaceElement
         self.maps = FS if maps is None else maps
         self.x = arr
         self.FS = FS
-        assert self.x.shape[0] == self.dof_map.shape[0] + 1
+        assert self.x.shape[0] == self.dof_map.shape[0]
 
     def asarray(self): return self.x
 
@@ -615,7 +615,7 @@ class adaptive_func:  # odl DiscretizedSpaceElement
         else:
             FS = self.FS
             self.update(FS.old2new(self.x, self.dof_map, copy=False)
-                       +FS.old2new(other.x, other.dof_map, copy=False),
+                        + FS.old2new(other.x, other.dof_map, copy=False),
                         FS)
 
     def __isub__(self, other):
@@ -626,7 +626,7 @@ class adaptive_func:  # odl DiscretizedSpaceElement
         else:
[…]

### 2022-03-14 code/lasso.py

@@ -16,7 +16,7 @@ and plotting etc. within the mesh.
 A forward model of Gaussian bluring and tomography is also implemented.
 '''
 from numpy import (empty, array, zeros, isscalar, log, pi, sqrt, log10,
-    log2, arange, concatenate, linspace, prod)
+                   log2, arange, concatenate, linspace, prod)
 from scipy.sparse import csr_matrix
 from numpy.linalg import norm
 from matplotlib import pyplot as plt
@@ -24,7 +24,7 @@ from sparse_bin import jit, FTYPE, _blur_coarse
 from sparse_ops import func, kernelMap, op, ker2meshmat2, ker2meshfunc2, sparse_matvec
 from math import (exp as c_exp, erf as c_erf, sin as c_sin, cos as c_cos, sqrt as c_sqrt, floor)
 from algorithms import (stopping_criterion, faster_FISTA, _makeVid,
-    FB, shrink, shrink_vec, FISTA)
+                        FB, shrink, shrink_vec, FISTA)
 from adaptive_spaces import sparse_function as sparse_func, sparse_FS as sparse_mesh, adaptive_func as Array
 
 
@@ -266,10 +266,12 @@ class kernelMap2D(kernelMap):
             def base_eval(i, x, y): return EXP((x - X[i, 0]) * (x - X[i, 0]) + (y - X[i, 1]) * (y - X[i, 1]))
 
             @jit(nopython=True, fastmath=True)
-            def gradx(i, x, y): return -p[1] * (x - X[i, 0]) * EXP((x - X[i, 0]) * (x - X[i, 0]) + (y - X[i, 1]) * (y - X[i, 1]))
+            def gradx(i, x, y): return -p[1] * (x - X[i, 0]) * \
+                EXP((x - X[i, 0]) * (x - X[i, 0]) + (y - X[i, 1]) * (y - X[i, 1]))
 
             @jit(nopython=True, fastmath=True)
-            def grady(i, x, y): return -p[1] * (y - X[i, 1]) * EXP((x - X[i, 0]) * (x - X[i, 0]) + (y - X[i, 1]) * (y - X[i, 1]))
+            def grady(i, x, y): return -p[1] * (y - X[i, 1]) * \
+                EXP((x - X[i, 0]) * (x - X[i, 0]) + (y - X[i, 1]) * (y - X[i, 1]))
 
             @jit(nopython=True, fastmath=True)
             def base_int(i, x0, y0, x1, y1):
[…]

### 2022-03-16 paper.tex
Measurable domains

@@
 		Suppose \edit{}{$\norm\cdot_q\lesssim \Norm\cdot$ (i.e.
-}$\F{U}\subset L^q(\Domain)$\edit{}{)} for some \edit{}{$q\in[1,\infty]$ and }connected, bounded domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{}.
+}$\F{U}\subset L^q(\Domain)$\edit{}{)} for some \edit{}{$q\in[1,\infty]$ and }connected, bounded\edit{}{, measurable} domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{}.
 We say that \edit{$\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$}{a collection $\F M$} is a \emph{mesh} if
